### 2021-01-14 Manuscript/Manuscript.Rmd
Initial commit!

---
title: "Manuscript"
author: "Angelo D'Ambrosio"
date: "14/1/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, error = F, dpi = 400)
```

## Results

### 2021-01-14 Setup.R

@@ -1,0 +1,1591 @@
+
+# Setup -------------------------------------------------------------------
+
+options(java.parameters = "-Xmx12g")
+
+if (!('librarian' %in% installed.packages())) install.packages('librarian')
+
+library(librarian)
+shelf(dplyr, stringr, readr, readxl, lubridate, Matrix, igraph, pbapply,
+			pbmcapply, rpart, bartMachine, tm, patchwork, ggplot2, scales, patchwork)
+
+required.pkgs <- setdiff(c('purrr', 'WriteXLS', 'tictoc', 'tidyr', 'arm', 'parallel'), installed.packages())
+
+if (length(required.pkgs) > 0) install.packages(required.pkgs)
+
+### Uncomment if mclapply fails on windows
+# mclapply <- lapply
+# pbmclapply <- pblapply
+
+
+if (bart_machine_num_cores() != parallel::detectCores()) {
+
+	message('Using ', parallel::detectCores(), ' cores')
+	set_bart_machine_num_cores(parallel::detectCores())
+	options(mc.cores = parallel::detectCores())
+}
+
+`%nin%` <- function (x, table) {
+	!(match(x, table, nomatch = 0L) > 0L)
+}
+
+
+# Article data management -------------------------------------------------
+
+
+read_bib <- function(files) {
+
+	pblapply(files, function(file) {
+
+		print(basename(file))
+
+		type <- NULL
+
+		if (str_detect(file, '\\.(nbib|txt)$')) {
+			entries <- read_file(file)
+
+			if (str_detect(entries, 'PMID-')) type <- 'nbib'
+
+		} else if (str_detect(file, '\\.(xlsx?|csv)$')) {
+			entries <- if (str_detect(file, '\\.csv$')) read_csv(file) else read_excel(file)
+
+			if ('UT (Unique WOS ID)' %in% colnames(entries)) type <- 'wos'
+			else if ('IEEE Terms' %in% colnames(entries)) type <- 'ieee'
+		}
+
+		if (is.null(type)) {
+			warning('Format not recognized')
+			return(NULL)
+		}
+
+		if (type == 'nbib') {
+
+			entries <- entries %>%
+				str_remove_all('\\r') %>%
+				str_replace_all('\\n\\s\\s+', ' ') %>%
+				str_split(fixed('\n\n')) %>% unlist
+
[…]

### 2021-01-14 Setup.R
feat: add summarise_by_source and ggrepel package

@@ -7,7 +7,8 @@ if (!('librarian' %in% installed.packages())) install.packages('librarian')
 
 library(librarian)
 shelf(dplyr, stringr, readr, readxl, lubridate, Matrix, igraph, pbapply,
-			pbmcapply, rpart, bartMachine, tm, patchwork, ggplot2, scales, patchwork)
+			pbmcapply, rpart, bartMachine, tm, patchwork, ggplot2, ggrepel,
+			scales, patchwork)
 
 required.pkgs <- setdiff(c('purrr', 'WriteXLS', 'tictoc', 'tidyr', 'arm', 'parallel'), installed.packages())
 
@@ -277,6 +278,15 @@ fix_duplicated_records <- function(Records) {
 
 	bind_rows(unique_sources, dup_sources) %>% select(-UID)
 }
+
+summarise_by_source <- function(file) {
+	data <- read_excel(file)
+
+	sources <- data$Source %>% str_split(., '; ') %>% unlist() %>% table()
+
+	c(setNames(as.vector(sources), names(sources)), Total = nrow(data))
+}
+
 
 
 # NLP ---------------------------------------------------------------------

### 2021-01-14 Setup.R
feat: add more info in summarise_annotations
add info about new predicted negative records and positive, negative and total manually reviewed records

@@ -1452,10 +1452,14 @@ summarise_annotations <- function(annotation.folder = 'Annotations', plot = T) {
 			status <- c(
 				Uncertain = sum(Predicted %in% 'unk'),
 				Positive = sum(Predicted %in% 'y'),
+				Negative = sum(Predicted %in% 'n'),
 				New_positive = sum(Predicted %in% 'y' & is.na(Manual)),
+				New_negative = sum(Predicted %in% 'y' & is.na(Manual)),
 				New_uncertain = with(Annotated_data, sum(Predicted_label == 'unk' & is.na(Rev_prediction))),
-				Total_positive = sum(Manual %in% 'y'),
-				Reviewed = sum(!is.na(Annotated_data$Rev_prediction)),
+				Reviewed_positive = sum(Manual %in% 'y'),
+				Reviewed_negative = sum(Manual %in% 'n'),
+				#Reviewed = sum(!is.na(Annotated_data$Rev_prediction)),
+				Reviewed = sum(!is.na(Manual)),
 				Discordant = sum(Predicted == 'check'),
 				False_positive = sum(Predicted %in% 'y' & Manual %in% 'n')
 			)

### 2021-01-14 Manuscript/Manuscript.Rmd
update
code: add cached results
text: finish initial manual labeling description

@@
 author: "Angelo D'Ambrosio"
-date: "14/1/2021"
-output: word_document
+date: "12/1/2021"
+output:
+  github_document
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F, message = F, warning = F, error = F, dpi = 400)
+```{r Setup, include=FALSE, cache=TRUE, cache.vars='annotation_summary'}
+knitr::opts_knit$set(root.dir = ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd()))
+
+print(getwd())
+
+knitr::opts_chunk$set(
+	echo = F,
+	error = F,
+	message = FALSE,
+	warning = FALSE,
+	dpi = 400
+)
+source('Setup.R')
+
+annotation_summary <- summarise_annotations(annotation.folder = "Annotations", plot = F)
 ```
@@
 ## Results
+
+```{r Results}
+
+first_query_file <- file.path("Annotations", "Records_2020-12-11", "Records_11.12.20.xlsx")
+
+sources_first_query <- summarise_by_source(first_query_file) %>% as.list()
+
+first_annotation_results <- annotation_summary %>% filter(Ord == 1, str_detect(Label,'Reviewed')) %>% {
+    df <- .
+    df$Value %>% setNames(make.names(df$Label)) %>% as.list()
+}
+```
+
+The first batch of searches, performed with the two manually curated input queries, returned `r sources_first_query$Total` unique results, specifically `r sources_first_query$Pubmed` unique results from Pubmed, `r sources_first_query$WOS` from Web of Science, and `r sources_first_query$IEEE` from IEEE.\
+Of the records retrieved using the input queries, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review.
+Of these `r with(first_annotation_results, sprintf('%d (%s)', Reviewed.positive, percent(Reviewed.positive/Reviewed)))` were labelled as positive, and `r with(first_annotation_results, sprintf('%d (%s)', Reviewed.negative, percent(Reviewed.negative/Reviewed)))` as negative.

### 2021-01-18 Setup.R
refactoring

@@ -1458,7 +1458,7 @@ summarise_annotations <- function(annotation.folder = 'Annotations', plot = T) {
 				Positive = sum(Predicted %in% 'y'),
 				Negative = sum(Predicted %in% 'n'),
 				New_positive = sum(Predicted %in% 'y' & is.na(Manual)),
-				#New_negative = sum(Predicted %in% 'n' & is.na(Manual)),
+				New_negative = sum(Predicted %in% 'n' & is.na(Manual)),
 				New_uncertain = with(Annotated_data, sum(Predicted_label == 'unk' & is.na(Rev_prediction))),
 				Reviewed_positive = sum(Manual %in% 'y'),
 				Reviewed_negative = sum(Manual %in% 'n'),
@@ -1478,8 +1478,7 @@ summarise_annotations <- function(annotation.folder = 'Annotations', plot = T) {
 			)
 		}) %>% bind_rows() %>% arrange(Date) %>%
 		mutate(
-			Ord = factor(paste(Date, str_detect(File, '_R_')), levels = unique(paste(Date, str_detect(File, '_R_')))) %>% as.numeric,
-			Label = str_replace_all(Label, c('_' = ' ', 'unc$' = 'uncertains'))
+			Ord = factor(paste(Date, str_detect(File, '_R_')), levels = unique(paste(Date, str_detect(File, '_R_')))) %>% as.numeric
 		) %>%
 		arrange(Ord)
 

### 2021-01-18 Manuscript/Manuscript.Rmd
feat: cache annotation_summary, add summary_table

@@
 
-```{r Setup, include=FALSE, cache=TRUE, cache.vars='annotation_summary'}
+```{r Setup, include=FALSE, cache.vars='annotation_summary'}
+
 knitr::opts_knit$set(root.dir = ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd()))
 
-print(getwd())
-
 knitr::opts_chunk$set(
-	echo = F,
-	error = F,
-	message = FALSE,
+	echo = FALSE,
+	error = FALSE,
+	message = T,
 	warning = FALSE,
@@
 )
+
 source('Setup.R')
 
+if (!file.exists('annotation_summary.rds')) {
 	annotation_summary <- summarise_annotations(annotation.folder = "Annotations", plot = F)
+
+	saveRDS(annotation_summary, 'annotation_summary.rds')
+} else annotation_summary <- readRDS('annotation_summary.rds')
+
 ```
@@
 
-first_annotation_results <- annotation_summary %>% filter(Ord == 1, str_detect(Label,'Reviewed')) %>% {
+first_annotation_results <- annotation_summary %>%
+	filter(Ord == 1, str_detect(Label,'Reviewed')) %>% {
 		df <- .
-    df$Value %>% setNames(make.names(df$Label)) %>% as.list()
+		df$Value %>% setNames(df$Label) %>% as.list()
 	}
+
+summary_table <- bind_rows(
+    annotation_summary %>%  filter(Ord == 1) %>% mutate(Ord = 0, File = 'Input_P_R', Value = replace(Value, !str_detect(Label, 'Reviewed'), 0)),
+    annotation_summary 
+) %>% 
+    filter(Label != 'Discordant') %>% 
+    mutate(
+        Task = case_when(str_detect(File, 'P_R') ~ 'R', T ~ 'P'),
+        Ord = Ord + 1
+    ) %>% 
+    select(Ord, Value, Total_records, Label, Task, Batch) %>% 
+    tidyr::pivot_wider(names_from = Label, values_from = Value) %>% 
+    transmute(
+        Task = Ord,
+        Task_type = .$Task,
+        across(c(Reviewed_positive, Reviewed_negative), ~ sapply(Task, function(i) {
+            ret = ''
+            if (Task_type[i] == 'R' & i != 1) {
+                prev.i <- max(Task[Task < i])
+
+                diff <- .x[i] - .x[prev.i]
+
+                if (diff != 0) ret <- paste0(' ', ifelse(diff > 0, '+', ''), diff)
+            }
+            ret
+        }), .names = "new_{.col}"),
+        Uncertain = ifelse(
+            Task_type == 'R',
+            '',
+            sprintf('%d (%s)%s', Uncertain, percent(Uncertain/Total_records), ifelse(New_uncertain > 0 , paste0(' +', New_uncertain), ''))
+        ),
+        Positive = ifelse(
+            Task_type == 'R',
+            sprintf('%d (%s)%s', Reviewed_positive, percent(Reviewed_positive/Total_records), new_Reviewed_positive),
+            sprintf('%d (%s)%s', Positive, percent(Positive/Total_records), ifelse(New_positive > 0, paste0(' +', New_positive), ''))
+        ),
+        Negative = ifelse(
+            Task_type == 'R',
+            sprintf('%d (%s)%s', Reviewed_negative, percent(Reviewed_negative/Total_records), new_Reviewed_negative),
+            sprintf('%d (%s)', Negative, percent(Negative/Total_records))
+        ),
+        Reviewed = ifelse(Task_type == 'R', Reviewed, ''),
+        Batch = factor(Batch) %>% as.numeric(),
+        New_rev_pos = NULL
+    ) %>% select(-matches('new')) %>% rename(`Task type` = Task_type) %>% group_split(Batch) %>% lapply(function(df) select(df, -Batch))
 ```
+
+### First search session
 
@@
 Of the records retrieved using the input queries, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review.
-Of these `r with(first_annotation_results, sprintf('%d (%s)', Reviewed.positive, percent(Reviewed.positive/Reviewed)))` were labelled as positive, and `r with(first_annotation_results, sprintf('%d (%s)', Reviewed.negative, percent(Reviewed.negative/Reviewed)))` as negative.
+Of these `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_positive, percent(Reviewed_positive/Reviewed)))` were labeled as positive, and `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_negative, percent(Reviewed_negative/Reviewed)))` as negative.
+
+Subsequently, cycles of prediction/review tasks were performed, in which manually reviewed records (R tasks) were used to train the ML classification algorithm which is used then to reclassify all records (P tasks).
+
+`r knitr::kable(summary_table[[1]], caption = 'Table 1.
+Prediction (P) / review (R) tasks\' results after the first query was performed.
+The Uncertain column shows the number of new labeled records not already reviewed in the precedent tasks and the possible increment compared to the previous P task.
+The Positive column has different meaning for the type of task: for the P tasks is the number of positevely labeled records followed by the number of new positives not previously reviewed, if any; for the R task, the cumulative number of positive and its increment, if any.
+The same interpretation stands for the Negative column, albeit increments are not shown for the R tasks, since the negative predictions are not reviewed.
+All values are also shown as percentege over total of records available when the task was performed.')`
+
+### Second search session

### 2021-01-18 Manuscript/Manuscript.Rmd
separate Results code into different chunks and complete paragraph

@@
 
-```{r Setup, include=FALSE, cache.vars='annotation_summary'}
+```{r Setup, include=FALSE}
 
@@
 ```{r Results}
-
-first_query_file <- file.path("Annotations", "Records_2020-12-11", "Records_11.12.20.xlsx")
-
-sources_first_query <- summarise_by_source(first_query_file) %>% as.list()
-
-first_annotation_results <- annotation_summary %>%
-	filter(Ord == 1, str_detect(Label,'Reviewed')) %>% {
-		df <- .
-		df$Value %>% setNames(df$Label) %>% as.list()
-	}
 
@@
 
+```{r Result 1}
+
+first_batch <- "Records_2020-12-11"
+
+first_query_file <- file.path("Annotations", first_batch, "Records_11.12.20.xlsx")
+
+sources_first_query <- summarise_by_source(first_query_file) %>% as.list()
+
+first_annotation_results <- annotation_summary %>%
+	filter(Ord == 1, str_detect(Label,'Reviewed')) %>% {
+		df <- .
+		df$Value %>% setNames(df$Label) %>% as.list()
+	}
+
+new_uncertains <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_uncertain') %>% pull(Value) %>% sum
+
+new_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_positive') %>% pull(Value) %>% sum
+
+task_table <- summary_table[[1]]$`Task type` %>% table
+```
+
 The first batch of searches, performed with the two manually curated input queries, returned `r sources_first_query$Total` unique results, specifically `r sources_first_query$Pubmed` unique results from Pubmed, `r sources_first_query$WOS` from Web of Science, and `r sources_first_query$IEEE` from IEEE.\
-Of the records retrieved using the input queries, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review.
+Of these records, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review.
 Of these `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_positive, percent(Reviewed_positive/Reviewed)))` were labeled as positive, and `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_negative, percent(Reviewed_negative/Reviewed)))` as negative.
@@
 Subsequently, cycles of prediction/review tasks were performed, in which manually reviewed records (R tasks) were used to train the ML classification algorithm which is used then to reclassify all records (P tasks).
+In total `r task_table[['R']] - 1` review tasks were required in addition to the initial one (tab.
+1), for a total of `r sum(new_uncertains, new_positives)` extra reviewed articles (`r new_uncertains` predicted as uncertain and `r new_positives` as positive).
+After task 11, the two susbsequent P tasks returned no uncertain or positive prediction which were not already reviewed and therefore the first cycle was termined.
 

### 2021-01-19 Manuscript/Manuscript.Rmd
update the first session results

--- 2021-01-18 Manuscript/Manuscript.Rmd
@@
 
-The first batch of searches, performed with the two manually curated input queries, returned `r sources_first_query$Total` unique results, specifically `r sources_first_query$Pubmed` unique results from Pubmed, `r sources_first_query$WOS` from Web of Science, and `r sources_first_query$IEEE` from IEEE.\
-Of the records retrieved using the input queries, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review.
+```{r Result 1}
+
+first_batch <- "Records_2020-12-11"
+
+first_query_file <- file.path("Annotations", first_batch, "Records_11.12.20.xlsx")
+
+sources_first_query <- summarise_by_source(first_query_file) %>% as.list()
+
+first_annotation_results <- annotation_summary %>%
+	filter(Ord == 1, str_detect(Label,'Reviewed')) %>% {
+		df <- .
+		df$Value %>% setNames(df$Label) %>% as.list()
+	}
+
+new_uncertains <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_uncertain') %>% pull(Value) %>% sum()
+
+new_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_positive') %>% pull(Value) %>% sum()
+
+all_unique_reviews <- annotation_summary %>% filter(Batch == first_batch & Label == 'Reviewed') %>% pull(Value) %>% max()
+
+task_table <- summary_table[[1]]$`Task type` %>% table()
+
+final_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'Reviewed_positive') %>% pull(Value) %>% max()
+```
+
+The first session of searches, performed using the two manually curated input queries, returned `r sources_first_query$Total` unique results, specifically `r sources_first_query$Pubmed` unique results for Pubmed, `r sources_first_query$WOS` for Web of Science, and `r sources_first_query$IEEE` for IEEE.\
+Of these records, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review.
 Of these `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_positive, percent(Reviewed_positive/Reviewed)))` were labeled as positive, and `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_negative, percent(Reviewed_negative/Reviewed)))` as negative.
 
-Subsequently, cycles of prediction/review tasks were performed, in which manually reviewed records (R tasks) were used to train the ML classification algorithm which is used then to reclassify all records (P tasks).
+Subsequently, cycles of prediction/review tasks were performed, in which manually reviewed records (R tasks) were used to train the ML classification algorithm which is then used to reclassify all records (P tasks).
+After task 11, two susbsequent P tasks returned no uncertain or positive unreviewed predictions, therefore the first session was termined.
+In total `r task_table[['R']] - 1` review tasks were required in addition to the initial manual classification (tab.
+1), for a total of `r sum(new_uncertains, new_positives)` extra reviewed articles (`r new_uncertains` predicted as uncertain and `r new_positives` as positive).\
+Overall `r new_uncertains + new_positives + first_annotation_results$Reviewed` classification/review actions on `r all_unique_reviews` records were required, that is the `r percent((new_uncertains + new_positives + first_annotation_results$Reviewed)/sources_first_query$Total)` of the total number of records (`r sources_first_query$Total`) collected in the first session, while the rest was classified automatically as non-relevant.
+The dataset at the end of the session contained a total of `r final_positives` positive records (+`r final_positives - first_annotation_results$Reviewed_positive` positive records compared to the initial manual classification).
 
@@
 The same interpretation stands for the Negative column, albeit increments are not shown for the R tasks, since the negative predictions are not reviewed.
-All values are also shown as percentege over total of records available when the task was performed.')`
+All values are also shown as percentege over total of records available in the session.')`
 

### 2021-01-19 Manuscript/Manuscript.Rmd
add perfomance estimates

@@
 
-if (!file.exists('annotation_summary.rds')) {
+bkp_file <- file.path('Manuscript', 'annotation_summary.rds')
+
+if (!file.exists(bkp_file)) {
 	annotation_summary <- summarise_annotations(annotation.folder = "Annotations", plot = F)
 
-	saveRDS(annotation_summary, 'annotation_summary.rds')
-} else annotation_summary <- readRDS('annotation_summary.rds')
+	saveRDS(annotation_summary, bkp_file)
+} else annotation_summary <- readRDS(bkp_file)
 
@@
 	tidyr::pivot_wider(names_from = Label, values_from = Value) %>%
+	mutate(across(c(Reviewed_positive, Reviewed_negative, Uncertain, Positive, Negative), as.numeric)) %>% 
 	transmute(
@@
 		Reviewed = ifelse(Task_type == 'R', Reviewed, ''),
+		across(c(AUC, Sensitivity, Specificity), ~ ifelse(Task_type == 'P', .x, ''), .names = '{.col} [98% Cr.I.]'),
 		Batch = factor(Batch) %>% as.numeric(),
@@
 		df <- .
-		df$Value %>% setNames(df$Label) %>% as.list()
+		df$Value %>% as.numeric() %>% setNames(df$Label) %>% as.list()
 	}
 
-new_uncertains <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_uncertain') %>% pull(Value) %>% sum()
+new_uncertains <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_uncertain') %>% pull(Value) %>% as.numeric() %>% sum()
 
-new_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_positive') %>% pull(Value) %>% sum()
+new_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_positive') %>% pull(Value) %>% as.numeric() %>% sum()
 
-all_unique_reviews <- annotation_summary %>% filter(Batch == first_batch & Label == 'Reviewed') %>% pull(Value) %>% max()
+all_unique_reviews <- annotation_summary %>% filter(Batch == first_batch & Label == 'Reviewed') %>% pull(Value) %>% as.numeric() %>% max()
 
@@
 
-final_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'Reviewed_positive') %>% pull(Value) %>% max()
+final_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'Reviewed_positive') %>% pull(Value) %>% as.numeric() %>% max()
+
+AUC_vec <- annotation_summary %>% filter(Batch == first_batch & Label == 'AUC') %>% pull(Value)
 ```
@@
 Overall `r new_uncertains + new_positives + first_annotation_results$Reviewed` classification/review actions on `r all_unique_reviews` records were required, that is the `r percent((new_uncertains + new_positives + first_annotation_results$Reviewed)/sources_first_query$Total)` of the total number of records (`r sources_first_query$Total`) collected in the first session, while the rest was classified automatically as non-relevant.
-The dataset at the end of the session contained a total of `r final_positives` positive records (+`r final_positives - first_annotation_results$Reviewed_positive` positive records compared to the initial manual classification).
+The dataset at the end of the session contained a total of `r final_positives` positive records (+`r final_positives - first_annotation_results$Reviewed_positive` positive records compared to the initial manual classification).\
+The ML algorithm showed a gradually improving out-of-bag performance, ranging from `r AUC_vec[1]` for the first predictive task to `r last(AUC_vec)` for the last, with the sensitivity always keeping an edge over the specificity, as per the model intentions.
 
-`r knitr::kable(summary_table[[1]], caption = 'Table 1.
+`r knitr::kable(summary_table[[1]], caption = '**Table 1**.
 Prediction (P) / review (R) tasks\' results after the first query was performed.
@@
 The same interpretation stands for the Negative column, albeit increments are not shown for the R tasks, since the negative predictions are not reviewed.
-All values are also shown as percentege over total of records available in the session.')`
+All values are also shown as percentege over total of records available in the session.
+Also, out-of-bag AUC, sensitivity and specificity are reported, computed as decribed in the methods, with the respective 98% Cr.I.')`
 

### 2021-01-19 Setup.R

@@ -1444,7 +1444,10 @@ summarise_annotations <- function(annotation.folder = 'Annotations', plot = T) {
 	Res <- list.files(annotation.folder, recursive = T, pattern = 'Records_P') %>%
 		str_subset('~\\$', negate = T) %>%
 		pbmclapply(function(file) {
+
 			Annotated_data <- read_excel(file.path('Annotations', file))
+			Performance <- read_excel(file.path('Annotations', file), sheet = 'Out_of_sample_perf')
+			Performance <- as.list(Performance$Value) %>% setNames(Performance$Indicator)
 
 			Predicted <- Annotated_data$Predicted_label
 			Manual <- with(Annotated_data, case_when(
@@ -1464,7 +1467,10 @@ summarise_annotations <- function(annotation.folder = 'Annotations', plot = T) {
 				Reviewed_negative = sum(Manual %in% 'n'),
 				Reviewed = sum(!is.na(Manual)),
 				Discordant = sum(Predicted == 'check'),
-				False_positive = sum(Predicted %in% 'y' & Manual %in% 'n')
+				False_positive = sum(Predicted %in% 'y' & Manual %in% 'n'),
+				AUC = Performance$AUC,
+				Sensitivity = Performance$Sens,
+				Specificity = Performance$Spec
 			)
 
 			data.frame(

### 2021-01-19 Manuscript/Manuscript.Rmd
add important keywords in the first session results

@@
 
+final_keywords <- annotation_summary %>% filter(Batch == first_batch & Label == 'Important_vars') %>% pull(Value) %>% last()
+
 AUC_vec <- annotation_summary %>% filter(Batch == first_batch & Label == 'AUC') %>% pull(Value)
@@
 The dataset at the end of the session contained a total of `r final_positives` positive records (+`r final_positives - first_annotation_results$Reviewed_positive` positive records compared to the initial manual classification).\
-The ML algorithm showed a gradually improving out-of-bag performance, ranging from `r AUC_vec[1]` for the first predictive task to `r last(AUC_vec)` for the last, with the sensitivity always keeping an edge over the specificity, as per the model intentions.
+The ML algorithm showed a gradually improving out-of-bag performance, ranging from `r AUC_vec[1]` for the first predictive task to `r last(AUC_vec)` for the last, with the sensitivity always keeping an edge over the specificity, as per the model intentions.\
+The 15 most important keywords for the ML algorithm at the end of the session were: *`r final_keywords`*.
 

### 2021-01-19 Setup.R

@@ -1215,7 +1215,7 @@ enrich_annotation_file <- function(file, DTM = NULL, pos.mult = 10,
 	out$Prediction_matrix <- avg_preds
 	out$DTM <- DTM
 
-	readr::write_rds(out, file.path('Models', paste0('Results_', time_stamp, '.rds')))
+	readr::write_rds(out, file.path('Models', paste0('Results_', time_stamp, '.rds')), compress = 'gz', )
 	tictoc::toc()
 
 	invisible(out)
@@ -1446,8 +1446,18 @@ summarise_annotations <- function(annotation.folder = 'Annotations', plot = T) {
 		pbmclapply(function(file) {
 
 			Annotated_data <- read_excel(file.path('Annotations', file))
+
 			Performance <- read_excel(file.path('Annotations', file), sheet = 'Out_of_sample_perf')
 			Performance <- as.list(Performance$Value) %>% setNames(Performance$Indicator)
+
+			Var_imp <- read_excel(file.path('Annotations', file), sheet = 'Variable_importance') %>%
+				filter(!str_detect(Term, 'MESH|KEYS')) %>%
+				mutate(Term = str_remove(Term, '.+__')) %>%
+				group_by(Term) %>% slice_max(order_by = Score) %>% ungroup() %>%
+				arrange(desc(Score)) %>% pull(Term) %>% head(15) %>%
+				str_replace('^\\w', str_to_upper) %>%
+				str_replace_all(c('\\._\\.' = ' ', '\\.' = ' OR ', '_' = ' ')) %>%
+				paste(collapse =', ')
 
 			Predicted <- Annotated_data$Predicted_label
 			Manual <- with(Annotated_data, case_when(
@@ -1470,7 +1480,8 @@ summarise_annotations <- function(annotation.folder = 'Annotations', plot = T) {
 				False_positive = sum(Predicted %in% 'y' & Manual %in% 'n'),
 				AUC = Performance$AUC,
 				Sensitivity = Performance$Sens,
-				Specificity = Performance$Spec
+				Specificity = Performance$Spec,
+				Important_vars = Var_imp
 			)
 
 			data.frame(

### 2021-02-07 Setup.R
feat(records): add function import previous classifications

@@ -926,6 +926,7 @@ order_by_query_match <- function(records, query) {
 
 save_annotation_file <- function(records, reorder_query = NULL,
 																 prev_annotation = NULL,
+																 prev_classification = NULL,
 																 annotation_folder = 'Annotations',
 																 session_name = 'Session1',
 																 out_type = c('xlsx', 'csv')) {
@@ -969,6 +970,7 @@ save_annotation_file <- function(records, reorder_query = NULL,
 		)
 
 	if (!is.null(prev_annotation) && file.exists(prev_annotation)) {
+		message('- appending to a previous annotation file')
 
 		if (str_detect(prev_annotation, '\\.xlsx?$')) {
 			prev_records <- read_excel(prev_annotation)
@@ -985,10 +987,17 @@ save_annotation_file <- function(records, reorder_query = NULL,
 				Parent_file = prev_annotation,
 			) %>%
 			fix_duplicated_records()
-
 	}
 
-	records <- records %>% arrange(Order)
+	if (!is.null(prev_classification) && file.exists(prev_classification)) {
+		message('- importing previous classifications')
+
+		if (str_detect(prev_classification, '\\.xlsx?$')) {
+			prev_records <- read_excel(prev_classification)
+		} else prev_records <- read_csv(prev_classification, col_types = cols())
+
+		records <- import_classification(records, prev_records = prev_records)
+	}
 
 	message('- saving records...')
 
@@ -1033,16 +1042,66 @@ fix_duplicated_records <- function(Records) {
 }
 
 summarise_by_source <- function(annotation_file) {
-	data <- if (is.character(annotation_file)) read_excel(annotation_file) else annotation_file
+	data <- if (is.character(annotation_file)) {
+		read_excel(annotation_file)
+		} else annotation_file
 
 	sources <- data$Source %>% str_split(., '; ') %>% unlist() %>% table()
 
 	c(setNames(as.vector(sources), names(sources)), Total = nrow(data))
 }
 
+import_classification <- function(records, IDs = records$ID, prev_records) {
+	records$uID = str_to_lower(records$Title) %>%
+		str_remove_all('[^\\w\\d\\s]+')
+	prev_records$uID = str_to_lower(prev_records$Title) %>%
+		str_remove_all('[^\\w\\d\\s]+')
+
[…]

### 2021-02-07 Setup.R
perf: use openxlsx instead of WriteXLS since it's faster

@@ -11,7 +11,7 @@ shelf(dplyr, stringr, glue, readr, readxl, lubridate, Matrix, igraph, pbapply,
 			patchwork)
 
 # Packages required but not loaded
-required.pkgs <- setdiff(c('purrr', 'WriteXLS', 'tictoc', 'tidyr', 'arm',
+required.pkgs <- setdiff(c('purrr', 'openxlsx', 'tictoc', 'tidyr', 'arm',
 													 'parallel', 'jsonlite', 'rentrez',
 													 'wosr'), installed.packages())
 
@@ -744,7 +744,7 @@ perform_search_session <- function(query, year_query = NULL, actions = c('API', 
 			write_fun <- write_csv
 			read_fun <- function(x) read_csv(x, col_types = cols())
 		} else if (str_detect(journal, '\\.xlsx?$')) {
-			write_fun <- WriteXLS::WriteXLS
+			write_fun <- function(x, file) openxlsx::write.xlsx(x, file, asTable = T)
 			read_fun <- read_excel
 		} else stop('Session journal file type must be csv or excel.')
 
@@ -1007,7 +1007,7 @@ save_annotation_file <- function(records, reorder_query = NULL,
 	file <- file.path(folder, paste0('Records_', safe_now(), '.', out_type))
 
 	if (out_type == 'xlsx') {
-		WriteXLS::WriteXLS(records, ExcelFileName = file)
+		openxlsx::write.xlsx(records, file = file, asTable = T)
 	} else write_csv(records, file = file)
 
 	invisible(records)
@@ -2031,14 +2031,16 @@ enrich_annotation_file <- function(file, DTM = NULL, pos.mult = 10,
 
 	time_stamp <- safe_now()
 
-	WriteXLS::WriteXLS(out, ExcelFileName = file.path('Annotations', paste0('Records_P_', time_stamp, '.xlsx')))
+	output_file <- file.path('Annotations', paste0('Records_P_', time_stamp, '.xlsx'))
+	openxlsx::write.xlsx(out, file = output_file, asTable = T)
 	tictoc::toc()
 
 	tictoc::tic()
 	out$Prediction_matrix <- avg_preds
 	out$DTM <- DTM
 
-	readr::write_rds(out, file.path('Models', paste0('Results_', time_stamp, '.rds')), compress = 'gz', )
+	output_file <- file.path('Models', paste0('Results_', time_stamp, '.rds'))
[…]

### 2021-02-07 Protocol.Rmd
First section

# Research Protocol

This document will guide the reader along the steps to utilize the framework and reproduce our results.

## Acquisition of the records

Once the framework is loaded, the user defines an initial search query which needs to be as specific as possible while still generating a sufficient number of positive matches:

```{r setup}
source('Setup.R') # Load the framework

# Initial query to be built on domain knowledge
query <- '((model OR models OR modeling OR network OR networks) AND (dissemination OR transmission OR spread OR diffusion) AND (nosocomial OR hospital OR "long-term-care" OR "long term care" OR "longterm care" OR "long-term care" OR "healthcare associated") AND (infection OR resistance OR resistant))'

# Year filter. The framework convert it to the API specific format seamlessly.
# common logical comparators can be used, i.e. <, <=, >, >=, while dashes
# denotes inclusive date intervals. A single year restricts results to one year
# period.
year_filter <- '2010-2020'

```

The query is passed to the `perform_search_session()` function, together with an unique identifier for the **search session** and **search query**. A session identifies a homogeneus group of complementary or alternative queries (e.g. sometimes it is easier to create two different simpler queries than a complex and long one that returns the same results).\
In our implementation we define as sessions the group of actions that includes the utilization of a search query and the subsequent cycle of manual review and relevancy prediction of its results.\

`perform_search_session()` will use common scientific research database APIs (at the moment Pubmed, Web of Science and IEEE) to look for records related to query, store them on the disk and returns or update **journal** (a csv/excel file) with all info about sessions, queries and search results. The records will be stored in folders with the following structure: Records/\*session_id\*/\*query_id\*.
If manually downloaded results are already available, users can create these folders manually and put the data there (the file name needs to contain the source name as written in the `sources` argument) and the function will acquire and parse them.\
Users can choose whether to perform an API search, parse already downloaded, or do both using the `actions` argument.

Note that for Pubmed, the API search may return slightly less records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the .nbib file in the Session/Query folder. `perform_search_session()` will acquire them seamlessly.

```{r perform searches}
# This call will perform an API search on Pubmed, WOS and IEEE services and/or
# (based on the `actions` argument) parse already downloaded data (.csv format
# for IEEE, .xls for WOS and .nbib for Pubmed).
# Set overwrite = TRUE to overwrite previously dowloaded/parsed records
journal <- perform_search_session(query = query, year_query = year_filter,
																	session_name = 'Session1', query_name = 'Query1',
																	records_folder = 'Records',
																	journal = 'Session_journal.csv')

```

Once the records are stored, they must be read and merged into an **annotation file** where the initial manual review of the records will be perfomed.\
A series of functions are available to prepare the data for manual evaluation:

```{r managing records}
# Extract the file paths of records. Arguments can be used to filter by session
# query, source. Only parsed files will be returned, not the raw ones downloaded
# manually.
Annotation_data <- extract_source_file_paths(journal) %>%

	# Read record files. Will parse them if raw data downloaded manually (not
	# necessary in this case). Return a list of records, one per file.
	read_bib_files() %>%

	# Join a list of records into one dataframe, solving duplicated records
	join_records() %>%

	# Order records by the sum of relative frequency of the query terms in the
	# title + abstract. Increases the chance of encountering relevant records at
	# the beginning of the manual classification.
	order_by_query_match(query) %>%

	# Add fields for the manual classification
	mutate(
			Rev_manual = NA,
			Rev_prediction = NA,
			.before = DOI
		)

# Store the file
dir.create(file.path('Annotations', 'Session1'))
folder <- file.path('Annotations', 'Session1')
dir.create(folder, recursive = T)
file <- file.path(folder, paste0('Records_', safe_now(), '.xlsx'))
WriteXLS::WriteXLS(records, ExcelFileName = file)
```

Actually all these step are more easily performed by `save_annotation_file()`. This function can take as input either the path to record files, or the parsed records (one data frame or a list of data frames) or a group of folders where to look for files into. In addition, it also allows to add the new records to a previous annotation file (arg `prev_annotation`), useful with subsequent searching sessions with different queries. Finally, previous manual classifications of the new records can be imported using `prev_classification`.

```{r save annotation file}
# This function extract the appropriate file paths from a session journal. By
# default it passes all stored files, otherwise it can be filtered by session,
# query, and source (i.e. Pubmed, WOS, IEEE)
record_files <- extract_source_file_paths(journal)

# save_annotation_file accept a great variety of inputs:

	# record file paths
save_annotation_file(record_files, session_name = 'Session1')

	# specific record file folders
save_annotation_file(file.path('Records', 'Session1'), session_name = 'Session1')

	# or parent folders, since it search for files recursively
save_annotation_file(file.path('Records'), session_name = 'Session1')

	# finally it can accept the already parsed files
read_bib_files(record_files) %>% save_annotation_file(session_name = 'Session1')

```

Notice that the framework is `tidyverse` friendly and the precedent steps can be all performed in one call (which is the suggested procedure):

```{r one call}
Records <- perform_search_session(query = query, year_query = year_filter,
											 session_name = 'Session1', query_name = 'Query1',
											 journal = 'Session_journal.csv') %>% # perform searches and parse files; save and return the journal
	extract_source_file_paths() %>% # return the record file paths
	save_annotation_file(reorder_query = query, session_name = 'Session1') # save and return the joined data
```

Now the annotation file is ready for manual classification of relevant and non-relevant records.

### 2021-02-07 Setup.R
fix(record_search): fix clean_record_textfields

@@ -771,9 +771,9 @@ perform_search_session <- function(query, year_query = NULL, actions = c('API', 
 clean_record_textfields <- function(df) {
 	mutate(df,
 				 across(where(is.character),
-				 			 ~ str_replace_all(c(' +;' = ';', '["\']+' = ' ')) %>%
+				 			 ~ str_replace_all(.x, c(' +;' = ';', '["\']+' = ' ')) %>%
 				 			 	str_squish() %>%
-				 			 	replace(.x, .x %in% c('', 'NA'), NA)
+				 			 	{replace(., . %in% c('', 'NA'), NA)}
 				 )
 	)
 }

### 2021-02-10 Setup.R
fix(records): improve deduplication

@@ -1059,15 +1059,22 @@ save_annotation_file <- function(records, reorder_query = NULL,
 	invisible(records)
 }
 
-fix_duplicated_records <- function(Records) {
-	Records <- Records %>% mutate(
-		UID = str_to_lower(Title) %>% str_remove_all('[^\\w\\d\\s]+')
-	)
+fix_duplicated_records <- function(records) {
+	records <- records %>%
+		mutate(
+			UID = str_to_lower(Title) %>% str_remove_all('[^\\w\\d]+')
+		) %>%
+		group_by(UID) %>%
+		mutate(DOI = na.omit(DOI)[1]) %>%
+		ungroup() %>%
+		mutate(
+			UID = ifelse(is.na(DOI), UID, DOI)
+		)
 
-	dup_recs <- Records$UID[duplicated(Records$UID) | duplicated(Records$DOI)]
+	dup_recs <- records$UID[duplicated(records$UID)]
 
-	unique_sources <- Records %>% filter(!(UID %in% dup_recs))
-	dup_sources <- Records %>% filter(UID %in% dup_recs)
+	unique_sources <- records %>% filter(!(UID %in% dup_recs))
+	dup_sources <- records %>% filter(UID %in% dup_recs)
 
 	dup_sources <- dup_sources %>%
 		group_by(UID) %>%
@@ -1075,10 +1082,11 @@ fix_duplicated_records <- function(Records) {
 			Order = min(Order),
 			across(any_of(c('Title', 'Abstract', 'Authors', 'Journal', 'Journal_short',
 											'Year', "Pred_delta", "Pred_Med", "Pred_Low", "Pred_Up")),
-						 ~ last(na.omit(.x))),
+						 ~ na.omit(.x)[1]),
 			across(any_of(c('ID', 'DOI', 'URL', 'Mesh', 'Article_type', 'Source',
 											'Source_type', 'FileID', "Rev_manual", "Rev_prediction",
-											"Predicted_label")), ~ na.omit(.x) %>% unique() %>% paste(collapse = '; ')),
+											"Rev_previous", "Predicted_label")),
+						 ~ na.omit(.x) %>% unique() %>% paste(collapse = '; ')),
 			Keywords = Keywords %>% str_split('; ') %>% unlist() %>% na.omit() %>% unique() %>%
 				purrr::keep(~ str_length(.x) > 0) %>%
 				paste(collapse = '; '),
[…]

### 2021-02-10 Setup.R
feat(records): save_annotation_file accept also data for prev_annotation/classification

@@ -1009,11 +1009,16 @@ save_annotation_file <- function(records, reorder_query = NULL,
 
 	if (!is.null(prev_annotation)) {
 		message('- appending to a previous annotation file')
-		if (!file.exists(prev_annotation)) stop(prev_annotation, ' do not exist')
+		if (is.character(prev_annotation)) {
+			if (!file.exists(prev_annotation)) stop(prev_annotation, ' do not exist')
 
-		if (str_detect(prev_annotation, '\\.xlsx?$')) {
-			prev_records <- read_excel(prev_annotation)
-		} else prev_records <- read_csv(prev_annotation, col_types = cols())
+			if (str_detect(prev_annotation, '\\.xlsx?$')) {
+				prev_records <- read_excel(prev_annotation)
+			} else prev_records <- read_csv(prev_annotation, col_types = cols())
+		} else if (is.data.frame(prev_annotation)) {
+			prev_records <- prev_annotation
+			prev_annotation <- NULL
+		} else stop('prev_annotation must be a file path or a data.frame')
 
 		records <- records %>% filter(!(ID %in% prev_records$ID))
 
@@ -1030,11 +1035,15 @@ save_annotation_file <- function(records, reorder_query = NULL,
 
 	if (!is.null(prev_classification)) {
 		message('- importing previous classifications')
-		if (!file.exists(prev_classification)) stop(prev_classification, ' do not exist')
+		if (is.character(prev_classification)) {
+			if (!file.exists(prev_classification)) stop(prev_classification, ' do not exist')
 
-		if (str_detect(prev_classification, '\\.xlsx?$')) {
-			prev_records <- read_excel(prev_classification)
-		} else prev_records <- read_csv(prev_classification, col_types = cols())
+			if (str_detect(prev_classification, '\\.xlsx?$')) {
+				prev_records <- read_excel(prev_classification)
+			} else prev_records <- read_csv(prev_classification, col_types = cols())
+		} else if (is.data.frame(prev_annotation)) {
+			prev_records <- prev_classification
+		} else stop('prev_annotation must be a file path or a data.frame')
 
 		records <- import_classification(records, prev_records = prev_records)
 	}

### 2021-02-10 Manuscript/Protocol.Rmd
update

--- 2021-02-07 Protocol.Rmd
@@
+---
+title: "Study protocol"
+date: Feb 1, 2021
+author:
+  - first_name: "Angelo"
+    last_name: "D'Ambrosio"
+    url: http://github.com/bakaburg1/
+    affiliation: Institute for Infection Prevention and Hospital Hygiene, Freiburg University Hospital
+    affiliation_url: https://www.uniklinik-freiburg.de/iuk.html
+    orcid_id: 0000-0002-2045-5155
+output: distill::distill_article
+---
+
 # Research Protocol
@@
 
-```{r setup}
+```{r setup, echo = TRUE, eval = FALSE}
 source('Setup.R') # Load the framework
@@
 
-`perform_search_session()` will use common scientific research database APIs (at the moment Pubmed, Web of Science and IEEE) to look for records related to query, store them on the disk and returns or update **journal** (a csv/excel file) with all info about sessions, queries and search results.
-The records will be stored in folders with the following structure: Records/\*session_id\*/\*query_id\*.
-If manually downloaded results are already available, users can create these folders manually and put the data there (the file name needs to contain the source name as written in the `sources` argument) and the function will acquire and parse them.\
-Users can choose whether to perform an API search, parse already downloaded, or do both using the `actions` argument.
+`perform_search_session()` will use common scientific research database APIs (at the moment Pubmed/Medline, Web of Science and IEEE) to look for records related to query, store them in a csv format and returns or update **journal** (a csv or excel file) with all the information about sessions, queries and search results.
+The records will be stored in folders with the following structure: Records/\*session_id\*/\*query_id\*.\
+If manually downloaded results are already available, users can create these folders manually and put the data there (the file name needs to contain the source name as written in the `sources` argument) and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g.
+Pubmed1.nbib, Pubmed2.nib, etc.).
+In addition of Pubmed, WOS and IEEE, this method permits to import also Embase and Scopus records, for which an API search was not yet implemented.\
+Users can choose whether to perform an API search, parse already downloaded results, or both using the `actions` argument.
 
@@
 
-```{r perform searches}
+```{r perform searches, echo = TRUE, eval = FALSE}
 # This call will perform an API search on Pubmed, WOS and IEEE services and/or
-# (based on the `actions` argument) parse already downloaded data (.csv format
-# for IEEE, .xls for WOS and .nbib for Pubmed).
-# Set overwrite = TRUE to overwrite previously dowloaded/parsed records
+# (based on the `actions` argument) parse already downloaded data (in our case, additional Pubmed results and Embase and Scopus results) manually added to the Session1/Query1 folder.
 journal <- perform_search_session(query = query, year_query = year_filter,
@@
 
-Once the records are stored, they must be read and merged into an **annotation file** where the initial manual review of the records will be perfomed.\
-A series of functions are available to prepare the data for manual evaluation:
+Once the records are stored, they must be read and merged into an **annotation file** where the initial manual review of the records will be performed.\
+A series of functions are available to prepare the data for the manual evaluation:
 
-```{r managing records}
+```{r managing records, echo = TRUE, eval = FALSE}
 # Extract the file paths of records. Arguments can be used to filter by session
@@
 
-	# Order records by the sum of relative frequency of the query terms in the
-	# title + abstract. Increases the chance of encountering relevant records at
+	# Order records by the relative frequency of the query terms in the
+	# title + abstract text. Increases the chance of encountering relevant records at
 	# the beginning of the manual classification.
@@
 	mutate(
-			Rev_manual = NA,
-			Rev_prediction = NA,
+			Rev_manual = NA, # Where the first manual classification will be made
+			Rev_prediction = NA, # Column for the evaluation of the predicted classes
 			.before = DOI
@@
 Actually all these step are more easily performed by `save_annotation_file()`.
-This function can take as input either the path to record files, or the parsed records (one data frame or a list of data frames) or a group of folders where to look for files into.
+This function can take as input either the path to record files, or the parsed records (one data frame or a list of data frames) or a group of folders where to look for files into./
 In addition, it also allows to add the new records to a previous annotation file (arg `prev_annotation`), useful with subsequent searching sessions with different queries.
-Finally, previous manual classifications of the new records can be imported using `prev_classification`.
+Finally, previous manual classifications of records can be imported using `prev_classification`.
 
-```{r save annotation file}
+```{r save annotation file, echo = TRUE, eval = FALSE}
 # This function extract the appropriate file paths from a session journal. By
@@
 
-Notice that the framework is `tidyverse` friendly and the precedent steps can be all performed in one call (which is the suggested procedure):
+Notice that the framework is "chaining" friendly and the precedent steps can be all performed in one call (which is the suggested procedure):
 
-```{r one call}
+```{r one call, echo = TRUE, eval = FALSE}
+# First create the Records/Session1/Query1 folder and put the manually downloaded files there if you have any. Otherwise the folders will be created automatically
 Records <- perform_search_session(query = query, year_query = year_filter,
@@
 	extract_source_file_paths() %>% # return the record file paths
-	save_annotation_file(reorder_query = query, session_name = 'Session1') # save and return the joined data
+	save_annotation_file(reorder_query = query, session_name = 'Session1') # read, join, reorder records and save them in the Annotations folder
 ```
 
+## Manual classification and prediction
+
 Now the annotation file is ready for manual classification of relevant and non-relevant records.
+The annotation file has a column called `Rev_manual`, where records will be classified as 'y' or 'n'.
+The suggestion is to classify manually until the rate of positive start to flatten out./
+The function `check_classification_trends` can help to visualize the trend of the positives/negatives as the number of classified records increases./s
+For a limited number of records, abstracts were not present in the API output for Web of Science; it was needed to retrieve them manually from the internet where if existing and add them to the annotation file.

### 2021-02-10 Setup.R
fix(records): fix wrong variable name

@@ -1041,9 +1041,9 @@ save_annotation_file <- function(records, reorder_query = NULL,
 			if (str_detect(prev_classification, '\\.xlsx?$')) {
 				prev_records <- read_excel(prev_classification)
 			} else prev_records <- read_csv(prev_classification, col_types = cols())
-		} else if (is.data.frame(prev_annotation)) {
+		} else if (is.data.frame(prev_classification)) {
 			prev_records <- prev_classification
-		} else stop('prev_annotation must be a file path or a data.frame')
+		} else stop('prev_classification must be a file path or a data.frame')
 
 		records <- import_classification(records, prev_records = prev_records)
 	}

### 2021-03-22 Manuscript/Protocol.Rmd
reorganize comments

@@
 ```{r one call, echo = TRUE, eval = FALSE}
-# First create the Records/Session1/Query1 folder and put the manually downloaded files there if you have any. Otherwise the folders will be created automatically
+# First create the Records/Session1/Query1 folder and put the manually
+# downloaded files there if you have any. Otherwise the folders will be created
+# automatically
+
+# perform searches and parse files; save and return the journal
 Records <- perform_search_session(query = query, year_query = year_filter,
 											 session_name = 'Session1', query_name = 'Query1',
-											 journal = 'Session_journal.csv') %>% # perform searches and parse files; save and return the journal
-	extract_source_file_paths() %>% # return the record file paths
-	save_annotation_file(reorder_query = query, session_name = 'Session1') # read, join, reorder records and save them in the Annotations folder
+											 journal = 'Session_journal.csv') %>% 
+	# return the record file paths
+	extract_source_file_paths() %>%
+	# read, join, reorder records and save them in the Sessions folder
+	save_annotation_file(reorder_query = query, session_name = 'Session1') 
 ```

### 2021-03-22 Setup.R
multiple changes
- remove duplicated package
- add brms package
- many comments improvements
- add function to describe a string vector
- add function to import an excel if the argument is a file path, otherwise return a data.frame if passed directly
- use coalesce() instead of ifelse() in multiple places for managing NA exceptions
- reorganize the folder in structure under a main Sessions folder (TODO: put also Records there)
- remove Rev_prediction when generating the first annotation file
- introduce the coalesce_labels function to join multiple labels
- increase the number of iterations in

@@ -7,13 +7,12 @@ if (!('librarian' %in% installed.packages())) install.packages('librarian')
 
 library(librarian)
 shelf(dplyr, stringr, glue, readr, readxl, lubridate, Matrix, igraph, pbapply,
-			pbmcapply, rpart, bartMachine, tm, patchwork, ggplot2, ggrepel, RLesur/crrri,
-			patchwork)
+			pbmcapply, rpart, bartMachine, tm, patchwork, ggplot2, ggrepel, RLesur/crrri)
 
 # Packages required but not loaded
 required.pkgs <- setdiff(c('purrr', 'openxlsx', 'tictoc', 'tidyr', 'arm',
 													 'parallel', 'jsonlite', 'rentrez',
-													 'wosr'), installed.packages())
+													 'wosr', 'brms'), installed.packages())
 
 if (length(required.pkgs) > 0) install.packages(required.pkgs)
 
@@ -32,7 +31,6 @@ if (bart_machine_num_cores() != parallel::detectCores()) {
 # Easier to use than !(a %in% b)
 '%nin%' <- Negate('%in%')
 
-
 # Nicer output than scales::percent()
 percent <- function(x) {
 	sapply(x, function(x) {
@@ -46,8 +44,20 @@ percent <- function(x) {
 	})
 }
 
+# override lubridate equivalents which always complain about the missing timezone
 today <- function() as_date(Sys.time())
 now <- function() Sys.time()
+
+# A file path friendly lubridate::now()
+safe_now <- function() {
+	str_replace_all(now(), c(' ' = 'T', ':' = '.'))
+}
+
+summarise_vector <- function(vec) {
+	if (length(vec) == 0) return(0)
+	table(vec) %>%
+		{paste0(names(.), ': ', ., ' (', percent(./sum(.)), ')', collapse = ', ')}
+}
 
 # Tool to grab XHR messages from dynamic websites
 get_website_resources <- function(url, url_filter = '.*', type_filter = '.*',
@@ -107,9 +117,14 @@ get_website_resources <- function(url, url_filter = '.*', type_filter = '.*',
 	}, timeouts = max(wait_for + 3, 30), cleaning_timeout = max(wait_for + 3, 30))
 }
 
-
-# A file path friendly lubridate::now()
-safe_now <- function() str_replace_all(now(), c(' ' = 'T', ':' = '.'))
[…]

### 2021-05-05 Setup.R
feat: add function that return the latest file in an annotation session

@@ -1150,7 +1150,7 @@ create_session <- function(Records, session_name,
 		switch(dup_session_action,
 					 silent = {
 					 	return(session_path)
-					 }
+					 },
 					 skip = {
 					 	warning('Session "', session_name, '" exists. Skipping...')
 					 	return(session_path)
@@ -1181,6 +1181,23 @@ create_session <- function(Records, session_name,
 
 	return(session_path)
 }
+
+get_last_annotation_file <- function(session_path) {
+	files <- list.files(session_path, recursive = T) %>% str_subset('Records')
+
+	if (length(files) == 0) return(NULL)
+
+	last_record_file <- tibble(
+		files,
+		iter = basename(files) %>%
+			str_extract('^\\d+') %>%
+			as.numeric() %>%
+			pmax(0, na.rm = T) # the source record file would have no iteration in the name, so will be considered as zero
+	) %>% with(files[iter == max(iter)])
+
+	file.path(session_path, last_record_file)
+}
+
 
 fix_duplicated_records <- function(records) {
 
@@ -2453,7 +2470,7 @@ compute_changes <- function(Annotations) {
 
 
 
-enrich_annotation_file <- function(file, session_name, DTM = NULL,
+enrich_annotation_file <- function(session_name, file = NULL, DTM = NULL,
 																	 ## Model parameters
 																	 pos_mult = 10,
 																	 n_models = 10,
@@ -2473,6 +2490,16 @@ enrich_annotation_file <- function(file, session_name, DTM = NULL,
 																	 use_prev_labels = T,
 																	 prev_classification = NULL,
 																	 rebuild = FALSE, ...) {
+
+	# pick the last annotated record file or the source one if any
+	if (is.null(file)) {
+		file <- get_last_annotation_file(file.path(sessions_folder, session_name))
+
+		if (is.null(file)) {
+			stop('No annotation files in this session, or the session folder doesn\'t exists.')
+		}
+		message('Processing file: ', file)
+	}
 
 	process_id <- paste0('.pID__', str_replace_all(file, fixed(.Platform$file.sep), '__'))
 
@@ -2996,16 +3023,16 @@ enrich_annotation_file <- function(file, session_name, DTM = NULL,
 
 	tictoc::toc()
 
+	if (file.exists('Model_backup.rds')) file.remove('Model_backup.rds')
+
+	file.remove(process_id)
+
 	if (autorun) {
 		if ('*' %nin% Annotated_data$Rev_prediction_new) {
[…]

### 2021-05-05 Manuscript/Protocol.Rmd
feat: better pkg loader function

@@
 
-# Store the file
-dir.create(file.path('Annotations', 'Session1'))
-folder <- file.path('Annotations', 'Session1')
-dir.create(folder, recursive = T)
-file <- file.path(folder, paste0('Records_', safe_now(), '.xlsx'))
-WriteXLS::WriteXLS(records, ExcelFileName = file)
+```
+
+This annotation file needs to be stored in an **Annotation Session** folder which will contain all annotation information.
+This operation is streamlined by the `create_session()`, which also help manage duplicated sessions.
+
+```{r managing records, echo = TRUE, eval = FALSE}
+create_session(Annotation_data, session_name = 'Session1')
 ```
@@
 	# read, join, reorder records and save them in the Sessions folder
-	save_annotation_file(reorder_query = query, session_name = 'Session1') 
+	save_annotation_file(reorder_query = query) %>%  
+	# Create a new session with the records
+	create_session(session_name = 'Session1')
 ```

### 2021-05-05 Setup.R

@@ -13,23 +13,32 @@ if (is.null(options('BartMem')[[1]])) {
 
 options(java.parameters = options('BartMem')$BartMem)
 
-local({
-	install_and_load <- c("dplyr", "stringr", "glue", "readr", "readxl", "lubridate", "Matrix", "igraph", "pbapply",
-												"pbmcapply", "rpart", "bartMachine", "tm", "patchwork", "ggplot2", "ggrepel", "RLesur/crrri",
-												"bakaburg1/tidytrees")
-	only_install <- c('purrr', 'openxlsx', 'tictoc', 'tidyr', 'arm',
-										'parallel', 'jsonlite', 'rentrez', 'wosr', 'brms')
+pkg.require <- function(install_and_load = c(), only_install = c()) {
 
 	if (!('devtools' %in% installed.packages())) install.packages('devtools')
 
-	for (pkg in setdiff(c(install_and_load, only_install), installed.packages())) {
-		if (grepl('/', pkg)) try(devtools::install_github(pkg)) else install.packages(pkg)
-	}
+	all_packages <- unique(c(install_and_load, only_install))
+	all_packages_clean <- sub(pattern = '^.*/', replacement = '', x = all_packages)
 
-	for (pkg in install_and_load) {
-		try(library(stringr::str_remove(pkg, '^.*/'), character.only = TRUE))
-	}
-})
+	only_install <- all_packages %in% only_install
+	is_github <- grepl('/', all_packages)
+	not_installed <- !(all_packages_clean %in% installed.packages()[,1])
+
+	# Install
+	sapply(all_packages[!is_github & not_installed], install.packages)
+	sapply(all_packages[is_github & not_installed], devtools::install_github)
+
+	# Load
+	sapply(all_packages_clean[!only_install], library, character.only = TRUE)
+}
+
+pkg.require(
+	install_and_load = c("dplyr", "stringr", "glue", "readr", "readxl", "lubridate", "Matrix", "igraph", "pbapply",
+												"pbmcapply", "rpart", "bartMachine", "tm", "patchwork", "ggplot2", "ggrepel", "RLesur/crrri",
+												"bakaburg1/tidytrees"),
+	only_install = c('purrr', 'openxlsx', 'tictoc', 'tidyr', 'arm',
+										'parallel', 'jsonlite', 'rentrez', 'wosr', 'brms')
+	)
 
 
 ### Windows do not support mclapply

### 2021-06-16 R/Record_search.R
code refactoring

@@ -181,9 +181,10 @@ search_pubmed <- function(query, year_query = NULL, additional_fields = NULL,
 	year_query <- clean_date_filter_arg(year_query, cases = list(
 		gt = '{year_piece + 1}[PDAT]:{year(today())}[PDAT]',
 		ge = '{year_piece}[PDAT]:{year(today())}[PDAT]',
-		eq = '{year_piece}[PDAT]:{year_piece}[PDAT]', le = '1000[PDAT]:{year_piece}[PDAT]',
-		range = '{year_piece[1]}[PDAT]:{year_piece[2]}[PDAT]',
+		eq = '{year_piece}[PDAT]:{year_piece}[PDAT]',
+		le = '1000[PDAT]:{year_piece}[PDAT]',
 		lt = '1000[PDAT]:{year_piece - 1}[PDAT]'),
+		range = '{year_piece[1]}[PDAT]:{year_piece[2]}[PDAT]',
 		arg_in_query_test = '[PDAT]', query = query)
 
 	year_query <- glue('({year_query})') # adding parenthesis around the dates

### 2021-06-16 R/Record_management.R
fix: remove reference to unused arguments
create_annotation_file doesn't save its output anymore

@@ -235,10 +235,7 @@ order_by_query_match <- function(records, query) {
 
 create_annotation_file <- function(records, reorder_query = NULL,
 																	 prev_records = NULL,
-																	 prev_classification = NULL,
-																	 out_type = c('xlsx', 'csv')) {
-
-	out_type <- match.arg(out_type)
+																	 prev_classification = NULL) {
 
 	if (class(records) %nin% c('character', 'list', 'data.frame')) {
 		stop('"records" should be either of vector of file/folder paths, a list of data.frame or a single data.frame')

### 2021-08-06 R/Analysis.R
fix: remove autoplotting

@@ -429,7 +429,7 @@ analyse_grid_search <- function(session_folder = 'Grid_Search', tot_pos = NULL,
 
 		p <- patchwork::wrap_plots(p) + legend
 
-		print(p)
+		#print(p)
 	}
 
 	list(

### 2021-08-06 Manuscript/Manuscript_Results.Rmd
manuscript first draft

---
title: "Manuscript"
date: "`r lubridate::today()`"
author:
  - first_name: "Angelo"
    last_name: "D'Ambrosio"
    url: http://github.com/bakaburg1/
    affiliation: Institute for Infection Prevention and Hospital Hygiene, Freiburg University Hospital
    affiliation_url: https://www.uniklinik-freiburg.de/iuk.html
    orcid_id: 0000-0002-2045-5155
  - first_name: "Tjibbe"
    last_name: "Donker"
    url: http://github.com/bakaburg1/
    affiliation: Institute for Infection Prevention and Hospital Hygiene, Freiburg University Hospital
    affiliation_url: https://www.uniklinik-freiburg.de/iuk.html
    orcid_id: 0000-0002-2045-5155
output: distill::distill_article
---

```{r Setup, include=FALSE}

knitr::opts_knit$set(root.dir = ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd()))

options(knitr.kable.NA = '')

knitr::opts_chunk$set(
	echo = FALSE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	dpi = 400,
	cache = FALSE
)

# The following are already the default, but better be explicit
options(basren.probs = c(.05, .5, .95))
options(basren.sessions_folder = 'Sessions')

```

## Results

```{r Results}

source(file.path('R', 'Setup.R'))

session1_files <- get_session_files('Session1')
session2_files <- get_session_files('Session2')

search_results <- summarise_sources_by_session(keep_session_label = TRUE)

source_list <- source_session_summary_to_list(search_results)

search_results$Session_label <- NULL

annotation_results <- summarise_annotations_by_session(remove_raw_data = TRUE)

```

### First session

```{r session 1}
records_s1 <- import_data(session1_files$Records)

source_summary <- source_list$Session1

all_records <- source_summary[names(source_summary) != 'Total'] %>%
	sapply('[[', 'Records') %>% sum()

source_distr <- get_source_distribution(records_s1, format_fun = identity)

session_summary <- summarise_annotations('Session1', remove_raw_data = FALSE)

num_first_labeling <- session_summary[1,]$tot_reviewed_

num_first_positives <- session_summary[1,]$Positives
num_first_negatives <- session_summary[1,]$Negatives

num_last_positives <- session_summary$Positives %>% last()
num_last_negatives <- session_summary$Negatives %>% last()
tot_reviewed <- session_summary$tot_reviewed_ %>% last()

n_review_rounds <- nrow(session_summary) - 1

var_importance <- extract_var_imp('Session1') %>%
	format_var_imp(as_data_frame = FALSE) %>%
	paste(collapse = ', ')

```

The first search session returned a total of `r all_records` unique records, specifically `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total` of the total) records from the *EMBASE* database, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from *Pubmed/Medline*, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from *Scopus*, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from *Web of Science*, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from *IEEE* (Table 1). There were various degrees of overlapping with the `r percent(1 - source_distr[1])` of records being present in more than one database and *EMBASE* and *IEEE* being the databases with the higher uniqueness ratios. The final dataset was composed by `r source_summary$Total$Records` unique records.\
The first `r num_first_labeling` records were manually labeled. Of these `r sprintf('%d (%s)', num_first_positives, percent(num_first_positives/num_first_labeling))` were labeled as positive, and `r sprintf('%d (%s)', num_first_negatives, percent(num_first_negatives/num_first_labeling))` as negative.

`r knitr::kable(search_results, caption = 'Table 1.')`

After the first manual classification, `r n_review_rounds` classification and review rounds (CR) were performed (Table 2). It is possible to observe how the number of records that required manual review dropped fast between iterations, indicating that the engine was converging while the uncertainties were resolved.\
This phenomenon is better depicted in figure 1 in the Suppl. Mat. S2. It shows the mixture distribution of the predicted probabilities for each record, specifically for the reviewed positive and negative records, and for records that need manual review after the classification step: it can be noticed how the distribution of the uncertain records shrinks (they concentrate in a shorter probability range) and shifts toward the negative zone as more positive matches are found and reviewed. Accordingly (Table 2), the number of new positives found drops after the first couple of iterations.
As per default, the classification process was stopped after four rounds with no new positive matches; a total number of `r num_last_positives` positives were found over `r tot_reviewed` manually reviewed records (`r percent(num_last_positives/tot_reviewed)` positivity rate).\

`r knitr::kable(annotation_results, caption = 'Table 2.')`

By evaluating how often the BART algorithm decided to use a term for classification, it is possible to list a subset of the variables most relevant for the classification of the documents: `r var_importance`. In parenthesis, it is reported the part of the record in which the term was used, while the numeric values indicate respectively the rate of posterior trees (over 10000 trees) in which a term was used, and the statistical score of the regression model that assesses the linear direction of the association between a term and the probability of a positive match (see methods). The "&" indicates that two terms are present together in a document but not close to each other.\
The engine was able to pick up the central concept of the research (i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections) and even one of the authors of the current study (Donker T.) or the region of interest ("Orange County") of another research group active on the topic. It is interesting to see that some terms were considered highly relevant (e.g., "Worker" in 6th position) although in a simpler linear model, their effect would be hardly significant (statistic: -1.21), and this highlight the extra predictive power brought by a highly non-linear model.\
A more extensive set of terms is presented in Table 1 of Supplemental Material S2.

### Second session

```{r session 2}
new_query <- import_data('Session_journal.csv') %>% 
    filter(Session_ID == 'Session2') %>% 
    with(Query[1])

records_s2 <- import_data(session2_files$Records)

source_summary <- source_list$Session2

all_records <- source_summary[names(source_summary) != 'Total'] %>%
	sapply('[[', 'Records') %>% sum()

session_diff <- (
	source_list$Session1$Total$Records + source_list$Session2$Total$Records
	) - source_list$`All Sessions`$Total$Records

source_distr <- get_source_distribution(records_s2, format_fun = identity)

session_summary <- summarise_annotations('Session2', remove_raw_data = FALSE)

num_last_positives <- session_summary$Positives %>% last()

tot_reviewed <- session_summary$tot_reviewed_ %>% last()

n_review_rounds <- nrow(session_summary) - 1
```

The results of the first classification session were used to create a second, data-driven query with the purpose of performing a more large-spectrum search to find records which may have escape the first search session. The resulting query was the following:\

*`r new_query`*

The final piece *AND ((antimicrobial resistance) OR (healthcare infection)* was added manually to better define the search domain, since the algorithm was trained on documents that were all more or less related to these topics.\
The generated query also provides a more nuanced understanding of the engine's internal classification logic, and this is helpful to spot possible biases in the model.

The new search produced `r all_records` records (Table 1), of which `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total`) from the *EMBASE*, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from *Pubmed/Medline*, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from *Scopus*, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from *Web of Science*, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from *IEEE*; compared to the first session, the relative weight of *EMBASE* and *Pubmed* over the total was decreased, while the amount of content specificity was greatly increased, as it was for *Scopus*. After removal of duplicates, `r source_summary$Total$Records` unique records were obtained. Once joined with the session 1 records and duplicates remove, we obtained `r nrow(records_s2)` unique records, with just `r session_diff` shared records between searches, that is the `r percent(session_diff / source_list[['All Sessions']]$Total$Records)`. The percentage of records shared by two or more source dropped to `r percent(1 - source_distr[1])`.

`r english::as.english(n_review_rounds) %>% str_to_title()` CR rounds were necessary to complete the second session classification, with just `r sum(session_summary[-1, 'Unlab. -> y'])` new positive found after reviewing `r tot_reviewed - session_summary$tot_reviewed_[1]` extra records. It is interesting to notice that the first CR round required the user to review a substantial number of records (1273), but just labelling 275 of them (the canonical 250 plus 25 that were already labelled during the framework performance evaluation) was sufficient to drop this number to just 190 in the subsequent round. An evaluation of the convergence (Figure 1, Suppl. Mat. S2) showed that, in addition to the dynamics already observed in session 1 (shrinkage and negative shift), a second mode appeared in the mixture distribution of the records to be reviewed, centred in a highly positive zone. The interpretation is that as the number of negative training records increases, the engine gets more and more sceptical and asks to review even some records labelled as positive in the initial labelling at the beginning of session 1. This behaviour can be useful to spot classification errors and inconsistencies.
Considering both sessions, `r tot_reviewed` records were reviewed and `r num_last_positives` (`r percent(num_last_positives / tot_reviewed)`) were found.

Again, the evaluation of the relative importance of the terms showed that the engine was quite capable of internalizing the concepts behind the research topic. A subsample of these terms is reported in Table 2 of Suppl. Mat. S2.

### Hyperparameter selection and performance evaluation

```{r Performance}

grid_search <- analyse_grid_search()

# Creating these summary is quite demanding, so it's better to cache them
# explicitly
perf_file <- file.path('Manuscript', 'Performance_summary.rds')

if (!file.exists(perf_file)) {
	Performance <- list(
		s1 = get_session_files('Session1')$Annotations %>% last() %>% import_data() %>% estimate_performance(),
		s2 = get_session_files('Session2')$Annotations %>% last() %>% import_data() %>% estimate_performance(),
	)

	write_rds(Performance, perf_file)

} else {
	Performance <- read_rds(perf_file)
}

perf_table <- format_performance(Performance$s1, Performance$s2)

#perf_s1$plot + guides(color = 'none', fill = 'none') + ggtitle('Session 1') + perf_s2$plot + ggtitle('Session 2')
```

As described in the methods, the selection of hyperparameters <!-- develop more in the methods, the data is not a random sample and it's ordered so performance evaluation needs to take this into account. also note that hyperparameter selection is necessary since even if bayesian methods are robust, the other parameters outside it are not--> was achieved via the evaluation of sensibility and efficiency with a grid search on a subset of 1200 completely manually labelled records (validation set). The best set of parameters suggested an initial input of 250 labelled records, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval. On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated). A summary of the results of the grid search is reported in Table 3 in Suppl. Mat. S2.

To evaluate the theoretical performance of the engine on the full datasets (i.e., session1 and session2 data), a Bayesian logistic model was trained to predict the label of the records from the probability estimated by the engine (see methods for details). The performance of such simple model is quite high (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2). The predicted cumulative number of positive matches was used to evaluate the performance in the non-reviewed records (Table 3).\

Figure 1 shows the actual and predicted (from the logistic model) cumulative number of positive matches, ordered by the initial simple ordering query. As confirmed by the high efficiency values reported in Table 3, it is striking how many more records one would have needed to evaluate manually to find all positive matches without using a smart search tool. Our engine was able to find matches even close to the end of the heuristically ordered list of records.
Specifically, in session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)`.\
In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows very large, even a small probability can translate, in the worst scenario, into a relevant number of predicted positive matches (`r Performance$s2$pred_positives %>% max()` in this case). To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no actual positive matches.

`r knitr::kable(perf_table, caption = 'Table 3.')`

```{r Performance plot, fig.width=12, fig.height=5}
Performance$s1$plot +
	guides(color = 'none', fill = 'none') +
	ggtitle('Session 1') +
	Performance$s2$plot +
	ggtitle('Session 2')
```

### 2021-08-06 Manuscript/Manuscript_old.Rmd
manuscript first draft

--- 2021-01-19 Manuscript/Manuscript.Rmd
@@
 ### Second search session
+The model trained on the last review task record was used to create new, data-driven, search queries to collect more results missed by the first batch of queries.
+As described in the methods, 2 slightly different query-generation algorithms were used and to both resulting string we added a further constrain to focus the results on "antimicrobial drug resistance" and "healthcare associated infections".

### 2021-08-06 R/Reporting.R
feat: add number of feature to summarise_annotation and fix a typo in format_performance()

@@ -177,9 +177,11 @@ summarise_annotations <- function(session_name, sessions_folder = options("basre
 				'Unlab. -> *' = `Change: unlab. -> *`,
 				'y -> n' = `Change: y -> n`,
 				'n -> y' = `Change: n -> y`,
+				'N. features' = `N. features`
 			) %>%
 			mutate(
-				Changes = select(., matches('->')) %>% rowSums()
+				Changes = select(., matches('->')) %>% rowSums(),
+				.before = `N. features`
 			)
 	}) %>% bind_rows() %>%  {
 		if (remove_empty_columns) {
@@ -568,7 +570,7 @@ format_performance <- function(..., session_names = NULL) {
 				'N. positive matches (% over total)' = glue("{obs_positives} ({percent(obs_positives/total_records)})"),
 				'Predicted positive matches [PrI]' = pred_positives %>% format_interval(),
 				'Expected sensitivity [PrI]' = sensitivity %>% format_interval(percent = TRUE),
-				'Model R^2' = mod_r2 %>% format_interval(percent = TRUE)
+				'Simple Model R^2 [PrI]' = mod_r2 %>% format_interval(percent = TRUE)
 		) %>%
 				mutate_all(as.character) %>%
 				tidyr::pivot_longer(everything(), names_to = 'Indicator', values_to = session_names[i]) %>%

### 2021-08-06 Manuscript/Manuscript_Results.Rmd
results update

@@
 date: "`r lubridate::today()`"
-author:
-  - first_name: "Angelo"
-    last_name: "D'Ambrosio"
-    url: http://github.com/bakaburg1/
-    affiliation: Institute for Infection Prevention and Hospital Hygiene, Freiburg University Hospital
-    affiliation_url: https://www.uniklinik-freiburg.de/iuk.html
-    orcid_id: 0000-0002-2045-5155
-  - first_name: "Tjibbe"
-    last_name: "Donker"
-    url: http://github.com/bakaburg1/
-    affiliation: Institute for Infection Prevention and Hospital Hygiene, Freiburg University Hospital
-    affiliation_url: https://www.uniklinik-freiburg.de/iuk.html
-    orcid_id: 0000-0002-2045-5155
-output: distill::distill_article
+output:
+  github_document:
+    html_preview: false
 ---
@@
 
-`r knitr::kable(search_results, caption = 'Table 1.')`
+`r knitr::kable(search_results, caption = "Table 1.
+Distribution of retrieved records by source and session.
+For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total.
+SAll session shows records after joining and deduplication of the Session1 and Session2 dataset.")`
 
-After the first manual classification, `r n_review_rounds` classification and review rounds (CR) were performed (Table 2).
+After the first manual classification, `r n_review_rounds` automatic classification and manual review rounds (CR) were performed (Table 2).
 It is possible to observe how the number of records that required manual review dropped fast between iterations, indicating that the engine was converging while the uncertainties were resolved.\
@@
 
-`r knitr::kable(annotation_results, caption = 'Table 2.')`
+`r knitr::kable(annotation_results, caption = "Table 2.
+Results of the automatic classifaction and manual review rounds.
+For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown.
+Also, the number of changes after review and their description is reported.
+\"Unlab.\" indicates unlabelled records marked for review.
+For each Iteration, also the number of features used by the engine is reported.
+The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1.
+In Session2, the engine uses the labels at the end of Session1 to classify the newly added records.")`
 
 By evaluating how often the BART algorithm decided to use a term for classification, it is possible to list a subset of the variables most relevant for the classification of the documents: `r var_importance`.
-In parenthesis, it is reported the part of the record in which the term was used, while the numeric values indicate respectively the rate of posterior trees (over 10000 trees) in which a term was used, and the statistical score of the regression model that assesses the linear direction of the association between a term and the probability of a positive match (see methods).
+In parenthesis, it is reported the part of the record in which the term was used, while the numeric values indicate respectively the rate of posterior trees (over 10000 trees) in which a term was used, and the number of standard errors of the association between a term and the probability of a positive match according to a simple logistic linear model (see methods).
 The "&" indicates that two terms are present together in a document but not close to each other.\
 The engine was able to pick up the central concept of the research (i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections) and even one of the authors of the current study (Donker T.) or the region of interest ("Orange County") of another research group active on the topic.
-It is interesting to see that some terms were considered highly relevant (e.g., "Worker" in 6th position) although in a simpler linear model, their effect would be hardly significant (statistic: -1.21), and this highlight the extra predictive power brought by a highly non-linear model.\
+It is interesting to see that some terms were considered highly relevant (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model, their effect would be hardly significant (statistic: -1.21 se), and this highlight the extra predictive power brought by a highly non-linear model.\
 A more extensive set of terms is presented in Table 1 of Supplemental Material S2.
@@
 After removal of duplicates, `r source_summary$Total$Records` unique records were obtained.
-Once joined with the session 1 records and duplicates remove, we obtained `r nrow(records_s2)` unique records, with just `r session_diff` shared records between searches, that is the `r percent(session_diff / source_list[['All Sessions']]$Total$Records)`.
+Once joined with the session 1 records and duplicates removed, we obtained `r nrow(records_s2)` unique records, with just `r session_diff` shared records between searches, that is the `r percent(session_diff / source_list[['All Sessions']]$Total$Records)`.
 The percentage of records shared by two or more source dropped to `r percent(1 - source_distr[1])`.
@@
 
-```{r Performance}
+```{r Performance, cache = FALSE}
 
-grid_search <- analyse_grid_search()
+grid_search <- analyse_grid_search()$best_parms %>%
+	tidyr::pivot_wider(values_from = value, names_from = Parameter)
 
@@
 	Performance <- list(
-		s1 = get_session_files('Session1')$Annotations %>% last() %>% import_data() %>% estimate_performance(),
-		s2 = get_session_files('Session2')$Annotations %>% last() %>% import_data() %>% estimate_performance(),
+		s1 = get_session_files('Session1')$Annotations %>% last() %>%
+			import_data() %>% estimate_performance(),
+		s2 = get_session_files('Session2')$Annotations %>% last() %>%
+			import_data() %>% estimate_performance()
 	)
@@
 perf_table <- format_performance(Performance$s1, Performance$s2)
-
-#perf_s1$plot + guides(color = 'none', fill = 'none') + ggtitle('Session 1') + perf_s2$plot + ggtitle('Session 2')
 ```
 
-As described in the methods, the selection of hyperparameters <!-- develop more in the methods, the data is not a random sample and it's ordered so performance evaluation needs to take this into account.
-also note that hyperparameter selection is necessary since even if bayesian methods are robust, the other parameters outside it are not--> was achieved via the evaluation of sensibility and efficiency with a grid search on a subset of 1200 completely manually labelled records (validation set).
+<!-- develop more in the methods, the data is not a random sample and it's ordered so performance evaluation needs to take this into account.
+also note that hyperparameter selection is necessary since even if bayesian methods are robust, the other parameters outside it are not-->
+
+As described in the methods, the selection of hyperparameters was achieved via the evaluation of sensibility and efficiency with a grid search on a subset of 1200 completely manually labelled records (validation set).
 The best set of parameters suggested an initial input of 250 labelled records, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
@@
 
-To evaluate the theoretical performance of the engine on the full datasets (i.e., session1 and session2 data), a Bayesian logistic model was trained to predict the label of the records from the probability estimated by the engine (see methods for details).
-The performance of such simple model is quite high (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2).
+To evaluate the theoretical performance of the engine on the full datasets (i.e., session1 and session2 data), a Bayesian logistic model was trained on each session dataset to predict the label of the records from the probability estimated by the engine (see methods for details).
+The performance of such simple models is quite high (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2) and the median of their cumulative predictive distribution matches quite well the actual number of cumulative positive records found.
 The predicted cumulative number of positive matches was used to evaluate the performance in the non-reviewed records (Table 3).\
@@
 Figure 1 shows the actual and predicted (from the logistic model) cumulative number of positive matches, ordered by the initial simple ordering query.
-As confirmed by the high efficiency values reported in Table 3, it is striking how many more records one would have needed to evaluate manually to find all positive matches without using a smart search tool.
+As confirmed by the high efficiency values reported in Table 3, it is striking how many more records would need to be evaluated manually to find all positive matches without using a smart search tool.
 Our engine was able to find matches even close to the end of the heuristically ordered list of records.
@@
 
-`r knitr::kable(perf_table, caption = 'Table 3.')`
+`r knitr::kable(perf_table, caption = "Table 3.
+Estimated performance summary.
+For each session, the number of reviewed records and the percentage over the total provide an idea of the work saved against manually labelling all retrieved records.
+Using a simple logistic model to predict a positive match from the probabilities outputted by the engine, the predictive distribution of the cumulative number of positive matches was computed and used to estimate the sensitivity and the efficiency of the engine for each session.
+Finally the Bayesian R^2 of the logistic models is reported.
+[PrI] represents the 90% Predictive Interval.")`
 
-```{r Performance plot, fig.width=12, fig.height=5}
+```{r Performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 1.
+90% Predictive distribution of the cumulative number of positive matches estimated by the logistic Bayesian models applied to the engine output.
+The distribution is depicted by the shaded area.
+The distribution is cut at the level of the observed cumulative distribution of positive matches (red dots), since there cannot be false positive in the dataset and predicted value below this line are not possible."}
 Performance$s1$plot +
@@
     Performance$s2$plot +
-	ggtitle('Session 2')
+    ggtitle('Session 2') &
+    theme(
+        legend.position = 'bottom'
+    ) &
+    plot_layout(guides = 'collect')
 ```

### 2021-08-16 Manuscript/Manuscript_Results.Rmd
clean: change package options namespace

@@
 # The following are already the default, but better be explicit
-options(basren.probs = c(.05, .5, .95))
-options(basren.sessions_folder = 'Sessions')
+options(baysren.probs = c(.05, .5, .95))
+options(baysren.sessions_folder = 'Sessions')
 
@@
 
-As described in the methods, the selection of hyperparameters was achieved via the evaluation of sensibility and efficiency with a grid search on a subset of 1200 completely manually labelled records (validation set).
+As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a subset of 1200 completely manually labelled records (validation set).
 The best set of parameters suggested an initial input of 250 labelled records, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.

### 2021-08-16 R/Analysis.R

@@ -86,8 +86,10 @@ estimate_positivity_rate_model <- function(train_data, seed = 14129189) {
 # 		rowSums()
 # }
 
-estimate_performance <- function(records, model = NULL, preds = NULL, plot = TRUE, quants = options('basren.probs')[[1]],
-																 nsamples = min(2500, sum(model$fit@sim$n_save)), seed = 23797297,
+estimate_performance <- function(records, model = NULL, preds = NULL, plot = TRUE,
+																 quants = options('baysren.probs')[[1]],
+																 nsamples = min(2500, sum(model$fit@sim$n_save)),
+																 seed = 23797297,
 																 save_preds = FALSE, save_model = FALSE) {
 
 	if (is.null(model)) {
@@ -271,7 +273,7 @@ estimate_performance <- function(records, model = NULL, preds = NULL, plot = TRU
 # }
 
 extract_var_imp <- function(session_name, num_vars = 15, score_filter = 1.5, recompute_DTM = FALSE,
-														sessions_folder = options("basren.sessions_folder")[[1]]) {
+														sessions_folder = options("baysren.sessions_folder")[[1]]) {
 
 	message('Retrieving data')
 	session_files <- get_session_files(session_name, sessions_folder)

### 2021-08-16 R/Model.R

@@ -146,7 +146,7 @@ compute_BART_model <- function(train_data, Y, preds = NULL, save = F,
 }
 
 # compute_pred_performance <- function(model, data = NULL, Y = NULL, summary = F,
-# 																		 quants = options('basren.probs')[[1]], AUC.thr = .9) {
+# 																		 quants = options('baysren.probs')[[1]], AUC.thr = .9) {
 #
 # 	library(scales)
 # 	library(pROC)
@@ -494,7 +494,7 @@ enrich_annotation_file <- function(session_name, file = NULL, DTM = NULL,
 																	 resample = F,
 																	 pred_quants = c(.01, .5, .99),
 																	 #
-																	 sessions_folder = options("basren.sessions_folder")[[1]],
+																	 sessions_folder = options("baysren.sessions_folder")[[1]],
 																	 pred_batch_size = 5000,
 																	 autorun = TRUE, replication = NULL,
 																	 stop_on_unreviewed = TRUE,
@@ -1115,7 +1115,7 @@ enrich_annotation_file <- function(session_name, file = NULL, DTM = NULL,
 	invisible(out)
 }
 
-consolidate_results <- function(session_name, sessions_folder = options("basren.sessions_folder")[[1]]) {
+consolidate_results <- function(session_name, sessions_folder = options("baysren.sessions_folder")[[1]]) {
 	annotations_files <- get_session_files(session_name, sessions_folder)$Annotations
 
 	message('Loading annotations...')

### 2021-08-16 R/Record_management.R

@@ -313,7 +313,7 @@ create_annotation_file <- function(records, reorder_query = NULL,
 }
 
 create_session <- function(Records, session_name,
-													 sessions_folder = options("basren.sessions_folder")[[1]],
+													 sessions_folder = options("baysren.sessions_folder")[[1]],
 													 DTM = NULL,
 													 dup_session_action = c('skip', 'stop', 'add', 'replace', 'silent'),
 													 use_time_stamp = TRUE) {
@@ -398,7 +398,7 @@ create_session <- function(Records, session_name,
 }
 
 get_session_files <- function(session_name,
-															sessions_folder = options("basren.sessions_folder")[[1]],
+															sessions_folder = options("baysren.sessions_folder")[[1]],
 															which = c('Records', 'Annotations',
 																				'DTM', 'Samples', 'Results')) {
 

### 2021-08-16 R/Setup.R

@@ -62,8 +62,8 @@ if (bart_machine_num_cores() != parallel::detectCores()) {
 }
 
 # Setting up other general parameters for the framework
-options(basren.probs = c(.05, .5, .95))
-options(basren.sessions_folder = 'Sessions')
+options(baysren.probs = c(.05, .5, .95))
+options(baysren.sessions_folder = 'Sessions')
 
 
 # Helper functions --------------------------------------------------------

### 2021-08-16 Manuscript/S1.Protocol.Rmd
file name update

---
title: "Study protocol"
date: `r lubridate::today()`
author:
  - first_name: "Angelo"
    last_name: "D'Ambrosio"
    url: http://github.com/bakaburg1/
    affiliation: Institute for Infection Prevention and Hospital Hygiene, Freiburg University Hospital
    affiliation_url: https://www.uniklinik-freiburg.de/iuk.html
    orcid_id: 0000-0002-2045-5155
output: distill::distill_article
---

```{r setup, echo = FALSE, eval = TRUE}

knitr::opts_chunk$set(
	echo = TRUE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	eval = FALSE,
	dpi = 400,
	fig.pos = "H", out.extra = ""
)

```

# Research Protocol

This document will guide the reader along the steps to utilize the framework and reproduce our results.

## Acquisition of the records

Once the framework is loaded, the user defines an initial search query which needs to be as specific as possible while still generating a sufficient number of positive matches:

```{r query creation, echo = TRUE, eval = TRUE}

source('Setup.R') # Load the framework

# Initial query to be built on domain knowledge
query <- '((model OR models OR modeling OR network OR networks) AND
(dissemination OR transmission OR spread OR diffusion) AND (nosocomial OR
hospital OR "long-term-care" OR "long term care" OR "longterm care" OR
"long-term care" OR "healthcare associated") AND (infection OR resistance OR
resistant))'

# Year filter. The framework convert it to the API specific format seamlessly.
# common logical comparators can be used, i.e. <, <=, >, >=, while dashes
# denotes inclusive date intervals. A single year restricts results to one year
# period.
year_filter <- '2010-2020'

```

The query is passed to the `perform_search_session()` function, together with an unique identifier for the **search session** and **search query**. A session identifies a homogeneous group of complementary or alternative queries (e.g. sometimes it is easier to create two different simpler queries than a complex and long one that returns the same results).\
In our implementation we define as sessions the group of actions that includes the utilization of a search query and the subsequent cycle of manual review and relevancy prediction of its results.\

`perform_search_session()` will use common scientific research database APIs (at the moment Pubmed/Medline, Web of Science and IEEE) to look for records related to query, store them in a csv format and returns or update **journal** (a csv or excel file) with all the information about sessions, queries and search results. The records will be stored in folders with the following structure: Records/\*session_id\*/\*query_id\*. Some API requires API key to access the data. These keys can be stored in the secret.R file with the following structure:

```{r secrets}
options(ieee_api_key = 'bb58ndv4xbv535b5779u93ka')
options(ncbi_api_key = '5cd65c6d044db651af2bf8e9c78fc54fa409')
options(wos_api_key = 'C4O2SHqGc1rf3jmNxqI')
```

This file will be automatically parsed from the framework.

If manually downloaded results are available, users can create the Record folders manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`) and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g. Pubmed1.nbib, Pubmed2.nib, etc.). In addition of Pubmed, WOS and IEEE, this method permits to import also Embase and Scopus records, for which an API search was not yet implemented.\
Users can choose whether to perform an API search, parse already downloaded results, or both using the `actions` argument.

Note that for Pubmed, the API search may return slightly less records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the resulting .nbib files in the Session/Query folder. `perform_search_session()` will acquire them seamlessly.

If a user wants to perform the API searches and results parsing manually for each source, the framework exposes the individual functions to search for records using the APIs and parsing bibliography files.

```{r perform searches}
# This call will perform an API search on Pubmed, WOS and IEEE services and/or
# (based on the `actions` argument) parse already downloaded data (in our case, additional Pubmed results and Embase and Scopus results) manually added to the Session1/Query1 folder.
journal <- perform_search_session(query = query, year_query = year_filter,
																	session_name = 'Session1', query_name = 'Query1',
																	records_folder = 'Records',
																	journal = 'Session_journal.csv')

```

Once the records are stored, they must be read and merged into an **annotation file** where the initial manual review of the records will be performed.\
A series of functions are available to prepare the data for the manual evaluation:

```{r managing records}
# Extract the file paths of records. Arguments can be used to filter by session
# query, source. Only parsed files will be returned, not the raw ones downloaded
# manually.
Annotation_data <- extract_source_file_paths(journal) %>%

	# Read record files. Will parse them if raw data downloaded manually (not
	# necessary in this case). Return a list of records, one per file.
	read_bib_files() %>%

	# Join a list of records into one dataframe, solving duplicated records
	join_records() %>%

	# Order records by the relative frequency of the query terms in the
	# title + abstract text. Increases the chance of encountering relevant records at
	# the beginning of the manual classification.
	order_by_query_match(query) %>%

	# Add fields for the manual classification
	mutate(
			Rev_manual = NA, # Where the first manual classification will be made
			Rev_prediction = NA, # Column for the evaluation of the predicted classes
			.before = DOI
		)

```

Actually all these step are more easily performed through `create_annotation_file()`. This function can take as input either the path to record files, or the parsed records (one data frame or a list of data frames) or a group of folders where to look for files into./
In addition, it also allows to add the new records to a previous annotation file (arg `prev_records`), useful with subsequent searching sessions with different queries; previous manual classifications of records can be imported using `prev_classification`. By passing the original query to the `reorder_query` argument, the records are reordered empirically in order to increase the probability to find positive matches first.

```{r save annotation file}
# This function extract the appropriate file paths from a session journal. By
# default it passes all stored files, otherwise it can be filtered by session,
# query, and source (i.e. Pubmed, WOS, IEEE)
record_files <- extract_source_file_paths(journal)

# create_annotation_file() accept a great variety of inputs:

	# record file paths
input <- record_files

	# specific record file folders
input <- file.path('Records', 'Session1', 'Query1')

	# or parent folders, since it search for files recursively
input <- 'Records'

	# finally it can accept the already parsed files
input <- read_bib_files(record_files)

# We can then call create_annotation_file() with one of the above input
Annotation_data <- create_annotation_file(record_files, reorder_query = query)

```

Once created, the annotations needs to be stored in an **Annotation Session** folder which will contain all informations necessary for the automatic classification. This operation is streamlined by the `create_session()` function, which also help manage duplicated sessions.

```{r managing records}
# Create the first session
create_session(Annotation_data, session_name = 'Session1')
```

The file annotation file is called `Records_{date}` in the folder `Sessions/{session_name}` with `date` being the creation timestamp and `session_name` being the name passed by the user.

Notice that the framework is "chaining" friendly and the precedent steps can be all performed in one call (which is the suggested procedure):

```{r one call}
# First create the Records/Session1/Query1 folder and put the manually
# downloaded records there if you have any. Otherwise the folders will be
# created automatically during the API search

# perform searches and parse files; save and return the journal
Records <- perform_search_session(query = query, year_query = year_filter,
											 session_name = 'Session1', query_name = 'Query1',
											 journal = 'Session_journal.csv') %>% 
	# return the record file paths
	extract_source_file_paths() %>%
	# read, join, reorder records and save them in the Sessions folder
	create_annotation_file(reorder_query = query) %>%  
	# Create a new session with the records
	create_session(session_name = 'Session1')
```

## Manual classification and prediction

Now the annotation file is ready for manual classification of relevant and non-relevant records. The annotation file has a column called `Rev_manual`, where records needs to be classified as "positve" (y) or negative (n) by the user. From our experience, around 250 manually classified records are sufficient if a minimum ~20% positivity rate is maintained (see the section about model parameter optimization)./
The function `check_classification_trends()` can help to visualize the trend of the positives/negatives as the number of classified records increases./

Once the first records are labelled manually, the function `enrich_annotation_file()` will use Bayesian Additive Regression Trees (BART) to learn the labeling pattern of the user and predict the positive match probability for the unlabelled records. This is a summary of the prediction process:

- a Document Term Matrix (DTM) is created, extracting terms from the (lemmatized) title and abstract of the records and adding the authors and keywords. For each term, a 0/1 label specifies if it is present in each record. Also co-occurrying terms are added as ngrams and highly copresent terms are joined as synonyms;
- the positive records are weighted 10x more than the negative ones to improve sensitivity;
- the function models the labeling pattern using the manually reviewed records (learning step);
- after the model is created, it assigns a probability distribution of positivity to each record, labelled and unlabelled (prediction step). If the number of records is large, the prediction step is broken in chunks of 5000 records, to avoid memory saturation problems; the user will need to set up this parameter according to her machine capabilities;
- this process is repeated 10 times and the distributions are averaged to induce shrinkage of the estimates;
- the resulting distribution is summarised by its 98% interval and the unlabelled records will receive a positive/negative predicted label if their interval ends up completely in the joint interval of the positively/negatively labelled records. All the other records will be labeled as unknown (unk) and will require manual review.

The user can define parameters like the positives' weight, the number of models to average, whether to apply bootstrap resampling before each repetition, the prediction chunk size, and the prediction distribution interval range.
To use the function, the only input needed is the session name, the function will automatically identify the relevant file to make predictions on.

```{r automatic annotation}
New_annotations <- enrich_annotation_file('Session1')
```

This function will produce a new excel file which is stored in the Annotations folder of the session; the file will contain a column called `Rev_prediction_new` were the user will find records that require manual review marked by "*". These are records with uncertain labelling ("unk"), but also positive predictions and "y"/"n" predictions that contradict previous manually inputed labels (labeled as "check"). This approach allows to increase the accuracy of the predictions, since the machine learning system is set up to favor sensitivity at the expense of specificity. If the function finds prelabelled records (`Rev_previous` column) added when the Annotation file was created or passed as a further input to `enrich_annotation_file()` (`prev_classification` argument), they will be used to relabel the records marked in the `Rev_prediction_new` column.

The function adds a number of diagnostic pages to the annotation file:

- a results summary page which reports the number of records that need manual review (which includes uncertain and unreviewed positive records or records with certain predictions which are different from previous manual labels), the changes, and the final distribution of the labels; it also shows other information like the number of terms in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later). The content of this summary is also saved as a csv file in the Results folder.
- a variable importance page which list the used terms in order of the fraction of BART trees in which they were used. If more than 1 model repetition is used, a more robust score is computed taking the ratio of the mean of the term tree fraction among models and its standard deviation.
- the arguments passed to the function if different from the default, useful for reproducibility.
- a classification performance summary (*this needs implementation*).

Finally, the posterior samples produced by the Bayesian engine are stored on the disk. This feature can be turned off to save disk space, but at least the samples of the last annotation are necessary to build a new search query building (see next section).

Once the manual review of the generated annotation file is completed, the user can **rerun exactly the same function**. The reviewed annotation file will be automatically picked up and used for a new round of classification and review (CR). In case the number of records that require manual review is excessively high (e.g. > 250) the function need to be called setting the `stop_on_unreviewed` argument to `FALSE` to allow the classification to proceed even in the presence of unreviewed records (i.e. marked by "*") in the `Rev_prediction_new` column.

If there are no positive results (after manual review) in a CR round, the framework records the next round as a "replication". After four replication with no positive matches are done, the function will prevent another round and send a warning message. The user can change the replication limit; furthermore it's possible to have the function to stop if either a number (or a fraction of the total records) has been manually reviewed already, or if a certain number of positive matches have been found. These three parameter are passed to the `limits` argument which has the following structure and defaults:

```{r replication limits}
list(
	stop_after = 4, pos_target = NULL,
	labeling_limit = NULL
)
```

The result files in the Results folder are generated after the Classification phase but before the Review one, and therefore show preliminary results. The function `consolidate_results(session_name)` will update the results files to show the results after the manual review. The temporary result data is anyway stored in the respective annotations file.

## New search query generation

It's not uncommon that for the first query used in a systematic review not to be the the most effective one, especially in terms of sensitivity. We tried to address the problem by creating automatic query generation system. The solution is experimental and favors sensitivity at the expense of specificity. After a step in which a set of candidate query rules (to be joined by a OR logic) are selected, the user is asked to review them and select rules that make more sense to the topic or deselect too general rules that would generate too many results. The algorithm is, of course, not topic aware and therefore may very likely pick terms that are only casually associated with the topic of study; therefore a human review and selection is still needed.

The steps for generating a query are the following:

```{r new query generation}

# The last annotation file and posterior sample matrix in the session are
# found; the most predictive terms (based on the importance score) are chosen
# and simple prediction trees are used to map the terms to a random subset of
# the posterior probabilities (extracted from the posterior sample matrix saved
# during the last CR step). The score threshold and the number of trees can be
# chosen by the user; less stringent values can greatly increase computation
# time;

candidate_queries <- extract_rules('Session1')

# The 'candidate_queries' contains the rules and the DMT and the labels on which
# the rules were built, which need to be passed to
# generate_rule_selection_set(). This function select the most effective (higher
# positive/negative matches delta) rules; also adds negative terms to increase
# specificity. A dataframe is generated (or automatically saved if save_path is
# set). The output proposes groups of equivalent (in terms of number of positive
# matches found) group of query, ordered by specificity; for each group the user
# needs to select the best rule by setting the selected_rule column to TRUE. The
# groups are in order of growing sensitivity/decreasing specificity, so it may
# make sense to exclude the last groups totally in order to avoid too many
# search results.

Target <- candidate_queries$DTM$Target
SpecificDTM <- candidate_queries$SpecificDTM

selection_set <- generate_rule_selection_set(
	candidate_queries$rule,
	target_vec = Target,
	target_data = SpecificDTM)

selection_set_file <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx')
openxlsx::write.xlsx(selection_set, selection_set_file)

# Once the manual selection is performed the selected rules can be further
# simplified in order to remove redundant rules and terms. The aim is to provide
# the shortest rule without loss of retrieving accuracy.

simplified_rules <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx') %>%
	import_data() %>%
	simplify_ruleset(ruleset = Target, SpecificDTM) %>%
	pull(rule)

# Finally, the selected rules need to be joined in a query that scientific
# search engines can understand

new_query <- rules_to_query(simplified_rules)

```

One last thing to keep in mind is that the query generation algorithm is only aware of the literature collected inside the annotation file it's working on; so it will only be able to pick term combinations that identify positive matches inside an already specific set of documents, while not necessarily being discriminant from the rest of the global literature.\
Therefore, once the final query is generated it is advisable to add a piece with a AND logic to restrict the results in the scope of the general topic of interest.\
In our case, we added "AND ((antimicrobial resistance) OR (healthcare infection))" since being the global topic of our research, those terms were understandably not selected by the query generation algorithm as discriminant.\

The final query was the following:

```{r second session query}
query <- "(((Donker T) NOT (bacterium isolate)) OR ((network patient) AND
(resistant staphylococcus aureus) NOT (monte carlo) NOT isolation) OR
(facility AND (network patient) AND regional NOT hospitals NOT increase NOT
(patient transport) NOT (control infection use)) OR ((patient transport) NOT
(Donker T) NOT worker) OR (hospitals AND (network patient) NOT
(patient transport) NOT regional NOT clinical) OR (facility AND
(network patient) NOT hospitals NOT (patient transport) NOT regional NOT
prevention NOT medical) OR ((healthcare facility) NOT (Donker T) NOT
worker NOT positive) OR (hospitals NOT (network patient) NOT medical NOT
environmental NOT outcome NOT global) OR ((network patient) NOT facility NOT
hospitals NOT (patient transport) NOT therapy NOT global)) AND
((antimicrobial resistance) OR (healthcare infection))"

```

Another advantage of this technique is an at-glance view of relevant concepts for the topic of interest.

## New search session

Once the new query was generated, a second search session called `Session2` was created, using the strategy described in the protocol. Due to the lower specificity of the second query, particular care was needed in managing the far larger amount of records, since manual downloading may be necessary from Pubmed, Embase, and Scopus (which usually have limits on the amount of records one can download at once), and because the automatic classification processing time increases proportionally to the number of records to label.\
It is advisable then to cosider removing iteratively the less specific rules from the query until a manageable number of records is found, considering that the probability of finding positive matches not already found by more specific queries drops exponentially.\

Once the new records are collected, `enrich_annotation_file('Session2')` can be used to perform the new CR cycles until no new positive matches are found. It may be possible that, during the first CR round, the number of records that require manual review is a large amount: we suggest to evaluate still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.

# Results evaluation

# Model parameters' optimization

As many complex machine learning models, the choosing of hyperparameters can greatly influence the framework performance. For a systematic review helper algorithm, we define the performance as the ability to find as many positive matches by manually labelling/reviewing as few records as possible.\
We added a number of simple tools to the framework to find a set of hyperparameters using by a "grid search" algorithm. We tested these tools on our dataset, manually labeling the first 1200 records (ordered by simple query match, as described when introducing the `create_annotation_file()` function)

### 2021-08-16 R/Reporting.R
clean: change package options namespace

@@ -39,7 +39,7 @@ summarise_by_source <- function(annotation_file, as_data_frame = FALSE,
 }
 
 summarise_sources_by_session <- function(sessions = list.files(sessions_folder),
-																				 sessions_folder = options("basren.sessions_folder")[[1]],
+																				 sessions_folder = options("baysren.sessions_folder")[[1]],
 																				 add_global_totals = TRUE, keep_session_label = FALSE, ...) {
 	if (length(sessions) == 1) {
 		res <- get_session_files(session, sessions_folder)$Records %>%
@@ -120,7 +120,7 @@ get_source_distribution <- function(annotation_file, as_propr = TRUE, format_fun
 	res
 }
 
-summarise_annotations <- function(session_name, sessions_folder = options("basren.sessions_folder")[[1]],
+summarise_annotations <- function(session_name, sessions_folder = options("baysren.sessions_folder")[[1]],
 																	remove_empty_columns = TRUE, remove_raw_data = TRUE) {
 	result_list <- get_session_files(session_name, sessions_folder)$Results %>%
 		lapply(function(file) {
@@ -196,7 +196,7 @@ summarise_annotations <- function(session_name, sessions_folder = options("basre
 	}
 }
 
-summarise_annotations_by_session <- function(sessions_folder = options("basren.sessions_folder")[[1]],
+summarise_annotations_by_session <- function(sessions_folder = options("baysren.sessions_folder")[[1]],
 																						 remove_empty_columns = TRUE,
 																						 remove_raw_data = TRUE) {
 	sessions <- list.files(sessions_folder)
@@ -584,7 +584,7 @@ format_performance <- function(..., session_names = NULL) {
 }
 
 plot_predictive_densities <- function(session_name,
-																			sessions_folder = options("basren.sessions_folder")[[1]]) {
+																			sessions_folder = options("baysren.sessions_folder")[[1]]) {
 
 	library(ggridges)
 

### 2021-08-16 R/Rule_building.R

@@ -1,5 +1,5 @@
 extract_rules <- function(session_name, rebuild_dtm = F, vimp.threshold = 1.25,
-													n.trees = 800, sessions_folder = options("basren.sessions_folder")[[1]], ...) {
+													n.trees = 800, sessions_folder = options("baysren.sessions_folder")[[1]], ...) {
 
 	message('Preparing the data')
 

### 2021-08-16 Manuscript/Manuscript_Results.Rmd
small changes in the last plot

@@
 
+source(file.path('R', 'Setup.R'))
+
 # The following are already the default, but better be explicit
@@
 ```{r Results}
-
-source(file.path('R', 'Setup.R'))
 
@@
 The distribution is cut at the level of the observed cumulative distribution of positive matches (red dots), since there cannot be false positive in the dataset and predicted value below this line are not possible."}
+
 Performance$s1$plot +
@@
 	Performance$s2$plot +
-    ggtitle('Session 2') &
+	ggtitle('Session 2') +
+	theme(
+		axis.title.y = element_blank()
+	) &
 	theme(

### 2021-08-16 R/Reporting.R
feat: add final labeling distribution to plot_predictive_densities

@@ -591,10 +591,19 @@ plot_predictive_densities <- function(session_name,
 	records_files <- get_session_files(session_name, sessions_folder)$Annotations
 	samples_files <- get_session_files(session_name, sessions_folder)$Samples
 
-	pbmclapply(1:length(records_files), function(i) {
-		records <- records_files[[i]] %>%
-			import_data() %>%
-			mutate(Rev_prediction_new = replace(Rev_prediction_new, !is.na(Rev_prediction_new), '*')) %>%
+	pbmclapply(1:(length(records_files) + 1), function(i) {
+		index <- min(i, length(records_files))
+
+		# The last file will be imported twice, the second time will show the final labelling
+		records <- records_files[[index]] %>%
+			import_data()
+
+		if (i <= length(records_files)) {
+		records <- records %>%
+			mutate(Rev_prediction_new = replace(Rev_prediction_new, !is.na(Rev_prediction_new), '*'))
+		}
+
+		records <- records %>%
 			transmute(
 				Pred_Low, Pred_Up,
 				ID,
@@ -604,7 +613,7 @@ plot_predictive_densities <- function(session_name,
 		neg_lim <- with(records, max(Pred_Up[Target %in% 'n']))
 		pos_lim <- with(records, min(Pred_Low[Target %in% 'y']))
 
-		samples <- samples_files[[i]] %>% read_rds()
+		samples <- samples_files[[index]] %>% read_rds()
 
 		unique(records$Target) %>% na.omit %>%
 			lapply(function(lab) {
@@ -613,7 +622,11 @@ plot_predictive_densities <- function(session_name,
 					as.matrix %>% as.vector %>% sample(size = 5000)
 
 				data.frame(
-					Iteration = i,
+					Iteration = factor(
+						i,
+						1:(length(records_files) + 1),
+						c(1:length(records_files), 'Final\nlabelling')
+					),
 					Label = lab,
 					Samples = postsamples,
 					Neg_lim = neg_lim,

### 2021-08-16 R/Analysis.R
fix: use import_data() instead of read_excel

@@ -317,7 +317,7 @@ analyse_grid_search <- function(session_folder = 'Grid_Search', tot_pos = NULL,
 
 	if (is.null(tot_pos) | is.null(tot_records)) {
 		Labels <- list.files(session_folder, pattern = 'Records_', recursive = T, full.names = T)[1] %>%
-			read_excel() %>%
+			import_data() %>%
 			mutate(
 				Target = coalesce_labels(., label_cols = c('Rev_prediction_new',
 																									 'Rev_prediction', 'Rev_manual',

### 2021-08-17 R/Analysis.R
feat: add best rule set to grid search output

@@ -450,6 +450,21 @@ analyse_grid_search <- function(session_folder = 'Grid_Search', tot_pos = NULL,
 				Efficiency = percent(Efficiency),
 				across(.fns = as.character)) %>%
 			tidyr::pivot_longer(everything(), names_to = 'Parameter', 'Value'),
+		best_by_rule = out %>% group_by(Cluster = Rule) %>%
+			slice_max(Score, n = 1, with_ties = T) %>%
+			slice_max(Sensitivity, n = 1, with_ties = T) %>%
+			slice_max(Score, n = 1, with_ties = F) %>%
+			# ungroup() %>%
+			# arrange(desc(Score), desc(Sensitivity), desc(Efficiency)) %>%
+			select(Cluster, Iter, Pos_labels, Tot_labeled, Sensitivity, Efficiency,
+						 Score, any_of(params)) %>%
+			mutate(
+				Pos_labels = glue("{Pos_labels} / {tot_pos}"),
+				Tot_labeled = glue("{Tot_labeled} / {tot_records}"),
+				Sensitivity = percent(Sensitivity),
+				Efficiency = percent(Efficiency),
+				Score = glue("{signif(Score, 3)} ({score})"),
+				across(.fns = as.character)),
 		plot = p
 	)
 }

### 2021-08-17 R/Reporting.R
fix: update column labels

@@ -674,11 +674,11 @@ format_var_imp <- function(var_imp, as_data_frame = TRUE) {
 			Term = str_replace_all(Term, c('^\\w+__' = '', '\\._\\.' = ' & ', '\\.' = ' | ', '_' = ' ')) %>% str_to_title(),
 			'Value (on 10K trees)' = signif(Value * 10000, 3),
 			RR = signif(exp(estimate), 3) %>% str_remove('\\.?0+$'),
-			Statistic = signif(statistic, 3) %>% str_remove('\\.?0+$'),
+			`Statistic (s.e.)` = signif(statistic, 3) %>% str_remove('\\.?0+$'),
 		)
 
 	if (!as_data_frame) {
-		var_imp <- 	with(var_imp, glue('{Term} ({Component}): {`Value (on 10K trees)`} [{Statistic}]'))
+		var_imp <- 	with(var_imp, glue('{Term} ({Component}): {`Value (on 10K trees)`} [{`Statistic (s.e.)`}]'))
 	}
 
 	var_imp

### 2021-08-17 R/Analysis.R
fix: update label in plot

@@ -422,7 +422,7 @@ analyse_grid_search <- function(session_folder = 'Grid_Search', tot_pos = NULL,
 			theme_minimal() +
 			scale_color_manual(values = colors) +
 			scale_fill_manual(values = colors) +
-			labs(color = glue('Par. group (mean {score})'))
+			labs(color = glue('Perf. cluster (mean {score})'))
 
 		tmp <- ggplot_gtable(ggplot_build(p_one))
 		leg <- which(tmp$layout$name == 'guide-box')

### 2021-08-17 Manuscript/S2.Additional_outputs.Rmd
first commit

---
title: "S2. Additional figures and table"
date: "`r lubridate::today()`"
output:
  github_document:
    html_preview: false
    toc: yes
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE, error = FALSE}

wd <- ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd())

knitr::opts_knit$set(root.dir = wd)

options(knitr.kable.NA = '')

knitr::opts_chunk$set(
	echo = FALSE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	dpi = 400,
	cache = TRUE,
	cache.rebuild = FALSE
)
# message(wd)
# sys.source(file.path(wd, 'R', 'Setup.R'), envir = knitr::knit_global())

```

```{r load framework, cache.rebuild=TRUE}
source(file.path('R', 'Setup.R'))

# The following are already the default, but better be explicit
options(baysren.probs = c(.05, .5, .95))
options(baysren.sessions_folder = 'Sessions')
```

# Posterior predictive distributions

Figure 1 show the mixture of the predictive distribution of the probability of a positive match, grouped by labelling status. The posterior samples for each record were extracted and joined in a global distribution; on this distribution, density was computed on the logit scale and then logistic transformed for display on a `[0-1]` scale. The light violet ridges show the distribution of the still unlabelled records.\
For each iteration, the thresholds which define the lower and the upper range of 98% predictive interval (PrI) respectively for the positive and negative records. The zone comprised between these two boundaries defines the uncertainty zone; records whose 98% PrI intersects this zone requires manual review.\
Notice how the positive and negative densities start overlapping starting with the second iteration of Session 2. Meanwhile the distribution of the records to be reviewed shrink and shift towards the negative side, as positive records get found and labeled.

```{r posterior distributions, fig.width=10, fig.height=10, fig.cap="Figure 1. Mixture predictive distribution of the probability of a positive match, grouped by labelling status."}

s1_plot <- plot_predictive_densities('Session1')

s2_plot <- plot_predictive_densities('Session2')

s1_plot +
    guides(color = 'none', fill = 'none') +
    ggtitle('Session 1') +
    s2_plot +
    ggtitle('Session 2') +
    theme(
        axis.title.y = element_blank()
        ) &
    theme(
        legend.position = 'bottom'
    ) &
    plot_layout(guides = 'collect')
```

# List of terms relevant for prediction

In table 1 and 2 are listed the 50 more relevant terms used by the BART algorithm to discriminate between positive and negative records, for Session 1 and 2. Term importance ("Value" in the tables) is defined as the proportion over 10 000 posterior trees in which a term was used divided by the standard deviation of this value among each model repetition. The symbol "|" indicate synonyms while terms joined by "&" represent terms that are co-present in a document component The component in which the term was used is reported in the leftmost column.\
Next to it, we added the relative risk of a positive match (RR) and statistical relevancy (measured as standard errors, s.e.) of the terms estimated through a Poisson regression, to evaluate its linear correlation with the probability of a positive match. A strong BART score with a low regression score identify terms whose effect is highly non linear (e.g., they are relevant only in the presence of other terms).

```{r var imp}

var_importance_s1 <- extract_var_imp('Session1', num_vars = 50, score_filter = 0) %>%
	format_var_imp(as_data_frame = TRUE)

var_importance_s2 <- extract_var_imp('Session1', num_vars = 50, score_filter = 0) %>%
	format_var_imp(as_data_frame = TRUE)
```

`r knitr::kable(var_importance_s1, caption = 'Table 1. Term importance at the end of Session 1')`

`r knitr::kable(var_importance_s2, caption = 'Table 2. Term importance at the end of Session 2')`

# Hyperparameters grid search

To select the engine hyperparameter set which would maximize sensitivity and efficiency, we set up a comprehensive grid search by running the algorithm on a fully labeled dataset of 1200 records. Using a partition tree algorithm we grouped the searches in a number of clusters with similar performance and selected the best parameter set in the best cluster.\
Table 3 shows the best parameter set and their performance for each cluster while figure 2 displays the conditional impact on performance of each parameter.

```{r hyperparameters, fig.width=14, fig.height=9, fig.cap="Performance clusters and impact of single hyperparameters on engine performance. The performance is measured as Sensitivity x Efficiency. Each cluster is color coded. Mods: num. of models in the ensemble; Quant: uncertainty zone interval to trigger manual review; Resamp: bootstrap resampling; Init: num. of initial training records; Multi: oversampling multiplier of positive matches."}

grid_out <- analyse_grid_search()

grid_out_params <- grid_out$best_by_rule %>% 
	rename(
		`Cluster (mean score)` = Cluster,
		`Num. iterations` = Iter,
		`Positive matches` = Pos_labels,
		`Reviewed records` = Tot_labeled,
		`Score (Sens. x Eff.)` = Score,
		`Num. ensemble models` = Mods,
		`Uncertainty interval` = Quant,
		`Resampling` = Resamp,
		`Num. initial training records` = Init,
		`Positives oversampling multiplier` = Mult
	)

print(grid_out$plot & labs(y = 'Sens. x. Eff.'))

```

`r knitr::kable(grid_out_params, caption = 'Table 3. Hyperparameter clusters and best cluster subsets. For each cluster, the defining rules and mean Sens. x Eff. is shown, followed by the per-cluster best set results.')`

### 2021-08-17 Manuscript/Manuscript_Results.Rmd
update

@@
 
-```{r Setup, include=FALSE}
+```{r setup, include=FALSE, message=FALSE, warning=FALSE, error = FALSE}
 
-knitr::opts_knit$set(root.dir = ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd()))
+wd <- ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd())
+
+knitr::opts_knit$set(root.dir = wd)
 
@@
 	dpi = 400,
-	cache = FALSE
+	cache = TRUE,
+	cache.rebuild = FALSE
 )
+# message(wd)
+# sys.source(file.path(wd, 'R', 'Setup.R'), envir = knitr::knit_global())
 
+```
+
+```{r load framework, cache.rebuild=TRUE}
 source(file.path('R', 'Setup.R'))
@@
 options(baysren.sessions_folder = 'Sessions')
-
 ```
@@
 
-```{r Results}
+```{r results}
 
@@
 
-```{r Performance, cache = FALSE}
+```{r performance, cache = FALSE}
 
@@
 As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a subset of 1200 completely manually labelled records (validation set).
-The best set of parameters suggested an initial input of 250 labelled records, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
+The best set of parameters suggested an initial input of 250 labelled records with 20x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
 On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
@@
 
-```{r Performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 1.
+```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 1.
 90% Predictive distribution of the cumulative number of positive matches estimated by the logistic Bayesian models applied to the engine output.

### 2021-08-17 Manuscript/Manuscript_Results.Rmd
update

@@
 )
-# message(wd)
-# sys.source(file.path(wd, 'R', 'Setup.R'), envir = knitr::knit_global())
 

### 2021-08-17 Manuscript/S2.Additional_outputs.Rmd
update

@@
 
-```{r hyperparameters, fig.width=14, fig.height=9, fig.cap="Performance clusters and impact of single hyperparameters on engine performance.
+```{r hyperparameters, fig.width=15, fig.height=9, fig.cap="Figure 2.
+Performance clusters and impact of single hyperparameters on engine performance.
 The performance is measured as Sensitivity x Efficiency.
@@
 grid_out_params <- grid_out$best_by_rule %>% 
+	mutate(Score = str_remove(Score, ' .+')) %>% 
 	rename(

### 2021-08-19 R/Record_search.R
fix: add namespace to options() calls

@@ -58,7 +58,7 @@ clean_date_filter_arg <- function(year_query, cases,
 }
 
 search_wos <- function(query, year_query = NULL, additional_fields = NULL,
-											 default_field = 'TS', api_key = options('wos_api_key'),
+											 default_field = 'TS', api_key = options('baysren.wos_api_key')[[1]],
 											 parallel = T, parse_query = T, ...) {
 
 	message('Searching WOS...')
@@ -168,7 +168,7 @@ search_wos <- function(query, year_query = NULL, additional_fields = NULL,
 }
 
 search_pubmed <- function(query, year_query = NULL, additional_fields = NULL,
-													api_key = options('ncbi_api_key'),
+													api_key = options('baysren.ncbi_api_key')[[1]],
 													record_limit = numeric(),
 													...) {
 
@@ -239,7 +239,7 @@ search_pubmed <- function(query, year_query = NULL, additional_fields = NULL,
 }
 
 search_ieee <- function(query, year_query = NULL, additional_fields = NULL,
-												api_key = options('ieee_api_key')[[1]], allow_web_scraping = T,
+												api_key = options('baysren.ieee_api_key')[[1]], allow_web_scraping = T,
 												file_name = glue('IEEE_{safe_now()}'), save = T,
 												wait_for = 20, record_limit = NULL) {
 	message('Searching IEEE...')

### 2021-08-19 R/Model.R
feat: set compute_performance default to FALSE
computing performance takes quite some time

@@ -504,7 +504,7 @@ enrich_annotation_file <- function(session_name, file = NULL, DTM = NULL,
 																	 	stop_after = 4, pos_target = NULL,
 																	 	labeling_limit = NULL
 																	 ),
-																	 compute_performance = TRUE,
+																	 compute_performance = FALSE,
 																	 test_data = NULL,
 																	 use_prev_labels = TRUE,
 																	 prev_classification = NULL,

### 2021-08-19 R/Analysis.R
cleaning

@@ -77,14 +77,7 @@ estimate_positivity_rate_model <- function(train_data, seed = 14129189) {
 				prior(student_t(3, 0, 2.5), class = "Intercept"),
 				prior(student_t(3, 0, 1.5), class = "b")
 			))
-
 }
-
-# predict_num_positives <- function(model, tot_records, start_index = 1,
-# 																	nsamples = min(2000, sum(model$fit@sim$n_save))) {
-# 	posterior_predict(mod, newdata = data.frame(Order = start_index:tot_records), nsamples = nsamples) %>%
-# 		rowSums()
-# }
 
 estimate_performance <- function(records, model = NULL, preds = NULL, plot = TRUE,
 																 quants = options('baysren.probs')[[1]],
@@ -94,8 +87,10 @@ estimate_performance <- function(records, model = NULL, preds = NULL, plot = TRU
 
 	if (is.null(model)) {
 		message('- build model...')
+
 		model <- estimate_positivity_rate_model(records, seed)
 	}
+
 
 	quants <- sort(quants)
 

### 2021-08-19 Manuscript/Manuscript_Results.Rmd
update

@@
 The engine was able to pick up the central concept of the research (i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections) and even one of the authors of the current study (Donker T.) or the region of interest ("Orange County") of another research group active on the topic.
-It is interesting to see that some terms were considered highly relevant (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model, their effect would be hardly significant (statistic: -1.21 se), and this highlight the extra predictive power brought by a highly non-linear model.\
+It is interesting to see that some terms were considered highly relevant (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model, their effect would be hardly significant (statistic: -1.21 s.e.), and this highlight the extra predictive power brought by a highly non-linear model.\
 A more extensive set of terms is presented in Table 1 of Supplemental Material S2.
@@
 
-To evaluate the theoretical performance of the engine on the full datasets (i.e., session1 and session2 data), a Bayesian logistic model was trained on each session dataset to predict the label of the records from the probability estimated by the engine (see methods for details).
+To evaluate the theoretical performance of the engine on the full datasets (i.e., session 1 and session 2 data), a Bayesian logistic model was trained on each session dataset to predict the label of the records from the probability estimated by the engine (see methods for details).
 The performance of such simple models is quite high (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2) and the median of their cumulative predictive distribution matches quite well the actual number of cumulative positive records found.
@@
 As confirmed by the high efficiency values reported in Table 3, it is striking how many more records would need to be evaluated manually to find all positive matches without using a smart search tool.
-Our engine was able to find matches even close to the end of the heuristically ordered list of records.
-Specifically, in session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)`.\
+The engine was able to find matches even close to the end of the heuristically ordered list of records.
+Specifically, in session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.\
 In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows very large, even a small probability can translate, in the worst scenario, into a relevant number of predicted positive matches (`r Performance$s2$pred_positives %>% max()` in this case).

### 2021-08-19 Manuscript/S2.Additional_outputs.Rmd
S1 update

@@
 Figure 1 show the mixture of the predictive distribution of the probability of a positive match, grouped by labelling status.
-The posterior samples for each record were extracted and joined in a global distribution; on this distribution, density was computed on the logit scale and then logistic transformed for display on a `[0-1]` scale.
+The posterior samples for each record were extracted and joined in a global distribution; on this distribution, density was computed on the logit scale and then logistic transformed for display on a \[[0 - 1]\] scale.
 The light violet ridges show the distribution of the still unlabelled records.\

### 2021-08-19 R/Model.R
fix: fix bug in perform_grid_evaluation
the bug could cause the algorithm to not create the required initial labeled records

@@ -1205,13 +1205,15 @@ perform_grid_evaluation <- function(records, sessions_folder = 'Grid_Search',
 		session_path <- file.path(sessions_folder, Grid[i,]$session)
 
 		# if no record files are present, recreate the session folder
-		if (length(list.files(session_path, pattern = 'Records', recursive = TRUE)) == 0) {
+		if (is.null(get_session_files(Grid[i,]$session, sessions_folder)$Records)) {
 			Records <- Records %>%
 				# remove labels in excess of "n_init"
-				mutate(across(
-					any_of(c('Rev_manual', 'Rev_prediction', 'Rev_prediction_new')),
-					~ replace(.x, Order > Grid[i,]$n_init, NA)
-				))
+				mutate(
+					Rev_manual = coalesce_labels(Records, c('Rev_manual', 'Rev_prediction', 'Rev_prediction_new', 'Rev_previous')) %>%
+						replace(Order > Grid[i,]$n_init, NA),
+					Rev_prediction = NA,
+					Rev_prediction_new = NA
+					)
 
 			create_session(Records, session_name = Grid[i,]$session,
 										 sessions_folder = sessions_folder,

### 2021-08-19 Manuscript/S2.Additional_outputs.Rmd
fixed picture size

@@
 
-```{r hyperparameters, fig.width=15, fig.height=9, fig.cap="Figure 2.
+```{r hyperparameters, fig.width=17, fig.height=10, fig.cap="Figure 2.
 Performance clusters and impact of single hyperparameters on engine performance.
@@
 of models in the ensemble; Quant: uncertainty zone interval to trigger manual review; Resamp: bootstrap resampling; Init: num.
-of initial training records; Multi: oversampling multiplier of positive matches."}
+of initial training records; Multi: oversampling multiplier of positive matches.", cache.rebuild=TRUE}
 

### 2021-08-19 Manuscript/S1.Protocol.Rmd
S1 first draft

@@
 title: "Study protocol"
-date: `r lubridate::today()`
-author:
-  - first_name: "Angelo"
-    last_name: "D'Ambrosio"
-    url: http://github.com/bakaburg1/
-    affiliation: Institute for Infection Prevention and Hospital Hygiene, Freiburg University Hospital
-    affiliation_url: https://www.uniklinik-freiburg.de/iuk.html
-    orcid_id: 0000-0002-2045-5155
-output: distill::distill_article
+date: "`r lubridate::today()`"
+output:
+  github_document:
+    html_preview: false
+    toc: yes
 ---
@@
 
-```{r query creation, echo = TRUE, eval = TRUE}
+```{r query creation}
 
-source('Setup.R') # Load the framework
+source('R/Setup.R') # Load the framework
 
@@
 sometimes it is easier to create two different simpler queries than a complex and long one that returns the same results).\
-In our implementation we define as sessions the group of actions that includes the utilization of a search query and the subsequent cycle of manual review and relevancy prediction of its results.\
+In our implementation we define as sessions the group of actions that includes the utilization of a search query and the subsequent iterations of manual review and automatic classification of its results.\
 
 `perform_search_session()` will use common scientific research database APIs (at the moment Pubmed/Medline, Web of Science and IEEE) to look for records related to query, store them in a csv format and returns or update **journal** (a csv or excel file) with all the information about sessions, queries and search results.
-The records will be stored in folders with the following structure: Records/\*session_id\*/\*query_id\*.
+The records will be stored in folders with the following structure: `Records/session_id/query_id`.
 Some API requires API key to access the data.
-These keys can be stored in the secret.R file with the following structure:
+These keys can be stored in the `secrets.R` file with the following example code (the "baysren" prefix identify the package specific options):
 
 ```{r secrets}
-options(ieee_api_key = 'bb58ndv4xbv535b5779u93ka')
-options(ncbi_api_key = '5cd65c6d044db651af2bf8e9c78fc54fa409')
-options(wos_api_key = 'C4O2SHqGc1rf3jmNxqI')
+options(baysren.ieee_api_key = 'your-ieee-api-key')
+options(baysren.ncbi_api_key = 'your-ncbi-api-key')
+options(baysren.wos_api_key = 'your-wos-api-key')
 ```
@@
 
-If manually downloaded results are available, users can create the Record folders manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`) and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g.
-Pubmed1.nbib, Pubmed2.nib, etc.).
+If manually downloaded results are available, users can create the `Record` folder manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`) and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g.
+`Pubmed1.nbib`, `Pubmed2.nib`, etc.).
 In addition of Pubmed, WOS and IEEE, this method permits to import also Embase and Scopus records, for which an API search was not yet implemented.\
@@
 
-Note that for Pubmed, the API search may return slightly less records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the resulting .nbib files in the Session/Query folder.
+Note that for Pubmed, the API search may return slightly less records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the resulting .nbib files in the `Session/Query` folder.
 `perform_search_session()` will acquire them seamlessly.
@@
 # (based on the `actions` argument) parse already downloaded data (in our case, additional Pubmed results and Embase and Scopus results) manually added to the Session1/Query1 folder.
-journal <- perform_search_session(query = query, year_query = year_filter,
+journal <- perform_search_session(
+	query = query, year_query = year_filter,
 	session_name = 'Session1', query_name = 'Query1',
@@
 
-```{r managing records}
+```{r create session}
 # Create the first session
@@
 
-Notice that the framework is "chaining" friendly and the precedent steps can be all performed in one call (which is the suggested procedure):
+Notice that the framework is "piping" friendly and the precedent steps can be all performed in one call (which is the suggested procedure):
 
@@
 # perform searches and parse files; save and return the journal
-Records <- perform_search_session(query = query, year_query = year_filter,
+Records <- perform_search_session(
+	query = query, year_query = year_filter,
 	session_name = 'Session1', query_name = 'Query1',
@@
 Now the annotation file is ready for manual classification of relevant and non-relevant records.
-The annotation file has a column called `Rev_manual`, where records needs to be classified as "positve" (y) or negative (n) by the user.
+The annotation file has a column called `Rev_manual`, where records needs to be classified as "positive" (y) or "negative" (n) by the user.
 From our experience, around 250 manually classified records are sufficient if a minimum ~20% positivity rate is maintained (see the section about model parameter optimization)./
@@
 - the arguments passed to the function if different from the default, useful for reproducibility.
-- a classification performance summary (*this needs implementation*).
+- a classification performance summary. The procedure may take some time and requires `cmdstan` installed on the machine. Therefore the `compute_performance` argument is set to FALSE by default.
 
@@
 Once the manual review of the generated annotation file is completed, the user can **rerun exactly the same function**.
-The reviewed annotation file will be automatically picked up and used for a new round of classification and review (CR).
+The reviewed annotation file will be automatically picked up and used for a new iteration of classification and review (CR).
 In case the number of records that require manual review is excessively high (e.g.
@@
 
-If there are no positive results (after manual review) in a CR round, the framework records the next round as a "replication".
-After four replication with no positive matches are done, the function will prevent another round and send a warning message.
+If there are no positive results (after manual review) in a CR iteration, the framework records the next iteration as a "replication".
+After four replication with no positive matches are done, the function will prevent another iteration and send a warning message.
 The user can change the replication limit; furthermore it's possible to have the function to stop if either a number (or a fraction of the total records) has been manually reviewed already, or if a certain number of positive matches have been found.
@@
 
-The result files in the Results folder are generated after the Classification phase but before the Review one, and therefore show preliminary results.
+The result files in the Results folder are generated after the Classification phase but before the Review one, and therefore show preliminary results with still unreviewed records.
 The function `consolidate_results(session_name)` will update the results files to show the results after the manual review.
@@
 # the posterior probabilities (extracted from the posterior sample matrix saved
-# during the last CR step). The score threshold and the number of trees can be
+# during the last CR iteration). The score threshold and the number of trees can be
 # chosen by the user; less stringent values can greatly increase computation
@@
 
-Once the new records are collected, `enrich_annotation_file('Session2')` can be used to perform the new CR cycles until no new positive matches are found.
-It may be possible that, during the first CR round, the number of records that require manual review is a large amount: we suggest to evaluate still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.
+Once the new records are collected, `enrich_annotation_file('Session2')` can be used to perform the new CR iteration until no new positive matches are found.
+It may be possible that, during the first CR iteration, the number of records that require manual review is a large amount: we suggest to evaluate still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.
+
+Finally a number of function is available (check `R/Reporting.R`) to summarise and format the results.
+For example, `summarise_by_source()` and `summarise_sources_by_session()`, respectively for one session or a group of sessions, summarise from which scientific database the records are collected from, while `get_source_distribution()` describe the distribution of the number of common sources per record.\
+`summarise_annotations()` and `summarise_annotations_by_session()` describe the results of the CR iterations, again for one or many sessions, reporting the number of positive and negative matches, the number of terms (features) used by the machine learning model, and how the labels changes between iterations.
+`format_performance()` and `format_var_imp()` format the output of the respective analyses.
+`plot_predictive_densities()` plots how the mixture of posterior predictive distributions of records, divided in positive, negative and to-review records, change between iterations,
 
@@
 
+A number of tools are available to evaluate the automatic classification performance.\
+As said before, a result file is stored in the session folder for each CR iteration with a number of information on the classification status; remember to run `consolidate_results(session_name)` if you want these files to include also the manual review of the uncertain records.\
+`compute_changes()` is a simpler function that take an annotation dataframe and computes the changes from the last annotation iteration.\
+The main function for result analysis is `estimate_performance()`.
+The function uses a Bayesian model to estimate how the probability of a positive match drops as the lower boundary of the posterior predictive interval of each record decreases.
+This model allows to estimate the distribution of possibly missed positive records, which in turn permits to compute theoretical sensitivity and efficiency boundaries.
+Of course, the results are hypothetical since it is not possible to know the actual number of missed positive records.\
+The function returns the Bayesian $R^2$ of the model (values below 85% would invalidate this analysis), the posterior sensitivity, the observed and theoretical number positives, the expected efficiency given the theoretical number of positives (that is 1 - the number of records reviewed above the number of records to review to find the predicted number of positives according to a negative hypergeometrical distribution).
+Also, the function plots the cumulative distribution of the observed and theoretical number of positive records.\
+`extract_var_imp()` extract the most important terms used by the BART model and summarises their relevancy for the machine learning model and their statistical relevancy in a simple generalized linear model.
+Discrepancy between these two scores indicate a strongly non-linear effect of the terms.
+
 # Model parameters' optimization
 
-As many complex machine learning models, the choosing of hyperparameters can greatly influence the framework performance.
-For a systematic review helper algorithm, we define the performance as the ability to find as many positive matches by manually labelling/reviewing as few records as possible.\
-We added a number of simple tools to the framework to find a set of hyperparameters using by a "grid search" algorithm.
-We tested these tools on our dataset, manually labeling the first 1200 records (ordered by simple query match, as described when introducing the `create_annotation_file()` function)
+As many complex machine learning models, the choice of hyperparameters can greatly influence the framework performance.
+For a systematic review helper algorithm, we define the performance as the ability to find as many positive matches by manually labelling/reviewing as few records as possible:\
+
+$$
+Sensitivity \times Efficiency = \\
+\frac{Pos.\ found}{Tot.\ pos.} \times \frac{Records\ reviewed}{Tot.\ records}
+$$
+We added a tools to the framework to find a set of hyperparameters using by a "grid search" algorithm.
+We tested these tools on our dataset, manually labeling the first 1200 records, ordered by simple query match.\
+The first step is to create a folder where to store the file required for the search, for example *Grid Search*.
+Then a fully reviewed records file in the format generated by `create_annotation_file()` is necessary; this file can be put in the *Grid Search* but it is not mandatory.
+Once the folder and the file are ready run:
+
+```{r grid search}
+Grid_search <- perform_grid_evaluation(records, sessions_folder = 'Grid_Search',
+																			 prev_classification = records,
+																			 ## Model parameters, deg
+																			 resample = c(FALSE, TRUE),
+																			 n_init = c(50, 100, 250, 500),
+																			 n_models = c(5, 10, 20, 40, 60),
+																			 pos_mult = c(1, 10, 20),
+																			 pred_quants = list(c(.1, .5, .9),
+																			 									 c(.05, .5, .95),
+																			 									 c(.01, .5, .99))
+)
+```
+
+with `records` being the fully annotated data frame or a file path to it. `prev_classification` can be used to import a different classification file with prelabeled records.
+
+The hyperparameters are the following:
+
+* resample: whether to use bootstrapping to increase variability between the ensemble models;
+* n_init: number of initial labelled records to train the machine learning model on;
+* n_models: the number of models to fit and then average, in order to decrease the variance due to random sampling in the mcmc algorithm. It reduces the likelihood of extreme predictions;
+* pos_mult: the oversampling rate of positive records. Useful to improve sensitivity;
+* pred_quants: the distribution quantiles of each posterior prediction, used to define the uncertain records that require manual review.
+
+Once the the grid search is performed, the function `analyse_grid_search()` can be used to analyze it's results.
+This function uses a partition tree analysis to identify hyperparameter sets (performance clusters) that are associated with a certain mean performance score.
+As said before, the default score is Sensitivity x Efficiency; alternatives are the Positive Rate (i.e., positive records found over total records), or Positive Rate x Sensitivity.\
+The function produces a dataframe with the score and the cluster of each combination of parameters, the best hyperparameter set (i.e.
+the most efficient set among the most sensitive in the best cluster) and the best set for each cluster.
+Also, the function creates a plot that helps visualize the individual impact on performance of each hyperparameter.
+
+Once chosen, the hyperparameters can be pass to `enrich_annotation_file()`.\
+Mind that the grid search process may take many days even on powerful computers, so we suggest to stick to the default set of `enrich_annotation_file()`.

### 2021-08-19 Manuscript/S1.Protocol.Rmd
some formatting fix

@@
   github_document:
-    html_preview: false
     toc: yes
@@
 # This call will perform an API search on Pubmed, WOS and IEEE services and/or
-# (based on the `actions` argument) parse already downloaded data (in our case, additional Pubmed results and Embase and Scopus results) manually added to the Session1/Query1 folder.
+# (based on the `actions` argument) parse already downloaded data (in our case,
+# additional Pubmed results and Embase and Scopus results) manually added to the
+# Session1/Query1 folder.
+
 journal <- perform_search_session(
@@
 
-# The last annotation file and posterior sample matrix in the session are
-# found; the most predictive terms (based on the importance score) are chosen
-# and simple prediction trees are used to map the terms to a random subset of
-# the posterior probabilities (extracted from the posterior sample matrix saved
-# during the last CR iteration). The score threshold and the number of trees can be
-# chosen by the user; less stringent values can greatly increase computation
+# The last annotation file and posterior sample matrix in the session are found;
+# the most predictive terms (based on the importance score) are chosen and
+# simple prediction trees are used to map the terms to a random subset of the
+# posterior probabilities (extracted from the posterior sample matrix saved
+# during the last CR iteration). The score threshold and the number of trees can
+# be chosen by the user; less stringent values can greatly increase computation
 # time;
@@
 $$
-We added a tools to the framework to find a set of hyperparameters using by a "grid search" algorithm.
+We added a tool that uses a “grid search” algorithm to find the best set of hyperparameters.
 We tested these tools on our dataset, manually labeling the first 1200 records, ordered by simple query match.\
@@
 ```{r grid search}
-Grid_search <- perform_grid_evaluation(records, sessions_folder = 'Grid_Search',
+Grid_search <- perform_grid_evaluation(
+	records, sessions_folder = 'Grid_Search',
 	prev_classification = records,
-																			 ## Model parameters, deg
+	## Model parameters
 	resample = c(FALSE, TRUE),
@@
 	pos_mult = c(1, 10, 20),
-																			 pred_quants = list(c(.1, .5, .9),
+	pred_quants = list(
+		c(.1, .5, .9),
 		c(.05, .5, .95),

### 2021-08-20 Manuscript/S1.Protocol.Rmd
proof check

@@
 
-# Year filter. The framework convert it to the API specific format seamlessly.
+# Year filter. The framework converts it to the API-specific format seamlessly.
 # common logical comparators can be used, i.e. <, <=, >, >=, while dashes
@@
 sometimes it is easier to create two different simpler queries than a complex and long one that returns the same results).\
-In our implementation we define as sessions the group of actions that includes the utilization of a search query and the subsequent iterations of manual review and automatic classification of its results.\
+In our implementation, we define as sessions the group of actions that includes the utilization of a search query and the subsequent iterations of manual review and automatic classification of its results.\
 
@@
 
-If manually downloaded results are available, users can create the `Record` folder manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`) and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g.
+If manually downloaded results are available, users can create the `Record` folder manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`), and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g.
 `Pubmed1.nbib`, `Pubmed2.nib`, etc.).
-In addition of Pubmed, WOS and IEEE, this method permits to import also Embase and Scopus records, for which an API search was not yet implemented.\
-Users can choose whether to perform an API search, parse already downloaded results, or both using the `actions` argument.
+In addition to Pubmed, WOS and IEEE, this method permits to import also Embase and Scopus records, for which an API search was not yet implemented.\
+Using the `actions` argument, users can choose whether to perform an API search, parse already downloaded results, or both.
 
-Note that for Pubmed, the API search may return slightly less records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the resulting .nbib files in the `Session/Query` folder.
+Note that for Pubmed, the API search may return slightly fewer records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the resulting .nbib files in the `Session/Query` folder.
 `perform_search_session()` will acquire them seamlessly.
@@
 
-Once the records are stored, they must be read and merged into an **annotation file** where the initial manual review of the records will be performed.\
+Once the records are stored, they must be read and merged into an **annotation file** where the initial manual review will be performed.\
 A series of functions are available to prepare the data for the manual evaluation:
@@
 
-	# Read record files. Will parse them if raw data downloaded manually (not
+	# Read record files. Will parse them if raw data is downloaded manually (not
 	# necessary in this case). Return a list of records, one per file.
@@
 
-	# Order records by the relative frequency of the query terms in the
-	# title + abstract text. Increases the chance of encountering relevant records at
-	# the beginning of the manual classification.
+	# Order records by the relative frequency of the query terms in the title +
+	# abstract text. Increases the chance of encountering relevant records at the
+	# beginning of the manual classification.
 	order_by_query_match(query) %>%
@@
 
-Actually all these step are more easily performed through `create_annotation_file()`.
+All these steps are more easily performed through `create_annotation_file()`.
 This function can take as input either the path to record files, or the parsed records (one data frame or a list of data frames) or a group of folders where to look for files into./
-In addition, it also allows to add the new records to a previous annotation file (arg `prev_records`), useful with subsequent searching sessions with different queries; previous manual classifications of records can be imported using `prev_classification`.
-By passing the original query to the `reorder_query` argument, the records are reordered empirically in order to increase the probability to find positive matches first.
+In addition, it also allows adding the new records to a previous annotation file (arg `prev_records`).
+This is useful with subsequent searching sessions with different queries; previous manual classifications can be imported using `prev_classification`.
+By passing the original query to the `reorder_query` argument, the records are reordered empirically to increase the probability of finding positive matches first.
 
 ```{r save annotation file}
-# This function extract the appropriate file paths from a session journal. By
+# This function extracts the appropriate file paths from a session journal. By
 # default it passes all stored files, otherwise it can be filtered by session,
@@
 
-	# or parent folders, since it search for files recursively
+	# or parent folders, since it searches for files recursively
 input <- 'Records'
@@
 
-Once created, the annotations needs to be stored in an **Annotation Session** folder which will contain all informations necessary for the automatic classification.
-This operation is streamlined by the `create_session()` function, which also help manage duplicated sessions.
+Once created, the annotations need to be stored in an **Annotation Session** folder, which will contain all information necessary for the automatic classification.
+This operation is streamlined by the `create_session()` function, which also helps manage duplicated sessions.
 
@@
 
-Notice that the framework is "piping" friendly and the precedent steps can be all performed in one call (which is the suggested procedure):
+Notice that the framework is "piping" friendly, and the precedent steps can be all performed in one call (which is the suggested procedure):
 
 ```{r one call}
-# First create the Records/Session1/Query1 folder and put the manually
-# downloaded records there if you have any. Otherwise the folders will be
+# First, create the Records/Session1/Query1 folder and put the manually
+# downloaded records there if there are any. Otherwise, the folders will be
 # created automatically during the API search
@@
 
-Now the annotation file is ready for manual classification of relevant and non-relevant records.
-The annotation file has a column called `Rev_manual`, where records needs to be classified as "positive" (y) or "negative" (n) by the user.
-From our experience, around 250 manually classified records are sufficient if a minimum ~20% positivity rate is maintained (see the section about model parameter optimization)./
-The function `check_classification_trends()` can help to visualize the trend of the positives/negatives as the number of classified records increases./
+Now the annotation file is ready for the manual classification records.
+The annotation file has a column called `Rev_manual`, where records need to be classified as "positive" (y) or "negative" (n) matches by the user.
+We suggest manually labelling around 250  records, which should be sufficient if a minimum ~20% positivity rate is maintained (see the section about model hyperparameter optimization)./
+The function `check_classification_trends()` can help visualize the trend of the positives/negatives as the number of classified records increases./
 
-Once the first records are labelled manually, the function `enrich_annotation_file()` will use Bayesian Additive Regression Trees (BART) to learn the labeling pattern of the user and predict the positive match probability for the unlabelled records.
-This is a summary of the prediction process:
+Once the first records are labelled manually, the function `enrich_annotation_file()` will use the Bayesian Additive Regression Trees (BART) machine learning model to learn the labelling pattern of the user and predict the positive match probability for the unlabelled records.
+Follows a summary of the prediction process:
 
@@
 For each term, a 0/1 label specifies if it is present in each record.
-Also co-occurrying terms are added as ngrams and highly copresent terms are joined as synonyms;
-- the positive records are weighted 10x more than the negative ones to improve sensitivity;
-- the function models the labeling pattern using the manually reviewed records (learning step);
+Also, co-occurring terms are added as n-grams, and highly copresent terms are joined as synonyms;
+- the positive records are oversampled **10x** to improve sensitivity;
+- the function models the labelling pattern using the manually labelled records (learning step);
 - after the model is created, it assigns a probability distribution of positivity to each record, labelled and unlabelled (prediction step).
-If the number of records is large, the prediction step is broken in chunks of 5000 records, to avoid memory saturation problems; the user will need to set up this parameter according to her machine capabilities;
-- this process is repeated 10 times and the distributions are averaged to induce shrinkage of the estimates;
-- the resulting distribution is summarised by its 98% interval and the unlabelled records will receive a positive/negative predicted label if their interval ends up completely in the joint interval of the positively/negatively labelled records.
-All the other records will be labeled as unknown (unk) and will require manual review.
+If the number of records is large, the prediction step is broken into chunks of **5000 records**, to avoid memory saturation; the user will need to set up this parameter according to her machine capabilities;
+- this process is repeated **10 times**, and the predictive distributions are averaged to induce shrinkage of the estimates (i.e., decrease the chance of outliers);
+- the resulting distribution is summarised by its **98% interval**, and the unlabelled records will receive a positive/negative predicted label if their interval ends up entirely in the joint interval of the positively/negatively labelled records.
+All the other records will be labelled as unknown (unk) and will require manual review.
 
-The user can define parameters like the positives' weight, the number of models to average, whether to apply bootstrap resampling before each repetition, the prediction chunk size, and the prediction distribution interval range.
-To use the function, the only input needed is the session name, the function will automatically identify the relevant file to make predictions on.
+The user can define parameters like the positives' oversampling rate, the number of models to average, whether to apply bootstrap resampling before each repetition, the prediction chunk size, and the prediction distribution interval range.
+To use the function, the only input needed is the session name; the function will automatically identify the relevant file to make predictions on.
 
@@
 
-This function will produce a new excel file which is stored in the Annotations folder of the session; the file will contain a column called `Rev_prediction_new` were the user will find records that require manual review marked by "*".
-These are records with uncertain labelling ("unk"), but also positive predictions and "y"/"n" predictions that contradict previous manually inputed labels (labeled as "check").
-This approach allows to increase the accuracy of the predictions, since the machine learning system is set up to favor sensitivity at the expense of specificity.
-If the function finds prelabelled records (`Rev_previous` column) added when the Annotation file was created or passed as a further input to `enrich_annotation_file()` (`prev_classification` argument), they will be used to relabel the records marked in the `Rev_prediction_new` column.
+This function will produce a new excel file which is stored in the Annotations folder of the session; the file will contain a column called `Rev_prediction_new` where the user will find records that require manual review marked by "*".
+These are records with uncertain labelling ("unk"), but also positive predictions and "y"/"n" predictions that contradict previous manually input labels (labelled as "check").
+This approach increases the accuracy of the predictions since the machine learning system is set up to favour sensitivity at the expense of specificity.
+If the function finds prelabelled records (`Rev_previous` column) added when the Annotation file was created or passed as a further input to `enrich_annotation_file()` (`prev_classification` argument), they will be used to label the records marked in the `Rev_prediction_new` column.
 
@@
 
-- a results summary page which reports the number of records that need manual review (which includes uncertain and unreviewed positive records or records with certain predictions which are different from previous manual labels), the changes, and the final distribution of the labels; it also shows other information like the number of terms in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later).
+- a results summary page reporting the number of records in need of manual review (which includes "unk", "check", and unreviewed "y" records), the changes, and the final distribution of the labels.
+It also shows other information like the number of terms in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later).
 The content of this summary is also saved as a csv file in the Results folder.
 - a variable importance page which list the used terms in order of the fraction of BART trees in which they were used.
-If more than 1 model repetition is used, a more robust score is computed taking the ratio of the mean of the term tree fraction among models and its standard deviation.
+If more than one model repetition is used, a more robust score is computed taking the ratio of the mean of the term tree fraction among models and its standard deviation.
 - the arguments passed to the function if different from the default, useful for reproducibility.
@@
 Finally, the posterior samples produced by the Bayesian engine are stored on the disk.
-This feature can be turned off to save disk space, but at least the samples of the last annotation are necessary to build a new search query building (see next section).
+This feature can be turned off to save disk space, but at least the samples of the last annotation are necessary to build a new search query building (see next section) and for classification performance estimation.
+
+The process of predicting labels and manually reviewing them is what defines a "classification and review (CR) iteration".
 
 Once the manual review of the generated annotation file is completed, the user can **rerun exactly the same function**.
-The reviewed annotation file will be automatically picked up and used for a new iteration of classification and review (CR).
-In case the number of records that require manual review is excessively high (e.g.
-> 250) the function need to be called setting the `stop_on_unreviewed` argument to `FALSE` to allow the classification to proceed even in the presence of unreviewed records (i.e.
-marked by "*") in the `Rev_prediction_new` column.
+The reviewed annotation file will be automatically picked up and used for a new CR iteration.
+If the number of records requiring manual review is excessively high (e.g.
+> 250), the function needs to be called with the `stop_on_unreviewed` argument set to `FALSE` to allow the classification to proceed even in the presence of unreviewed records in the `Rev_prediction_new` column.
 
 If there are no positive results (after manual review) in a CR iteration, the framework records the next iteration as a "replication".
-After four replication with no positive matches are done, the function will prevent another iteration and send a warning message.
-The user can change the replication limit; furthermore it's possible to have the function to stop if either a number (or a fraction of the total records) has been manually reviewed already, or if a certain number of positive matches have been found.
-These three parameter are passed to the `limits` argument which has the following structure and defaults:
+After four replications with no positive matches are complete, the function will prevent another iteration and send a warning message.
+The user can change the replication limit; furthermore, it is possible to have the function stop if either a specified number (or a fraction) of the total records has been manually reviewed or if a certain number of positive matches have been found.
+These three parameters are passed to the `limits` argument, which has the following structure and defaults:
 
@@
 list(
-	stop_after = 4, pos_target = NULL,
+	stop_after = 4,
+	pos_target = NULL,
 	labeling_limit = NULL
@@
 The function `consolidate_results(session_name)` will update the results files to show the results after the manual review.
-The temporary result data is anyway stored in the respective annotations file.
+The temporary result data is stored anyway in the respective annotations file.
 
@@
 
-It's not uncommon that for the first query used in a systematic review not to be the the most effective one, especially in terms of sensitivity.
-We tried to address the problem by creating automatic query generation system.
-The solution is experimental and favors sensitivity at the expense of specificity.
-After a step in which a set of candidate query rules (to be joined by a OR logic) are selected, the user is asked to review them and select rules that make more sense to the topic or deselect too general rules that would generate too many results.
-The algorithm is, of course, not topic aware and therefore may very likely pick terms that are only casually associated with the topic of study; therefore a human review and selection is still needed.
+It is not uncommon for the first query used in a systematic review not to be the most effective one, especially in terms of sensitivity.
+We tried to address the problem by creating an automatic query generation system.
+The solution is experimental and favours sensitivity at the expense of specificity.
+After a step in which a set of candidate query rules (to be joined by an OR logic) are selected, the user is asked to review them and select rules that make more sense to the topic or deselect too general rules that would generate many unspecific results.
+The algorithm is, of course, not topic aware and therefore may very likely pick terms that are only casually associated with the topic of study; therefore, human review and selection are still needed.
 
@@
 # the rules were built, which need to be passed to
-# generate_rule_selection_set(). This function select the most effective (higher
-# positive/negative matches delta) rules; also adds negative terms to increase
-# specificity. A dataframe is generated (or automatically saved if save_path is
-# set). The output proposes groups of equivalent (in terms of number of positive
-# matches found) group of query, ordered by specificity; for each group the user
-# needs to select the best rule by setting the selected_rule column to TRUE. The
-# groups are in order of growing sensitivity/decreasing specificity, so it may
-# make sense to exclude the last groups totally in order to avoid too many
-# search results.
+# generate_rule_selection_set(). This function selects the most effective
+# (higher positive/negative matches delta) rules; also adds negative terms to
+# increase specificity. A dataframe is generated (or automatically saved if
+# save_path is set). The output proposes groups of equivalent (in terms of the
+# number of positive matches found) groups of query, ordered by specificity; for
+# each group, the user needs to select the best rule by setting the
+# selected_rule column to TRUE. The groups are in order of growing
+# sensitivity/decreasing specificity, so it may make sense to exclude the last
+# groups totally in order to avoid too many search results.
 
@@
 
-One last thing to keep in mind is that the query generation algorithm is only aware of the literature collected inside the annotation file it's working on; so it will only be able to pick term combinations that identify positive matches inside an already specific set of documents, while not necessarily being discriminant from the rest of the global literature.\
-Therefore, once the final query is generated it is advisable to add a piece with a AND logic to restrict the results in the scope of the general topic of interest.\
+One last thing to keep in mind is that the query generation algorithm is only aware of the literature collected inside the annotation file.
+So it will only be able to pick term combinations that identify positive matches inside the already specific set of documents while not necessarily being discriminant from the rest of the global literature.\
+Once the final query is generated, it is advisable to add a constraining subquery with an AND logic to restrict the results to the scope of the topic of interest.\
 In our case, we added "AND ((antimicrobial resistance) OR (healthcare infection))" since being the global topic of our research, those terms were understandably not selected by the query generation algorithm as discriminant.\
@@
 Once the new query was generated, a second search session called `Session2` was created, using the strategy described in the protocol.
-Due to the lower specificity of the second query, particular care was needed in managing the far larger amount of records, since manual downloading may be necessary from Pubmed, Embase, and Scopus (which usually have limits on the amount of records one can download at once), and because the automatic classification processing time increases proportionally to the number of records to label.\
-It is advisable then to cosider removing iteratively the less specific rules from the query until a manageable number of records is found, considering that the probability of finding positive matches not already found by more specific queries drops exponentially.\
+Due to the lower specificity of the second query, particular care was needed in managing the far larger amount of records since manual downloading may be necessary from Pubmed, Embase, and Scopus (which usually have limits on the amount of records one can download at once), and because the automatic classification processing time increases proportionally with the number of records to label.\
+It is advisable then to consider removing the less specific rules iteratively from the query until a manageable number of records is obtained, considering that the probability of finding new positive matches not already found by more specific queries drops exponentially.\
 
-Once the new records are collected, `enrich_annotation_file('Session2')` can be used to perform the new CR iteration until no new positive matches are found.
-It may be possible that, during the first CR iteration, the number of records that require manual review is a large amount: we suggest to evaluate still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.
+Once the new records are collected, `enrich_annotation_file('Session2')` (or any other new session name) can be used to perform the new CR iterations.
+It may be possible that during the first CR iteration the number of records requiring manual review is a large amount: we suggest evaluating still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.
 
-Finally a number of function is available (check `R/Reporting.R`) to summarise and format the results.
+## Result analysis and reporting
+
+A number of tools are available to evaluate the automatic classification performance.\
+As said before, a result file is stored in the session folder for each CR iteration with information on the classification status; remember to run `consolidate_results(session_name)` if you want these results to take into account the manual review of the predicted labels.\
+`compute_changes()` is a simple function that take an annotation dataframe and computes the changes from the last annotation iteration.\
+The primary function for result analysis is `estimate_performance()`.
+The function uses a Bayesian model to estimate how the probability of a positive match drops as records' lower boundary of the posterior predictive interval decreases.
+This model computes the cumulative distribution of possibly missed positive records, which in turn permits extraction of the engine's theoretical sensitivity and efficiency boundaries.
+These boundaries are worse case scenarios since it is impossible to know the number of missed positive records.\
+The function returns the Bayesian $R^2$ of the model (values below 85-90% would invalidate this analysis), the posterior sensitivity, the observed and theoretical number positives, the expected efficiency given the theoretical number of positives (that is 1 - the number of records reviewed above the number of records to review to find the predicted number of positives according to a negative hypergeometrical distribution).
+Also, the function plots the cumulative distribution of the observed and theoretical number of positive records.\
+`extract_var_imp()` extract the most relevant terms used by the BART model and summarises their relevancy for the machine learning model and their statistical relevancy in a simple generalized linear model.
+A discrepancy between these two scores indicates a non-linear effect of the terms.
+
+Finally, several functions are available (check `R/Reporting.R`) to summarise and format the results.
 For example, `summarise_by_source()` and `summarise_sources_by_session()`, respectively for one session or a group of sessions, summarise from which scientific database the records are collected from, while `get_source_distribution()` describe the distribution of the number of common sources per record.\
 `summarise_annotations()` and `summarise_annotations_by_session()` describe the results of the CR iterations, again for one or many sessions, reporting the number of positive and negative matches, the number of terms (features) used by the machine learning model, and how the labels changes between iterations.
-`format_performance()` and `format_var_imp()` format the output of the respective analyses.
-`plot_predictive_densities()` plots how the mixture of posterior predictive distributions of records, divided in positive, negative and to-review records, change between iterations,
-
-# Results evaluation
-
-A number of tools are available to evaluate the automatic classification performance.\
-As said before, a result file is stored in the session folder for each CR iteration with a number of information on the classification status; remember to run `consolidate_results(session_name)` if you want these files to include also the manual review of the uncertain records.\
-`compute_changes()` is a simpler function that take an annotation dataframe and computes the changes from the last annotation iteration.\
-The main function for result analysis is `estimate_performance()`.
-The function uses a Bayesian model to estimate how the probability of a positive match drops as the lower boundary of the posterior predictive interval of each record decreases.
-This model allows to estimate the distribution of possibly missed positive records, which in turn permits to compute theoretical sensitivity and efficiency boundaries.
-Of course, the results are hypothetical since it is not possible to know the actual number of missed positive records.\
-The function returns the Bayesian $R^2$ of the model (values below 85% would invalidate this analysis), the posterior sensitivity, the observed and theoretical number positives, the expected efficiency given the theoretical number of positives (that is 1 - the number of records reviewed above the number of records to review to find the predicted number of positives according to a negative hypergeometrical distribution).
-Also, the function plots the cumulative distribution of the observed and theoretical number of positive records.\
-`extract_var_imp()` extract the most important terms used by the BART model and summarises their relevancy for the machine learning model and their statistical relevancy in a simple generalized linear model.
-Discrepancy between these two scores indicate a strongly non-linear effect of the terms.
+`format_performance()` and `format_var_imp()` format the output of the similarly named analyses.
+`plot_predictive_densities()` plots how the mixture of posterior predictive distributions of records, divided into positive, negative and to-review records, change between iterations,
 
@@
 
-As many complex machine learning models, the choice of hyperparameters can greatly influence the framework performance.
+As with many complex machine learning models, the choice of hyperparameters can significantly influence the framework performance.
 For a systematic review helper algorithm, we define the performance as the ability to find as many positive matches by manually labelling/reviewing as few records as possible:\
@@
 $$
-We added a tool that uses a “grid search” algorithm to find the best set of hyperparameters.
-We tested these tools on our dataset, manually labeling the first 1200 records, ordered by simple query match.\
+
+We added a “grid search” algorithm to find the best set of hyperparameters. We tested these tools on our dataset, manually labeling the first 1200 records, ordered by simple query match.\
 The first step is to create a folder where to store the file required for the search, for example *Grid Search*.
@@
 * resample: whether to use bootstrapping to increase variability between the ensemble models;
-* n_init: number of initial labelled records to train the machine learning model on;
-* n_models: the number of models to fit and then average, in order to decrease the variance due to random sampling in the mcmc algorithm. It reduces the likelihood of extreme predictions;
+* n_init: number of initially labelled records to train the machine learning model on;
+* n_models: the number of models to fit and then average to decrease the variance due to random sampling in the MCMC algorithm. It reduces the likelihood of extreme predictions;
 * pos_mult: the oversampling rate of positive records. Useful to improve sensitivity;
@@
 
-Once the the grid search is performed, the function `analyse_grid_search()` can be used to analyze it's results.
-This function uses a partition tree analysis to identify hyperparameter sets (performance clusters) that are associated with a certain mean performance score.
-As said before, the default score is Sensitivity x Efficiency; alternatives are the Positive Rate (i.e., positive records found over total records), or Positive Rate x Sensitivity.\
-The function produces a dataframe with the score and the cluster of each combination of parameters, the best hyperparameter set (i.e.
-the most efficient set among the most sensitive in the best cluster) and the best set for each cluster.
-Also, the function creates a plot that helps visualize the individual impact on performance of each hyperparameter.
+Once the grid search is performed, the function `analyse_grid_search()` can be used to analyze its results.
+This function uses a partition tree analysis to identify hyperparameter sets (performance clusters) with different mean performance scores.
+As said before, the default score is Sensitivity x Efficiency; alternatives are the Positive Rate (i.e., positive records found over total records) or Positive Rate x Sensitivity.\
+The function produces a dataframe with the score and the cluster of reference of each combination of parameters, the best hyperparameter set (i.e., the most efficient set among the most sensitive in the best cluster) and the best set for each cluster.
+Also, the function creates a plot to visualize the individual impact on performance of each hyperparameter.
 
 Once chosen, the hyperparameters can be pass to `enrich_annotation_file()`.\
-Mind that the grid search process may take many days even on powerful computers, so we suggest to stick to the default set of `enrich_annotation_file()`.
+Mind that the grid search process may take many days, even on powerful computers, so we suggest sticking to the default set of `enrich_annotation_file()`. \

### 2021-08-30 Manuscript/Manuscript_Methods.Rmd
Initial commit

---
title: "Methods"
date: "`r lubridate::today()`"
output:
  github_document:
    html_preview: false
---

### 2021-08-30 R/Record_search.R
fix: pubmed search was not using the api in the correct way
I don't forsee any problem with the search results anyway

@@ -214,7 +214,7 @@ search_pubmed <- function(query, year_query = NULL, additional_fields = NULL,
 			rescords <- try(rentrez::entrez_fetch(db = "pubmed", web_history = res$web_history,
 																						retstart = step * 200, retmax = min(200, total_count - step * 200),
 																						rettype = 'medline', parsed = F,
-																						api_key = options('ncbi_api_key')), silent = T)
+																						api_key = api_key), silent = T)
 
 			have.results <- class(rescords) == 'character'
 			trials <- trials + 1

### 2021-08-30 Manuscript/Manuscript_Methods.Rmd
methods update

@@
 ---
+
+## Methods
+
+### General description
+
+We built an R [@rstat] based framework with the aim of simplifying two aspects of systematic reviews: record acquisition and relevance classification.
+The framework is composed by several components which act together while being independent enough to be in principle be substituted by alternative implementations, given that the structure of the intermediate data outputs is respected.
+Check Supplemental Material S1 for an in-depth description of the framework and how to use it.\
+The tasks carried out by the framework are grouped into "sessions", that is a set of actions that starts from a search query with which collect a set of unlabelled records and ends with the having a fully labelelled set (Fig.
+1).
+From this labelled set, the framework allows to generate a new query and perform a new session.\
+Follows a description of the method components.
+
+![Metods' visual depiction](methods_diagram.png)
+### Records' acquisition
+We built a set of tools to let user automatically search and download records data from three major scientific databases: MEDLINE, Web Of Science (WOS) and the Institute of Electrical and Electronics Engineers (IEEE).
+The user needs to input a boolean query and a date range.
+For WOS an API key is nece

### 2021-08-30 Manuscript/S3.Search_guide.Rmd
initial commit

---
title: "Databases' search guide"
date: "`r lubridate::today()`"
output:
  github_document:
    toc: yes
---

## WOS
- activate your institution proxy or log in in some way (it is only needed to get the API key, then you can log off the proxy)
- go to https://apps.webofknowledge.com/
- extract the API key from the URL, is denominated by SID
- put the key in the secrets.R file and source it or source Setup.R
- perform the search using the API

## IEEE
- get your API key and put it into the secrets.R
- source the file source Setup.R
- perform the search using the API

## Scopus
- change the NOT in the query to AND NOT
- go to https://www.scopus.com/search/form.uri?display=basic#basic
- log in with your institution credential
- set up the year range
- search within: title, abstract, keywords, authors
- select years in order to have just less than 2000 records
- download csv (Excel). Choose "Citation information" and "Abstract & keywords"
- call the files Scopus#.csv with # being a sequential number
- perform_search_session() will find and parse the files

## Pubmed
- put your API key in the secrets.R file and source it or source Setup.R
- perform the search using the API
- put the same query into pubmed and download records in the Pubmed format.
- only 10k records can be downloaded at once, so use the year filter to partition the records
- call the file Pubmed#.nbib with # being a sequential number
- perform_search_session() will find and parse the files

## Embase
- Login from within the institution or activate remote access
- go to https://www.embase.com/#advancedSearch/default
- set your date range
- in the mapping field select all apart from "Limit to terms indexed in article as 'major focus'"
- in "Sources" select Embase
- select records in blocks of 10K
- chose format: Csv - fields by column, output: Full record (may take a while to prepare the download and you can download only one batch at time)
- call the files Embase#.csv with # being a sequential number

### 2021-08-30 Manuscript/Manuscript_Results.Rmd
Title change
results update
put info on the first query

@@
 ---
-title: "Manuscript"
+title: "Results"
 date: "`r lubridate::today()`"
@@
 ```{r session 1}
+
+first_query <- import_data('Session_journal.csv') %>% 
+    filter(Session_ID == 'Session1') %>% 
+    with(Query[1])
+
 records_s1 <- import_data(session1_files$Records)
@@
 ```
+
+The input search query was:\
+
+*`r first_query`*
+
+including results between 2010 and 2020 (included).
+The automatic search tools were used for MEDLINE, WOS and IEEE, while a manual search and importation was necessary for EMBASE and SCOPUS.
+The search was repeated manually also for MEDLINE, since, as reported in the methods, the web interface may return different results from the API.
 
@@
 The final piece *AND ((antimicrobial resistance) OR (healthcare infection)* was added manually to better define the search domain, since the algorithm was trained on documents that were all more or less related to these topics.\
-The generated query also provides a more nuanced understanding of the engine's internal classification logic, and this is helpful to spot possible biases in the model.
+The generated query also provides a more nuanced understanding of the engine's internal classification logic, and this is helpful to spot possible biases in the model.\
+
+The search was done with the same year filter and procedures of the first session.\
 

### 2021-08-30 Manuscript/Manuscript_Methods.Rmd
methods update

@@
 From this labelled set, the framework allows to generate a new query and perform a new session.\
-Follows a description of the method components.
+It is advisable that the research starts using the framework with a specific query from which she expects a high relevant/non-relevant record ratio.\
+Follows a description of the framework's components.\
 
-![Metods' visual depiction](methods_diagram.png)
+![Figure 1. Framework visual depiction.](methods_diagram.png)
 ### Records' acquisition
-We built a set of tools to let user automatically search and download records data from three major scientific databases: MEDLINE, Web Of Science (WOS) and the Institute of Electrical and Electronics Engineers (IEEE).
-The user needs to input a boolean query and a date range.
-For WOS an API key is nece
+We built a set of tools to let user automatically search and download records data from three major scientific databases: MEDLINE (https://pubmed.ncbi.nlm.nih.gov/), Web Of Science (WOS, https://apps.webofknowledge.com/) and the Institute of Electrical and Electronics Engineers (IEEE, https://ieeexplore.ieee.org/Xplore/home.jsp).
+The user needs to input a search query and a date range.
+The query may contain boolean operators AND, OR, NOT and nested parentheses.
+The dabatase will be also called "sources" in the rest of the text.\
+For WOS an Application Programming Interface (API) key is necessary to use the automatic search tools; for IEEE, if an API key is not available, a slower, webscraping-based solution will be employed; for MEDLINE the API key is required for high frequency requests to the NCBI server [@pubmed], which may happen if the chosen query produces a large number of records, since our tool splits a big API requests in multiple smaller ones.\
+It is also possible to download and import records in the framework manually.
+This is particularly useful to acquire records from the SCOPUS (https://www.scopus.com/search/form.uri?display=basic#basic) and EMBASE databases (https://www.embase.com/#advancedSearch/default), for which a comprehensive API interface was not easy to build; the framework will be able to import the manually downloaded results seamlessly.A short guide on how to setup the search for each supported database is available in Supplemental Material S3.\
+Once the records are dowloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources, and ordering the records by simple query term frequency, putting the most likely relevant on top.
+The output is an "Annotation file".
+
+### Document-Term matrix generation

### 2021-08-31 Manuscript/Manuscript_Methods.Rmd
docs: added some commenting

@@
 date: "`r lubridate::today()`"
+bibliography: references.bib
+csl: apa.csl
 output:
@@
 ![Figure 1. Framework visual depiction.](methods_diagram.png)
+
 ### Records' acquisition
-We built a set of tools to let user automatically search and download records data from three major scientific databases: MEDLINE (https://pubmed.ncbi.nlm.nih.gov/), Web Of Science (WOS, https://apps.webofknowledge.com/) and the Institute of Electrical and Electronics Engineers (IEEE, https://ieeexplore.ieee.org/Xplore/home.jsp).
+We built a set of tools to let user automatically search and download records data from three major scientific databases: MEDLINE (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
 The user needs to input a search query and a date range.
@@
 It is also possible to download and import records in the framework manually.
-This is particularly useful to acquire records from the SCOPUS (https://www.scopus.com/search/form.uri?display=basic#basic) and EMBASE databases (https://www.embase.com/#advancedSearch/default), for which a comprehensive API interface was not easy to build; the framework will be able to import the manually downloaded results seamlessly.A short guide on how to setup the search for each supported database is available in Supplemental Material S3.\
-Once the records are dowloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources, and ordering the records by simple query term frequency, putting the most likely relevant on top.
+This is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/search/form.uri?display=basic#basic>) and EMBASE databases (<https://www.embase.com/#advancedSearch/default>), for which a comprehensive API interface was not easy to build; the framework will be able to import the manually downloaded results seamlessly.A short guide on how to setup the search for each supported database is available in Supplemental Material S3.\
+Once the records are downloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources, and ordering the records by simple query term frequency, putting the most likely relevant on top.
 The output is an "Annotation file".
@@
 ### Document-Term matrix generation
+The annotation file produced in the previous step has a number of fields describing a publication.
+Of these we use the following to model its relevance: title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
+We use a series of Natural Language Processing (NLP) techniques (*should I put a general reference?*) to transform the textual information in these fields into machine learning features.
+The first steps are tokenizing the text (i.e., separate the terms), remove common stopwords (i.e.
+grammar term bringing no meaning) and lemmatizing the remaining terms (i.e.
+reduce them to their base grammar form).
+Tokenization for authors, keywords and MESH terms works differently than for title and abstract text, since it keep a whole unit without breaking it in its single terms.\

### 2021-08-31 R/Model.R

@@ -14,8 +14,10 @@ create_training_set <- function(Records, min_freq = 0.05) {
 			ID, Title, Abstract, Authors, Keywords, Mesh
 		)
 
+	# Compute minimum term frequency among documents
 	min_freq <- max(floor(sum(Records$Target %in% c('y', 'n')) * min_freq), 1)
 
+	# Ensure that all positive document terms are kept
 	Records <- Records[c(
 		rep(which(Records$Target %in% 'y'), min_freq),
 		which(Records$Target %nin% 'y')),]

### 2021-08-31 Manuscript/S2.Additional_outputs.Rmd
added page break after TOC
small improvement

--- 2021-08-19 Manuscript/S2.Additional_outputs.Rmd
@@
 ---
+
+\newpage
 
@@
 The light violet ridges show the distribution of the still unlabelled records.\
-For each iteration, the thresholds which define the lower and the upper range of 98% predictive interval (PrI) respectively for the positive and negative records.
-The zone comprised between these two boundaries defines the uncertainty zone; records whose 98% PrI intersects this zone requires manual review.\
+For each iteration, the thresholds which define the lower and the upper range of 98% predictive interval (PrI) respectively for the positive and negative records are shown.
+The zone included between these two boundaries defines the uncertainty zone; records whose 98% PrI intersects this zone requires manual review.\
 Notice how the positive and negative densities start overlapping starting with the second iteration of Session 2.

### 2021-08-31 Manuscript/Manuscript_Methods.Rmd
update

@@
 csl: apa.csl
-output:
-  github_document:
-    html_preview: false
+output: pdf_document
 ---
@@
 
-### Records' acquisition
+### Record's acquisition and inital labeling
 We built a set of tools to let user automatically search and download records data from three major scientific databases: MEDLINE (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
@@
 Once the records are downloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources, and ordering the records by simple query term frequency, putting the most likely relevant on top.
-The output is an "Annotation file".
+The output is an "Annotation file".\
+
+To allow the automatic classification of the records, a first initial manual input is needed.
+We suggest to manually label as relevant ("positive" in the rest of the text) or not ("negative") the first 250 records (see "hyperparameter optimization" later).\
 
@@
 The annotation file produced in the previous step has a number of fields describing a publication.
-Of these we use the following to model its relevance: title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
+We use the following fields to model its relevance: title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
 We use a series of Natural Language Processing (NLP) techniques (*should I put a general reference?*) to transform the textual information in these fields into machine learning features.
@@
 Tokenization for authors, keywords and MESH terms works differently than for title and abstract text, since it keep a whole unit without breaking it in its single terms.\
+To reduce noise and save computation time, terms that appeared in less than 5% of the corpus of labelled documents (positive and negatives) were removed from those labelled as negative.
+All terms in the positive set are kept to increase sensitivity at the cost of specificity.\
+Some terms tend to co-appears in records even if not consecutively in the text (non-consecutive ngrams, nc-ngrams); when they do so they often carry a particular meaning.
+To detect these terms we generated a network representation of all terms based on their cosine similarity in terms of co-presence in a document, keeping only pairs with cosine similarity > 0.5.
+From this network we extracted the maximal cliques [@eppstein2010listing], that is group of terms which all tend to appear together often; These generated terms are added to the dataset.
+To avoid overfitting, we kept nc-ngrams of maximum 10 terms.\
+The similarity network is rebuilt also considering the nc-ngrams, this time using a similarity of .9 as threshold and finding the cliques again.
+In this case, the cliques represent terms that always appear together and therefore can be considered synonyms.
+These terms are merged in the dataset to increase computation efficiency and reduce overfitting.\
+The final output is a matrix, also called a Document-Term Matrix (DTM), with $N_d$ rows for each record $D$, $N_t$ terms column for each $t_{field}$ (divided by record field) and ${0,1}$ values whether $t_{field} \in D$.
+We also enriched the DTM with a feature for each record field recording the number of terms in each, to relate the terms relative importance (e.g., the same term can have different relevance given on the length of a document).
+
+### Label prediction
+We used a Bayesian Additive Regression Trees (BART) model [@chipman2010bart] [in the implementation of @kapelner2013bartmachine] to model the probability of a record of being relevant for the systematic review, given the information coded into the enriched DTM.
+BART models have a number of advantages; as other boosted trees techniques [@hastie2009boosting] they can model complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.
+The Bayesian framework they are built on provides further advantages, namely, less sensitivity on hyperparameter choices, natural regularization, and, most of all, predictive distributions as output in place of point-wise predictions.\
+We setup the BART model to use 2000 iterations (after 250 burn in iterations) and 50 trees; we used a $k$ value of 2 to regularized extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction].
+Since for our purpose it is more important to find all positive matches (i.e., focus on sensitivity).\
+The output is a posterior predictive distribution (PPD) of the probability of a positive match for each record.
+To further improve prediction stability, an ensemble of ten models was fitted, averaging the predictions between models.\
+To choose how to label a record we exploit the uncertainty typical of Bayesian estimates, assigning a positive label to records whose posterior distribution of the probability of being positive ends up almost totally in the range of probabilities of records already labelled as positives, without crossing the range of the records previously labelled as negatives.\
+
+To describe the process formally, first we define
+
+$$\pi_i = Pr(L_{D_i} = \text{pos}|DTM,model)$$
+
+as the PPD of a record $D_i$ of being assigned a positive label ($L_{D_i}$) and
+
+$$\{\pi_{i,l} = [\pi_i : Pr(\pi_i) = 1\%], \pi_{i,u} = [\pi_i : Pr(\pi_i) = 99\%]\}$$
+as respectively the lower and upper boundaries of the 98% quantile interval of $\pi_i$ (predictive interval, PrI).\
+A record will be labelled as positive if
+
+$$\pi_{i,l} > max(\max_{i:L_{D_i}=\text{neg}}\pi_{i,u},\min_{i:L_{D_i}=\text{pos}}\pi_{i,l})$$
+with $L$ being a manually assigned/reviewed label.
+That is, to be positive, a record lower 98% PrI boundary should be higher than both the highest among the upper boundaries of negative records and the lowest of boundaries of the positive ones (*I wonder whether a picture could help...*), in other words, its PrI should be included in the mixture of distributions of the already labbeled positive records and not cross those of the negative ones.\
+Conversely, a record is labelled as negative if
+
+$$\pi_{i,u} < min(\min_{i:L_{D_i}=\text{pos}}\pi_{i,l},\max_{i:L_{D_i}=\text{neg}}\pi_{i,u})$$
+All other records are labelled as urcertain, because their PrI crosses the "uncertainty zone" defined as:
+
+$$U=\pi:\pi \in[\min_{i:L_{D_i}=\text{pos}}\pi_{i,l}, \max_{i:L_{D_i}=\text{neg}}\pi_{i,u}]$$

### 2021-09-08 Manuscript/Manuscript_Methods.Rmd
complete draft

--- 2021-08-30 Manuscript/Manuscript_Methods.Rmd
@@
 date: "`r lubridate::today()`"
+bibliography: references.bib
+csl: apa.csl
 output:
-  github_document:
-    html_preview: false
+  # pdf_document:
+  #   includes:
+  #     in_header: header.tex
+  github_document: default
 ---
@@
 
-We built an R [@rstat] based framework with the aim of simplifying two aspects of systematic reviews: record acquisition and relevance classification.
-The framework is composed by several components which act together while being independent enough to be in principle be substituted by alternative implementations, given that the structure of the intermediate data outputs is respected.
-Check Supplemental Material S1 for an in-depth description of the framework and how to use it.\
-The tasks carried out by the framework are grouped into "sessions", that is a set of actions that starts from a search query with which collect a set of unlabelled records and ends with the having a fully labelelled set (Fig.
+We built an R [@rstat] based framework with the goal of simplifying two aspects of systematic reviews: record acquisition and classification.
+The framework is composed of several components which act together while being independent enough to be in principle be substituted by alternative implementations, given that the structure of the intermediate data outputs is respected.
+See Supplemental Material S1 for an in-depth description of the framework and how to use it.\
+The tasks carried out by the framework are grouped into "sessions", that is, a set of actions that starts from using a search query to obtain a set of scientific publications (records), which will be eventually labelled as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest (Fig.
 1).
 From this labelled set, the framework allows to generate a new query and perform a new session.\
-It is advisable that the research starts using the framework with a specific query from which she expects a high relevant/non-relevant record ratio.\
+The researcher should use the framework with a specific query from which she expects a high relevant/non-relevant record ratio.\
 Follows a description of the framework's components.\
 
-![Figure 1. Framework visual depiction.](methods_diagram.png)
-### Records' acquisition
-We built a set of tools to let user automatically search and download records data from three major scientific databases: MEDLINE (https://pubmed.ncbi.nlm.nih.gov/), Web Of Science (WOS, https://apps.webofknowledge.com/) and the Institute of Electrical and Electronics Engineers (IEEE, https://ieeexplore.ieee.org/Xplore/home.jsp).
+```{r method_diagram, fig.cap = "Figure 1.Framework's visual depiction.", echo = FALSE, out.width = "100%"}
+knitr::include_graphics("methods_diagram.png", auto_pdf = T)
+```
+
+<!-- ![Figure 1. Framework visual depiction.](methods_diagram.png) -->
+
+### Record's acquisition and initial labelling
+We built a set of tools to let users automatically search and download records data from three major scientific databases ("sources"): MEDLINE (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
 The user needs to input a search query and a date range.
-The query may contain boolean operators AND, OR, NOT and nested parentheses.
-The dabatase will be also called "sources" in the rest of the text.\
-For WOS an Application Programming Interface (API) key is necessary to use the automatic search tools; for IEEE, if an API key is not available, a slower, webscraping-based solution will be employed; for MEDLINE the API key is required for high frequency requests to the NCBI server [@pubmed], which may happen if the chosen query produces a large number of records, since our tool splits a big API requests in multiple smaller ones.\
+The query may contain boolean operators AND, OR, NOT and nested parentheses.\
+For WOS, an Application Programming Interface (API) key is necessary to use the automatic search tools; for IEEE, if an API key is not available, a slower, web scraping-based solution will be employed; for MEDLINE, an API key is required only for high-frequency requests to the NCBI server [@pubmed], or if a large number of records is expected since our tool splits big API requests in multiple smaller ones.\
 It is also possible to download and import records in the framework manually.
-This is particularly useful to acquire records from the SCOPUS (https://www.scopus.com/search/form.uri?display=basic#basic) and EMBASE databases (https://www.embase.com/#advancedSearch/default), for which a comprehensive API interface was not easy to build; the framework will be able to import the manually downloaded results seamlessly.A short guide on how to setup the search for each supported database is available in Supplemental Material S3.\
-Once the records are dowloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources, and ordering the records by simple query term frequency, putting the most likely relevant on top.
-The output is an "Annotation file".
+This is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/search/form.uri?display=basic#basic>) and EMBASE databases (<https://www.embase.com/#advancedSearch/default>), for which a comprehensive API interface was not easy to build.
+A short guide on how to set up the framework for each supported database is available in Supplemental Material S3.\
+Once the records are downloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources, ordering the records by simple query term frequency ("simple ordering"), putting the most likely relevant records on top.
+The output is an "Annotation file".\
+
+A first initial set of manually labelled records is needed to start the automatic classification. We suggest manually label the first 250 records (see "hyperparameter optimization" later).\
 
 ### Document-Term matrix generation
+The annotation file produced in the previous step has a number of fields characterizing a scientific publication.
+The framework models the relevance of a record based on the following fields: title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
+A series of Natural Language Processing (NLP) techniques <mark>(*should I put a general reference?*)</mark>) are employed to transform the textual information in these fields into features for machine learning.
+The processing of free text fields includes tokenization (i.e., extracting the terms), common stopwords (i.e.
+sentence components bringing no meaning) removal, part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatization of the terms (i.e.
+reduction to their base grammar form).
+Processing for authors, keywords and MESH terms identify logical units (e.g., author's full names, composite keywords) without breaking them into single terms, and no stopwords removal or lemmatization are applied.\
+To reduce noise and save computation time, terms that appeared in less than 5% of the labelled documents (positive and negatives) are removed from negative records.
+All terms in the positive set are kept to increase sensitivity at the cost of specificity.\
+Some terms tend to co-appear in records (non-consecutive ngrams, nc-ngrams), often carrying a particular meaning when copresent.
+To detect nc-ngrams, we generated a network representation posing edges between terms with a cosine similarity in terms of records copresence > 0.5.
+We extracted the maximal cliques in the network [@eppstein2010listing] representing highly correlated groups of terms; These generated terms are added to the data set.
+To avoid overfitting, we kept nc-ngrams of a maximum of ten terms.\
+A similarity network is built again using a similarity threshold of 0.9 and finding the cliques again.
+In this case, the cliques represent terms that always appear together and therefore can be considered synonyms.
+These terms are merged in the data set to increase computation efficiency and reduce overfitting.\
+The final output is a matrix, also called a Document-Term Matrix (DTM), with $N_d$ rows representing the records $D$, $N_t$ terms column for the $t_{field}$ terms (divided by record field) and ${0,1}$ values whether $t_{field} \in D$.
+We also enriched the DTM with features storing the number of terms in each field to help the model scale term importance based on the document length.
+
+### Label prediction
+We used a Bayesian Additive Regression Trees (BART) machine learning model [@chipman2010bart] [in the implementation of @kapelner2013bartmachine] to predict the probability of a record of being relevant, given the information coded into the enriched DTM.
+BART models have several advantages: as other boosted trees techniques [@hastie2009boosting], they can model complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.
+However, the Bayesian framework they are built on provides further benefits: less sensitivity on hyperparameter choices, natural regularization, and, most of all, predictive distributions as output in place of point-wise predictions.\
+We set up the BART model to use 2000 iterations (after 250 burn-in iterations) and 50 trees; we used a $k$ value of 2 to regularized extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction].
+Since the goal is to find all positive matches (i.e., focus on sensitivity), positive records are oversampled ten times.\
+The output is a posterior predictive distribution (PPD) of each record's probability of a positive match.
+An ensemble of ten models was fitted to improve prediction stability by averaging the predictions between models.\
+To choose how to label a record, we exploit the uncertainty typical of Bayesian estimates to decide a record label and whether it requires manual evaluation.
+To describe the process formally, we define
+
+$$\pi_i = \frac{1}{M}\sum_mPr(L_i = \text{pos}|DTM,model_m)$$
+
+as the PPD of a record $D_i$ being assigned a positive label ($L_i$), averaging the PPDs of the ensemble of $M=10$ models, and
+
+$$\pi_{i,l} = \{\pi_i : Pr(\pi_i) = 1\%\}\\
+\pi_{i,u} = \{\pi_i : Pr(\pi_i) = 99\%\}$$
+
+as respectively the lower and upper boundaries of the 98% quantile interval of $\pi_i$ (98% predictive interval, 98% PrI).\
+Then we identify the "uncertainty zone"
+
+$$U_\pi=[\max_{D_i \in L_n}\pi_{i,u}, \min_{D_i \in L_p}\pi_{i,l}]$$
+
+that is, a range of $\pi$ values between the smallest $\pi_{i,l}$ in the set of already labelled positive records $L_p$ and the largest $pi_{i,u}$ related to the negative ones $L_n$, noting that the two limits can appear in any order.\
+Consequently, a record $D_i$ will be labelled as positive if
+
+$$\pi_{i,l} > \max_{\pi \in U_\pi} \pi$$
+
+that is, its lower 98% PrI boundary should be higher than every value in the uncertainty zone.
+In other words, for a record to be labelled positive, its PPD should be within the range of the mixture of PPD of the previously labelled positive records and not cross the distributions of the negative records.\
+Conversely, a record is labelled as negative if
+
+$$\pi_{i,u} > \min_{\pi \in U_\pi} \pi$$
+
+All other records are labelled as uncertain and will require manual labelling.
+Also, positive labelled records are to be reviewed to avoid false positives.
+Furthermore, if a predicted label differs from the existing one, a manual check will be required; this could identify uncertainty in the labelling criteria of the same researcher or between different researchers.
+
+The automatic classification task and the manual review step form an iterative loop (CR iterations).
+The whole algorithm falls in the pattern defined as active machine learning [@settles2009active], with the machine querying the user to address and progressively resolve uncertainty in the classification.\
+The CR iterations continue until no new positive matches are found in four consecutive iterations.
+The framework supports alternative stopping conditions like limits on the fraction or number of total records reviewed and on the total number of positive matches found.
+
+### New search query generation
+We created an algorithm that helps create a new search query that could detect further relevant publications missed during the first search, possibly at a reasonable cost in specificity (i.e., a higher number of negative results).\
+The algorithm encompasses a number of steps:
+
+* We fit a partition tree [@rpart] between the DTM and 800 samples from the PPD; if a term is present multiple times in the DTM (e.g.
+both title and abstract), they are counted just one, and field term count features are removed.
+This step generates a list of rules composed by $AND$/$NOT$ "conditions" made of terms/authors/keywords/MESH, which together identify a group of records.
+* For each rule, we add a set of negative conditions ($NOT$ statements in the rule), removing non-relevant records in a group: a condition removing the largest number of non-relevant records is found, and then iteratively, more are added with the same logic, until no conditions are found that would not also remove positive records.
+* The extended set of rules is sorted by the difference between the number of positive and negative records they identify in descending order.
+Given this ordered list, the cumulative number of unique positive records is computed and used to group the rules: each rule in the same group of rules adds the same number of positive records to the preceding group but are ordered according to the number of negative records they identify.
+* These groups of rules are outputted, and the researcher is asked to review them, selecting one or more (useful if they convey radically different meaning) rules from each group, or edit them (in case too specific positive or negative conditions were included).
+By default, the framework suggests keeping the first rule of each group since it would identify the lower number of non-relevant records for the same number of positive one (.e., higher specificity).
+It is possible to exclude a group of rules altogether, especially the last ones with very low positive/negative records ratios.
+* The selected rules are joined together by $OR$ statements, defining a subset of records with a sensibly higher proportion of positive records than the original one.
+* Given this data set, the next step removes redundant rules (i.e., rules whose positive records are already included in more specific ones) and conditions (i.e., conditions that once removed do not decrease the total number of positive or do not increase the negative records).
+* Finally, the rules are re-elaborated in a format usable on the major scientific databases.
+
+It is important to note that this process is entirely data-driven.
+The algorithm is only aware of the "world" defined by the data set, itself generated by a specific search query focused on a particular topic.
+Therefore, the new query may not be specific once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
+We suggest extending the query by adding domain-specific terms linked by an $AND$ statement, separating the original query and the new addendum in two distinct logical blocks by enclosing them in parentheses.
+See the Results for the specific query used in the second session.
+<mark>*not sure whether to put this part here or in the discussion*</mark>
+
+### Hyperparameter search
+The machine learning model behind the algorithm has a number of hyperparameters in addition to the BART specific ones: the number of ensemble models, the source of randomness between models (just derived from MCMC sampling, the default, or whether to bootstrap the data first), the oversampling of positive records, the PrI quantiles, the number of initial manually labelled records.
+These parameters have a relevant effect on the algorithm performance.\
+We set up a grid search to evaluate the parameters on a subset made of the first 1200 records from the first session; these records were fully labelled as relevant or not.
+We run the framework for each combination of parameter values, automatizing the manual review part using the already collected labels.
+The framework ran until four CR iterations with no positive records were returned, or the whole dataset was labelled.\
+For each combination, a performance score was computed as the product of *Efficiency* (number of records that required review over the total) and *Sensitivity* (number of positive records found over the total of positives).
+We then identified homogeneous "performance clusters" of parameter values using a decision tree on the score.
+For the final analysis, we chose the best cluster of parameter value combinations and, inside the cluster, the best combination in order of Sensitivity and Efficiency.
+
+### Performance evaluation
+It is hard to estimate the generalized performance of such a model since the data is not a random sample (the records are presumably the whole population of articles from the searched databases for those search criteria), and since the order of records matters (it drives the choice of the initial labelling set).
+Therefore we postulated that usual random train/test methods to estimate the out-of-sample machine learning performance [@kohavi1995study] would not be representative in this situation.
+Also, common time-series based predictive performance methodologies would reveal inadequate [@tashman2000out] since the expected proportion of positive matches is not constant throughout the data set and is expected to fall fast as the first matches are found.\
+Our solution was to use Bayesian logistic regression to model the label of the manually reviewed records on the lower bound of the [98% PrI] produced by our algorithm.
+For the model we used weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).
+The goal of the model is to estimate the PPD of the missed number of positive matches in the whole data set.
+Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing a plausible worst-case scenario.
+The quality of the model was evaluated through Bayesian $R^2$ [@gelman2019r] of which we reported the posterior median and 90% Credible Interval [90% CrI].\
+The predictive distribution of the number of missed positive records allows to estimate the expected long-run *Sensitivity* and the *Work saved over random* (WSoR) of the algorithm.
+The WSoR is based on a negative hypergeometric model to estimate the number of records to manually label to find the same number of positives if records were evaluated in random order [@chae1993presenting]; the WSoR is then one minus the ratio of the reviewed records over this number.
+For the number of predicted positive records, the sensitivity and WSoR, we reported the truncated 90% PrI [trunc.
+90% PrI], which is the uncertainty interval bounded at the number of observed total positive records: since each positive match is manually verified, the probability of a number of total positive records lower than observed is zero.

### 2021-09-08 Manuscript/Manuscript_Results.Rmd
update table output
and other small things

@@
 output:
-  github_document:
-    html_preview: false
+  pdf_document:
+    includes:
+      in_header: header.tex
+  github_document: default
 ---
@@
 
-including results between 2010 and 2020 (included).
+subsetting results between 2010 and 2020 (included).
 The automatic search tools were used for MEDLINE, WOS and IEEE, while a manual search and importation was necessary for EMBASE and SCOPUS.
@@
 
-`r knitr::kable(search_results, caption = "Table 1.
+`r print_table(search_results, caption = "Table 1.
 Distribution of retrieved records by source and session.
@@
 
-`r knitr::kable(annotation_results, caption = "Table 2.
+`r print_table(annotation_results, caption = "Table 2.
 Results of the automatic classifaction and manual review rounds.
@@
 
-### Hyperparameter selection and performance evaluation
+### Hyperparameter selection
 
@@
 
+### Performance evaluation
+
 To evaluate the theoretical performance of the engine on the full datasets (i.e., session 1 and session 2 data), a Bayesian logistic model was trained on each session dataset to predict the label of the records from the probability estimated by the engine (see methods for details).
@@
 
-`r knitr::kable(perf_table, caption = "Table 3.
+`r print_table(perf_table, caption = "Table 3.
 Estimated performance summary.
-For each session, the number of reviewed records and the percentage over the total provide an idea of the work saved against manually labelling all retrieved records.
-Using a simple logistic model to predict a positive match from the probabilities outputted by the engine, the predictive distribution of the cumulative number of positive matches was computed and used to estimate the sensitivity and the efficiency of the engine for each session.
-Finally the Bayesian R^2 of the logistic models is reported.
-[PrI] represents the 90% Predictive Interval.")`
+The table reports for each session, the number of reviewed records and the percentage over the total.
+Also, the posterior expected number of positive records, *Sensitivity* and *Work saved over random* (WSoR) are reported, with their 90% PrI truncated to a number of positive matches equal to the observed one.
+Finally the median Bayesian R^2 [90% CrI] of the logistic models is reported.
+[PrI] represents the 90% Predictive Interval while [trunc.
+PrI] indicate the residual PrI truncated at the observed realization (see.
+methods).")`
 
-```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 1.
-90% Predictive distribution of the cumulative number of positive matches estimated by the logistic Bayesian models applied to the engine output.
-The distribution is depicted by the shaded area.
-The distribution is cut at the level of the observed cumulative distribution of positive matches (red dots), since there cannot be false positive in the dataset and predicted value below this line are not possible."}
+```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 2.
+Observed cumulative number of positive matches (red dots) sorted by simple query ordering.
+The [trunc.
+90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines).
+The median of the PrI is represented by a darker blue line."}
 

### 2021-09-08 Manuscript/S2.Additional_outputs.Rmd
update table output
and other small things

@@
 output:
+  # pdf_document:
+  #   toc: yes
+  #   includes:
+  #     in_header: header.tex
   github_document:
-    html_preview: false
     toc: yes
@@
 Figure 1 show the mixture of the predictive distribution of the probability of a positive match, grouped by labelling status.
-The posterior samples for each record were extracted and joined in a global distribution; on this distribution, density was computed on the logit scale and then logistic transformed for display on a \[[0 - 1]\] scale.
+The posterior samples for each record were extracted and joined in a global distribution; on this distribution, density was computed on the logit scale and then logistic transformed for display on a $[0 - 1]$ scale.
 The light violet ridges show the distribution of the still unlabelled records.\
@@
 
-`r knitr::kable(var_importance_s1, caption = 'Table 1. Term importance at the end of Session 1')`
+`r print_table(var_importance_s1, caption = 'Table 1. Term importance at the end of Session 1.')`
 
-`r knitr::kable(var_importance_s2, caption = 'Table 2. Term importance at the end of Session 2')`
+`r print_table(var_importance_s2, caption = 'Table 2. Term importance at the end of Session 2.')`
 
@@
 
-`r knitr::kable(grid_out_params, caption = 'Table 3.
+`r print_table(grid_out_params, caption = 'Table 3.
 Hyperparameter clusters and best cluster subsets.

### 2021-09-08 Manuscript/S1.Protocol.Rmd
white space cleaning
added page break after TOC
add reminder to put some more info in S1
add pdf output

@@
 output:
+  pdf_document:
+    toc: yes
   github_document:
@@
 This document will guide the reader along the steps to utilize the framework and reproduce our results.
+
+Add intallation and setup info here
 
@@
 
-The process of predicting labels and manually reviewing them is what defines a "classification and review (CR) iteration".
+The process of predicting labels and manually reviewing them is what defines a "classification-review (CR) iteration".
 

### 2021-09-08 R/Analysis.R
fix: fix minor bug

@@ -448,7 +448,7 @@ analyse_grid_search <- function(session_folder = 'Grid_Search', tot_pos = NULL,
 		best_by_rule = out %>% group_by(Cluster = Rule) %>%
 			slice_max(Score, n = 1, with_ties = T) %>%
 			slice_max(Sensitivity, n = 1, with_ties = T) %>%
-			slice_max(Score, n = 1, with_ties = F) %>%
+			slice_max(Efficiency, n = 1, with_ties = F) %>%
 			# ungroup() %>%
 			# arrange(desc(Score), desc(Sensitivity), desc(Efficiency)) %>%
 			select(Cluster, Iter, Pos_labels, Tot_labeled, Sensitivity, Efficiency,

### 2021-09-08 R/NLP.R
docs: add comment

@@ -138,7 +138,7 @@ tokenize_MESH <- function(mesh) {
 
 text_to_DTM <- function(corpus, min.freq = 20, ids = 1:length(corpus),
 												freq.subset.ids = ids,
-												included.pos = c('Noun', 'Verb', 'Adjective'),
+												included.pos = c('Noun', 'Verb', 'Adjective'), #TODO: add Plural and Noun Phrase
 												tokenize.fun = tokenize_text, add.ngrams = T,
 												aggr.synonyms = T, n.gram.thresh = .5,
 												syn.thresh = .9, label = 'TERM__', na.as.missing = T) {

### 2021-09-08 R/Reporting.R
feat: add function to pretty print tables in pdf
also updated performance table column names

@@ -564,13 +564,13 @@ format_performance <- function(..., session_names = NULL) {
 		elements[[i]] %>% with({
 			tibble(
 				#Session = session_names[i],
-				'Tot. records' = total_records,
-				'N. reviewed records (% over total)' = glue("{n_reviewed} ({percent(n_reviewed/total_records)})"),
-				'Expected efficiency [PrI]' = efficiency %>% format_interval(percent = TRUE),
-				'N. positive matches (% over total)' = glue("{obs_positives} ({percent(obs_positives/total_records)})"),
-				'Predicted positive matches [PrI]' = pred_positives %>% format_interval(),
-				'Expected sensitivity [PrI]' = sensitivity %>% format_interval(percent = TRUE),
-				'Simple Model R^2 [PrI]' = mod_r2 %>% format_interval(percent = TRUE)
+				'Total records' = total_records,
+				'Reviewed records (% over total records)' = glue("{n_reviewed} ({percent(n_reviewed/total_records)})"),
+				'Expected efficiency (over random) [trunc. 90% CrI]' = efficiency %>% format_interval(percent = TRUE),
+				'Observed positive matches (% over total records)' = glue("{obs_positives} ({percent(obs_positives/total_records)})"),
+				'Predicted positive matches [trunc. 90% PrI]' = pred_positives %>% format_interval(),
+				'Expected sensitivity [trunc. 90% PrI]' = sensitivity %>% format_interval(percent = TRUE),
+				'Simple Model $R^2$ [90% PrI]' = mod_r2 %>% format_interval(percent = TRUE)
 		) %>%
 				mutate_all(as.character) %>%
 				tidyr::pivot_longer(everything(), names_to = 'Indicator', values_to = session_names[i]) %>%
@@ -682,4 +682,23 @@ format_var_imp <- function(var_imp, as_data_frame = TRUE) {
 	}
 
 	var_imp
+}
+
+print_table <- function(data, caption = '') {
+	if (knitr::is_latex_output()) {
+		knitr::kable(data, "latex", booktabs = T,
+								 caption = caption %>% str_squish()
+								 #format.args = list(floating = FALSE)
+		) %>%
+			kableExtra::kable_styling(
+				latex_options = c(
+					"striped",
+					if (ncol(data) > 5) "scale_down" else NULL,
+					"hold_position"
+				)
+			)
+	} else {
+		knitr::kable(data, caption = caption)
+	}
+
 }

### 2021-09-08 R/Rule_building.R
clean: minor change

@@ -220,7 +220,7 @@ add_negative_terms <- function(rules, target_vec, target_data) {
 
 		terms$selected_term[1] <- TRUE
 
-		rep <- T
+		rep <- TRUE
 
 		while (rep) {
 

### 2021-09-08 R/Setup.R
feat: add knitr and kableExtra packages

@@ -42,7 +42,8 @@ pkg.require(
 											 "pbmcapply", "rpart", "bartMachine", "tm", "patchwork", "ggplot2", "ggrepel", "RLesur/crrri",
 											 "bakaburg1/tidytrees"),
 	only_install = c('purrr', 'openxlsx', 'tictoc', 'tidyr', 'arm', 'english',
-									 'parallel', 'jsonlite', 'rentrez', 'wosr', 'brms', 'ggridges')
+									 'parallel', 'jsonlite', 'rentrez', 'wosr', 'brms', 'ggridges',
+									 'knitr', 'kableExtra')
 )
 
 

### 2021-09-17 Manuscript/Manuscript_Introduction.Rmd
update

---
title: "Introduction"
date: "`r lubridate::today()`"
bibliography: references.bib
csl: apa.csl
output:
  pdf_document:
    includes:
      in_header: header.tex
  github_document: default
---

## Introduction

Scientific production has experienced a continuous exponential growth in last decades [@larsen2010rate; @bornmann2015growth]. This is especially true for biomedical research, a trend further increased by the COVID19 pandemic, thanks also to a decrease in journals' processing time and to the diffusion of preprint databases' usage [@aviv2021publication; @horbach2020pandemic; @hoy2020rise]. Consequently, it gets harder for researchers and practitioners to stay up-to-date on the latest findings in their field. Secondary research is of paramount relevance in this scenario, providing useful summaries of the state of the art, but is getting ever more demanding in terms of time and human resources [@allen1999estimating; @borah2017analysis; cohen2010evidence; bastian2010seventy].\
The article collection and screening phases of a systematic review are particularly problematic tasks [systematic review tutorial]. The first is the collection of published research possibly relevant to a scientific question through the an appropriately built search queries used with scientific database search engines. The construction of search queries is a particularly delicate tasks [@lefebvre2011searching; @hammerstrom2010searching], requiring both domain and some knowledge of the databases' query languages; the goal is to produce a set of results containing all relevant articles (high sensitivity) and as few non-relevant ones as possible (high specificity), focusing on the first aspect at the cost of the second [@hammerstrom2010searching]. Furthermore, often manual work is required to download, store and organize the publication data. This aspect may be complicated by limits in the number of records that can be downloaded at once [], and by the necessity to harmonize different formats and resolve duplication. The screening phase consists of classifying the collected publications as relevant or not for the topic of interest [@bannach2019machine]. It is usually the more resource demanding task of a systematic review; even with appropriately built search queries, the returned results easily range in the tens of thousands of which just a small fraction is actually relevant [@lefebvre2011searching]. It was estimated that labelling 10 000 publications may take as much as 40 weeks of work, while the average clinical systematic review takes 63 weeks to be completed [@bannach2019machine; @borah2017analysis; @allen1999estimating].\
The field of Data Science applied to evidence synthesis and acquisition has since years reached maturation [@marshall2015systematic; @beller2018making]. Through the application of natural language processing (NLP) it is possible to transform free text into quantitative features, with various level of abstraction and generalization [@ananiadou2006text; @cohen2008getting]; with machine learning, such text-derived data can be used to map and reproduce human judgment to automatize the screening given an initial human labeled set [@ikonomakis2005text].\
The field of automatization of systematic reviews has been ripe of improvements in the last years [@ananiadou2009supporting; @o2015using; @tsafnat2013automation], and it is possible to foresee that such techniques will become a standard approach [@beller2018making]. Some example...
Despite the great advances, each method has a various shortcoming, both in usability and efficiency [@o2015using].
We tried to addresses some of these limitations creating an integrated framework which tries to simplify systematic reviews in innovative ways: our framework provides solutions for automatic publication collection from multiple online sources and management, and a Bayesian, active machine learning based tool to support humans in the screening task, exponentially reducing the number of records to review. Finally, we propose an experimental method to semi-automatically generate efficient search queries given an already labelled set of publications.\
We apply this solution in the production of a systematic review evaluating the mathematical modeling of patient referral networks among hospitals and its impact on the diffusion of healthcare-associated pathogenic microrganisms with a focus on antimicrobial resistant strains. The systematic review protocol is published in [].

### 2021-09-17 Manuscript/Manuscript_Methods.Rmd
update

@@
 output:
-  # pdf_document:
-  #   includes:
-  #     in_header: header.tex
+  pdf_document:
+    includes:
+      in_header: header.tex
   github_document: default
@@
 The automatic classification task and the manual review step form an iterative loop (CR iterations).
-The whole algorithm falls in the pattern defined as active machine learning [@settles2009active], with the machine querying the user to address and progressively resolve uncertainty in the classification.\
+The whole algorithm falls in the pattern defined as active machine learning [@settles2009active, miwa2014reducing], with the machine querying the user to address and progressively resolve uncertainty in the classification.\
 The CR iterations continue until no new positive matches are found in four consecutive iterations.
@@
 The framework ran until four CR iterations with no positive records were returned, or the whole dataset was labelled.\
-For each combination, a performance score was computed as the product of *Efficiency* (number of records that required review over the total) and *Sensitivity* (number of positive records found over the total of positives).
+For each combination, a performance score was computed as the product of *Efficiency* (1 minus the number of records that required review over the total) and *Sensitivity* (number of positive records found over the total of positives).
 We then identified homogeneous "performance clusters" of parameter values using a decision tree on the score.

### 2021-09-17 Manuscript/Manuscript_Results.Rmd
update

@@
 
-Figure 1 shows the actual and predicted (from the logistic model) cumulative number of positive matches, ordered by the initial simple ordering query.
+Figure 2 shows the actual and predicted (from the logistic model) cumulative number of positive matches, ordered by the initial simple ordering query.
 As confirmed by the high efficiency values reported in Table 3, it is striking how many more records would need to be evaluated manually to find all positive matches without using a smart search tool.

### 2021-09-17 Manuscript/Manuscript_Methods.Rmd
better explanation of simple ordering

@@
 A short guide on how to set up the framework for each supported database is available in Supplemental Material S3.\
-Once the records are downloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources, ordering the records by simple query term frequency ("simple ordering"), putting the most likely relevant records on top.
-The output is an "Annotation file".\
+Once the records are downloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources.
+The records are ordered according to the frequency of the positive terms (e.g., not preceded by a $NOT$ modifier) of the query appear in the title and abstract ("simple ordering"); this approach is a modification of @wallace2010active.
+The final output is an "Annotation file" with all the record's info and its label when present´.\
 
@@
 The automatic classification task and the manual review step form an iterative loop (CR iterations).
-The whole algorithm falls in the pattern defined as active machine learning [@settles2009active, miwa2014reducing], with the machine querying the user to address and progressively resolve uncertainty in the classification.\
+The whole algorithm falls in the pattern defined as active machine learning [@settles2009active, @miwa2014reducing], with the machine querying the user to address and progressively resolve uncertainty in the classification.\
 The CR iterations continue until no new positive matches are found in four consecutive iterations.

### 2021-09-21 Manuscript/Manuscript_Introduction.Rmd
update

@@
 
-Scientific production has experienced a continuous exponential growth in last decades [@larsen2010rate; @bornmann2015growth].
-This is especially true for biomedical research, a trend further increased by the COVID19 pandemic, thanks also to a decrease in journals' processing time and to the diffusion of preprint databases' usage [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].
+Scientific production has experienced continuous exponential growth in the last decades [@larsen2010rate; @bornmann2015growth].
+This is especially true for biomedical research, a trend further increased by the COVID19 pandemic, thanks to decreased journals' processing time and the diffusion of preprint databases' usage [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].
 Consequently, it gets harder for researchers and practitioners to stay up-to-date on the latest findings in their field.
-Secondary research is of paramount relevance in this scenario, providing useful summaries of the state of the art, but is getting ever more demanding in terms of time and human resources [@allen1999estimating; @borah2017analysis; cohen2010evidence; bastian2010seventy].\
+Secondary research is of paramount relevance in this scenario, providing valuable summaries of the state of the art, but is getting ever more demanding in terms of time and human resources [@allen1999estimating; @borah2017analysis; @cohen2010evidence; @bastian2010seventy].\
 The article collection and screening phases of a systematic review are particularly problematic tasks [systematic review tutorial].
-The first is the collection of published research possibly relevant to a scientific question through the an appropriately built search queries used with scientific database search engines.
-The construction of search queries is a particularly delicate tasks [@lefebvre2011searching; @hammerstrom2010searching], requiring both domain and some knowledge of the databases' query languages; the goal is to produce a set of results containing all relevant articles (high sensitivity) and as few non-relevant ones as possible (high specificity), focusing on the first aspect at the cost of the second [@hammerstrom2010searching].
-Furthermore, often manual work is required to download, store and organize the publication data.
-This aspect may be complicated by limits in the number of records that can be downloaded at once [], and by the necessity to harmonize different formats and resolve duplication.
-The screening phase consists of classifying the collected publications as relevant or not for the topic of interest [@bannach2019machine].
-It is usually the more resource demanding task of a systematic review; even with appropriately built search queries, the returned results easily range in the tens of thousands of which just a small fraction is actually relevant [@lefebvre2011searching].
-It was estimated that labelling 10 000 publications may take as much as 40 weeks of work, while the average clinical systematic review takes 63 weeks to be completed [@bannach2019machine; @borah2017analysis; @allen1999estimating].\
-The field of Data Science applied to evidence synthesis and acquisition has since years reached maturation [@marshall2015systematic; @beller2018making].
-Through the application of natural language processing (NLP) it is possible to transform free text into quantitative features, with various level of abstraction and generalization [@ananiadou2006text; @cohen2008getting]; with machine learning, such text-derived data can be used to map and reproduce human judgment to automatize the screening given an initial human labeled set [@ikonomakis2005text].\
-The field of automatization of systematic reviews has been ripe of improvements in the last years [@ananiadou2009supporting; @o2015using; @tsafnat2013automation], and it is possible to foresee that such techniques will become a standard approach [@beller2018making].
-Some example...
-Despite the great advances, each method has a various shortcoming, both in usability and efficiency [@o2015using].
-We tried to addresses some of these limitations creating an integrated framework which tries to simplify systematic reviews in innovative ways: our framework provides solutions for automatic publication collection from multiple online sources and management, and a Bayesian, active machine learning based tool to support humans in the screening task, exponentially reducing the number of records to review.
+First, relevant published research needs to be collected from scientific databases through appropriately built search queries.
+The construction of search queries is a particularly delicate task [@lefebvre2011searching; @hammerstrom2010searching], requiring both domain and some knowledge of the databases' query languages; the goal is to produce a set of results containing all relevant articles (high sensitivity) while keeping the total number low (high specificity), focusing on the first aspect at the cost of the second [@hammerstrom2010searching].
+If an integrated search tool is not used, manual work is required to download, store and organize the publication data.
+Searching manually may be complicated by limits in the number of records that can be downloaded at once [] and the necessity to harmonize different formats and resolve duplication.
+The citation screening phase consists of classifying the collected publications as relevant or not for the topic of interest [@bannach2019machine].
+It is usually the more resource-demanding task of a systematic review: even with appropriately built search queries, the returned results easily range in the tens of thousands of which just a small fraction is actually relevant [@lefebvre2011searching].
+It was estimated that labelling 10 000 publications may take as much as 40 weeks of work, while the average clinical systematic review takes 63 weeks to be completed [@bannach2019machine; @borah2017analysis; @allen1999estimating].
+A consequence is that often systematic reviews are already outdated once they are published [@beller2013systematic].\
+The field of Data Science applied to evidence synthesis and acquisition has greatly maturated in the last years [@marshall2015systematic; @beller2018making; @tsafnat2014systematic].
+Through the application of natural language processing (NLP), it is possible to transform free text into quantitative features, with various levels of abstraction and generalization [@ananiadou2006text; @cohen2008getting]; with machine learning (ML), such text-derived data can be used to map and reproduce human judgment and automatize the citation screening [@ikonomakis2005text].
+One of the most successful approaches to text screening is active ML: researchers review the predictions made by the ML algorithm, focusing on the most uncertain predictions ("uncertainty" based active ML)  or on those giving a document a higher probability of being relevant ("certainty" based active ML) [@miwa2014reducing].\
+The automatization of systematic reviews has been ripe with improvements in the last years, and it is possible to foresee that such techniques will become a standard approach [@beller2018making].
+See @ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating for in-depth evaluations of research in this field.
+Many of these studies have generated a set of user-friendly commercial and free-to-use tools [see @marshall2015systematic, table 1].
+Despite the significant advances, each method has various shortcomings, both in usability and efficiency [@o2015using].
+We tried to address some of these limitations by creating an integrated framework that tries to simplify systematic reviews in innovative ways: our framework provides solutions for automatic citation collection and management from multiple online sources and a Bayesian, active machine learning-based tool to support humans in the screening task, exponentially reducing the number of records to review.
+In particular, we exploit the characteristics of Bayesian analysis to overcome the shortcoming of both "certainty" and "uncertainty" based active learning and the difficulties in defining stopping rules [@miwa2014reducing].
 Finally, we propose an experimental method to semi-automatically generate efficient search queries given an already labelled set of publications.\
-We apply this solution in the production of a systematic review evaluating the mathematical modeling of patient referral networks among hospitals and its impact on the diffusion of healthcare-associated pathogenic microrganisms with a focus on antimicrobial resistant strains.
+We apply this solution in the production of a systematic review evaluating the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms with a focus on antimicrobial-resistant strains.
 The systematic review protocol is published in [].

### 2021-09-21 Manuscript/Manuscript_Methods.Rmd
update

@@
 The framework models the relevance of a record based on the following fields: title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
-A series of Natural Language Processing (NLP) techniques <mark>(*should I put a general reference?*)</mark>) are employed to transform the textual information in these fields into features for machine learning.
+A series of Natural Language Processing (NLP) techniques [@marshall2015systematic; @ananiadou2006text] are employed to transform the textual information in these fields into features for machine learning, through a bag-of-words approach [@marshall2015systematic].
 The processing of free text fields includes tokenization (i.e., extracting the terms), common stopwords (i.e.
@@
 An ensemble of ten models was fitted to improve prediction stability by averaging the predictions between models.\
-To choose how to label a record, we exploit the uncertainty typical of Bayesian estimates to decide a record label and whether it requires manual evaluation.
+To choose how to label a record, we exploit the uncertainty typical of Bayesian estimates to decide a record label and whether it requires manual evaluation, an approach joining the "uncertainty" and "certainty" selection criteria of previous work in the field [@miwa2014reducing].
 To describe the process formally, we define

### 2021-10-05 Manuscript/Manuscript_Discussion.Rmd
Discussion draft

---
title: "Discussion"
date: "`r lubridate::today()`"
bibliography: references.bib
csl: apa.csl
output:
  pdf_document:
    includes:
      in_header: header.tex
  github_document: default
---

## Discussion

We propose a new integrated framework to help researcher collect and screen research publications characterized by high performance and versatility, joining the growing field of systematic review automatization (SRA) and helpers (SRH) tools.\
The International Collaboration for the Automation of Systematic Reviews (ICASR) proposes a number of features tools for automatic research synthesis should possess, defining the so called Vienna Principles [@beller2018making]. We tried to adopt some of the concepts advocated by the ICAS; for example we are sharing the tool as an open source R package, and we tried to follow the paradigms of modular programming [@mccracken2003modular], building separated components communicating through intermediate outputs stored in common formats (Comma Separated Values/Microsoft Excel™), which make it possible for users to extend the framework or integrate it with other tools in their pipeline.\
Our framework has two main components, an integrated query-based citation search and management engine and an active machine learning record screener\

Our search engine is capable of automatically collecting citation data from three well known scientific databases, that is, Pubmed, Web of Science and the database of the Institute of Electrical and Electronics Engineers, implementing also institutional access rights; in addition, it can process manually downloaded results from all mentioned databases plus records from the SCOPUS and EMBASE databases. Once the citations are downloaded, they are translated in a uniform format and deduplicated. The online search algorithm is efficient enough to manage tens of thousands of search results, using various expedients to overcome the online databases limitations in terms of traffic and download quota. Most SRH tools we are aware of, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/), often focused on a particular topic [@visser2010performing] or relying on only one external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia]. To our knowledge, our tool is the first capable to fully automatize searching on three different well known scientific databases and to import raw data from five of them. Mixing different database is fundamental to have a more complete view of the literature on a topic [@bajpai2011search; @wilkins2005embase; @woods1998medline]: in our results, 18.7% of the positive matches were unique for one of the different data sources and no positive record was present among all of them (data not shown).\

Modern NLP techniques were used to transform textual data into actionable numeric inputs [@ananiadou2006text; @cohen2008getting]. One particular improvement was to use network analysis to identify associated terms, which we labelled as non-consecutive ngrams, which confer particular meaning when present together into a text while not necessary being close to each other. A similar network approach was used to merge redundant terms, in order to make model estimation more efficient and reduce possible noise. The use of network inspired modeling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text] and is a valuable tool to extract semantic information not evident in one-word of consecutive ngram models.

The citation screening functionality of the framework implements active machine learning based document classification, adopting best practices and bringing further improvements at various levels. At the base of our classification algorithm we use BART [@chipman2010bart; @kapelner2013bartmachine], a Bayesian machine learning technique characterized by exceptional predictive performance and speed even in large dataset. This model builds consecutive decision trees associating the presence/absence of set of terms to the probability of a positive match, each tree trying to decrease the prediction error of the precedent one [@hastie2009boosting]. The Bayesian approach explore distributions of trees which are justified by the data, while using a set of prior distributions to avoid overfitting by discouraging excessively deep trees, long sequences of trees, or extreme predicted probabilities. To further improve generalizability we ran multiple replications of the model and then averaged their record predictive distributions; this technique is called ensembling and it has been shown to improve out-of-sample predictive performance []. In a Bayesian setting, this effect comes from a reduction of the probability mass in the tails of the predictive distributions while not shifting their locations (i.e., it decreases variance without impacting bias) [bias/variance tradeoff, better if in Bayesian analysis and/or focusing to ensemble]. Instead, imposing stronger general priors against extreme predictions would decreased variance but also shifted the distribution mass towards a non-decision zone, therefore increasing bias. In our data it can be seen how using more then one model replica greatly improved sensitivity and efficiency, with a performance stabilization after 10 replicas (Suppl. Mat. S2); since the number of model replicas greatly impacted computation times we decided to use ten replicas since it was also associated with the higher sensitivity in the same performance cluster. The variability between models derives only from the randomness in the MCMC fitting phase []; an alternative was to impose additional variability by bootstrapping [] but this approach actually decreased performance (Suppl. Mat. S2), probably due to the low proportion of positive matches in the data and the loss of information with bootstrapping in unbalanced classification tasks [].\
The strong imbalance between relevant and non-relevant records [@sampson2011precision] can affect sensitivity []. To overcome the problem, we oversampled the positive records ten times before model fitting. Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance. An alternative approach would be record weighting to change error costs during estimation [] but the BART implementation we used did not allow observation weighting and using simple oversampling allows to use different modeling engines. Also, the simple query ordering of the record during the creation of the initial training set allowed to have a far higher prevalence of relevant records (17.2%) compared to the overall one (0.11%) and this boosts the overall sensitivity of the model. A known risk with oversampling of the target class is the missclassification of negative records as positive [], but since in our approach all predicted positive are manually reviewed we are ensured to achieve always 100% specificity/positive predictive value.\
One of the innovation in our approach is the overcoming of simple stopping rules in SRA classification tasks []. Static supervised learning models requires to manually label a certain amount of records (i.e., the training set) which are then used to train the algorithm and classify the rest (the test set) [], but this method requires to decide the size of the training set in advance. Active learning tries to alleviate the problem by splitting the classification task in an iterative process in which prediction and review phases alternate, but even in this case, one has to define a stopping rule regarding how many records to screen manually in every iteration []. By exploiting the Bayesian nature of BART we produce a distribution of probabilities and not a single value for each record; by joining these distribution in the positive and negative record groups it's possible to identify a "uncertainty zone" so that all record whose predictive distribution crosses this zone needs manual verification. Therefore the researcher will have a defined number or records to check at every iteration which dynamically decreases as uncertain predictions are reviewed and the uncertainty shrinks (Suppl. Mat. S2 Fig. 1). In this model, researcher do not need to choose a priori the number of records to review but just the size of the uncertainty zone (by setting the PPD quantiles used to built it) and after how many iterations with no new positive matches to stop; both the parameters are more theoretical and general than a simple stopping rule and nevertheless the hyperparameter tuning did not indicate a big impact of these parameters. Since our approach requires researchers to review both unlabelled records with a positive predicted label and those with a PPD inside the uncertainty zone, it can be considered as a unifying syinthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

To evaluate performance we avoided the classic random out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study] because we deemed them not realistic in this setting. It is assumed that the corpus to be screened is not a random sample, but the entire population of citation for a given query; a random validation would be useful to estimate the performance of this method on a new dataset derived by the same data-generating process, but this is a totally theoretical goal with no usefulness since all the existing data related was alread acquired. Instead a more relevant question is to estimate the long run sensitivity of our prediction method in finding all relevant records in the whole data set. Since the records are ordered, again a random approach would not work since it assumes that the prevalence of positive records is equal on average in every possible sample [@tashman2000out], while instead it drops as more records are considered (Fig. 2). We instead used a Bayesian model to estimate the likelihood of a positive match given the prediction scores of the BART model. This approach showed to fit the data very well (high $R^2$) and the Bayesian predictive distribution can be exploited to draw a worse case scenario given the data.\
In our study our approach reached 98.8% sensitivity during the hyperparameter optimization (deterministic, small sample ) and on the whole data set we predicted a theoretical sensitivity of 100% [93.5%, 100%] in the first session and of 97.3% [73.8%, 100%] in the second, a lower value as is expected by the probabilistic accumulation of random events; both results are above the usual results in the field [@o2015using] and in line with the 92% average sensitivity estimated after human only screening [@edwards2002identification]. In one interesting case, the model spotted a missclassification during initial labeling, demonstrating its robustness and its value also as a second screener, as already suggested by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].\
Also we showed that such sensitivity was achieved screening just 1.34% of all downloaded records, a sensible reduction in workload; finally, albeit the simple query based ordering did concentrate most of the relevant matches in the first 20-25 thousands records, some relevant records would have required almost the full data set to be manually checked to be found.\
The model takes ~5-20 minutes per iteration to perform predictions in session 1 (17755 documents) and 20-40 minutes in session 2 (98371 documents) on a 8 core, 2.5 GhZ, 16 GB RAM laptop from 2014 and that equate to 1-3 days per session to manually review and perform predictions, for a total of 1-2 weeks for the whole process, a huge saving of time compared to the months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating]. To our knowledge, our data sets are larger than what common in most SRA studies [@o2015using; @olorisade2016critical], emphasizing the reliability of the tool in real world scenarios.\

The last component of our framework is a data-driven query generation algorithm. The creation of an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximize the number of relevant search results while minimizing the total number of results. We propose a solution based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the posterior predicted probabilities; the technique tries to extract high sensitivity subqueries from the labeled data, enrich them with negative terms to increase specificity [@abdelmgeid2008using] and then let researcher evaluate them and pick the most meaningful ones. The framework will then join them and remove redundancies. The aim is to generate a second query that complement the first human made one and help find possible missing records not found during the first session.\
The generated query allowed to retrieve few more positive matches not found in session 1 at the cost of a large increase in the amount of documents. One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules internalized by the classification model, showing which combination of terms was particularly relevant and even spotting authors and locations associated to the topic of study. The generated query therefore acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to spot bias in black box classification algorithms [@malhi2020explainable] and that is increasingly legally required for high-stack machine learning applications [@bibal2021legal; @bibal2020impact].\^
It is important to note that this process is entirely data-driven. The algorithm is only aware of the "world" defined by the data set, itself generated by a specific search query focused on a particular topic. Therefore, the new query may not be specific once applied to an unbounded search domain, returning an unmanageable amount of unrelated results. The solution we found was to add another component specifying the general topic (antimicrobial resistance and healthcare associated infections) of our research.\

As reported, our framwork builds on modularity. We designed it in order to easily implement complete independency of the main modules in future iterations; especially, we plan to allow users create their custom made components in addition or in place of the original ones, further expanding its functionalities. In our view it would be possible to easily add custom citation search and parsing functions for other scientific databases, alternative text features building algorithms and alternative machine learning modules.\
We deem such interoperability extremely relevant, because the main strength of our tool is the composition of many solutions and the general approach related to Bayesian active machine learning, but each of its components could benefit greatly from the recent improvements in text mining.\
For example, our text feature generation approach is based on the boolean bag-of-words paradigm, and surely it could be improved by more nuanced text representations: it could be evaluated if feature transformations like Tf-Idf [@baeza1999modern; @ananiadou2006text], would be advantageous, even if we hypothesize that tree based classification algorithms like BART are robust enough to not need such operation. Word embedding could be considered, which transform terms in semantic vectors based on the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep], and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context; another option would be to use unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis, etc., [@pavlinek2017text; @chen2016short; @landauer1998introduction] to extract topics to enrich the feature space.\
Our classification algorithm can be implemented with any Bayesian supervised machine learning method which produces full PPDs; therefore alternative models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian]. Even more interesting would be to test  advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher level features in the text like term context and sequences, long distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\

### 2021-10-05 Manuscript/Manuscript_Discussion_TD.Rmd
Discussion draft

---
title: "Discussion"
date: "`r lubridate::today()`"
bibliography: references.bib
csl: apa.csl
output:
  pdf_document:
    includes:
      in_header: header.tex
  github_document: default
---

## Discussion

We propose a new integrated framework to help researcher collect and screen scientific publications characterized by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools. By sharing the tool as an open source R package and following a modular design of the tool, we tried to adopt some of the so called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making]. Our tool thus consists of three main components: 1) an integrated query-based citation search and management engine, 2) an active machine learning based citation screener, and 3) a data-driven query generation algorithm.\

The framework's search engine module is capable of automatically collecting citation data from three well known scientific databases (i.e. Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases. The online search algorithm is efficient enough to manage tens of thousands of search results, using various expedients to overcome the online databases limitations in terms of traffic and download quota.\

Most SRH tools we are aware of, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) that focus on a particular topic [@visser2010performing] or rely on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia]. To our knowledge, our tool is the first capable to fully automatize searching on three different well known scientific databases and to import raw data from five of them. Mixing different database is fundamental to have a more complete view of the literature on a topic [@bajpai2011search; @wilkins2005embase; @woods1998medline]: in our results, 18.7% of the positive matches were unique for one of the different data sources and no positive record was present among all of them (data not shown).\

We improved the transformation of textual data into actionable numeric inputs [@ananiadou2006text; @cohen2008getting] by using network analysis to identify associated terms, labelled as non-consecutive ngrams, conferring particular meaning when present together into a text while not necessary being close to each other. A similar network approach was used to merge redundant terms, in order to make model estimation more efficient and reduce possible noise. The use of network inspired modeling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text] and is a valuable tool to extract semantic information not evident in one-word of consecutive ngram models.\

The framework's record screening module implements active machine learning based classification, bringing improvements at various levels. At the base of our classification algorithm we use BART [@chipman2010bart; @kapelner2013bartmachine], a Bayesian machine learning technique characterized by exceptional predictive performance and speed even in large dataset. This Bayesian approach explores distributions of decision trees which are justified by the data [@hastie2009boosting], while using a set of prior distributions to avoid overfitting by discouraging excessively deep trees, long sequences of trees, or extreme predicted probabilities.\

To further improve generalizability we ran multiple replications of the model and averaged their record predictive distributions; this technique, known as ensembling, has been shown to improve out-of-sample predictive performance []. In a Bayesian setting, this effect comes from a reduction of the probability mass in the tails of the predictive distributions while not shifting their locations (i.e., it decreases variance without impacting bias). Instead, imposing stronger general priors against extreme predictions would decreased variance but also shifted the distribution mass towards a non-decision zone, therefore increasing bias.\

Using more then one model replica greatly improved sensitivity and efficiency, with a performance stabilization after 10 replications (Suppl. Mat. S2); since the number of model replications greatly impacted computation times we decided to use ten replicas since it was also associated with the higher sensitivity in the same performance cluster. The variability between models derives only from the randomness in the MCMC fitting phase []; an alternative was to impose additional variability by bootstrapping [] but this approach decreased performance (Suppl. Mat. S2), probably due to the low proportion of positive matches in the data and the loss of information with bootstrapping in unbalanced classification tasks [].\

Given that our framework can (automatically) collect a vast amount of records, most records will be non-relevant (labelled negative). This strong imbalance between positive and negative records [@sampson2011precision] can affect sensitivity []. To overcome the problem, we oversampled the positive records ten times before model fitting. Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance. A known risk with oversampling of the target class is the missclassification of negative records as positive [], but since in our approach all predicted positive are manually reviewed we are ensured to achieve always 100% specificity/positive predictive value. An alternative approach would be record weighting to change error costs during estimation [] but the BART implementation we used did not allow observation weighting and using simple oversampling allows to use different modeling engines. Furthermore, the simple query ordering of the record during the record collection allowed for a far higher prevalence of relevant records in the initial training set (17.2%) compared to the overall one (0.11%) and this boosts the overall sensitivity of the model.\

At every iteration the researcher is asked to manually review a number or records, defined by the size of the uncertainty zone, which is dynamically shrinking (Suppl. Mat. S2 Fig. 1). This uncertainty zone is identified by joining the distribution of probabilities produced by exploiting the Bayesian nature of BART for both the positive and negative record groups. The researcher therefore doesn't need to choose a priori the number of records to review but just the size of the uncertainty zone (by setting the PPD quantiles used to built it) and after how many iterations with no new positive matches to stop. This is where our approach offers a major innovation in overcoming of simple stopping rules in SRA classification tasks []. Since our approach requires researchers to review both unlabelled records with a positive predicted label and those with a PPD inside the uncertainty zone, it can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

To evaluate performance we avoided the classic random out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study] because we deemed them not realistic in this setting. It is instead more relevant to estimate the long run sensitivity of our prediction method in finding all relevant records in the whole data set. Since the records are ordered, again a random approach would not work since it assumes that the prevalence of positive records is equal on average in every possible sample [@tashman2000out], while instead it drops as more records are considered (Fig. 2). We instead used a Bayesian model to estimate the likelihood of a positive match given the prediction scores of the BART model. This approach showed to fit the data very well (high $R^2$) and the Bayesian predictive distribution can be exploited to draw a worse case scenario given the data.\

Our framework achieved a very high sensitivity screening just 1.34% of all downloaded records, a sensible reduction in workload. The approach reached 98.8% sensitivity during the hyperparameter optimization (deterministic, small sample) and on the whole data set we predicted a theoretical sensitivity of 100% [93.5%, 100%] in the first session and of 97.3% [73.8%, 100%] in the second, a lower value as is expected by the probabilistic accumulation of random events. Both results are above the usual results in the field [@o2015using] and in line with the 92% average sensitivity estimated after human only screening [@edwards2002identification]. In one interesting case, the model spotted a misclassification during initial labeling, demonstrating its robustness and its value also as a second screener, as already suggested by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards]. Finally, albeit the simple query based ordering did concentrate most of the relevant matches in the first 20-25 thousands records, some relevant records would have required almost the full data set to be manually checked to be found.\

The model takes ~5-20 minutes per iteration to perform predictions in session 1 (17755 documents) and 20-40 minutes in session 2 (98371 documents) on a 8 core, 2.5 GhZ, 16 GB RAM laptop from 2014 and that equate to 1-3 days per session to manually review and perform predictions, for a total of 1-2 weeks for the whole process, a huge saving of time compared to the months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating]. To our knowledge, our data sets are larger than what common in most SRA studies [@o2015using; @olorisade2016critical], emphasizing the reliability of the tool in real world scenarios.\

The last module of our framework is a data-driven query generation algorithm. The creation of an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximize the number of relevant search results while minimizing the total number of results. We propose a solution based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the posterior predicted probabilities; the technique tries to extract high sensitivity subqueries from the labeled data, enrich them with negative terms to increase specificity [@abdelmgeid2008using] and then let researcher evaluate them and pick the most meaningful ones. The framework will then join them and remove redundancies. The aim is to generate a second query that complement the first human made one and help find possible missing records not found during the first session.\

The generated query allowed to retrieve few more positive matches not found in session 1 at the cost of a large increase in the amount of documents. One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules internalized by the classification model, showing which combination of terms was particularly relevant and even spotting authors and locations associated to the topic of study. The generated query therefore acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to spot bias in black box classification algorithms [@malhi2020explainable] and that is increasingly legally required for high-stack machine learning applications [@bibal2021legal; @bibal2020impact].\

It is important to note that this process is entirely data-driven. The algorithm is only aware of the "world" defined by the data set, itself generated by a specific search query focused on a particular topic. Therefore, the new query may not be specific once applied to an unbounded search domain, returning an unmanageable amount of unrelated results. The solution we found was to add another component specifying the general topic (antimicrobial resistance and healthcare associated infections) of our research.\

As reported, our framework builds on modularity. We designed it in order to easily implement complete independency of the main modules in future iterations. In our view it would be possible to easily add custom citation search and parsing functions for other scientific databases, alternative text features building algorithms and alternative machine learning modules. We deem such interoperability extremely relevant, because the main strength of our tool is the composition of many solutions and the general approach related to Bayesian active machine learning, but each of its components could benefit greatly from the recent improvements in text mining. For example, our text feature generation approach is based on the boolean bag-of-words paradigm, and surely it could be improved by more nuanced text representations: it could be evaluated if feature transformations like Tf-Idf [@baeza1999modern; @ananiadou2006text], would be advantageous, even if we hypothesize that tree based classification algorithms like BART are robust enough to not need such operation. Word embedding could be considered, which transform terms in semantic vectors based on the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep], and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context; another option would be to use unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis, etc., [@pavlinek2017text; @chen2016short; @landauer1998introduction] to extract topics to enrich the feature space.\

Our classification algorithm can be implemented with any Bayesian supervised machine learning method which produces full PPDs; therefore alternative models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian]. Even more interesting would be to test  advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher level features in the text like term context and sequences, long distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\

### 2021-10-05 Manuscript/Manuscript_Introduction.Rmd
small edits and added references

@@
 Secondary research is of paramount relevance in this scenario, providing valuable summaries of the state of the art, but is getting ever more demanding in terms of time and human resources [@allen1999estimating; @borah2017analysis; @cohen2010evidence; @bastian2010seventy].\
-The article collection and screening phases of a systematic review are particularly problematic tasks [systematic review tutorial].
-First, relevant published research needs to be collected from scientific databases through appropriately built search queries.
+The article collection and screening phases of a systematic review are particularly problematic tasks [@babar2009systematic].
+First, relevant published research needs to be collected from scientific databases through appropriately built search queries (retrieval phase) [@bannach2019machine; @tsafnat2014systematic; @higgins2019cochrane].
 The construction of search queries is a particularly delicate task [@lefebvre2011searching; @hammerstrom2010searching], requiring both domain and some knowledge of the databases' query languages; the goal is to produce a set of results containing all relevant articles (high sensitivity) while keeping the total number low (high specificity), focusing on the first aspect at the cost of the second [@hammerstrom2010searching].
@@
 Searching manually may be complicated by limits in the number of records that can be downloaded at once [] and the necessity to harmonize different formats and resolve duplication.
-The citation screening phase consists of classifying the collected publications as relevant or not for the topic of interest [@bannach2019machine].
+The citation screening phase consists of classifying the collected publications as relevant or not for the topic of interest (appraisal phase) [@bannach2019machine; @tsafnat2014systematic; @higgins2019cochrane].
 It is usually the more resource-demanding task of a systematic review: even with appropriately built search queries, the returned results easily range in the tens of thousands of which just a small fraction is actually relevant [@lefebvre2011searching].
@@
 We apply this solution in the production of a systematic review evaluating the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms with a focus on antimicrobial-resistant strains.
-The systematic review protocol is published in [].
+The systematic review protocol is published in [@newis].

### 2021-10-05 Manuscript/Manuscript_Methods.Rmd
various edits

@@
 
-A first initial set of manually labelled records is needed to start the automatic classification. We suggest manually label the first 250 records (see "hyperparameter optimization" later).\
+An initial training set of manually labelled records is needed to start the automatic classification. We suggest manually label the first 250 records (see "hyperparameter optimization" later).\
 
@@
 The framework models the relevance of a record based on the following fields: title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
-A series of Natural Language Processing (NLP) techniques [@marshall2015systematic; @ananiadou2006text] are employed to transform the textual information in these fields into features for machine learning, through a bag-of-words approach [@marshall2015systematic].
+A series of Natural Language Processing (NLP) techniques [@baeza1999modern; @marshall2015systematic; @ananiadou2006text] are employed to transform the textual information in these fields into features for machine learning, through a bag-of-words approach [@marshall2015systematic].
 The processing of free text fields includes tokenization (i.e., extracting the terms), common stopwords (i.e.
@@
 
-$$\pi_i = \frac{1}{M}\sum_mPr(L_i = \text{pos}|DTM,model_m)$$
+$$\pi_i = \frac{1}{M}\sum_{j=1}^MPr(L_i = \text{pos}|DTM,m_j)$$
 
-as the PPD of a record $D_i$ being assigned a positive label ($L_i$), averaging the PPDs of the ensemble of $M=10$ models, and
+as the PPD of a record $D_i$ being assigned a positive label ($L_i$), averaging the PPDs of the ensemble of $M=10$ models $m$, and
 
@@
 * Finally, the rules are re-elaborated in a format usable on the major scientific databases.
-
-It is important to note that this process is entirely data-driven.
-The algorithm is only aware of the "world" defined by the data set, itself generated by a specific search query focused on a particular topic.
-Therefore, the new query may not be specific once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
-We suggest extending the query by adding domain-specific terms linked by an $AND$ statement, separating the original query and the new addendum in two distinct logical blocks by enclosing them in parentheses.
-See the Results for the specific query used in the second session.
-<mark>*not sure whether to put this part here or in the discussion*</mark>
+Since the algorithm is data-driven and creates rules that are specific for the dataset but may be not once applied to comprehensive research databases, we added a new subquery in $AND$ specifying the general topics of our search.
 
@@
 The framework ran until four CR iterations with no positive records were returned, or the whole dataset was labelled.\
-For each combination, a performance score was computed as the product of *Efficiency* (1 minus the number of records that required review over the total) and *Sensitivity* (number of positive records found over the total of positives).
+For each combination, a performance score was computed as the product of *Efficiency* (1 minus the ratio of records that required review over the total) and *Sensitivity* (number of positive records found over the total of positives).
 We then identified homogeneous "performance clusters" of parameter values using a decision tree on the score.
@@
 ### Performance evaluation
-It is hard to estimate the generalized performance of such a model since the data is not a random sample (the records are presumably the whole population of articles from the searched databases for those search criteria), and since the order of records matters (it drives the choice of the initial labelling set).
-Therefore we postulated that usual random train/test methods to estimate the out-of-sample machine learning performance [@kohavi1995study] would not be representative in this situation.
-Also, common time-series based predictive performance methodologies would reveal inadequate [@tashman2000out] since the expected proportion of positive matches is not constant throughout the data set and is expected to fall fast as the first matches are found.\
-Our solution was to use Bayesian logistic regression to model the label of the manually reviewed records on the lower bound of the [98% PrI] produced by our algorithm.
-For the model we used weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).
-The goal of the model is to estimate the PPD of the missed number of positive matches in the whole data set.
+The citation data is not a random sample and it is ordered and for this reason, simple random sample based predictive performance approaches would not be useful (see Discussion).
+We focused on estimating the expected total sensitivity in the dataset, using a Bayesian logistic regression to model the label of the manually reviewed records on the lower bound of the [98% PrI] produced by our algorithm and then using this last model to produce a predictive cumulative distribution of the number of missed positive records.
+For this model, we used weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).
 Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing a plausible worst-case scenario.

### 2021-10-05 R/Model.R
fix: implement get_session_files into the grid search

@@ -1039,14 +1039,6 @@ enrich_annotation_file <- function(session_name, file = NULL, DTM = NULL,
 	common_tag <- glue('{if (repl > 1) paste0("rep", repl, "_") else ""}{safe_now()}')
 	iter <- with(Results, Value[Indicator == 'Iter'])
 
-	# message('- DTM...')
-	# tictoc::tic()
-	# DTM_file <- file.path(session_path, 'DTM.rds')
-	#
-	# readr::write_rds(DTM, file = DTM_file, compress = 'gz')
-	#
-	# tictoc::toc()
-
 	message('- annotated records...')
 	tictoc::tic()
 	output_file_ann <- file.path(session_path, 'Annotations',
@@ -1092,7 +1084,8 @@ enrich_annotation_file <- function(session_name, file = NULL, DTM = NULL,
 			rm(Predicted_data, Annotated_data, Var_imp, Samples)
 			gc()
 
-			enrich_annotation_file(output_file_ann, DTM = DTM_file,
+			enrich_annotation_file(output_file_ann,
+														 DTM = get_session_files(session_name, sessions_folder)$DTM,
 														 ## Model parameters
 														 pos_mult = pos_mult,
 														 n_models = n_models,
@@ -1160,7 +1153,7 @@ perform_grid_evaluation <- function(records, sessions_folder = 'Grid_Search',
 																		## Model parameters
 																		resample = c(FALSE, TRUE),
 																		n_init = c(50, 100, 250, 500),
-																		n_models = c(5, 10, 20, 40, 60),
+																		n_models = c(1, 5, 10, 20, 40, 60),
 																		pos_mult = c(1, 10, 20),
 																		pred_quants = list(c(.1, .5, .9),
 																											 c(.05, .5, .95),
@@ -1172,7 +1165,7 @@ perform_grid_evaluation <- function(records, sessions_folder = 'Grid_Search',
 																			pos_target = NULL, labeling_limit = NULL
 																		)) {
 
-	# file: 'Sessions/Session1/Records_2021-03-18T13.09.24.xlsx'
+	# file: 'Grid_Search/Classification_data.xlsx'
 
 	# prepare the parameter grid
 	Grid <- tidyr::expand_grid(
@@ -1223,7 +1216,12 @@ perform_grid_evaluation <- function(records, sessions_folder = 'Grid_Search',
 		}
 
 		# pick the last annotated record file or the source one if any
[…]

### 2021-10-05 R/Record_management.R
fix: explictly output a named list from get_session_files

@@ -404,7 +404,7 @@ get_session_files <- function(session_name,
 
 	session_path <- file.path(sessions_folder, session_name)
 
-	sapply(which, function(type) {
+	lapply(which, function(type) {
 		files <- list.files(session_path, recursive = T) %>% str_subset(type)
 
 		files <- files[str_detect(basename(files), '^\\w')]
@@ -424,7 +424,7 @@ get_session_files <- function(session_name,
 		) %>% arrange(iter) %>% pull(files)
 
 		file.path(session_path, files)
-	})
+	}) %>% setNames(which)
 }
 
 

### 2021-10-11 Manuscript/Manuscript_Discussion_TD.Rmd
update

@@
 
-We propose a new integrated framework to help researcher collect and screen scientific publications characterized by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools.
-By sharing the tool as an open source R package and following a modular design of the tool, we tried to adopt some of the so called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].
-Our tool thus consists of three main components: 1) an integrated query-based citation search and management engine, 2) an active machine learning based citation screener, and 3) a data-driven query generation algorithm.\
+We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
+By sharing the tool as an open-source R package and following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
+Our tool thus consists of three main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) an active machine learning-based citation screener, and 4) a data-driven search query generation algorithm.\
 
-The framework's search engine module is capable of automatically collecting citation data from three well known scientific databases (i.e.
+The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e.
 Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases.
-The online search algorithm is efficient enough to manage tens of thousands of search results, using various expedients to overcome the online databases limitations in terms of traffic and download quota.\
+In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
+Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
+in our results, 18.7% of the positive matches found were unique for one of the different data sources, and no positive record was present in all of them (data not shown).\ 
+The online search algorithm is efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the online database in terms of traffic and download quota.\
 
-Most SRH tools we are aware of, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) that focus on a particular topic [@visser2010performing] or rely on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].
-To our knowledge, our tool is the first capable to fully automatize searching on three different well known scientific databases and to import raw data from five of them.
-Mixing different database is fundamental to have a more complete view of the literature on a topic [@bajpai2011search; @wilkins2005embase; @woods1998medline]: in our results, 18.7% of the positive matches were unique for one of the different data sources and no positive record was present among all of them (data not shown).\
+The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
+We did not include classical n-grams [@schonlau2017text], but we used network analysis to find non-consecutive frequently associated terms, a generalisation of n-grams relaxing the term adjacency assumption.
+A similar network approach was applied to merge redundant terms to make model estimation more efficient and reduce possible noise.
+The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\
 
-We improved the transformation of textual data into actionable numeric inputs [@ananiadou2006text; @cohen2008getting] by using network analysis to identify associated terms, labelled as non-consecutive ngrams, conferring particular meaning when present together into a text while not necessary being close to each other.
-A similar network approach was used to merge redundant terms, in order to make model estimation more efficient and reduce possible noise.
-The use of network inspired modeling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text] and is a valuable tool to extract semantic information not evident in one-word of consecutive ngram models.\
+The framework's record screening module implements active machine learning-based classification [@settles2009active, @miwa2014reducing] based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine], adopting best practices from other SRA studies and bringing improvements at various levels.\
+As with other boosted trees algorithms [@hastie2009boosting], BART can explore complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.\
+However, its Bayesian foundation provides further benefits:
+less sensitivity on hyperparameter choices, natural regularisation through priors, and, especially, predictive distributions as output in place of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
+By selecting relatively tight prior distributions, we discouraged excessively deep trees, long sequences of trees, or extreme predicted probabilities, to decrease the risk of overfitting.\
+The algorithm runs multiple replications of the model and averages their predictive distributions to create an "ensemble", a technique that has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble] as confirmed by the hyperparameter evaluation (Suppl.
+Mat.
+S2).
+This approach reduces the uncertainty in the predictive distribution tails due to the randomness in the MCMC fit [@robert2004monte], generating a shift of probability mass towards the centre and stabilising the distributions (i.e., decreasing variance without impacting bias).
+On the other hand, just imposing robust uninformative priors against extreme predictions would have decreased variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
+Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which performance stabilises.\
+We also evaluated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory, it was demonstrated to be slightly detrimental (Suppl.
+Mat.
+S2) compared to same-data ensembling [@diez2015diversity].\
 
-The framework's record screening module implements active machine learning based classification, bringing improvements at various levels.
-At the base of our classification algorithm we use BART [@chipman2010bart; @kapelner2013bartmachine], a Bayesian machine learning technique characterized by exceptional predictive performance and speed even in large dataset.
-This Bayesian approach explores distributions of decision trees which are justified by the data [@hastie2009boosting], while using a set of prior distributions to avoid overfitting by discouraging excessively deep trees, long sequences of trees, or extreme predicted probabilities.\
+A low rate of relevant matches (class imbalance) is typical in literature reviews [@sampson2011precision; @wallace2010semi; @o2015using], and such strong imbalance between positive and negative records can affect sensitivity [@khoshgoftaar2010comparing; @chawla2004special].\
+To overcome the problem, we oversampled [@batista2004study] the positive records ten times before model fitting.
+Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance.\
+A known risk with positive oversampling is the misclassification of negative records [@ramezankhani2016impact].
+However, since all predicted positives get manually reviewed in our approach, we are always ensured to achieve 100% specificity/positive predictive value: the only price for the increased sensitivity due to oversampling is a larger number of records to review.\
+An alternative to oversampling would be applying different weights and/or cost to the classes [@abd2013review; @diez2015diversity], but the BART implementation we used did not have this feature;
+also, using simple oversampling permits broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
+Finally, ordering the records by query term frequency (simple query ordering) generate a far higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), and this boosts the sensitivity of the model.\
 
-To further improve generalizability we ran multiple replications of the model and averaged their record predictive distributions; this technique, known as ensembling, has been shown to improve out-of-sample predictive performance [].
-In a Bayesian setting, this effect comes from a reduction of the probability mass in the tails of the predictive distributions while not shifting their locations (i.e., it decreases variance without impacting bias).
-Instead, imposing stronger general priors against extreme predictions would decreased variance but also shifted the distribution mass towards a non-decision zone, therefore increasing bias.\
+One of the central innovations we introduced is the concept of "uncertainty zone", which derives from the Bayesian foundation of the classification model.
+This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Suppl. Mat. S2 Fig. 1).
+This approach permits overcoming the limitations of active learning related to selecting a stopping rule which focus on hard thresholds or propose singular new items at each iteration instead of a batch [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
+Our algorithm instead requires more general parameters, like the PPD intervals based on which the uncertainty zone is built and the maximum number of iterations with no positive matches after which a session is concluded; also, the hyperparamer evaluation shows that the algorithm is robust against variations in these parameters.\
+Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\
 
-Using more then one model replica greatly improved sensitivity and efficiency, with a performance stabilization after 10 replications (Suppl.
-Mat.
-S2); since the number of model replications greatly impacted computation times we decided to use ten replicas since it was also associated with the higher sensitivity in the same performance cluster.
-The variability between models derives only from the randomness in the MCMC fitting phase []; an alternative was to impose additional variability by bootstrapping [] but this approach decreased performance (Suppl.
-Mat.
-S2), probably due to the low proportion of positive matches in the data and the loss of information with bootstrapping in unbalanced classification tasks [].\
+We evaluated performance as the capability of the screening procedure (automatic classification plus manual review) to find the largest number of relevant records while reviewing as few of them as possible (i.e., sensitivity $\times$ efficiency).
+We avoided the classic out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study; @james2013introduction].
+Such methods primarily assume that the probability of a positive match is equal on average in both the training and test set [@tashman2000out];
+this uniformity is broken by how the initial training set and the subsequent reviewed records are selected by the query-based ordering and the active learning algorithm, determining a lower positivity rate in the unlabelled records (Fig.
+2).
+Also, a literature corpus is unique per search query/database combination, and therefore any out-of-sample performance estimate is not replicable since no new data can be acquired related to the current corpus.\
+Instead, to estimate overall sensitivity, we implemented a surrogate, strongly regularised [@van2021bayesian], Bayesian regression model relying on just the lower interval of the generated PPD as predictor to abstract the active learning-based classification process and achieve a maximum entropy [@harremoes2001maximum] probabilistic estimate of the number of missed positive matches among the unreviewed records.
+This simple surrogate model fitted the data very well ($R^2$ consistently above 97%), and its posterior predictive distribution could be exploited to explore worse case scenarios in terms of sensitivity.\
 
-Given that our framework can (automatically) collect a vast amount of records, most records will be non-relevant (labelled negative).
-This strong imbalance between positive and negative records [@sampson2011precision] can affect sensitivity [].
-To overcome the problem, we oversampled the positive records ten times before model fitting.
-Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance.
-A known risk with oversampling of the target class is the missclassification of negative records as positive [], but since in our approach all predicted positive are manually reviewed we are ensured to achieve always 100% specificity/positive predictive value.
-An alternative approach would be record weighting to change error costs during estimation [] but the BART implementation we used did not allow observation weighting and using simple oversampling allows to use different modeling engines.
-Furthermore, the simple query ordering of the record during the record collection allowed for a far higher prevalence of relevant records in the initial training set (17.2%) compared to the overall one (0.11%) and this boosts the overall sensitivity of the model.\
+Our framework achieved very high sensitivity by screening a markedly small fraction of all records, bringing a sensible reduction in workload.\
+Based on the surrogate model, we predicted a theoretical median sensitivity of 100% [93.5%, 100%] in the first session (screening 4.29% of records) and of 97.3% [73.8%, 100%] in the second (screening 1.34% of records):
+efficiency increased significantly in the second session since only a few new positive matches were found, but given the large number of records, uncertainty regarding sensitivity also expectedly increased.\
+Both results are above the usual performance in the field [@o2015using] and in line with the 92% average sensitivity estimated after human-only screening [@edwards2002identification].
+In one interesting case, the model spotted a human misclassification in the initial training set, demonstrating its robustness and value as a second screener, as already suggested by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
+Finally, albeit the simple query ordering already concentrated most of the relevant matches in the first 20-25 thousand records, without the tool support some relevant records would have required almost the complete data set to be manually checked to be found.\
 
-At every iteration the researcher is asked to manually review a number or records, defined by the size of the uncertainty zone, which is dynamically shrinking (Suppl.
-Mat.
-S2 Fig.
-1).
-This uncertainty zone is identified by joining the distribution of probabilities produced by exploiting the Bayesian nature of BART for both the positive and negative record groups.
-The researcher therefore doesn't need to choose a priori the number of records to review but just the size of the uncertainty zone (by setting the PPD quantiles used to built it) and after how many iterations with no new positive matches to stop.
-This is where our approach offers a major innovation in overcoming of simple stopping rules in SRA classification tasks [].
-Since our approach requires researchers to review both unlabelled records with a positive predicted label and those with a PPD inside the uncertainty zone, it can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\
-
-To evaluate performance we avoided the classic random out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study] because we deemed them not realistic in this setting.
-It is instead more relevant to estimate the long run sensitivity of our prediction method in finding all relevant records in the whole data set.
-Since the records are ordered, again a random approach would not work since it assumes that the prevalence of positive records is equal on average in every possible sample [@tashman2000out], while instead it drops as more records are considered (Fig.
-2).
-We instead used a Bayesian model to estimate the likelihood of a positive match given the prediction scores of the BART model.
-This approach showed to fit the data very well (high $R^2$) and the Bayesian predictive distribution can be exploited to draw a worse case scenario given the data.\
-
-Our framework achieved a very high sensitivity screening just 1.34% of all downloaded records, a sensible reduction in workload.
-The approach reached 98.8% sensitivity during the hyperparameter optimization (deterministic, small sample) and on the whole data set we predicted a theoretical sensitivity of 100% [93.5%, 100%] in the first session and of 97.3% [73.8%, 100%] in the second, a lower value as is expected by the probabilistic accumulation of random events.
-Both results are above the usual results in the field [@o2015using] and in line with the 92% average sensitivity estimated after human only screening [@edwards2002identification].
-In one interesting case, the model spotted a misclassification during initial labeling, demonstrating its robustness and its value also as a second screener, as already suggested by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
-Finally, albeit the simple query based ordering did concentrate most of the relevant matches in the first 20-25 thousands records, some relevant records would have required almost the full data set to be manually checked to be found.\
-
-The model takes ~5-20 minutes per iteration to perform predictions in session 1 (17755 documents) and 20-40 minutes in session 2 (98371 documents) on a 8 core, 2.5 GhZ, 16 GB RAM laptop from 2014 and that equate to 1-3 days per session to manually review and perform predictions, for a total of 1-2 weeks for the whole process, a huge saving of time compared to the months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
-To our knowledge, our data sets are larger than what common in most SRA studies [@o2015using; @olorisade2016critical], emphasizing the reliability of the tool in real world scenarios.\
+The model took ~5-20 minutes per iteration to perform predictions in session 1 (17,755 documents) and 20-40 minutes in session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM laptop from 2014;
+including manual record review, one session required 1-3 days of work, for a total of 1-2 weeks for the whole process (including record collection).
+That is a considerable saving of time compared to the months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
+To our knowledge, our data sets are larger than what is typical in most SRA studies [@o2015using; @olorisade2016critical], emphasising the reliability of the tool in real-world scenarios.\
 
 The last module of our framework is a data-driven query generation algorithm.
-The creation of an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximize the number of relevant search results while minimizing the total number of results.
-We propose a solution based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the posterior predicted probabilities; the technique tries to extract high sensitivity subqueries from the labeled data, enrich them with negative terms to increase specificity [@abdelmgeid2008using] and then let researcher evaluate them and pick the most meaningful ones.
-The framework will then join them and remove redundancies.
-The aim is to generate a second query that complement the first human made one and help find possible missing records not found during the first session.\
-
-The generated query allowed to retrieve few more positive matches not found in session 1 at the cost of a large increase in the amount of documents.
-One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules internalized by the classification model, showing which combination of terms was particularly relevant and even spotting authors and locations associated to the topic of study.
-The generated query therefore acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to spot bias in black box classification algorithms [@malhi2020explainable] and that is increasingly legally required for high-stack machine learning applications [@bibal2021legal; @bibal2020impact].\
-
+Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of results.
+Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD with a human review step and an efficiency-driven query joiner.
+The aim is to generate a second query that helps find records missed during the first session search.
+The generated query allowed indeed to retrieve few more positive matches not found in session 1, but at the cost of a significant increase in the number of documents.\
+One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
+The generated query, therefore, acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to understand and spot bias in black-box classification algorithms [@malhi2020explainable];
+explainability is often required or even legally mandatory for high-stake machine learning applications [@bibal2021legal; @bibal2020impact].\
 It is important to note that this process is entirely data-driven.
-The algorithm is only aware of the "world" defined by the data set, itself generated by a specific search query focused on a particular topic.
+The algorithm is only aware of the "world" defined by the data set generated by a specific search query focused on a particular topic.
 Therefore, the new query may not be specific once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
-The solution we found was to add another component specifying the general topic (antimicrobial resistance and healthcare associated infections) of our research.\
+The solution we found was to add another component specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research to the query.\
 
 As reported, our framework builds on modularity.
-We designed it in order to easily implement complete independency of the main modules in future iterations.
-In our view it would be possible to easily add custom citation search and parsing functions for other scientific databases, alternative text features building algorithms and alternative machine learning modules.
-We deem such interoperability extremely relevant, because the main strength of our tool is the composition of many solutions and the general approach related to Bayesian active machine learning, but each of its components could benefit greatly from the recent improvements in text mining.
-For example, our text feature generation approach is based on the boolean bag-of-words paradigm, and surely it could be improved by more nuanced text representations: it could be evaluated if feature transformations like Tf-Idf [@baeza1999modern; @ananiadou2006text], would be advantageous, even if we hypothesize that tree based classification algorithms like BART are robust enough to not need such operation.
-Word embedding could be considered, which transform terms in semantic vectors based on the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep], and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context; another option would be to use unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis, etc., [@pavlinek2017text; @chen2016short; @landauer1998introduction] to extract topics to enrich the feature space.\
+We designed it to easily implement complete independence of the main modules in future iterations, making it possible for users to add custom features like citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
+We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general approach related to Bayesian active machine learning.
+However, each of its components could benefit considerably from the recent improvements in text mining.\
+For example, our text processing approach is based on the boolean bag-of-words paradigm, and indeed it could be improved by more nuanced text representations.
+It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operation.
+Word embedding, a technique that transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep], could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.
+Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis or Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] to extract topics to enrich the feature space.\
+Our classification algorithm can be implemented with any Bayesian supervised machine learning method that provides full PPDs;
+therefore alternative models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
+Even more interesting would be to test advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher-level features in the text like term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
 
-Our classification algorithm can be implemented with any Bayesian supervised machine learning method which produces full PPDs; therefore alternative models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
-Even more interesting would be to test  advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher level features in the text like term context and sequences, long distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
+The field of literature review automatisation is becoming mature and ripe with innovation, and we expect an increasing use of such technologies to confront the ever-faster production of scientific literature.
+We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.
+We tried to contribute to the field with an innovative methodology and tool that provides excellent performance and easy integration with existing systematic review pipelines.

### 2021-10-11 Manuscript/Manuscript_Introduction.Rmd
update

@@
 We apply this solution in the production of a systematic review evaluating the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms with a focus on antimicrobial-resistant strains.
-The systematic review protocol is published in [@newis].
+The systematic review protocol is published in [@newis].\
+We give an overview of the framework in the Methods section and its results once applied to the topic of patient referral network modeling in Results section; in the Discussion we lay out the methodological justification behind the different components and features of the framework.

### 2021-10-11 Manuscript/Manuscript_Methods.Rmd
update

@@
 We built an R [@rstat] based framework with the goal of simplifying two aspects of systematic reviews: record acquisition and classification.
-The framework is composed of several components which act together while being independent enough to be in principle be substituted by alternative implementations, given that the structure of the intermediate data outputs is respected.
+The framework is composed of several modules which communicate through intermediate outputs stored in common formats (Comma Separated Values/or Microsoft Excel™), which make it possible for users to extend the framework or easily integrate it with other tools in their pipeline.
 See Supplemental Material S1 for an in-depth description of the framework and how to use it.\
-The tasks carried out by the framework are grouped into "sessions", that is, a set of actions that starts from using a search query to obtain a set of scientific publications (records), which will be eventually labelled as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest (Fig.
+The tasks carried out by the framework are grouped into "sessions", that is, a set of actions that starts from a search query to obtain a set of scientific publication data (records), which will be eventually labelled as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest (Fig.
 1).
-From this labelled set, the framework allows to generate a new query and perform a new session.\
-The researcher should use the framework with a specific query from which she expects a high relevant/non-relevant record ratio.\
+From this labelled set, the framework can generate a new query and perform a new session to find records possible missed by the first query.\
+The researcher should use the framework with a starting query from which she expects a high relevant/non-relevant record ratio.\
 Follows a description of the framework's components.\
@@
 We used a Bayesian Additive Regression Trees (BART) machine learning model [@chipman2010bart] [in the implementation of @kapelner2013bartmachine] to predict the probability of a record of being relevant, given the information coded into the enriched DTM.
-BART models have several advantages: as other boosted trees techniques [@hastie2009boosting], they can model complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.
-However, the Bayesian framework they are built on provides further benefits: less sensitivity on hyperparameter choices, natural regularization, and, most of all, predictive distributions as output in place of point-wise predictions.\
-We set up the BART model to use 2000 iterations (after 250 burn-in iterations) and 50 trees; we used a $k$ value of 2 to regularized extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction].
+We set up the BART model to use 2000 MCMC iterations (after 250 burn-in iterations) and 50 trees; we used a $k$ value of 2 to regularized extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction].
 Since the goal is to find all positive matches (i.e., focus on sensitivity), positive records are oversampled ten times.\
@@
 ### Performance evaluation
-The citation data is not a random sample and it is ordered and for this reason, simple random sample based predictive performance approaches would not be useful (see Discussion).
-We focused on estimating the expected total sensitivity in the dataset, using a Bayesian logistic regression to model the label of the manually reviewed records on the lower bound of the [98% PrI] produced by our algorithm and then using this last model to produce a predictive cumulative distribution of the number of missed positive records.
+Each literature corpus is unique per database/search query, so we did noWe focused on estimating the expected total sensitivity in the dataset, using a surrogate [] Bayesian logistic regression to model the record labels on the lower bound of the [98% PrI] produced by our algorithm and then using this last model to produce a predictive cumulative distribution of the number of missed positive records.
 For this model, we used weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).

### 2021-10-11 Manuscript/Manuscript_Results.Rmd
update

@@
 output:
-  pdf_document:
-    includes:
-      in_header: header.tex
+  # pdf_document:
+  #   includes:
+  #     in_header: header.tex
   github_document: default
@@
 As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a subset of 1200 completely manually labelled records (validation set).
-The best set of parameters suggested an initial input of 250 labelled records with 20x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
+The best set of parameters suggested an initial input of 250 labelled records with 10x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
 On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).

### 2021-10-11 R/Analysis.R
fix: edited grid search plot legend title

@@ -417,7 +417,7 @@ analyse_grid_search <- function(session_folder = 'Grid_Search', tot_pos = NULL,
 			theme_minimal() +
 			scale_color_manual(values = colors) +
 			scale_fill_manual(values = colors) +
-			labs(color = glue('Perf. cluster (mean {score})'))
+			labs(color = glue('Perf. cluster'))
 
 		tmp <- ggplot_gtable(ggplot_build(p_one))
 		leg <- which(tmp$layout$name == 'guide-box')

### 2021-10-11 R/Setup.R
fix: add missing package

@@ -43,7 +43,7 @@ pkg.require(
 											 "bakaburg1/tidytrees"),
 	only_install = c('purrr', 'openxlsx', 'tictoc', 'tidyr', 'arm', 'english',
 									 'parallel', 'jsonlite', 'rentrez', 'wosr', 'brms', 'ggridges',
-									 'knitr', 'kableExtra')
+									 'knitr', 'kableExtra', 'extraDistr')
 )
 
 

### 2021-10-20 R/Analysis.R
clean: use getOption to, well, get options

@@ -80,7 +80,7 @@ estimate_positivity_rate_model <- function(train_data, seed = 14129189) {
 }
 
 estimate_performance <- function(records, model = NULL, preds = NULL, plot = TRUE,
-																 quants = options('baysren.probs')[[1]],
+																 quants = getOption('baysren.probs'),
 																 nsamples = min(2500, sum(model$fit@sim$n_save)),
 																 seed = 23797297,
 																 save_preds = FALSE, save_model = FALSE) {
@@ -268,7 +268,7 @@ estimate_performance <- function(records, model = NULL, preds = NULL, plot = TRU
 # }
 
 extract_var_imp <- function(session_name, num_vars = 15, score_filter = 1.5, recompute_DTM = FALSE,
-														sessions_folder = options("baysren.sessions_folder")[[1]]) {
+														sessions_folder = getOption("baysren.sessions_folder")) {
 
 	message('Retrieving data')
 	session_files <- get_session_files(session_name, sessions_folder)

### 2021-10-20 R/Model.R

@@ -148,7 +148,7 @@ compute_BART_model <- function(train_data, Y, preds = NULL, save = F,
 }
 
 # compute_pred_performance <- function(model, data = NULL, Y = NULL, summary = F,
-# 																		 quants = options('baysren.probs')[[1]], AUC.thr = .9) {
+# 																		 quants = getOption('baysren.probs'), AUC.thr = .9) {
 #
 # 	library(scales)
 # 	library(pROC)
@@ -496,7 +496,7 @@ enrich_annotation_file <- function(session_name, file = NULL, DTM = NULL,
 																	 resample = F,
 																	 pred_quants = c(.01, .5, .99),
 																	 #
-																	 sessions_folder = options("baysren.sessions_folder")[[1]],
+																	 sessions_folder = getOption("baysren.sessions_folder"),
 																	 pred_batch_size = 5000,
 																	 autorun = TRUE, replication = NULL,
 																	 stop_on_unreviewed = TRUE,
@@ -1110,7 +1110,7 @@ enrich_annotation_file <- function(session_name, file = NULL, DTM = NULL,
 	invisible(out)
 }
 
-consolidate_results <- function(session_name, sessions_folder = options("baysren.sessions_folder")[[1]]) {
+consolidate_results <- function(session_name, sessions_folder = getOption("baysren.sessions_folder")) {
 	annotations_files <- get_session_files(session_name, sessions_folder)$Annotations
 
 	message('Loading annotations...')

### 2021-10-20 R/Record_management.R

@@ -313,7 +313,7 @@ create_annotation_file <- function(records, reorder_query = NULL,
 }
 
 create_session <- function(Records, session_name,
-													 sessions_folder = options("baysren.sessions_folder")[[1]],
+													 sessions_folder = getOption("baysren.sessions_folder"),
 													 DTM = NULL,
 													 dup_session_action = c('skip', 'stop', 'add', 'replace', 'silent'),
 													 use_time_stamp = TRUE) {
@@ -398,7 +398,7 @@ create_session <- function(Records, session_name,
 }
 
 get_session_files <- function(session_name,
-															sessions_folder = options("baysren.sessions_folder")[[1]],
+															sessions_folder = getOption("baysren.sessions_folder"),
 															which = c('Records', 'Annotations',
 																				'DTM', 'Samples', 'Results')) {
 

### 2021-10-20 R/Record_search.R

@@ -58,7 +58,7 @@ clean_date_filter_arg <- function(year_query, cases,
 }
 
 search_wos <- function(query, year_query = NULL, additional_fields = NULL,
-											 default_field = 'TS', api_key = options('baysren.wos_api_key')[[1]],
+											 default_field = 'TS', api_key = getOption('baysren.wos_api_key'),
 											 parallel = T, parse_query = T, ...) {
 
 	message('Searching WOS...')
@@ -168,7 +168,7 @@ search_wos <- function(query, year_query = NULL, additional_fields = NULL,
 }
 
 search_pubmed <- function(query, year_query = NULL, additional_fields = NULL,
-													api_key = options('baysren.ncbi_api_key')[[1]],
+													api_key = getOption('baysren.ncbi_api_key'),
 													record_limit = numeric(),
 													...) {
 
@@ -239,7 +239,7 @@ search_pubmed <- function(query, year_query = NULL, additional_fields = NULL,
 }
 
 search_ieee <- function(query, year_query = NULL, additional_fields = NULL,
-												api_key = options('baysren.ieee_api_key')[[1]], allow_web_scraping = T,
+												api_key = getOption('baysren.ieee_api_key'), allow_web_scraping = T,
 												file_name = glue('IEEE_{safe_now()}'), save = T,
 												wait_for = 20, record_limit = NULL) {
 	message('Searching IEEE...')

### 2021-10-20 R/Reporting.R

@@ -39,7 +39,7 @@ summarise_by_source <- function(annotation_file, as_data_frame = FALSE,
 }
 
 summarise_sources_by_session <- function(sessions = list.files(sessions_folder),
-																				 sessions_folder = options("baysren.sessions_folder")[[1]],
+																				 sessions_folder = getOption("baysren.sessions_folder"),
 																				 add_global_totals = TRUE, keep_session_label = FALSE, ...) {
 	if (length(sessions) == 1) {
 		res <- get_session_files(session, sessions_folder)$Records %>%
@@ -120,7 +120,7 @@ get_source_distribution <- function(annotation_file, as_propr = TRUE, format_fun
 	res
 }
 
-summarise_annotations <- function(session_name, sessions_folder = options("baysren.sessions_folder")[[1]],
+summarise_annotations <- function(session_name, sessions_folder = getOption("baysren.sessions_folder"),
 																	remove_empty_columns = TRUE, remove_raw_data = TRUE) {
 	result_list <- get_session_files(session_name, sessions_folder)$Results %>%
 		lapply(function(file) {
@@ -196,7 +196,7 @@ summarise_annotations <- function(session_name, sessions_folder = options("baysr
 	}
 }
 
-summarise_annotations_by_session <- function(sessions_folder = options("baysren.sessions_folder")[[1]],
+summarise_annotations_by_session <- function(sessions_folder = getOption("baysren.sessions_folder"),
 																						 remove_empty_columns = TRUE,
 																						 remove_raw_data = TRUE) {
 	sessions <- list.files(sessions_folder)
@@ -584,7 +584,7 @@ format_performance <- function(..., session_names = NULL) {
 }
 
 plot_predictive_densities <- function(session_name,
-																			sessions_folder = options("baysren.sessions_folder")[[1]]) {
+																			sessions_folder = getOption("baysren.sessions_folder")) {
 
 	library(ggridges)
 

### 2021-10-20 R/Rule_building.R

@@ -1,5 +1,5 @@
 extract_rules <- function(session_name, rebuild_dtm = F, vimp.threshold = 1.25,
-													n.trees = 800, sessions_folder = options("baysren.sessions_folder")[[1]], ...) {
+													n.trees = 800, sessions_folder = getOption("baysren.sessions_folder"), ...) {
 
 	message('Preparing the data')
 

### 2021-10-20 R/Setup.R

@@ -4,7 +4,7 @@
 
 Sys.setenv(LANG = "en")
 
-if (is.null(options('BartMem')[[1]]) & interactive()) {
+if (is.null(getOption('BartMem')) & interactive()) {
 	local({
 		mem <- readline("How much GB of memory should be used (better no more than 90% of available one)?")
 
@@ -16,7 +16,7 @@ if (is.null(options('BartMem')[[1]]) & interactive()) {
 	})
 }
 
-options(java.parameters = options('BartMem')$BartMem)
+options(java.parameters = getOption('BartMem'))
 
 pkg.require <- function(install_and_load = c(), only_install = c()) {
 

### 2021-10-20 Manuscript/Manuscript_Discussion.Rmd
update

@@
 We propose a new integrated framework to help researcher collect and screen research publications characterized by high performance and versatility, joining the growing field of systematic review automatization (SRA) and helpers (SRH) tools.\
-The International Collaboration for the Automation of Systematic Reviews (ICASR) proposes a number of features tools for automatic research synthesis should possess, defining the so called Vienna Principles [@beller2018making].
-We tried to adopt some of the concepts advocated by the ICAS; for example we are sharing the tool as an open source R package, and we tried to follow the paradigms of modular programming [@mccracken2003modular], building separated components communicating through intermediate outputs stored in common formats (Comma Separated Values/Microsoft Excel™), which make it possible for users to extend the framework or integrate it with other tools in their pipeline.\
+The International Collaboration for the Automation of Systematic Reviews (ICASR) proposes a number of features tools for automatic research synthesis should possess, defining the so called Vienna Principles [@beller2018making].We tried to adopt some of the concepts advocated by the ICAS; for example we are sharing the tool as an open source R package, and we tried to follow the paradigms of modular programming [@mccracken2003modular], building separated components communicating through intermediate outputs stored in common formats (Comma Separated Values/Microsoft Excel™), which make it possible for users to extend the framework or integrate it with other tools in their pipeline.\
 Our framework has two main components, an integrated query-based citation search and management engine and an active machine learning record screener\

### 2021-10-20 Manuscript/Manuscript_Discussion_TD.Rmd
update

@@
 We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
-By sharing the tool as an open-source R package and following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
-Our tool thus consists of three main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) an active machine learning-based citation screener, and 4) a data-driven search query generation algorithm.\
+This framework joins standard approaches and uses ad-hoc solutions to deal with common SRA issues.\
+By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
+Our tool consists of four main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) a Bayesian active machine learning-based citation classifier, and 4) a data-driven search query generation algorithm.\
 
@@
 in our results, 18.7% of the positive matches found were unique for one of the different data sources, and no positive record was present in all of them (data not shown).\ 
-The online search algorithm is efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the online database in terms of traffic and download quota.\
+The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the online database in terms of traffic and download quota.\
+The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
+The preliminary ordering allow to increase the positivity rate in the initial training set [@wallace2010active].
 
@@
 We did not include classical n-grams [@schonlau2017text], but we used network analysis to find non-consecutive frequently associated terms, a generalisation of n-grams relaxing the term adjacency assumption.
-A similar network approach was applied to merge redundant terms to make model estimation more efficient and reduce possible noise.
-The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\
+A similar network approach was applied to merge redundant terms to make model estimation more efficient and reduce noise.\
+The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\
 
-The framework's record screening module implements active machine learning-based classification [@settles2009active, @miwa2014reducing] based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine], adopting best practices from other SRA studies and bringing improvements at various levels.\
+The framework's record classification module implements an active machine learning approach [@settles2009active, @miwa2014reducing] and is based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine].
+When implementing our algorithm we adopted best practices from other SRA studies, bringing improvements at various levels.\
 As with other boosted trees algorithms [@hastie2009boosting], BART can explore complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.\
@@
 By selecting relatively tight prior distributions, we discouraged excessively deep trees, long sequences of trees, or extreme predicted probabilities, to decrease the risk of overfitting.\
-The algorithm runs multiple replications of the model and averages their predictive distributions to create an "ensemble", a technique that has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble] as confirmed by the hyperparameter evaluation (Suppl.
-Mat.
-S2).
-This approach reduces the uncertainty in the predictive distribution tails due to the randomness in the MCMC fit [@robert2004monte], generating a shift of probability mass towards the centre and stabilising the distributions (i.e., decreasing variance without impacting bias).
+The algorithm runs multiple replications of the model and averages their predictive distributions creating an "ensemble";
+this technique has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble], as we were able to confirm during the hyperparameter evaluation (Supplemental Material S2).
+Ensembling reduces the uncertainty in the predictive distribution tails related to the randomness in the MCMC fit [@robert2004monte], generating a shift of probability mass towards the distribution centre and stabilising it (i.e., decreasing variance without impacting bias).
 On the other hand, just imposing robust uninformative priors against extreme predictions would have decreased variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
-Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which performance stabilises.\
-We also evaluated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory, it was demonstrated to be slightly detrimental (Suppl.
-Mat.
-S2) compared to same-data ensembling [@diez2015diversity].\
+Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which showed performance stabilisation during the hyperparameter evaluation.\
+We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory [@diez2015diversity], it was demonstrated to be slightly detrimental (Supplemental Material S2) compared to simple ensembling.\
 
@@
 also, using simple oversampling permits broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
-Finally, ordering the records by query term frequency (simple query ordering) generate a far higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), and this boosts the sensitivity of the model.\
+Finally, ordering the records by query term frequency (simple query ordering) generates a far higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), and this boosts the sensitivity of the model.\
 
-One of the central innovations we introduced is the concept of "uncertainty zone", which derives from the Bayesian foundation of the classification model.
-This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Suppl. Mat. S2 Fig. 1).
-This approach permits overcoming the limitations of active learning related to selecting a stopping rule which focus on hard thresholds or propose singular new items at each iteration instead of a batch [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
-Our algorithm instead requires more general parameters, like the PPD intervals based on which the uncertainty zone is built and the maximum number of iterations with no positive matches after which a session is concluded; also, the hyperparamer evaluation shows that the algorithm is robust against variations in these parameters.\
+One of the central innovations we introduced is the concept of "uncertainty zone", whose implementation is possible thanks to the Bayesian foundation of the classification model.
+This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig.
+1).\
+This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
+The parameters our algorithm needs are instead quite general and non task-specific, like the PPD intervals based on which the uncertainty zone is built ,and the maximum number of iterations with no positive matches after which a session is concluded;
+the hyperparamer evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to preform well on most datasets.\
 Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\
 
-We evaluated performance as the capability of the screening procedure (automatic classification plus manual review) to find the largest number of relevant records while reviewing as few of them as possible (i.e., sensitivity $\times$ efficiency).
+We evaluated performance as the capability of the screening procedure (automatic classification plus manual review) to find the largest number of relevant records while reviewing as few of them as possible (i.e., sensitivity $\times$ efficiency).\
 We avoided the classic out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study; @james2013introduction].
-Such methods primarily assume that the probability of a positive match is equal on average in both the training and test set [@tashman2000out];
+Such methods primarily assume that the rate of positivity is equal on average in every random subset of the data [@tashman2000out];
 this uniformity is broken by how the initial training set and the subsequent reviewed records are selected by the query-based ordering and the active learning algorithm, determining a lower positivity rate in the unlabelled records (Fig.
@@
 Also, a literature corpus is unique per search query/database combination, and therefore any out-of-sample performance estimate is not replicable since no new data can be acquired related to the current corpus.\
-Instead, to estimate overall sensitivity, we implemented a surrogate, strongly regularised [@van2021bayesian], Bayesian regression model relying on just the lower interval of the generated PPD as predictor to abstract the active learning-based classification process and achieve a maximum entropy [@harremoes2001maximum] probabilistic estimate of the number of missed positive matches among the unreviewed records.
-This simple surrogate model fitted the data very well ($R^2$ consistently above 97%), and its posterior predictive distribution could be exploited to explore worse case scenarios in terms of sensitivity.\
+Instead, to estimate overall sensitivity, we employed simple Bayesian regression (surrogate model) on the manually reviewed data to abstract the classification model predictions and achieve a maximum entropy [@harremoes2001maximum] estimate of the number of missed positive matches among the unreviewed records in the whole dataset.
+This simple surrogate model fitted the data very well ($R^2$ consistently above 97%) using just the lower 98% PrI bound of the PPDs as predictor, indicating predictive consistency in the classification model.
+The surrogate model posterior predictive distribution could be exploited to explore worse case scenarios in terms of sensitivity.\
 
 Our framework achieved very high sensitivity by screening a markedly small fraction of all records, bringing a sensible reduction in workload.\
-Based on the surrogate model, we predicted a theoretical median sensitivity of 100% [93.5%, 100%] in the first session (screening 4.29% of records) and of 97.3% [73.8%, 100%] in the second (screening 1.34% of records):
+Based on the surrogate model, we predicted a predicted median sensitivity of 100% [93.5%, 100%] in the first session (screening 4.29% of records) and of 97.3% [73.8%, 100%] in the second (screening 1.34% of records):
 efficiency increased significantly in the second session since only a few new positive matches were found, but given the large number of records, uncertainty regarding sensitivity also expectedly increased.\
 Both results are above the usual performance in the field [@o2015using] and in line with the 92% average sensitivity estimated after human-only screening [@edwards2002identification].
-In one interesting case, the model spotted a human misclassification in the initial training set, demonstrating its robustness and value as a second screener, as already suggested by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
+In one interesting case, the model spotted a human-made misclassification error, demonstrating its robustness and value as a second screener, a role already suggested for SRA tools by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
 Finally, albeit the simple query ordering already concentrated most of the relevant matches in the first 20-25 thousand records, without the tool support some relevant records would have required almost the complete data set to be manually checked to be found.\
@@
 including manual record review, one session required 1-3 days of work, for a total of 1-2 weeks for the whole process (including record collection).
-That is a considerable saving of time compared to the months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
-To our knowledge, our data sets are larger than what is typical in most SRA studies [@o2015using; @olorisade2016critical], emphasising the reliability of the tool in real-world scenarios.\
+That is a considerable saving of time compared to the multiple months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
+To our knowledge, the amount of data processed (~100.000 records) were larger than what is typical in most SRA studies [@o2015using; @olorisade2016critical], emphasising the reliability of the tool in real-world scenarios.\
 
 The last module of our framework is a data-driven query generation algorithm.
-Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of results.
-Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD with a human review step and an efficiency-driven query joiner.
+Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to review.
+Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD with a human review step and an efficiency-driven query builder.
 The aim is to generate a second query that helps find records missed during the first session search.
@@
 It is important to note that this process is entirely data-driven.
-The algorithm is only aware of the "world" defined by the data set generated by a specific search query focused on a particular topic.
-Therefore, the new query may not be specific once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
-The solution we found was to add another component specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research to the query.\
+The algorithm is only aware of the "world" defined by the data set used as input, which is generated by a specific search query focused on a particular topic.
+Therefore, the new query may not be specific enough once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
+The solution we found was to add another component to the query, specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research.\
 
@@
 We designed it to easily implement complete independence of the main modules in future iterations, making it possible for users to add custom features like citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
-We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general approach related to Bayesian active machine learning.
+We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general idea of Bayesian active machine learning and uncertainty zone.
 However, each of its components could benefit considerably from the recent improvements in text mining.\
-For example, our text processing approach is based on the boolean bag-of-words paradigm, and indeed it could be improved by more nuanced text representations.
-It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operation.
-Word embedding, a technique that transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep], could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.
-Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis or Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] to extract topics to enrich the feature space.\
+For example, our text processing approach is quite simple, based on the boolean bag-of-words paradigm, and indeed could be improved by more nuanced text representations.
+It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operations.
+Word embedding could be worth exploring:
+this technique transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep] and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.
+Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics to enrich the feature space.\
 Our classification algorithm can be implemented with any Bayesian supervised machine learning method that provides full PPDs;
-therefore alternative models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
+therefore alternative classification models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
 Even more interesting would be to test advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher-level features in the text like term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
+Finally, a natural improvement would be to provide a graphical user interface to make the framework easy to use also for less technical users.
 
-The field of literature review automatisation is becoming mature and ripe with innovation, and we expect an increasing use of such technologies to confront the ever-faster production of scientific literature.
-We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.
+The field of literature review automatisation is mature and ripe with innovation, and we expect an increasing use of such technologies to confront the ever-faster production of scientific literature.
+We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.\
 We tried to contribute to the field with an innovative methodology and tool that provides excellent performance and easy integration with existing systematic review pipelines.
+The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of solutions we developed to solve various SRA issues and that can be used to improve existing solutions.

### 2021-10-20 Manuscript/Manuscript_Methods.Rmd
update

@@
 
-We built an R [@rstat] based framework with the goal of simplifying two aspects of systematic reviews: record acquisition and classification.
-The framework is composed of several modules which communicate through intermediate outputs stored in common formats (Comma Separated Values/or Microsoft Excel™), which make it possible for users to extend the framework or easily integrate it with other tools in their pipeline.
+We built an R [@rstat] based framework to simplify two aspects of systematic reviews:
+record acquisition and classification.
+The framework comprises several modules that communicate through intermediate outputs stored in standard formats, which make it possible for users to extend the framework or easily integrate it with other tools in their pipeline.
 See Supplemental Material S1 for an in-depth description of the framework and how to use it.\
-The tasks carried out by the framework are grouped into "sessions", that is, a set of actions that starts from a search query to obtain a set of scientific publication data (records), which will be eventually labelled as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest (Fig.
+The tasks carried out by the framework are grouped into "sessions", i.e., a set of actions that starts from a search query to obtain a set of scientific citation data (records), which are then labelled as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest (Fig.
 1).
-From this labelled set, the framework can generate a new query and perform a new session to find records possible missed by the first query.\
-The researcher should use the framework with a starting query from which she expects a high relevant/non-relevant record ratio.\
+The framework can generate a new query from this labelled set and perform a new session to find records possibly missed by the first query.\
+The researcher initiates the process with a starting query derived by domain knowledge from which she expects a high relevant/non-relevant record ratio.\
 Follows a description of the framework's components.\
@@
 ### Record's acquisition and initial labelling
-We built a set of tools to let users automatically search and download records data from three major scientific databases ("sources"): MEDLINE (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
-The user needs to input a search query and a date range.
-The query may contain boolean operators AND, OR, NOT and nested parentheses.\
-For WOS, an Application Programming Interface (API) key is necessary to use the automatic search tools; for IEEE, if an API key is not available, a slower, web scraping-based solution will be employed; for MEDLINE, an API key is required only for high-frequency requests to the NCBI server [@pubmed], or if a large number of records is expected since our tool splits big API requests in multiple smaller ones.\
-It is also possible to download and import records in the framework manually.
-This is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/search/form.uri?display=basic#basic>) and EMBASE databases (<https://www.embase.com/#advancedSearch/default>), for which a comprehensive API interface was not easy to build.
+We built a set of tools to let users automatically search and download citation data from three major scientific databases ("sources"):
+MEDLINE (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
+The framework takes care of authorization management for non-open databases like WOS and IEEE.
+It is also possible to download and import records in the framework manually;
+this is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/search/form.uri?display=basic#basic>) and EMBASE databases (<https://www.embase.com/#advancedSearch/default>), for which a comprehensive API interface was not easy to build.
 A short guide on how to set up the framework for each supported database is available in Supplemental Material S3.\
-Once the records are downloaded and acquired, the framework merges them into a single database, resolving duplicates and different formatting between sources.
-The records are ordered according to the frequency of the positive terms (e.g., not preceded by a $NOT$ modifier) of the query appear in the title and abstract ("simple ordering"); this approach is a modification of @wallace2010active.
-The final output is an "Annotation file" with all the record's info and its label when present´.\
+The acquired records are merged into a single database, resolving duplicates and different formatting between sources.
+The records are ordered according to the frequency of the positive query terms (e.g., not preceded by a $NOT$ modifier) in the title and abstract ("simple query ordering").\
+The researcher is then asked to label a number of records to create the "initial training set" needed to start the automatic classification.
+We suggest manually labelling the first 250 records (see "hyperparameter optimization" later).
+The simple query ordering increases the positivity rate in the initial training set [@wallace2010active], which provide higher sensitivity during automatic classification [@chawla2004special].
 
-An initial training set of manually labelled records is needed to start the automatic classification. We suggest manually label the first 250 records (see "hyperparameter optimization" later).\
-
-### Document-Term matrix generation
-The annotation file produced in the previous step has a number of fields characterizing a scientific publication.
-The framework models the relevance of a record based on the following fields: title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
-A series of Natural Language Processing (NLP) techniques [@baeza1999modern; @marshall2015systematic; @ananiadou2006text] are employed to transform the textual information in these fields into features for machine learning, through a bag-of-words approach [@marshall2015systematic].
-The processing of free text fields includes tokenization (i.e., extracting the terms), common stopwords (i.e.
+### Text feature extraction
+The collected citation data have a number of fields characterizing a scientific publication.
+The framework models the relevance of a record based on the following fields:
+title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
+A series of Natural Language Processing (NLP) techniques [@baeza1999modern; @marshall2015systematic; @ananiadou2006text] are employed to transform the textual information in these fields into features for machine learning through a bag-of-words approach [@marshall2015systematic].
+The processing of free text fields (title, abstract) includes: tokenization (i.e., extracting the terms), common stopwords (i.e.
 sentence components bringing no meaning) removal, part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatization of the terms (i.e.
 reduction to their base grammar form).
-Processing for authors, keywords and MESH terms identify logical units (e.g., author's full names, composite keywords) without breaking them into single terms, and no stopwords removal or lemmatization are applied.\
-To reduce noise and save computation time, terms that appeared in less than 5% of the labelled documents (positive and negatives) are removed from negative records.
+Text processing for authors, keywords and MESH terms identifies logical units (e.g., author's full names, composite keywords) and extracts them.\
+Terms appearing in less than 5% of the labelled documents are removed from negative records.
 All terms in the positive set are kept to increase sensitivity at the cost of specificity.\
 Some terms tend to co-appear in records (non-consecutive ngrams, nc-ngrams), often carrying a particular meaning when copresent.
-To detect nc-ngrams, we generated a network representation posing edges between terms with a cosine similarity in terms of records copresence > 0.5.
-We extracted the maximal cliques in the network [@eppstein2010listing] representing highly correlated groups of terms; These generated terms are added to the data set.
-To avoid overfitting, we kept nc-ngrams of a maximum of ten terms.\
-A similarity network is built again using a similarity threshold of 0.9 and finding the cliques again.
-In this case, the cliques represent terms that always appear together and therefore can be considered synonyms.
-These terms are merged in the data set to increase computation efficiency and reduce overfitting.\
-The final output is a matrix, also called a Document-Term Matrix (DTM), with $N_d$ rows representing the records $D$, $N_t$ terms column for the $t_{field}$ terms (divided by record field) and ${0,1}$ values whether $t_{field} \in D$.
-We also enriched the DTM with features storing the number of terms in each field to help the model scale term importance based on the document length.
+To detect nc-ngrams, we generated a word network representation [@rousseau2015graph] posing edges between terms with a cosine similarity in terms of record co-occurrence > 0.5.
+We extracted the maximal cliques in the network [@eppstein2010listing] representing highly correlated groups of terms;
+These groups of terms are added to the data set as individual features.
+Only nc-ngrams comprising a maximum of ten terms are kept.\
+A second network is built using a co-occurrence threshold of 0.9.
+In this case, the cliques represent terms that always appear together and therefore can be considered redundant (i.e. they do not need to be considered separately).
+These terms are merged to increase computation efficiency and reduce overfitting.\
+The output is a Document-Term Matrix (DTM), with $N_d$ rows representing the records ($D_i$), $N_t$ terms column for the $t_{field}$ terms (divided by record field) and ${0,1}$ values whether $t_{field} \in D_i$.
+We also enriched the DTM with features referencing the number of terms in each field to help the model scale term importance based on the field length.
 
 ### Label prediction
-We used a Bayesian Additive Regression Trees (BART) machine learning model [@chipman2010bart] [in the implementation of @kapelner2013bartmachine] to predict the probability of a record of being relevant, given the information coded into the enriched DTM.
-We set up the BART model to use 2000 MCMC iterations (after 250 burn-in iterations) and 50 trees; we used a $k$ value of 2 to regularized extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction].
-Since the goal is to find all positive matches (i.e., focus on sensitivity), positive records are oversampled ten times.\
-The output is a posterior predictive distribution (PPD) of each record's probability of a positive match.
-An ensemble of ten models was fitted to improve prediction stability by averaging the predictions between models.\
-To choose how to label a record, we exploit the uncertainty typical of Bayesian estimates to decide a record label and whether it requires manual evaluation, an approach joining the "uncertainty" and "certainty" selection criteria of previous work in the field [@miwa2014reducing].
+We used a Bayesian Additive Regression Trees (BART) machine learning "classification model" [@chipman2010bart] [in the implementation of @kapelner2013bartmachine] to predict the probability of a record of being relevant, given the information coded into the enriched DTM and the initial training set.
+We set up the BART model to use 2000 MCMC iterations (after 250 burn-in iterations) and 50 trees;
+we used a $k$ value of 2 to regularize extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction].
+Positive records are oversampled ten times to increase sensitivity [@batista2004study].\
+The output is a posterior predictive distribution (PPD) for each record describing its probability of being relevant (i.e., a positive match).
+An ensemble of ten models was fitted to improve prediction stability by averaging the PPD between models [@zhou2021ensemble; @dietterich2000ensemble].\
+
+To assign the labels, we employed an "active learning" [@settles2009active, @miwa2014reducing] approach, where a human reviews a specific subset of predictions made from the machine, which is then retrained on the manually reviewed dataset.
+This process proceeds iteratively, decreasing prediction uncertainty.\
+Label assignment is done through the identification of an "uncertainty zone" whose construction is possible thanks to the Bayesian nature of BART, which provides full PPDs instead of point-wise predictions for each record.\
 To describe the process formally, we define
 
-$$\pi_i = \frac{1}{M}\sum_{j=1}^MPr(L_i = \text{pos}|DTM,m_j)$$
+$$\pi_i = \frac{1}{M}\sum_{j=1}^MPr(L_i = \text{1}|DTM,m_j)$$
 
-as the PPD of a record $D_i$ being assigned a positive label ($L_i$), averaging the PPDs of the ensemble of $M=10$ models $m$, and
+as the PPD of a record $D_i$ being relevant (i.e, having a positive label, $L_i = 1$), averaging the PPDs of the ensemble of $M=10$ models $m$, and
 
-$$\pi_{i,l} = \{\pi_i : Pr(\pi_i) = 1\%\}\\
-\pi_{i,u} = \{\pi_i : Pr(\pi_i) = 99\%\}$$
+$$
+\begin{aligned}
+\pi_{i,l} = \{\pi_i : Pr(\pi_i) = 1\%\}\\
+\pi_{i,u} = \{\pi_i : Pr(\pi_i) = 99\%\}
+\end{aligned}
+$$
 
-as respectively the lower and upper boundaries of the 98% quantile interval of $\pi_i$ (98% predictive interval, 98% PrI).\
-Then we identify the "uncertainty zone"
+as respectively the lower and upper boundaries of the 98% quantile interval of $\pi_i$ (98% Predictive Interval, 98% PrI).\
+Then we identify the "uncertainty zone" as
 
-$$U_\pi=[\max_{D_i \in L_n}\pi_{i,u}, \min_{D_i \in L_p}\pi_{i,l}]$$
-
-that is, a range of $\pi$ values between the smallest $\pi_{i,l}$ in the set of already labelled positive records $L_p$ and the largest $pi_{i,u}$ related to the negative ones $L_n$, noting that the two limits can appear in any order.\
+$$U_\pi=[\max\vec{\pi}_{u}^-, \min\vec{\pi}_{l}^+]$$
+with $\vec{\pi}_{u}^-$ being the vector of $\pi_{i,u}$ with a negative label and $\vec{\pi}_{l}^+$ the vector of $\pi_{i,l}$ with a positive label.
+That is, $U_\pi$ defines a range of values between the smallest $\pi_{i,l}$ in the set of already labelled positive records $L_p$ and the largest $pi_{i,u}$ related to the negative ones $L_n$, noting that the two limits can appear in any order.\
 Consequently, a record $D_i$ will be labelled as positive if
@@
 
-that is, its lower 98% PrI boundary should be higher than every value in the uncertainty zone.
+that is, the record lower 98% PrI boundary should be higher than every value in the uncertainty zone.
 In other words, for a record to be labelled positive, its PPD should be within the range of the mixture of PPD of the previously labelled positive records and not cross the distributions of the negative records.\
@@
 
-$$\pi_{i,u} > \min_{\pi \in U_\pi} \pi$$
+$$\pi_{i,u} < \min_{\pi \in U_\pi} \pi$$
 
-All other records are labelled as uncertain and will require manual labelling.
-Also, positive labelled records are to be reviewed to avoid false positives.
-Furthermore, if a predicted label differs from the existing one, a manual check will be required; this could identify uncertainty in the labelling criteria of the same researcher or between different researchers.
+All other records are labelled as "uncertain".
 
-The automatic classification task and the manual review step form an iterative loop (CR iterations).
-The whole algorithm falls in the pattern defined as active machine learning [@settles2009active, @miwa2014reducing], with the machine querying the user to address and progressively resolve uncertainty in the classification.\
-The CR iterations continue until no new positive matches are found in four consecutive iterations.
-The framework supports alternative stopping conditions like limits on the fraction or number of total records reviewed and on the total number of positive matches found.
+Manual review is then necessary for: 1) uncertain records, 2) positive records (to avoid false positives), 3) records whose predicted label differs from the existing manual one.
+The last case helps identify human errors or inconsistent labelling criteria.
+
+The automatic classification and the manual review steps alternate in a loop (CR iterations) until no new positive matches are found in four consecutive iterations.
 
 ### New search query generation
-We created an algorithm that helps create a new search query that could detect further relevant publications missed during the first search, possibly at a reasonable cost in specificity (i.e., a higher number of negative results).\
+We created an algorithm that generates a new search query to acquire further relevant publications missed during the first search, possibly at a reasonable cost in specificity (i.e., a higher number of negative results).\
 The algorithm encompasses a number of steps:
 
-* We fit a partition tree [@rpart] between the DTM and 800 samples from the PPD; if a term is present multiple times in the DTM (e.g.
-both title and abstract), they are counted just one, and field term count features are removed.
-This step generates a list of rules composed by $AND$/$NOT$ "conditions" made of terms/authors/keywords/MESH, which together identify a group of records.
-* For each rule, we add a set of negative conditions ($NOT$ statements in the rule), removing non-relevant records in a group: a condition removing the largest number of non-relevant records is found, and then iteratively, more are added with the same logic, until no conditions are found that would not also remove positive records.
-* The extended set of rules is sorted by the difference between the number of positive and negative records they identify in descending order.
-Given this ordered list, the cumulative number of unique positive records is computed and used to group the rules: each rule in the same group of rules adds the same number of positive records to the preceding group but are ordered according to the number of negative records they identify.
-* These groups of rules are outputted, and the researcher is asked to review them, selecting one or more (useful if they convey radically different meaning) rules from each group, or edit them (in case too specific positive or negative conditions were included).
-By default, the framework suggests keeping the first rule of each group since it would identify the lower number of non-relevant records for the same number of positive one (.e., higher specificity).
-It is possible to exclude a group of rules altogether, especially the last ones with very low positive/negative records ratios.
+* We fit a partition tree [@rpart] between the DTM and 800 samples from the PPD;
+if a term is present multiple times in the DTM (e.g. both title and abstract), they are counted just one, and field term count features are removed.
+This step generates a list of rules composed by $AND$/$NOT$ "conditions" made of terms/authors/keywords/MESH tokens, which together identify a group of records.
+* For each rule, negative conditions (i.e., $NOT$ statements) are added iteratively, starting from the most specific one, until no conditions are found that would not also remove positive records.
+* The extended set of rules is sorted by positive-negative record difference in descending order.
+The cumulative number of unique positive records is computed and used to group the rules.
+Rules inside each group are ordered by specificity.
+* The researcher is then asked to review the rule groups, selecting one or more rules (useful if they convey different meaning) from each, or edit them (in case too specific positive or negative conditions were included).
+It is possible to exclude a group of rules altogether, especially those with the worse sensitivity/specificity ratio.
 * The selected rules are joined together by $OR$ statements, defining a subset of records with a sensibly higher proportion of positive records than the original one.
-* Given this data set, the next step removes redundant rules (i.e., rules whose positive records are already included in more specific ones) and conditions (i.e., conditions that once removed do not decrease the total number of positive or do not increase the negative records).
-* Finally, the rules are re-elaborated in a format usable on the major scientific databases.
-Since the algorithm is data-driven and creates rules that are specific for the dataset but may be not once applied to comprehensive research databases, we added a new subquery in $AND$ specifying the general topics of our search.
+* Redundant rules (i.e., rules whose positive records are already included in more specific ones) and conditions (i.e., conditions that once removed do not decrease the total number of positive or do not increase the negative records) are removed.
+* Finally, the rules are re-elaborated in a query usable on the major scientific databases.
 
-### Hyperparameter search
-The machine learning model behind the algorithm has a number of hyperparameters in addition to the BART specific ones: the number of ensemble models, the source of randomness between models (just derived from MCMC sampling, the default, or whether to bootstrap the data first), the oversampling of positive records, the PrI quantiles, the number of initial manually labelled records.
-These parameters have a relevant effect on the algorithm performance.\
-We set up a grid search to evaluate the parameters on a subset made of the first 1200 records from the first session; these records were fully labelled as relevant or not.
-We run the framework for each combination of parameter values, automatizing the manual review part using the already collected labels.
-The framework ran until four CR iterations with no positive records were returned, or the whole dataset was labelled.\
-For each combination, a performance score was computed as the product of *Efficiency* (1 minus the ratio of records that required review over the total) and *Sensitivity* (number of positive records found over the total of positives).
-We then identified homogeneous "performance clusters" of parameter values using a decision tree on the score.
-For the final analysis, we chose the best cluster of parameter value combinations and, inside the cluster, the best combination in order of Sensitivity and Efficiency.
+Since the algorithm is data-driven, it creates queries that effectively select positive records from the input dataset but may be not specific enough once applied to actual research databases.
+Therefore we appended an extra subquery in $AND$, which specifies the general topics of our search and delimitates the search domain.\
+The new query was used to initiate a second search session.
 
 ### Performance evaluation
-Each literature corpus is unique per database/search query, so we did noWe focused on estimating the expected total sensitivity in the dataset, using a surrogate [] Bayesian logistic regression to model the record labels on the lower bound of the [98% PrI] produced by our algorithm and then using this last model to produce a predictive cumulative distribution of the number of missed positive records.
-For this model, we used weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).
-Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing a plausible worst-case scenario.
-The quality of the model was evaluated through Bayesian $R^2$ [@gelman2019r] of which we reported the posterior median and 90% Credible Interval [90% CrI].\
-The predictive distribution of the number of missed positive records allows to estimate the expected long-run *Sensitivity* and the *Work saved over random* (WSoR) of the algorithm.
-The WSoR is based on a negative hypergeometric model to estimate the number of records to manually label to find the same number of positives if records were evaluated in random order [@chae1993presenting]; the WSoR is then one minus the ratio of the reviewed records over this number.
-For the number of predicted positive records, the sensitivity and WSoR, we reported the truncated 90% PrI [trunc.
-90% PrI], which is the uncertainty interval bounded at the number of observed total positive records: since each positive match is manually verified, the probability of a number of total positive records lower than observed is zero.
+We trained a simple Bayesian logistic regression (surrogate model) on the reviewed records to evaluate the classification model consistency (see Discussion for the theoretical justification).
+The surrogate model uses as predictor the lower bound of the 98% PrI of the records' PPD with weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).\
+The quality of the model was evaluated through Bayesian $R^2$ [@gelman2019r], of which we reported the posterior median and 90% Credible Interval [90% CrI].
+The $R^2$ also provides an evaluation of the consistency of the original classification model.
+Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing plausible worst-case scenarios.\
+The surrogate model is then used to generate the predictive cumulative distribution of the number of missed positive records in the whole dataset.
+This distribution allows estimating the expected total posterior "Sensitivity" and the "Work saved over random" (WSoR) of the classification model in the full (unreviewed) dataset.
+The WSoR is one minus the number of records to manually label at random to find the same number of positives; this last quantity is estimated through a negative hypergeometric distribution [@chae1993presenting].\
+For the number of predicted positive records, the sensitivity and the WSoR, we reported the "truncated 90% PrI" [trunc.
+90% PrI], which is the uncertainty interval bounded at the number of observed total positive records (i.e., there cannot be less predicted positive records than observed).
+
+### Hyperparameter evaluation
+Our classification algorithm has a number of hyperparameters:
+
+* The number of ensemble models;
+* The source of randomness between models in the ensemble, that is, either MCMC sampling only [@robert2004monte], or MCMC plus data bootstrapping [@breiman1996bagging] before training;
+* The oversampling rate of positive records;
+* The PrI quantiles to define the uncertainty zone;
+* The size of the initial training set.
+
+To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled subset made of the first 1200 records from the first session dataset.
+See Supplemental Material S1 for the combinations of hyperparameter used and other details on the method.\
+The framework tested each hyperparameter combination until four CR iterations with no positive records were returned or the whole dataset got labelled.\
+For each combination, a performance score was computed as the product of *Efficiency* (1 minus the ratio of records that required review over the total) and *Sensitivity* (number of positive records found over the total of positives).
+We then identified homogeneous "performance clusters" of hyperparameter values and scores using a partition tree.
+For the rest of our study, we chose the best cluster of parameter value combinations and, inside the cluster, the best combination according to Sensitivity and Efficiency in this order.

### 2021-10-20 Manuscript/S1.Protocol.Rmd
update

@@
 
-# Initial query to be built on domain knowledge
+# Initial query to be built on domain knowledge. It accepts OR, AND, NOT boolean
+# operators and round brackets to group terms.
 query <- '((model OR models OR modeling OR network OR networks) AND
@@
 
-`perform_search_session()` will use common scientific research database APIs (at the moment Pubmed/Medline, Web of Science and IEEE) to look for records related to query, store them in a csv format and returns or update **journal** (a csv or excel file) with all the information about sessions, queries and search results.
-The records will be stored in folders with the following structure: `Records/session_id/query_id`.
-Some API requires API key to access the data.
-These keys can be stored in the `secrets.R` file with the following example code (the "baysren" prefix identify the package specific options):
+`perform_search_session()` will use common scientific research database APIs (at the moment Pubmed/Medline, Web of Science and IEEE) to acquire records related to the query.
+The records will be stored as CSV files in folders with the following structure: `Records/session_id/query_id`, created automatically.
+The function also creates or update a **journal** (a CSV or Microsoft Excel file) with all the information about sessions, queries and search results.\
+Some services (IEEE, WOS) requires API key to access the data; an API key is not mandatory for Pubmed but can help avoid quota limitations in case of a large number of results.
+IEEE can also be searched without API;
+the framework will utilize a webscraping engine in case the API key is missing, but the success of this method is not guaranteed.
+See Supplemental Material S3 for detailed instruction on preliminary steps and tips for each supported search engine.
+These keys can be stored in the `secrets.R` file with the following example code (the "*baysren*" prefix identify the package specific options):
 
@@
 
-If manually downloaded results are available, users can create the `Record` folder manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`), and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g.
+If previously downloaded results are already available, users can create the `Record` folder manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`), and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g.
 `Pubmed1.nbib`, `Pubmed2.nib`, etc.).
@@
 	n_init = c(50, 100, 250, 500),
-	n_models = c(5, 10, 20, 40, 60),
+	n_models = c(1, 5, 10, 20, 40, 60),
 	pos_mult = c(1, 10, 20),

### 2021-10-20 Manuscript/Manuscript_Introduction.Rmd
split into separate lines per sentence. other minor edits

--- 2021-09-21 Manuscript/Manuscript_Introduction.Rmd
@@
 Consequently, it gets harder for researchers and practitioners to stay up-to-date on the latest findings in their field.
-Secondary research is of paramount relevance in this scenario, providing valuable summaries of the state of the art, but is getting ever more demanding in terms of time and human resources [@allen1999estimating; @borah2017analysis; @cohen2010evidence; @bastian2010seventy].\
-The article collection and screening phases of a systematic review are particularly problematic tasks [systematic review tutorial].
-First, relevant published research needs to be collected from scientific databases through appropriately built search queries.
-The construction of search queries is a particularly delicate task [@lefebvre2011searching; @hammerstrom2010searching], requiring both domain and some knowledge of the databases' query languages; the goal is to produce a set of results containing all relevant articles (high sensitivity) while keeping the total number low (high specificity), focusing on the first aspect at the cost of the second [@hammerstrom2010searching].
-If an integrated search tool is not used, manual work is required to download, store and organize the publication data.
-Searching manually may be complicated by limits in the number of records that can be downloaded at once [] and the necessity to harmonize different formats and resolve duplication.
-The citation screening phase consists of classifying the collected publications as relevant or not for the topic of interest [@bannach2019machine].
-It is usually the more resource-demanding task of a systematic review: even with appropriately built search queries, the returned results easily range in the tens of thousands of which just a small fraction is actually relevant [@lefebvre2011searching].
-It was estimated that labelling 10 000 publications may take as much as 40 weeks of work, while the average clinical systematic review takes 63 weeks to be completed [@bannach2019machine; @borah2017analysis; @allen1999estimating].
+Secondary research is of paramount relevance in this scenario, providing valuable summaries of the latest research results, but is getting ever more demanding in terms of time and human resources [@allen1999estimating; @borah2017analysis; @cohen2010evidence; @bastian2010seventy].\
+The article collection and screening phases of a systematic review are particularly demanding [@babar2009systematic].
+First, relevant published research needs to be collected from scientific databases through appropriately built search queries (retrieval phase); secondly, the acquired scientific citations need to be screened, selecting only those relevant to the topic (appraisal phase) [@bannach2019machine; @tsafnat2014systematic; @higgins2019cochrane].\
+The construction of search queries is a complex task [@lefebvre2011searching; @hammerstrom2010searching], requiring both domain and some knowledge of the databases' query languages;
+the goal is to produce a set of results containing all relevant articles (high sensitivity) while keeping the total number low (high specificity), focusing on the first aspect at the cost of the second [@hammerstrom2010searching].
+If an integrated search tool is not used, manual work is required to download, store and organise the publication data;
+this approach is complicated by limits in the number of records that can be downloaded at once and the necessity to harmonise different formats and resolve record duplication [@marshall2015systematic].\
+The citation screening phase is usually the more resource-demanding task of a systematic review:
+even with appropriately built search queries, the returned results easily range in the tens of thousands of which just a small fraction is actually relevant [@lefebvre2011searching].
+It was estimated that labelling 10,000 publications may take as much as 40 weeks of work and that the average clinical systematic review takes 63 weeks to be completed [@bannach2019machine; @borah2017analysis; @allen1999estimating].
 A consequence is that often systematic reviews are already outdated once they are published [@beller2013systematic].\
 The field of Data Science applied to evidence synthesis and acquisition has greatly maturated in the last years [@marshall2015systematic; @beller2018making; @tsafnat2014systematic].
-Through the application of natural language processing (NLP), it is possible to transform free text into quantitative features, with various levels of abstraction and generalization [@ananiadou2006text; @cohen2008getting]; with machine learning (ML), such text-derived data can be used to map and reproduce human judgment and automatize the citation screening [@ikonomakis2005text].
-One of the most successful approaches to text screening is active ML: researchers review the predictions made by the ML algorithm, focusing on the most uncertain predictions ("uncertainty" based active ML)  or on those giving a document a higher probability of being relevant ("certainty" based active ML) [@miwa2014reducing].\
-The automatization of systematic reviews has been ripe with improvements in the last years, and it is possible to foresee that such techniques will become a standard approach [@beller2018making].
+Through the application of natural language processing (NLP), it is possible to transform free text into quantitative features, with various levels of abstraction and generalisation [@ananiadou2006text; @cohen2008getting];
+with machine learning, such text-derived data can be used to map and reproduce human judgment, automating the citation screening [@ikonomakis2005text].
+One of the most successful approaches to text screening is active machine learning:
+researchers review the predictions made by the learning algorithm, focusing on the most uncertain predictions ("uncertainty" based active machine learning) or on those giving a document a higher probability of being relevant ("certainty" based active ML) [@miwa2014reducing].\
+The automatisation of systematic reviews has been ripe with improvements in the last years, and it is possible to foresee that such techniques will become a standard approach [@beller2018making].
 See @ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating for in-depth evaluations of research in this field.
@@
 Despite the significant advances, each method has various shortcomings, both in usability and efficiency [@o2015using].
-We tried to address some of these limitations by creating an integrated framework that tries to simplify systematic reviews in innovative ways: our framework provides solutions for automatic citation collection and management from multiple online sources and a Bayesian, active machine learning-based tool to support humans in the screening task, exponentially reducing the number of records to review.
+We tried to address some of these limitations by creating an integrated framework that tries to simplify systematic reviews in innovative ways:
+we provide solutions for automatic citation collection and management from multiple online sources and a Bayesian, active machine learning-based tool to support humans in the screening task, exponentially reducing the number of records to review.
 In particular, we exploit the characteristics of Bayesian analysis to overcome the shortcoming of both "certainty" and "uncertainty" based active learning and the difficulties in defining stopping rules [@miwa2014reducing].
 Finally, we propose an experimental method to semi-automatically generate efficient search queries given an already labelled set of publications.\
-We apply this solution in the production of a systematic review evaluating the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms with a focus on antimicrobial-resistant strains.
-The systematic review protocol is published in [].
+We tested the framework in the retrieval and appraisal phases of an example topic of interest for our group:
+the evaluation of the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms.
+The actual protocol of this systematic review is published in [@newis].\
+We give an overview of the framework in the Methods section;
+in the Result section, we show the framework outputs and performance once applied to the example topic; in the Discussion,
+we lay out the methodological justification behind the different components and features of the framework.

### 2021-10-21 Manuscript/Manuscript_Methods.Rmd
Switched medline to pubmed and added reference about api and web search giving different results

@@
 We built a set of tools to let users automatically search and download citation data from three major scientific databases ("sources"):
-MEDLINE (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
+Pubmed (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
 The framework takes care of authorization management for non-open databases like WOS and IEEE.
@@
 this is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/search/form.uri?display=basic#basic>) and EMBASE databases (<https://www.embase.com/#advancedSearch/default>), for which a comprehensive API interface was not easy to build.
+An extra manual search was necessary also for Pubmed, since the API and the web interface have different rule expansion algorithms and return slightly different results [@pubmedUpdate].
 A short guide on how to set up the framework for each supported database is available in Supplemental Material S3.\

### 2021-10-21 R/Reporting.R
feat: updated reporting of variable importance
The inclusion stability score was included and the text representation shows all data.

@@ -672,13 +672,14 @@ format_var_imp <- function(var_imp, as_data_frame = TRUE) {
 				factor(c('ABSTR', 'TITLE', 'AUTH', 'KEYS', 'MESH'),
 							 c('Abstract', 'Title', 'Author', 'Keyword', 'Mesh term')),
 			Term = str_replace_all(Term, c('^\\w+__' = '', '\\._\\.' = ' & ', '\\.' = ' | ', '_' = ' ')) %>% str_to_title(),
-			'Value (on 10K trees)' = signif(Value * 10000, 3),
+			'Inclusion rate' = signif(Value * 10000, 3),
+			IS = signif(Score, 3),
 			RR = signif(exp(estimate), 3) %>% str_remove('\\.?0+$'),
-			`Statistic (s.e.)` = signif(statistic, 3) %>% str_remove('\\.?0+$'),
+			`Statistic` = signif(statistic, 3) %>% str_remove('\\.?0+$'),
 		)
 
 	if (!as_data_frame) {
-		var_imp <- 	with(var_imp, glue('{Term} ({Component}): {`Value (on 10K trees)`} [{`Statistic (s.e.)`}]'))
+		var_imp <- 	with(var_imp, glue('{Term} ({Component}): {`Value (on 10K trees)`} ({IS}) [{RR}, {`Statistic (s.e.)`}]'))
 	}
 
 	var_imp

### 2021-10-21 R/Model.R
clean: code formatting

@@ -971,7 +971,11 @@ enrich_annotation_file <- function(session_name, file = NULL, DTM = NULL,
 		)
 	}) %>% bind_rows() %>%
 		group_by(Term) %>%
-		summarise(Value = mean(Val), Score = if (n_models > 1) Value / sd(Val) else Value, n_models = n())
+		summarise(
+			Value = mean(Val),
+			Score = if (n_models > 1) Value / sd(Val) else Value,
+			n_models = n()
+		)
 
 	message('Adding annotation summary')
 

### 2021-10-21 Manuscript/S2.Additional_outputs.Rmd
improved session on term relevance

@@
 
-In table 1 and 2 are listed the 50 more relevant terms used by the BART algorithm to discriminate between positive and negative records, for Session 1 and 2.
-Term importance ("Value" in the tables) is defined as the proportion over 10 000 posterior trees in which a term was used divided by the standard deviation of this value among each model repetition.
-The symbol "|" indicate synonyms while terms joined by "&" represent terms that are co-present in a document component The component in which the term was used is reported in the leftmost column.\
-Next to it, we added the relative risk of a positive match (RR) and statistical relevancy (measured as standard errors, s.e.) of the terms estimated through a Poisson regression, to evaluate its linear correlation with the probability of a positive match.
-A strong BART score with a low regression score identify terms whose effect is highly non linear (e.g., they are relevant only in the presence of other terms).
-
 ```{r var imp}
 
-var_importance_s1 <- extract_var_imp('Session1', num_vars = 50, score_filter = 0) %>%
+n_terms <- 50
+
+var_importance_s1 <- extract_var_imp('Session1', num_vars = n_terms, score_filter = 0) %>%
 	format_var_imp(as_data_frame = TRUE)
 
-var_importance_s2 <- extract_var_imp('Session1', num_vars = 50, score_filter = 0) %>%
+var_importance_s2 <- extract_var_imp('Session1', num_vars = n_terms, score_filter = 0) %>%
 	format_var_imp(as_data_frame = TRUE)
 ```
+
+In table 1 and 2 are listed the `r n_terms` more relevant terms used by the BART algorithm to discriminate between positive and negative records, for Session 1 and 2 (see Methods).
+Term importance ("Inclusion rate" in the tables) is defined as the ensemble average inclusion rate in posterior trees over 10,000 total term inclusions, while the Inclusion Stability (IS) is the ratio of the average inclusion rate over its standard deviation among the ensemble models.
+The symbol "|" in the terms indicate redundant terms while "&" indicate nc-grams.
+The component in which the term was used is reported in the leftmost column.\
+For each term, we added its linear association with a positive label estimated through a Poisson regression, reporting it as Relative Risk (RR) and its statistical significance (Statistic) measured as number of standard errors, s.e., of the terms.
+A strong BART score with a Statistic close to zero identify terms whose effect is highly non-linear (e.g., they are relevant only in the presence of other terms).
 

### 2021-10-21 Manuscript/Manuscript_Methods.Rmd
added missing newlines and added section on terms relevance

@@
 A series of Natural Language Processing (NLP) techniques [@baeza1999modern; @marshall2015systematic; @ananiadou2006text] are employed to transform the textual information in these fields into features for machine learning through a bag-of-words approach [@marshall2015systematic].
-The processing of free text fields (title, abstract) includes: tokenization (i.e., extracting the terms), common stopwords (i.e.
-sentence components bringing no meaning) removal, part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatization of the terms (i.e.
-reduction to their base grammar form).
+The processing of free text fields (title, abstract) includes: tokenization (i.e., extracting the terms), common stopwords (i.e., sentence components bringing no meaning) removal, part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatization of the terms (i.e., reduction to their base grammar form).
 Text processing for authors, keywords and MESH terms identifies logical units (e.g., author's full names, composite keywords) and extracts them.\
@@
 A second network is built using a co-occurrence threshold of 0.9.
-In this case, the cliques represent terms that always appear together and therefore can be considered redundant (i.e. they do not need to be considered separately).
+In this case, the cliques represent terms that always appear together and therefore can be considered redundant (i.e., they do not need to be considered separately).
 These terms are merged to increase computation efficiency and reduce overfitting.\
@@
 
+### Relevant terms' extraction
+BART model it is possible to extract the proportion of times a term was used in a posterior tree over the sum of total inclusions of all variables [@kapelner2013bartmachine], as a measure of feature importance for the model.
+We extracted the terms, the part of the citation data they were used in, the average "inclusion rate" among the ensemble models (over 10,000 inclusions) and its ratio over the standard deviation of this inclusion (inclusion stability, IS).
+For each term we ran a Poisson regression to get its linear association with a positive label and reported it as Relative Risk (RR) with the number of standard errors as significance index (Statistic);
+the comparison between the inclusion rate in the BART models and the linear association allows to spot relevant non-linear effects (i.e, the feature is relevant only in association with others).
+We reported in the Results only the first (in order of inclusion rate) 15 terms with IS > 1.5 while the first fifty terms regardless of inclusion stability are reported in Supplemental Material S2.
+
 ### New search query generation
@@
 * We fit a partition tree [@rpart] between the DTM and 800 samples from the PPD;
-if a term is present multiple times in the DTM (e.g. both title and abstract), they are counted just one, and field term count features are removed.
+if a term is present multiple times in the DTM (e.g., both title and abstract), they are counted just one, and field term count features are removed.
 This step generates a list of rules composed by $AND$/$NOT$ "conditions" made of terms/authors/keywords/MESH tokens, which together identify a group of records.
@@
 
-To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled subset made of the first 1200 records from the first session dataset.
+To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled "validation set" made of the first 1200 records from the first session dataset.
 See Supplemental Material S1 for the combinations of hyperparameter used and other details on the method.\
 The framework tested each hyperparameter combination until four CR iterations with no positive records were returned or the whole dataset got labelled.\
-For each combination, a performance score was computed as the product of *Efficiency* (1 minus the ratio of records that required review over the total) and *Sensitivity* (number of positive records found over the total of positives).
+For each combination, a performance score was computed as the product of "Efficiency" (1 minus the ratio of records that required review over the total) and "Sensitivity" (number of positive records found over the total of positives).
 We then identified homogeneous "performance clusters" of hyperparameter values and scores using a partition tree.

### 2021-10-21 Manuscript/Manuscript_Results.Rmd
update

@@
 
-The input search query was:\
+The input search query for the first session was:\
 
@@
 
-subsetting results between 2010 and 2020 (included).
-The automatic search tools were used for MEDLINE, WOS and IEEE, while a manual search and importation was necessary for EMBASE and SCOPUS.
-The search was repeated manually also for MEDLINE, since, as reported in the methods, the web interface may return different results from the API.
+selecting only results between 2010 and 2020 (included).
+Results were collected from Pubmed, WOS, IEEE, EMBASE and SCOPUS, using the framework tools as described in Methods and Supplemental Material S1.
 
-The first search session returned a total of `r all_records` unique records, specifically `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total` of the total) records from the *EMBASE* database, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from *Pubmed/Medline*, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from *Scopus*, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from *Web of Science*, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from *IEEE* (Table 1).
-There were various degrees of overlapping with the `r percent(1 - source_distr[1])` of records being present in more than one database and *EMBASE* and *IEEE* being the databases with the higher uniqueness ratios.
+The first search session returned a total of `r all_records` unique records, specifically `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total` of the total) records from the EMBASE database, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from Pubmed, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from SCOPUS, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from WOS, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from IEEE (Table 1).
+There were various degrees of overlapping between sources, with the `r percent(1 - source_distr[1])` of records being present in more than one database and EMBASE and IEEE being the databases with the higher uniqueness ratios.
 The final dataset was composed by `r source_summary$Total$Records` unique records.\
@@
 
-`r print_table(search_results, caption = "Table 1.
+`r print_table(search_results, caption = "**Table 1**.
 Distribution of retrieved records by source and session.
 For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total.
-SAll session shows records after joining and deduplication of the Session1 and Session2 dataset.")`
+SAll session shows records after joining and deduplication of the Session 1 and Session 2 dataset.")`
 
-After the first manual classification, `r n_review_rounds` automatic classification and manual review rounds (CR) were performed (Table 2).
-It is possible to observe how the number of records that required manual review dropped fast between iterations, indicating that the engine was converging while the uncertainties were resolved.\
-This phenomenon is better depicted in figure 1 in the Suppl.
-Mat.
-S2.
-It shows the mixture distribution of the predicted probabilities for each record, specifically for the reviewed positive and negative records, and for records that need manual review after the classification step: it can be noticed how the distribution of the uncertain records shrinks (they concentrate in a shorter probability range) and shifts toward the negative zone as more positive matches are found and reviewed.
+Records were joined into a database and arrange by simple query ordering;
+of these, the first 250 records were labelled to create the initial training set.\
+Using the classification model,`r n_review_rounds` automatic classification and manual review iterations (CR) were performed (Table 2).
+It is possible to observe how the number of records that required manual review dropped rapidly between iterations, indicating that the engine was converging while the uncertainties were resolved.\
+This phenomenon is better depicted in Fig. 1 of the Supplemental Material S2.
+It shows the mixture distribution of the PPD of the records, specifically for the reviewed positive and negative records, and for records that need manual review after the classification step:
+it can be noticed how the distribution of the uncertain records shrinks (they concentrate in a shorter probability range) and shifts toward the negative zone as more positive matches are found and reviewed.
 Accordingly (Table 2), the number of new positives found drops after the first couple of iterations.
-As per default, the classification process was stopped after four rounds with no new positive matches; a total number of `r num_last_positives` positives were found over `r tot_reviewed` manually reviewed records (`r percent(num_last_positives/tot_reviewed)` positivity rate).\
+As per default, the classification process was stopped after four rounds with no new positive matches;
+a total number of `r num_last_positives` positives were found over `r tot_reviewed` manually reviewed records (`r percent(num_last_positives/tot_reviewed)` positivity rate).\
 
-`r print_table(annotation_results, caption = "Table 2.
+`r print_table(annotation_results, caption = "**Table 2**.
 Results of the automatic classifaction and manual review rounds.
 For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown.
-Also, the number of changes after review and their description is reported.
-\"Unlab.\" indicates unlabelled records marked for review.
+Also, the number of changes after review and their description is reported.\"Unlab.\" indicates unlabelled records marked for review.
 For each Iteration, also the number of features used by the engine is reported.
 The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1.
-In Session2, the engine uses the labels at the end of Session1 to classify the newly added records.")`
+In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.")`
 
-By evaluating how often the BART algorithm decided to use a term for classification, it is possible to list a subset of the variables most relevant for the classification of the documents: `r var_importance`.
-In parenthesis, it is reported the part of the record in which the term was used, while the numeric values indicate respectively the rate of posterior trees (over 10000 trees) in which a term was used, and the number of standard errors of the association between a term and the probability of a positive match according to a simple logistic linear model (see methods).
-The "&" indicates that two terms are present together in a document but not close to each other.\
-The engine was able to pick up the central concept of the research (i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections) and even one of the authors of the current study (Donker T.) or the region of interest ("Orange County") of another research group active on the topic.
-It is interesting to see that some terms were considered highly relevant (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model, their effect would be hardly significant (statistic: -1.21 s.e.), and this highlight the extra predictive power brought by a highly non-linear model.\
+By evaluating how often a term was used by the classification model, it is possible to define their relevance in labeling the records (see Methods).
+Here follows the 15 most relevant terms by inclusion rate over 10,000 posterior tree inclusions, described as:
+Term (citation part): Inclusion Rate (Inclusion Stability) [linear Relative Risk, Statistic].
+
+`r var_importance`.
+
+The "&" indicates nc-ngrams, i.e., terms strongly co-occurrent in the documents.\
+The engine was able to pick up the central concept of the research, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) or the region of interest ("Orange County") of another research group active on the topic of healthcare asociated pathogen spreading over hospital networks.
+It is interesting to see that some terms were considered highly relevant for the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
+these are terms which are relevant only together with other terms but not by themselves, highlighting the extra predictive power brought by a non-linear model like BART.\
 A more extensive set of terms is presented in Table 1 of Supplemental Material S2.
@@
 
-The new search produced `r all_records` records (Table 1), of which `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total`) from the *EMBASE*, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from *Pubmed/Medline*, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from *Scopus*, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from *Web of Science*, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from *IEEE*; compared to the first session, the relative weight of *EMBASE* and *Pubmed* over the total was decreased, while the amount of content specificity was greatly increased, as it was for *Scopus*.
+The new search produced `r all_records` records (Table 1), of which `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total`) from the EMBASE, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from Pubmed, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from SCOPUS, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from WOS, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from IEEE;
+compared with the first session, the relative weight of EMBASE and Pubmed was decreased, while the amount of content specificity was greatly increased, as it was for SCOPUS.
 After removal of duplicates, `r source_summary$Total$Records` unique records were obtained.
@@
 -> y'])` new positive found after reviewing `r tot_reviewed - session_summary$tot_reviewed_[1]` extra records.
-It is interesting to notice that the first CR round required the user to review a substantial number of records (1273), but just labelling 275 of them (the canonical 250 plus 25 that were already labelled during the framework performance evaluation) was sufficient to drop this number to just 190 in the subsequent round.
-An evaluation of the convergence (Figure 1, Suppl.
-Mat.
-S2) showed that, in addition to the dynamics already observed in session 1 (shrinkage and negative shift), a second mode appeared in the mixture distribution of the records to be reviewed, centred in a highly positive zone.
-The interpretation is that as the number of negative training records increases, the engine gets more and more sceptical and asks to review even some records labelled as positive in the initial labelling at the beginning of session 1.
+The first CR iteration required the user to review a substantial number of records (1,273), but just labelling 275 of them (the canonical 250 plus 25 that were already labelled during the framework hyperparameter tuning) was sufficient to drop this number to just 190 in the subsequent round.
+An evaluation of the convergence (Figure 1, Supplemental Material S2) showed that, in addition to the dynamics already observed in session 1 (shrinkage and negative shift), a second mode appeared in the mixture distribution of the records to be reviewed, centred in a highly positive zone.
+The interpretation is that as the number of negative training records increases, the engine gets more and more skeptical and asks to review even some records labelled as positive in the initial training set in Session 1.
 This behaviour can be useful to spot classification errors and inconsistencies.
@@
 
-Again, the evaluation of the relative importance of the terms showed that the engine was quite capable of internalizing the concepts behind the research topic.
-A subsample of these terms is reported in Table 2 of Suppl.
-Mat.
-S2.
+Again, the evaluation of the inclusion rate of the terms showed that the engine was quite capable of internalizing the concepts behind the research topic
+A subsample of the terms is reported in Table 2 of Supplemental Material S2.
 
@@
 
-```{r performance, cache = FALSE}
+```{r hyperparameters}
 
@@
 	tidyr::pivot_wider(values_from = value, names_from = Parameter)
+```
+
+<!-- develop more in the methods, the data is not a random sample and it's ordered so performance evaluation needs to take this into account.
+also note that hyperparameter selection is necessary since even if bayesian methods are robust, the other parameters outside it are not-->
+
+As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a validation set of 1200 completely manually labelled records.
+The best set of parameters suggested an initial input of 250 labelled records with 10x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
+On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
+A summary of the results of the grid search is reported in Table 3 of Supplemental Material S2.
+
+### Performance evaluation
+
+```{r performance}
 
@@
 
-<!-- develop more in the methods, the data is not a random sample and it's ordered so performance evaluation needs to take this into account.
-also note that hyperparameter selection is necessary since even if bayesian methods are robust, the other parameters outside it are not-->
+To evaluate the theoretical performance of the engine, a surrogate Bayesian logistic regression model was trained on the manually reviewed labels using only the lower bound of the record PPDs as predictor (see Methods for details).
+The surrogate model show the high predictive power of the scores produced by the classification model (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2).\
 
-As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a subset of 1200 completely manually labelled records (validation set).
-The best set of parameters suggested an initial input of 250 labelled records with 10x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
-On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
-A summary of the results of the grid search is reported in Table 3 in Suppl.
-Mat.
-S2.
+Figure 2 presents the actual and predicted (from the surrogate model) cumulative number of positive matches, ordered by the initial simple ordering query:
+the median of surrogate models' cumulative predictive distributions matches quite well the actual number of positive records found.
+It is striking how many more records would have needed to be evaluated manually to find the same number of positive matches without using a smart classification tool;
+some relevant record was found even close to the end of the heuristically ordered list of records.\
 
-### Performance evaluation
+Table 3 shows various performance indexes for both sessions, both descriptive (Total records, Reviewed records, Observed positive matches) and estimated through the surrogate model (Expected efficiency, Predicted positive matches, Expected sensitivity, $R^2$).\
+In session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.
+In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows, even a small probability can translate, in the worst case scenario, into a relevant number of missed positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
+To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no additional positive matches.
 
-To evaluate the theoretical performance of the engine on the full datasets (i.e., session 1 and session 2 data), a Bayesian logistic model was trained on each session dataset to predict the label of the records from the probability estimated by the engine (see methods for details).
-The performance of such simple models is quite high (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2) and the median of their cumulative predictive distribution matches quite well the actual number of cumulative positive records found.
-The predicted cumulative number of positive matches was used to evaluate the performance in the non-reviewed records (Table 3).\
-
-Figure 2 shows the actual and predicted (from the logistic model) cumulative number of positive matches, ordered by the initial simple ordering query.
-As confirmed by the high efficiency values reported in Table 3, it is striking how many more records would need to be evaluated manually to find all positive matches without using a smart search tool.
-The engine was able to find matches even close to the end of the heuristically ordered list of records.
-Specifically, in session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.\
-In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows very large, even a small probability can translate, in the worst scenario, into a relevant number of predicted positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
-To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no actual positive matches.
-
-`r print_table(perf_table, caption = "Table 3.
+`r print_table(perf_table, caption = "**Table 3**.
 Estimated performance summary.

### 2021-10-21 R/Reporting.R
fix: in format_var_imp the text output didn't match the table one

@@ -679,7 +679,7 @@ format_var_imp <- function(var_imp, as_data_frame = TRUE) {
 		)
 
 	if (!as_data_frame) {
-		var_imp <- 	with(var_imp, glue('{Term} ({Component}): {`Value (on 10K trees)`} ({IS}) [{RR}, {`Statistic (s.e.)`}]'))
+		var_imp <- 	with(var_imp, glue('{Term} ({Component}): {`Inclusion rate`} ({IS}) [{RR}, {`Statistic`}]'))
 	}
 
 	var_imp

### 2021-10-21 Manuscript/Manuscript_Methods.Rmd
formatting

@@
 ### Record's acquisition and initial labelling
+
 We built a set of tools to let users automatically search and download citation data from three major scientific databases ("sources"):
@@
 ### Text feature extraction
+
 The collected citation data have a number of fields characterizing a scientific publication.
@@
 ### Label prediction
+
 We used a Bayesian Additive Regression Trees (BART) machine learning "classification model" [@chipman2010bart] [in the implementation of @kapelner2013bartmachine] to predict the probability of a record of being relevant, given the information coded into the enriched DTM and the initial training set.
@@
 ### Relevant terms' extraction
+
 BART model it is possible to extract the proportion of times a term was used in a posterior tree over the sum of total inclusions of all variables [@kapelner2013bartmachine], as a measure of feature importance for the model.
@@
 ### New search query generation
+
 We created an algorithm that generates a new search query to acquire further relevant publications missed during the first search, possibly at a reasonable cost in specificity (i.e., a higher number of negative results).\
@@
 ### Performance evaluation
+
 We trained a simple Bayesian logistic regression (surrogate model) on the reviewed records to evaluate the classification model consistency (see Discussion for the theoretical justification).
@@
 ### Hyperparameter evaluation
+
 Our classification algorithm has a number of hyperparameters:
@@
 For each combination, a performance score was computed as the product of "Efficiency" (1 minus the ratio of records that required review over the total) and "Sensitivity" (number of positive records found over the total of positives).
-We then identified homogeneous "performance clusters" of hyperparameter values and scores using a partition tree.
-For the rest of our study, we chose the best cluster of parameter value combinations and, inside the cluster, the best combination according to Sensitivity and Efficiency in this order.
+We then identified homogeneous "performance clusters" of scores given hyperparameter values using a partition tree.
+For the rest of our study, we chose the best cluster of parameter value combinations and, inside the cluster, the best combination according to Sensitivity and Efficiency, in this order.

### 2021-10-21 Manuscript/Manuscript_Results.Rmd
added extra description on hyperparam tuining results

@@
 On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
-A summary of the results of the grid search is reported in Table 3 of Supplemental Material S2.
+The results of the hyperparameter tuning are reported in Table 3 of Supplemental Material S2.
+Figure 2 in Supplemental Material S2 demonstrates that the positive record oversampling rate, the number of ensemble models and the size of the initial training set were the parameters that most impact performance.
 

### 2021-10-22 Manuscript/Manuscript_Methods.Rmd
put hyperparameter values in the Methods

@@
 
-* The number of ensemble models;
-* The source of randomness between models in the ensemble, that is, either MCMC sampling only [@robert2004monte], or MCMC plus data bootstrapping [@breiman1996bagging] before training;
-* The oversampling rate of positive records;
-* The PrI quantiles to define the uncertainty zone;
-* The size of the initial training set.
+* Size of the initial training set: 50, 100, 250, 500 records;
+* Number of models in the ensemble: 1, 5, 10, 20, 40, 60 repetitions;
+* Oversampling rate of positive records: (1x (i.e., no oversampling), 10x, 20x;
+* PrI quantiles for building the uncertainty zone: 80%, 90%, 98%;
+* Source of randomness between models in the ensemble: MCMC sampling only [@robert2004monte], MCMC plus data bootstrapping [@breiman1996bagging] of the training set.
 
 To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled "validation set" made of the first 1200 records from the first session dataset.
-See Supplemental Material S1 for the combinations of hyperparameter used and other details on the method.\
 The framework tested each hyperparameter combination until four CR iterations with no positive records were returned or the whole dataset got labelled.\
 For each combination, a performance score was computed as the product of "Efficiency" (1 minus the ratio of records that required review over the total) and "Sensitivity" (number of positive records found over the total of positives).
-We then identified homogeneous "performance clusters" of scores given hyperparameter values using a partition tree.
-For the rest of our study, we chose the best cluster of parameter value combinations and, inside the cluster, the best combination according to Sensitivity and Efficiency, in this order.
+We then identified homogeneous "performance clusters" of scores given hyperparameter values using a partition tree [@rpart].
+For the rest of the study, we used the best hyperparameter set in terms of Sensitivity followed by Efficiency from the cluster with the highest average score.

### 2021-10-22 Manuscript/S2.Additional_outputs.Rmd
update

@@
 output:
-  # pdf_document:
-  #   toc: yes
-  #   includes:
-  #     in_header: header.tex
+  pdf_document:
+    toc: yes
+    includes:
+      in_header: header.tex
   github_document:
@@
 
-Figure 1 show the mixture of the predictive distribution of the probability of a positive match, grouped by labelling status.
-The posterior samples for each record were extracted and joined in a global distribution; on this distribution, density was computed on the logit scale and then logistic transformed for display on a $[0 - 1]$ scale.
-The light violet ridges show the distribution of the still unlabelled records.\
-For each iteration, the thresholds which define the lower and the upper range of 98% predictive interval (PrI) respectively for the positive and negative records are shown.
-The zone included between these two boundaries defines the uncertainty zone; records whose 98% PrI intersects this zone requires manual review.\
-Notice how the positive and negative densities start overlapping starting with the second iteration of Session 2.
-Meanwhile the distribution of the records to be reviewed shrink and shift towards the negative side, as positive records get found and labeled.
+Figure 1 show the mixture of the PPD of the probability of a positive match, grouped by label (only records manually labelled or reviewed are considered).
+The posterior samples for each record were extracted and joined into a global distribution;
+on this distribution, density was computed on the logit scale and then logistic transformed for displaying on a $[0 - 1]$ scale.
+The purple ridges show the distribution of the still unlabelled records.\
+For each iteration, the thresholds which define the "uncertainty zone", i.e, the lower and the upper range of 98% PrI for the positive and negative records respectively, are shown.
+Records whose 98% PrI intersects the uncertainty zone requires manual review.\
+Notice how the positive and negative record densities tend to increasingly overlap at each iteration;
+meanwhile the distribution of the records to be reviewed shrinks and shifts towards the negative side, as positive records get found and labeled.\
+In Session 2, as the number of negative records reviewed increased, also already positively labelled records re-entered the uncertainty zone;
+this is due to the baseline positivity rate decreasing as the number of negatives in the training data increased, forcing to review dubious records that may have been mislabelled.
 
@@
 
-To select the engine hyperparameter set which would maximize sensitivity and efficiency, we set up a comprehensive grid search by running the algorithm on a fully labeled dataset of 1200 records.
-Using a partition tree algorithm we grouped the searches in a number of clusters with similar performance and selected the best parameter set in the best cluster.\
-Table 3 shows the best parameter set and their performance for each cluster while figure 2 displays the conditional impact on performance of each parameter.
+Table 3 shows the best hyperparameter set and their performance for each cluster while figure 2 displays the conditional impact on performance of each hyperparameter.
+
+The most influential parameters were the number of models in the ensemble, the oversampling rate and the initial training set size. The use of bootstrap resampling seemed detrimental.
 
 ```{r hyperparameters, fig.width=17, fig.height=10, fig.cap="Figure 2.
-Performance clusters and impact of single hyperparameters on engine performance.
+Score clusters and impact of single hyperparameters on engine performance.
 The performance is measured as Sensitivity x Efficiency.
 Each cluster is color coded.
-Mods: num.
-of models in the ensemble; Quant: uncertainty zone interval to trigger manual review; Resamp: bootstrap resampling; Init: num.
-of initial training records; Multi: oversampling multiplier of positive matches."}
+Mods: number of models in the ensemble; Quant: PrI quantiles for the uncertainty zone; Resamp: bootstrap resampling between models; Init: size of initial training set; Multi: oversampling rate of positive records"}
 

### 2021-10-22 R/Analysis.R
fix: error in best parameter set per cluster selection

@@ -433,8 +433,6 @@ analyse_grid_search <- function(session_folder = 'Grid_Search', tot_pos = NULL,
 		iterations = out,
 		best_parms = out %>% filter(str_detect(Rule, '^1\\.')) %>%
 			arrange(desc(Sensitivity), desc(Efficiency)) %>% head(1) %>%
-			# slice_max(Sensitivity, n = 1, with_ties = T) %>%
-			# slice_max(Score, n = 1, with_ties = F) %>%
 			select(Iter, Rep, Pos_labels, Sensitivity, Tot_labeled, Efficiency,
 						 Score, any_of(params)) %>%
 			mutate(
@@ -446,11 +444,7 @@ analyse_grid_search <- function(session_folder = 'Grid_Search', tot_pos = NULL,
 				across(.fns = as.character)) %>%
 			tidyr::pivot_longer(everything(), names_to = 'Parameter', 'Value'),
 		best_by_rule = out %>% group_by(Cluster = Rule) %>%
-			slice_max(Score, n = 1, with_ties = T) %>%
-			slice_max(Sensitivity, n = 1, with_ties = T) %>%
-			slice_max(Efficiency, n = 1, with_ties = F) %>%
-			# ungroup() %>%
-			# arrange(desc(Score), desc(Sensitivity), desc(Efficiency)) %>%
+			arrange(desc(Sensitivity), desc(Efficiency)) %>% slice_head(n = 1) %>%
 			select(Cluster, Iter, Pos_labels, Tot_labeled, Sensitivity, Efficiency,
 						 Score, any_of(params)) %>%
 			mutate(

### 2021-10-25 R/Reporting.R
feat: print_table manages latex commands and other non-compliant symbols

@@ -566,7 +566,7 @@ format_performance <- function(..., session_names = NULL) {
 				#Session = session_names[i],
 				'Total records' = total_records,
 				'Reviewed records (% over total records)' = glue("{n_reviewed} ({percent(n_reviewed/total_records)})"),
-				'Expected efficiency (over random) [trunc. 90% CrI]' = efficiency %>% format_interval(percent = TRUE),
+				'Expected efficiency (over random) [trunc. 90% PrI]' = efficiency %>% format_interval(percent = TRUE),
 				'Observed positive matches (% over total records)' = glue("{obs_positives} ({percent(obs_positives/total_records)})"),
 				'Predicted positive matches [trunc. 90% PrI]' = pred_positives %>% format_interval(),
 				'Expected sensitivity [trunc. 90% PrI]' = sensitivity %>% format_interval(percent = TRUE),
@@ -687,8 +687,13 @@ format_var_imp <- function(var_imp, as_data_frame = TRUE) {
 
 print_table <- function(data, caption = '') {
 	if (knitr::is_latex_output()) {
-		knitr::kable(data, "latex", booktabs = T,
-								 caption = caption %>% str_squish()
+	data %>%
+			mutate(across(where(is.character), ~ str_replace_all(.x, '%', '\\\\%'))) %>%
+			dplyr::rename_with(~ str_replace_all(.x, '%', '\\\\%')) %>%
+		knitr::kable(format = "latex", booktabs = T,
+								 caption = caption %>% str_squish() %>%
+								 	str_replace_all(c('%' = '\\\\%', '\\*\\*([^\\n]+)\\*\\*' = '\\\\textbf{\\1}')),
+								 escape = FALSE
 								 #format.args = list(floating = FALSE)
 		) %>%
 			kableExtra::kable_styling(

### 2021-10-25 Manuscript/Manuscript.Rmd
update

--- 2021-01-19 Manuscript/Manuscript.Rmd
@@
 ---
-title: "Manuscript"
-author: "Angelo D'Ambrosio"
-date: "12/1/2021"
+title: Main manuscript
+authors:
+  - name: David S. Hippocampus
+    thanks: Use footnote for providing further information about author (webpage, alternative address)---*not* for acknowledging funding agencies. Optional.
+    department: Department of Computer Science
+    affiliation: Cranberry-Lemon University
+    location: Pittsburgh, PA 15213
+    email: hippo@cs.cranberry-lemon.edu
+  - name: Elias D. Striatum
+    department: Department of Electrical Engineering
+    affiliation: Mount-Sheikh University
+    location: Santa Narimana, Levand
+    email: stariate@ee.mount-sheikh.edu
+abstract: |
+  Enter the text of your abstract here.
+keywords:
+  - blah
+  - blee
+  - bloo
+  - these are optional and can be removed
+bibliography: references.bib
 output: 
-  github_document
+  rticles::arxiv_article:
+    number_sections: no
+    keep_tex: true
+    includes:
+      in_header: header.tex
 ---
 
-```{r Setup, include=FALSE}
+```{r, echo=FALSE, results='asis', message = FALSE, warning = FALSE, error = FALSE, dpi = 400, fig.width=12, fig.height=5}
 
-knitr::opts_knit$set(root.dir = ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd()))
+getOption("mc.cores", parallel::detectCores())
 
-knitr::opts_chunk$set(
-	echo = FALSE,
-	error = FALSE,
-	message = T,
-	warning = FALSE,
-	dpi = 400
-)
+out <- unlist(lapply(c(
+	'Manuscript_Introduction.Rmd',
+	'Manuscript_Methods.Rmd',
+	'Manuscript_Results.Rmd',
+	'Manuscript_Discussion.Rmd'
+), knitr::knit_child, quiet = TRUE))
 
-source('Setup.R')
-
-if (!file.exists('annotation_summary.rds')) {
-	annotation_summary <- summarise_annotations(annotation.folder = "Annotations", plot = F)
-
-	saveRDS(annotation_summary, 'annotation_summary.rds')
-} else annotation_summary <- readRDS('annotation_summary.rds')
+cat(out, sep = '\n')
 
@@
 
-## Results
+\newpage
 
-```{r Results}
-
-summary_table <- bind_rows(
-    annotation_summary %>%  filter(Ord == 1) %>% mutate(Ord = 0, File = 'Input_P_R', Value = replace(Value, !str_detect(Label, 'Reviewed'), 0)),
-    annotation_summary 
-) %>% 
-    filter(Label != 'Discordant') %>% 
-    mutate(
-        Task = case_when(str_detect(File, 'P_R') ~ 'R', T ~ 'P'),
-        Ord = Ord + 1
-    ) %>% 
-    select(Ord, Value, Total_records, Label, Task, Batch) %>% 
-    tidyr::pivot_wider(names_from = Label, values_from = Value) %>% 
-    transmute(
-        Task = Ord,
-        Task_type = .$Task,
-        across(c(Reviewed_positive, Reviewed_negative), ~ sapply(Task, function(i) {
-            ret = ''
-            if (Task_type[i] == 'R' & i != 1) {
-                prev.i <- max(Task[Task < i])
-
-                diff <- .x[i] - .x[prev.i]
-
-                if (diff != 0) ret <- paste0(' ', ifelse(diff > 0, '+', ''), diff)
-            }
-            ret
-        }), .names = "new_{.col}"),
-        Uncertain = ifelse(
-            Task_type == 'R',
-            '',
-            sprintf('%d (%s)%s', Uncertain, percent(Uncertain/Total_records), ifelse(New_uncertain > 0 , paste0(' +', New_uncertain), ''))
-        ),
-        Positive = ifelse(
-            Task_type == 'R',
-            sprintf('%d (%s)%s', Reviewed_positive, percent(Reviewed_positive/Total_records), new_Reviewed_positive),
-            sprintf('%d (%s)%s', Positive, percent(Positive/Total_records), ifelse(New_positive > 0, paste0(' +', New_positive), ''))
-        ),
-        Negative = ifelse(
-            Task_type == 'R',
-            sprintf('%d (%s)%s', Reviewed_negative, percent(Reviewed_negative/Total_records), new_Reviewed_negative),
-            sprintf('%d (%s)', Negative, percent(Negative/Total_records))
-        ),
-        Reviewed = ifelse(Task_type == 'R', Reviewed, ''),
-        Batch = factor(Batch) %>% as.numeric(),
-        New_rev_pos = NULL
-    ) %>% select(-matches('new')) %>% rename(`Task type` = Task_type) %>% group_split(Batch) %>% lapply(function(df) select(df, -Batch))
-```
-
-### First search session
-
-```{r Result 1}
-
-first_batch <- "Records_2020-12-11"
-
-first_query_file <- file.path("Annotations", first_batch, "Records_11.12.20.xlsx")
-
-sources_first_query <- summarise_by_source(first_query_file) %>% as.list()
-
-first_annotation_results <- annotation_summary %>%
-	filter(Ord == 1, str_detect(Label,'Reviewed')) %>% {
-		df <- .
-		df$Value %>% setNames(df$Label) %>% as.list()
-	}
-
-new_uncertains <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_uncertain') %>% pull(Value) %>% sum()
-
-new_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_positive') %>% pull(Value) %>% sum()
-
-all_unique_reviews <- annotation_summary %>% filter(Batch == first_batch & Label == 'Reviewed') %>% pull(Value) %>% max()
-
-task_table <- summary_table[[1]]$`Task type` %>% table()
-
-final_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'Reviewed_positive') %>% pull(Value) %>% max()
-```
-
-The first session of searches, performed using the two manually curated input queries, returned `r sources_first_query$Total` unique results, specifically `r sources_first_query$Pubmed` unique results for Pubmed, `r sources_first_query$WOS` for Web of Science, and `r sources_first_query$IEEE` for IEEE.\
-Of these records, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review.
-Of these `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_positive, percent(Reviewed_positive/Reviewed)))` were labeled as positive, and `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_negative, percent(Reviewed_negative/Reviewed)))` as negative.
-
-Subsequently, cycles of prediction/review tasks were performed, in which manually reviewed records (R tasks) were used to train the ML classification algorithm which is then used to reclassify all records (P tasks).
-After task 11, two susbsequent P tasks returned no uncertain or positive unreviewed predictions, therefore the first session was termined.
-In total `r task_table[['R']] - 1` review tasks were required in addition to the initial manual classification (tab.
-1), for a total of `r sum(new_uncertains, new_positives)` extra reviewed articles (`r new_uncertains` predicted as uncertain and `r new_positives` as positive).\
-Overall `r new_uncertains + new_positives + first_annotation_results$Reviewed` classification/review actions on `r all_unique_reviews` records were required, that is the `r percent((new_uncertains + new_positives + first_annotation_results$Reviewed)/sources_first_query$Total)` of the total number of records (`r sources_first_query$Total`) collected in the first session, while the rest was classified automatically as non-relevant.
-The dataset at the end of the session contained a total of `r final_positives` positive records (+`r final_positives - first_annotation_results$Reviewed_positive` positive records compared to the initial manual classification).
-
-`r knitr::kable(summary_table[[1]], caption = 'Table 1.
-Prediction (P) / review (R) tasks\' results after the first query was performed.
-The Uncertain column shows the number of new labeled records not already reviewed in the precedent tasks and the possible increment compared to the previous P task.
-The Positive column has different meaning for the type of task: for the P tasks is the number of positevely labeled records followed by the number of new positives not previously reviewed, if any; for the R task, the cumulative number of positive and its increment, if any.
-The same interpretation stands for the Negative column, albeit increments are not shown for the R tasks, since the negative predictions are not reviewed.
-All values are also shown as percentege over total of records available in the session.')`
-
-### Second search session
+# References

### 2021-10-25 Manuscript/Manuscript.tex
update

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{graphicx}

\title{Main manuscript}

\author{
    David S. Hippocampus
    \thanks{Use footnote for providing further information about author
(webpage, alternative address)---\emph{not} for acknowledging funding
agencies. Optional.}
   \\
    Department of Computer Science \\
    Cranberry-Lemon University \\
  Pittsburgh, PA 15213 \\
  \texttt{\href{mailto:hippo@cs.cranberry-lemon.edu}{\nolinkurl{hippo@cs.cranberry-lemon.edu}}} \\
   \And
    Elias D. Striatum
   \\
    Department of Electrical Engineering \\
    Mount-Sheikh University \\
  Santa Narimana, Levand \\
  \texttt{\href{mailto:stariate@ee.mount-sheikh.edu}{\nolinkurl{stariate@ee.mount-sheikh.edu}}} \\
  }

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{caption}
\usepackage{placeins}
\usepackage{amsmath}
\captionsetup[table]{labelformat=empty}
\captionsetup[figure]{labelformat=empty}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}
\maketitle

\def\tightlist{}

\begin{abstract}
Enter the text of your abstract here.
\end{abstract}

\keywords{
    blah
   \and
    blee
   \and
    bloo
   \and
    these are optional and can be removed
  }

{[}1{]} 8

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Scientific production has experienced continuous exponential growth in
the last decades (Larsen and Von Ins 2010; Bornmann and Mutz 2015). This
is especially true for biomedical research, a trend further increased by
the COVID19 pandemic, thanks to decreased journals' processing time and
the diffusion of preprint databases' usage (Aviv-Reuven and Rosenfeld
2021; Horbach 2020; Hoy 2020). Consequently, it gets harder for
researchers and practitioners to stay up-to-date on the latest findings
in their field. Secondary research is of paramount relevance in this
scenario, providing valuable summaries of the latest research results,
but is getting ever more demanding in terms of time and human resources
(Allen and Olkin 1999; Borah et al. 2017; A. M. Cohen et al. 2010;
Bastian, Glasziou, and Chalmers 2010).\\
The article collection and screening phases of a systematic review are
particularly demanding (Babar and Zhang 2009). First, relevant published
research needs to be collected from scientific databases through
appropriately built search queries (retrieval phase); secondly, the
acquired scientific citations need to be screened, selecting only those
relevant to the topic (appraisal phase) (Bannach-Brown et al. 2019;
Tsafnat et al. 2014; Higgins et al. 2019).\\
The construction of search queries is a complex task (Lefebvre et al.
2011; Hammerstrøm et al. 2010), requiring both domain and some knowledge
of the databases' query languages; the goal is to produce a set of
results containing all relevant articles (high sensitivity) while
keeping the total number low (high specificity), focusing on the first
aspect at the cost of the second (Hammerstrøm et al. 2010). If an
integrated search tool is not used, manual work is required to download,
store and organise the publication data; this approach is complicated by
limits in the number of records that can be downloaded at once and the
necessity to harmonise different formats and resolve record duplication
(Marshall and Wallace 2019).\\
The citation screening phase is usually the more resource-demanding task
of a systematic review: even with appropriately built search queries,
the returned results easily range in the tens of thousands of which just
a small fraction is actually relevant (Lefebvre et al. 2011). It was
estimated that labelling 10,000 publications may take as much as 40
weeks of work and that the average clinical systematic review takes 63
weeks to be completed (Bannach-Brown et al. 2019; Borah et al. 2017;
Allen and Olkin 1999). A consequence is that often systematic reviews
are already outdated once they are published (E. M. Beller et al.
2013).\\
The field of Data Science applied to evidence synthesis and acquisition
has greatly maturated in the last years (Marshall and Wallace 2019; E.
Beller et al. 2018; Tsafnat et al. 2014). Through the application of
natural language processing (NLP), it is possible to transform free text
into quantitative features, with various levels of abstraction and
generalisation (Ananiadou and McNaught 2006; K. B. Cohen and Hunter
2008); with machine learning, such text-derived data can be used to map
and reproduce human judgment, automating the citation screening
(Ikonomakis, Kotsiantis, and Tampakas 2005). One of the most successful
approaches to text screening is active machine learning: researchers
review the predictions made by the learning algorithm, focusing on the
most uncertain predictions (``uncertainty'' based active machine
learning) or on those giving a document a higher probability of being
relevant (``certainty'' based active ML) (Miwa et al. 2014).\\
The automatisation of systematic reviews has been ripe with improvements
in the last years, and it is possible to foresee that such techniques
will become a standard approach (E. Beller et al. 2018). See Ananiadou
et al. (2009); O'Mara-Eves et al. (2015); Tsafnat et al. (2013);
Jonnalagadda, Goyal, and Huffman (2015) for in-depth evaluations of
research in this field. Many of these studies have generated a set of
user-friendly commercial and free-to-use tools (see Marshall and Wallace
2019, table 1). Despite the significant advances, each method has
various shortcomings, both in usability and efficiency (O'Mara-Eves et
al. 2015). We tried to address some of these limitations by creating an
integrated framework that tries to simplify systematic reviews in
innovative ways: we provide solutions for automatic citation collection
and management from multiple online sources and a Bayesian, active
machine learning-based tool to support humans in the screening task,
exponentially reducing the number of records to review. In particular,
we exploit the characteristics of Bayesian analysis to overcome the
shortcoming of both ``certainty'' and ``uncertainty'' based active
learning and the difficulties in defining stopping rules (Miwa et al.
2014). Finally, we propose an experimental method to semi-automatically
generate efficient search queries given an already labelled set of
publications.\\
We tested the framework in the retrieval and appraisal phases of an
example topic of interest for our group: the evaluation of the
mathematical modelling of patient referral networks among hospitals and
their impact on the diffusion of healthcare-associated pathogenic
microorganisms. The actual protocol of this systematic review is
published in (Sadaghiani et al. 2020).\\
We give an overview of the framework in the Methods section; in the
Result section, we show the framework outputs and performance once
applied to the example topic; in the Discussion, we lay out the
methodological justification behind the different components and
features of the framework.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{general-description}{%
\subsection{General description}\label{general-description}}

We built an R (R Core Team 2020) based framework to simplify two aspects
of systematic reviews: record acquisition and classification. The
framework comprises several modules that communicate through
intermediate outputs stored in standard formats, which make it possible
for users to extend the framework or easily integrate it with other
tools in their pipeline. See Supplemental Material S1 for an in-depth
description of the framework and how to use it.\\
The tasks carried out by the framework are grouped into ``sessions,''
i.e., a set of actions that starts from a search query to obtain a set
of scientific citation data (records), which are then labelled as
relevant (``positive'' in the rest of the text) or not (``negative'')
for the topic of interest (Fig. 1). The framework can generate a new
query from this labelled set and perform a new session to find records
possibly missed by the first query.\\
The researcher initiates the process with a starting query derived by
domain knowledge from which she expects a high relevant/non-relevant
record ratio.\\
Follows a description of the framework's components.\\

\begin{figure}
\includegraphics[width=1\linewidth]{methods_diagram} \caption{Figure 1.Framework's visual depiction.}\label{fig:method_diagram}
\end{figure}

\hypertarget{records-acquisition-and-initial-labelling}{%
\subsection{Record's acquisition and initial
labelling}\label{records-acquisition-and-initial-labelling}}

We built a set of tools to let users automatically search and download
citation data from three major scientific databases (``sources''):
Pubmed (\url{https://pubmed.ncbi.nlm.nih.gov/}), Web Of Science (WOS,
\url{https://apps.webofknowledge.com/}) and the Institute of Electrical
and Electronics Engineers (IEEE,
\url{https://ieeexplore.ieee.org/Xplore/home.jsp}). The framework takes
care of authorization management for non-open databases like WOS and
IEEE. It is also possible to download and import records in the
framework manually; this is particularly useful to acquire records from
the SCOPUS
(\url{https://www.scopus.com/search/form.uri?display=basic\#basic}) and
EMBASE databases
(\url{https://www.embase.com/\#advancedSearch/default}), for which a
comprehensive API interface was not easy to build. An extra manual
search was necessary also for Pubmed, since the API and the web
interface have different rule expansion algorithms and return slightly
different results ({``NCBI Insights : Updated Pubmed e-Utilities Coming
in April 2022!''} n.d.). A short guide on how to set up the framework
for each supported database is available in Supplemental Material S3.\\
The acquired records are merged into a single database, resolving
duplicates and different formatting between sources. The records are
ordered according to the frequency of the positive query terms (e.g.,
not preceded by a \(NOT\) modifier) in the title and abstract (``simple
query ordering'').\\
The researcher is then asked to label a number of records to create the
``initial training set'' needed to start the automatic classification.
We suggest manually labelling the first 250 records (see
``hyperparameter optimization'' later). The simple query ordering
increases the positivity rate in the initial training set (Wallace,
Small, et al. 2010), which provide higher sensitivity during automatic
classification (Chawla, Japkowicz, and Kotcz 2004).

\hypertarget{text-feature-extraction}{%
\subsection{Text feature extraction}\label{text-feature-extraction}}

The collected citation data have a number of fields characterizing a
scientific publication. The framework models the relevance of a record
based on the following fields: title, abstract, authors, keywords, MESH
terms (Lipscomb 2000). A series of Natural Language Processing (NLP)
techniques (Baeza-Yates, Ribeiro-Neto, and others 1999; Marshall and
Wallace 2019; Ananiadou and McNaught 2006) are employed to transform the
textual information in these fields into features for machine learning
through a bag-of-words approach (Marshall and Wallace 2019). The
processing of free text fields (title, abstract) includes: tokenization
(i.e., extracting the terms), common stopwords (i.e., sentence
components bringing no meaning) removal, part-of-speech filtering (only
nouns, adjectives, verbs and untagged terms are retained), and
lemmatization of the terms (i.e., reduction to their base grammar form).
Text processing for authors, keywords and MESH terms identifies logical
units (e.g., author's full names, composite keywords) and extracts
them.\\
Terms appearing in less than 5\% of the labelled documents are removed
from negative records. All terms in the positive set are kept to
increase sensitivity at the cost of specificity.\\
Some terms tend to co-appear in records (non-consecutive ngrams,
nc-ngrams), often carrying a particular meaning when copresent. To
detect nc-ngrams, we generated a word network representation (Francois
Rousseau 2015) posing edges between terms with a cosine similarity in
terms of record co-occurrence \textgreater{} 0.5. We extracted the
maximal cliques in the network (Eppstein, Löffler, and Strash 2010)
representing highly correlated groups of terms; These groups of terms
are added to the data set as individual features. Only nc-ngrams
comprising a maximum of ten terms are kept.\\
A second network is built using a co-occurrence threshold of 0.9. In
this case, the cliques represent terms that always appear together and
therefore can be considered redundant (i.e., they do not need to be
considered separately). These terms are merged to increase computation
efficiency and reduce overfitting.\\
The output is a Document-Term Matrix (DTM), with \(N_d\) rows
representing the records (\(D_i\)), \(N_t\) terms column for the
\(t_{field}\) terms (divided by record field) and \({0,1}\) values
whether \(t_{field} \in D_i\). We also enriched the DTM with features
referencing the number of terms in each field to help the model scale
term importance based on the field length.

\hypertarget{label-prediction}{%
\subsection{Label prediction}\label{label-prediction}}

We used a Bayesian Additive Regression Trees (BART) machine learning
``classification model'' (Chipman et al. 2010) (in the implementation of
Kapelner and Bleich 2013) to predict the probability of a record of
being relevant, given the information coded into the enriched DTM and
the initial training set. We set up the BART model to use 2000 MCMC
iterations (after 250 burn-in iterations) and 50 trees; we used a \(k\)
value of 2 to regularize extreme prediction and let the model use
missing fields in the DTM as features (Kapelner and Bleich 2015).
Positive records are oversampled ten times to increase sensitivity
(Batista, Prati, and Monard 2004).\\
The output is a posterior predictive distribution (PPD) for each record
describing its probability of being relevant (i.e., a positive match).
An ensemble of ten models was fitted to improve prediction stability by
averaging the PPD between models (Zhou 2021; Dietterich 2000).\\

To assign the labels, we employed an ``active learning'' Miwa et al.
(2014) approach, where a human reviews a specific subset of predictions
made from the machine, which is then retrained on the manually reviewed
dataset. This process proceeds iteratively, decreasing prediction
uncertainty.\\
Label assignment is done through the identification of an ``uncertainty
zone'' whose construction is possible thanks to the Bayesian nature of
BART, which provides full PPDs instead of point-wise predictions for
each record.\\
To describe the process formally, we define

\[\pi_i = \frac{1}{M}\sum_{j=1}^M Pr(L_i = \text{1}|DTM,m_j)\]

as the PPD of a record \(D_i\) being relevant (i.e, having a positive
label, \(L_i = 1\)), averaging the PPDs of the ensemble of \(M=10\)
models \(m\), and

\[
\begin{aligned}
\pi_{i,l} = \{\pi_i : Pr(\pi_i) = 1\%\}\\
\pi_{i,u} = \{\pi_i : Pr(\pi_i) = 99\%\}
\end{aligned}
\]

as respectively the lower and upper boundaries of the 98\% quantile
interval of \(\pi_i\) (98\% Predictive Interval, 98\% PrI).\\
Then we identify the ``uncertainty zone'' as

\[U_\pi=[\max\vec{\pi}_{u}^-, \min\vec{\pi}_{l}^+]\] with
\(\vec{\pi}_{u}^-\) being the vector of \(\pi_{i,u}\) with a negative
label and \(\vec{\pi}_{l}^+\) the vector of \(\pi_{i,l}\) with a
positive label. That is, \(U_\pi\) defines a range of values between the
smallest \(\pi_{i,l}\) in the set of already labelled positive records
\(L_p\) and the largest \(pi_{i,u}\) related to the negative ones
\(L_n\), noting that the two limits can appear in any order.\\
Consequently, a record \(D_i\) will be labelled as positive if

\[\pi_{i,l} > \max_{\pi \in U_\pi} \pi\]

that is, the record lower 98\% PrI boundary should be higher than every
value in the uncertainty zone. In other words, for a record to be
labelled positive, its PPD should be within the range of the mixture of
PPD of the previously labelled positive records and not cross the
distributions of the negative records.\\
Conversely, a record is labelled as negative if

\[\pi_{i,u} < \min_{\pi \in U_\pi} \pi\]

All other records are labelled as ``uncertain.''

Manual review is then necessary for: 1) uncertain records, 2) positive
records (to avoid false positives), 3) records whose predicted label
differs from the existing manual one. The last case helps identify human
errors or inconsistent labelling criteria.

The automatic classification and the manual review steps alternate in a
loop (CR iterations) until no new positive matches are found in four
consecutive iterations.

\hypertarget{relevant-terms-extraction}{%
\subsection{Relevant terms'
extraction}\label{relevant-terms-extraction}}

BART model it is possible to extract the proportion of times a term was
used in a posterior tree over the sum of total inclusions of all
variables (Kapelner and Bleich 2013), as a measure of feature importance
for the model. We extracted the terms, the part of the citation data
they were used in, the average ``inclusion rate'' among the ensemble
models (over 10,000 inclusions) and its ratio over the standard
deviation of this inclusion (inclusion stability, IS). For each term we
ran a Poisson regression to get its linear association with a positive
label and reported it as Relative Risk (RR) with the number of standard
errors as significance index (Statistic); the comparison between the
inclusion rate in the BART models and the linear association allows to
spot relevant non-linear effects (i.e, the feature is relevant only in
association with others). We reported in the Results only the first (in
order of inclusion rate) 15 terms with IS \textgreater{} 1.5 while the
first fifty terms regardless of inclusion stability are reported in
Supplemental Material S2.

\hypertarget{new-search-query-generation}{%
\subsection{New search query
generation}\label{new-search-query-generation}}

We created an algorithm that generates a new search query to acquire
further relevant publications missed during the first search, possibly
at a reasonable cost in specificity (i.e., a higher number of negative
results).\\
The algorithm encompasses a number of steps:

\begin{itemize}
\tightlist
\item
  We fit a partition tree (Therneau and Atkinson 2019) between the DTM
  and 800 samples from the PPD; if a term is present multiple times in
  the DTM (e.g., both title and abstract), they are counted just one,
  and field term count features are removed. This step generates a list
  of rules composed by \(AND\)/\(NOT\) ``conditions'' made of
  terms/authors/keywords/MESH tokens, which together identify a group of
  records.
\item
  For each rule, negative conditions (i.e., \(NOT\) statements) are
  added iteratively, starting from the most specific one, until no
  conditions are found that would not also remove positive records.
\item
  The extended set of rules is sorted by positive-negative record
  difference in descending order. The cumulative number of unique
  positive records is computed and used to group the rules. Rules inside
  each group are ordered by specificity.
\item
  The researcher is then asked to review the rule groups, selecting one
  or more rules (useful if they convey different meaning) from each, or
  edit them (in case too specific positive or negative conditions were
  included). It is possible to exclude a group of rules altogether,
  especially those with the worse sensitivity/specificity ratio.
\item
  The selected rules are joined together by \(OR\) statements, defining
  a subset of records with a sensibly higher proportion of positive
  records than the original one.
\item
  Redundant rules (i.e., rules whose positive records are already
  included in more specific ones) and conditions (i.e., conditions that
  once removed do not decrease the total number of positive or do not
  increase the negative records) are removed.
\item
  Finally, the rules are re-elaborated in a query usable on the major
  scientific databases.
\end{itemize}

Since the algorithm is data-driven, it creates queries that effectively
select positive records from the input dataset but may be not specific
enough once applied to actual research databases. Therefore we appended
an extra subquery in \(AND\), which specifies the general topics of our
search and delimitates the search domain.\\
The new query was used to initiate a second search session.

\hypertarget{performance-evaluation}{%
\subsection{Performance evaluation}\label{performance-evaluation}}

We trained a simple Bayesian logistic regression (surrogate model) on
the reviewed records to evaluate the classification model consistency
(see Discussion for the theoretical justification). The surrogate model
uses as predictor the lower bound of the 98\% PrI of the records' PPD
with weakly regularizing, robust priors for the intercept (Student T
with \(\nu=3,\mu=0,\sigma=2.5\)) and the linear coefficient (Student T
with \(\nu=3,\mu=0,\sigma=1.5\)).\\
The quality of the model was evaluated through Bayesian \(R^2\) (Gelman
et al. 2019), of which we reported the posterior median and 90\%
Credible Interval {[}90\% CrI{]}. The \(R^2\) also provides an
evaluation of the consistency of the original classification model.
Given that this model is conditional only on the BART predictions and
not on the DTM, it is characterized by more uncertainty, providing
plausible worst-case scenarios.\\
The surrogate model is then used to generate the predictive cumulative
distribution of the number of missed positive records in the whole
dataset. This distribution allows estimating the expected total
posterior ``Sensitivity'' and the ``Work saved over random'' (WSoR) of
the classification model in the full (unreviewed) dataset. The WSoR is
one minus the number of records to manually label at random to find the
same number of positives; this last quantity is estimated through a
negative hypergeometric distribution (Chae 1993).\\
For the number of predicted positive records, the sensitivity and the
WSoR, we reported the ``truncated 90\% PrI'' {[}trunc. 90\% PrI{]},
which is the uncertainty interval bounded at the number of observed
total positive records (i.e., there cannot be less predicted positive
records than observed).

\hypertarget{hyperparameter-evaluation}{%
\subsection{Hyperparameter evaluation}\label{hyperparameter-evaluation}}

Our classification algorithm has a number of hyperparameters:

\begin{itemize}
\tightlist
\item
  Size of the initial training set: 50, 100, 250, 500 records;
\item
  Number of models in the ensemble: 1, 5, 10, 20, 40, 60 repetitions;
\item
  Oversampling rate of positive records: (1x (i.e., no oversampling),
  10x, 20x;
\item
  PrI quantiles for building the uncertainty zone: 80\%, 90\%, 98\%;
\item
  Source of randomness between models in the ensemble: MCMC sampling
  only (Robert, Casella, and Casella 2004), MCMC plus data bootstrapping
  (Breiman 1996) of the training set.
\end{itemize}

To evaluate the hyperparameter effect of performance, we set up a ``grid
search'' (Claesen and De Moor 2015; L. Yang and Shami 2020) on a
prelabelled ``validation set'' made of the first 1200 records from the
first session dataset. The framework tested each hyperparameter
combination until four CR iterations with no positive records were
returned or the whole dataset got labelled.\\
For each combination, a performance score was computed as the product of
``Efficiency'' (1 minus the ratio of records that required review over
the total) and ``Sensitivity'' (number of positive records found over
the total of positives). We then identified homogeneous ``performance
clusters'' of scores given hyperparameter values using a partition tree
(Therneau and Atkinson 2019). For the rest of the study, we used the
best hyperparameter set in terms of Sensitivity followed by Efficiency
from the cluster with the highest average score.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{first-session}{%
\subsection{First session}\label{first-session}}

The input search query for the first session was:\\

\emph{((model OR models OR modeling OR network OR networks) AND
(dissemination OR transmission OR spread OR diffusion) AND (nosocomial
OR hospital OR ``long-term-care'' OR ``long term care'' OR ``longterm
care'' OR ``long-term care'' OR ``healthcare associated'') AND
(infection OR resistance OR resistant))}

selecting only results between 2010 and 2020 (included). Results were
collected from Pubmed, WOS, IEEE, EMBASE and SCOPUS, using the framework
tools as described in Methods and Supplemental Material S1.

The first search session returned a total of 27600 unique records,
specifically 12719 (71.6\% of the total) records from the EMBASE
database, followed by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from
SCOPUS, 2100 (11.8\%) from WOS, and 60 (0.34\%) from IEEE (Table 1).
There were various degrees of overlapping between sources, with the
38.4\% of records being present in more than one database and EMBASE and
IEEE being the databases with the higher uniqueness ratios. The final
dataset was composed by 17755 unique records.\\
The first 250 records were manually labeled. Of these 43 (17.2\%) were
labeled as positive, and 207 (82.8\%) as negative.

\begin{table}[!h]

\caption{\label{tab:session 1}\textbf{Table 1}. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. SAll session shows records after joining and deduplication of the Session 1 and Session 2 dataset.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlrl}
\toprule
Session & Source & Records & \% over total & Source specific records & \% over source total\\
\midrule
\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 12719 & 71.6\% & 6683 & 52.5\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3457} & \cellcolor{gray!6}{36.2\%}\\
 & Scopus & 3175 & 17.9\% & 298 & 9.39\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
\addlinespace
 & IEEE & 60 & 0.34\% & 29 & 48.3\%\\
\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 48396 & 58.6\% & 40826 & 84.4\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18021} & \cellcolor{gray!6}{62.5\%}\\
 & Scopus & 17070 & 20.7\% & 4908 & 28.8\%\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2817} & \cellcolor{gray!6}{21.7\%}\\
 & IEEE & 61 & 0.074\% & 22 & 36.1\%\\
\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 59604 & 60.6\% & 46942 & 78.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21371} & \cellcolor{gray!6}{57.3\%}\\
\addlinespace
 & Scopus & 19353 & 19.7\% & 5181 & 26.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3175} & \cellcolor{gray!6}{22.1\%}\\
 & IEEE & 108 & 0.11\% & 48 & 44.4\%\\
\bottomrule
\end{tabular}}
\end{table}

Records were joined into a database and arrange by simple query
ordering; of these, the first 250 records were labelled to create the
initial training set.\\
Using the classification model,7 automatic classification and manual
review iterations (CR) were performed (Table 2). It is possible to
observe how the number of records that required manual review dropped
rapidly between iterations, indicating that the engine was converging
while the uncertainties were resolved.\\
This phenomenon is better depicted in Fig. 1 of the Supplemental
Material S2. It shows the mixture distribution of the PPD of the
records, specifically for the reviewed positive and negative records,
and for records that need manual review after the classification step:
it can be noticed how the distribution of the uncertain records shrinks
(they concentrate in a shorter probability range) and shifts toward the
negative zone as more positive matches are found and reviewed.
Accordingly (Table 2), the number of new positives found drops after the
first couple of iterations. As per default, the classification process
was stopped after four rounds with no new positive matches; a total
number of 101 positives were found over 766 manually reviewed records
(13.2\% positivity rate).\\

\begin{table}[!h]

\caption{\label{tab:session 1}\textbf{Table 2}. Results of the automatic classifaction and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported."Unlab." indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrrlrrrrrr}
\toprule
Session & Iteration & Positives & Negatives & Total labelled (\%) & Unlab. -> y & Unlab. -> n & Unlab. -> * & n -> y & Changes & N. features\\
\midrule
\cellcolor{gray!6}{Session1 (n = 17755)} & \cellcolor{gray!6}{Initial labelling} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{250 (1.41\%)} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{2289}\\
 & 1 & 93 & 529 & 622 (3.5\%) & 50 & 322 & 0 & 0 & 372 & 2289\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{614} & \cellcolor{gray!6}{714 (4.02\%)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{86} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{3750}\\
 & 3 & 101 & 625 & 726 (4.09\%) & 1 & 11 & 0 & 0 & 12 & 3834\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{648} & \cellcolor{gray!6}{749 (4.22\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{3856}\\
\addlinespace
 & 5 & 101 & 651 & 752 (4.24\%) & 0 & 3 & 0 & 0 & 3 & 3856\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{660} & \cellcolor{gray!6}{761 (4.29\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{3856}\\
 & 7 & 101 & 665 & 766 (4.31\%) & 0 & 5 & 0 & 0 & 5 & 3856\\
\cellcolor{gray!6}{Session2 (n = 98371)} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{106} & \cellcolor{gray!6}{934} & \cellcolor{gray!6}{1040 (1.06\%)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{270} & \cellcolor{gray!6}{998} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1273} & \cellcolor{gray!6}{4729}\\
 & 2 & 107 & 1123 & 1230 (1.25\%) & 1 & 189 & 0 & 0 & 190 & 4729\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1176} & \cellcolor{gray!6}{1283 (1.3\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{4733}\\
 & 4 & 107 & 1200 & 1307 (1.33\%) & 0 & 24 & 0 & 0 & 24 & 4729\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1209} & \cellcolor{gray!6}{1316 (1.34\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{4729}\\
 & 6 & 107 & 1226 & 1333 (1.36\%) & 0 & 17 & 0 & 0 & 17 & 4729\\
\bottomrule
\end{tabular}}
\end{table}

By evaluating how often a term was used by the classification model, it
is possible to define their relevance in labeling the records (see
Methods). Here follows the 15 most relevant terms by inclusion rate over
10,000 posterior tree inclusions, described as: Term (citation part):
Inclusion Rate (Inclusion Stability) {[}linear Relative Risk,
Statistic{]}.

Patient Transport (Keyword): 61.2 (3.77) {[}99.1, 21.3{]}, Transfer
(Abstract): 57 (3.93) {[}22.5, 15.4{]}, Network (Title): 56.5 (2.91)
{[}18, 14.2{]}, Network \& Patient (Abstract): 54.2 (4.66) {[}26.3,
15.2{]}, Donker T (Author): 53.5 (4.56) {[}159, 16.5{]}, Worker
(Abstract): 50 (3.33) {[}0.421, -1.21{]}, Hospitals (Keyword): 49.8
(4.31) {[}27.8, 16.5{]}, Movement (Abstract): 47.8 (2.7) {[}27.2, 15{]},
Spread (Title): 46.6 (2.25) {[}16.2, 12.1{]}, Facility (Abstract): 45
(2.22) {[}19.6, 14.8{]}, Orange County (Keyword): 44.3 (3.19) {[}199,
17.2{]}, Conduct (Abstract): 42.6 (3.7) {[}0.221, -2.57{]}, Patient
(Abstract): 42 (3.61) {[}27.6, 7.23{]}, Perform (Abstract): 41.9 (2.38)
{[}0.342, -2.55{]}, Hospital (Title): 39 (1.95) {[}12.5, 12.5{]}.

The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
documents.\\
The engine was able to pick up the central concept of the research,
i.e., ``patient transport'' or ``transfer'' through a ``network'' of
``facility''ies that facilitates the ``spread'' of infections, and even
one of the authors of this study (Donker T.) or the region of interest
(``Orange County'') of another research group active on the topic of
healthcare asociated pathogen spreading over hospital networks. It is
interesting to see that some terms were considered highly relevant for
the BART models (e.g., ``Worker'' in 6th position out of more than 3800
terms considered) although in a simpler linear model their effect would
be hardly significant (statistic: -1.21 s.e.); these are terms which are
relevant only together with other terms but not by themselves,
highlighting the extra predictive power brought by a non-linear model
like BART.\\
A more extensive set of terms is presented in Table 1 of Supplemental
Material S2.

\hypertarget{second-session}{%
\subsection{Second session}\label{second-session}}

The results of the first classification session were used to create a
second, data-driven query with the purpose of performing a more
large-spectrum search to find records which may have escape the first
search session. The resulting query was the following:\\

\emph{(((Donker T) NOT (bacterium isolate)) OR ((network patient) AND
(resistant staphylococcus aureus) NOT (monte carlo) NOT isolation) OR
(facility AND (network patient) AND regional NOT hospitals NOT increase
NOT (patient transport) NOT (control infection use)) OR ((patient
transport) NOT (Donker T) NOT worker) OR (hospitals AND (network
patient) NOT (patient transport) NOT regional NOT clinical) OR (facility
AND (network patient) NOT hospitals NOT (patient transport) NOT regional
NOT prevention NOT medical) OR ((healthcare facility) NOT (Donker T) NOT
worker NOT positive) OR (hospitals NOT (network patient) NOT medical NOT
environmental NOT outcome NOT global) OR ((network patient) NOT facility
NOT hospitals NOT (patient transport) NOT therapy NOT global)) AND
((antimicrobial resistance) OR (healthcare infection))}

The final piece \emph{AND ((antimicrobial resistance) OR (healthcare
infection)} was added manually to better define the search domain, since
the algorithm was trained on documents that were all more or less
related to these topics.\\
The generated query also provides a more nuanced understanding of the
engine's internal classification logic, and this is helpful to spot
possible biases in the model.\\

The search was done with the same year filter and procedures of the
first session.\\

The new search produced 107294 records (Table 1), of which 48396
(58.6\%) from the EMBASE, followed by 28811 (34.9\%) from Pubmed, 17070
(20.7\%) from SCOPUS, 12956 (15.7\%) from WOS, and 61 (0.074\%) from
IEEE; compared with the first session, the relative weight of EMBASE and
Pubmed was decreased, while the amount of content specificity was
greatly increased, as it was for SCOPUS. After removal of duplicates,
82579 unique records were obtained. Once joined with the session 1
records and duplicates removed, we obtained 98371 unique records, with
just 1963 shared records between searches, that is the 2\%. The
percentage of records shared by two or more source dropped to 22\%.

Six CR rounds were necessary to complete the second session
classification, with just 6 new positive found after reviewing 568 extra
records. The first CR iteration required the user to review a
substantial number of records (1,273), but just labelling 275 of them
(the canonical 250 plus 25 that were already labelled during the
framework hyperparameter tuning) was sufficient to drop this number to
just 190 in the subsequent round. An evaluation of the convergence
(Figure 1, Supplemental Material S2) showed that, in addition to the
dynamics already observed in session 1 (shrinkage and negative shift), a
second mode appeared in the mixture distribution of the records to be
reviewed, centred in a highly positive zone. The interpretation is that
as the number of negative training records increases, the engine gets
more and more skeptical and asks to review even some records labelled as
positive in the initial training set in Session 1. This behaviour can be
useful to spot classification errors and inconsistencies. Considering
both sessions, 1333 records were reviewed and 107 (8.03\%) were found.

Again, the evaluation of the inclusion rate of the terms showed that the
engine was quite capable of internalizing the concepts behind the
research topic A subsample of the terms is reported in Table 2 of
Supplemental Material S2.

\hypertarget{hyperparameter-selection}{%
\subsection{Hyperparameter selection}\label{hyperparameter-selection}}

As described in the methods, the selection of hyperparameters was
achieved via evaluation of sensibility and efficiency through a grid
search on a validation set of 1200 completely manually labelled records.
The best set of parameters suggested an initial input of 250 labelled
records with 10x positive matches oversampling, an averaged ensemble of
10 models, no bootstrapping and an uncertainty zone defined by the 98\%
predictive interval. On the validation set, this combination of
parameters reached a sensitivity of 98.8\% (81 / 82 positive matches
found) and efficiency of 61.5\% (462 / 1200 records evaluated). The
results of the hyperparameter tuning are reported in Table 3 of
Supplemental Material S2. Figure 2 in Supplemental Material S2
demonstrates that the positive record oversampling rate, the number of
ensemble models and the size of the initial training set were the
parameters that most impact performance.

\hypertarget{performance-evaluation-1}{%
\subsection{Performance evaluation}\label{performance-evaluation-1}}

To evaluate the theoretical performance of the engine, a surrogate
Bayesian logistic regression model was trained on the manually reviewed
labels using only the lower bound of the record PPDs as predictor (see
Methods for details). The surrogate model show the high predictive power
of the scores produced by the classification model (Bayesian R2: 98.1\%
{[}97.4\%, 98.3\%{]} for session 1 and 98.2\% {[}97.6\%, 98.3\%{]} for
session 2).\\

Figure 2 presents the actual and predicted (from the surrogate model)
cumulative number of positive matches, ordered by the initial simple
ordering query: the median of surrogate models' cumulative predictive
distributions matches quite well the actual number of positive records
found. It is striking how many more records would have needed to be
evaluated manually to find the same number of positive matches without
using a smart classification tool; some relevant record was found even
close to the end of the heuristically ordered list of records.\\

Table 3 shows various performance indexes for both sessions, both
descriptive (Total records, Reviewed records, Observed positive matches)
and estimated through the surrogate model (Expected efficiency,
Predicted positive matches, Expected sensitivity, \(R^2\)).\\
In session 1 we observe an expected total number of positives of 101
{[}101, 108{]} for an estimated sensitivity of 100\% {[}93.5\%, 100\%{]}
and efficiency of 95.7\% {[}95.3\%, 95.7\%{]}. In session 2 we observed
a drop in the expected sensitivity, especially in the lower margin
(97.3\% {[}73.8\%, 100\%{]}), due to the fact that as the number of
records grows, even a small probability can translate, in the worst case
scenario, into a relevant number of missed positive matches (145 in this
case). To ascertain that no evident positives were missed, we evaluated
100 more records between the unreviewed ones with the highest median
predicted probability produced by the engine and found no additional
positive matches.

\begin{table}[!h]

\caption{\label{tab:performance}\textbf{Table 3}. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Work saved over random" (WSoR) are reported, with their 90\% PrI truncated to a number of positive matches equal to the observed one. Finally the median Bayesian $R^2$ [90\% CrI] of the logistic models is reported. [PrI] represents the 90\% Predictive Interval while [trunc. PrI] indicate the residual PrI truncated at the observed realization (see. methods).}
\centering
\begin{tabular}[t]{lll}
\toprule
Indicator & Session 1 & Session 2\\
\midrule
\cellcolor{gray!6}{Total records} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{98371}\\
Reviewed records (\% over total records) & 761 (4.29\%) & 1316 (1.34\%)\\
\cellcolor{gray!6}{Expected efficiency (over random) [trunc. 90\% PrI]} & \cellcolor{gray!6}{95.7\% [95.3\%, 95.7\%]} & \cellcolor{gray!6}{98.6\% [98.2\%, 98.7\%]}\\
Observed positive matches (\% over total records) & 101 (0.57\%) & 107 (0.11\%)\\
\cellcolor{gray!6}{Predicted positive matches [trunc. 90\% PrI]} & \cellcolor{gray!6}{101 [101, 108]} & \cellcolor{gray!6}{110 [107, 145]}\\
\addlinespace
Expected sensitivity [trunc. 90\% PrI] & 100\% [93.5\%, 100\%] & 97.3\% [73.8\%, 100\%]\\
\cellcolor{gray!6}{Simple Model $R^2$ [90\% PrI]} & \cellcolor{gray!6}{98.1\% [97.4\%, 98.3\%]} & \cellcolor{gray!6}{98.2\% [97.6\%, 98.3\%]}\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/performance plot-1.pdf}
\caption{\textbf{Figure 2}. Observed cumulative number of positive
matches (red dots) sorted by simple query ordering. The {[}trunc. 90\%
PrI{]} of the cumulative positive matches estimated by the logistic
Bayesian model is shown as shaded area delimited by the 95\% quantile of
the PrI and by the observed number of positive matches (light blue
lines). The median of the PrI is represented by a darker blue line.}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

We propose a new integrated framework to help researchers collect and
screen scientific publications characterised by high performance and
versatility, joining the growing field of systematic review automation
(SRA) and helpers (SRH) tools (A. M. Cohen et al. 2006, 2010; Ananiadou
et al. 2009; O'Mara-Eves et al. 2015). This framework joins standard
approaches and uses ad-hoc solutions to deal with common SRA issues.\\
By freely sharing the tool as an open-source R package and by following
a modular design, we tried to adopt some of the so-called Vienna
Principles advocated by the International Collaboration for the
Automation of Systematic Reviews (ICASR) (E. Beller et al. 2018).\\
Our tool consists of four main components: 1) an integrated query-based
citation search and management engine, 2) a text-to-feature extractor
module, 3) a Bayesian active machine learning-based citation classifier,
and 4) a data-driven search query generation algorithm.\\

The framework's search engine module is capable of automatically
collecting citation data from three well-known scientific databases
(i.e.~Pubmed, Web of Science, and the database of the Institute of
Electrical and Electronics Engineers) as well as process manually
downloaded results from both the mentioned and other (SCOPUS, EMBASE)
databases. In comparison, most SRH tools, commercial or free to use,
rely either on internal databases (e.g., Mendeley
\url{https://www.mendeley.com/}) sometimes focusing just on a particular
topic (Visser 2010) or on a single external data source (Thomas and
Brunton 2007; Poulter et al. 2008; Soto, Przybyła, and Ananiadou
2019).\\
Mixing different databases is fundamental to have a more comprehensive
view of the literature (Bajpai et al. 2011; Wilkins, Gillies, and Davies
2005; Woods and Trewheellar 1998): in our results, 18.7\% of the
positive matches found were unique for one of the different data
sources, and no positive record was present in all of them (data not
shown).~ The online search algorithms are efficient enough to manage
tens of thousands of search results, using various expedients to
overcome the limitations of the online database in terms of traffic and
download quota.\\
The results are then automatically organized, deduplicated and arranged
by ``simple query ordering'' in a uniform corpus. The preliminary
ordering allow to increase the positivity rate in the initial training
set (Wallace, Small, et al. 2010).

The feature extractor module uses modern NLP techniques (Ananiadou and
McNaught 2006; K. B. Cohen and Hunter 2008) to transform text into input
data for machine learning. We did not include classical n-grams
(Schonlau and Guenther 2017), but we used network analysis to find
non-consecutive frequently associated terms, a generalisation of n-grams
relaxing the term adjacency assumption. A similar network approach was
applied to merge redundant terms to make model estimation more efficient
and reduce noise.\\
The use of concurrency network-driven modelling of text is not new
(Francois Rousseau 2015; Violos et al. 2016; François Rousseau, Kiagias,
and Vazirgiannis 2015; Ohsawa, Benson, and Yachida 1998) and is a
valuable tool to extract semantic information not evident in one-word or
consecutive n-gram models.\\

The framework's record classification module implements an active
machine learning approach Miwa et al. (2014) and is based on Bayesian
Additive Regression Trees (BART) (Chipman et al. 2010; Kapelner and
Bleich 2013). When implementing our algorithm we adopted best practices
from other SRA studies, bringing improvements at various levels.\\
As with other boosted trees algorithms (Hastie, Tibshirani, and Friedman
2009), BART can explore complex non-linearities, perform variable
selection, manage missing data while sporting high performance in
predictive power.\\
However, its Bayesian foundation provides further benefits: less
sensitivity on hyperparameter choices, natural regularisation through
priors, and, especially, predictive distributions as output in place of
point-wise predictions (Soria-Olivas et al. 2011; Joo, Chung, and Seo
2020; Jospin et al. 2020). By selecting relatively tight prior
distributions, we discouraged excessively deep trees, long sequences of
trees, or extreme predicted probabilities, to decrease the risk of
overfitting.\\
The algorithm runs multiple replications of the model and averages their
predictive distributions creating an ``ensemble''; this technique has
been shown to improve out-of-sample predictive performance (Zhou 2021;
Dietterich 2000), as we were able to confirm during the hyperparameter
evaluation (Supplemental Material S2). Ensembling reduces the
uncertainty in the predictive distribution tails related to the
randomness in the MCMC fit (Robert, Casella, and Casella 2004),
generating a shift of probability mass towards the distribution centre
and stabilising it (i.e., decreasing variance without impacting bias).
On the other hand, just imposing robust uninformative priors against
extreme predictions would have decreased variance but also shifted the
distribution towards a non-decision zone, increasing bias (Hansen and
others 2000).\\
Since the number of model replications significantly impacts computation
times, we decided to use ten replicas, the lower value after which
showed performance stabilisation during the hyperparameter evaluation.\\
We also investigated whether bootstrapping between replications (Breiman
1996) would improve performance, but, contrary to theory (Díez-Pastor et
al. 2015), it was demonstrated to be slightly detrimental (Supplemental
Material S2) compared to simple ensembling.\\

A low rate of relevant matches (class imbalance) is typical in
literature reviews (Sampson, Tetzlaff, and Urquhart 2011; Wallace,
Trikalinos, et al. 2010; O'Mara-Eves et al. 2015), and such strong
imbalance between positive and negative records can affect sensitivity
(Khoshgoftaar, Van Hulse, and Napolitano 2010; Chawla, Japkowicz, and
Kotcz 2004).\\
To overcome the problem, we oversampled (Batista, Prati, and Monard
2004) the positive records ten times before model fitting. Our
hyperparameter analysis showed that together with model ensembling, the
oversampling rate was the parameter with the highest impact on
performance.\\
A known risk with positive oversampling is the misclassification of
negative records (Ramezankhani et al. 2016). However, since all
predicted positives get manually reviewed in our approach, we are always
ensured to achieve 100\% specificity/positive predictive value: the only
price for the increased sensitivity due to oversampling is a larger
number of records to review.\\
An alternative to oversampling would be applying different weights
and/or cost to the classes (Abd Elrahman and Abraham 2013; Díez-Pastor
et al. 2015), but the BART implementation we used did not have this
feature; also, using simple oversampling permits broader compatibility
with different modelling engines (Galar et al. 2011; Roshan and Asadi
2020).\\
Finally, ordering the records by query term frequency (simple query
ordering) generates a far higher rate of relevant records in the initial
training set (17.2\%) compared to the overall data (0.11\%), and this
boosts the sensitivity of the model.\\

One of the central innovations we introduced is the concept of
``uncertainty zone,'' whose implementation is possible thanks to the
Bayesian foundation of the classification model. This construct guides
the selection of the records to review, dynamically updating and
shrinking after every CR iteration, as more uncertain predictions are
evaluated (Supplemental Material S2 Fig. 1).\\
This approach overcomes the usual requirement of dataset-specific hard
thresholds in active machine learning, and also allows to review
multiple items at once between iterations (Laws and Schütze 2008; Miwa
et al. 2014; Zhu et al. 2010). The parameters our algorithm needs are
instead quite general and non task-specific, like the PPD intervals
based on which the uncertainty zone is built ,and the maximum number of
iterations with no positive matches after which a session is concluded;
the hyperparamer evaluation shows that the algorithm is robust against
variations in these parameters and we expect the default values to
preform well on most datasets.\\
Since researchers are asked to review both records with a positive
predicted label and those inside the uncertainty zone, this method can
be considered as a unifying synthesis of the ``certainty'' and
``uncertainty'' paradigms of active learning (Miwa et al. 2014).\\

We evaluated performance as the capability of the screening procedure
(automatic classification plus manual review) to find the largest number
of relevant records while reviewing as few of them as possible (i.e.,
sensitivity \(\times\) efficiency).\\
We avoided the classic out-of-sample approaches like train-test
sampling, out-of-bag bootstrapping or cross-validation (Kohavi and
others 1995; James et al. 2013). Such methods primarily assume that the
rate of positivity is equal on average in every random subset of the
data (Tashman 2000); this uniformity is broken by how the initial
training set and the subsequent reviewed records are selected by the
query-based ordering and the active learning algorithm, determining a
lower positivity rate in the unlabelled records (Fig. 2). Also, a
literature corpus is unique per search query/database combination, and
therefore any out-of-sample performance estimate is not replicable since
no new data can be acquired related to the current corpus.\\
Instead, to estimate overall sensitivity, we employed simple Bayesian
regression (surrogate model) on the manually reviewed data to abstract
the classification model predictions and achieve a maximum entropy
(Harremoës and Topsøe 2001) estimate of the number of missed positive
matches among the unreviewed records in the whole dataset. This simple
surrogate model fitted the data very well (\(R^2\) consistently above
97\%) using just the lower 98\% PrI bound of the PPDs as predictor,
indicating predictive consistency in the classification model. The
surrogate model posterior predictive distribution could be exploited to
explore worse case scenarios in terms of sensitivity.\\

Our framework achieved very high sensitivity by screening a markedly
small fraction of all records, bringing a sensible reduction in
workload.\\
Based on the surrogate model, we predicted a predicted median
sensitivity of 100\% {[}93.5\%, 100\%{]} in the first session (screening
4.29\% of records) and of 97.3\% {[}73.8\%, 100\%{]} in the second
(screening 1.34\% of records): efficiency increased significantly in the
second session since only a few new positive matches were found, but
given the large number of records, uncertainty regarding sensitivity
also expectedly increased.\\
Both results are above the usual performance in the field (O'Mara-Eves
et al. 2015) and in line with the 92\% average sensitivity estimated
after human-only screening (Edwards et al. 2002). In one interesting
case, the model spotted a human-made misclassification error,
demonstrating its robustness and value as a second screener, a role
already suggested for SRA tools by previous studies (Frunza, Inkpen, and
Matwin 2010; Bekhuis and Demner-Fushman 2012, 2010). Finally, albeit the
simple query ordering already concentrated most of the relevant matches
in the first 20-25 thousand records, without the tool support some
relevant records would have required almost the complete data set to be
manually checked to be found.\\

The model took \textasciitilde5-20 minutes per iteration to perform
predictions in session 1 (17,755 documents) and 20-40 minutes in session
2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM laptop from
2014; including manual record review, one session required 1-3 days of
work, for a total of 1-2 weeks for the whole process (including record
collection). That is a considerable saving of time compared to the
multiple months usually required for the screening phase of systematic
reviews (Bannach-Brown et al. 2019; Borah et al. 2017; Allen and Olkin
1999). To our knowledge, the amount of data processed
(\textasciitilde100.000 records) were larger than what is typical in
most SRA studies (O'Mara-Eves et al. 2015; Olorisade et al. 2016),
emphasising the reliability of the tool in real-world scenarios.\\

The last module of our framework is a data-driven query generation
algorithm. Creating an efficient and efficacious search query is a
complex task (Lefebvre et al. 2011; Hammerstrøm et al. 2010) since it
requires building a combination of positive and negative terms to
maximise the number of relevant search results while minimising the
total number of records to review. Our solution joins a
sensitivity-driven subquery proposal engine based on concurrent decision
trees (Blanco-Justicia and Domingo-Ferrer 2019; Moore et al. 2018) built
on the BART ensemble PPD with a human review step and an
efficiency-driven query builder. The aim is to generate a second query
that helps find records missed during the first session search. The
generated query allowed indeed to retrieve few more positive matches not
found in session 1, but at the cost of a significant increase in the
number of documents.\\
One interesting aspect of this functionality is that it provides a
human-readable overview of the classification rules learned by the
classification model, showing which combination of terms was
particularly relevant and even spotting authors and geographical
locations associated with the study topic. The generated query,
therefore, acted as a tool for machine learning explainability (Bhatt et
al. 2020; Burkart and Huber 2021), a feature useful to understand and
spot bias in black-box classification algorithms (Malhi, Knapic, and
Främling 2020); explainability is often required or even legally
mandatory for high-stake machine learning applications (Bibal et al.
2021, 2020).\\
It is important to note that this process is entirely data-driven. The
algorithm is only aware of the ``world'' defined by the data set used as
input, which is generated by a specific search query focused on a
particular topic. Therefore, the new query may not be specific enough
once applied to an unbounded search domain, returning an unmanageable
amount of unrelated results. The solution we found was to add another
component to the query, specifying the general topic (antimicrobial
resistance and healthcare-associated infections) of our research.\\

As reported, our framework builds on modularity. We designed it to
easily implement complete independence of the main modules in future
iterations, making it possible for users to add custom features like
citation search and parsing for other scientific databases, alternative
text processing algorithms or machine learning modules. We deem such
interoperability extremely relevant because the main strength of our
tool is the composition of many solutions and the general idea of
Bayesian active machine learning and uncertainty zone. However, each of
its components could benefit considerably from the recent improvements
in text mining.\\
For example, our text processing approach is quite simple, based on the
boolean bag-of-words paradigm, and indeed could be improved by more
nuanced text representations. It could be evaluated if feature
transformations like TF-IDF (Baeza-Yates, Ribeiro-Neto, and others 1999;
Ananiadou and McNaught 2006) would be advantageous, even if we
hypothesise that tree-based classification algorithms like BART are
robust enough not to need such operations. Word embedding could be worth
exploring: this technique transforms terms in semantic vectors derived
from the surrounding text Minaee et al. (2021) and could be used to
eliminate semantically redundant terms or differentiate identical terms
with different meanings given the context. Another option would be to
employ unsupervised learning models like Latent Dirichlet Analysis,
Latent Semantic Analysis (Pavlinek and Podgorelec 2017; Q. Chen, Yao,
and Yang 2016; Landauer, Foltz, and Laham 1998) or graph-of-word
techniques (Ohsawa, Benson, and Yachida 1998; Francois Rousseau 2015) to
extract topics to enrich the feature space.\\
Our classification algorithm can be implemented with any Bayesian
supervised machine learning method that provides full PPDs; therefore
alternative classification models could be evaluated, like Gaussian
Processes which are known for their flexibility (Jayashree and Srijith
2020; S.-H. Chen et al. 2015). Even more interesting would be to test
advanced learning algorithms that surpass the bag-of-words approach,
taking into consideration higher-level features in the text like term
context and sequences, long-distance term relationships, semantic
structures, etc., (Cheng et al. 2019; Minaee et al. 2021; Li et al.
2020; J. Yang, Bai, and Guo 2020; Lai et al. 2015; Farkas 1995), given
that a Bayesian implementation of such algorithms is available (for
example C. Chen, Lin, and Terejanu (2018)).\\
Finally, a natural improvement would be to provide a graphical user
interface to make the framework easy to use also for less technical
users.

The field of literature review automatisation is mature and ripe with
innovation, and we expect an increasing use of such technologies to
confront the ever-faster production of scientific literature. We believe
it is appreciable that a multiplicity of tools are being made available
to let researchers and policymakers find the instrument that better fits
their needs.\\
We tried to contribute to the field with an innovative methodology and
tool that provides excellent performance and easy integration with
existing systematic review pipelines. The value of this work lies not
only in the framework itself, which we provide as open-source software,
but in the set of solutions we developed to solve various SRA issues and
that can be used to improve existing solutions.

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-abd2013review}{}%
Abd Elrahman, Shaza M, and Ajith Abraham. 2013. {``A Review of Class
Imbalance Problem.''} \emph{Journal of Network and Innovative Computing}
1 (2013): 332--40.

\leavevmode\hypertarget{ref-allen1999estimating}{}%
Allen, I Elaine, and Ingram Olkin. 1999. {``Estimating Time to Conduct a
Meta-Analysis from Number of Citations Retrieved.''} \emph{Jama} 282
(7): 634--35.

\leavevmode\hypertarget{ref-ananiadou2006text}{}%
Ananiadou, Sophia, and John McNaught. 2006. \emph{Text Mining for
Biology and Biomedicine}. Citeseer.

\leavevmode\hypertarget{ref-ananiadou2009supporting}{}%
Ananiadou, Sophia, Brian Rea, Naoaki Okazaki, Rob Procter, and James
Thomas. 2009. {``Supporting Systematic Reviews Using Text Mining.''}
\emph{Social Science Computer Review} 27 (4): 509--23.

\leavevmode\hypertarget{ref-aviv2021publication}{}%
Aviv-Reuven, Shir, and Ariel Rosenfeld. 2021. {``Publication Patterns'
Changes Due to the COVID-19 Pandemic: A Longitudinal and Short-Term
Scientometric Analysis.''} \emph{Scientometrics}, 1--24.

\leavevmode\hypertarget{ref-babar2009systematic}{}%
Babar, Muhammad Ali, and He Zhang. 2009. {``Systematic Literature
Reviews in Software Engineering: Preliminary Results from Interviews
with Researchers.''} In \emph{2009 3rd International Symposium on
Empirical Software Engineering and Measurement}, 346--55. IEEE.

\leavevmode\hypertarget{ref-baeza1999modern}{}%
Baeza-Yates, Ricardo, Berthier Ribeiro-Neto, and others. 1999.
\emph{Modern Information Retrieval}. Vol. 463. ACM press New York.

\leavevmode\hypertarget{ref-bajpai2011search}{}%
Bajpai, Akhilesh, Sravanthi Davuluri, Haritha Haridas, Greta Kasliwal, H
Deepti, KS Sreelakshmi, Darshan Chandrashekar, et al. 2011. {``In Search
of the Right Literature Search Engine (s).''} \emph{Nature Precedings},
1--1.

\leavevmode\hypertarget{ref-bannach2019machine}{}%
Bannach-Brown, Alexandra, Piotr Przybyła, James Thomas, Andrew SC Rice,
Sophia Ananiadou, Jing Liao, and Malcolm Robert Macleod. 2019.
{``Machine Learning Algorithms for Systematic Review: Reducing Workload
in a Preclinical Review of Animal Studies and Reducing Human Screening
Error.''} \emph{Systematic Reviews} 8 (1): 1--12.

\leavevmode\hypertarget{ref-bastian2010seventy}{}%
Bastian, Hilda, Paul Glasziou, and Iain Chalmers. 2010. {``Seventy-Five
Trials and Eleven Systematic Reviews a Day: How Will We Ever Keep Up?''}
\emph{PLoS Medicine} 7 (9): e1000326.

\leavevmode\hypertarget{ref-batista2004study}{}%
Batista, Gustavo EAPA, Ronaldo C Prati, and Maria Carolina Monard. 2004.
{``A Study of the Behavior of Several Methods for Balancing Machine
Learning Training Data.''} \emph{ACM SIGKDD Explorations Newsletter} 6
(1): 20--29.

\leavevmode\hypertarget{ref-bekhuis2010towards}{}%
Bekhuis, Tanja, and Dina Demner-Fushman. 2010. {``Towards Automating the
Initial Screening Phase of a Systematic Review.''} \emph{MEDINFO 2010},
146--50.

\leavevmode\hypertarget{ref-bekhuis2012screening}{}%
---------. 2012. {``Screening Nonrandomized Studies for Medical
Systematic Reviews: A Comparative Study of Classifiers.''}
\emph{Artificial Intelligence in Medicine} 55 (3): 197--207.

\leavevmode\hypertarget{ref-beller2013systematic}{}%
Beller, Elaine M, Joyce Kee-Hsin Chen, Una Li-Hsiang Wang, and Paul P
Glasziou. 2013. {``Are Systematic Reviews up-to-Date at the Time of
Publication?''} \emph{Systematic Reviews} 2 (1): 1--6.

\leavevmode\hypertarget{ref-beller2018making}{}%
Beller, Elaine, Justin Clark, Guy Tsafnat, Clive Adams, Heinz Diehl,
Hans Lund, Mourad Ouzzani, et al. 2018. {``Making Progress with the
Automation of Systematic Reviews: Principles of the International
Collaboration for the Automation of Systematic Reviews (ICASR).''}
\emph{Systematic Reviews} 7 (1): 1--7.

\leavevmode\hypertarget{ref-bhatt2020machine}{}%
Bhatt, Umang, McKane Andrus, Adrian Weller, and Alice Xiang. 2020.
{``Machine Learning Explainability for External Stakeholders.''}
\emph{arXiv Preprint arXiv:2007.05408}.

\leavevmode\hypertarget{ref-bibal2021legal}{}%
Bibal, Adrien, Michael Lognoul, Alexandre De Streel, and Benoît Frénay.
2021. {``Legal Requirements on Explainability in Machine Learning.''}
\emph{Artificial Intelligence and Law} 29 (2): 149--69.

\leavevmode\hypertarget{ref-bibal2020impact}{}%
Bibal, Adrien, Michael Lognoul, Alexandre de Streel, and Benoît Frénay.
2020. {``Impact of Legal Requirements on Explainability in Machine
Learning.''} \emph{arXiv Preprint arXiv:2007.05479}.

\leavevmode\hypertarget{ref-blanco2019machine}{}%
Blanco-Justicia, Alberto, and Josep Domingo-Ferrer. 2019. {``Machine
Learning Explainability Through Comprehensible Decision Trees.''} In
\emph{International Cross-Domain Conference for Machine Learning and
Knowledge Extraction}, 15--26. Springer.

\leavevmode\hypertarget{ref-bollegala2015embedding}{}%
Bollegala, Danushka, Takanori Maehara, and Ken-ichi Kawarabayashi. 2015.
{``Embedding Semantic Relations into Word Representations.''} In
\emph{Twenty-Fourth International Joint Conference on Artificial
Intelligence}.

\leavevmode\hypertarget{ref-borah2017analysis}{}%
Borah, Rohit, Andrew W Brown, Patrice L Capers, and Kathryn A Kaiser.
2017. {``Analysis of the Time and Workers Needed to Conduct Systematic
Reviews of Medical Interventions Using Data from the PROSPERO
Registry.''} \emph{BMJ Open} 7 (2): e012545.

\leavevmode\hypertarget{ref-bornmann2015growth}{}%
Bornmann, Lutz, and Rüdiger Mutz. 2015. {``Growth Rates of Modern
Science: A Bibliometric Analysis Based on the Number of Publications and
Cited References.''} \emph{Journal of the Association for Information
Science and Technology} 66 (11): 2215--22.

\leavevmode\hypertarget{ref-breiman1996bagging}{}%
Breiman, Leo. 1996. {``Bagging Predictors.''} \emph{Machine Learning} 24
(2): 123--40.

\leavevmode\hypertarget{ref-burkart2021survey}{}%
Burkart, Nadia, and Marco F Huber. 2021. {``A Survey on the
Explainability of Supervised Machine Learning.''} \emph{Journal of
Artificial Intelligence Research} 70: 245--317.

\leavevmode\hypertarget{ref-chae1993presenting}{}%
Chae, Kyung-Chul. 1993. {``Presenting the Negative Hypergeometric
Distribution to the Introductory Statistics Courses.''}
\emph{International Journal of Mathematical Education in Science and
Technology} 24 (4): 523--26.

\leavevmode\hypertarget{ref-chawla2004special}{}%
Chawla, Nitesh V, Nathalie Japkowicz, and Aleksander Kotcz. 2004.
{``Special Issue on Learning from Imbalanced Data Sets.''} \emph{ACM
SIGKDD Explorations Newsletter} 6 (1): 1--6.

\leavevmode\hypertarget{ref-chen2018approximate}{}%
Chen, Chao, Xiao Lin, and Gabriel Terejanu. 2018. {``An Approximate
Bayesian Long Short-Term Memory Algorithm for Outlier Detection.''} In
\emph{2018 24th International Conference on Pattern Recognition (ICPR)},
201--6. IEEE.

\leavevmode\hypertarget{ref-chen2016short}{}%
Chen, Qiuxing, Lixiu Yao, and Jie Yang. 2016. {``Short Text
Classification Based on LDA Topic Model.''} In \emph{2016 International
Conference on Audio, Language and Image Processing (ICALIP)}, 749--53.
IEEE.

\leavevmode\hypertarget{ref-chen2015gaussian}{}%
Chen, Sih-Huei, Yuan-Shan Lee, Tzu-Chiang Tai, and Jia-Ching Wang. 2015.
{``Gaussian Process Based Text Categorization for Healthy
Information.''} In \emph{2015 International Conference on Orange
Technologies (ICOT)}, 30--33.
\url{https://doi.org/10.1109/ICOT.2015.7498487}.

\leavevmode\hypertarget{ref-cheng2019document}{}%
Cheng, Y, Z Ye, M Wang, and Q Zhang. 2019. {``Document Classification
Based on Convolutional Neural Network and Hierarchical Attention
Network.''} \emph{Neural Network World} 29 (2): 83--98.

\leavevmode\hypertarget{ref-chipman2010bart}{}%
Chipman, Hugh A, Edward I George, Robert E McCulloch, and others. 2010.
{``BART: Bayesian Additive Regression Trees.''} \emph{The Annals of
Applied Statistics} 4 (1): 266--98.

\leavevmode\hypertarget{ref-claesen2015hyperparameter}{}%
Claesen, Marc, and Bart De Moor. 2015. {``Hyperparameter Search in
Machine Learning.''} \emph{arXiv Preprint arXiv:1502.02127}.

\leavevmode\hypertarget{ref-cohen2010evidence}{}%
Cohen, Aaron M, Clive E Adams, John M Davis, Clement Yu, Philip S Yu,
Weiyi Meng, Lorna Duggan, Marian McDonagh, and Neil R Smalheiser. 2010.
{``Evidence-Based Medicine, the Essential Role of Systematic Reviews,
and the Need for Automated Text Mining Tools.''} In \emph{Proceedings of
the 1st ACM International Health Informatics Symposium}, 376--80.

\leavevmode\hypertarget{ref-cohen2006reducing}{}%
Cohen, Aaron M, William R Hersh, Kim Peterson, and Po-Yin Yen. 2006.
{``Reducing Workload in Systematic Review Preparation Using Automated
Citation Classification.''} \emph{Journal of the American Medical
Informatics Association} 13 (2): 206--19.

\leavevmode\hypertarget{ref-cohen2008getting}{}%
Cohen, K Bretonnel, and Lawrence Hunter. 2008. {``Getting Started in
Text Mining.''} \emph{PLoS Computational Biology} 4 (1): e20.

\leavevmode\hypertarget{ref-dietterich2000ensemble}{}%
Dietterich, Thomas G. 2000. {``Ensemble Methods in Machine Learning.''}
In \emph{International Workshop on Multiple Classifier Systems}, 1--15.
Springer.

\leavevmode\hypertarget{ref-diez2015diversity}{}%
Díez-Pastor, José F, Juan J Rodríguez, César I García-Osorio, and
Ludmila I Kuncheva. 2015. {``Diversity Techniques Improve the
Performance of the Best Imbalance Learning Ensembles.''}
\emph{Information Sciences} 325: 98--117.

\leavevmode\hypertarget{ref-edwards2002identification}{}%
Edwards, Phil, Mike Clarke, Carolyn DiGuiseppi, Sarah Pratap, Ian
Roberts, and Reinhard Wentz. 2002. {``Identification of Randomized
Controlled Trials in Systematic Reviews: Accuracy and Reliability of
Screening Records.''} \emph{Statistics in Medicine} 21 (11): 1635--40.

\leavevmode\hypertarget{ref-eppstein2010listing}{}%
Eppstein, David, Maarten Löffler, and Darren Strash. 2010. {``Listing
All Maximal Cliques in Sparse Graphs in Near-Optimal Time.''} In
\emph{International Symposium on Algorithms and Computation}, 403--14.
Springer.

\leavevmode\hypertarget{ref-farkas1995document}{}%
Farkas, Jennifer. 1995. {``Document Classification and Recurrent Neural
Networks.''} In \emph{Proceedings of the 1995 Conference of the Centre
for Advanced Studies on Collaborative Research}, 21.

\leavevmode\hypertarget{ref-frunza2010building}{}%
Frunza, Oana, Diana Inkpen, and Stan Matwin. 2010. {``Building
Systematic Reviews Using Automatic Text Classification Techniques.''} In
\emph{Coling 2010: Posters}, 303--11.

\leavevmode\hypertarget{ref-galar2011review}{}%
Galar, Mikel, Alberto Fernandez, Edurne Barrenechea, Humberto Bustince,
and Francisco Herrera. 2011. {``A Review on Ensembles for the Class
Imbalance Problem: Bagging-, Boosting-, and Hybrid-Based Approaches.''}
\emph{IEEE Transactions on Systems, Man, and Cybernetics, Part C
(Applications and Reviews)} 42 (4): 463--84.

\leavevmode\hypertarget{ref-gelman2019r}{}%
Gelman, Andrew, Ben Goodrich, Jonah Gabry, and Aki Vehtari. 2019.
{``R-Squared for Bayesian Regression Models.''} \emph{The American
Statistician}.

\leavevmode\hypertarget{ref-hammerstrom2010searching}{}%
Hammerstrøm, Karianne, Anne Wade, Anne-Marie Klint Jørgensen, and
Karianne Hammerstrøm. 2010. {``Searching for Studies.''}
\emph{Education} 54 (11.3).

\leavevmode\hypertarget{ref-hansen2000bayesian}{}%
Hansen, Lars Kai, and others. 2000. {``Bayesian Averaging Is
Well-Temperated.''} In \emph{Proceedings of NIPS}, 99:265--71.

\leavevmode\hypertarget{ref-harremoes2001maximum}{}%
Harremoës, Peter, and Flemming Topsøe. 2001. {``Maximum Entropy
Fundamentals.''} \emph{Entropy} 3 (3): 191--226.

\leavevmode\hypertarget{ref-hastie2009boosting}{}%
Hastie, Trevor, Robert Tibshirani, and Jerome Friedman. 2009.
{``Boosting and Additive Trees.''} In \emph{The Elements of Statistical
Learning}, 337--87. Springer.

\leavevmode\hypertarget{ref-higgins2019cochrane}{}%
Higgins, Julian PT, James Thomas, Jacqueline Chandler, Miranda Cumpston,
Tianjing Li, Matthew J Page, and Vivian A Welch. 2019. \emph{Cochrane
Handbook for Systematic Reviews of Interventions}. John Wiley \& Sons.

\leavevmode\hypertarget{ref-horbach2020pandemic}{}%
Horbach, Serge PJM. 2020. {``Pandemic Publishing: Medical Journals
Strongly Speed up Their Publication Process for COVID-19.''}
\emph{Quantitative Science Studies} 1 (3): 1056--67.

\leavevmode\hypertarget{ref-hoy2020rise}{}%
Hoy, Matthew B. 2020. {``Rise of the Rxivs: How Preprint Servers Are
Changing the Publishing Process.''} \emph{Medical Reference Services
Quarterly} 39 (1): 84--89.

\leavevmode\hypertarget{ref-ikonomakis2005text}{}%
Ikonomakis, M, Sotiris Kotsiantis, and V Tampakas. 2005. {``Text
Classification Using Machine Learning Techniques.''} \emph{WSEAS
Transactions on Computers} 4 (8): 966--74.

\leavevmode\hypertarget{ref-james2013introduction}{}%
James, Gareth, Daniela Witten, Trevor Hastie, and Robert Tibshirani.
2013. \emph{An Introduction to Statistical Learning}. Vol. 112.
Springer.

\leavevmode\hypertarget{ref-jayashree2020evaluation}{}%
Jayashree, P, and PK Srijith. 2020. {``Evaluation of Deep Gaussian
Processes for Text Classification.''} In \emph{Proceedings of the 12th
Language Resources and Evaluation Conference}, 1485--91.

\leavevmode\hypertarget{ref-jonnalagadda2015automating}{}%
Jonnalagadda, Siddhartha R, Pawan Goyal, and Mark D Huffman. 2015.
{``Automating Data Extraction in Systematic Reviews: A Systematic
Review.''} \emph{Systematic Reviews} 4 (1): 1--16.

\leavevmode\hypertarget{ref-joo2020being}{}%
Joo, Taejong, Uijung Chung, and Min-Gwan Seo. 2020. {``Being Bayesian
about Categorical Probability.''} In \emph{International Conference on
Machine Learning}, 4950--61. PMLR.

\leavevmode\hypertarget{ref-jospin2020hands}{}%
Jospin, Laurent Valentin, Wray Buntine, Farid Boussaid, Hamid Laga, and
Mohammed Bennamoun. 2020. {``Hands-on Bayesian Neural Networks--a
Tutorial for Deep Learning Users.''} \emph{arXiv Preprint
arXiv:2007.06823}.

\leavevmode\hypertarget{ref-kapelner2013bartmachine}{}%
Kapelner, Adam, and Justin Bleich. 2013. {``bartMachine: Machine
Learning with Bayesian Additive Regression Trees.''} \emph{arXiv
Preprint arXiv:1312.2171}.

\leavevmode\hypertarget{ref-kapelner2015prediction}{}%
---------. 2015. {``Prediction with Missing Data via Bayesian Additive
Regression Trees.''} \emph{Canadian Journal of Statistics} 43 (2):
224--39.

\leavevmode\hypertarget{ref-khoshgoftaar2010comparing}{}%
Khoshgoftaar, Taghi M, Jason Van Hulse, and Amri Napolitano. 2010.
{``Comparing Boosting and Bagging Techniques with Noisy and Imbalanced
Data.''} \emph{IEEE Transactions on Systems, Man, and Cybernetics-Part
A: Systems and Humans} 41 (3): 552--68.

\leavevmode\hypertarget{ref-kohavi1995study}{}%
Kohavi, Ron, and others. 1995. {``A Study of Cross-Validation and
Bootstrap for Accuracy Estimation and Model Selection.''} In
\emph{Ijcai}, 14:1137--45. 2. Montreal, Canada.

\leavevmode\hypertarget{ref-lai2015recurrent}{}%
Lai, Siwei, Liheng Xu, Kang Liu, and Jun Zhao. 2015. {``Recurrent
Convolutional Neural Networks for Text Classification.''} In
\emph{Twenty-Ninth AAAI Conference on Artificial Intelligence}.

\leavevmode\hypertarget{ref-landauer1998introduction}{}%
Landauer, Thomas K, Peter W Foltz, and Darrell Laham. 1998. {``An
Introduction to Latent Semantic Analysis.''} \emph{Discourse Processes}
25 (2-3): 259--84.

\leavevmode\hypertarget{ref-larsen2010rate}{}%
Larsen, Peder, and Markus Von Ins. 2010. {``The Rate of Growth in
Scientific Publication and the Decline in Coverage Provided by Science
Citation Index.''} \emph{Scientometrics} 84 (3): 575--603.

\leavevmode\hypertarget{ref-laws2008stopping}{}%
Laws, Florian, and Hinrich Schütze. 2008. {``Stopping Criteria for
Active Learning of Named Entity Recognition.''} In \emph{Proceedings of
the 22nd International Conference on Computational Linguistics (Coling
2008)}, 465--72.

\leavevmode\hypertarget{ref-lefebvre2011searching}{}%
Lefebvre, C, E Manheimer, J Glanville, J Higgins, and S Green. 2011.
{``Searching for Studies (Chapter 6).''} \emph{Cochrane Handbook for
Systematic Reviews of Interventions Version} 510.

\leavevmode\hypertarget{ref-li2020survey}{}%
Li, Qian, Hao Peng, Jianxin Li, Congying Xia, Renyu Yang, Lichao Sun,
Philip S Yu, and Lifang He. 2020. {``A Survey on Text Classification:
From Shallow to Deep Learning.''} \emph{arXiv Preprint
arXiv:2008.00364}.

\leavevmode\hypertarget{ref-lipscomb2000medical}{}%
Lipscomb, Carolyn E. 2000. {``Medical Subject Headings (MeSH).''}
\emph{Bulletin of the Medical Library Association} 88 (3): 265.

\leavevmode\hypertarget{ref-malhi2020explainable}{}%
Malhi, Avleen, Samanta Knapic, and Kary Främling. 2020. {``Explainable
Agents for Less Bias in Human-Agent Decision Making.''} In
\emph{International Workshop on Explainable, Transparent Autonomous
Agents and Multi-Agent Systems}, 129--46. Springer.

\leavevmode\hypertarget{ref-marshall2015systematic}{}%
Marshall, Iain J, and Byron C Wallace. 2019. {``Toward Systematic Review
Automation: A Practical Guide to Using Machine Learning Tools in
Research Synthesis.''} In \emph{Systematic Reviews}, 8:1--10. 1.
Springer.

\leavevmode\hypertarget{ref-minaee2021deep}{}%
Minaee, Shervin, Nal Kalchbrenner, Erik Cambria, Narjes Nikzad, Meysam
Chenaghlu, and Jianfeng Gao. 2021. {``Deep Learning--Based Text
Classification: A Comprehensive Review.''} \emph{ACM Computing Surveys
(CSUR)} 54 (3): 1--40.

\leavevmode\hypertarget{ref-miwa2014reducing}{}%
Miwa, Makoto, James Thomas, Alison O'Mara-Eves, and Sophia Ananiadou.
2014. {``Reducing Systematic Review Workload Through Certainty-Based
Screening.''} \emph{Journal of Biomedical Informatics} 51: 242--53.

\leavevmode\hypertarget{ref-moore2018transparent}{}%
Moore, Alexander, Vanessa Murdock, Yaxiong Cai, and Kristine Jones.
2018. {``Transparent Tree Ensembles.''} In \emph{The 41st International
ACM SIGIR Conference on Research \& Development in Information
Retrieval}, 1241--44.

\leavevmode\hypertarget{ref-pubmedUpdate}{}%
{``NCBI Insights : Updated Pubmed e-Utilities Coming in April 2022!''}
n.d. U.S. National Library of Medicine.
\url{https://ncbiinsights.ncbi.nlm.nih.gov/2021/10/05/updated-pubmed-api/}.

\leavevmode\hypertarget{ref-o2015using}{}%
O'Mara-Eves, Alison, James Thomas, John McNaught, Makoto Miwa, and
Sophia Ananiadou. 2015. {``Using Text Mining for Study Identification in
Systematic Reviews: A Systematic Review of Current Approaches.''}
\emph{Systematic Reviews} 4 (1): 1--22.

\leavevmode\hypertarget{ref-ohsawa1998keygraph}{}%
Ohsawa, Yukio, Nels E Benson, and Masahiko Yachida. 1998. {``KeyGraph:
Automatic Indexing by Co-Occurrence Graph Based on Building Construction
Metaphor.''} In \emph{Proceedings IEEE International Forum on Research
and Technology Advances in Digital Libraries-ADL'98-}, 12--18. IEEE.

\leavevmode\hypertarget{ref-olorisade2016critical}{}%
Olorisade, Babatunde K, Ed de Quincey, Pearl Brereton, and Peter Andras.
2016. {``A Critical Analysis of Studies That Address the Use of Text
Mining for Citation Screening in Systematic Reviews.''} In
\emph{Proceedings of the 20th International Conference on Evaluation and
Assessment in Software Engineering}, 1--11.

\leavevmode\hypertarget{ref-pavlinek2017text}{}%
Pavlinek, Miha, and Vili Podgorelec. 2017. {``Text Classification Method
Based on Self-Training and LDA Topic Models.''} \emph{Expert Systems
with Applications} 80: 83--93.

\leavevmode\hypertarget{ref-poulter2008mscanner}{}%
Poulter, Graham L, Daniel L Rubin, Russ B Altman, and Cathal Seoighe.
2008. {``MScanner: A Classifier for Retrieving Medline Citations.''}
\emph{BMC Bioinformatics} 9 (1): 1--12.

\leavevmode\hypertarget{ref-rstat}{}%
R Core Team. 2020. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\leavevmode\hypertarget{ref-ramezankhani2016impact}{}%
Ramezankhani, Azra, Omid Pournik, Jamal Shahrabi, Fereidoun Azizi,
Farzad Hadaegh, and Davood Khalili. 2016. {``The Impact of Oversampling
with SMOTE on the Performance of 3 Classifiers in Prediction of Type 2
Diabetes.''} \emph{Medical Decision Making} 36 (1): 137--44.

\leavevmode\hypertarget{ref-robert2004monte}{}%
Robert, Christian P, George Casella, and George Casella. 2004.
\emph{Monte Carlo Statistical Methods}. Vol. 2. Springer.

\leavevmode\hypertarget{ref-roshan2020improvement}{}%
Roshan, Seyed Ehsan, and Shahrokh Asadi. 2020. {``Improvement of Bagging
Performance for Classification of Imbalanced Datasets Using Evolutionary
Multi-Objective Optimization.''} \emph{Engineering Applications of
Artificial Intelligence} 87: 103319.

\leavevmode\hypertarget{ref-rousseau2015graph}{}%
Rousseau, Francois. 2015. {``Graph-of-Words: Mining and Retrieving Text
with Networks of Features.''} PhD thesis, Ph. D. dissertation.

\leavevmode\hypertarget{ref-rousseau2015text}{}%
Rousseau, François, Emmanouil Kiagias, and Michalis Vazirgiannis. 2015.
{``Text Categorization as a Graph Classification Problem.''} In
\emph{Proceedings of the 53rd Annual Meeting of the Association for
Computational Linguistics and the 7th International Joint Conference on
Natural Language Processing (Volume 1: Long Papers)}, 1702--12.

\leavevmode\hypertarget{ref-newis}{}%
Sadaghiani, Catharina, Tjibbe Donker, Xanthi Andrianou, Balázs Babarczy,
Gerolf De Boer, Francesco Di Ruscio, Shona Cairns, et al. 2020.
\emph{National Health Care Infrastructures, Health Care Utilization and
Patient Movements Between Hospitals - Networks Working to Improve
Surveillance: A Systematic Literature Review}. PROSPERO.
\url{http://www.crd.york.ac.uk/PROSPERO/display_record.asp?ID=CRD42020157987}.

\leavevmode\hypertarget{ref-sampson2011precision}{}%
Sampson, Margaret, Jennifer Tetzlaff, and Christine Urquhart. 2011.
{``Precision of Healthcare Systematic Review Searches in a
Cross-Sectional Sample.''} \emph{Research Synthesis Methods} 2 (2):
119--25.

\leavevmode\hypertarget{ref-schonlau2017text}{}%
Schonlau, Matthias, and Nick Guenther. 2017. {``Text Mining Using
n-Grams.''} \emph{Schonlau, M., Guenther, N. Sucholutsky, I. Text Mining
Using n-Gram Variables. The Stata Journal} 17 (4): 866--81.

\leavevmode\hypertarget{ref-settles2009active}{}%
Settles, Burr. 2009. {``Active Learning Literature Survey.''}

\leavevmode\hypertarget{ref-soria2011belm}{}%
Soria-Olivas, Emilio, Juan Gomez-Sanchis, José D Martin, Joan
Vila-Frances, Marcelino Martinez, José R Magdalena, and Antonio J
Serrano. 2011. {``BELM: Bayesian Extreme Learning Machine.''} \emph{IEEE
Transactions on Neural Networks} 22 (3): 505--9.

\leavevmode\hypertarget{ref-soto2019thalia}{}%
Soto, Axel J, Piotr Przybyła, and Sophia Ananiadou. 2019. {``Thalia:
Semantic Search Engine for Biomedical Abstracts.''}
\emph{Bioinformatics} 35 (10): 1799--1801.

\leavevmode\hypertarget{ref-tashman2000out}{}%
Tashman, Leonard J. 2000. {``Out-of-Sample Tests of Forecasting
Accuracy: An Analysis and Review.''} \emph{International Journal of
Forecasting} 16 (4): 437--50.

\leavevmode\hypertarget{ref-rpart}{}%
Therneau, Terry, and Beth Atkinson. 2019. \emph{Rpart: Recursive
Partitioning and Regression Trees}.
\url{https://CRAN.R-project.org/package=rpart}.

\leavevmode\hypertarget{ref-thomas2007eppi}{}%
Thomas, James, and Jeff Brunton. 2007. {``EPPI-Reviewer: Software for
Research Synthesis.''}

\leavevmode\hypertarget{ref-tsafnat2013automation}{}%
Tsafnat, Guy, Adam Dunn, Paul Glasziou, and Enrico Coiera. 2013. {``The
Automation of Systematic Reviews.''} British Medical Journal Publishing
Group.

\leavevmode\hypertarget{ref-tsafnat2014systematic}{}%
Tsafnat, Guy, Paul Glasziou, Miew Keen Choong, Adam Dunn, Filippo
Galgani, and Enrico Coiera. 2014. {``Systematic Review Automation
Technologies.''} \emph{Systematic Reviews} 3 (1): 1--15.

\leavevmode\hypertarget{ref-turian2010word}{}%
Turian, Joseph, Lev Ratinov, and Yoshua Bengio. 2010. {``Word
Representations: A Simple and General Method for Semi-Supervised
Learning.''} In \emph{Proceedings of the 48th Annual Meeting of the
Association for Computational Linguistics}, 384--94.

\leavevmode\hypertarget{ref-violos2016sentiment}{}%
Violos, John, Konstantinos Tserpes, Evangelos Psomakelis, Konstantinos
Psychas, and Theodora Varvarigou. 2016. {``Sentiment Analysis Using
Word-Graphs.''} In \emph{Proceedings of the 6th International Conference
on Web Intelligence, Mining and Semantics}, 1--9.

\leavevmode\hypertarget{ref-visser2010performing}{}%
Visser, Eelco. 2010. {``Performing Systematic Literature Reviews with
Researchr: Tool Demonstration.''} \emph{Technical Report Series
TUD-SERG-2010-010}.

\leavevmode\hypertarget{ref-wallace2010active}{}%
Wallace, Byron C, Kevin Small, Carla E Brodley, and Thomas A Trikalinos.
2010. {``Active Learning for Biomedical Citation Screening.''} In
\emph{Proceedings of the 16th ACM SIGKDD International Conference on
Knowledge Discovery and Data Mining}, 173--82.

\leavevmode\hypertarget{ref-wallace2010semi}{}%
Wallace, Byron C, Thomas A Trikalinos, Joseph Lau, Carla Brodley, and
Christopher H Schmid. 2010. {``Semi-Automated Screening of Biomedical
Citations for Systematic Reviews.''} \emph{BMC Bioinformatics} 11 (1):
1--11.

\leavevmode\hypertarget{ref-wilkins2005embase}{}%
Wilkins, Thad, Ralph A Gillies, and Kathy Davies. 2005. {``EMBASE Versus
MEDLINE for Family Medicine Searches: Can MEDLINE Searches Find the
Forest or a Tree?''} \emph{Canadian Family Physician} 51 (6): 848--49.

\leavevmode\hypertarget{ref-woods1998medline}{}%
Woods, David, and Kate Trewheellar. 1998. {``Medline and Embase
Complement Each Other in Literature Searches.''} \emph{BMJ: British
Medical Journal} 316 (7138): 1166.

\leavevmode\hypertarget{ref-yang2020survey}{}%
Yang, JinXiong, Liang Bai, and Yanming Guo. 2020. {``A Survey of Text
Classification Models.''} In \emph{Proceedings of the 2020 2nd
International Conference on Robotics, Intelligent Control and Artificial
Intelligence}, 327--34.

\leavevmode\hypertarget{ref-yang2020hyperparameter}{}%
Yang, Li, and Abdallah Shami. 2020. {``On Hyperparameter Optimization of
Machine Learning Algorithms: Theory and Practice.''}
\emph{Neurocomputing} 415: 295--316.

\leavevmode\hypertarget{ref-zhou2021ensemble}{}%
Zhou, Zhi-Hua. 2021. {``Ensemble Learning.''} In \emph{Machine
Learning}, 181--210. Springer.

\leavevmode\hypertarget{ref-zhu2010confidence}{}%
Zhu, Jingbo, Huizhen Wang, Eduard Hovy, and Matthew Ma. 2010.
{``Confidence-Based Stopping Criteria for Active Learning for Data
Annotation.''} \emph{ACM Transactions on Speech and Language Processing
(TSLP)} 6 (3): 1--24.

\end{CSLReferences}

\bibliographystyle{unsrt}
\bibliography{references.bib}

\end{document}

### 2021-10-25 Manuscript/Manuscript_Discussion.Rmd
update

@@
 
-## Discussion
+# Discussion
 
-We propose a new integrated framework to help researcher collect and screen research publications characterized by high performance and versatility, joining the growing field of systematic review automatization (SRA) and helpers (SRH) tools.\
-The International Collaboration for the Automation of Systematic Reviews (ICASR) proposes a number of features tools for automatic research synthesis should possess, defining the so called Vienna Principles [@beller2018making].We tried to adopt some of the concepts advocated by the ICAS; for example we are sharing the tool as an open source R package, and we tried to follow the paradigms of modular programming [@mccracken2003modular], building separated components communicating through intermediate outputs stored in common formats (Comma Separated Values/Microsoft Excel™), which make it possible for users to extend the framework or integrate it with other tools in their pipeline.\
-Our framework has two main components, an integrated query-based citation search and management engine and an active machine learning record screener\
+We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
+This framework joins standard approaches and uses ad-hoc solutions to deal with common SRA issues.\
+By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
+Our tool consists of four main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) a Bayesian active machine learning-based citation classifier, and 4) a data-driven search query generation algorithm.\
 
-Our search engine is capable of automatically collecting citation data from three well known scientific databases, that is, Pubmed, Web of Science and the database of the Institute of Electrical and Electronics Engineers, implementing also institutional access rights; in addition, it can process manually downloaded results from all mentioned databases plus records from the SCOPUS and EMBASE databases.
-Once the citations are downloaded, they are translated in a uniform format and deduplicated.
-The online search algorithm is efficient enough to manage tens of thousands of search results, using various expedients to overcome the online databases limitations in terms of traffic and download quota.
-Most SRH tools we are aware of, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/), often focused on a particular topic [@visser2010performing] or relying on only one external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].
-To our knowledge, our tool is the first capable to fully automatize searching on three different well known scientific databases and to import raw data from five of them.
-Mixing different database is fundamental to have a more complete view of the literature on a topic [@bajpai2011search; @wilkins2005embase; @woods1998medline]: in our results, 18.7% of the positive matches were unique for one of the different data sources and no positive record was present among all of them (data not shown).\
+The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e.
+Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases.
+In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
+Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
+in our results, 18.7% of the positive matches found were unique for one of the different data sources, and no positive record was present in all of them (data not shown).\ 
+The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the online database in terms of traffic and download quota.\
+The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
+The preliminary ordering allow to increase the positivity rate in the initial training set [@wallace2010active].
 
-Modern NLP techniques were used to transform textual data into actionable numeric inputs [@ananiadou2006text; @cohen2008getting].
-One particular improvement was to use network analysis to identify associated terms, which we labelled as non-consecutive ngrams, which confer particular meaning when present together into a text while not necessary being close to each other.
-A similar network approach was used to merge redundant terms, in order to make model estimation more efficient and reduce possible noise.
-The use of network inspired modeling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text] and is a valuable tool to extract semantic information not evident in one-word of consecutive ngram models.
+The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
+We did not include classical n-grams [@schonlau2017text], but we used network analysis to find non-consecutive frequently associated terms, a generalisation of n-grams relaxing the term adjacency assumption.
+A similar network approach was applied to merge redundant terms to make model estimation more efficient and reduce noise.\
+The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\
 
-The citation screening functionality of the framework implements active machine learning based document classification, adopting best practices and bringing further improvements at various levels.
-At the base of our classification algorithm we use BART [@chipman2010bart; @kapelner2013bartmachine], a Bayesian machine learning technique characterized by exceptional predictive performance and speed even in large dataset.
-This model builds consecutive decision trees associating the presence/absence of set of terms to the probability of a positive match, each tree trying to decrease the prediction error of the precedent one [@hastie2009boosting].
-The Bayesian approach explore distributions of trees which are justified by the data, while using a set of prior distributions to avoid overfitting by discouraging excessively deep trees, long sequences of trees, or extreme predicted probabilities.
-To further improve generalizability we ran multiple replications of the model and then averaged their record predictive distributions; this technique is called ensembling and it has been shown to improve out-of-sample predictive performance [].
-In a Bayesian setting, this effect comes from a reduction of the probability mass in the tails of the predictive distributions while not shifting their locations (i.e., it decreases variance without impacting bias) [bias/variance tradeoff, better if in Bayesian analysis and/or focusing to ensemble].
-Instead, imposing stronger general priors against extreme predictions would decreased variance but also shifted the distribution mass towards a non-decision zone, therefore increasing bias.
-In our data it can be seen how using more then one model replica greatly improved sensitivity and efficiency, with a performance stabilization after 10 replicas (Suppl.
-Mat.
-S2); since the number of model replicas greatly impacted computation times we decided to use ten replicas since it was also associated with the higher sensitivity in the same performance cluster.
-The variability between models derives only from the randomness in the MCMC fitting phase []; an alternative was to impose additional variability by bootstrapping [] but this approach actually decreased performance (Suppl.
-Mat.
-S2), probably due to the low proportion of positive matches in the data and the loss of information with bootstrapping in unbalanced classification tasks [].\
-The strong imbalance between relevant and non-relevant records [@sampson2011precision] can affect sensitivity [].
-To overcome the problem, we oversampled the positive records ten times before model fitting.
-Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance.
-An alternative approach would be record weighting to change error costs during estimation [] but the BART implementation we used did not allow observation weighting and using simple oversampling allows to use different modeling engines.
-Also, the simple query ordering of the record during the creation of the initial training set allowed to have a far higher prevalence of relevant records (17.2%) compared to the overall one (0.11%) and this boosts the overall sensitivity of the model.
-A known risk with oversampling of the target class is the missclassification of negative records as positive [], but since in our approach all predicted positive are manually reviewed we are ensured to achieve always 100% specificity/positive predictive value.\
-One of the innovation in our approach is the overcoming of simple stopping rules in SRA classification tasks [].
-Static supervised learning models requires to manually label a certain amount of records (i.e., the training set) which are then used to train the algorithm and classify the rest (the test set) [], but this method requires to decide the size of the training set in advance.
-Active learning tries to alleviate the problem by splitting the classification task in an iterative process in which prediction and review phases alternate, but even in this case, one has to define a stopping rule regarding how many records to screen manually in every iteration [].
-By exploiting the Bayesian nature of BART we produce a distribution of probabilities and not a single value for each record; by joining these distribution in the positive and negative record groups it's possible to identify a "uncertainty zone" so that all record whose predictive distribution crosses this zone needs manual verification.
-Therefore the researcher will have a defined number or records to check at every iteration which dynamically decreases as uncertain predictions are reviewed and the uncertainty shrinks (Suppl.
-Mat.
-S2 Fig.
-1).
-In this model, researcher do not need to choose a priori the number of records to review but just the size of the uncertainty zone (by setting the PPD quantiles used to built it) and after how many iterations with no new positive matches to stop; both the parameters are more theoretical and general than a simple stopping rule and nevertheless the hyperparameter tuning did not indicate a big impact of these parameters.
-Since our approach requires researchers to review both unlabelled records with a positive predicted label and those with a PPD inside the uncertainty zone, it can be considered as a unifying syinthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\
+The framework's record classification module implements an active machine learning approach [@settles2009active, @miwa2014reducing] and is based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine].
+When implementing our algorithm we adopted best practices from other SRA studies, bringing improvements at various levels.\
+As with other boosted trees algorithms [@hastie2009boosting], BART can explore complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.\
+However, its Bayesian foundation provides further benefits:
+less sensitivity on hyperparameter choices, natural regularisation through priors, and, especially, predictive distributions as output in place of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
+By selecting relatively tight prior distributions, we discouraged excessively deep trees, long sequences of trees, or extreme predicted probabilities, to decrease the risk of overfitting.\
+The algorithm runs multiple replications of the model and averages their predictive distributions creating an "ensemble";
+this technique has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble], as we were able to confirm during the hyperparameter evaluation (Supplemental Material S2).
+Ensembling reduces the uncertainty in the predictive distribution tails related to the randomness in the MCMC fit [@robert2004monte], generating a shift of probability mass towards the distribution centre and stabilising it (i.e., decreasing variance without impacting bias).
+On the other hand, just imposing robust uninformative priors against extreme predictions would have decreased variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
+Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which showed performance stabilisation during the hyperparameter evaluation.\
+We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory [@diez2015diversity], it was demonstrated to be slightly detrimental (Supplemental Material S2) compared to simple ensembling.\
 
-To evaluate performance we avoided the classic random out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study] because we deemed them not realistic in this setting.
-It is assumed that the corpus to be screened is not a random sample, but the entire population of citation for a given query; a random validation would be useful to estimate the performance of this method on a new dataset derived by the same data-generating process, but this is a totally theoretical goal with no usefulness since all the existing data related was alread acquired.
-Instead a more relevant question is to estimate the long run sensitivity of our prediction method in finding all relevant records in the whole data set.
-Since the records are ordered, again a random approach would not work since it assumes that the prevalence of positive records is equal on average in every possible sample [@tashman2000out], while instead it drops as more records are considered (Fig.
+A low rate of relevant matches (class imbalance) is typical in literature reviews [@sampson2011precision; @wallace2010semi; @o2015using], and such strong imbalance between positive and negative records can affect sensitivity [@khoshgoftaar2010comparing; @chawla2004special].\
+To overcome the problem, we oversampled [@batista2004study] the positive records ten times before model fitting.
+Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance.\
+A known risk with positive oversampling is the misclassification of negative records [@ramezankhani2016impact].
+However, since all predicted positives get manually reviewed in our approach, we are always ensured to achieve 100% specificity/positive predictive value: the only price for the increased sensitivity due to oversampling is a larger number of records to review.\
+An alternative to oversampling would be applying different weights and/or cost to the classes [@abd2013review; @diez2015diversity], but the BART implementation we used did not have this feature;
+also, using simple oversampling permits broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
+Finally, ordering the records by query term frequency (simple query ordering) generates a far higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), and this boosts the sensitivity of the model.\
+
+One of the central innovations we introduced is the concept of "uncertainty zone", whose implementation is possible thanks to the Bayesian foundation of the classification model.
+This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig.
+1).\
+This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
+The parameters our algorithm needs are instead quite general and non task-specific, like the PPD intervals based on which the uncertainty zone is built ,and the maximum number of iterations with no positive matches after which a session is concluded;
+the hyperparamer evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to preform well on most datasets.\
+Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\
+
+We evaluated performance as the capability of the screening procedure (automatic classification plus manual review) to find the largest number of relevant records while reviewing as few of them as possible (i.e., sensitivity $\times$ efficiency).\
+We avoided the classic out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study; @james2013introduction].
+Such methods primarily assume that the rate of positivity is equal on average in every random subset of the data [@tashman2000out];
+this uniformity is broken by how the initial training set and the subsequent reviewed records are selected by the query-based ordering and the active learning algorithm, determining a lower positivity rate in the unlabelled records (Fig.
 2).
-We instead used a Bayesian model to estimate the likelihood of a positive match given the prediction scores of the BART model.
-This approach showed to fit the data very well (high $R^2$) and the Bayesian predictive distribution can be exploited to draw a worse case scenario given the data.\
-In our study our approach reached 98.8% sensitivity during the hyperparameter optimization (deterministic, small sample ) and on the whole data set we predicted a theoretical sensitivity of 100% [93.5%, 100%] in the first session and of 97.3% [73.8%, 100%] in the second, a lower value as is expected by the probabilistic accumulation of random events; both results are above the usual results in the field [@o2015using] and in line with the 92% average sensitivity estimated after human only screening [@edwards2002identification].
-In one interesting case, the model spotted a missclassification during initial labeling, demonstrating its robustness and its value also as a second screener, as already suggested by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].\
-Also we showed that such sensitivity was achieved screening just 1.34% of all downloaded records, a sensible reduction in workload; finally, albeit the simple query based ordering did concentrate most of the relevant matches in the first 20-25 thousands records, some relevant records would have required almost the full data set to be manually checked to be found.\
-The model takes ~5-20 minutes per iteration to perform predictions in session 1 (17755 documents) and 20-40 minutes in session 2 (98371 documents) on a 8 core, 2.5 GhZ, 16 GB RAM laptop from 2014 and that equate to 1-3 days per session to manually review and perform predictions, for a total of 1-2 weeks for the whole process, a huge saving of time compared to the months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
-To our knowledge, our data sets are larger than what common in most SRA studies [@o2015using; @olorisade2016critical], emphasizing the reliability of the tool in real world scenarios.\
+Also, a literature corpus is unique per search query/database combination, and therefore any out-of-sample performance estimate is not replicable since no new data can be acquired related to the current corpus.\
+Instead, to estimate overall sensitivity, we employed simple Bayesian regression (surrogate model) on the manually reviewed data to abstract the classification model predictions and achieve a maximum entropy [@harremoes2001maximum] estimate of the number of missed positive matches among the unreviewed records in the whole dataset.
+This simple surrogate model fitted the data very well ($R^2$ consistently above 97%) using just the lower 98% PrI bound of the PPDs as predictor, indicating predictive consistency in the classification model.
+The surrogate model posterior predictive distribution could be exploited to explore worse case scenarios in terms of sensitivity.\
 
-The last component of our framework is a data-driven query generation algorithm.
-The creation of an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximize the number of relevant search results while minimizing the total number of results.
-We propose a solution based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the posterior predicted probabilities; the technique tries to extract high sensitivity subqueries from the labeled data, enrich them with negative terms to increase specificity [@abdelmgeid2008using] and then let researcher evaluate them and pick the most meaningful ones.
-The framework will then join them and remove redundancies.
-The aim is to generate a second query that complement the first human made one and help find possible missing records not found during the first session.\
-The generated query allowed to retrieve few more positive matches not found in session 1 at the cost of a large increase in the amount of documents.
-One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules internalized by the classification model, showing which combination of terms was particularly relevant and even spotting authors and locations associated to the topic of study.
-The generated query therefore acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to spot bias in black box classification algorithms [@malhi2020explainable] and that is increasingly legally required for high-stack machine learning applications [@bibal2021legal; @bibal2020impact].\^
+Our framework achieved very high sensitivity by screening a markedly small fraction of all records, bringing a sensible reduction in workload.\
+Based on the surrogate model, we predicted a predicted median sensitivity of 100% [93.5%, 100%] in the first session (screening 4.29% of records) and of 97.3% [73.8%, 100%] in the second (screening 1.34% of records):
+efficiency increased significantly in the second session since only a few new positive matches were found, but given the large number of records, uncertainty regarding sensitivity also expectedly increased.\
+Both results are above the usual performance in the field [@o2015using] and in line with the 92% average sensitivity estimated after human-only screening [@edwards2002identification].
+In one interesting case, the model spotted a human-made misclassification error, demonstrating its robustness and value as a second screener, a role already suggested for SRA tools by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
+Finally, albeit the simple query ordering already concentrated most of the relevant matches in the first 20-25 thousand records, without the tool support some relevant records would have required almost the complete data set to be manually checked to be found.\
+
+The model took ~5-20 minutes per iteration to perform predictions in session 1 (17,755 documents) and 20-40 minutes in session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM laptop from 2014;
+including manual record review, one session required 1-3 days of work, for a total of 1-2 weeks for the whole process (including record collection).
+That is a considerable saving of time compared to the multiple months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
+To our knowledge, the amount of data processed (~100.000 records) were larger than what is typical in most SRA studies [@o2015using; @olorisade2016critical], emphasising the reliability of the tool in real-world scenarios.\
+
+The last module of our framework is a data-driven query generation algorithm.
+Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to review.
+Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD with a human review step and an efficiency-driven query builder.
+The aim is to generate a second query that helps find records missed during the first session search.
+The generated query allowed indeed to retrieve few more positive matches not found in session 1, but at the cost of a significant increase in the number of documents.\
+One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
+The generated query, therefore, acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to understand and spot bias in black-box classification algorithms [@malhi2020explainable];
+explainability is often required or even legally mandatory for high-stake machine learning applications [@bibal2021legal; @bibal2020impact].\
 It is important to note that this process is entirely data-driven.
-The algorithm is only aware of the "world" defined by the data set, itself generated by a specific search query focused on a particular topic.
-Therefore, the new query may not be specific once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
-The solution we found was to add another component specifying the general topic (antimicrobial resistance and healthcare associated infections) of our research.\
+The algorithm is only aware of the "world" defined by the data set used as input, which is generated by a specific search query focused on a particular topic.
+Therefore, the new query may not be specific enough once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
+The solution we found was to add another component to the query, specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research.\
 
-As reported, our framwork builds on modularity.
-We designed it in order to easily implement complete independency of the main modules in future iterations; especially, we plan to allow users create their custom made components in addition or in place of the original ones, further expanding its functionalities.
-In our view it would be possible to easily add custom citation search and parsing functions for other scientific databases, alternative text features building algorithms and alternative machine learning modules.\
-We deem such interoperability extremely relevant, because the main strength of our tool is the composition of many solutions and the general approach related to Bayesian active machine learning, but each of its components could benefit greatly from the recent improvements in text mining.\
-For example, our text feature generation approach is based on the boolean bag-of-words paradigm, and surely it could be improved by more nuanced text representations: it could be evaluated if feature transformations like Tf-Idf [@baeza1999modern; @ananiadou2006text], would be advantageous, even if we hypothesize that tree based classification algorithms like BART are robust enough to not need such operation.
-Word embedding could be considered, which transform terms in semantic vectors based on the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep], and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context; another option would be to use unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis, etc., [@pavlinek2017text; @chen2016short; @landauer1998introduction] to extract topics to enrich the feature space.\
-Our classification algorithm can be implemented with any Bayesian supervised machine learning method which produces full PPDs; therefore alternative models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
-Even more interesting would be to test  advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher level features in the text like term context and sequences, long distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
+As reported, our framework builds on modularity.
+We designed it to easily implement complete independence of the main modules in future iterations, making it possible for users to add custom features like citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
+We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general idea of Bayesian active machine learning and uncertainty zone.
+However, each of its components could benefit considerably from the recent improvements in text mining.\
+For example, our text processing approach is quite simple, based on the boolean bag-of-words paradigm, and indeed could be improved by more nuanced text representations.
+It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operations.
+Word embedding could be worth exploring:
+this technique transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep] and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.
+Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics to enrich the feature space.\
+Our classification algorithm can be implemented with any Bayesian supervised machine learning method that provides full PPDs;
+therefore alternative classification models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
+Even more interesting would be to test advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher-level features in the text like term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
+Finally, a natural improvement would be to provide a graphical user interface to make the framework easy to use also for less technical users.
+
+The field of literature review automatisation is mature and ripe with innovation, and we expect an increasing use of such technologies to confront the ever-faster production of scientific literature.
+We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.\
+We tried to contribute to the field with an innovative methodology and tool that provides excellent performance and easy integration with existing systematic review pipelines.
+The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of solutions we developed to solve various SRA issues and that can be used to improve existing solutions.

### 2021-10-25 Manuscript/Manuscript_Results.Rmd
update

@@
 
-```{r load framework, cache.rebuild=TRUE}
-source(file.path('R', 'Setup.R'))
+```{r load framework, cache.rebuild=TRUE, include=FALSE}
+source(file.path('R', 'Setup.R'), local = knitr::knit_global())
 
@@
 
-## Results
+# Results
 
@@
 
-### First session
+## First session
 
@@
 
-### Second session
+## Second session
 
@@
 
-### Hyperparameter selection
+## Hyperparameter selection
 
@@
 
-### Performance evaluation
+## Performance evaluation
 
@@
 
-`r print_table(perf_table, caption = "**Table 3**.
+`r print_table(perf_table, caption = '**Table 3**.
 Estimated performance summary.
 The table reports for each session, the number of reviewed records and the percentage over the total.
-Also, the posterior expected number of positive records, *Sensitivity* and *Work saved over random* (WSoR) are reported, with their 90% PrI truncated to a number of positive matches equal to the observed one.
-Finally the median Bayesian R^2 [90% CrI] of the logistic models is reported.
+Also, the posterior expected number of positive records, "Sensitivity" and "Work saved over random" (WSoR) are reported, with their 90% PrI truncated to a number of positive matches equal to the observed one.
+Finally the median Bayesian $R^2$ [90% CrI] of the logistic models is reported.
 [PrI] represents the 90% Predictive Interval while [trunc.
 PrI] indicate the residual PrI truncated at the observed realization (see.
-methods).")`
+methods).')`
 
-```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 2.
+```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="**Figure 2**.
 Observed cumulative number of positive matches (red dots) sorted by simple query ordering.

### 2021-10-25 Manuscript/S2.Additional_outputs.tex
update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={S2. Additional figures and table},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\usepackage{amsmath}
\captionsetup[table]{labelformat=empty}
\captionsetup[figure]{labelformat=empty}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{S2. Additional figures and table}
\author{}
\date{\vspace{-2.5em}2021-10-25}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\newpage

\hypertarget{posterior-predictive-distributions}{%
\section{Posterior predictive
distributions}\label{posterior-predictive-distributions}}

Figure 1 show the mixture of the PPD of the probability of a positive
match, grouped by label (only records manually labelled or reviewed are
considered). The posterior samples for each record were extracted and
joined into a global distribution; on this distribution, density was
computed on the logit scale and then logistic transformed for displaying
on a \([0 - 1]\) scale. The purple ridges show the distribution of the
still unlabelled records.\\
For each iteration, the thresholds which define the ``uncertainty
zone'', i.e, the lower and the upper range of 98\% PrI for the positive
and negative records respectively, are shown. Records whose 98\% PrI
intersects the uncertainty zone requires manual review.\\
Notice how the positive and negative record densities tend to
increasingly overlap at each iteration; meanwhile the distribution of
the records to be reviewed shrinks and shifts towards the negative side,
as positive records get found and labeled.\\
In Session 2, as the number of negative records reviewed increased, also
already positively labelled records re-entered the uncertainty zone;
this is due to the baseline positivity rate decreasing as the number of
negatives in the training data increased, forcing to review dubious
records that may have been mislabelled.

\begin{figure}
\centering
\includegraphics{S2.Additional_outputs_files/figure-latex/posterior distributions-1.pdf}
\caption{Figure 1. Mixture predictive distribution of the probability of
a positive match, grouped by labelling status.}
\end{figure}

\hypertarget{list-of-terms-relevant-for-prediction}{%
\section{List of terms relevant for
prediction}\label{list-of-terms-relevant-for-prediction}}

In table 1 and 2 are listed the 50 more relevant terms used by the BART
algorithm to discriminate between positive and negative records, for
Session 1 and 2 (see Methods). Term importance (``Inclusion rate'' in
the tables) is defined as the ensemble average inclusion rate in
posterior trees over 10,000 total term inclusions, while the Inclusion
Stability (IS) is the ratio of the average inclusion rate over its
standard deviation among the ensemble models. The symbol ``\textbar{}''
in the terms indicate redundant terms while ``\&'' indicate nc-grams.
The component in which the term was used is reported in the leftmost
column.\\
For each term, we added its linear association with a positive label
estimated through a Poisson regression, reporting it as Relative Risk
(RR) and its statistical significance (Statistic) measured as number of
standard errors, s.e., of the terms. A strong BART score with a
Statistic close to zero identify terms whose effect is highly non-linear
(e.g., they are relevant only in the presence of other terms).

\begin{table}[!h]

\caption{\label{tab:var imp}Table 1. Term importance at the end of Session 1.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrrll}
\toprule
Component & Term & Inclusion rate & IS & RR & Statistic\\
\midrule
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Patient Transport} & \cellcolor{gray!6}{61.2} & \cellcolor{gray!6}{3.77} & \cellcolor{gray!6}{99.1} & \cellcolor{gray!6}{21.3}\\
Abstract & Transfer & 57.0 & 3.93 & 22.5 & 15.4\\
\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Network} & \cellcolor{gray!6}{56.5} & \cellcolor{gray!6}{2.91} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{14.2}\\
Abstract & Network & Patient & 54.2 & 4.66 & 26.3 & 15.2\\
\cellcolor{gray!6}{Author} & \cellcolor{gray!6}{Donker T} & \cellcolor{gray!6}{53.5} & \cellcolor{gray!6}{4.56} & \cellcolor{gray!6}{159} & \cellcolor{gray!6}{16.5}\\
\addlinespace
Abstract & Worker & 50.0 & 3.33 & 0.421 & -1.21\\
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Hospitals} & \cellcolor{gray!6}{49.8} & \cellcolor{gray!6}{4.31} & \cellcolor{gray!6}{27.8} & \cellcolor{gray!6}{16.5}\\
Abstract & Movement & 47.8 & 2.70 & 27.2 & 15\\
\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Spread} & \cellcolor{gray!6}{46.6} & \cellcolor{gray!6}{2.25} & \cellcolor{gray!6}{16.2} & \cellcolor{gray!6}{12.1}\\
Abstract & Facility & 45.0 & 2.22 & 19.6 & 14.8\\
\addlinespace
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Orange County} & \cellcolor{gray!6}{44.3} & \cellcolor{gray!6}{3.19} & \cellcolor{gray!6}{199} & \cellcolor{gray!6}{17.2}\\
Abstract & Conduct & 42.6 & 3.70 & 0.221 & -2.57\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Patient} & \cellcolor{gray!6}{42.0} & \cellcolor{gray!6}{3.61} & \cellcolor{gray!6}{27.6} & \cellcolor{gray!6}{7.23}\\
Abstract & Perform & 41.9 & 2.38 & 0.342 & -2.55\\
\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Hospital} & \cellcolor{gray!6}{39.0} & \cellcolor{gray!6}{1.95} & \cellcolor{gray!6}{12.5} & \cellcolor{gray!6}{12.5}\\
\addlinespace
Abstract & Regional & 38.9 & 3.08 & 21.7 & 14.9\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Agent} & \cellcolor{gray!6}{38.1} & \cellcolor{gray!6}{2.74} & \cellcolor{gray!6}{4.36} & \cellcolor{gray!6}{6.28}\\
Abstract & California & 37.3 & 2.60 & 38 & 12.6\\
\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Transfer} & \cellcolor{gray!6}{36.6} & \cellcolor{gray!6}{3.54} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{11.8}\\
Keyword & Patient Transfer | Patient Transfer & Patient Transport & 36.6 & 2.16 & 164 & 2\\
\addlinespace
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Finding} & \cellcolor{gray!6}{33.2} & \cellcolor{gray!6}{1.78} & \cellcolor{gray!6}{0.372} & \cellcolor{gray!6}{-2.35}\\
Title & Outbreak & 32.9 & 2.91 & 3.4 & 3.51\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Collect} & \cellcolor{gray!6}{32.4} & \cellcolor{gray!6}{1.82} & \cellcolor{gray!6}{0.408} & \cellcolor{gray!6}{-1.95}\\
Title & Regional & 32.3 & 2.68 & 44.2 & 14.2\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Network} & \cellcolor{gray!6}{31.6} & \cellcolor{gray!6}{3.09} & \cellcolor{gray!6}{12.8} & \cellcolor{gray!6}{11.7}\\
\addlinespace
Abstract & Resistant & 31.6 & 2.55 & 11 & 11.2\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Outcome} & \cellcolor{gray!6}{31.2} & \cellcolor{gray!6}{1.93} & \cellcolor{gray!6}{0.178} & \cellcolor{gray!6}{-2.95}\\
Abstract & Discharge & 31.1 & 3.79 & 9.99 & 9.02\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{30.3} & \cellcolor{gray!6}{1.84} & \cellcolor{gray!6}{0.588} & \cellcolor{gray!6}{-1.04}\\
Abstract & Practice & 29.5 & 2.47 & 0.508 & -1.33\\
\addlinespace
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Culture} & \cellcolor{gray!6}{28.9} & \cellcolor{gray!6}{2.14} & \cellcolor{gray!6}{0.378} & \cellcolor{gray!6}{-1.66}\\
Abstract & Positive & 28.8 & 1.96 & 0.346 & -2.52\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Gene} & \cellcolor{gray!6}{28.3} & \cellcolor{gray!6}{1.29} & \cellcolor{gray!6}{2.4e-07} & \cellcolor{gray!6}{-0.0415}\\
Abstract & Disease & 28.0 & 2.42 & 0.365 & -3.7\\
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Enterococci} & \cellcolor{gray!6}{27.5} & \cellcolor{gray!6}{1.92} & \cellcolor{gray!6}{25.2} & \cellcolor{gray!6}{6.33}\\
\addlinespace
Abstract & Month & 27.3 & 1.86 & 0.288 & -2.44\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Healthcare} & \cellcolor{gray!6}{Facility} & \cellcolor{gray!6}{26.2} & \cellcolor{gray!6}{1.74} & \cellcolor{gray!6}{34.9} & \cellcolor{gray!6}{17}\\
Abstract & Prevalence & 26.2 & 1.71 & 4.08 & 6.69\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Effort} & \cellcolor{gray!6}{26.1} & \cellcolor{gray!6}{1.22} & \cellcolor{gray!6}{6.64} & \cellcolor{gray!6}{8.57}\\
Abstract & Length & 25.3 & 1.44 & 6.1 & 6.45\\
\addlinespace
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{System} & \cellcolor{gray!6}{25.0} & \cellcolor{gray!6}{1.43} & \cellcolor{gray!6}{11.9} & \cellcolor{gray!6}{3.47}\\
Abstract & Laboratory & 24.4 & 1.38 & 0.442 & -1.39\\
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Resistant Staphylococcus Aureus} & \cellcolor{gray!6}{24.4} & \cellcolor{gray!6}{1.59} & \cellcolor{gray!6}{22.8} & \cellcolor{gray!6}{11.2}\\
Abstract & Clinical & 23.6 & 2.10 & 0.421 & -2.9\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Dataset} & \cellcolor{gray!6}{22.5} & \cellcolor{gray!6}{1.47} & \cellcolor{gray!6}{8.75} & \cellcolor{gray!6}{6.5}\\
\addlinespace
Abstract & Development & 22.2 & 1.22 & 0.148 & -2.68\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Hand} & \cellcolor{gray!6}{22.0} & \cellcolor{gray!6}{1.97} & \cellcolor{gray!6}{0.822} & \cellcolor{gray!6}{-0.335}\\
Keyword & Pathogen Transmission & 21.8 & 3.26 & 67.9 & 7.2\\
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Cross Infection} & \cellcolor{gray!6}{Humans} & \cellcolor{gray!6}{Transmission} & \cellcolor{gray!6}{21.7} & \cellcolor{gray!6}{1.40} & \cellcolor{gray!6}{31.1} & \cellcolor{gray!6}{15.5}\\
Abstract & Flow & 21.4 & 1.14 & 4.07 & 4.56\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[!h]

\caption{\label{tab:var imp}Table 2. Term importance at the end of Session 2.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrrll}
\toprule
Component & Term & Inclusion rate & IS & RR & Statistic\\
\midrule
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Patient Transport} & \cellcolor{gray!6}{61.2} & \cellcolor{gray!6}{3.77} & \cellcolor{gray!6}{99.1} & \cellcolor{gray!6}{21.3}\\
Abstract & Transfer & 57.0 & 3.93 & 22.5 & 15.4\\
\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Network} & \cellcolor{gray!6}{56.5} & \cellcolor{gray!6}{2.91} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{14.2}\\
Abstract & Network & Patient & 54.2 & 4.66 & 26.3 & 15.2\\
\cellcolor{gray!6}{Author} & \cellcolor{gray!6}{Donker T} & \cellcolor{gray!6}{53.5} & \cellcolor{gray!6}{4.56} & \cellcolor{gray!6}{159} & \cellcolor{gray!6}{16.5}\\
\addlinespace
Abstract & Worker & 50.0 & 3.33 & 0.421 & -1.21\\
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Hospitals} & \cellcolor{gray!6}{49.8} & \cellcolor{gray!6}{4.31} & \cellcolor{gray!6}{27.8} & \cellcolor{gray!6}{16.5}\\
Abstract & Movement & 47.8 & 2.70 & 27.2 & 15\\
\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Spread} & \cellcolor{gray!6}{46.6} & \cellcolor{gray!6}{2.25} & \cellcolor{gray!6}{16.2} & \cellcolor{gray!6}{12.1}\\
Abstract & Facility & 45.0 & 2.22 & 19.6 & 14.8\\
\addlinespace
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Orange County} & \cellcolor{gray!6}{44.3} & \cellcolor{gray!6}{3.19} & \cellcolor{gray!6}{199} & \cellcolor{gray!6}{17.2}\\
Abstract & Conduct & 42.6 & 3.70 & 0.221 & -2.57\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Patient} & \cellcolor{gray!6}{42.0} & \cellcolor{gray!6}{3.61} & \cellcolor{gray!6}{27.6} & \cellcolor{gray!6}{7.23}\\
Abstract & Perform & 41.9 & 2.38 & 0.342 & -2.55\\
\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Hospital} & \cellcolor{gray!6}{39.0} & \cellcolor{gray!6}{1.95} & \cellcolor{gray!6}{12.5} & \cellcolor{gray!6}{12.5}\\
\addlinespace
Abstract & Regional & 38.9 & 3.08 & 21.7 & 14.9\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Agent} & \cellcolor{gray!6}{38.1} & \cellcolor{gray!6}{2.74} & \cellcolor{gray!6}{4.36} & \cellcolor{gray!6}{6.28}\\
Abstract & California & 37.3 & 2.60 & 38 & 12.6\\
\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Transfer} & \cellcolor{gray!6}{36.6} & \cellcolor{gray!6}{3.54} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{11.8}\\
Keyword & Patient Transfer | Patient Transfer & Patient Transport & 36.6 & 2.16 & 164 & 2\\
\addlinespace
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Finding} & \cellcolor{gray!6}{33.2} & \cellcolor{gray!6}{1.78} & \cellcolor{gray!6}{0.372} & \cellcolor{gray!6}{-2.35}\\
Title & Outbreak & 32.9 & 2.91 & 3.4 & 3.51\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Collect} & \cellcolor{gray!6}{32.4} & \cellcolor{gray!6}{1.82} & \cellcolor{gray!6}{0.408} & \cellcolor{gray!6}{-1.95}\\
Title & Regional & 32.3 & 2.68 & 44.2 & 14.2\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Network} & \cellcolor{gray!6}{31.6} & \cellcolor{gray!6}{3.09} & \cellcolor{gray!6}{12.8} & \cellcolor{gray!6}{11.7}\\
\addlinespace
Abstract & Resistant & 31.6 & 2.55 & 11 & 11.2\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Outcome} & \cellcolor{gray!6}{31.2} & \cellcolor{gray!6}{1.93} & \cellcolor{gray!6}{0.178} & \cellcolor{gray!6}{-2.95}\\
Abstract & Discharge & 31.1 & 3.79 & 9.99 & 9.02\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{30.3} & \cellcolor{gray!6}{1.84} & \cellcolor{gray!6}{0.588} & \cellcolor{gray!6}{-1.04}\\
Abstract & Practice & 29.5 & 2.47 & 0.508 & -1.33\\
\addlinespace
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Culture} & \cellcolor{gray!6}{28.9} & \cellcolor{gray!6}{2.14} & \cellcolor{gray!6}{0.378} & \cellcolor{gray!6}{-1.66}\\
Abstract & Positive & 28.8 & 1.96 & 0.346 & -2.52\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Gene} & \cellcolor{gray!6}{28.3} & \cellcolor{gray!6}{1.29} & \cellcolor{gray!6}{2.4e-07} & \cellcolor{gray!6}{-0.0415}\\
Abstract & Disease & 28.0 & 2.42 & 0.365 & -3.7\\
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Enterococci} & \cellcolor{gray!6}{27.5} & \cellcolor{gray!6}{1.92} & \cellcolor{gray!6}{25.2} & \cellcolor{gray!6}{6.33}\\
\addlinespace
Abstract & Month & 27.3 & 1.86 & 0.288 & -2.44\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Healthcare} & \cellcolor{gray!6}{Facility} & \cellcolor{gray!6}{26.2} & \cellcolor{gray!6}{1.74} & \cellcolor{gray!6}{34.9} & \cellcolor{gray!6}{17}\\
Abstract & Prevalence & 26.2 & 1.71 & 4.08 & 6.69\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Effort} & \cellcolor{gray!6}{26.1} & \cellcolor{gray!6}{1.22} & \cellcolor{gray!6}{6.64} & \cellcolor{gray!6}{8.57}\\
Abstract & Length & 25.3 & 1.44 & 6.1 & 6.45\\
\addlinespace
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{System} & \cellcolor{gray!6}{25.0} & \cellcolor{gray!6}{1.43} & \cellcolor{gray!6}{11.9} & \cellcolor{gray!6}{3.47}\\
Abstract & Laboratory & 24.4 & 1.38 & 0.442 & -1.39\\
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Resistant Staphylococcus Aureus} & \cellcolor{gray!6}{24.4} & \cellcolor{gray!6}{1.59} & \cellcolor{gray!6}{22.8} & \cellcolor{gray!6}{11.2}\\
Abstract & Clinical & 23.6 & 2.10 & 0.421 & -2.9\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Dataset} & \cellcolor{gray!6}{22.5} & \cellcolor{gray!6}{1.47} & \cellcolor{gray!6}{8.75} & \cellcolor{gray!6}{6.5}\\
\addlinespace
Abstract & Development & 22.2 & 1.22 & 0.148 & -2.68\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Hand} & \cellcolor{gray!6}{22.0} & \cellcolor{gray!6}{1.97} & \cellcolor{gray!6}{0.822} & \cellcolor{gray!6}{-0.335}\\
Keyword & Pathogen Transmission & 21.8 & 3.26 & 67.9 & 7.2\\
\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Cross Infection} & \cellcolor{gray!6}{Humans} & \cellcolor{gray!6}{Transmission} & \cellcolor{gray!6}{21.7} & \cellcolor{gray!6}{1.40} & \cellcolor{gray!6}{31.1} & \cellcolor{gray!6}{15.5}\\
Abstract & Flow & 21.4 & 1.14 & 4.07 & 4.56\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{hyperparameters-grid-search}{%
\section{Hyperparameters grid
search}\label{hyperparameters-grid-search}}

Table 3 shows the best hyperparameter set and their performance for each
cluster while figure 2 displays the conditional impact on performance of
each hyperparameter.

The most influential parameters were the number of models in the
ensemble, the oversampling rate and the initial training set size. The
use of bootstrap resampling seemed detrimental.

\begin{figure}
\centering
\includegraphics{S2.Additional_outputs_files/figure-latex/hyperparameters-1.pdf}
\caption{\textbf{Figure 2}. Score clusters and impact of single
hyperparameters on engine performance. The performance is measured as
Sensitivity x Efficiency. Each cluster is color coded. Mods: number of
models in the ensemble; Quant: PrI quantiles for the uncertainty zone;
Resamp: bootstrap resampling between models; Init: size of initial
training set; Multi: oversampling rate of positive records}
\end{figure}

\begin{table}[!h]

\caption{\label{tab:hyperparameters}Table 3. Hyperparameter clusters and best cluster subsets. For each cluster, the defining rules and mean Sens. x Eff. is shown, followed by the per-cluster best set results.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllllllllll}
\toprule
Cluster (mean score) & Num. iterations & Positive matches & Reviewed records & Sensitivity & Efficiency & Score (Sens. x Eff.) & Num. ensemble models & Uncertainty interval & Resampling & Num. initial training records & Positives oversampling multiplier\\
\midrule
\cellcolor{gray!6}{1. Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = n} & \cellcolor{gray!6}{Init = 100,250 (0.64)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{462 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{61.5\%} & \cellcolor{gray!6}{0.608} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
2. Mult = 10,20 & Mods = 10,20,40,60 & Resamp = y & Init = 250,500 & Mods = 20,40,60 (0.56) & 5 & 82 / 82 & 618 / 1200 & 100\% & 48.5\% & 0.485 & 20 & 80 & y & 250 & 10\\
\cellcolor{gray!6}{3. Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = n} & \cellcolor{gray!6}{Init = 50,500 (0.5)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{589 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{50.9\%} & \cellcolor{gray!6}{0.503} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{10}\\
4. Mult = 10,20 & Mods = 1,5 & Resamp = n & Mods = 5 (0.47) & 8 & 82 / 82 & 1123 / 1200 & 100\% & 6.42\% & 0.0642 & 5 & 98 & n & 50 & 10\\
\cellcolor{gray!6}{5. Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = y} & \cellcolor{gray!6}{Init = 250,500} & \cellcolor{gray!6}{Mods = 10 (0.39)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{685 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{42.9\%} & \cellcolor{gray!6}{0.429} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{80} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
\addlinespace
6. Mult = 10,20 & Mods = 1,5 & Resamp = n & Mods = 1 & Init = 250,500 (0.31) & 5 & 82 / 82 & 874 / 1200 & 100\% & 27.2\% & 0.272 & 1 & 90 & n & 250 & 10\\
\cellcolor{gray!6}{7. Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = y} & \cellcolor{gray!6}{Init = 50,100 (0.23)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{948 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{21\%} & \cellcolor{gray!6}{0.21} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
8. Mult = 1 & Init = 250,500 & Mods = 20,40,60 (0.21) & 5 & 82 / 82 & 806 / 1200 & 100\% & 32.8\% & 0.328 & 60 & 80 & y & 250 & 1\\
\cellcolor{gray!6}{9. Mult = 10,20} & \cellcolor{gray!6}{Mods = 1,5} & \cellcolor{gray!6}{Resamp = n} & \cellcolor{gray!6}{Mods = 1} & \cellcolor{gray!6}{Init = 50,100 (0.078)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{1139 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{5.08\%} & \cellcolor{gray!6}{0.0508} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
10. Mult = 10,20 & Mods = 1,5 & Resamp = y (0.054) & 5 & 82 / 82 & 832 / 1200 & 100\% & 30.7\% & 0.307 & 5 & 80 & y & 250 & 20\\
\addlinespace
\cellcolor{gray!6}{11. Mult = 1} & \cellcolor{gray!6}{Init = 250,500} & \cellcolor{gray!6}{Mods = 1,5,10 (0.025)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{981 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{18.2\%} & \cellcolor{gray!6}{0.182} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{1}\\
12. Mult = 1 & Init = 50,100 (0.0045) & 6 & 82 / 82 & 1151 / 1200 & 100\% & 4.08\% & 0.0408 & 20 & 80 & y & 50 & 1\\
\bottomrule
\end{tabular}}
\end{table}

\end{document}

### 2021-10-26 R/Reporting.R
feat: allow enabling of $$ math parsing (experimental)

@@ -234,16 +234,16 @@ summarise_annotations_by_session <- function(sessions_folder = getOption("baysre
 	}
 }
 
-	# summarise_annotations <- function(annotation.folder = 'Annotations', plot = F) {
-	# 	# list.files('Models') %>% pbmclapply(function(file) {
-	# 	# 	Model <- read_rds(file.path('Models', file))
-	#
-	# 	Res <- list.files(annotation.folder, recursive = T, pattern = 'Records_P') %>%
-	# 		str_subset('~\\$', negate = T) %>%
-	# 		pbmclapply(function(file) {
-	#
-	# 			file_path <- file.path(annotation.folder, file)
-	#
+# summarise_annotations <- function(annotation.folder = 'Annotations', plot = F) {
+# 	# list.files('Models') %>% pbmclapply(function(file) {
+# 	# 	Model <- read_rds(file.path('Models', file))
+#
+# 	Res <- list.files(annotation.folder, recursive = T, pattern = 'Records_P') %>%
+# 		str_subset('~\\$', negate = T) %>%
+# 		pbmclapply(function(file) {
+#
+# 			file_path <- file.path(annotation.folder, file)
+#
 # 			Annotated_data <- read_excel(file_path)
 #
 # 			Performance <- read_excel(file_path, sheet = 'Out_of_sample_perf')
@@ -571,7 +571,7 @@ format_performance <- function(..., session_names = NULL) {
 				'Predicted positive matches [trunc. 90% PrI]' = pred_positives %>% format_interval(),
 				'Expected sensitivity [trunc. 90% PrI]' = sensitivity %>% format_interval(percent = TRUE),
 				'Simple Model $R^2$ [90% PrI]' = mod_r2 %>% format_interval(percent = TRUE)
-		) %>%
+			) %>%
 				mutate_all(as.character) %>%
 				tidyr::pivot_longer(everything(), names_to = 'Indicator', values_to = session_names[i]) %>%
 				{
@@ -599,8 +599,8 @@ plot_predictive_densities <- function(session_name,
 			import_data()
 
 		if (i <= length(records_files)) {
-		records <- records %>%
-			mutate(Rev_prediction_new = replace(Rev_prediction_new, !is.na(Rev_prediction_new), '*'))
+			records <- records %>%
[…]

### 2021-10-26 Manuscript/S2.Additional_outputs.Rmd
updated formatting

@@
 
-```{r posterior distributions, fig.width=10, fig.height=10, fig.cap="Figure 1. Mixture predictive distribution of the probability of a positive match, grouped by labelling status."}
+```{r posterior distributions, fig.width=10, fig.height=10, fig.cap="**Figure 1**. Mixture predictive distribution of the probability of a positive match, grouped by labelling status."}
 
@@
 
-`r print_table(var_importance_s1, caption = 'Table 1. Term importance at the end of Session 1.')`
+`r print_table(var_importance_s1, caption = '**Table 1**. Term importance at the end of Session 1.')`
 
-`r print_table(var_importance_s2, caption = 'Table 2. Term importance at the end of Session 2.')`
+`r print_table(var_importance_s2, caption = '**Table 2**. Term importance at the end of Session 2.')`
 
@@
 
-```{r hyperparameters, fig.width=17, fig.height=10, fig.cap="Figure 2.
+```{r hyperparameters, fig.width=17, fig.height=10, fig.cap="**Figure 2**.
 Score clusters and impact of single hyperparameters on engine performance.
@@
 
-`r print_table(grid_out_params, caption = 'Table 3.
+`r print_table(grid_out_params, caption = '**Table 3**.
 Hyperparameter clusters and best cluster subsets.

### 2021-10-26 R/Reporting.R
clean: moved function into Reporting.R

@@ -1,3 +1,9 @@
+summarise_vector <- function(vec) {
+	if (length(vec) == 0) return(0)
+	table(vec) %>%
+		{paste0(names(.), ': ', ., ' (', percent(./sum(.)), ')', collapse = ', ')}
+}
+
 summarise_by_source <- function(annotation_file, as_data_frame = FALSE,
 																add_session_totals = TRUE) {
 	data <- import_data(annotation_file)

### 2021-10-26 R/Setup.R

@@ -95,12 +95,6 @@ safe_now <- function() {
 	str_replace_all(now(), c(' ' = 'T', ':' = '.'))
 }
 
-summarise_vector <- function(vec) {
-	if (length(vec) == 0) return(0)
-	table(vec) %>%
-		{paste0(names(.), ': ', ., ' (', percent(./sum(.)), ')', collapse = ', ')}
-}
-
 # Tool to grab XHR messages from dynamic websites
 get_website_resources <- function(url, url_filter = '.*', type_filter = '.*',
 																	wait_for = 20,

### 2021-10-26 Manuscript/Manuscript.Rmd
fixed locazation problem that was misplacing commas around quot marks

@@
 bibliography: references.bib
+lang: en-GB
 output: 
@@
 ```{r, echo=FALSE, results='asis', message = FALSE, warning = FALSE, error = FALSE, dpi = 400, fig.width=12, fig.height=5}
-
-getOption("mc.cores", parallel::detectCores())
 

### 2021-10-26 Manuscript/Manuscript.tex
small typo
fixed locazation problem that was misplacing commas around quot marks

@@
   }
-
-{[}1{]} 8
 
@@
 description of the framework and how to use it.\\
-The tasks carried out by the framework are grouped into ``sessions,''
+The tasks carried out by the framework are grouped into ``sessions'',
 i.e., a set of actions that starts from a search query to obtain a set
@@
 interface have different rule expansion algorithms and return slightly
-different results ({``NCBI Insights : Updated Pubmed e-Utilities Coming
-in April 2022!''} n.d.). A short guide on how to set up the framework
-for each supported database is available in Supplemental Material S3.\\
+different results ({`NCBI Insights : Updated Pubmed e-Utilities Coming
+in April 2022!'} n.d.). A short guide on how to set up the framework for
+each supported database is available in Supplemental Material S3.\\
 The acquired records are merged into a single database, resolving
@@
 
-All other records are labelled as ``uncertain.''
+All other records are labelled as ``uncertain''.
 
@@
 For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total.
-SAll session shows records after joining and deduplication of the Session 1 and Session 2 dataset.}
+All session shows records after joining and deduplication of the Session 1 and Session 2 dataset.}
 \centering
@@
 One of the central innovations we introduced is the concept of
-``uncertainty zone,'' whose implementation is possible thanks to the
+``uncertainty zone'', whose implementation is possible thanks to the
 Bayesian foundation of the classification model. This construct guides
@@
 \leavevmode\hypertarget{ref-abd2013review}{}%
-Abd Elrahman, Shaza M, and Ajith Abraham. 2013. {``A Review of Class
-Imbalance Problem.''} \emph{Journal of Network and Innovative Computing}
+Abd Elrahman, Shaza M, and Ajith Abraham. 2013. {`A Review of Class
+Imbalance Problem.'} \emph{Journal of Network and Innovative Computing}
 1 (2013): 332--40.
@@
 \leavevmode\hypertarget{ref-allen1999estimating}{}%
-Allen, I Elaine, and Ingram Olkin. 1999. {``Estimating Time to Conduct a
-Meta-Analysis from Number of Citations Retrieved.''} \emph{Jama} 282
-(7): 634--35.
+Allen, I Elaine, and Ingram Olkin. 1999. {`Estimating Time to Conduct a
+Meta-Analysis from Number of Citations Retrieved.'} \emph{Jama} 282 (7):
+634--35.
 
@@
 Ananiadou, Sophia, Brian Rea, Naoaki Okazaki, Rob Procter, and James
-Thomas. 2009. {``Supporting Systematic Reviews Using Text Mining.''}
+Thomas. 2009. {`Supporting Systematic Reviews Using Text Mining.'}
 \emph{Social Science Computer Review} 27 (4): 509--23.
@@
 \leavevmode\hypertarget{ref-aviv2021publication}{}%
-Aviv-Reuven, Shir, and Ariel Rosenfeld. 2021. {``Publication Patterns'
+Aviv-Reuven, Shir, and Ariel Rosenfeld. 2021. {`Publication Patterns'
 Changes Due to the COVID-19 Pandemic: A Longitudinal and Short-Term
-Scientometric Analysis.''} \emph{Scientometrics}, 1--24.
+Scientometric Analysis.'} \emph{Scientometrics}, 1--24.
 
 \leavevmode\hypertarget{ref-babar2009systematic}{}%
-Babar, Muhammad Ali, and He Zhang. 2009. {``Systematic Literature
-Reviews in Software Engineering: Preliminary Results from Interviews
-with Researchers.''} In \emph{2009 3rd International Symposium on
-Empirical Software Engineering and Measurement}, 346--55. IEEE.
+Babar, Muhammad Ali, and He Zhang. 2009. {`Systematic Literature Reviews
+in Software Engineering: Preliminary Results from Interviews with
+Researchers.'} In \emph{2009 3rd International Symposium on Empirical
+Software Engineering and Measurement}, 346--55. IEEE.
 
@@
 Bajpai, Akhilesh, Sravanthi Davuluri, Haritha Haridas, Greta Kasliwal, H
-Deepti, KS Sreelakshmi, Darshan Chandrashekar, et al. 2011. {``In Search
-of the Right Literature Search Engine (s).''} \emph{Nature Precedings},
+Deepti, KS Sreelakshmi, Darshan Chandrashekar, et al. 2011. {`In Search
+of the Right Literature Search Engine (s).'} \emph{Nature Precedings},
 1--1.
@@
 Bannach-Brown, Alexandra, Piotr Przybyła, James Thomas, Andrew SC Rice,
-Sophia Ananiadou, Jing Liao, and Malcolm Robert Macleod. 2019.
-{``Machine Learning Algorithms for Systematic Review: Reducing Workload
-in a Preclinical Review of Animal Studies and Reducing Human Screening
-Error.''} \emph{Systematic Reviews} 8 (1): 1--12.
+Sophia Ananiadou, Jing Liao, and Malcolm Robert Macleod. 2019. {`Machine
+Learning Algorithms for Systematic Review: Reducing Workload in a
+Preclinical Review of Animal Studies and Reducing Human Screening
+Error.'} \emph{Systematic Reviews} 8 (1): 1--12.
 
 \leavevmode\hypertarget{ref-bastian2010seventy}{}%
-Bastian, Hilda, Paul Glasziou, and Iain Chalmers. 2010. {``Seventy-Five
-Trials and Eleven Systematic Reviews a Day: How Will We Ever Keep Up?''}
+Bastian, Hilda, Paul Glasziou, and Iain Chalmers. 2010. {`Seventy-Five
+Trials and Eleven Systematic Reviews a Day: How Will We Ever Keep Up?'}
 \emph{PLoS Medicine} 7 (9): e1000326.
@@
 Batista, Gustavo EAPA, Ronaldo C Prati, and Maria Carolina Monard. 2004.
-{``A Study of the Behavior of Several Methods for Balancing Machine
-Learning Training Data.''} \emph{ACM SIGKDD Explorations Newsletter} 6
+{`A Study of the Behavior of Several Methods for Balancing Machine
+Learning Training Data.'} \emph{ACM SIGKDD Explorations Newsletter} 6
 (1): 20--29.
@@
 \leavevmode\hypertarget{ref-bekhuis2010towards}{}%
-Bekhuis, Tanja, and Dina Demner-Fushman. 2010. {``Towards Automating the
-Initial Screening Phase of a Systematic Review.''} \emph{MEDINFO 2010},
+Bekhuis, Tanja, and Dina Demner-Fushman. 2010. {`Towards Automating the
+Initial Screening Phase of a Systematic Review.'} \emph{MEDINFO 2010},
 146--50.
@@
 \leavevmode\hypertarget{ref-bekhuis2012screening}{}%
----------. 2012. {``Screening Nonrandomized Studies for Medical
-Systematic Reviews: A Comparative Study of Classifiers.''}
+---------. 2012. {`Screening Nonrandomized Studies for Medical
+Systematic Reviews: A Comparative Study of Classifiers.'}
 \emph{Artificial Intelligence in Medicine} 55 (3): 197--207.
@@
 Beller, Elaine M, Joyce Kee-Hsin Chen, Una Li-Hsiang Wang, and Paul P
-Glasziou. 2013. {``Are Systematic Reviews up-to-Date at the Time of
-Publication?''} \emph{Systematic Reviews} 2 (1): 1--6.
+Glasziou. 2013. {`Are Systematic Reviews up-to-Date at the Time of
+Publication?'} \emph{Systematic Reviews} 2 (1): 1--6.
 
@@
 Beller, Elaine, Justin Clark, Guy Tsafnat, Clive Adams, Heinz Diehl,
-Hans Lund, Mourad Ouzzani, et al. 2018. {``Making Progress with the
+Hans Lund, Mourad Ouzzani, et al. 2018. {`Making Progress with the
 Automation of Systematic Reviews: Principles of the International
-Collaboration for the Automation of Systematic Reviews (ICASR).''}
+Collaboration for the Automation of Systematic Reviews (ICASR).'}
 \emph{Systematic Reviews} 7 (1): 1--7.
@@
 Bhatt, Umang, McKane Andrus, Adrian Weller, and Alice Xiang. 2020.
-{``Machine Learning Explainability for External Stakeholders.''}
+{`Machine Learning Explainability for External Stakeholders.'}
 \emph{arXiv Preprint arXiv:2007.05408}.
@@
 Bibal, Adrien, Michael Lognoul, Alexandre De Streel, and Benoît Frénay.
-2021. {``Legal Requirements on Explainability in Machine Learning.''}
+2021. {`Legal Requirements on Explainability in Machine Learning.'}
 \emph{Artificial Intelligence and Law} 29 (2): 149--69.
@@
 Bibal, Adrien, Michael Lognoul, Alexandre de Streel, and Benoît Frénay.
-2020. {``Impact of Legal Requirements on Explainability in Machine
-Learning.''} \emph{arXiv Preprint arXiv:2007.05479}.
+2020. {`Impact of Legal Requirements on Explainability in Machine
+Learning.'} \emph{arXiv Preprint arXiv:2007.05479}.
 
 \leavevmode\hypertarget{ref-blanco2019machine}{}%
-Blanco-Justicia, Alberto, and Josep Domingo-Ferrer. 2019. {``Machine
-Learning Explainability Through Comprehensible Decision Trees.''} In
+Blanco-Justicia, Alberto, and Josep Domingo-Ferrer. 2019. {`Machine
+Learning Explainability Through Comprehensible Decision Trees.'} In
 \emph{International Cross-Domain Conference for Machine Learning and
@@
 Bollegala, Danushka, Takanori Maehara, and Ken-ichi Kawarabayashi. 2015.
-{``Embedding Semantic Relations into Word Representations.''} In
+{`Embedding Semantic Relations into Word Representations.'} In
 \emph{Twenty-Fourth International Joint Conference on Artificial
@@
 Borah, Rohit, Andrew W Brown, Patrice L Capers, and Kathryn A Kaiser.
-2017. {``Analysis of the Time and Workers Needed to Conduct Systematic
+2017. {`Analysis of the Time and Workers Needed to Conduct Systematic
 Reviews of Medical Interventions Using Data from the PROSPERO
-Registry.''} \emph{BMJ Open} 7 (2): e012545.
+Registry.'} \emph{BMJ Open} 7 (2): e012545.
 
 \leavevmode\hypertarget{ref-bornmann2015growth}{}%
-Bornmann, Lutz, and Rüdiger Mutz. 2015. {``Growth Rates of Modern
+Bornmann, Lutz, and Rüdiger Mutz. 2015. {`Growth Rates of Modern
 Science: A Bibliometric Analysis Based on the Number of Publications and
-Cited References.''} \emph{Journal of the Association for Information
+Cited References.'} \emph{Journal of the Association for Information
 Science and Technology} 66 (11): 2215--22.
@@
 \leavevmode\hypertarget{ref-breiman1996bagging}{}%
-Breiman, Leo. 1996. {``Bagging Predictors.''} \emph{Machine Learning} 24
+Breiman, Leo. 1996. {`Bagging Predictors.'} \emph{Machine Learning} 24
 (2): 123--40.
@@
 \leavevmode\hypertarget{ref-burkart2021survey}{}%
-Burkart, Nadia, and Marco F Huber. 2021. {``A Survey on the
-Explainability of Supervised Machine Learning.''} \emph{Journal of
+Burkart, Nadia, and Marco F Huber. 2021. {`A Survey on the
+Explainability of Supervised Machine Learning.'} \emph{Journal of
 Artificial Intelligence Research} 70: 245--317.
@@
 \leavevmode\hypertarget{ref-chae1993presenting}{}%
-Chae, Kyung-Chul. 1993. {``Presenting the Negative Hypergeometric
-Distribution to the Introductory Statistics Courses.''}
+Chae, Kyung-Chul. 1993. {`Presenting the Negative Hypergeometric
+Distribution to the Introductory Statistics Courses.'}
 \emph{International Journal of Mathematical Education in Science and
@@
 Chawla, Nitesh V, Nathalie Japkowicz, and Aleksander Kotcz. 2004.
-{``Special Issue on Learning from Imbalanced Data Sets.''} \emph{ACM
+{`Special Issue on Learning from Imbalanced Data Sets.'} \emph{ACM
 SIGKDD Explorations Newsletter} 6 (1): 1--6.
@@
 \leavevmode\hypertarget{ref-chen2018approximate}{}%
-Chen, Chao, Xiao Lin, and Gabriel Terejanu. 2018. {``An Approximate
-Bayesian Long Short-Term Memory Algorithm for Outlier Detection.''} In
+Chen, Chao, Xiao Lin, and Gabriel Terejanu. 2018. {`An Approximate
+Bayesian Long Short-Term Memory Algorithm for Outlier Detection.'} In
 \emph{2018 24th International Conference on Pattern Recognition (ICPR)},
@@
 \leavevmode\hypertarget{ref-chen2016short}{}%
-Chen, Qiuxing, Lixiu Yao, and Jie Yang. 2016. {``Short Text
-Classification Based on LDA Topic Model.''} In \emph{2016 International
+Chen, Qiuxing, Lixiu Yao, and Jie Yang. 2016. {`Short Text
+Classification Based on LDA Topic Model.'} In \emph{2016 International
 Conference on Audio, Language and Image Processing (ICALIP)}, 749--53.
@@
 Chen, Sih-Huei, Yuan-Shan Lee, Tzu-Chiang Tai, and Jia-Ching Wang. 2015.
-{``Gaussian Process Based Text Categorization for Healthy
-Information.''} In \emph{2015 International Conference on Orange
-Technologies (ICOT)}, 30--33.
-\url{https://doi.org/10.1109/ICOT.2015.7498487}.
+{`Gaussian Process Based Text Categorization for Healthy Information.'}
+In \emph{2015 International Conference on Orange Technologies (ICOT)},
+30--33. \url{https://doi.org/10.1109/ICOT.2015.7498487}.
 
 \leavevmode\hypertarget{ref-cheng2019document}{}%
-Cheng, Y, Z Ye, M Wang, and Q Zhang. 2019. {``Document Classification
+Cheng, Y, Z Ye, M Wang, and Q Zhang. 2019. {`Document Classification
 Based on Convolutional Neural Network and Hierarchical Attention
-Network.''} \emph{Neural Network World} 29 (2): 83--98.
+Network.'} \emph{Neural Network World} 29 (2): 83--98.
 
@@
 Chipman, Hugh A, Edward I George, Robert E McCulloch, and others. 2010.
-{``BART: Bayesian Additive Regression Trees.''} \emph{The Annals of
+{`BART: Bayesian Additive Regression Trees.'} \emph{The Annals of
 Applied Statistics} 4 (1): 266--98.
@@
 \leavevmode\hypertarget{ref-claesen2015hyperparameter}{}%
-Claesen, Marc, and Bart De Moor. 2015. {``Hyperparameter Search in
-Machine Learning.''} \emph{arXiv Preprint arXiv:1502.02127}.
+Claesen, Marc, and Bart De Moor. 2015. {`Hyperparameter Search in
+Machine Learning.'} \emph{arXiv Preprint arXiv:1502.02127}.
 
@@
 Weiyi Meng, Lorna Duggan, Marian McDonagh, and Neil R Smalheiser. 2010.
-{``Evidence-Based Medicine, the Essential Role of Systematic Reviews,
-and the Need for Automated Text Mining Tools.''} In \emph{Proceedings of
-the 1st ACM International Health Informatics Symposium}, 376--80.
+{`Evidence-Based Medicine, the Essential Role of Systematic Reviews, and
+the Need for Automated Text Mining Tools.'} In \emph{Proceedings of the
+1st ACM International Health Informatics Symposium}, 376--80.
 
@@
 Cohen, Aaron M, William R Hersh, Kim Peterson, and Po-Yin Yen. 2006.
-{``Reducing Workload in Systematic Review Preparation Using Automated
-Citation Classification.''} \emph{Journal of the American Medical
+{`Reducing Workload in Systematic Review Preparation Using Automated
+Citation Classification.'} \emph{Journal of the American Medical
 Informatics Association} 13 (2): 206--19.
@@
 \leavevmode\hypertarget{ref-cohen2008getting}{}%
-Cohen, K Bretonnel, and Lawrence Hunter. 2008. {``Getting Started in
-Text Mining.''} \emph{PLoS Computational Biology} 4 (1): e20.
+Cohen, K Bretonnel, and Lawrence Hunter. 2008. {`Getting Started in Text
+Mining.'} \emph{PLoS Computational Biology} 4 (1): e20.
 
 \leavevmode\hypertarget{ref-dietterich2000ensemble}{}%
-Dietterich, Thomas G. 2000. {``Ensemble Methods in Machine Learning.''}
-In \emph{International Workshop on Multiple Classifier Systems}, 1--15.
+Dietterich, Thomas G. 2000. {`Ensemble Methods in Machine Learning.'} In
+\emph{International Workshop on Multiple Classifier Systems}, 1--15.
 Springer.
@@
 Díez-Pastor, José F, Juan J Rodríguez, César I García-Osorio, and
-Ludmila I Kuncheva. 2015. {``Diversity Techniques Improve the
-Performance of the Best Imbalance Learning Ensembles.''}
-\emph{Information Sciences} 325: 98--117.
+Ludmila I Kuncheva. 2015. {`Diversity Techniques Improve the Performance
+of the Best Imbalance Learning Ensembles.'} \emph{Information Sciences}
+325: 98--117.
 
@@
 Edwards, Phil, Mike Clarke, Carolyn DiGuiseppi, Sarah Pratap, Ian
-Roberts, and Reinhard Wentz. 2002. {``Identification of Randomized
+Roberts, and Reinhard Wentz. 2002. {`Identification of Randomized
 Controlled Trials in Systematic Reviews: Accuracy and Reliability of
-Screening Records.''} \emph{Statistics in Medicine} 21 (11): 1635--40.
+Screening Records.'} \emph{Statistics in Medicine} 21 (11): 1635--40.
 
 \leavevmode\hypertarget{ref-eppstein2010listing}{}%
-Eppstein, David, Maarten Löffler, and Darren Strash. 2010. {``Listing
-All Maximal Cliques in Sparse Graphs in Near-Optimal Time.''} In
+Eppstein, David, Maarten Löffler, and Darren Strash. 2010. {`Listing All
+Maximal Cliques in Sparse Graphs in Near-Optimal Time.'} In
 \emph{International Symposium on Algorithms and Computation}, 403--14.
@@
 \leavevmode\hypertarget{ref-farkas1995document}{}%
-Farkas, Jennifer. 1995. {``Document Classification and Recurrent Neural
-Networks.''} In \emph{Proceedings of the 1995 Conference of the Centre
+Farkas, Jennifer. 1995. {`Document Classification and Recurrent Neural
+Networks.'} In \emph{Proceedings of the 1995 Conference of the Centre
 for Advanced Studies on Collaborative Research}, 21.
@@
 \leavevmode\hypertarget{ref-frunza2010building}{}%
-Frunza, Oana, Diana Inkpen, and Stan Matwin. 2010. {``Building
-Systematic Reviews Using Automatic Text Classification Techniques.''} In
+Frunza, Oana, Diana Inkpen, and Stan Matwin. 2010. {`Building Systematic
+Reviews Using Automatic Text Classification Techniques.'} In
 \emph{Coling 2010: Posters}, 303--11.
@@
 Galar, Mikel, Alberto Fernandez, Edurne Barrenechea, Humberto Bustince,
-and Francisco Herrera. 2011. {``A Review on Ensembles for the Class
-Imbalance Problem: Bagging-, Boosting-, and Hybrid-Based Approaches.''}
+and Francisco Herrera. 2011. {`A Review on Ensembles for the Class
+Imbalance Problem: Bagging-, Boosting-, and Hybrid-Based Approaches.'}
 \emph{IEEE Transactions on Systems, Man, and Cybernetics, Part C
@@
 Gelman, Andrew, Ben Goodrich, Jonah Gabry, and Aki Vehtari. 2019.
-{``R-Squared for Bayesian Regression Models.''} \emph{The American
+{`R-Squared for Bayesian Regression Models.'} \emph{The American
 Statistician}.
@@
 Hammerstrøm, Karianne, Anne Wade, Anne-Marie Klint Jørgensen, and
-Karianne Hammerstrøm. 2010. {``Searching for Studies.''}
-\emph{Education} 54 (11.3).
+Karianne Hammerstrøm. 2010. {`Searching for Studies.'} \emph{Education}
+54 (11.3).
 
 \leavevmode\hypertarget{ref-hansen2000bayesian}{}%
-Hansen, Lars Kai, and others. 2000. {``Bayesian Averaging Is
-Well-Temperated.''} In \emph{Proceedings of NIPS}, 99:265--71.
+Hansen, Lars Kai, and others. 2000. {`Bayesian Averaging Is
+Well-Temperated.'} In \emph{Proceedings of NIPS}, 99:265--71.
 
 \leavevmode\hypertarget{ref-harremoes2001maximum}{}%
-Harremoës, Peter, and Flemming Topsøe. 2001. {``Maximum Entropy
-Fundamentals.''} \emph{Entropy} 3 (3): 191--226.
+Harremoës, Peter, and Flemming Topsøe. 2001. {`Maximum Entropy
+Fundamentals.'} \emph{Entropy} 3 (3): 191--226.
 
 \leavevmode\hypertarget{ref-hastie2009boosting}{}%
-Hastie, Trevor, Robert Tibshirani, and Jerome Friedman. 2009.
-{``Boosting and Additive Trees.''} In \emph{The Elements of Statistical
-Learning}, 337--87. Springer.
+Hastie, Trevor, Robert Tibshirani, and Jerome Friedman. 2009. {`Boosting
+and Additive Trees.'} In \emph{The Elements of Statistical Learning},
+337--87. Springer.
 
@@
 \leavevmode\hypertarget{ref-horbach2020pandemic}{}%
-Horbach, Serge PJM. 2020. {``Pandemic Publishing: Medical Journals
-Strongly Speed up Their Publication Process for COVID-19.''}
+Horbach, Serge PJM. 2020. {`Pandemic Publishing: Medical Journals
+Strongly Speed up Their Publication Process for COVID-19.'}
 \emph{Quantitative Science Studies} 1 (3): 1056--67.
@@
 \leavevmode\hypertarget{ref-hoy2020rise}{}%
-Hoy, Matthew B. 2020. {``Rise of the Rxivs: How Preprint Servers Are
-Changing the Publishing Process.''} \emph{Medical Reference Services
+Hoy, Matthew B. 2020. {`Rise of the Rxivs: How Preprint Servers Are
+Changing the Publishing Process.'} \emph{Medical Reference Services
 Quarterly} 39 (1): 84--89.
@@
 \leavevmode\hypertarget{ref-ikonomakis2005text}{}%
-Ikonomakis, M, Sotiris Kotsiantis, and V Tampakas. 2005. {``Text
-Classification Using Machine Learning Techniques.''} \emph{WSEAS
+Ikonomakis, M, Sotiris Kotsiantis, and V Tampakas. 2005. {`Text
+Classification Using Machine Learning Techniques.'} \emph{WSEAS
 Transactions on Computers} 4 (8): 966--74.
@@
 \leavevmode\hypertarget{ref-jayashree2020evaluation}{}%
-Jayashree, P, and PK Srijith. 2020. {``Evaluation of Deep Gaussian
-Processes for Text Classification.''} In \emph{Proceedings of the 12th
+Jayashree, P, and PK Srijith. 2020. {`Evaluation of Deep Gaussian
+Processes for Text Classification.'} In \emph{Proceedings of the 12th
 Language Resources and Evaluation Conference}, 1485--91.
@@
 Jonnalagadda, Siddhartha R, Pawan Goyal, and Mark D Huffman. 2015.
-{``Automating Data Extraction in Systematic Reviews: A Systematic
-Review.''} \emph{Systematic Reviews} 4 (1): 1--16.
+{`Automating Data Extraction in Systematic Reviews: A Systematic
+Review.'} \emph{Systematic Reviews} 4 (1): 1--16.
 
 \leavevmode\hypertarget{ref-joo2020being}{}%
-Joo, Taejong, Uijung Chung, and Min-Gwan Seo. 2020. {``Being Bayesian
-about Categorical Probability.''} In \emph{International Conference on
+Joo, Taejong, Uijung Chung, and Min-Gwan Seo. 2020. {`Being Bayesian
+about Categorical Probability.'} In \emph{International Conference on
 Machine Learning}, 4950--61. PMLR.
@@
 Jospin, Laurent Valentin, Wray Buntine, Farid Boussaid, Hamid Laga, and
-Mohammed Bennamoun. 2020. {``Hands-on Bayesian Neural Networks--a
-Tutorial for Deep Learning Users.''} \emph{arXiv Preprint
+Mohammed Bennamoun. 2020. {`Hands-on Bayesian Neural Networks--a
+Tutorial for Deep Learning Users.'} \emph{arXiv Preprint
 arXiv:2007.06823}.
@@
 \leavevmode\hypertarget{ref-kapelner2013bartmachine}{}%
-Kapelner, Adam, and Justin Bleich. 2013. {``bartMachine: Machine
-Learning with Bayesian Additive Regression Trees.''} \emph{arXiv
-Preprint arXiv:1312.2171}.
+Kapelner, Adam, and Justin Bleich. 2013. {`bartMachine: Machine Learning
+with Bayesian Additive Regression Trees.'} \emph{arXiv Preprint
+arXiv:1312.2171}.
 
 \leavevmode\hypertarget{ref-kapelner2015prediction}{}%
----------. 2015. {``Prediction with Missing Data via Bayesian Additive
-Regression Trees.''} \emph{Canadian Journal of Statistics} 43 (2):
+---------. 2015. {`Prediction with Missing Data via Bayesian Additive
+Regression Trees.'} \emph{Canadian Journal of Statistics} 43 (2):
 224--39.
@@
 Khoshgoftaar, Taghi M, Jason Van Hulse, and Amri Napolitano. 2010.
-{``Comparing Boosting and Bagging Techniques with Noisy and Imbalanced
-Data.''} \emph{IEEE Transactions on Systems, Man, and Cybernetics-Part
-A: Systems and Humans} 41 (3): 552--68.
+{`Comparing Boosting and Bagging Techniques with Noisy and Imbalanced
+Data.'} \emph{IEEE Transactions on Systems, Man, and Cybernetics-Part A:
+Systems and Humans} 41 (3): 552--68.
 
 \leavevmode\hypertarget{ref-kohavi1995study}{}%
-Kohavi, Ron, and others. 1995. {``A Study of Cross-Validation and
-Bootstrap for Accuracy Estimation and Model Selection.''} In
+Kohavi, Ron, and others. 1995. {`A Study of Cross-Validation and
+Bootstrap for Accuracy Estimation and Model Selection.'} In
 \emph{Ijcai}, 14:1137--45. 2. Montreal, Canada.
@@
 \leavevmode\hypertarget{ref-lai2015recurrent}{}%
-Lai, Siwei, Liheng Xu, Kang Liu, and Jun Zhao. 2015. {``Recurrent
-Convolutional Neural Networks for Text Classification.''} In
+Lai, Siwei, Liheng Xu, Kang Liu, and Jun Zhao. 2015. {`Recurrent
+Convolutional Neural Networks for Text Classification.'} In
 \emph{Twenty-Ninth AAAI Conference on Artificial Intelligence}.
@@
 \leavevmode\hypertarget{ref-landauer1998introduction}{}%
-Landauer, Thomas K, Peter W Foltz, and Darrell Laham. 1998. {``An
-Introduction to Latent Semantic Analysis.''} \emph{Discourse Processes}
+Landauer, Thomas K, Peter W Foltz, and Darrell Laham. 1998. {`An
+Introduction to Latent Semantic Analysis.'} \emph{Discourse Processes}
 25 (2-3): 259--84.
@@
 \leavevmode\hypertarget{ref-larsen2010rate}{}%
-Larsen, Peder, and Markus Von Ins. 2010. {``The Rate of Growth in
+Larsen, Peder, and Markus Von Ins. 2010. {`The Rate of Growth in
 Scientific Publication and the Decline in Coverage Provided by Science
-Citation Index.''} \emph{Scientometrics} 84 (3): 575--603.
+Citation Index.'} \emph{Scientometrics} 84 (3): 575--603.
 
 \leavevmode\hypertarget{ref-laws2008stopping}{}%
-Laws, Florian, and Hinrich Schütze. 2008. {``Stopping Criteria for
-Active Learning of Named Entity Recognition.''} In \emph{Proceedings of
-the 22nd International Conference on Computational Linguistics (Coling
-2008)}, 465--72.
+Laws, Florian, and Hinrich Schütze. 2008. {`Stopping Criteria for Active
+Learning of Named Entity Recognition.'} In \emph{Proceedings of the 22nd
+International Conference on Computational Linguistics (Coling 2008)},
+465--72.
 
@@
 Lefebvre, C, E Manheimer, J Glanville, J Higgins, and S Green. 2011.
-{``Searching for Studies (Chapter 6).''} \emph{Cochrane Handbook for
+{`Searching for Studies (Chapter 6).'} \emph{Cochrane Handbook for
 Systematic Reviews of Interventions Version} 510.
@@
 Li, Qian, Hao Peng, Jianxin Li, Congying Xia, Renyu Yang, Lichao Sun,
-Philip S Yu, and Lifang He. 2020. {``A Survey on Text Classification:
-From Shallow to Deep Learning.''} \emph{arXiv Preprint
-arXiv:2008.00364}.
+Philip S Yu, and Lifang He. 2020. {`A Survey on Text Classification:
+From Shallow to Deep Learning.'} \emph{arXiv Preprint arXiv:2008.00364}.
 
 \leavevmode\hypertarget{ref-lipscomb2000medical}{}%
-Lipscomb, Carolyn E. 2000. {``Medical Subject Headings (MeSH).''}
+Lipscomb, Carolyn E. 2000. {`Medical Subject Headings (MeSH).'}
 \emph{Bulletin of the Medical Library Association} 88 (3): 265.
@@
 \leavevmode\hypertarget{ref-malhi2020explainable}{}%
-Malhi, Avleen, Samanta Knapic, and Kary Främling. 2020. {``Explainable
-Agents for Less Bias in Human-Agent Decision Making.''} In
+Malhi, Avleen, Samanta Knapic, and Kary Främling. 2020. {`Explainable
+Agents for Less Bias in Human-Agent Decision Making.'} In
 \emph{International Workshop on Explainable, Transparent Autonomous
@@
 \leavevmode\hypertarget{ref-marshall2015systematic}{}%
-Marshall, Iain J, and Byron C Wallace. 2019. {``Toward Systematic Review
+Marshall, Iain J, and Byron C Wallace. 2019. {`Toward Systematic Review
 Automation: A Practical Guide to Using Machine Learning Tools in
-Research Synthesis.''} In \emph{Systematic Reviews}, 8:1--10. 1.
+Research Synthesis.'} In \emph{Systematic Reviews}, 8:1--10. 1.
 Springer.
@@
 Minaee, Shervin, Nal Kalchbrenner, Erik Cambria, Narjes Nikzad, Meysam
-Chenaghlu, and Jianfeng Gao. 2021. {``Deep Learning--Based Text
-Classification: A Comprehensive Review.''} \emph{ACM Computing Surveys
+Chenaghlu, and Jianfeng Gao. 2021. {`Deep Learning--Based Text
+Classification: A Comprehensive Review.'} \emph{ACM Computing Surveys
 (CSUR)} 54 (3): 1--40.
@@
 Miwa, Makoto, James Thomas, Alison O'Mara-Eves, and Sophia Ananiadou.
-2014. {``Reducing Systematic Review Workload Through Certainty-Based
-Screening.''} \emph{Journal of Biomedical Informatics} 51: 242--53.
+2014. {`Reducing Systematic Review Workload Through Certainty-Based
+Screening.'} \emph{Journal of Biomedical Informatics} 51: 242--53.
 
@@
 Moore, Alexander, Vanessa Murdock, Yaxiong Cai, and Kristine Jones.
-2018. {``Transparent Tree Ensembles.''} In \emph{The 41st International
+2018. {`Transparent Tree Ensembles.'} In \emph{The 41st International
 ACM SIGIR Conference on Research \& Development in Information
@@
 \leavevmode\hypertarget{ref-pubmedUpdate}{}%
-{``NCBI Insights : Updated Pubmed e-Utilities Coming in April 2022!''}
+{`NCBI Insights : Updated Pubmed e-Utilities Coming in April 2022!'}
 n.d. U.S. National Library of Medicine.
@@
 O'Mara-Eves, Alison, James Thomas, John McNaught, Makoto Miwa, and
-Sophia Ananiadou. 2015. {``Using Text Mining for Study Identification in
-Systematic Reviews: A Systematic Review of Current Approaches.''}
+Sophia Ananiadou. 2015. {`Using Text Mining for Study Identification in
+Systematic Reviews: A Systematic Review of Current Approaches.'}
 \emph{Systematic Reviews} 4 (1): 1--22.
@@
 \leavevmode\hypertarget{ref-ohsawa1998keygraph}{}%
-Ohsawa, Yukio, Nels E Benson, and Masahiko Yachida. 1998. {``KeyGraph:
+Ohsawa, Yukio, Nels E Benson, and Masahiko Yachida. 1998. {`KeyGraph:
 Automatic Indexing by Co-Occurrence Graph Based on Building Construction
-Metaphor.''} In \emph{Proceedings IEEE International Forum on Research
+Metaphor.'} In \emph{Proceedings IEEE International Forum on Research
 and Technology Advances in Digital Libraries-ADL'98-}, 12--18. IEEE.
@@
 Olorisade, Babatunde K, Ed de Quincey, Pearl Brereton, and Peter Andras.
-2016. {``A Critical Analysis of Studies That Address the Use of Text
-Mining for Citation Screening in Systematic Reviews.''} In
+2016. {`A Critical Analysis of Studies That Address the Use of Text
+Mining for Citation Screening in Systematic Reviews.'} In
 \emph{Proceedings of the 20th International Conference on Evaluation and
@@
 \leavevmode\hypertarget{ref-pavlinek2017text}{}%
-Pavlinek, Miha, and Vili Podgorelec. 2017. {``Text Classification Method
-Based on Self-Training and LDA Topic Models.''} \emph{Expert Systems
-with Applications} 80: 83--93.
+Pavlinek, Miha, and Vili Podgorelec. 2017. {`Text Classification Method
+Based on Self-Training and LDA Topic Models.'} \emph{Expert Systems with
+Applications} 80: 83--93.
 
@@
 Poulter, Graham L, Daniel L Rubin, Russ B Altman, and Cathal Seoighe.
-2008. {``MScanner: A Classifier for Retrieving Medline Citations.''}
+2008. {`MScanner: A Classifier for Retrieving Medline Citations.'}
 \emph{BMC Bioinformatics} 9 (1): 1--12.
@@
 Ramezankhani, Azra, Omid Pournik, Jamal Shahrabi, Fereidoun Azizi,
-Farzad Hadaegh, and Davood Khalili. 2016. {``The Impact of Oversampling
+Farzad Hadaegh, and Davood Khalili. 2016. {`The Impact of Oversampling
 with SMOTE on the Performance of 3 Classifiers in Prediction of Type 2
-Diabetes.''} \emph{Medical Decision Making} 36 (1): 137--44.
+Diabetes.'} \emph{Medical Decision Making} 36 (1): 137--44.
 
@@
 \leavevmode\hypertarget{ref-roshan2020improvement}{}%
-Roshan, Seyed Ehsan, and Shahrokh Asadi. 2020. {``Improvement of Bagging
+Roshan, Seyed Ehsan, and Shahrokh Asadi. 2020. {`Improvement of Bagging
 Performance for Classification of Imbalanced Datasets Using Evolutionary
-Multi-Objective Optimization.''} \emph{Engineering Applications of
+Multi-Objective Optimization.'} \emph{Engineering Applications of
 Artificial Intelligence} 87: 103319.
@@
 \leavevmode\hypertarget{ref-rousseau2015graph}{}%
-Rousseau, Francois. 2015. {``Graph-of-Words: Mining and Retrieving Text
-with Networks of Features.''} PhD thesis, Ph. D. dissertation.
+Rousseau, Francois. 2015. {`Graph-of-Words: Mining and Retrieving Text
+with Networks of Features.'} PhD thesis, Ph. D. dissertation.
 
@@
 Rousseau, François, Emmanouil Kiagias, and Michalis Vazirgiannis. 2015.
-{``Text Categorization as a Graph Classification Problem.''} In
+{`Text Categorization as a Graph Classification Problem.'} In
 \emph{Proceedings of the 53rd Annual Meeting of the Association for
@@
 Sampson, Margaret, Jennifer Tetzlaff, and Christine Urquhart. 2011.
-{``Precision of Healthcare Systematic Review Searches in a
-Cross-Sectional Sample.''} \emph{Research Synthesis Methods} 2 (2):
+{`Precision of Healthcare Systematic Review Searches in a
+Cross-Sectional Sample.'} \emph{Research Synthesis Methods} 2 (2):
 119--25.
@@
 \leavevmode\hypertarget{ref-schonlau2017text}{}%
-Schonlau, Matthias, and Nick Guenther. 2017. {``Text Mining Using
-n-Grams.''} \emph{Schonlau, M., Guenther, N. Sucholutsky, I. Text Mining
+Schonlau, Matthias, and Nick Guenther. 2017. {`Text Mining Using
+n-Grams.'} \emph{Schonlau, M., Guenther, N. Sucholutsky, I. Text Mining
 Using n-Gram Variables. The Stata Journal} 17 (4): 866--81.
@@
 \leavevmode\hypertarget{ref-settles2009active}{}%
-Settles, Burr. 2009. {``Active Learning Literature Survey.''}
+Settles, Burr. 2009. {`Active Learning Literature Survey.'}
 
@@
 Vila-Frances, Marcelino Martinez, José R Magdalena, and Antonio J
-Serrano. 2011. {``BELM: Bayesian Extreme Learning Machine.''} \emph{IEEE
+Serrano. 2011. {`BELM: Bayesian Extreme Learning Machine.'} \emph{IEEE
 Transactions on Neural Networks} 22 (3): 505--9.
@@
 \leavevmode\hypertarget{ref-soto2019thalia}{}%
-Soto, Axel J, Piotr Przybyła, and Sophia Ananiadou. 2019. {``Thalia:
-Semantic Search Engine for Biomedical Abstracts.''}
-\emph{Bioinformatics} 35 (10): 1799--1801.
+Soto, Axel J, Piotr Przybyła, and Sophia Ananiadou. 2019. {`Thalia:
+Semantic Search Engine for Biomedical Abstracts.'} \emph{Bioinformatics}
+35 (10): 1799--1801.
 
 \leavevmode\hypertarget{ref-tashman2000out}{}%
-Tashman, Leonard J. 2000. {``Out-of-Sample Tests of Forecasting
-Accuracy: An Analysis and Review.''} \emph{International Journal of
-Forecasting} 16 (4): 437--50.
+Tashman, Leonard J. 2000. {`Out-of-Sample Tests of Forecasting Accuracy:
+An Analysis and Review.'} \emph{International Journal of Forecasting} 16
+(4): 437--50.
 
@@
 \leavevmode\hypertarget{ref-thomas2007eppi}{}%
-Thomas, James, and Jeff Brunton. 2007. {``EPPI-Reviewer: Software for
-Research Synthesis.''}
+Thomas, James, and Jeff Brunton. 2007. {`EPPI-Reviewer: Software for
+Research Synthesis.'}
 
 \leavevmode\hypertarget{ref-tsafnat2013automation}{}%
-Tsafnat, Guy, Adam Dunn, Paul Glasziou, and Enrico Coiera. 2013. {``The
-Automation of Systematic Reviews.''} British Medical Journal Publishing
+Tsafnat, Guy, Adam Dunn, Paul Glasziou, and Enrico Coiera. 2013. {`The
+Automation of Systematic Reviews.'} British Medical Journal Publishing
 Group.
@@
 Tsafnat, Guy, Paul Glasziou, Miew Keen Choong, Adam Dunn, Filippo
-Galgani, and Enrico Coiera. 2014. {``Systematic Review Automation
-Technologies.''} \emph{Systematic Reviews} 3 (1): 1--15.
+Galgani, and Enrico Coiera. 2014. {`Systematic Review Automation
+Technologies.'} \emph{Systematic Reviews} 3 (1): 1--15.
 
 \leavevmode\hypertarget{ref-turian2010word}{}%
-Turian, Joseph, Lev Ratinov, and Yoshua Bengio. 2010. {``Word
+Turian, Joseph, Lev Ratinov, and Yoshua Bengio. 2010. {`Word
 Representations: A Simple and General Method for Semi-Supervised
-Learning.''} In \emph{Proceedings of the 48th Annual Meeting of the
+Learning.'} In \emph{Proceedings of the 48th Annual Meeting of the
 Association for Computational Linguistics}, 384--94.
@@
 Violos, John, Konstantinos Tserpes, Evangelos Psomakelis, Konstantinos
-Psychas, and Theodora Varvarigou. 2016. {``Sentiment Analysis Using
-Word-Graphs.''} In \emph{Proceedings of the 6th International Conference
+Psychas, and Theodora Varvarigou. 2016. {`Sentiment Analysis Using
+Word-Graphs.'} In \emph{Proceedings of the 6th International Conference
 on Web Intelligence, Mining and Semantics}, 1--9.
@@
 \leavevmode\hypertarget{ref-visser2010performing}{}%
-Visser, Eelco. 2010. {``Performing Systematic Literature Reviews with
-Researchr: Tool Demonstration.''} \emph{Technical Report Series
+Visser, Eelco. 2010. {`Performing Systematic Literature Reviews with
+Researchr: Tool Demonstration.'} \emph{Technical Report Series
 TUD-SERG-2010-010}.
@@
 Wallace, Byron C, Kevin Small, Carla E Brodley, and Thomas A Trikalinos.
-2010. {``Active Learning for Biomedical Citation Screening.''} In
+2010. {`Active Learning for Biomedical Citation Screening.'} In
 \emph{Proceedings of the 16th ACM SIGKDD International Conference on
@@
 Wallace, Byron C, Thomas A Trikalinos, Joseph Lau, Carla Brodley, and
-Christopher H Schmid. 2010. {``Semi-Automated Screening of Biomedical
-Citations for Systematic Reviews.''} \emph{BMC Bioinformatics} 11 (1):
+Christopher H Schmid. 2010. {`Semi-Automated Screening of Biomedical
+Citations for Systematic Reviews.'} \emph{BMC Bioinformatics} 11 (1):
 1--11.
@@
 \leavevmode\hypertarget{ref-wilkins2005embase}{}%
-Wilkins, Thad, Ralph A Gillies, and Kathy Davies. 2005. {``EMBASE Versus
+Wilkins, Thad, Ralph A Gillies, and Kathy Davies. 2005. {`EMBASE Versus
 MEDLINE for Family Medicine Searches: Can MEDLINE Searches Find the
-Forest or a Tree?''} \emph{Canadian Family Physician} 51 (6): 848--49.
+Forest or a Tree?'} \emph{Canadian Family Physician} 51 (6): 848--49.
 
 \leavevmode\hypertarget{ref-woods1998medline}{}%
-Woods, David, and Kate Trewheellar. 1998. {``Medline and Embase
-Complement Each Other in Literature Searches.''} \emph{BMJ: British
+Woods, David, and Kate Trewheellar. 1998. {`Medline and Embase
+Complement Each Other in Literature Searches.'} \emph{BMJ: British
 Medical Journal} 316 (7138): 1166.
@@
 \leavevmode\hypertarget{ref-yang2020survey}{}%
-Yang, JinXiong, Liang Bai, and Yanming Guo. 2020. {``A Survey of Text
-Classification Models.''} In \emph{Proceedings of the 2020 2nd
+Yang, JinXiong, Liang Bai, and Yanming Guo. 2020. {`A Survey of Text
+Classification Models.'} In \emph{Proceedings of the 2020 2nd
 International Conference on Robotics, Intelligent Control and Artificial
@@
 \leavevmode\hypertarget{ref-yang2020hyperparameter}{}%
-Yang, Li, and Abdallah Shami. 2020. {``On Hyperparameter Optimization of
-Machine Learning Algorithms: Theory and Practice.''}
+Yang, Li, and Abdallah Shami. 2020. {`On Hyperparameter Optimization of
+Machine Learning Algorithms: Theory and Practice.'}
 \emph{Neurocomputing} 415: 295--316.
@@
 \leavevmode\hypertarget{ref-zhou2021ensemble}{}%
-Zhou, Zhi-Hua. 2021. {``Ensemble Learning.''} In \emph{Machine
-Learning}, 181--210. Springer.
+Zhou, Zhi-Hua. 2021. {`Ensemble Learning.'} In \emph{Machine Learning},
+181--210. Springer.
 
@@
 Zhu, Jingbo, Huizhen Wang, Eduard Hovy, and Matthew Ma. 2010.
-{``Confidence-Based Stopping Criteria for Active Learning for Data
-Annotation.''} \emph{ACM Transactions on Speech and Language Processing
+{`Confidence-Based Stopping Criteria for Active Learning for Data
+Annotation.'} \emph{ACM Transactions on Speech and Language Processing
 (TSLP)} 6 (3): 1--24.

### 2021-10-26 Manuscript/Manuscript_Methods.Rmd
update
changed list style

@@
 bibliography: references.bib
-csl: apa.csl
 output:
@@
 
-## Methods
+# Methods
 
-### General description
+## General description
 
@@
 
-### Record's acquisition and initial labelling
+## Record's acquisition and initial labelling
 
@@
 
-### Text feature extraction
+## Text feature extraction
 
@@
 
-### Label prediction
+## Label prediction
 
@@
 
-$$\pi_i = \frac{1}{M}\sum_{j=1}^MPr(L_i = \text{1}|DTM,m_j)$$
+$$\pi_i = \frac{1}{M}\sum_{j=1}^M Pr(L_i = \text{1}|DTM,m_j)$$
 
@@
 
-### Relevant terms' extraction
+## Relevant terms' extraction
 
@@
 
-### New search query generation
+## New search query generation
 
@@
 
-* We fit a partition tree [@rpart] between the DTM and 800 samples from the PPD;
+- We fit a partition tree [@rpart] between the DTM and 800 samples from the PPD;
 if a term is present multiple times in the DTM (e.g., both title and abstract), they are counted just one, and field term count features are removed.
 This step generates a list of rules composed by $AND$/$NOT$ "conditions" made of terms/authors/keywords/MESH tokens, which together identify a group of records.
-* For each rule, negative conditions (i.e., $NOT$ statements) are added iteratively, starting from the most specific one, until no conditions are found that would not also remove positive records.
-* The extended set of rules is sorted by positive-negative record difference in descending order.
+- For each rule, negative conditions (i.e., $NOT$ statements) are added iteratively, starting from the most specific one, until no conditions are found that would not also remove positive records.
+- The extended set of rules is sorted by positive-negative record difference in descending order.
 The cumulative number of unique positive records is computed and used to group the rules.
 Rules inside each group are ordered by specificity.
-* The researcher is then asked to review the rule groups, selecting one or more rules (useful if they convey different meaning) from each, or edit them (in case too specific positive or negative conditions were included).
+- The researcher is then asked to review the rule groups, selecting one or more rules (useful if they convey different meaning) from each, or edit them (in case too specific positive or negative conditions were included).
 It is possible to exclude a group of rules altogether, especially those with the worse sensitivity/specificity ratio.
-* The selected rules are joined together by $OR$ statements, defining a subset of records with a sensibly higher proportion of positive records than the original one.
-* Redundant rules (i.e., rules whose positive records are already included in more specific ones) and conditions (i.e., conditions that once removed do not decrease the total number of positive or do not increase the negative records) are removed.
-* Finally, the rules are re-elaborated in a query usable on the major scientific databases.
+- The selected rules are joined together by $OR$ statements, defining a subset of records with a sensibly higher proportion of positive records than the original one.
+- Redundant rules (i.e., rules whose positive records are already included in more specific ones) and conditions (i.e., conditions that once removed do not decrease the total number of positive or do not increase the negative records) are removed.
+- Finally, the rules are re-elaborated in a query usable on the major scientific databases.
 
@@
 
-### Hyperparameter evaluation
+## Hyperparameter evaluation
 
@@
 
-* Size of the initial training set: 50, 100, 250, 500 records;
-* Number of models in the ensemble: 1, 5, 10, 20, 40, 60 repetitions;
-* Oversampling rate of positive records: (1x (i.e., no oversampling), 10x, 20x;
-* PrI quantiles for building the uncertainty zone: 80%, 90%, 98%;
-* Source of randomness between models in the ensemble: MCMC sampling only [@robert2004monte], MCMC plus data bootstrapping [@breiman1996bagging] of the training set.
+- Size of the initial training set: 50, 100, 250, 500 records;
+- Number of models in the ensemble: 1, 5, 10, 20, 40, 60 repetitions;
+- Oversampling rate of positive records: (1x (i.e., no oversampling), 10x, 20x;
+- PrI quantiles for building the uncertainty zone: 80%, 90%, 98%;
+- Source of randomness between models in the ensemble: MCMC sampling only [@robert2004monte], MCMC plus data bootstrapping [@breiman1996bagging] of the training set.
 

### 2021-10-26 Manuscript/S1.Protocol.Rmd
update

@@
 
-This document will guide the reader along the steps to utilize the framework and reproduce our results.
+This document will guide the reader along the steps to utilise the framework and reproduce our results.
 
-Add intallation and setup info here
+Add installation and setup info here.
 
@@
 sometimes it is easier to create two different simpler queries than a complex and long one that returns the same results).\
-In our implementation, we define as sessions the group of actions that includes the utilization of a search query and the subsequent iterations of manual review and automatic classification of its results.\
+In our implementation, we define as sessions the group of actions that includes the utilisation of a search query and the subsequent iterations of manual review and automatic classification of its results.\
 
@@
 The records will be stored as CSV files in folders with the following structure: `Records/session_id/query_id`, created automatically.
-The function also creates or update a **journal** (a CSV or Microsoft Excel file) with all the information about sessions, queries and search results.\
-Some services (IEEE, WOS) requires API key to access the data; an API key is not mandatory for Pubmed but can help avoid quota limitations in case of a large number of results.
-IEEE can also be searched without API;
-the framework will utilize a webscraping engine in case the API key is missing, but the success of this method is not guaranteed.
+The function also creates or updates a **journal** (a CSV or Microsoft Excel file) with all the information about sessions, queries and search results.\
+Some services (IEEE, WOS) requires an API key to access the data;
+the API key is not mandatory for Pubmed but can help avoid quota limitations in case of a large number of results.
+IEEE can also be searched without API:
+the framework will utilise a web scraping approach if the API key is missing, but the success of this method is not guaranteed.
 See Supplemental Material S3 for detailed instruction on preliminary steps and tips for each supported search engine.
-These keys can be stored in the `secrets.R` file with the following example code (the "*baysren*" prefix identify the package specific options):
+These keys can be stored in the `secrets.R` file in the working directory, with the following example code (the "*baysren*" prefix identifies the package specific options):
 
@@
 
-If previously downloaded results are already available, users can create the `Record` folder manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`), and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g.
+If previously downloaded results are already available, users can create the `Record` folder manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`).
+The function will acquire and parse them into a standard format, even if split into multiple files due to download limits (e.g.
 `Pubmed1.nbib`, `Pubmed2.nib`, etc.).
-In addition to Pubmed, WOS and IEEE, this method permits to import also Embase and Scopus records, for which an API search was not yet implemented.\
+In addition to Pubmed, WOS and IEEE, this method permits to import also EMBASE and SCOPUS records, for which an API search was not yet implemented.\
 Using the `actions` argument, users can choose whether to perform an API search, parse already downloaded results, or both.
 
-Note that for Pubmed, the API search may return slightly fewer records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the resulting .nbib files in the `Session/Query` folder.
+Note that for Pubmed, the API search may return slightly fewer records than a manual one due to a different query expansion algorithm (this divergence should be solved in April 2022) between the two services, therefore is advisable to perform also a manual search and put the resulting .nbib files in the `Session/Query` folder.
 `perform_search_session()` will acquire them seamlessly.
@@
 
-Once the records are stored, they must be read and merged into an **annotation file** where the initial manual review will be performed.\
-A series of functions are available to prepare the data for the manual evaluation:
+Once the records are stored, they must be read and merged into an **annotation file**, where the initial manual review will be performed.\
+A series of functions are available to prepare the data for manual evaluation:
 
@@
 
-All these steps are more easily performed through `create_annotation_file()`.
+All these steps are joined into the `create_annotation_file()` function.
 This function can take as input either the path to record files, or the parsed records (one data frame or a list of data frames) or a group of folders where to look for files into./
 In addition, it also allows adding the new records to a previous annotation file (arg `prev_records`).
-This is useful with subsequent searching sessions with different queries; previous manual classifications can be imported using `prev_classification`.
-By passing the original query to the `reorder_query` argument, the records are reordered empirically to increase the probability of finding positive matches first.
+This is useful when performing consecutive search sessions with different queries;
+previous manual classifications can be imported using `prev_classification`.\
+If the original query is passed to the `reorder_query` argument, the records are reordered according to the frequency of query terms in the title and abstract (**simple query ordering**);
+this approach lets increase the rate of relevant matches at the beginning of the dataset.
 
@@
 
-	# record file paths
+	# either record file paths
 input <- record_files
 
-	# specific record file folders
+	# or specific record file folders
 input <- file.path('Records', 'Session1', 'Query1')
@@
 
-	# finally it can accept the already parsed files
+	# or the already parsed files
 input <- read_bib_files(record_files)
@@
 # We can then call create_annotation_file() with one of the above input
-Annotation_data <- create_annotation_file(record_files, reorder_query = query)
+Annotation_data <- create_annotation_file(input, reorder_query = query)
 
@@
 
-The file annotation file is called `Records_{date}` in the folder `Sessions/{session_name}` with `date` being the creation timestamp and `session_name` being the name passed by the user.
+The file annotation file is called `Records_{date}`, situated in the folder `Sessions/{session_name}`;
+`date` here represents the session creation timestamp, and `session_name` the name passed by the user.
 
-Notice that the framework is "piping" friendly, and the precedent steps can be all performed in one call (which is the suggested procedure):
+Notice that the framework is "pipe" friendly, and the precedent steps can be all performed in one call:
 
@@
 	journal = 'Session_journal.csv') %>%
+
 	# return the record file paths
 	extract_source_file_paths() %>%
+
 	# read, join, reorder records and save them in the Sessions folder
 	create_annotation_file(reorder_query = query) %>%
+
 	# Create a new session with the records
@@
 The annotation file has a column called `Rev_manual`, where records need to be classified as "positive" (y) or "negative" (n) matches by the user.
-We suggest manually labelling around 250  records, which should be sufficient if a minimum ~20% positivity rate is maintained (see the section about model hyperparameter optimization)./
-The function `check_classification_trends()` can help visualize the trend of the positives/negatives as the number of classified records increases./
+We suggest manually labelling an **initial training set** of 250 records, which should be sufficient if a minimum ~20% positivity rate is present (see the section about model hyperparameter optimisation)./
+The function `check_classification_trends()` can help visualise the trend of the positives/negatives as the number of classified records increases./
 
-Once the first records are labelled manually, the function `enrich_annotation_file()` will use the Bayesian Additive Regression Trees (BART) machine learning model to learn the labelling pattern of the user and predict the positive match probability for the unlabelled records.
-Follows a summary of the prediction process:
+Once the initial training set is prepared, the function `enrich_annotation_file()` will use a Bayesian Additive Regression Trees (BART) machine learning model to learn the labelling pattern given the record data and predict the positive match probability for the unlabelled records.\
+`enrich_annotation_file()` comprises two steps.
+The first step is the creation of a **Document Term Matrix** (DTM):
 
-- a Document Term Matrix (DTM) is created, extracting terms from the (lemmatized) title and abstract of the records and adding the authors and keywords.
-For each term, a 0/1 label specifies if it is present in each record.
-Also, co-occurring terms are added as n-grams, and highly copresent terms are joined as synonyms;
-- the positive records are oversampled **10x** to improve sensitivity;
-- the function models the labelling pattern using the manually labelled records (learning step);
-- after the model is created, it assigns a probability distribution of positivity to each record, labelled and unlabelled (prediction step).
-If the number of records is large, the prediction step is broken into chunks of **5000 records**, to avoid memory saturation; the user will need to set up this parameter according to her machine capabilities;
-- this process is repeated **10 times**, and the predictive distributions are averaged to induce shrinkage of the estimates (i.e., decrease the chance of outliers);
-- the resulting distribution is summarised by its **98% interval**, and the unlabelled records will receive a positive/negative predicted label if their interval ends up entirely in the joint interval of the positively/negatively labelled records.
-All the other records will be labelled as unknown (unk) and will require manual review.
+- The framework extracts **features** from text data (i.e., title and abstract) of the records, authors, keywords and MESH terms (see Methods for more info).
+Before features extraction, text data terms are lemmatised, stop-words are removed, and only nouns, adjectives, verbs and untagged terms are retained.
+Authors, keywords, and MESH are kept unmodified.
+Co-occurrent features (non-consecutive ngrams, **nc-grams**) are identified and **redundant features** (i.e. terms always appearing together) are joined to decrease the feature space noise.
+- For each term, a 0/1 label specifies if it is present in each record.
+- Positive records are oversampled **10x** to improve sensitivity;
+- An extra feature is added for each record field (title, abstract, authors, keywords, MESH terms), reporting the number of terms in each.
 
-The user can define parameters like the positives' oversampling rate, the number of models to average, whether to apply bootstrap resampling before each repetition, the prediction chunk size, and the prediction distribution interval range.
-To use the function, the only input needed is the session name; the function will automatically identify the relevant file to make predictions on.
+The second step is the modelling of the labelling pattern and the predictions of the relevancy/positivity probability:
+
+- The function models the labelling pattern using the manually labelled records (**learning phaseéé);
+- After the model is created, it assigns a **posterior predictive distribution** (PPD) of the probability of positivity to each record (**prediction phase**).
+If the number of records is large, the prediction step is broken into chunks of **5000 records**, to avoid memory saturation;
+the users can set up this parameter according to their machine capabilities;
+- This process is repeated **10 times**, and the predictive distributions are averaged to induce shrinkage of the estimates (i.e., decrease the chance of outliers), creating a prediction **ensemble**;
+- The resulting distributions are summarised by the **98% interval** [98% PrI] and the median;
+the [98% PrI] identifies the **uncertainty zone**;
+- The unlabelled records will receive a positive/negative predicted label;
+the label is positive if its lower [98% PrI] bound is higher than the uncertainty zone upper bound and negative if the upper [98% PrI] bound is lower than the uncertainty zone lower bound.
+All other records are labelled as **uncertain** (unk);
+- If a predicted label does not match an existing one, the record will be labelled as **check**.
+
+The user can define parameters like the positives' oversampling rate, the number of models to average in the ensemble, whether to apply bootstrap resampling before each repetition, the prediction chunk size, and the PPD quantiles used to build the uncertainty zone.
+To use the function, the only input needed is the session name;
+the function will automatically identify the relevant file to make predictions on.
 
@@
 
-This function will produce a new excel file which is stored in the Annotations folder of the session; the file will contain a column called `Rev_prediction_new` where the user will find records that require manual review marked by "*".
+This function will produce a new file which is stored in the Annotations folder of the session;
+the file will contain a column called `Rev_prediction_new` where the user will find records that require manual review marked by "*".
 These are records with uncertain labelling ("unk"), but also positive predictions and "y"/"n" predictions that contradict previous manually input labels (labelled as "check").
@@
 
-- a results summary page reporting the number of records in need of manual review (which includes "unk", "check", and unreviewed "y" records), the changes, and the final distribution of the labels.
-It also shows other information like the number of terms in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later).
-The content of this summary is also saved as a csv file in the Results folder.
-- a variable importance page which list the used terms in order of the fraction of BART trees in which they were used.
-If more than one model repetition is used, a more robust score is computed taking the ratio of the mean of the term tree fraction among models and its standard deviation.
-- the arguments passed to the function if different from the default, useful for reproducibility.
-- a classification performance summary. The procedure may take some time and requires `cmdstan` installed on the machine. Therefore the `compute_performance` argument is set to FALSE by default.
+- A results summary page reporting the number of records in need of manual review (which includes "unk", "check", and unreviewed "y" records), the changes, and the final distribution of the labels.
+It also shows other information like the number of features in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later).
+The content of this summary is also saved as a CSV file in the Results folder.
+- A variable importance page which list the used terms in order of the fraction of BART trees in which they were used.
+If an ensemble of models is used, a more robust score is computed, taking the ratio of the mean of the term tree fraction among models and its standard deviation.
+- The arguments passed to the function if different from the default, useful for reproducibility.
+- A classification performance summary. The procedure may take some time and requires `cmdstan` installed on the machine. Therefore the `compute_performance` argument is set to `FALSE` by default.
 
-Finally, the posterior samples produced by the Bayesian engine are stored on the disk.
-This feature can be turned off to save disk space, but at least the samples of the last annotation are necessary to build a new search query building (see next section) and for classification performance estimation.
+Finally, the PPD ensemble produced by the Bayesian engine is stored on the disk.
+This feature can be turned off to save disk space, but at least the samples of the last annotation are necessary to build a new search query (see next section).
 
@@
 Once the manual review of the generated annotation file is completed, the user can **rerun exactly the same function**.
-The reviewed annotation file will be automatically picked up and used for a new CR iteration.
+The last reviewed annotation file will be automatically picked up and used for a new CR iteration.
 If the number of records requiring manual review is excessively high (e.g.
@@
 
-If there are no positive results (after manual review) in a CR iteration, the framework records the next iteration as a "replication".
-After four replications with no positive matches are complete, the function will prevent another iteration and send a warning message.
-The user can change the replication limit; furthermore, it is possible to have the function stop if either a specified number (or a fraction) of the total records has been manually reviewed or if a certain number of positive matches have been found.
+If there are no positive results (after manual review) in a CR iteration, the framework records the next iteration as a **replication**.
+After four replications with no new positive matches, the function will prevent another iteration and send a warning message, indicating that the session is complete.
+The user can change the replication limit;
+furthermore, it is possible to prevent the function from starting if either a specified number (or a fraction) of the total records has been manually reviewed or if a certain number of positive matches have been found.
 These three parameters are passed to the `limits` argument, which has the following structure and defaults:
@@
 
-The result files in the Results folder are generated after the Classification phase but before the Review one, and therefore show preliminary results with still unreviewed records.
+The result files in the Results folder are generated after the Classification step but before the Review one, and therefore show preliminary results with still unreviewed records.
 The function `consolidate_results(session_name)` will update the results files to show the results after the manual review.
-The temporary result data is stored anyway in the respective annotations file.
+The original result data is stored anyway in the respective annotations files.
 
@@
 It is not uncommon for the first query used in a systematic review not to be the most effective one, especially in terms of sensitivity.
-We tried to address the problem by creating an automatic query generation system.
-The solution is experimental and favours sensitivity at the expense of specificity.
-After a step in which a set of candidate query rules (to be joined by an OR logic) are selected, the user is asked to review them and select rules that make more sense to the topic or deselect too general rules that would generate many unspecific results.
-The algorithm is, of course, not topic aware and therefore may very likely pick terms that are only casually associated with the topic of study; therefore, human review and selection are still needed.
+We tried to address the problem by creating an automatic query generation system.\
+The solution is experimental and greatly favours sensitivity at the expense of specificity.
+This is the general query generation mechanism:
+
+- We fit a partition tree between the DTM and 800 samples from the PPD;
+if a term is present multiple times in the DTM (e.g., both title and abstract), they are counted just one, and field term count features are removed.
+This step generates a list of rules composed by $AND$/$NOT$ "conditions" made of terms/authors/keywords/MESH tokens, which together identify a group of records.
+- For each rule, negative conditions (i.e., $NOT$ statements) are added iteratively, starting from the most specific one, until no conditions are found that would not also remove positive records.
+- The extended set of rules is sorted by positive-negative record difference in descending order.
+The cumulative number of unique positive records is computed and used to group the rules.
+Rules inside each group are ordered by specificity.
+- The researcher is then asked to review the rule groups, selecting one or more rules (useful if they convey different meaning) from each, or edit them (in case too specific positive or negative conditions were included).
+It is possible to exclude a group of rules altogether, especially those with the worse sensitivity/specificity ratio.
+- The selected rules are joined together by $OR$ statements, defining a subset of records with a sensibly higher proportion of positive records than the original one.
+- Redundant rules (i.e., rules whose positive records are already included in more specific ones) and conditions (i.e., conditions that once removed do not decrease the total number of positive or do not increase the negative records) are removed.
+- Finally, the rules are re-elaborated in a query usable on the major scientific databases.
 
@@
 # (higher positive/negative matches delta) rules; also adds negative terms to
-# increase specificity. A dataframe is generated (or automatically saved if
+# increase specificity. A data frame is generated (or automatically saved if
 # save_path is set). The output proposes groups of equivalent (in terms of the
@@
 Once the final query is generated, it is advisable to add a constraining subquery with an AND logic to restrict the results to the scope of the topic of interest.\
-In our case, we added "AND ((antimicrobial resistance) OR (healthcare infection))" since being the global topic of our research, those terms were understandably not selected by the query generation algorithm as discriminant.\
+In our case, we added "AND ((antimicrobial resistance) OR (healthcare infection))" since, being the global topic of our research, those terms were understandably not selected by the query generation algorithm as discriminant.\
 
@@
 Once the new query was generated, a second search session called `Session2` was created, using the strategy described in the protocol.
-Due to the lower specificity of the second query, particular care was needed in managing the far larger amount of records since manual downloading may be necessary from Pubmed, Embase, and Scopus (which usually have limits on the amount of records one can download at once), and because the automatic classification processing time increases proportionally with the number of records to label.\
-It is advisable then to consider removing the less specific rules iteratively from the query until a manageable number of records is obtained, considering that the probability of finding new positive matches not already found by more specific queries drops exponentially.\
+Due to the lower specificity of the second query, particular care may be needed in managing the far larger amount of records:
+multiple record files may need to be downloaded from Pubmed, EMBASE, and SCOPUS since they have limits on the number of records one can download at once;
+also, the machine learning classification processing time increases proportionally with the number of records to label.\
+It is advisable then to consider removing the less specific rules iteratively from the new query until a manageable number of records is obtained, considering that the probability of finding new positive matches not already found by more specific queries drops exponentially.\
 
 Once the new records are collected, `enrich_annotation_file('Session2')` (or any other new session name) can be used to perform the new CR iterations.
-It may be possible that during the first CR iteration the number of records requiring manual review is a large amount: we suggest evaluating still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.
+It may be possible that during the first CR iteration, the number of records requiring manual review is a significant number:
+we suggest evaluating still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.
 
@@
 
-A number of tools are available to evaluate the automatic classification performance.\
-As said before, a result file is stored in the session folder for each CR iteration with information on the classification status; remember to run `consolidate_results(session_name)` if you want these results to take into account the manual review of the predicted labels.\
-`compute_changes()` is a simple function that take an annotation dataframe and computes the changes from the last annotation iteration.\
+A number of tools are available to evaluate the classification performance.\
+As said before, a result file is stored in the session folder for each CR iteration with information on the classification status;
+remember to run `consolidate_results(session_name)` if you want these results to take into account the manual review of the predicted labels.\
+`compute_changes()` is a simple function that take an annotation data frame and computes the changes from the last annotation iteration.\
 The primary function for result analysis is `estimate_performance()`.
 The function uses a Bayesian model to estimate how the probability of a positive match drops as records' lower boundary of the posterior predictive interval decreases.
-This model computes the cumulative distribution of possibly missed positive records, which in turn permits extraction of the engine's theoretical sensitivity and efficiency boundaries.
-These boundaries are worse case scenarios since it is impossible to know the number of missed positive records.\
-The function returns the Bayesian $R^2$ of the model (values below 85-90% would invalidate this analysis), the posterior sensitivity, the observed and theoretical number positives, the expected efficiency given the theoretical number of positives (that is 1 - the number of records reviewed above the number of records to review to find the predicted number of positives according to a negative hypergeometrical distribution).
+This model computes the cumulative distribution of possibly missed positive records, which permits extraction of the engine's theoretical sensitivity and efficiency to lower 90% credibility boundaries (i.e., the indicators are better than these values with 95% probability).
+These boundaries depict worse case scenarios since it is impossible to know the actual number of missed positive records.\
+The function returns the Bayesian $R^2$ of the model (values below 85-90% would invalidate the model analysis), the posterior sensitivity, the observed and theoretical number positives, the expected efficiency given the theoretical number of positives (that is 1 - the number of reviewed records above the number of records to review to find the predicted number of positives according to a negative hypergeometrical distribution).
 Also, the function plots the cumulative distribution of the observed and theoretical number of positive records.\
-`extract_var_imp()` extract the most relevant terms used by the BART model and summarises their relevancy for the machine learning model and their statistical relevancy in a simple generalized linear model.
-A discrepancy between these two scores indicates a non-linear effect of the terms.
+`extract_var_imp()` extract the most relevant terms used by the BART model and summarises their relevancy for the machine learning model and their statistical relevancy in a simple generalised linear model.
+A discrepancy between these two scores indicates a non-linear effect/interaction between terms.
 
-Finally, several functions are available (check `R/Reporting.R`) to summarise and format the results.
-For example, `summarise_by_source()` and `summarise_sources_by_session()`, respectively for one session or a group of sessions, summarise from which scientific database the records are collected from, while `get_source_distribution()` describe the distribution of the number of common sources per record.\
-`summarise_annotations()` and `summarise_annotations_by_session()` describe the results of the CR iterations, again for one or many sessions, reporting the number of positive and negative matches, the number of terms (features) used by the machine learning model, and how the labels changes between iterations.
+Finally, several functions are available (check `R/Reporting.R`) to summarise and format the results.\
+For example, `summarise_by_source()` and `summarise_sources_by_session()`, respectively for one session or a group of sessions, report the scientific databases the records are collected from, while `get_source_distribution()` describes the distribution of the number of common sources per record.\
+`summarise_annotations()` and `summarise_annotations_by_session()` describe the results of the CR iterations, again for one or multiple sessions, reporting the number of positive and negative matches, the number of terms (features) used by the machine learning model, and how the labels change between iterations.
 `format_performance()` and `format_var_imp()` format the output of the similarly named analyses.
-`plot_predictive_densities()` plots how the mixture of posterior predictive distributions of records, divided into positive, negative and to-review records, change between iterations,
+`plot_predictive_densities()` plots how the mixture of posterior predictive distributions of records, divided into positive, negative and to-review records, change between iterations.
 
-# Model parameters' optimization
+# Model parameters' optimisation
 
@@
 Sensitivity \times Efficiency = \\
-\frac{Pos.\ found}{Tot.\ pos.} \times \frac{Records\ reviewed}{Tot.\ records}
+\frac{Pos.\ found}{Tot.\ pos.} \times \bigg(1 - \frac{Records\ reviewed}{Tot.\ records}\bigg)
 $$
 
-We added a “grid search” algorithm to find the best set of hyperparameters. We tested these tools on our dataset, manually labeling the first 1200 records, ordered by simple query match.\
-The first step is to create a folder where to store the file required for the search, for example *Grid Search*.
-Then a fully reviewed records file in the format generated by `create_annotation_file()` is necessary; this file can be put in the *Grid Search* but it is not mandatory.
-Once the folder and the file are ready run:
+We utilise a “grid search” algorithm to find the best set of hyperparameters.
+We tested these tools on our dataset, manually labelling the first 1200 records, ordered by simple query match.\
+The first step is to create a folder where to store the file required for the search, for example, *Grid Search*.
+Then a fully reviewed record file in the format generated by `create_annotation_file()` is necessary;
+this file can be put in the *Grid Search*, but it is not mandatory.\
+
+Once the folder and the file are ready, run:
 
@@
 	prev_classification = records,
-	## Model parameters
+	## Model parameters (can be changed by users)
 	resample = c(FALSE, TRUE),
@@
 
-with `records` being the fully annotated data frame or a file path to it. `prev_classification` can be used to import a different classification file with prelabeled records.
+with `records` being the fully annotated data frame or a file path to it.
+`prev_classification` can be used to import a different classification file with prelabeled records.
 
@@
 
-* resample: whether to use bootstrapping to increase variability between the ensemble models;
-* n_init: number of initially labelled records to train the machine learning model on;
-* n_models: the number of models to fit and then average to decrease the variance due to random sampling in the MCMC algorithm. It reduces the likelihood of extreme predictions;
-* pos_mult: the oversampling rate of positive records. Useful to improve sensitivity;
-* pred_quants: the distribution quantiles of each posterior prediction, used to define the uncertain records that require manual review.
+- resample: whether to use bootstrapping to increase variability between the ensemble models;
+- n_init: number of initially labelled records to train the machine learning model on;
+- n_models: the number of models to fit and then average to decrease the variance due to random sampling in the MCMC algorithm. It reduces the likelihood of extreme predictions;
+- pos_mult: the oversampling rate of positive records. Useful to improve sensitivity;
+- pred_quants: the distribution quantiles of each PPD, used to define the uncertainty zone and identify records to review.
 
-Once the grid search is performed, the function `analyse_grid_search()` can be used to analyze its results.
-This function uses a partition tree analysis to identify hyperparameter sets (performance clusters) with different mean performance scores.
-As said before, the default score is Sensitivity x Efficiency; alternatives are the Positive Rate (i.e., positive records found over total records) or Positive Rate x Sensitivity.\
-The function produces a dataframe with the score and the cluster of reference of each combination of parameters, the best hyperparameter set (i.e., the most efficient set among the most sensitive in the best cluster) and the best set for each cluster.
-Also, the function creates a plot to visualize the individual impact on performance of each hyperparameter.
+Once the grid search is performed, the function `analyse_grid_search()` can be used to analyse its results.
+This function uses a partition tree analysis to identify hyperparameter sets (**performance clusters**) with different mean performance scores.
+As said before, the default score is Sensitivity x Efficiency;
+alternatives are the Positive Rate (i.e., positive records found over total records) or Positive Rate x Sensitivity.\
+The function produces a data frame with the score and the cluster of reference of each combination of parameters, the best hyperparameter set (i.e., the most efficient set among the most sensitive in the best cluster) and the best set for each cluster.
+Also, the function creates a plot to visualise the individual impact on performance of each hyperparameter.
 
-Once chosen, the hyperparameters can be pass to `enrich_annotation_file()`.\
-Mind that the grid search process may take many days, even on powerful computers, so we suggest sticking to the default set of `enrich_annotation_file()`. \
+Once chosen, the hyperparameters can be passed to `enrich_annotation_file()`.\
+Mind that the grid search process may take many days, even on powerful computers, so we suggest sticking to the default set of parameters when using `enrich_annotation_file()`. \

### 2021-11-23 R/Model.R
Clean: remove old commented or redundant code

@@ -147,348 +147,6 @@ compute_BART_model <- function(train_data, Y, preds = NULL, save = F,
 	model
 }
 
-# compute_pred_performance <- function(model, data = NULL, Y = NULL, summary = F,
-# 																		 quants = getOption('baysren.probs'), AUC.thr = .9) {
-#
-# 	library(scales)
-# 	library(pROC)
-# 	library(glue)
-# 	library(pbapply)
-# 	library(pbmcapply)
-#
-# 	if (!is.null(data)) {
-# 		if (is.null(Y)) stop('Define the Y variable name.')
-#
-# 		X <- data %>% select(all_of(model$X %>% colnames()))
-# 		y <- data[[Y]]
-# 	} else {
-# 		X <- model$X
-# 		y <- model$y
-# 	}
-#
-# 	if (is.factor(y)) {
-# 		y <- relevel(y, ref = levels(y)[2])
-# 		y_levels <- levels(y)
-# 	} else {
-# 		y_levels <- sort(unique(y), T)
-# 	}
-#
-# 	samples <- bart_machine_get_posterior(model, new_data = X)$y_hat_posterior_samples
-#
-# 	out <- mclapply(1:ncol(samples), function(i) {
-# 		roc <- pROC::roc(response = y, predictor = samples[,i])
-# 		data.frame(
-# 			AUC = pROC::auc(roc) %>% as.vector(),
-# 			pROC::coords(roc, "best",
-# 									 ret = c('threshold', 'sensitivity',
-# 									 				'specificity', 'accuracy', 'ppv', 'npv'),
-# 									 transpose = F) %>%
-# 				as.list() %>% as.data.frame.list() %>% head(1) %>%
-# 				setNames(c('Threshold', 'Sens', 'Spec', 'Acc', 'PPV', 'NPV')),
-# 			Sens.thr = quantile(samples[y == y_levels[1], i], min(quants)),
-# 			Spec.thr = quantile(samples[y == y_levels[2], i], max(quants))
-# 		)
-# 	}) %>% bind_rows()
-#
-# 	if (summary) {
-# 		summarise_pred_perf(out, quants)
-# 	} else out
-#
-# }
-
-# compute_pred_performance2 <- function(DTM, models, pred_quants = c(.01, .5, .99),
-# 																			negLim = NULL, posLim = NULL) {
-# 	message('Build indexes')
[…]

### 2021-11-23 R/Setup.R

@@ -169,21 +169,6 @@ import_data <- function(input, ...) {
 	stop('Input should be an existing csv/excel file path or a data.frame, found "', class(input),'".')
 }
 
-summarise_args <- function(args) {
-	print(args %>% names())
-	args %>%
-		names %>% lapply(function(name) {
-
-			if (name == '' || !exists(name)) return(NULL)
-			obj <- get(name)
-			data.frame(
-				name,
-				value = if (is.data.frame(obj)) paste(class(obj), collapse = ', ') else capture.output(str(obj)) %>% head() %>% paste(collapse = '\n') %>% str_trim()
-			)
-		}) %>% bind_rows()
-}
-
-
 
 # Load the infrastructure -------------------------------------------------
 

### 2021-11-23 R/Record_management.R
Docs: added function documentation, plus some code clean-up and reordering

@@ -1,3 +1,9 @@
+#' Clean up problematic text in the citation data.
+#'
+#' @param df The data frame to be cleaned.
+#'
+#' @return The cleaned data frame
+#'
 clean_record_textfields <- function(df) {
 	mutate(df,
 				 across(where(is.character),
@@ -8,17 +14,69 @@ clean_record_textfields <- function(df) {
 	)
 }
 
+
+#'Extract the path to citation records files
+#'
+#'The information on the records' location is stored in the session journal
+#'created by `perform_search_session()`. It is possible to select records from
+#'specific session, query, source combinations. Only parsed or API downloaded
+#'record paths will be returned, not the raw data source files.
+#'
+#'@param journal A data frame produced by `perform_search_session()` or a file
+#'  path to it.
+#'@param sessions,queries,sources Sessions, queries and sources for which one
+#'  wants to get the record data. By default all record file paths are
+#'  retrieved.
+#'@param records_folder The path to the folder where the records are stored. By
+#'  default is named "Records".
+#'
+#'@return A vector of file paths.
+#'@export
+#'
+#'@examples
+#'
+#'\dontrun{
+#' journal <- perform_search_session(
+#'   query = query, year_query = year_filter,
+#'   session_name = 'Session1', query_name = 'Query1',
+#'   records_folder = 'Records',
+#'   journal = 'Session_journal.csv')
+#'
+#'   # using the journal as data frame
+#'   paths <- extract_source_file_paths(journal)
+#'
+#'   # using the journal path
+#'   paths <- extract_source_file_paths('Session_journal.csv')
+#'}
 extract_source_file_paths <- function(journal, sessions = journal$Session_ID,
 																			queries = journal$Query_ID,
 																			sources = journal$Source,
 																			records_folder = 'Records') {
-	journal %>% filter(Session_ID %in% sessions, Query_ID %in%  queries,
-										 Source %in% sources) %>%
+	import_data(journal) %>%
+		filter(Session_ID %in% sessions, Query_ID %in% queries, Source %in% sources) %>%
 		with(file.path(records_folder, Session_ID, Query_ID, Output_file)) %>%
 		unique()
 }
 
[…]

### 2021-11-23 R/Record_search.R
Clean: pubmed is more correct of medline, which is a subset of pubmed

@@ -229,7 +229,7 @@ search_pubmed <- function(query, year_query = NULL, additional_fields = NULL,
 
 	message('- parsing results')
 
-	records <- parse_medline(records %>% unlist() %>% paste(collapse = '\\n\\n')) %>%
+	records <- parse_pubmed(records %>% unlist() %>% paste(collapse = '\\n\\n')) %>%
 		mutate(Source_type = 'API')
 
 	message('...found ', nrow(records), ' records.')
@@ -501,7 +501,7 @@ perform_search_session <- function(query, year_query = NULL, actions = c('API', 
 
 		if (file.exists(out_file)) {
 			if (!overwrite) {
-				warning(basename(out_file), ' already present and argument overwrite == FALSE.', call. = F)
+				warning(basename(out_file), ' already present and argument overwrite is FALSE.', call. = F)
 
 				read_csv(out_file, col_types = cols())
 			} else {

### 2021-11-23 Manuscript/S1.Protocol.Rmd
clean: rename and move check_classification_trends in another source file

@@
 We suggest manually labelling an **initial training set** of 250 records, which should be sufficient if a minimum ~20% positivity rate is present (see the section about model hyperparameter optimisation)./
-The function `check_classification_trends()` can help visualise the trend of the positives/negatives as the number of classified records increases./
+The function `plot_classification_trends()` can help visualise the trend of the positives/negatives as the number of classified records increases./
 

### 2021-11-23 R/Record_management.R

@@ -808,69 +808,3 @@ get_session_files <- function(session_name,
 		file.path(session_path, files)
 	}) %>% setNames(which)
 }
-
-#' Plot the cumulative trend of positive and negative labelled records.
-#'
-#' @param records An annotated data frame of records.
-#' @param column The column from which the record labels are taken. By default
-#'   the labels are taken by the manual plus the automatic classification,
-#'   excluding labels imported using \code{import_classification()}.
-#' @param step_size The interval with which the cumulative numbers are plotted.
-#' @param limit How many records to display.
-#'
-#' @return A `ggplot2` object.
-#' @export
-#'
-#'\dontrun{
-#'data <- get_session_files('Session1')$Annotations %>% last() %>%
-#'  import_data()
-#'
-#'check_classification_trend(data)
-#'}
-check_classification_trend <- function(records, column = NULL,
-																			 step_size = 20, limit = NULL) {
-
-	# Join manual classifications in one target column
-	if (is.null(column)) {
-		records <- records %>%
-			mutate(Target = coalesce_labels(., c('Rev_prediction', 'Rev_manual')))
-	} else records$Target <- records[[column]]
-
-	records <- records %>% arrange(Order) %>%
-		filter(!is.na(Target))
-
-	# Define plot breaks according to a limit of reviewed records
-	if (is.null(limit)) limit <- max(which(!is.na(records$Target)))
-	steps <- seq(step_size, limit, by = step_size) %>% c(limit) %>% unique()
-
-	# Count positive and negative matches in every break
-	df <- pblapply(steps, function(step) {
-		records %>% head(step) %>%
-			summarise(
-				Yes = sum(Target == 'y', na.rm = T),
-				No = sum(Target == 'n', na.rm = T)
-			)
-	}) %>% bind_rows()
-
-	# Plot trends
-	p <- df %>%
-		ggplot(aes(x = steps)) +
-		geom_line(aes(y = Yes, color = 'yes'), size = 1) +
-		geom_line(aes(y = No, color = 'no'), size = 1) +
-		labs(y = 'Records', x = 'Records', color = 'Classification') +
-		theme_minimal()
-
-	# Remove consecutive non changing values to avoid label cluttering
-	df <- mutate(
-		df,
-		across(c(Yes, No), function(x) {
-			c(x[1], sapply(2:(n() - 1), function(i) {
[…]

### 2021-11-23 R/Reporting.R

@@ -589,6 +589,54 @@ format_performance <- function(..., session_names = NULL) {
 
 }
 
+format_var_imp <- function(var_imp, as_data_frame = TRUE) {
+	var_imp <- var_imp %>%
+		transmute(
+			Component = str_extract(Term, '^\\w+(?=__)') %>%
+				factor(c('ABSTR', 'TITLE', 'AUTH', 'KEYS', 'MESH'),
+							 c('Abstract', 'Title', 'Author', 'Keyword', 'Mesh term')),
+			Term = str_replace_all(Term, c('^\\w+__' = '', '\\._\\.' = ' & ', '\\.' = ' | ', '_' = ' ')) %>% str_to_title(),
+			'Inclusion rate' = signif(Value * 10000, 3),
+			IS = signif(Score, 3),
+			RR = signif(exp(estimate), 3) %>% str_remove('\\.?0+$'),
+			`Statistic` = signif(statistic, 3) %>% str_remove('\\.?0+$'),
+		)
+
+	if (!as_data_frame) {
+		var_imp <- 	with(var_imp, glue('{Term} ({Component}): {`Inclusion rate`} ({IS}) [{RR}, {`Statistic`}]'))
+	}
+
+	var_imp
+}
+
+print_table <- function(data, caption = '', allow_math = F) {
+	if (knitr::is_latex_output()) {
+		if (isTRUE(allow_math)) {
+			data <- data %>%
+				mutate(across(where(is.character), ~ str_replace_all(.x, '%', '\\\\%'))) %>%
+				dplyr::rename_with(~ str_replace_all(.x, '%', '\\\\%'))
+		}
+
+		data %>%
+			knitr::kable(format = "latex", booktabs = T,
+									 caption = caption %>% str_squish() %>%
+									 	str_replace_all(c('%' = '\\\\%', '\\*\\*([^\\n]+)\\*\\*' = '\\\\textbf{\\1}')),
+									 escape = !allow_math
+									 #format.args = list(floating = FALSE)
+			) %>%
+			kableExtra::kable_styling(
+				latex_options = c(
+					"striped",
+					if (ncol(data) > 5) "scale_down" else NULL,
+					"hold_position"
+				)
+			)
+	} else {
+		knitr::kable(data, caption = caption)
+	}
+
+}
+
 plot_predictive_densities <- function(session_name,
 																			sessions_folder = getOption("baysren.sessions_folder")) {
 
@@ -671,50 +719,68 @@ plot_predictive_densities <- function(session_name,
 		}
 }
 
[…]

### 2021-12-07 R/Reporting.R
feat: allow passing arguments to kable

@@ -576,7 +576,7 @@ format_performance <- function(..., session_names = NULL) {
 				'Observed positive matches (% over total records)' = glue("{obs_positives} ({percent(obs_positives/total_records)})"),
 				'Predicted positive matches [trunc. 90% PrI]' = pred_positives %>% format_interval(),
 				'Expected sensitivity [trunc. 90% PrI]' = sensitivity %>% format_interval(percent = TRUE),
-				'Simple Model $R^2$ [90% PrI]' = mod_r2 %>% format_interval(percent = TRUE)
+				'Simple Model $R^2$ [90% CrI]' = mod_r2 %>% format_interval(percent = TRUE)
 			) %>%
 				mutate_all(as.character) %>%
 				tidyr::pivot_longer(everything(), names_to = 'Indicator', values_to = session_names[i]) %>%
@@ -609,7 +609,7 @@ format_var_imp <- function(var_imp, as_data_frame = TRUE) {
 	var_imp
 }
 
-print_table <- function(data, caption = '', allow_math = F) {
+print_table <- function(data, caption = '', allow_math = F, ...) {
 	if (knitr::is_latex_output()) {
 		if (isTRUE(allow_math)) {
 			data <- data %>%
@@ -621,7 +621,8 @@ print_table <- function(data, caption = '', allow_math = F) {
 			knitr::kable(format = "latex", booktabs = T,
 									 caption = caption %>% str_squish() %>%
 									 	str_replace_all(c('%' = '\\\\%', '\\*\\*([^\\n]+)\\*\\*' = '\\\\textbf{\\1}')),
-									 escape = !allow_math
+									 escape = !allow_math,
+									 ...
 									 #format.args = list(floating = FALSE)
 			) %>%
 			kableExtra::kable_styling(
@@ -632,7 +633,7 @@ print_table <- function(data, caption = '', allow_math = F) {
 				)
 			)
 	} else {
-		knitr::kable(data, caption = caption)
+		knitr::kable(data, caption = caption, ...)
 	}
 
 }

### 2021-12-07 R/Setup.R
feat: added missing required package

@@ -43,7 +43,7 @@ pkg.require(
 											 "bakaburg1/tidytrees"),
 	only_install = c('purrr', 'openxlsx', 'tictoc', 'tidyr', 'arm', 'english',
 									 'parallel', 'jsonlite', 'rentrez', 'wosr', 'brms', 'ggridges',
-									 'knitr', 'kableExtra', 'extraDistr')
+									 'knitr', 'kableExtra', 'extraDistr', 'broom')
 )
 
 

### 2021-12-07 Manuscript/Manuscript_Discussion.Rmd
including Tjibbe's review

@@
 We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
-This framework joins standard approaches and uses ad-hoc solutions to deal with common SRA issues.\
+This framework joins standard approaches and uses ad-hoc solutions to deal with common SRA issues.
 By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
-Our tool consists of four main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) a Bayesian active machine learning-based citation classifier, and 4) a data-driven search query generation algorithm.\
+The framework consists of four main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) a Bayesian active machine learning-based citation classifier, and 4) a data-driven search query generation algorithm.\
 
@@
 in our results, 18.7% of the positive matches found were unique for one of the different data sources, and no positive record was present in all of them (data not shown).\
-The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the online database in terms of traffic and download quota.\
+The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the queried databases in terms of traffic and download quota.
 The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
@@
 The parameters our algorithm needs are instead quite general and non task-specific, like the PPD intervals based on which the uncertainty zone is built ,and the maximum number of iterations with no positive matches after which a session is concluded;
-the hyperparamer evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to preform well on most datasets.\
+the hyperparameter evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to preform well on most datasets.\
 Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\
@@
 
-The field of literature review automatisation is mature and ripe with innovation, and we expect an increasing use of such technologies to confront the ever-faster production of scientific literature.
+The field of literature review automation is maturing rapidly, and we expect an increasing use of such technologies to manage the ever-faster rate of scientific production.
 We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.\
-We tried to contribute to the field with an innovative methodology and tool that provides excellent performance and easy integration with existing systematic review pipelines.
-The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of solutions we developed to solve various SRA issues and that can be used to improve existing solutions.
+We contribute to this field with an innovative framework that provide excellent performance and easy integration with existing systematic review pipelines.
+The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of methodologies we developed to solve various SRA issues and that can be used to improve already existing solutions.

### 2021-12-07 Manuscript/Manuscript_Introduction.Rmd
update
including Tjibbe's review

@@
 
-## Introduction
+# Introduction
 
 Scientific production has experienced continuous exponential growth in the last decades [@larsen2010rate; @bornmann2015growth].
-This is especially true for biomedical research, a trend further increased by the COVID19 pandemic, thanks to decreased journals' processing time and the diffusion of preprint databases' usage [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].
+This is especially true for biomedical research, a trend further increased by the COVID-19 pandemic, thanks to faster article' processing time by publishers and the diffusion of preprint databases' usage [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].
 Consequently, it gets harder for researchers and practitioners to stay up-to-date on the latest findings in their field.
@@
 Through the application of natural language processing (NLP), it is possible to transform free text into quantitative features, with various levels of abstraction and generalisation [@ananiadou2006text; @cohen2008getting];
-with machine learning, such text-derived data can be used to map and reproduce human judgment, automating the citation screening [@ikonomakis2005text].
-One of the most successful approaches to text screening is active machine learning:
-researchers review the predictions made by the learning algorithm, focusing on the most uncertain predictions ("uncertainty" based active machine learning) or on those giving a document a higher probability of being relevant ("certainty" based active ML) [@miwa2014reducing].\
-The automatisation of systematic reviews has been ripe with improvements in the last years, and it is possible to foresee that such techniques will become a standard approach [@beller2018making].
-See @ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating for in-depth evaluations of research in this field.
-Many of these studies have generated a set of user-friendly commercial and free-to-use tools [see @marshall2015systematic, table 1].
-Despite the significant advances, each method has various shortcomings, both in usability and efficiency [@o2015using].
-We tried to address some of these limitations by creating an integrated framework that tries to simplify systematic reviews in innovative ways:
-we provide solutions for automatic citation collection and management from multiple online sources and a Bayesian, active machine learning-based tool to support humans in the screening task, exponentially reducing the number of records to review.
-In particular, we exploit the characteristics of Bayesian analysis to overcome the shortcoming of both "certainty" and "uncertainty" based active learning and the difficulties in defining stopping rules [@miwa2014reducing].
-Finally, we propose an experimental method to semi-automatically generate efficient search queries given an already labelled set of publications.\
+with machine learning, such text-derived data can be used to map and reproduce human judgment, automating the citation screening [@ikonomakis2005text].\
+The automation of systematic reviews has been ripe with improvements in the last years [@ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating], and it is possible to foresee that it is going to become the standard approach in the field [@beller2018making], with many solutions already being turned into commercial and free-to-use tools [see @marshall2015systematic, table 1].\
+In this manuscript we present an open source, production-ready framework which further contributes to the state-of-the-art in systematic review automation (SRA) and helpers (SRH) tools.
+We improve the "retrieval phase" by providing a unified framework for the automatic collection and management of scientific literature from multiple online sources.
+For the citation screening (appraisal) phase, we built an active machine learning-based [@settles2009active, @miwa2014reducing; @miwa2014reducing] protocol, which exploits a Bayesian framework to efficiently identify potentially relevant documents that require human review while automatically screening-out the large majority of clearly non-relevant ones;
+the algorithm then uses human reviews to iteratively increase classification accuracy.
+Finally, we included a tool to generate new search queries given an already labelled citation data set, in order to identify relevant research possibly missed by human-made queries.\
 We tested the framework in the retrieval and appraisal phases of an example topic of interest for our group:
-the evaluation of the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms.
-The actual protocol of this systematic review is published in [@newis].\
+the evaluation of the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms;
+the protocol is published in [@newis].\
 We give an overview of the framework in the Methods section;
-in the Result section, we show the framework outputs and performance once applied to the example topic; in the Discussion,
-we lay out the methodological justification behind the different components and features of the framework.
+in the Result section, we show the framework outputs and performance once applied to the example topic;
+in the Discussion, we lay out the methodological justification behind the different components and features of the framework.

### 2021-12-07 Manuscript/Manuscript_Methods.Rmd
including Tjibbe's review

@@
 record acquisition and classification.
-The framework comprises several modules that communicate through intermediate outputs stored in standard formats, which make it possible for users to extend the framework or easily integrate it with other tools in their pipeline.
+The code used to generate the results in the manuscript is available at X while an update version of the framework is distributed as an R package at Y.
+The framework includes several modules that communicate through intermediate outputs stored in standard formats, which make it possible for users to extend the framework or easily integrate it with other tools in their pipeline.
 See Supplemental Material S1 for an in-depth description of the framework and how to use it.\
-The tasks carried out by the framework are grouped into "sessions", i.e., a set of actions that starts from a search query to obtain a set of scientific citation data (records), which are then labelled as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest (Fig.
+The tasks carried out by the framework are grouped into "sessions", which comprise obtaining scientific citation data (records) using a search query and then labelling them as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest with the help of a machine learning engine (Fig.
 1).
-The framework can generate a new query from this labelled set and perform a new session to find records possibly missed by the first query.\
-The researcher initiates the process with a starting query derived by domain knowledge from which she expects a high relevant/non-relevant record ratio.\
-Follows a description of the framework's components.\
+The initial search query should be built using domain knowledge, trying to achieve a high relevant/non-relevant record ratio.\
+The framework can then generate a new data-driven query from this labelled set to perform a new session to find records possibly missed by the first query.\
 
@@
 It is also possible to download and import records in the framework manually;
-this is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/search/form.uri?display=basic#basic>) and EMBASE databases (<https://www.embase.com/#advancedSearch/default>), for which a comprehensive API interface was not easy to build.
+this is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/>) and EMBASE databases (<https://www.embase.com/>), for which a comprehensive API interface was not easy to build.
 An extra manual search was necessary also for Pubmed, since the API and the web interface have different rule expansion algorithms and return slightly different results [@pubmedUpdate].
@@
 
-The collected citation data have a number of fields characterizing a scientific publication.
+The collected citation data have a number of fields characterising a scientific publication.
 The framework models the relevance of a record based on the following fields:
@@
 
-To assign the labels, we employed an "active learning" [@settles2009active, @miwa2014reducing] approach, where a human reviews a specific subset of predictions made from the machine, which is then retrained on the manually reviewed dataset.
+To assign the labels, we employed an "active learning" [@settles2009active, @miwa2014reducing] approach, where a human reviews a specific subset of predictions made from the machine, which is then retrained on the manually reviewed data set.
 This process proceeds iteratively, decreasing prediction uncertainty.\
@@
 
-## Relevant terms' extraction
+## Relevant term extraction
 
@@
 
-Since the algorithm is data-driven, it creates queries that effectively select positive records from the input dataset but may be not specific enough once applied to actual research databases.
+Since the algorithm is data-driven, it creates queries that effectively select positive records from the input data set but may be not specific enough once applied to actual research databases.
 Therefore we appended an extra subquery in $AND$, which specifies the general topics of our search and delimitates the search domain.\
@@
 Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing plausible worst-case scenarios.\
-The surrogate model is then used to generate the predictive cumulative distribution of the number of missed positive records in the whole dataset.
-This distribution allows estimating the expected total posterior "Sensitivity" and the "Work saved over random" (WSoR) of the classification model in the full (unreviewed) dataset.
-The WSoR is one minus the number of records to manually label at random to find the same number of positives; this last quantity is estimated through a negative hypergeometric distribution [@chae1993presenting].\
-For the number of predicted positive records, the sensitivity and the WSoR, we reported the "truncated 90% PrI" [trunc.
+The surrogate model is then used to generate the predictive cumulative distribution of the number of total positive records in the whole data set.
+This distribution allows estimating the expected total posterior "Sensitivity" and "Efficiency" of the classification model in the full (unreviewed) data set.
+Efficiency is summarised by the "Work saved over random" (WSoR) statistic:
+one minus the ratio between the number of record manually reviewed and those that would be required to find the same number of positives if classification was performed choosing records randomly;
+this last quantity is estimated through a negative hypergeometric distribution [@chae1993presenting] over the predicted amount of positive records.\
+For the number of predicted positive records, the sensitivity and the efficiency, we reported the "truncated 90% PrI" [trunc.
 90% PrI], which is the uncertainty interval bounded at the number of observed total positive records (i.e., there cannot be less predicted positive records than observed).
@@
 
-To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled "validation set" made of the first 1200 records from the first session dataset.
-The framework tested each hyperparameter combination until four CR iterations with no positive records were returned or the whole dataset got labelled.\
+To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled "validation set" made of the first 1200 records from the first session data set.
+The framework tested each hyperparameter combination until four CR iterations with no positive records were returned or the whole data set got labelled.\
 For each combination, a performance score was computed as the product of "Efficiency" (1 minus the ratio of records that required review over the total) and "Sensitivity" (number of positive records found over the total of positives).

### 2021-12-07 Manuscript/Manuscript_Results.Rmd
update
including Tjibbe's review

@@
   pdf_document:
+    keep_tex: true
     includes:
@@
 
-The input search query for the first session was:\
+The initial search query for the example topic was:\
 
@@
 There were various degrees of overlapping between sources, with the `r percent(1 - source_distr[1])` of records being present in more than one database and EMBASE and IEEE being the databases with the higher uniqueness ratios.
-The final dataset was composed by `r source_summary$Total$Records` unique records.\
-The first `r num_first_labeling` records were manually labeled.
+The final data set was composed by `r source_summary$Total$Records` unique records.\
+The first `r num_first_labeling` records (based on "simple query ordering") were manually labeled.
 Of these `r sprintf('%d (%s)', num_first_positives, percent(num_first_positives/num_first_labeling))` were labeled as positive, and `r sprintf('%d (%s)', num_first_negatives, percent(num_first_negatives/num_first_labeling))` as negative.
@@
 For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total.
-SAll session shows records after joining and deduplication of the Session 1 and Session 2 dataset.")`
+All session shows records after joining and deduplication of the Session 1 and Session 2 data set.", label = "Table 1")`
 
@@
 The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1.
-In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.")`
+In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.", label = "Table 2")`
 
 By evaluating how often a term was used by the classification model, it is possible to define their relevance in labeling the records (see Methods).
-Here follows the 15 most relevant terms by inclusion rate over 10,000 posterior tree inclusions, described as:
+Here follows the 15 most relevant terms by inclusion rate over 10,000 posterior tree, described as:
 Term (citation part): Inclusion Rate (Inclusion Stability) [linear Relative Risk, Statistic].
@@
 The "&" indicates nc-ngrams, i.e., terms strongly co-occurrent in the documents.\
-The engine was able to pick up the central concept of the research, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) or the region of interest ("Orange County") of another research group active on the topic of healthcare asociated pathogen spreading over hospital networks.
+The engine was able to pick up the central concept of the research, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) as well as the region of interest ("Orange County") of another research group active on the topic of healthcare asociated pathogen spreading over hospital networks.
 It is interesting to see that some terms were considered highly relevant for the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
@@
 
-<!-- develop more in the methods, the data is not a random sample and it's ordered so performance evaluation needs to take this into account.
-also note that hyperparameter selection is necessary since even if bayesian methods are robust, the other parameters outside it are not-->
-
 As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a validation set of 1200 completely manually labelled records.
@@
 The table reports for each session, the number of reviewed records and the percentage over the total.
-Also, the posterior expected number of positive records, "Sensitivity" and "Work saved over random" (WSoR) are reported, with their 90% PrI truncated to a number of positive matches equal to the observed one.
+Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90% PrI truncated to the observed realization in the dataset [trunc.
+PrI] (see.
+methods).
 Finally the median Bayesian $R^2$ [90% CrI] of the logistic models is reported.
-[PrI] represents the 90% Predictive Interval while [trunc.
-PrI] indicate the residual PrI truncated at the observed realization (see.
-methods).')`
+PrI: Predictive Intervals; CrI: Credibility Intervals', allow_math = TRUE, label = "Table 3")`
 
-```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="**Figure 2**.
+```{r performance plot, cache = FALSE, fig.width=6, fig.height=2.5, fig.cap="**Figure 2**.
 Observed cumulative number of positive matches (red dots) sorted by simple query ordering.

### 2021-12-08 Manuscript/Manuscript.tex
add line numbers

@@
 \usepackage{microtype}      % microtypography
-\usepackage{lipsum}
 \usepackage{graphicx}
@@
 \usepackage{amsmath}
+\usepackage{lineno}
+\linenumbers
 \captionsetup[table]{labelformat=empty}
@@
 is especially true for biomedical research, a trend further increased by
-the COVID19 pandemic, thanks to decreased journals' processing time and
-the diffusion of preprint databases' usage (Aviv-Reuven and Rosenfeld
-2021; Horbach 2020; Hoy 2020). Consequently, it gets harder for
-researchers and practitioners to stay up-to-date on the latest findings
-in their field. Secondary research is of paramount relevance in this
-scenario, providing valuable summaries of the latest research results,
-but is getting ever more demanding in terms of time and human resources
-(Allen and Olkin 1999; Borah et al. 2017; A. M. Cohen et al. 2010;
-Bastian, Glasziou, and Chalmers 2010).\\
+the COVID-19 pandemic, thanks to faster article' processing time by
+publishers and the diffusion of preprint databases' usage (Aviv-Reuven
+and Rosenfeld 2021; Horbach 2020; Hoy 2020). Consequently, it gets
+harder for researchers and practitioners to stay up-to-date on the
+latest findings in their field. Secondary research is of paramount
+relevance in this scenario, providing valuable summaries of the latest
+research results, but is getting ever more demanding in terms of time
+and human resources (Allen and Olkin 1999; Borah et al. 2017; A. M.
+Cohen et al. 2010; Bastian, Glasziou, and Chalmers 2010).\\
 The article collection and screening phases of a systematic review are
@@
 and reproduce human judgment, automating the citation screening
-(Ikonomakis, Kotsiantis, and Tampakas 2005). One of the most successful
-approaches to text screening is active machine learning: researchers
-review the predictions made by the learning algorithm, focusing on the
-most uncertain predictions (``uncertainty'' based active machine
-learning) or on those giving a document a higher probability of being
-relevant (``certainty'' based active ML) (Miwa et al. 2014).\\
-The automatisation of systematic reviews has been ripe with improvements
-in the last years, and it is possible to foresee that such techniques
-will become a standard approach (E. Beller et al. 2018). See Ananiadou
-et al. (2009); O'Mara-Eves et al. (2015); Tsafnat et al. (2013);
-Jonnalagadda, Goyal, and Huffman (2015) for in-depth evaluations of
-research in this field. Many of these studies have generated a set of
-user-friendly commercial and free-to-use tools (see Marshall and Wallace
-2019, table 1). Despite the significant advances, each method has
-various shortcomings, both in usability and efficiency (O'Mara-Eves et
-al. 2015). We tried to address some of these limitations by creating an
-integrated framework that tries to simplify systematic reviews in
-innovative ways: we provide solutions for automatic citation collection
-and management from multiple online sources and a Bayesian, active
-machine learning-based tool to support humans in the screening task,
-exponentially reducing the number of records to review. In particular,
-we exploit the characteristics of Bayesian analysis to overcome the
-shortcoming of both ``certainty'' and ``uncertainty'' based active
-learning and the difficulties in defining stopping rules (Miwa et al.
-2014). Finally, we propose an experimental method to semi-automatically
-generate efficient search queries given an already labelled set of
-publications.\\
+(Ikonomakis, Kotsiantis, and Tampakas 2005).\\
+The automation of systematic reviews has been ripe with improvements in
+the last years (Ananiadou et al. 2009; O'Mara-Eves et al. 2015; Tsafnat
+et al. 2013; Jonnalagadda, Goyal, and Huffman 2015), and it is possible
+to foresee that it is going to become the standard approach in the field
+(E. Beller et al. 2018), with many solutions already being turned into
+commercial and free-to-use tools (see Marshall and Wallace 2019, table
+1).\\
+In this manuscript we present an open source, production-ready framework
+which further contributes to the state-of-the-art in systematic review
+automation (SRA) and helpers (SRH) tools. We improve the ``retrieval
+phase'' by providing a unified framework for the automatic collection
+and management of scientific literature from multiple online sources.
+For the citation screening (appraisal) phase, we built an active machine
+learning-based Miwa et al. (2014) protocol, which exploits a Bayesian
+framework to efficiently identify potentially relevant documents that
+require human review while automatically screening-out the large
+majority of clearly non-relevant ones; the algorithm then uses human
+reviews to iteratively increase classification accuracy. Finally, we
+included a tool to generate new search queries given an already labelled
+citation data set, in order to identify relevant research possibly
+missed by human-made queries.\\
 We tested the framework in the retrieval and appraisal phases of an
@@
 their impact on the diffusion of healthcare-associated pathogenic
-microorganisms. The actual protocol of this systematic review is
-published in (Sadaghiani et al. 2020).\\
+microorganisms; the protocol is published in (Sadaghiani et al. 2020).\\
 We give an overview of the framework in the Methods section; in the
@@
 We built an R (R Core Team 2020) based framework to simplify two aspects
-of systematic reviews: record acquisition and classification. The
-framework comprises several modules that communicate through
+of systematic reviews: record acquisition and classification. The code
+used to generate the results in the manuscript is available at X while
+an update version of the framework is distributed as an R package at Y.
+The framework includes several modules that communicate through
 intermediate outputs stored in standard formats, which make it possible
@@
 The tasks carried out by the framework are grouped into ``sessions'',
-i.e., a set of actions that starts from a search query to obtain a set
-of scientific citation data (records), which are then labelled as
-relevant (``positive'' in the rest of the text) or not (``negative'')
-for the topic of interest (Fig. 1). The framework can generate a new
-query from this labelled set and perform a new session to find records
-possibly missed by the first query.\\
-The researcher initiates the process with a starting query derived by
-domain knowledge from which she expects a high relevant/non-relevant
-record ratio.\\
-Follows a description of the framework's components.\\
+which comprise obtaining scientific citation data (records) using a
+search query and then labelling them as relevant (``positive'' in the
+rest of the text) or not (``negative'') for the topic of interest with
+the help of a machine learning engine (Fig. 1). The initial search query
+should be built using domain knowledge, trying to achieve a high
+relevant/non-relevant record ratio.\\
+The framework can then generate a new data-driven query from this
+labelled set to perform a new session to find records possibly missed by
+the first query.\\
 
@@
 framework manually; this is particularly useful to acquire records from
-the SCOPUS
-(\url{https://www.scopus.com/search/form.uri?display=basic\#basic}) and
-EMBASE databases
-(\url{https://www.embase.com/\#advancedSearch/default}), for which a
-comprehensive API interface was not easy to build. An extra manual
-search was necessary also for Pubmed, since the API and the web
-interface have different rule expansion algorithms and return slightly
-different results ({`NCBI Insights : Updated Pubmed e-Utilities Coming
-in April 2022!'} n.d.). A short guide on how to set up the framework for
-each supported database is available in Supplemental Material S3.\\
+the SCOPUS (\url{https://www.scopus.com/}) and EMBASE databases
+(\url{https://www.embase.com/}), for which a comprehensive API interface
+was not easy to build. An extra manual search was necessary also for
+Pubmed, since the API and the web interface have different rule
+expansion algorithms and return slightly different results ({`NCBI
+Insights : Updated Pubmed e-Utilities Coming in April 2022!'}, n.d.). A
+short guide on how to set up the framework for each supported database
+is available in Supplemental Material S3.\\
 The acquired records are merged into a single database, resolving
@@
 
-The collected citation data have a number of fields characterizing a
+The collected citation data have a number of fields characterising a
 scientific publication. The framework models the relevance of a record
@@
 terms (Lipscomb 2000). A series of Natural Language Processing (NLP)
-techniques (Baeza-Yates, Ribeiro-Neto, and others 1999; Marshall and
-Wallace 2019; Ananiadou and McNaught 2006) are employed to transform the
-textual information in these fields into features for machine learning
-through a bag-of-words approach (Marshall and Wallace 2019). The
-processing of free text fields (title, abstract) includes: tokenization
-(i.e., extracting the terms), common stopwords (i.e., sentence
-components bringing no meaning) removal, part-of-speech filtering (only
-nouns, adjectives, verbs and untagged terms are retained), and
-lemmatization of the terms (i.e., reduction to their base grammar form).
-Text processing for authors, keywords and MESH terms identifies logical
-units (e.g., author's full names, composite keywords) and extracts
-them.\\
+techniques (Baeza-Yates, Ribeiro-Neto, et al. 1999; Marshall and Wallace
+2019; Ananiadou and McNaught 2006) are employed to transform the textual
+information in these fields into features for machine learning through a
+bag-of-words approach (Marshall and Wallace 2019). The processing of
+free text fields (title, abstract) includes: tokenization (i.e.,
+extracting the terms), common stopwords (i.e., sentence components
+bringing no meaning) removal, part-of-speech filtering (only nouns,
+adjectives, verbs and untagged terms are retained), and lemmatization of
+the terms (i.e., reduction to their base grammar form). Text processing
+for authors, keywords and MESH terms identifies logical units (e.g.,
+author's full names, composite keywords) and extracts them.\\
 Terms appearing in less than 5\% of the labelled documents are removed
@@
 made from the machine, which is then retrained on the manually reviewed
-dataset. This process proceeds iteratively, decreasing prediction
+data set. This process proceeds iteratively, decreasing prediction
 uncertainty.\\
@@
 
-\hypertarget{relevant-terms-extraction}{%
-\subsection{Relevant terms'
-extraction}\label{relevant-terms-extraction}}
+\hypertarget{relevant-term-extraction}{%
+\subsection{Relevant term extraction}\label{relevant-term-extraction}}
 
@@
 Since the algorithm is data-driven, it creates queries that effectively
-select positive records from the input dataset but may be not specific
+select positive records from the input data set but may be not specific
 enough once applied to actual research databases. Therefore we appended
@@
 The surrogate model is then used to generate the predictive cumulative
-distribution of the number of missed positive records in the whole
-dataset. This distribution allows estimating the expected total
-posterior ``Sensitivity'' and the ``Work saved over random'' (WSoR) of
-the classification model in the full (unreviewed) dataset. The WSoR is
-one minus the number of records to manually label at random to find the
-same number of positives; this last quantity is estimated through a
-negative hypergeometric distribution (Chae 1993).\\
+distribution of the number of total positive records in the whole data
+set. This distribution allows estimating the expected total posterior
+``Sensitivity'' and ``Efficiency'' of the classification model in the
+full (unreviewed) data set. Efficiency is summarised by the ``Work saved
+over random'' (WSoR) statistic: one minus the ratio between the number
+of record manually reviewed and those that would be required to find the
+same number of positives if classification was performed choosing
+records randomly; this last quantity is estimated through a negative
+hypergeometric distribution (Chae 1993) over the predicted amount of
+positive records.\\
 For the number of predicted positive records, the sensitivity and the
-WSoR, we reported the ``truncated 90\% PrI'' {[}trunc. 90\% PrI{]},
-which is the uncertainty interval bounded at the number of observed
-total positive records (i.e., there cannot be less predicted positive
-records than observed).
+efficiency, we reported the ``truncated 90\% PrI'' {[}trunc. 90\%
+PrI{]}, which is the uncertainty interval bounded at the number of
+observed total positive records (i.e., there cannot be less predicted
+positive records than observed).
 
@@
 prelabelled ``validation set'' made of the first 1200 records from the
-first session dataset. The framework tested each hyperparameter
+first session data set. The framework tested each hyperparameter
 combination until four CR iterations with no positive records were
-returned or the whole dataset got labelled.\\
+returned or the whole data set got labelled.\\
 For each combination, a performance score was computed as the product of
@@
 
-The input search query for the first session was:\\
+The initial search query for the example topic was:\\
 
@@
 IEEE being the databases with the higher uniqueness ratios. The final
-dataset was composed by 17755 unique records.\\
-The first 250 records were manually labeled. Of these 43 (17.2\%) were
-labeled as positive, and 207 (82.8\%) as negative.
+data set was composed by 17755 unique records.\\
+The first 250 records (based on ``simple query ordering'') were manually
+labeled. Of these 43 (17.2\%) were labeled as positive, and 207 (82.8\%)
+as negative.
 
@@
 
-\caption{\label{tab:session 1}\textbf{Table 1}.
+\caption{\label{tab:Table 1}\textbf{Table 1}.
 Distribution of retrieved records by source and session.
 For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total.
-All session shows records after joining and deduplication of the Session 1 and Session 2 dataset.}
+All session shows records after joining and deduplication of the Session 1 and Session 2 data set.}
 \centering
@@
 
-\caption{\label{tab:session 1}\textbf{Table 2}.
+\caption{\label{tab:Table 2}\textbf{Table 2}.
 Results of the automatic classifaction and manual review rounds.
@@
 Methods). Here follows the 15 most relevant terms by inclusion rate over
-10,000 posterior tree inclusions, described as: Term (citation part):
-Inclusion Rate (Inclusion Stability) {[}linear Relative Risk,
-Statistic{]}.
+10,000 posterior tree, described as: Term (citation part): Inclusion
+Rate (Inclusion Stability) {[}linear Relative Risk, Statistic{]}.
 
@@
 ``facility''ies that facilitates the ``spread'' of infections, and even
-one of the authors of this study (Donker T.) or the region of interest
-(``Orange County'') of another research group active on the topic of
-healthcare asociated pathogen spreading over hospital networks. It is
-interesting to see that some terms were considered highly relevant for
-the BART models (e.g., ``Worker'' in 6th position out of more than 3800
-terms considered) although in a simpler linear model their effect would
-be hardly significant (statistic: -1.21 s.e.); these are terms which are
-relevant only together with other terms but not by themselves,
+one of the authors of this study (Donker T.) as well as the region of
+interest (``Orange County'') of another research group active on the
+topic of healthcare asociated pathogen spreading over hospital networks.
+It is interesting to see that some terms were considered highly relevant
+for the BART models (e.g., ``Worker'' in 6th position out of more than
+3800 terms considered) although in a simpler linear model their effect
+would be hardly significant (statistic: -1.21 s.e.); these are terms
+which are relevant only together with other terms but not by themselves,
 highlighting the extra predictive power brought by a non-linear model
@@
 
-\caption{\label{tab:performance}\textbf{Table 3}.
+\caption{\label{tab:Table 3}\textbf{Table 3}.
 Estimated performance summary.
 The table reports for each session, the number of reviewed records and the percentage over the total.
-Also, the posterior expected number of positive records, "Sensitivity" and "Work saved over random" (WSoR) are reported, with their 90\% PrI truncated to a number of positive matches equal to the observed one.
+Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90\% PrI truncated to the observed realization in the dataset [trunc.
+PrI] (see.
+methods).
 Finally the median Bayesian $R^2$ [90\% CrI] of the logistic models is reported.
-[PrI] represents the 90\% Predictive Interval while [trunc.
-PrI] indicate the residual PrI truncated at the observed realization (see.
-methods).}
+PrI: Predictive Intervals; CrI: Credibility Intervals}
 \centering
@@
 Expected sensitivity [trunc. 90\% PrI] & 100\% [93.5\%, 100\%] & 97.3\% [73.8\%, 100\%]\\
-\cellcolor{gray!6}{Simple Model $R^2$ [90\% PrI]} & \cellcolor{gray!6}{98.1\% [97.4\%, 98.3\%]} & \cellcolor{gray!6}{98.2\% [97.6\%, 98.3\%]}\\
+\cellcolor{gray!6}{Simple Model $R^2$ [90\% CrI]} & \cellcolor{gray!6}{98.1\% [97.4\%, 98.3\%]} & \cellcolor{gray!6}{98.2\% [97.6\%, 98.3\%]}\\
 \bottomrule
@@
 et al. 2009; O'Mara-Eves et al. 2015). This framework joins standard
-approaches and uses ad-hoc solutions to deal with common SRA issues.\\
-By freely sharing the tool as an open-source R package and by following
-a modular design, we tried to adopt some of the so-called Vienna
+approaches and uses ad-hoc solutions to deal with common SRA issues. By
+freely sharing the tool as an open-source R package and by following a
+modular design, we tried to adopt some of the so-called Vienna
 Principles advocated by the International Collaboration for the
 Automation of Systematic Reviews (ICASR) (E. Beller et al. 2018).\\
-Our tool consists of four main components: 1) an integrated query-based
-citation search and management engine, 2) a text-to-feature extractor
-module, 3) a Bayesian active machine learning-based citation classifier,
-and 4) a data-driven search query generation algorithm.\\
+The framework consists of four main components: 1) an integrated
+query-based citation search and management engine, 2) a text-to-feature
+extractor module, 3) a Bayesian active machine learning-based citation
+classifier, and 4) a data-driven search query generation algorithm.\\
 
@@
 sources, and no positive record was present in all of them (data not
-shown).~ The online search algorithms are efficient enough to manage
-tens of thousands of search results, using various expedients to
-overcome the limitations of the online database in terms of traffic and
-download quota.\\
-The results are then automatically organized, deduplicated and arranged
-by ``simple query ordering'' in a uniform corpus. The preliminary
-ordering allow to increase the positivity rate in the initial training
-set (Wallace, Small, et al. 2010).
+shown).\\
+The online search algorithms are efficient enough to manage tens of
+thousands of search results, using various expedients to overcome the
+limitations of the queried databases in terms of traffic and download
+quota. The results are then automatically organized, deduplicated and
+arranged by ``simple query ordering'' in a uniform corpus. The
+preliminary ordering allow to increase the positivity rate in the
+initial training set (Wallace, Small, et al. 2010).
 
@@
 extreme predictions would have decreased variance but also shifted the
-distribution towards a non-decision zone, increasing bias (Hansen and
-others 2000).\\
+distribution towards a non-decision zone, increasing bias (Hansen et al.
+2000).\\
 Since the number of model replications significantly impacts computation
@@
 iterations with no positive matches after which a session is concluded;
-the hyperparamer evaluation shows that the algorithm is robust against
+the hyperparameter evaluation shows that the algorithm is robust against
 variations in these parameters and we expect the default values to
@@
 We avoided the classic out-of-sample approaches like train-test
-sampling, out-of-bag bootstrapping or cross-validation (Kohavi and
-others 1995; James et al. 2013). Such methods primarily assume that the
-rate of positivity is equal on average in every random subset of the
-data (Tashman 2000); this uniformity is broken by how the initial
-training set and the subsequent reviewed records are selected by the
-query-based ordering and the active learning algorithm, determining a
-lower positivity rate in the unlabelled records (Fig. 2). Also, a
-literature corpus is unique per search query/database combination, and
-therefore any out-of-sample performance estimate is not replicable since
-no new data can be acquired related to the current corpus.\\
+sampling, out-of-bag bootstrapping or cross-validation (Kohavi et al.
+1995; James et al. 2013). Such methods primarily assume that the rate of
+positivity is equal on average in every random subset of the data
+(Tashman 2000); this uniformity is broken by how the initial training
+set and the subsequent reviewed records are selected by the query-based
+ordering and the active learning algorithm, determining a lower
+positivity rate in the unlabelled records (Fig. 2). Also, a literature
+corpus is unique per search query/database combination, and therefore
+any out-of-sample performance estimate is not replicable since no new
+data can be acquired related to the current corpus.\\
 Instead, to estimate overall sensitivity, we employed simple Bayesian
@@
 nuanced text representations. It could be evaluated if feature
-transformations like TF-IDF (Baeza-Yates, Ribeiro-Neto, and others 1999;
+transformations like TF-IDF (Baeza-Yates, Ribeiro-Neto, et al. 1999;
 Ananiadou and McNaught 2006) would be advantageous, even if we
@@
 
-The field of literature review automatisation is mature and ripe with
-innovation, and we expect an increasing use of such technologies to
-confront the ever-faster production of scientific literature. We believe
-it is appreciable that a multiplicity of tools are being made available
-to let researchers and policymakers find the instrument that better fits
-their needs.\\
-We tried to contribute to the field with an innovative methodology and
-tool that provides excellent performance and easy integration with
-existing systematic review pipelines. The value of this work lies not
-only in the framework itself, which we provide as open-source software,
-but in the set of solutions we developed to solve various SRA issues and
-that can be used to improve existing solutions.
+The field of literature review automation is maturing rapidly, and we
+expect an increasing use of such technologies to manage the ever-faster
+rate of scientific production. We believe it is appreciable that a
+multiplicity of tools are being made available to let researchers and
+policymakers find the instrument that better fits their needs.\\
+We contribute to this field with an innovative framework that provide
+excellent performance and easy integration with existing systematic
+review pipelines. The value of this work lies not only in the framework
+itself, which we provide as open-source software, but in the set of
+methodologies we developed to solve various SRA issues and that can be
+used to improve already existing solutions.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-abd2013review}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-abd2013review}{}}%
 Abd Elrahman, Shaza M, and Ajith Abraham. 2013. {`A Review of Class
-Imbalance Problem.'} \emph{Journal of Network and Innovative Computing}
+Imbalance Problem'}. \emph{Journal of Network and Innovative Computing}
 1 (2013): 332--40.
 
-\leavevmode\hypertarget{ref-allen1999estimating}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-allen1999estimating}{}}%
 Allen, I Elaine, and Ingram Olkin. 1999. {`Estimating Time to Conduct a
-Meta-Analysis from Number of Citations Retrieved.'} \emph{Jama} 282 (7):
+Meta-Analysis from Number of Citations Retrieved'}. \emph{Jama} 282 (7):
 634--35.
 
-\leavevmode\hypertarget{ref-ananiadou2006text}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ananiadou2006text}{}}%
 Ananiadou, Sophia, and John McNaught. 2006. \emph{Text Mining for
@@
 
-\leavevmode\hypertarget{ref-ananiadou2009supporting}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ananiadou2009supporting}{}}%
 Ananiadou, Sophia, Brian Rea, Naoaki Okazaki, Rob Procter, and James
-Thomas. 2009. {`Supporting Systematic Reviews Using Text Mining.'}
+Thomas. 2009. {`Supporting Systematic Reviews Using Text Mining'}.
 \emph{Social Science Computer Review} 27 (4): 509--23.
 
-\leavevmode\hypertarget{ref-aviv2021publication}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-aviv2021publication}{}}%
 Aviv-Reuven, Shir, and Ariel Rosenfeld. 2021. {`Publication Patterns'
 Changes Due to the COVID-19 Pandemic: A Longitudinal and Short-Term
-Scientometric Analysis.'} \emph{Scientometrics}, 1--24.
-
-\leavevmode\hypertarget{ref-babar2009systematic}{}%
+Scientometric Analysis'}. \emph{Scientometrics}, 1--24.
+
+\leavevmode\vadjust pre{\hypertarget{ref-babar2009systematic}{}}%
 Babar, Muhammad Ali, and He Zhang. 2009. {`Systematic Literature Reviews
 in Software Engineering: Preliminary Results from Interviews with
-Researchers.'} In \emph{2009 3rd International Symposium on Empirical
+Researchers'}. In \emph{2009 3rd International Symposium on Empirical
 Software Engineering and Measurement}, 346--55. IEEE.
 
-\leavevmode\hypertarget{ref-baeza1999modern}{}%
-Baeza-Yates, Ricardo, Berthier Ribeiro-Neto, and others. 1999.
-\emph{Modern Information Retrieval}. Vol. 463. ACM press New York.
-
-\leavevmode\hypertarget{ref-bajpai2011search}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-baeza1999modern}{}}%
+Baeza-Yates, Ricardo, Berthier Ribeiro-Neto, et al. 1999. \emph{Modern
+Information Retrieval}. Vol. 463. ACM press New York.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bajpai2011search}{}}%
 Bajpai, Akhilesh, Sravanthi Davuluri, Haritha Haridas, Greta Kasliwal, H
 Deepti, KS Sreelakshmi, Darshan Chandrashekar, et al. 2011. {`In Search
-of the Right Literature Search Engine (s).'} \emph{Nature Precedings},
+of the Right Literature Search Engine (s)'}. \emph{Nature Precedings},
 1--1.
 
-\leavevmode\hypertarget{ref-bannach2019machine}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bannach2019machine}{}}%
 Bannach-Brown, Alexandra, Piotr Przybyła, James Thomas, Andrew SC Rice,
@@
 Preclinical Review of Animal Studies and Reducing Human Screening
-Error.'} \emph{Systematic Reviews} 8 (1): 1--12.
-
-\leavevmode\hypertarget{ref-bastian2010seventy}{}%
+Error'}. \emph{Systematic Reviews} 8 (1): 1--12.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bastian2010seventy}{}}%
 Bastian, Hilda, Paul Glasziou, and Iain Chalmers. 2010. {`Seventy-Five
-Trials and Eleven Systematic Reviews a Day: How Will We Ever Keep Up?'}
+Trials and Eleven Systematic Reviews a Day: How Will We Ever Keep Up?'}.
 \emph{PLoS Medicine} 7 (9): e1000326.
 
-\leavevmode\hypertarget{ref-batista2004study}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-batista2004study}{}}%
 Batista, Gustavo EAPA, Ronaldo C Prati, and Maria Carolina Monard. 2004.
 {`A Study of the Behavior of Several Methods for Balancing Machine
-Learning Training Data.'} \emph{ACM SIGKDD Explorations Newsletter} 6
+Learning Training Data'}. \emph{ACM SIGKDD Explorations Newsletter} 6
 (1): 20--29.
 
-\leavevmode\hypertarget{ref-bekhuis2010towards}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bekhuis2010towards}{}}%
 Bekhuis, Tanja, and Dina Demner-Fushman. 2010. {`Towards Automating the
-Initial Screening Phase of a Systematic Review.'} \emph{MEDINFO 2010},
+Initial Screening Phase of a Systematic Review'}. \emph{MEDINFO 2010},
 146--50.
 
-\leavevmode\hypertarget{ref-bekhuis2012screening}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bekhuis2012screening}{}}%
 ---------. 2012. {`Screening Nonrandomized Studies for Medical
-Systematic Reviews: A Comparative Study of Classifiers.'}
+Systematic Reviews: A Comparative Study of Classifiers'}.
 \emph{Artificial Intelligence in Medicine} 55 (3): 197--207.
 
-\leavevmode\hypertarget{ref-beller2013systematic}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-beller2013systematic}{}}%
 Beller, Elaine M, Joyce Kee-Hsin Chen, Una Li-Hsiang Wang, and Paul P
 Glasziou. 2013. {`Are Systematic Reviews up-to-Date at the Time of
-Publication?'} \emph{Systematic Reviews} 2 (1): 1--6.
-
-\leavevmode\hypertarget{ref-beller2018making}{}%
+Publication?'}. \emph{Systematic Reviews} 2 (1): 1--6.
+
+\leavevmode\vadjust pre{\hypertarget{ref-beller2018making}{}}%
 Beller, Elaine, Justin Clark, Guy Tsafnat, Clive Adams, Heinz Diehl,
@@
 Automation of Systematic Reviews: Principles of the International
-Collaboration for the Automation of Systematic Reviews (ICASR).'}
+Collaboration for the Automation of Systematic Reviews (ICASR)'}.
 \emph{Systematic Reviews} 7 (1): 1--7.
 
-\leavevmode\hypertarget{ref-bhatt2020machine}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bhatt2020machine}{}}%
 Bhatt, Umang, McKane Andrus, Adrian Weller, and Alice Xiang. 2020.
-{`Machine Learning Explainability for External Stakeholders.'}
+{`Machine Learning Explainability for External Stakeholders'}.
 \emph{arXiv Preprint arXiv:2007.05408}.
 
-\leavevmode\hypertarget{ref-bibal2021legal}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bibal2021legal}{}}%
 Bibal, Adrien, Michael Lognoul, Alexandre De Streel, and Benoît Frénay.
-2021. {`Legal Requirements on Explainability in Machine Learning.'}
+2021. {`Legal Requirements on Explainability in Machine Learning'}.
 \emph{Artificial Intelligence and Law} 29 (2): 149--69.
 
-\leavevmode\hypertarget{ref-bibal2020impact}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bibal2020impact}{}}%
 Bibal, Adrien, Michael Lognoul, Alexandre de Streel, and Benoît Frénay.
 2020. {`Impact of Legal Requirements on Explainability in Machine
-Learning.'} \emph{arXiv Preprint arXiv:2007.05479}.
-
-\leavevmode\hypertarget{ref-blanco2019machine}{}%
+Learning'}. \emph{arXiv Preprint arXiv:2007.05479}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-blanco2019machine}{}}%
 Blanco-Justicia, Alberto, and Josep Domingo-Ferrer. 2019. {`Machine
-Learning Explainability Through Comprehensible Decision Trees.'} In
+Learning Explainability Through Comprehensible Decision Trees'}. In
 \emph{International Cross-Domain Conference for Machine Learning and
@@
 
-\leavevmode\hypertarget{ref-bollegala2015embedding}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bollegala2015embedding}{}}%
 Bollegala, Danushka, Takanori Maehara, and Ken-ichi Kawarabayashi. 2015.
-{`Embedding Semantic Relations into Word Representations.'} In
+{`Embedding Semantic Relations into Word Representations'}. In
 \emph{Twenty-Fourth International Joint Conference on Artificial
@@
 
-\leavevmode\hypertarget{ref-borah2017analysis}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-borah2017analysis}{}}%
 Borah, Rohit, Andrew W Brown, Patrice L Capers, and Kathryn A Kaiser.
@@
 Reviews of Medical Interventions Using Data from the PROSPERO
-Registry.'} \emph{BMJ Open} 7 (2): e012545.
-
-\leavevmode\hypertarget{ref-bornmann2015growth}{}%
+Registry'}. \emph{BMJ Open} 7 (2): e012545.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bornmann2015growth}{}}%
 Bornmann, Lutz, and Rüdiger Mutz. 2015. {`Growth Rates of Modern
 Science: A Bibliometric Analysis Based on the Number of Publications and
-Cited References.'} \emph{Journal of the Association for Information
+Cited References'}. \emph{Journal of the Association for Information
 Science and Technology} 66 (11): 2215--22.
 
-\leavevmode\hypertarget{ref-breiman1996bagging}{}%
-Breiman, Leo. 1996. {`Bagging Predictors.'} \emph{Machine Learning} 24
+\leavevmode\vadjust pre{\hypertarget{ref-breiman1996bagging}{}}%
+Breiman, Leo. 1996. {`Bagging Predictors'}. \emph{Machine Learning} 24
 (2): 123--40.
 
-\leavevmode\hypertarget{ref-burkart2021survey}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-burkart2021survey}{}}%
 Burkart, Nadia, and Marco F Huber. 2021. {`A Survey on the
-Explainability of Supervised Machine Learning.'} \emph{Journal of
+Explainability of Supervised Machine Learning'}. \emph{Journal of
 Artificial Intelligence Research} 70: 245--317.
 
-\leavevmode\hypertarget{ref-chae1993presenting}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chae1993presenting}{}}%
 Chae, Kyung-Chul. 1993. {`Presenting the Negative Hypergeometric
-Distribution to the Introductory Statistics Courses.'}
+Distribution to the Introductory Statistics Courses'}.
 \emph{International Journal of Mathematical Education in Science and
@@
 
-\leavevmode\hypertarget{ref-chawla2004special}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chawla2004special}{}}%
 Chawla, Nitesh V, Nathalie Japkowicz, and Aleksander Kotcz. 2004.
-{`Special Issue on Learning from Imbalanced Data Sets.'} \emph{ACM
+{`Special Issue on Learning from Imbalanced Data Sets'}. \emph{ACM
 SIGKDD Explorations Newsletter} 6 (1): 1--6.
 
-\leavevmode\hypertarget{ref-chen2018approximate}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chen2018approximate}{}}%
 Chen, Chao, Xiao Lin, and Gabriel Terejanu. 2018. {`An Approximate
-Bayesian Long Short-Term Memory Algorithm for Outlier Detection.'} In
+Bayesian Long Short-Term Memory Algorithm for Outlier Detection'}. In
 \emph{2018 24th International Conference on Pattern Recognition (ICPR)},
@@
 
-\leavevmode\hypertarget{ref-chen2016short}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chen2016short}{}}%
 Chen, Qiuxing, Lixiu Yao, and Jie Yang. 2016. {`Short Text
-Classification Based on LDA Topic Model.'} In \emph{2016 International
+Classification Based on LDA Topic Model'}. In \emph{2016 International
 Conference on Audio, Language and Image Processing (ICALIP)}, 749--53.
@@
 
-\leavevmode\hypertarget{ref-chen2015gaussian}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chen2015gaussian}{}}%
 Chen, Sih-Huei, Yuan-Shan Lee, Tzu-Chiang Tai, and Jia-Ching Wang. 2015.
-{`Gaussian Process Based Text Categorization for Healthy Information.'}
+{`Gaussian Process Based Text Categorization for Healthy Information'}.
 In \emph{2015 International Conference on Orange Technologies (ICOT)},
@@
 
-\leavevmode\hypertarget{ref-cheng2019document}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cheng2019document}{}}%
 Cheng, Y, Z Ye, M Wang, and Q Zhang. 2019. {`Document Classification
 Based on Convolutional Neural Network and Hierarchical Attention
-Network.'} \emph{Neural Network World} 29 (2): 83--98.
-
-\leavevmode\hypertarget{ref-chipman2010bart}{}%
-Chipman, Hugh A, Edward I George, Robert E McCulloch, and others. 2010.
-{`BART: Bayesian Additive Regression Trees.'} \emph{The Annals of
+Network'}. \emph{Neural Network World} 29 (2): 83--98.
+
+\leavevmode\vadjust pre{\hypertarget{ref-chipman2010bart}{}}%
+Chipman, Hugh A, Edward I George, Robert E McCulloch, et al. 2010.
+{`BART: Bayesian Additive Regression Trees'}. \emph{The Annals of
 Applied Statistics} 4 (1): 266--98.
 
-\leavevmode\hypertarget{ref-claesen2015hyperparameter}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-claesen2015hyperparameter}{}}%
 Claesen, Marc, and Bart De Moor. 2015. {`Hyperparameter Search in
-Machine Learning.'} \emph{arXiv Preprint arXiv:1502.02127}.
-
-\leavevmode\hypertarget{ref-cohen2010evidence}{}%
+Machine Learning'}. \emph{arXiv Preprint arXiv:1502.02127}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cohen2010evidence}{}}%
 Cohen, Aaron M, Clive E Adams, John M Davis, Clement Yu, Philip S Yu,
@@
 {`Evidence-Based Medicine, the Essential Role of Systematic Reviews, and
-the Need for Automated Text Mining Tools.'} In \emph{Proceedings of the
+the Need for Automated Text Mining Tools'}. In \emph{Proceedings of the
 1st ACM International Health Informatics Symposium}, 376--80.
 
-\leavevmode\hypertarget{ref-cohen2006reducing}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cohen2006reducing}{}}%
 Cohen, Aaron M, William R Hersh, Kim Peterson, and Po-Yin Yen. 2006.
 {`Reducing Workload in Systematic Review Preparation Using Automated
-Citation Classification.'} \emph{Journal of the American Medical
+Citation Classification'}. \emph{Journal of the American Medical
 Informatics Association} 13 (2): 206--19.
 
-\leavevmode\hypertarget{ref-cohen2008getting}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cohen2008getting}{}}%
 Cohen, K Bretonnel, and Lawrence Hunter. 2008. {`Getting Started in Text
-Mining.'} \emph{PLoS Computational Biology} 4 (1): e20.
-
-\leavevmode\hypertarget{ref-dietterich2000ensemble}{}%
-Dietterich, Thomas G. 2000. {`Ensemble Methods in Machine Learning.'} In
+Mining'}. \emph{PLoS Computational Biology} 4 (1): e20.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dietterich2000ensemble}{}}%
+Dietterich, Thomas G. 2000. {`Ensemble Methods in Machine Learning'}. In
 \emph{International Workshop on Multiple Classifier Systems}, 1--15.
@@
 
-\leavevmode\hypertarget{ref-diez2015diversity}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-diez2015diversity}{}}%
 Díez-Pastor, José F, Juan J Rodríguez, César I García-Osorio, and
 Ludmila I Kuncheva. 2015. {`Diversity Techniques Improve the Performance
-of the Best Imbalance Learning Ensembles.'} \emph{Information Sciences}
+of the Best Imbalance Learning Ensembles'}. \emph{Information Sciences}
 325: 98--117.
 
-\leavevmode\hypertarget{ref-edwards2002identification}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-edwards2002identification}{}}%
 Edwards, Phil, Mike Clarke, Carolyn DiGuiseppi, Sarah Pratap, Ian
@@
 Controlled Trials in Systematic Reviews: Accuracy and Reliability of
-Screening Records.'} \emph{Statistics in Medicine} 21 (11): 1635--40.
-
-\leavevmode\hypertarget{ref-eppstein2010listing}{}%
+Screening Records'}. \emph{Statistics in Medicine} 21 (11): 1635--40.
+
+\leavevmode\vadjust pre{\hypertarget{ref-eppstein2010listing}{}}%
 Eppstein, David, Maarten Löffler, and Darren Strash. 2010. {`Listing All
-Maximal Cliques in Sparse Graphs in Near-Optimal Time.'} In
+Maximal Cliques in Sparse Graphs in Near-Optimal Time'}. In
 \emph{International Symposium on Algorithms and Computation}, 403--14.
@@
 
-\leavevmode\hypertarget{ref-farkas1995document}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-farkas1995document}{}}%
 Farkas, Jennifer. 1995. {`Document Classification and Recurrent Neural
-Networks.'} In \emph{Proceedings of the 1995 Conference of the Centre
+Networks'}. In \emph{Proceedings of the 1995 Conference of the Centre
 for Advanced Studies on Collaborative Research}, 21.
 
-\leavevmode\hypertarget{ref-frunza2010building}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-frunza2010building}{}}%
 Frunza, Oana, Diana Inkpen, and Stan Matwin. 2010. {`Building Systematic
-Reviews Using Automatic Text Classification Techniques.'} In
+Reviews Using Automatic Text Classification Techniques'}. In
 \emph{Coling 2010: Posters}, 303--11.
 
-\leavevmode\hypertarget{ref-galar2011review}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-galar2011review}{}}%
 Galar, Mikel, Alberto Fernandez, Edurne Barrenechea, Humberto Bustince,
 and Francisco Herrera. 2011. {`A Review on Ensembles for the Class
-Imbalance Problem: Bagging-, Boosting-, and Hybrid-Based Approaches.'}
+Imbalance Problem: Bagging-, Boosting-, and Hybrid-Based Approaches'}.
 \emph{IEEE Transactions on Systems, Man, and Cybernetics, Part C
@@
 
-\leavevmode\hypertarget{ref-gelman2019r}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gelman2019r}{}}%
 Gelman, Andrew, Ben Goodrich, Jonah Gabry, and Aki Vehtari. 2019.
-{`R-Squared for Bayesian Regression Models.'} \emph{The American
+{`R-Squared for Bayesian Regression Models'}. \emph{The American
 Statistician}.
 
-\leavevmode\hypertarget{ref-hammerstrom2010searching}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hammerstrom2010searching}{}}%
 Hammerstrøm, Karianne, Anne Wade, Anne-Marie Klint Jørgensen, and
-Karianne Hammerstrøm. 2010. {`Searching for Studies.'} \emph{Education}
+Karianne Hammerstrøm. 2010. {`Searching for Studies'}. \emph{Education}
 54 (11.3).
 
-\leavevmode\hypertarget{ref-hansen2000bayesian}{}%
-Hansen, Lars Kai, and others. 2000. {`Bayesian Averaging Is
-Well-Temperated.'} In \emph{Proceedings of NIPS}, 99:265--71.
-
-\leavevmode\hypertarget{ref-harremoes2001maximum}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hansen2000bayesian}{}}%
+Hansen, Lars Kai et al. 2000. {`Bayesian Averaging Is Well-Temperated'}.
+In \emph{Proceedings of NIPS}, 99:265--71.
+
+\leavevmode\vadjust pre{\hypertarget{ref-harremoes2001maximum}{}}%
 Harremoës, Peter, and Flemming Topsøe. 2001. {`Maximum Entropy
-Fundamentals.'} \emph{Entropy} 3 (3): 191--226.
-
-\leavevmode\hypertarget{ref-hastie2009boosting}{}%
+Fundamentals'}. \emph{Entropy} 3 (3): 191--226.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hastie2009boosting}{}}%
 Hastie, Trevor, Robert Tibshirani, and Jerome Friedman. 2009. {`Boosting
-and Additive Trees.'} In \emph{The Elements of Statistical Learning},
+and Additive Trees'}. In \emph{The Elements of Statistical Learning},
 337--87. Springer.
 
-\leavevmode\hypertarget{ref-higgins2019cochrane}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-higgins2019cochrane}{}}%
 Higgins, Julian PT, James Thomas, Jacqueline Chandler, Miranda Cumpston,
@@
 
-\leavevmode\hypertarget{ref-horbach2020pandemic}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-horbach2020pandemic}{}}%
 Horbach, Serge PJM. 2020. {`Pandemic Publishing: Medical Journals
-Strongly Speed up Their Publication Process for COVID-19.'}
+Strongly Speed up Their Publication Process for COVID-19'}.
 \emph{Quantitative Science Studies} 1 (3): 1056--67.
 
-\leavevmode\hypertarget{ref-hoy2020rise}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hoy2020rise}{}}%
 Hoy, Matthew B. 2020. {`Rise of the Rxivs: How Preprint Servers Are
-Changing the Publishing Process.'} \emph{Medical Reference Services
+Changing the Publishing Process'}. \emph{Medical Reference Services
 Quarterly} 39 (1): 84--89.
 
-\leavevmode\hypertarget{ref-ikonomakis2005text}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ikonomakis2005text}{}}%
 Ikonomakis, M, Sotiris Kotsiantis, and V Tampakas. 2005. {`Text
-Classification Using Machine Learning Techniques.'} \emph{WSEAS
+Classification Using Machine Learning Techniques'}. \emph{WSEAS
 Transactions on Computers} 4 (8): 966--74.
 
-\leavevmode\hypertarget{ref-james2013introduction}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-james2013introduction}{}}%
 James, Gareth, Daniela Witten, Trevor Hastie, and Robert Tibshirani.
@@
 
-\leavevmode\hypertarget{ref-jayashree2020evaluation}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-jayashree2020evaluation}{}}%
 Jayashree, P, and PK Srijith. 2020. {`Evaluation of Deep Gaussian
-Processes for Text Classification.'} In \emph{Proceedings of the 12th
+Processes for Text Classification'}. In \emph{Proceedings of the 12th
 Language Resources and Evaluation Conference}, 1485--91.
 
-\leavevmode\hypertarget{ref-jonnalagadda2015automating}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-jonnalagadda2015automating}{}}%
 Jonnalagadda, Siddhartha R, Pawan Goyal, and Mark D Huffman. 2015.
 {`Automating Data Extraction in Systematic Reviews: A Systematic
-Review.'} \emph{Systematic Reviews} 4 (1): 1--16.
-
-\leavevmode\hypertarget{ref-joo2020being}{}%
+Review'}. \emph{Systematic Reviews} 4 (1): 1--16.
+
+\leavevmode\vadjust pre{\hypertarget{ref-joo2020being}{}}%
 Joo, Taejong, Uijung Chung, and Min-Gwan Seo. 2020. {`Being Bayesian
-about Categorical Probability.'} In \emph{International Conference on
+about Categorical Probability'}. In \emph{International Conference on
 Machine Learning}, 4950--61. PMLR.
 
-\leavevmode\hypertarget{ref-jospin2020hands}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-jospin2020hands}{}}%
 Jospin, Laurent Valentin, Wray Buntine, Farid Boussaid, Hamid Laga, and
 Mohammed Bennamoun. 2020. {`Hands-on Bayesian Neural Networks--a
-Tutorial for Deep Learning Users.'} \emph{arXiv Preprint
+Tutorial for Deep Learning Users'}. \emph{arXiv Preprint
 arXiv:2007.06823}.
 
-\leavevmode\hypertarget{ref-kapelner2013bartmachine}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kapelner2013bartmachine}{}}%
 Kapelner, Adam, and Justin Bleich. 2013. {`bartMachine: Machine Learning
-with Bayesian Additive Regression Trees.'} \emph{arXiv Preprint
+with Bayesian Additive Regression Trees'}. \emph{arXiv Preprint
 arXiv:1312.2171}.
 
-\leavevmode\hypertarget{ref-kapelner2015prediction}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kapelner2015prediction}{}}%
 ---------. 2015. {`Prediction with Missing Data via Bayesian Additive
-Regression Trees.'} \emph{Canadian Journal of Statistics} 43 (2):
+Regression Trees'}. \emph{Canadian Journal of Statistics} 43 (2):
 224--39.
 
-\leavevmode\hypertarget{ref-khoshgoftaar2010comparing}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-khoshgoftaar2010comparing}{}}%
 Khoshgoftaar, Taghi M, Jason Van Hulse, and Amri Napolitano. 2010.
 {`Comparing Boosting and Bagging Techniques with Noisy and Imbalanced
-Data.'} \emph{IEEE Transactions on Systems, Man, and Cybernetics-Part A:
+Data'}. \emph{IEEE Transactions on Systems, Man, and Cybernetics-Part A:
 Systems and Humans} 41 (3): 552--68.
 
-\leavevmode\hypertarget{ref-kohavi1995study}{}%
-Kohavi, Ron, and others. 1995. {`A Study of Cross-Validation and
-Bootstrap for Accuracy Estimation and Model Selection.'} In
-\emph{Ijcai}, 14:1137--45. 2. Montreal, Canada.
-
-\leavevmode\hypertarget{ref-lai2015recurrent}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kohavi1995study}{}}%
+Kohavi, Ron et al. 1995. {`A Study of Cross-Validation and Bootstrap for
+Accuracy Estimation and Model Selection'}. In \emph{Ijcai}, 14:1137--45.
+2. Montreal, Canada.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lai2015recurrent}{}}%
 Lai, Siwei, Liheng Xu, Kang Liu, and Jun Zhao. 2015. {`Recurrent
-Convolutional Neural Networks for Text Classification.'} In
+Convolutional Neural Networks for Text Classification'}. In
 \emph{Twenty-Ninth AAAI Conference on Artificial Intelligence}.
 
-\leavevmode\hypertarget{ref-landauer1998introduction}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-landauer1998introduction}{}}%
 Landauer, Thomas K, Peter W Foltz, and Darrell Laham. 1998. {`An
-Introduction to Latent Semantic Analysis.'} \emph{Discourse Processes}
+Introduction to Latent Semantic Analysis'}. \emph{Discourse Processes}
 25 (2-3): 259--84.
 
-\leavevmode\hypertarget{ref-larsen2010rate}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-larsen2010rate}{}}%
 Larsen, Peder, and Markus Von Ins. 2010. {`The Rate of Growth in
 Scientific Publication and the Decline in Coverage Provided by Science
-Citation Index.'} \emph{Scientometrics} 84 (3): 575--603.
-
-\leavevmode\hypertarget{ref-laws2008stopping}{}%
+Citation Index'}. \emph{Scientometrics} 84 (3): 575--603.
+
+\leavevmode\vadjust pre{\hypertarget{ref-laws2008stopping}{}}%
 Laws, Florian, and Hinrich Schütze. 2008. {`Stopping Criteria for Active
-Learning of Named Entity Recognition.'} In \emph{Proceedings of the 22nd
+Learning of Named Entity Recognition'}. In \emph{Proceedings of the 22nd
 International Conference on Computational Linguistics (Coling 2008)},
@@
 
-\leavevmode\hypertarget{ref-lefebvre2011searching}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lefebvre2011searching}{}}%
 Lefebvre, C, E Manheimer, J Glanville, J Higgins, and S Green. 2011.
-{`Searching for Studies (Chapter 6).'} \emph{Cochrane Handbook for
+{`Searching for Studies (Chapter 6)'}. \emph{Cochrane Handbook for
 Systematic Reviews of Interventions Version} 510.
 
-\leavevmode\hypertarget{ref-li2020survey}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-li2020survey}{}}%
 Li, Qian, Hao Peng, Jianxin Li, Congying Xia, Renyu Yang, Lichao Sun,
 Philip S Yu, and Lifang He. 2020. {`A Survey on Text Classification:
-From Shallow to Deep Learning.'} \emph{arXiv Preprint arXiv:2008.00364}.
-
-\leavevmode\hypertarget{ref-lipscomb2000medical}{}%
-Lipscomb, Carolyn E. 2000. {`Medical Subject Headings (MeSH).'}
+From Shallow to Deep Learning'}. \emph{arXiv Preprint arXiv:2008.00364}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lipscomb2000medical}{}}%
+Lipscomb, Carolyn E. 2000. {`Medical Subject Headings (MeSH)'}.
 \emph{Bulletin of the Medical Library Association} 88 (3): 265.
 
-\leavevmode\hypertarget{ref-malhi2020explainable}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-malhi2020explainable}{}}%
 Malhi, Avleen, Samanta Knapic, and Kary Främling. 2020. {`Explainable
-Agents for Less Bias in Human-Agent Decision Making.'} In
+Agents for Less Bias in Human-Agent Decision Making'}. In
 \emph{International Workshop on Explainable, Transparent Autonomous
@@
 
-\leavevmode\hypertarget{ref-marshall2015systematic}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-marshall2015systematic}{}}%
 Marshall, Iain J, and Byron C Wallace. 2019. {`Toward Systematic Review
 Automation: A Practical Guide to Using Machine Learning Tools in
-Research Synthesis.'} In \emph{Systematic Reviews}, 8:1--10. 1.
+Research Synthesis'}. In \emph{Systematic Reviews}, 8:1--10. 1.
 Springer.
 
-\leavevmode\hypertarget{ref-minaee2021deep}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-minaee2021deep}{}}%
 Minaee, Shervin, Nal Kalchbrenner, Erik Cambria, Narjes Nikzad, Meysam
 Chenaghlu, and Jianfeng Gao. 2021. {`Deep Learning--Based Text
-Classification: A Comprehensive Review.'} \emph{ACM Computing Surveys
+Classification: A Comprehensive Review'}. \emph{ACM Computing Surveys
 (CSUR)} 54 (3): 1--40.
 
-\leavevmode\hypertarget{ref-miwa2014reducing}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-miwa2014reducing}{}}%
 Miwa, Makoto, James Thomas, Alison O'Mara-Eves, and Sophia Ananiadou.
 2014. {`Reducing Systematic Review Workload Through Certainty-Based
-Screening.'} \emph{Journal of Biomedical Informatics} 51: 242--53.
-
-\leavevmode\hypertarget{ref-moore2018transparent}{}%
+Screening'}. \emph{Journal of Biomedical Informatics} 51: 242--53.
+
+\leavevmode\vadjust pre{\hypertarget{ref-moore2018transparent}{}}%
 Moore, Alexander, Vanessa Murdock, Yaxiong Cai, and Kristine Jones.
-2018. {`Transparent Tree Ensembles.'} In \emph{The 41st International
+2018. {`Transparent Tree Ensembles'}. In \emph{The 41st International
 ACM SIGIR Conference on Research \& Development in Information
@@
 
-\leavevmode\hypertarget{ref-pubmedUpdate}{}%
-{`NCBI Insights : Updated Pubmed e-Utilities Coming in April 2022!'}
+\leavevmode\vadjust pre{\hypertarget{ref-pubmedUpdate}{}}%
+{`NCBI Insights : Updated Pubmed e-Utilities Coming in April 2022!'}.
 n.d. U.S. National Library of Medicine.
@@
 
-\leavevmode\hypertarget{ref-o2015using}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-o2015using}{}}%
 O'Mara-Eves, Alison, James Thomas, John McNaught, Makoto Miwa, and
 Sophia Ananiadou. 2015. {`Using Text Mining for Study Identification in
-Systematic Reviews: A Systematic Review of Current Approaches.'}
+Systematic Reviews: A Systematic Review of Current Approaches'}.
 \emph{Systematic Reviews} 4 (1): 1--22.
 
-\leavevmode\hypertarget{ref-ohsawa1998keygraph}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ohsawa1998keygraph}{}}%
 Ohsawa, Yukio, Nels E Benson, and Masahiko Yachida. 1998. {`KeyGraph:
 Automatic Indexing by Co-Occurrence Graph Based on Building Construction
-Metaphor.'} In \emph{Proceedings IEEE International Forum on Research
+Metaphor'}. In \emph{Proceedings IEEE International Forum on Research
 and Technology Advances in Digital Libraries-ADL'98-}, 12--18. IEEE.
 
-\leavevmode\hypertarget{ref-olorisade2016critical}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-olorisade2016critical}{}}%
 Olorisade, Babatunde K, Ed de Quincey, Pearl Brereton, and Peter Andras.
 2016. {`A Critical Analysis of Studies That Address the Use of Text
-Mining for Citation Screening in Systematic Reviews.'} In
+Mining for Citation Screening in Systematic Reviews'}. In
 \emph{Proceedings of the 20th International Conference on Evaluation and
@@
 
-\leavevmode\hypertarget{ref-pavlinek2017text}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-pavlinek2017text}{}}%
 Pavlinek, Miha, and Vili Podgorelec. 2017. {`Text Classification Method
-Based on Self-Training and LDA Topic Models.'} \emph{Expert Systems with
+Based on Self-Training and LDA Topic Models'}. \emph{Expert Systems with
 Applications} 80: 83--93.
 
-\leavevmode\hypertarget{ref-poulter2008mscanner}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-poulter2008mscanner}{}}%
 Poulter, Graham L, Daniel L Rubin, Russ B Altman, and Cathal Seoighe.
-2008. {`MScanner: A Classifier for Retrieving Medline Citations.'}
+2008. {`MScanner: A Classifier for Retrieving Medline Citations'}.
 \emph{BMC Bioinformatics} 9 (1): 1--12.
 
-\leavevmode\hypertarget{ref-rstat}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rstat}{}}%
 R Core Team. 2020. \emph{R: A Language and Environment for Statistical
@@
 
-\leavevmode\hypertarget{ref-ramezankhani2016impact}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ramezankhani2016impact}{}}%
 Ramezankhani, Azra, Omid Pournik, Jamal Shahrabi, Fereidoun Azizi,
@@
 with SMOTE on the Performance of 3 Classifiers in Prediction of Type 2
-Diabetes.'} \emph{Medical Decision Making} 36 (1): 137--44.
-
-\leavevmode\hypertarget{ref-robert2004monte}{}%
+Diabetes'}. \emph{Medical Decision Making} 36 (1): 137--44.
+
+\leavevmode\vadjust pre{\hypertarget{ref-robert2004monte}{}}%
 Robert, Christian P, George Casella, and George Casella. 2004.
@@
 
-\leavevmode\hypertarget{ref-roshan2020improvement}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-roshan2020improvement}{}}%
 Roshan, Seyed Ehsan, and Shahrokh Asadi. 2020. {`Improvement of Bagging
 Performance for Classification of Imbalanced Datasets Using Evolutionary
-Multi-Objective Optimization.'} \emph{Engineering Applications of
+Multi-Objective Optimization'}. \emph{Engineering Applications of
 Artificial Intelligence} 87: 103319.
 
-\leavevmode\hypertarget{ref-rousseau2015graph}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rousseau2015graph}{}}%
 Rousseau, Francois. 2015. {`Graph-of-Words: Mining and Retrieving Text
-with Networks of Features.'} PhD thesis, Ph. D. dissertation.
-
-\leavevmode\hypertarget{ref-rousseau2015text}{}%
+with Networks of Features'}. PhD thesis, Ph. D. dissertation.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rousseau2015text}{}}%
 Rousseau, François, Emmanouil Kiagias, and Michalis Vazirgiannis. 2015.
-{`Text Categorization as a Graph Classification Problem.'} In
+{`Text Categorization as a Graph Classification Problem'}. In
 \emph{Proceedings of the 53rd Annual Meeting of the Association for
@@
 
-\leavevmode\hypertarget{ref-newis}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-newis}{}}%
 Sadaghiani, Catharina, Tjibbe Donker, Xanthi Andrianou, Balázs Babarczy,
@@
 
-\leavevmode\hypertarget{ref-sampson2011precision}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-sampson2011precision}{}}%
 Sampson, Margaret, Jennifer Tetzlaff, and Christine Urquhart. 2011.
 {`Precision of Healthcare Systematic Review Searches in a
-Cross-Sectional Sample.'} \emph{Research Synthesis Methods} 2 (2):
+Cross-Sectional Sample'}. \emph{Research Synthesis Methods} 2 (2):
 119--25.
 
-\leavevmode\hypertarget{ref-schonlau2017text}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-schonlau2017text}{}}%
 Schonlau, Matthias, and Nick Guenther. 2017. {`Text Mining Using
-n-Grams.'} \emph{Schonlau, M., Guenther, N. Sucholutsky, I. Text Mining
+n-Grams'}. \emph{Schonlau, M., Guenther, N. Sucholutsky, I. Text Mining
 Using n-Gram Variables. The Stata Journal} 17 (4): 866--81.
 
-\leavevmode\hypertarget{ref-settles2009active}{}%
-Settles, Burr. 2009. {`Active Learning Literature Survey.'}
-
-\leavevmode\hypertarget{ref-soria2011belm}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-settles2009active}{}}%
+Settles, Burr. 2009. {`Active Learning Literature Survey'}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-soria2011belm}{}}%
 Soria-Olivas, Emilio, Juan Gomez-Sanchis, José D Martin, Joan
 Vila-Frances, Marcelino Martinez, José R Magdalena, and Antonio J
-Serrano. 2011. {`BELM: Bayesian Extreme Learning Machine.'} \emph{IEEE
+Serrano. 2011. {`BELM: Bayesian Extreme Learning Machine'}. \emph{IEEE
 Transactions on Neural Networks} 22 (3): 505--9.
 
-\leavevmode\hypertarget{ref-soto2019thalia}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-soto2019thalia}{}}%
 Soto, Axel J, Piotr Przybyła, and Sophia Ananiadou. 2019. {`Thalia:
-Semantic Search Engine for Biomedical Abstracts.'} \emph{Bioinformatics}
+Semantic Search Engine for Biomedical Abstracts'}. \emph{Bioinformatics}
 35 (10): 1799--1801.
 
-\leavevmode\hypertarget{ref-tashman2000out}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-tashman2000out}{}}%
 Tashman, Leonard J. 2000. {`Out-of-Sample Tests of Forecasting Accuracy:
-An Analysis and Review.'} \emph{International Journal of Forecasting} 16
+An Analysis and Review'}. \emph{International Journal of Forecasting} 16
 (4): 437--50.
 
-\leavevmode\hypertarget{ref-rpart}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rpart}{}}%
 Therneau, Terry, and Beth Atkinson. 2019. \emph{Rpart: Recursive
@@
 
-\leavevmode\hypertarget{ref-thomas2007eppi}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-thomas2007eppi}{}}%
 Thomas, James, and Jeff Brunton. 2007. {`EPPI-Reviewer: Software for
-Research Synthesis.'}
-
-\leavevmode\hypertarget{ref-tsafnat2013automation}{}%
+Research Synthesis'}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tsafnat2013automation}{}}%
 Tsafnat, Guy, Adam Dunn, Paul Glasziou, and Enrico Coiera. 2013. {`The
-Automation of Systematic Reviews.'} British Medical Journal Publishing
+Automation of Systematic Reviews'}. British Medical Journal Publishing
 Group.
 
-\leavevmode\hypertarget{ref-tsafnat2014systematic}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-tsafnat2014systematic}{}}%
 Tsafnat, Guy, Paul Glasziou, Miew Keen Choong, Adam Dunn, Filippo
 Galgani, and Enrico Coiera. 2014. {`Systematic Review Automation
-Technologies.'} \emph{Systematic Reviews} 3 (1): 1--15.
-
-\leavevmode\hypertarget{ref-turian2010word}{}%
+Technologies'}. \emph{Systematic Reviews} 3 (1): 1--15.
+
+\leavevmode\vadjust pre{\hypertarget{ref-turian2010word}{}}%
 Turian, Joseph, Lev Ratinov, and Yoshua Bengio. 2010. {`Word
 Representations: A Simple and General Method for Semi-Supervised
-Learning.'} In \emph{Proceedings of the 48th Annual Meeting of the
+Learning'}. In \emph{Proceedings of the 48th Annual Meeting of the
 Association for Computational Linguistics}, 384--94.
 
-\leavevmode\hypertarget{ref-violos2016sentiment}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-violos2016sentiment}{}}%
 Violos, John, Konstantinos Tserpes, Evangelos Psomakelis, Konstantinos
 Psychas, and Theodora Varvarigou. 2016. {`Sentiment Analysis Using
-Word-Graphs.'} In \emph{Proceedings of the 6th International Conference
+Word-Graphs'}. In \emph{Proceedings of the 6th International Conference
 on Web Intelligence, Mining and Semantics}, 1--9.
 
-\leavevmode\hypertarget{ref-visser2010performing}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-visser2010performing}{}}%
 Visser, Eelco. 2010. {`Performing Systematic Literature Reviews with
-Researchr: Tool Demonstration.'} \emph{Technical Report Series
+Researchr: Tool Demonstration'}. \emph{Technical Report Series
 TUD-SERG-2010-010}.
 
-\leavevmode\hypertarget{ref-wallace2010active}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wallace2010active}{}}%
 Wallace, Byron C, Kevin Small, Carla E Brodley, and Thomas A Trikalinos.
-2010. {`Active Learning for Biomedical Citation Screening.'} In
+2010. {`Active Learning for Biomedical Citation Screening'}. In
 \emph{Proceedings of the 16th ACM SIGKDD International Conference on
@@
 
-\leavevmode\hypertarget{ref-wallace2010semi}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wallace2010semi}{}}%
 Wallace, Byron C, Thomas A Trikalinos, Joseph Lau, Carla Brodley, and
 Christopher H Schmid. 2010. {`Semi-Automated Screening of Biomedical
-Citations for Systematic Reviews.'} \emph{BMC Bioinformatics} 11 (1):
+Citations for Systematic Reviews'}. \emph{BMC Bioinformatics} 11 (1):
 1--11.
 
-\leavevmode\hypertarget{ref-wilkins2005embase}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wilkins2005embase}{}}%
 Wilkins, Thad, Ralph A Gillies, and Kathy Davies. 2005. {`EMBASE Versus
 MEDLINE for Family Medicine Searches: Can MEDLINE Searches Find the
-Forest or a Tree?'} \emph{Canadian Family Physician} 51 (6): 848--49.
-
-\leavevmode\hypertarget{ref-woods1998medline}{}%
+Forest or a Tree?'}. \emph{Canadian Family Physician} 51 (6): 848--49.
+
+\leavevmode\vadjust pre{\hypertarget{ref-woods1998medline}{}}%
 Woods, David, and Kate Trewheellar. 1998. {`Medline and Embase
-Complement Each Other in Literature Searches.'} \emph{BMJ: British
+Complement Each Other in Literature Searches'}. \emph{BMJ: British
 Medical Journal} 316 (7138): 1166.
 
-\leavevmode\hypertarget{ref-yang2020survey}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-yang2020survey}{}}%
 Yang, JinXiong, Liang Bai, and Yanming Guo. 2020. {`A Survey of Text
-Classification Models.'} In \emph{Proceedings of the 2020 2nd
+Classification Models'}. In \emph{Proceedings of the 2020 2nd
 International Conference on Robotics, Intelligent Control and Artificial
@@
 
-\leavevmode\hypertarget{ref-yang2020hyperparameter}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-yang2020hyperparameter}{}}%
 Yang, Li, and Abdallah Shami. 2020. {`On Hyperparameter Optimization of
-Machine Learning Algorithms: Theory and Practice.'}
+Machine Learning Algorithms: Theory and Practice'}.
 \emph{Neurocomputing} 415: 295--316.
 
-\leavevmode\hypertarget{ref-zhou2021ensemble}{}%
-Zhou, Zhi-Hua. 2021. {`Ensemble Learning.'} In \emph{Machine Learning},
+\leavevmode\vadjust pre{\hypertarget{ref-zhou2021ensemble}{}}%
+Zhou, Zhi-Hua. 2021. {`Ensemble Learning'}. In \emph{Machine Learning},
 181--210. Springer.
 
-\leavevmode\hypertarget{ref-zhu2010confidence}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-zhu2010confidence}{}}%
 Zhu, Jingbo, Huizhen Wang, Eduard Hovy, and Matthew Ma. 2010.
 {`Confidence-Based Stopping Criteria for Active Learning for Data
-Annotation.'} \emph{ACM Transactions on Speech and Language Processing
+Annotation'}. \emph{ACM Transactions on Speech and Language Processing
 (TSLP)} 6 (3): 1--24.

### 2021-12-13 Manuscript/Manuscript.Rmd
added abstract and title

@@
 ---
-title: Main manuscript
+title: An open-source integrated framework for the automation of citation collection and screening in systematic reviews. 
 authors:
@@
 abstract: |
-  Enter the text of your abstract here.
+  The exponential growth in scientific production makes its summarisation through secondary literature exceedingly demanding in terms of time and human resources.
+  We introduce a new open-source framework that significantly increases efficiency during the citation collection and screening phases of systematic reviews.\
+  The framework introduces three main tools:
+  an automatic citation search engine and manager that allows collecting records from multiple citation databases (PUBMED, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax;
+  a citation screening tool based on Bayesian active machine learning and natural language processing, which requires users feedback only on uncertain classifications to increase predictive accuracy iteratively;
+  a semi-automatic data-driven query generator to create new search queries from existing reviewed citation data sets.\
+  The framework was applied on an example topic performing citation collection and screening.
+  We estimated median posterior Sensitivity and Efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of possibly missed relevant matches in the unreviewed records.\
+  17755 unique records were collected through the framework citation manager;
+  101 over 766 records were found to be relevant after manual evaluation, while the rest were excluded by the automatic classification;
+  the expected Efficiency was 95.7% [95.3%, 95.7%] for a Sensitivity of 100% [93.5%, 100%].
+  A new search query was generated from the labelled dataset, and 82579 more records were collected.
+Only 567 records required human review after the automatic screening, and six additional positive matches were found.
+  Including the additional records, the overall expected Sensitivity dropped to 97.3% [73.8%, 100%] while the Efficiency raised to 98.6% [98.2%, 98.7%].\
+  The framework can significantly reduce human resources requirements for systematic reviews by simplifying citation collection and screening while demonstrating exceptional sensitivity even on large data sets.
 keywords:
-  - blah
-  - blee
-  - bloo
-  - these are optional and can be removed
+  - Systematic review automation
+  - Citation management
+  - Online data collection
+  - Active machine learning
+  - Natural language processing
+  - Bayesian modeling
 bibliography: references.bib

### 2021-12-13 Manuscript/Manuscript.tex
added abstract and title

--- 2021-10-26 Manuscript/Manuscript.tex
@@
 \usepackage{microtype}      % microtypography
-\usepackage{lipsum}
 \usepackage{graphicx}
 
-\title{Main manuscript}
+\title{An open-source integrated framework for the automation of
+citation collection and screening in systematic reviews.}
 
@@
 \begin{abstract}
-Enter the text of your abstract here.
+The exponential growth in scientific production makes its summarisation
+through secondary literature exceedingly demanding in terms of time and
+human resources. We introduce a new open-source framework that
+significantly increases efficiency during the citation collection and
+screening phases of systematic reviews.\\
+The framework introduces three main tools: an automatic citation search
+engine and manager that allows collecting records from multiple citation
+databases (PUBMED, WOS, SCOPUS, EMBASE, IEEE) with a unified query
+syntax; a citation screening tool based on Bayesian active machine
+learning and natural language processing, which requires users feedback
+only on uncertain classifications to increase predictive accuracy
+iteratively; a semi-automatic data-driven query generator to create new
+search queries from existing reviewed citation data sets.\\
+The framework was applied on an example topic performing citation
+collection and screening. We estimated median posterior Sensitivity and
+Efficiency {[}90\% Credible Intervals{]} using Bayesian simulation to
+predict the distribution of possibly missed relevant matches in the
+unreviewed records.\\
+17755 unique records were collected through the framework citation
+manager; 101 over 766 records were found to be relevant after manual
+evaluation, while the rest were excluded by the automatic
+classification; the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]}
+for a Sensitivity of 100\% {[}93.5\%, 100\%{]}. A new search query was
+generated from the labelled dataset, and 82579 more records were
+collected. Only 567 records required human review after the automatic
+screening, and six additional positive matches were found. Including the
+additional records, the overall expected Sensitivity dropped to 97.3\%
+{[}73.8\%, 100\%{]} while the Efficiency raised to 98.6\% {[}98.2\%,
+98.7\%{]}.\\
+The framework can significantly reduce human resources requirements for
+systematic reviews by simplifying citation collection and screening
+while demonstrating exceptional sensitivity even on large data sets.
 \end{abstract}
@@
 \keywords{
-    blah
+    Systematic review automation
    \and
-    blee
+    Citation management
    \and
-    bloo
+    Online data collection
    \and
-    these are optional and can be removed
+    Active machine learning
+   \and
+    Natural language processing
+   \and
+    Bayesian modeling
   }
@@
 methodological justification behind the different components and
-features of the framework.
+features of the framework.\\
 
@@
 framework manually; this is particularly useful to acquire records from
-the SCOPUS
-(\url{https://www.scopus.com/search/form.uri?display=basic\#basic}) and
-EMBASE databases
-(\url{https://www.embase.com/\#advancedSearch/default}), for which a
-comprehensive API interface was not easy to build. An extra manual
-search was necessary also for Pubmed, since the API and the web
-interface have different rule expansion algorithms and return slightly
-different results ({`NCBI Insights : Updated Pubmed e-Utilities Coming
-in April 2022!'} n.d.). A short guide on how to set up the framework for
-each supported database is available in Supplemental Material S3.\\
+the SCOPUS (\url{https://www.scopus.com/}) and EMBASE databases
+(\url{https://www.embase.com/}), for which a comprehensive API interface
+was not easy to build. An extra manual search was necessary also for
+Pubmed, since the API and the web interface have different rule
+expansion algorithms and return slightly different results ({`NCBI
+Insights : Updated Pubmed e-Utilities Coming in April 2022!'} n.d.). A
+short guide on how to set up the framework for each supported database
+is available in Supplemental Material S3.\\
 The acquired records are merged into a single database, resolving
@@
 best hyperparameter set in terms of Sensitivity followed by Efficiency
-from the cluster with the highest average score.
+from the cluster with the highest average score.\\
 
@@
 
-The first search session returned a total of 27600 unique records,
-specifically 12719 (71.6\% of the total) records from the EMBASE
-database, followed by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from
-SCOPUS, 2100 (11.8\%) from WOS, and 60 (0.34\%) from IEEE (Table 1).
-There were various degrees of overlapping between sources, with the
-38.4\% of records being present in more than one database and EMBASE and
-IEEE being the databases with the higher uniqueness ratios. The final
-dataset was composed by 17755 unique records.\\
-The first 250 records were manually labeled. Of these 43 (17.2\%) were
-labeled as positive, and 207 (82.8\%) as negative.
+The first search session returned a total of 27600 records, specifically
+12719 (71.6\% of the total) records from the EMBASE database, followed
+by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from SCOPUS, 2100 (11.8\%)
+from WOS, and 60 (0.34\%) from IEEE (Table 1). There were various
+degrees of overlapping between sources, with the 38.4\% of records being
+present in more than one database and EMBASE and IEEE being the
+databases with the higher uniqueness ratios. The final data set was
+composed by 17755 unique records.\\
+The first 250 records (based on ``simple query ordering'') were manually
+labeled. Of these 43 (17.2\%) were labeled as positive, and 207 (82.8\%)
+as negative.
 
@@
 
-\caption{\label{tab:session 1}\textbf{Table 1}.
+\caption{\label{tab:Table 1}\textbf{Table 1}.
 Distribution of retrieved records by source and session.
-For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total.
-All session shows records after joining and deduplication of the Session 1 and Session 2 dataset.}
+For each source it is reported the number of records, percentage over the session total (after removing duplicates), and number or records specific for a source as absolute value and as percentage over the source total.
+All session shows records after joining and deduplication of the Session 1 and Session 2 data set.}
 \centering
@@
 
-Records were joined into a database and arrange by simple query
-ordering; of these, the first 250 records were labelled to create the
-initial training set.\\
-Using the classification model,7 automatic classification and manual
-review iterations (CR) were performed (Table 2). It is possible to
-observe how the number of records that required manual review dropped
-rapidly between iterations, indicating that the engine was converging
-while the uncertainties were resolved.\\
+The labeled records were used to train the Bayesian classification model
+used to label the remaining records. After seven classification and
+review (CR) iterations (three resulting in new positive matches and four
+extra replications to account for stochastic variability), a total of
+101 positives matches were found, requiring manual review of 766 records
+(13.2\% positivity rate).\\
+It is possible to observe how the number of records that required manual
+review dropped rapidly between iterations (Table 2), indicating that the
+engine was converging while the uncertainties were resolved.\\
 This phenomenon is better depicted in Fig. 1 of the Supplemental
-Material S2. It shows the mixture distribution of the PPD of the
+Material S2, showing the mixture distribution of the PPDs of the
 records, specifically for the reviewed positive and negative records,
 and for records that need manual review after the classification step:
-it can be noticed how the distribution of the uncertain records shrinks
-(they concentrate in a shorter probability range) and shifts toward the
+it can be noticed how the distribution of the uncertain records shrinked
+(they concentrate in a shorter probability range) and shifted toward the
 negative zone as more positive matches are found and reviewed.
-Accordingly (Table 2), the number of new positives found drops after the
-first couple of iterations. As per default, the classification process
-was stopped after four rounds with no new positive matches; a total
-number of 101 positives were found over 766 manually reviewed records
-(13.2\% positivity rate).\\
 
@@
 
-By evaluating how often a term was used by the classification model, it
-is possible to define their relevance in labeling the records (see
-Methods). Here follows the 15 most relevant terms by inclusion rate over
-10,000 posterior tree inclusions, described as: Term (citation part):
-Inclusion Rate (Inclusion Stability) {[}linear Relative Risk,
-Statistic{]}.
+We extracted the 15 term more relevant for the classification model,
+described as: Term (citation part): Inclusion Rate (Inclusion Stability)
+{[}linear Relative Risk, Statistic{]}.
 
@@
 ``facility''ies that facilitates the ``spread'' of infections, and even
-one of the authors of this study (Donker T.) or the region of interest
-(``Orange County'') of another research group active on the topic of
-healthcare asociated pathogen spreading over hospital networks. It is
-interesting to see that some terms were considered highly relevant for
-the BART models (e.g., ``Worker'' in 6th position out of more than 3800
-terms considered) although in a simpler linear model their effect would
-be hardly significant (statistic: -1.21 s.e.); these are terms which are
-relevant only together with other terms but not by themselves,
-highlighting the extra predictive power brought by a non-linear model
-like BART.\\
+one of the authors of this study (Donker T.) as well as the region of
+interest (``Orange County'') of another research group active on the
+topic of healthcare asociated pathogen spreading over hospital networks.
+Some terms were considered highly relevant for the BART models (e.g.,
+``Worker'' in 6th position out of more than 3800 terms considered)
+although in a simpler linear model their effect would be hardly
+significant (statistic: -1.21 s.e.); these are terms which are relevant
+only in conjunction with other terms but not by themselves, highlighting
+the extra predictive power brought by a non-linear model like BART.\\
 A more extensive set of terms is presented in Table 1 of Supplemental
@@
 more and more skeptical and asks to review even some records labelled as
-positive in the initial training set in Session 1. This behaviour can be
-useful to spot classification errors and inconsistencies. Considering
-both sessions, 1333 records were reviewed and 107 (8.03\%) were found.
+positive in the initial training set generated during Session 1. This
+behaviour can be useful to spot classification errors and
+inconsistencies. Considering both sessions, 1333 records were reviewed
+and 107 (8.03\%) were found.
 
@@
 predicted probability produced by the engine and found no additional
-positive matches.
+positive matches.\\
 
@@
 
-The field of literature review automatisation is mature and ripe with
-innovation, and we expect an increasing use of such technologies to
-confront the ever-faster production of scientific literature. We believe
-it is appreciable that a multiplicity of tools are being made available
-to let researchers and policymakers find the instrument that better fits
-their needs.\\
-We tried to contribute to the field with an innovative methodology and
-tool that provides excellent performance and easy integration with
-existing systematic review pipelines. The value of this work lies not
-only in the framework itself, which we provide as open-source software,
-but in the set of solutions we developed to solve various SRA issues and
-that can be used to improve existing solutions.
+The field of literature review automation is maturing rapidly, and we
+expect an increasing use of such technologies to manage the ever-faster
+rate of scientific production. We believe it is appreciable that a
+multiplicity of tools are being made available to let researchers and
+policymakers find the instrument that better fits their needs.\\
+We contribute to this field with an innovative framework that provide
+excellent performance and easy integration with existing systematic
+review pipelines. The value of this work lies not only in the framework
+itself, which we provide as open-source software, but in the set of
+methodologies we developed to solve various SRA issues and that can be
+used to improve already existing solutions.\\
 

### 2021-12-13 R/Analysis.R

@@ -1,16 +1,13 @@
-# compute_rnd_sample_needed <- function(obs_pos, obs_neg, tot_records, tot_pos = obs_pos,
-# 																			tot_neg = tot_records - tot_pos,
-# 																			quants = c(.01, .99)) {
-# 	n_needed <- extraDistr::qnhyper(quants, tot_neg, tot_pos, obs_pos)
-#
-# 	list(
-# 		n_needed = n_needed,
-# 		used_prop = (obs_pos + obs_neg) / n_needed,
-# 		needed_prop = n_needed / (obs_pos + obs_neg),
-# 		efficiency = 1 - (obs_pos + obs_neg) / n_needed
-# 	)
-# }
-
+#' Describe changes in the record labels after a Classification/Review Iteration
+#'
+#' Once \code{\link{}}
+#'
+#' @param Annotations
+#'
+#' @return
+#' @export
+#'
+#' @examples
 compute_changes <- function(Annotations) {
 	Annotations %>%
 		transmute(

### 2021-12-13 Manuscript/Manuscript_Discussion.Rmd
added extra line before references

@@
 We contribute to this field with an innovative framework that provide excellent performance and easy integration with existing systematic review pipelines.
-The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of methodologies we developed to solve various SRA issues and that can be used to improve already existing solutions.
+The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of methodologies we developed to solve various SRA issues and that can be used to improve already existing solutions.\

### 2021-12-13 Manuscript/Manuscript_Methods.Rmd
added extra line before references

@@
 We then identified homogeneous "performance clusters" of scores given hyperparameter values using a partition tree [@rpart].
-For the rest of the study, we used the best hyperparameter set in terms of Sensitivity followed by Efficiency from the cluster with the highest average score.
+For the rest of the study, we used the best hyperparameter set in terms of Sensitivity followed by Efficiency from the cluster with the highest average score.\

### 2021-12-13 Manuscript/Manuscript_Results.Rmd
add line numbers
some rewriting

@@
   pdf_document:
-    keep_tex: true
     includes:
@@
 
-The first search session returned a total of `r all_records` unique records, specifically `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total` of the total) records from the EMBASE database, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from Pubmed, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from SCOPUS, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from WOS, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from IEEE (Table 1).
+The first search session returned a total of `r all_records` records, specifically `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total` of the total) records from the EMBASE database, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from Pubmed, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from SCOPUS, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from WOS, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from IEEE (Table 1).
 There were various degrees of overlapping between sources, with the `r percent(1 - source_distr[1])` of records being present in more than one database and EMBASE and IEEE being the databases with the higher uniqueness ratios.
@@
 Distribution of retrieved records by source and session.
-For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total.
+For each source it is reported the number of records, percentage over the session total (after removing duplicates), and number or records specific for a source as absolute value and as percentage over the source total.
 All session shows records after joining and deduplication of the Session 1 and Session 2 data set.", label = "Table 1")`
 
-Records were joined into a database and arrange by simple query ordering;
-of these, the first 250 records were labelled to create the initial training set.\
-Using the classification model,`r n_review_rounds` automatic classification and manual review iterations (CR) were performed (Table 2).
-It is possible to observe how the number of records that required manual review dropped rapidly between iterations, indicating that the engine was converging while the uncertainties were resolved.\
-This phenomenon is better depicted in Fig. 1 of the Supplemental Material S2.
-It shows the mixture distribution of the PPD of the records, specifically for the reviewed positive and negative records, and for records that need manual review after the classification step:
-it can be noticed how the distribution of the uncertain records shrinks (they concentrate in a shorter probability range) and shifts toward the negative zone as more positive matches are found and reviewed.
-Accordingly (Table 2), the number of new positives found drops after the first couple of iterations.
-As per default, the classification process was stopped after four rounds with no new positive matches;
-a total number of `r num_last_positives` positives were found over `r tot_reviewed` manually reviewed records (`r percent(num_last_positives/tot_reviewed)` positivity rate).\
+The labeled records were used to train the Bayesian classification model used to label the remaining records.
+After seven classification and review (CR) iterations (three resulting in new positive matches and four extra replications to account for stochastic variability), a total of `r num_last_positives` positives matches were found, requiring manual review of `r tot_reviewed` records (`r percent(num_last_positives/tot_reviewed)` positivity rate).\
+It is possible to observe how the number of records that required manual review dropped rapidly between iterations (Table 2), indicating that the engine was converging while the uncertainties were resolved.\
+This phenomenon is better depicted in Fig.
+1 of the Supplemental Material S2, showing the mixture distribution of the PPDs of the records, specifically for the reviewed positive and negative records, and for records that need manual review after the classification step:
+it can be noticed how the distribution of the uncertain records shrinked (they concentrate in a shorter probability range) and shifted toward the negative zone as more positive matches are found and reviewed.
 
@@
 
-By evaluating how often a term was used by the classification model, it is possible to define their relevance in labeling the records (see Methods).
-Here follows the 15 most relevant terms by inclusion rate over 10,000 posterior tree, described as:
+We extracted the 15 term more relevant for the classification model, described as:
 Term (citation part): Inclusion Rate (Inclusion Stability) [linear Relative Risk, Statistic].
@@
 The engine was able to pick up the central concept of the research, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) as well as the region of interest ("Orange County") of another research group active on the topic of healthcare asociated pathogen spreading over hospital networks.
-It is interesting to see that some terms were considered highly relevant for the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
-these are terms which are relevant only together with other terms but not by themselves, highlighting the extra predictive power brought by a non-linear model like BART.\
+Some terms were considered highly relevant for the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
+these are terms which are relevant only in conjunction with other terms but not by themselves, highlighting the extra predictive power brought by a non-linear model like BART.\
 A more extensive set of terms is presented in Table 1 of Supplemental Material S2.
@@
 An evaluation of the convergence (Figure 1, Supplemental Material S2) showed that, in addition to the dynamics already observed in session 1 (shrinkage and negative shift), a second mode appeared in the mixture distribution of the records to be reviewed, centred in a highly positive zone.
-The interpretation is that as the number of negative training records increases, the engine gets more and more skeptical and asks to review even some records labelled as positive in the initial training set in Session 1.
+The interpretation is that as the number of negative training records increases, the engine gets more and more skeptical and asks to review even some records labelled as positive in the initial training set generated during Session 1.
 This behaviour can be useful to spot classification errors and inconsistencies.
@@
 In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows, even a small probability can translate, in the worst case scenario, into a relevant number of missed positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
-To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no additional positive matches.
+To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no additional positive matches.\
 

### 2021-12-20 R/Reporting.R
docs: documented functions
plus some small edits

@@ -1,9 +1,59 @@
+
+# Summarising -------------------------------------------------------------
+
+
+
+#' Summarise a discrete vector
+#'
+#' Shows for each unique element its numerosity and percentage.
+#'
+#' @param vec A vector.
+#'
+#' @return A string listing each unique element in the vector, its numerosity
+#'   and percentage over the vector length (including missings).
+#'
+#' @examples
+#'
+#' summarise_vector(iris$Species)
+#' # setosa: 50 (33.3%), versicolor: 50 (33.3%), virginica: 50 (33.3%)
+#'
 summarise_vector <- function(vec) {
-	if (length(vec) == 0) return(0)
+	if (length(vec) == 0 | is.list(vec) | !is.null(dim(vec))) return('incorrect input')
+	all_els <- length(vec)
 	table(vec) %>%
-		{paste0(names(.), ': ', ., ' (', percent(./sum(.)), ')', collapse = ', ')}
+		{paste0(names(.), ': ', ., ' (', percent(./all_els), ')', collapse = ', ')}
 }
 
+#' Record distribution between sources in an Annotation file
+#'
+#' Summarises the distribution of the source databases among the the citation
+#' records in an Annotation data set. Also reports the fraction of records which
+#' are unique for each database.
+#'
+#' @param annotation_file An annotation data frame or a file path to it.
+#' @param as_data_frame Whether to return the results as a data frame
+#'   (\code{TRUE}) or a list (\code{FALSE}).
+#' @param add_session_totals Whether to add the total number of record.
+#'
+#' @return For each source:\item{Records}{The number of records related to the
+#'   source.}\item{\% over total}{the percentage over the total
+#'   records.}\item{Source specific records}{the number of record derived only
+#'   from that source.}\item{\% over source total}{the value in \code{Source
+#'   specific records} as percentage over the source total.} If
+#'   \code{as_data_frame} is \code{TRUE}, the results are returned as a data
+#'   frame with a row for each source, otherwise as a nested list.
+#'   \code{add_session_totals} adds another entry with the total number of
+#'   records in the \code{annotation_file}.
+#'
+#' @examples
+#'
+#' \dontrun{
+#'
+#' records <- get_session_files('Session1')$Records
+#'
+#' summarise_by_source(records)
+#'
+#' }
[…]

### 2021-12-20 R/Helpers.R
clean: moved helper functions in their own file

@@ -1,0 +1,102 @@
+
+# Easier to use than !(a %in% b)
+'%nin%' <- Negate('%in%')
+
+# Nicer output than scales::percent()
+percent <- function(x) {
+	sapply(x, function(x) {
+		if (!is.na(x)) {
+			if (abs(x * 100) < 1) {
+				sprintf('%s%%', signif(x * 100, 2))
+			} else {
+				sprintf('%s%%', signif(x * 100, 3))
+			}
+		} else NA
+	})
+}
+
+# override lubridate equivalents which always complain about the missing timezone
+today <- function() as_date(Sys.time())
+now <- function() Sys.time()
+
+# A file path friendly lubridate::now()
+safe_now <- function() {
+	str_replace_all(now(), c(' ' = 'T', ':' = '.'))
+}
+
+# Tool to grab XHR messages from dynamic websites
+get_website_resources <- function(url, url_filter = '.*', type_filter = '.*',
+																	wait_for = 20,
+																	n_of_resources = NULL, interactive = F) {
+
+	crrri::perform_with_chrome(function(client) {
+		Fetch <- client$Fetch
+		Page <- client$Page
+
+		if (interactive) client$inspect()
+
+		out <- new.env()
+
+		out$results <- list()
+		out$resolve_function <- NULL
+
+		out$pr <- promises::promise(function(resolve, reject) {
+			out$resolve_function <- resolve
+
+			Fetch$enable(patterns = list(list(urlPattern="*", requestStage="Response"))) %...>% {
+				Fetch$requestPaused(callback = function(params) {
+
+					if (str_detect(params$request$url, url_filter) & str_detect(params$resourceType, type_filter)) {
+
+						Fetch$getResponseBody(requestId = params$requestId) %...>% {
+							resp <- .
+
+							if (resp$body != '') {
+								if (resp$base64Encoded) resp$body = jsonlite::base64_dec(resp$body) %>% rawToChar()
+
+								body <- list(list(
+									url = params$request$url,
+									response = resp
+								)) %>% setNames(params$requestId)
+
+								#str(body)
+
+								out$results <- append(out$results, body)
+
+								if (!is.null(n_of_resources) & length(out$results) >= n_of_resources) out$resolve_function(out$results)
+							}
+
+						}
+					}
+
+					Fetch$continueRequest(requestId = params$requestId)
+				})
[…]

### 2021-12-20 R/Setup.R

@@ -67,93 +67,6 @@ options(baysren.probs = c(.05, .5, .95))
 options(baysren.sessions_folder = 'Sessions')
 
 
-# Helper functions --------------------------------------------------------
-
-
-# Easier to use than !(a %in% b)
-'%nin%' <- Negate('%in%')
-
-# Nicer output than scales::percent()
-percent <- function(x) {
-	sapply(x, function(x) {
-		if (!is.na(x)) {
-			if (abs(x * 100) < 1) {
-				sprintf('%s%%', signif(x * 100, 2))
-			} else {
-				sprintf('%s%%', signif(x * 100, 3))
-			}
-		} else NA
-	})
-}
-
-# override lubridate equivalents which always complain about the missing timezone
-today <- function() as_date(Sys.time())
-now <- function() Sys.time()
-
-# A file path friendly lubridate::now()
-safe_now <- function() {
-	str_replace_all(now(), c(' ' = 'T', ':' = '.'))
-}
-
-# Tool to grab XHR messages from dynamic websites
-get_website_resources <- function(url, url_filter = '.*', type_filter = '.*',
-																	wait_for = 20,
-																	n_of_resources = NULL, interactive = F) {
-
-	crrri::perform_with_chrome(function(client) {
-		Fetch <- client$Fetch
-		Page <- client$Page
-
-		if (interactive) client$inspect()
-
-		out <- new.env()
-
-		out$results <- list()
-		out$resolve_function <- NULL
-
-		out$pr <- promises::promise(function(resolve, reject) {
-			out$resolve_function <- resolve
-
-			Fetch$enable(patterns = list(list(urlPattern="*", requestStage="Response"))) %...>% {
-				Fetch$requestPaused(callback = function(params) {
-
-					if (str_detect(params$request$url, url_filter) & str_detect(params$resourceType, type_filter)) {
-
-						Fetch$getResponseBody(requestId = params$requestId) %...>% {
-							resp <- .
-
-							if (resp$body != '') {
-								if (resp$base64Encoded) resp$body = jsonlite::base64_dec(resp$body) %>% rawToChar()
-
-								body <- list(list(
-									url = params$request$url,
-									response = resp
-								)) %>% setNames(params$requestId)
-
-								#str(body)
-
-								out$results <- append(out$results, body)
-
-								if (!is.null(n_of_resources) & length(out$results) >= n_of_resources) out$resolve_function(out$results)
-							}
-
[…]

### 2021-12-20 R/Setup.R
bug: declare missing packages

@@ -43,7 +43,7 @@ pkg.require(
 											 "bakaburg1/tidytrees"),
 	only_install = c('purrr', 'openxlsx', 'tictoc', 'tidyr', 'arm', 'english',
 									 'parallel', 'jsonlite', 'rentrez', 'wosr', 'brms', 'ggridges',
-									 'knitr', 'kableExtra', 'extraDistr', 'broom')
+									 'knitr', 'kableExtra', 'extraDistr', 'broom', 'viridis')
 )
 
 

### 2021-12-20 R/Analysis.R
docs: add documentation

@@ -1,14 +1,35 @@
 #' Describe changes in the record labels after a Classification/Review Iteration
 #'
-#' Once \code{\link{}}
+#' Takes an Annotation file with a \code{Rev_prediction_new} column and computes
+#' differences in the labeling introduced by the last automatic classification /
+#' review.
 #'
-#' @param Annotations
+#' @param Annotations An Annotation data set, as data frame or as a file path to
+#'   it.
 #'
-#' @return
-#' @export
+#' @return A data frame with total reviewed positive and negative labels and
+#'   their sum, the new labels added in the \code{Rev_prediction_new} column,
+#'   and and summary of all changes in the last iteration, e.g.: n -> y (a
+#'   previously non relevant record becoming relevant) or unlab. -> n (an
+#'   unlabeled record becoming negative).
 #'
 #' @examples
+#'
+#' \dontrun{
+#'
+#' # Taking the path to an annotation data file; also the actual data frame can
+#' # be passed
+#'  Annotations <- get_session_files("Session1")$Annotations[2]
+#'
+#'  out <- compute_changes(Annotations)
+#'
+#'  # The output is easier to read if changed in a long format:
+#'  str(out) # the easiest solution for fast inspection of results
+#'  tidyr::pivot_longer(everything(), names_to = 'Indicator', values_to = 'Value') # To get a long format data frame
+#' }
 compute_changes <- function(Annotations) {
+	Annotations <- import_data(Annotations)
+
 	Annotations %>%
 		transmute(
 			Target = coalesce_labels(cur_data(), c('Rev_prediction_new',
@@ -41,11 +62,31 @@ compute_changes <- function(Annotations) {
 		}
 }
 
+#' Train a simple Bayesian logistic model on classification results
+#'
+#' The function uses an Annotation data set to train a Bayesian logistic model
+#' that estimates the probability of a relevant record given the lower
+#' boundaries of the PPD produced by the classification model for the records
+#' whose label was manually reviewed.
+#'
+#' The produced model can be used to predict the distribution of the cumulative
+#' number of total unseen positive records.
+#'
+#' Usually this function is not to be used directly but through
+#' \code{\link{estimate_performance()}}.
+#'
+#' @param train_data An Annotation data set with predictions produced by
+#'   \code{enrich_annotation_file()}.
+#' @param seed An integer to replicate results
+#'
+#' @return An object of class \code{brmsfit}. See
[…]

### 2021-12-20 R/Helpers.R
clean: format TRUE and FALSE in long format

@@ -27,7 +27,7 @@ safe_now <- function() {
 # Tool to grab XHR messages from dynamic websites
 get_website_resources <- function(url, url_filter = '.*', type_filter = '.*',
 																	wait_for = 20,
-																	n_of_resources = NULL, interactive = F) {
+																	n_of_resources = NULL, interactive = FALSE) {
 
 	crrri::perform_with_chrome(function(client) {
 		Fetch <- client$Fetch

### 2021-12-20 R/Model.R

@@ -84,7 +84,7 @@ create_training_set <- function(Records, min_freq = 0.05) {
 	Abstract_DTM <- with(
 		Records,
 		Abstract %>%
-			str_remove_all(regex('\\b(background|introduction|method\\w*|result\\w*|conclusion\\w*|discussion)',ignore_case = T)) %>%
+			str_remove_all(regex('\\b(background|introduction|method\\w*|result\\w*|conclusion\\w*|discussion)',ignore_case = TRUE)) %>%
 			text_to_DTM(min.freq = min_freq, label = 'ABSTR__', ids = ID,
 									freq.subset.ids = ID[Target %in% c('y', 'n')])
 	)
@@ -96,7 +96,7 @@ create_training_set <- function(Records, min_freq = 0.05) {
 		Records,
 		text_to_DTM(Authors, tokenize.fun = tokenize_authors, min.freq = min_freq,
 								label = 'AUTH__', ids = ID, freq.subset.ids = ID[Target %in% c('y', 'n')],
-								add.ngrams = F, aggr.synonyms = F)
+								add.ngrams = FALSE, aggr.synonyms = FALSE)
 	)
 
 	message('dimensions: ', paste(dim(Authors_DTM), collapse = ', '))
@@ -116,7 +116,7 @@ create_training_set <- function(Records, min_freq = 0.05) {
 		Records,
 		text_to_DTM(Mesh, tokenize.fun = tokenize_MESH, min.freq = min_freq,
 								label = 'MESH__', ids = ID, freq.subset.ids = ID[Target %in% c('y', 'n')],
-								add.ngrams = F)
+								add.ngrams = FALSE)
 	)
 
 	message('dimensions: ', paste(dim(Mesh_DTM), collapse = ', '))
@@ -132,7 +132,7 @@ create_training_set <- function(Records, min_freq = 0.05) {
 		distinct() %>% # remove the duplicated positive matches
 		select(
 			where(~ !is.numeric(.x)), # Keep ID and Target
-			where(~ suppressWarnings(sum(as.numeric(.x), na.rm = T)) > 1) # Keep features with more than one match in a document
+			where(~ suppressWarnings(sum(as.numeric(.x), na.rm = TRUE)) > 1) # Keep features with more than one match in a document
 		)
 
 }
@@ -383,7 +383,7 @@ enrich_annotation_file <- function(session_name,
 																	 ## Model parameters
 																	 pos_mult = 10,
 																	 n_models = 10,
-																	 resample = F,
[…]

### 2021-12-20 R/NLP.R

@@ -15,7 +15,7 @@ lemmatize <- function(text_vec, dict = lexicon::hash_lemmas) {
 	separator <- '_tagseparator_'
 
 	terms <- paste(text_vec, separator, collapse = ' ')
-	terms <- gsub(sprintf(' *%s$', separator), '', terms, perl = T) %>%
+	terms <- gsub(sprintf(' *%s$', separator), '', terms, perl = TRUE) %>%
 		str_split('\\b') %>% unlist()
 	terms <- terms[!(terms %in% c('', ' '))]
 
@@ -28,8 +28,8 @@ lemmatize <- function(text_vec, dict = lexicon::hash_lemmas) {
 		paste(collapse = ' ') %>%
 		str_split(sprintf(' *%s *', separator)) %>% unlist
 
-	output <- gsub('\\s+', ' ', output, perl = T)
-	output <- gsub('^\\s+|\\s+$', '', output, perl = T)
+	output <- gsub('\\s+', ' ', output, perl = TRUE)
+	output <- gsub('^\\s+|\\s+$', '', output, perl = TRUE)
 
 	replace(output, output == 'NA', NA)
 }
@@ -52,11 +52,11 @@ tokenize_text <- function(corpus) {
 
 	tictoc::tic()
 	corpus <- tolower(corpus)
-	corpus <- gsub('-', '_', corpus, fixed = T)
+	corpus <- gsub('-', '_', corpus, fixed = TRUE)
 	corpus <- removeWords(corpus, stopwords("english"))
-	corpus <- gsub("\'(s|re|t|d)?\\b", '', corpus, perl = T)
-	corpus <- gsub('_',' ', corpus, fixed = T)
-	corpus <- gsub('[^\\w\\d\\s]+', ' ', corpus, perl = T)
+	corpus <- gsub("\'(s|re|t|d)?\\b", '', corpus, perl = TRUE)
+	corpus <- gsub('_',' ', corpus, fixed = TRUE)
+	corpus <- gsub('[^\\w\\d\\s]+', ' ', corpus, perl = TRUE)
 	corpus <- lemmatize(corpus)
 
 	tictoc::toc()
@@ -357,9 +357,9 @@ DTM.aggr_synonyms <- function(DTM, min.sim = .9) {
 
 	mat.sparse <- as(mat, "dgCMatrix") # Using sparse matrices
 
-	TTM <- (t(mat.sparse) %*% mat.sparse)/sqrt(tcrossprod(colSums(mat^2, na.rm = T))) # Cosine similarity
[…]

### 2021-12-20 R/Record_management.R

@@ -479,7 +479,7 @@ fix_duplicated_records <- function(records) {
 				purrr::keep(~ str_length(.x) > 0) %>%
 				paste(collapse = '; '),
 			## TODO: clean up is necessary for Source and Source_type
-			N_citations = suppressWarnings(na.omit(N_citations) %>% max(na.rm = T) %>%
+			N_citations = suppressWarnings(na.omit(N_citations) %>% max(na.rm = TRUE) %>%
 																		 	purrr::modify_if(~ !is.finite(.x), ~ NA))
 		)
 
@@ -548,8 +548,8 @@ create_annotation_file <- function(records, reorder_query = NULL,
 
 	if (is.character(records)) {
 		records <- c(
-			list.files(records, full.names = T, recursive = T) %>%
-				str_subset('~\\$', negate = T) %>%
+			list.files(records, full.names = TRUE, recursive = TRUE) %>%
+				str_subset('~\\$', negate = TRUE) %>%
 				str_subset('(parsed|API)\\.csv'),
 			records[!dir.exists(records)]
 		) %>% unique()
@@ -734,14 +734,14 @@ create_session <- function(Records, session_name,
 	dup_session_action <- match.arg(dup_session_action)
 
 	initialise_session <- function(Records, session_path, DTM = NULL,
-																 use_time_stamp = T) {
+																 use_time_stamp = TRUE) {
 
 		if (use_time_stamp) ts <- glue('_{safe_now()}') else ''
 
 		# Create the session folder
 		if (!dir.exists(session_path)) {
 			message('- create session folder "', session_path, '".')
-			dir.create(session_path, recursive = T, showWarnings = FALSE)
+			dir.create(session_path, recursive = TRUE, showWarnings = FALSE)
 		}
 
 		# At the moment csv files will be converted to excel, eventually both file
@@ -754,9 +754,9 @@ create_session <- function(Records, session_name,
 		if (is.character(Records) | is.factor(Records)) {
 			if (!file.exists(Records)) stop(Records, ' does not exists.')
 
-			file.copy(Records, file_path, overwrite = T, recursive = F)
+			file.copy(Records, file_path, overwrite = TRUE, recursive = FALSE)
 		} else {
-			openxlsx::write.xlsx(Records, file = file_path, asTable = T)
+			openxlsx::write.xlsx(Records, file = file_path, asTable = TRUE)
 		}
 
 		message("- Copy or write the DTM data")
[…]

### 2021-12-20 R/Record_search.R

@@ -203,7 +203,7 @@ search_wos <- function(query, year_query = NULL, additional_fields = NULL,
 
 		if (str_detect(query, '^\\w+ ?= ?')) {
 			pieces <- str_split(query, '( ?AND ?)?\\w{2} ?= ?') %>% unlist() %>%
-				str_squish() %>% str_subset('^$', negate = T)
+				str_squish() %>% str_subset('^$', negate = TRUE)
 
 			fields <- str_extract_all(query, '\\w{2} ?= ?') %>% unlist() %>%
 				str_squish() %>% str_remove(' ?= ?')
@@ -336,7 +336,7 @@ search_pubmed <- function(query, year_query = NULL, additional_fields = NULL,
 	query <- paste(query, year_query, additional_fields, collapse = ' AND ') %>% str_squish()
 
 	res <- rentrez::entrez_search(db = "pubmed", term = query, retmax = 0,
-																api_key = api_key, use_history = T)
+																api_key = api_key, use_history = TRUE)
 
 	total_count <- min(res$count, record_limit)
 
@@ -353,8 +353,8 @@ search_pubmed <- function(query, year_query = NULL, additional_fields = NULL,
 		while (!have.results & trials < 20) {
 			records <- try(rentrez::entrez_fetch(db = "pubmed", web_history = res$web_history,
 																						retstart = step * 200, retmax = min(200, total_count - step * 200),
-																						rettype = 'medline', parsed = F,
-																						api_key = api_key), silent = T)
+																						rettype = 'medline', parsed = FALSE,
+																						api_key = api_key), silent = TRUE)
 
 			have.results <- class(records) == 'character'
 			trials <- trials + 1
@@ -756,11 +756,11 @@ perform_search_session <- function(query, year_query = NULL, actions = c('API', 
 
 		if (file.exists(out_file)) {
 			if (!overwrite) {
-				warning(basename(out_file), ' already present and argument overwrite is FALSE.', call. = F)
+				warning(basename(out_file), ' already present and argument overwrite is FALSE.', call. = FALSE)
 
 				read_csv(out_file, col_types = cols())
 			} else {
-				warning(basename(out_file), ' will be overwritten.', call. = F)
+				warning(basename(out_file), ' will be overwritten.', call. = FALSE)
 				NULL
 			}
 		} else NULL
[…]

### 2021-12-20 R/Reporting.R

@@ -377,7 +377,7 @@ summarise_annotations_by_session <- function(sessions_folder = getOption("baysre
 		session <- sessions[i]
 
 		res <- summarise_annotations(session, sessions_folder,
-																 remove_empty_columns = F, remove_raw_data = F)
+																 remove_empty_columns = FALSE, remove_raw_data = FALSE)
 
 		if (i > 1) {
 			res <- tail(res, -1)
@@ -552,7 +552,7 @@ print_table <- function(data, caption = '', allow_math = FALSE, ...) {
 		}
 
 		data %>%
-			knitr::kable(format = "latex", booktabs = T,
+			knitr::kable(format = "latex", booktabs = TRUE,
 									 caption = caption %>% str_squish() %>%
 									 	str_replace_all(c('%' = '\\\\%', '\\*\\*([^\\n]+)\\*\\*' = '\\\\textbf{\\1}')),
 									 escape = !allow_math,

### 2021-12-20 R/Rule_building.R

@@ -1,4 +1,4 @@
-extract_rules <- function(session_name, rebuild_dtm = F, vimp.threshold = 1.25,
+extract_rules <- function(session_name, rebuild_dtm = FALSE, vimp.threshold = 1.25,
 													n.trees = 800, sessions_folder = getOption("baysren.sessions_folder"), ...) {
 
 	message('Preparing the data')
@@ -28,13 +28,13 @@ extract_rules <- function(session_name, rebuild_dtm = F, vimp.threshold = 1.25,
 	message('Generating feature dataset')
 
 	specific.terms <- Variable_importance %>% filter(Score > vimp.threshold) %>% pull(Term) %>%
-		str_subset('^MESH', negate = T) %>% str_remove('.+__') %>%
+		str_subset('^MESH', negate = TRUE) %>% str_remove('.+__') %>%
 		str_sub(1, 2500) %>% # str_sub() is necessary since many functions cannot use such long names
 		unique()
 
 
 	SpecificDTM <- pbmclapply(specific.terms, function(term) {
-		values <- select(DTM, matches(paste0('__', term, '$'))) %>% rowSums(na.rm = T)
+		values <- select(DTM, matches(paste0('__', term, '$'))) %>% rowSums(na.rm = TRUE)
 
 		factor((values > 0) + 0)
 	}) %>%
@@ -64,7 +64,7 @@ extract_rules <- function(session_name, rebuild_dtm = F, vimp.threshold = 1.25,
 		)
 
 		rpart(Pred ~ ., data = df, control = rpart.control(...)) %>%
-			tidytrees::tidy_tree(eval_ready = T, simplify_rules = T)
+			tidytrees::tidy_tree(eval_ready = TRUE, simplify_rules = TRUE)
 	}) %>% bind_rows()
 
 	list(
@@ -138,7 +138,7 @@ generate_rule_selection_set <- function(rules, target_vec, target_data, add_nega
 	rules <- rules %>%
 		add_cumulative() %>%
 		group_by(cum_pos) %>%
-		mutate(selected_rule = c(T, rep(F, n() - 1)), .before = rule) %>%
+		mutate(selected_rule = c(TRUE, rep(FALSE, n() - 1)), .before = rule) %>%
 		summarise_all(~ c(.x, NA)) %>%
 		mutate(cum_pos = replace(cum_pos, is.na(rule), NA)) %>%
[…]

### 2021-12-20 R/Setup.R

@@ -72,7 +72,7 @@ options(baysren.sessions_folder = 'Sessions')
 if (file.exists('secrets.R')) source('secrets.R')
 
 local({
-	for (file in file.path('R', list.files('R') %>% str_subset('Setup', negate = T))) {
+	for (file in file.path('R', list.files('R') %>% str_subset('Setup', negate = TRUE))) {
 		source(file)
 	}
 })

### 2021-12-20 R/Setup.R
bug: add missing library

@@ -43,7 +43,7 @@ pkg.require(
 											 "bakaburg1/tidytrees"),
 	only_install = c('purrr', 'openxlsx', 'tictoc', 'tidyr', 'arm', 'english',
 									 'parallel', 'jsonlite', 'rentrez', 'wosr', 'brms', 'ggridges',
-									 'knitr', 'kableExtra', 'extraDistr', 'broom', 'viridis')
+									 'knitr', 'kableExtra', 'extraDistr', 'broom', 'viridis', 'lexicon')
 )
 
 

### 2021-12-23 R/Record_search.R
docs: docs update

@@ -1,19 +1,24 @@
 #' Transform a year range into the format required by a specific search engine
 #'
-#' Take a year range in the form of:
+#' Take a period definition and transform it into a specific format passed
+#' through the \code{cases} argument.
 #'
-#' greater than: > Year; greater then or equal to: >= Year; lower than: < Year;
-#' lower then or equal to: <= Year; equal to: Year; range: Year1 - Year2.
+#' The input period specified in \code{year_query} must follow this format:
+#' \itemize{\item{\code{> Year}: }{greater than \code{Year}.}\item{\code{>=
+#' Year}: }{greater then or equal to \code{Year}.}\item{\code{< Year}: }{lower
+#' than \code{Year}.}\item{\code{<= Year}: }{lower then or equal to
+#' \code{Year}.}\item{\code{Year}: }{equal to
+#' \code{Year}.}\item{\code{Year1-Year2}: }{range from \code{Year1} to
+#' \code{Year2}.}}
 #'
-#' and transform it into a specific format passed through the \code{cases}
-#' argument. Some checks are performed to evaluate if \code{year_query} is
-#' clearly in an invalid format.
+#' The input is checked to evaluate if \code{year_query} the format is clearly
+#' invalid.
 #'
-#' @param year_query A string identifying a year or a range o years.
+#' @param year_query A string identifying a search period (see Details).
 #' @param cases The search engine syntax specification into which convert the
 #'   year query It needs to be a list with the following items: gt (greater
-#'   than), ge (greater then or equal to), lt (lower then), le (lower then or
-#'   equal to), ep (equal to), range (range of years). Inside the specification,
+#'   than), ge (greater than or equal to), lt (lower than), le (lower than or
+#'   equal to), eq (equal to), range (range of years). Inside the specification,
 #'   the year in the query can be retrieved with the \code{year_piece}
 #'   placeholder, which in the case of a closed range is a vector of two
 #'   elements (see examples).
@@ -25,7 +30,7 @@
 #'   present. If \code{query} is set, also the \code{arg_in_query_test} argument
 #'   must be set.
 #'
-#' @return The formatted, search engine specific, year filter.
+#' @return The formatted, search engine specific, period filter.
 #'
 #' @examples
 #'
@@ -273,19 +278,21 @@ search_wos <- function(query, year_query = NULL, additional_fields = NULL,
 #' Automatic search on Pubmed database
 #'
 #' Perform an API search using Pubmed E-utilities
[…]

### 2021-12-23 R/Rule_building.R

@@ -1,5 +1,44 @@
+#' Extract screening rules from an Annotation data set
+#'
+#' Starting from a Document Term Matrix (DTM) and a posterior predictive
+#' distribution (PPD) matrix produced by the Bayesian classification engine, a
+#' decision tree algorithm is used to extract rules that partition a subset of
+#' draws from the PPD. Beware that the generation of the rules may take a long
+#' time.
+#'
+#' The algorithm allows to use only a subset of the terms in the DTM and of the
+#' samples in the PPD matrix to cut on computation time. In the first case, a
+#' threshold is used to filter only the most relevant features in the DTM.
+#' Before being used, terms in the DTM are aggregated if they appear in multiple
+#' fields of the citation records and only their general presence in the record
+#' will be stored.
+#'
+#' @param session_name A session identifier corresponding to folders into the
+#'   \code{sessions_folder} folder.
+#' @param rebuild_dtm Whether to use the last DTM stored in the
+#'   \code{session_name} folder (\code{FALSE}) or rebuild it from the last
+#'   Annotation file (\code{TRUE}).
+#' @param vimp.threshold A threshold in the standardized variable importance
+#'   score to filter out less relevant terms in the DTM.
+#' @param n.trees How many draws to use from the PPD matrix to build decision
+#'   trees. This parameter strongly impacts computational time but increases
+#'   sensitivity of the rules found.
+#' @param sessions_folder Where to find the \code{sessions} folders.
+#' @param save_path Since generating the rules is a computation intense process
+#'   it's advisable to save the output in a .rds file placed inside the
+#'   \code{session_name} folder. User need only to provide the name of the file.
+#' @param ... Additional arguments passed to
+#'   \code{\link[rpart:rpart.control]{rpart::rpart.control()}}.
+#'
+#' @return A list with: \item{SpecificDTM}{The DTM with the less relevant terms
+#'   being filtered out and terms in multiple record fields being
+#'   aggregated.}\item{DTM}{The full DTM with the predicted
+#'   classification.}\item{rules}{A data frame reporting the selected rules with
+#'   the average PPD.}
+#'
 extract_rules <- function(session_name, rebuild_dtm = FALSE, vimp.threshold = 1.25,
[…]

### 2021-12-23 R/Record_management.R
feat: add rds parsing to import_data()

@@ -26,6 +26,8 @@ import_data <- function(input, ...) {
 			return(read_excel(input, guess_max = 10^6, ...))
 		} else if (str_detect(input, '\\.csv$')) {
 			return(read_csv(input, guess_max = 10^6, col_types = cols(), ...))
+		} else if (str_detect(input, '\\.rds$')) {
+			return(read_rds(input))
 		}
 	} else if (is.data.frame(input)) {
 		return(input)

### 2021-12-23 R/Analysis.R
docs: reviewed and proofread docs

@@ -1,17 +1,17 @@
 #' Describe changes in the record labels after a Classification/Review Iteration
 #'
 #' Takes an Annotation file with a \code{Rev_prediction_new} column and computes
-#' differences in the labeling introduced by the last automatic classification /
-#' review.
+#' differences in the labelling introduced by the last automatic classification
+#' / review.
 #'
 #' @param Annotations An Annotation data set, as data frame or as a file path to
 #'   it.
 #'
 #' @return A data frame with total reviewed positive and negative labels and
 #'   their sum, the new labels added in the \code{Rev_prediction_new} column,
-#'   and and summary of all changes in the last iteration, e.g.: n -> y (a
-#'   previously non relevant record becoming relevant) or unlab. -> n (an
-#'   unlabeled record becoming negative).
+#'   and and summary of all changes in the last iteration, e.g.: \code{n -> y}
+#'   (a previously non relevant record becoming relevant) or \code{unlab. -> n}
+#'   (an unlabeled record becoming negative).
 #'
 #' @examples
 #'
@@ -73,14 +73,14 @@ compute_changes <- function(Annotations) {
 #' number of total unseen positive records.
 #'
 #' Usually this function is not to be used directly but through
-#' \code{\link{estimate_performance()}}.
+#' \code{\link{estimate_performance}()}.
 #'
 #' @param train_data An Annotation data set with predictions produced by
-#'   \code{enrich_annotation_file()}.
+#'   \code{\link{enrich_annotation_file}()}.
 #' @param seed An integer to replicate results
 #'
 #' @return An object of class \code{brmsfit}. See
-#'   \code{\link[brms:brm]{brms::brm()}} for mode info.
+#'   \code{\link[brms:brm]{brms::brm}()} for mode info.
 #'
 estimate_positivity_rate_model <- function(train_data, seed = 14129189) {
 
@@ -99,35 +99,35 @@ estimate_positivity_rate_model <- function(train_data, seed = 14129189) {
 
 #' Evaluate and report classification performance of given an Annotation file
 #'
-#' This function estimate Sensitivity and Efficiency (the latter as Work saved
-#' over random classification, WSoR) of the classification process (i.e., both
-#' the automatic classification and the human). To compute these statistics,
-#' first a robust estimate of the total number of relevant (positive) records in
-#' the whole data set is needed.
+#' This function estimate Sensitivity and Efficiency (the latter as "Work saved
+#' over random classification", WSoR) of the classification process (i.e., both
+#' the automatic classification and the human). A robust estimate of the total
[…]

### 2021-12-23 R/Model.R

@@ -1,15 +1,15 @@
 
 #' Join classification labels into one
 #'
-#' In the same Annotation file there could be multiple classification labels for
-#' a record, derived by different phases of the labeling procedure. This
-#' function joins them hierarchically, using the label from the label from the
-#' lower hierarchies to fill up \code{NA}s in the upper ones. The hierarchy is
+#' In the same Annotation file, there could be multiple classification labels
+#' for a record derived by different phases of the labelling procedure. This
+#' function joins them hierarchically, using the label from the lower
+#' hierarchies to fill up \code{NA}s in the upper ones. The hierarchy is
 #' considered from left to right.
 #'
 #' This function is a wrapper over
-#' \code{\link[dplyr:coalesce]{dplyr::coalesce()}} which allow to have a standard
-#' coalescing scheme for an annotation file.
+#' \code{\link[dplyr:coalesce]{dplyr::coalesce}()} which allow to have a
+#' standard coalescing scheme for an annotation file.
 #'
 #' @param data An Annotation data frame.
 #' @param label_cols The label columns to coalesce. They are considered
@@ -28,12 +28,12 @@ coalesce_labels <- function(data, label_cols = c('Rev_prediction_new','Rev_predi
 #'
 #' Given an Annotation file, it creates and join Document Term Matrices (DTM)
 #' for the title, abstract, authors, keywords and MESH terms of a record,
-#' keeping terms above a given document frequency among the negative labeled
+#' keeping terms above a given document frequency among the negative labelled
 #' records and which are present in at least two records
 #'
 #' @param Records An Annotation data frame.
 #' @param min_freq Minimum document frequency (between 0 and 1) in negative
-#'   labeled records above which a term is considered.
+#'   labelled records above which a term is considered.
 #'
 #' @return An enriched DTM which is the merge of the title, abstract, authors,
 #'   keywords and MESH terms DTMs plus the record ID and label if present.
@@ -139,8 +139,8 @@ create_training_set <- function(Records, min_freq = 0.05) {
 
 #' Use Bayesian Additive Regression Trees to predict records labels
 #'
-#' This the prediction engine of the framework. It produces a model which
-#' assignes a probability distribution for each record of the probability of
+#' The prediction engine of the framework. It produces a model which
+#' assigns a probability distribution for each record of the probability of
 #' being relevant (i.e., positive label). It is not used alone but inside
 #' \code\link{enrich_annotation_file}.
 #'
[…]

### 2021-12-23 R/NLP.R

@@ -2,7 +2,7 @@
 #'
 #' @param text_vec A vector of text documents.
 #' @param dict A dictionary to use to find base forms. See
-#'   \code{\link[lexicon:hash_lemmas]{lexicon::hash_lemmas()}} for the required
+#'   \code{\link[lexicon:hash_lemmas]{lexicon::hash_lemmas}()} for the required
 #'   structure.
 #'
 #' @return The vector with terms transformed into their base form, when
@@ -152,15 +152,15 @@ tokenize_MESH <- function(mesh) {
 #' Convert a vector of text documents into a Document Term Matrix
 #'
 #' A Document Term Matrix (DTM) is a structure describing the association of a
-#' term to a document. In this case we used a binary matrix with ones if a term
+#' term to a document. In this case, we used a binary matrix with ones if a term
 #' is present in a document and one otherwise.
 #'
 #' Before computing the DTM, document terms are cleaned, tokenized and
 #' lemmatized, and stop-words are removed.
 #'
 #' To reduce noise, only terms that appear in a fraction of documents higher
-#' than \code{min.freq} are considered. The function uses also cosine similarity
-#' to identify relevant subclusters of related terms or redundant one.
+#' than \code{min.freq} are considered. The function also uses cosine similarity
+#' to identify relevant subclusters of related terms or redundant ones.
 #'
 #' @param corpus A vector of text documents.
 #' @param min.freq Minimum number of document in which a term need to be present
@@ -168,7 +168,7 @@ tokenize_MESH <- function(mesh) {
 #' @param ids Identification ID of documents.
 #' @param freq.subset.ids IDs to consider when computing term frequency.
 #' @param included.pos Part of speech (POS) to consider when building the DTM.
-#'   See \code{\link[lexicon:hash_grady_pos]{lexicon::hash_grady_pos()}} for a
+#'   See \code{\link[lexicon:hash_grady_pos]{lexicon::hash_grady_pos}()} for a
 #'   list of recognized POS.
 #' @param tokenize.fun Function to use to clean up text.
 #' @param add.ngrams Whether to search and add non-consecutive n-grams. See
@@ -176,15 +176,15 @@ tokenize_MESH <- function(mesh) {
 #' @param n.gram.thresh The threshold to use to identify the network of
 #'   non-consecutive n-grams if \code{add.ngrams} is \code{TRUE}.
 #' @param aggr.synonyms Whether to aggregate terms which almost always appear
-#'   together. See \code{\link{DTM.aggr_synonyms}}.
[…]

### 2021-12-23 R/Record_management.R

@@ -1,10 +1,15 @@
 
 #' Read a data file/object
 #'
-#' @param input A file path to an Excel/CSV file or a data frame object
+#' General wrapper that imports CSV/Excel/RDS files if a file path is given in
+#' \code{input}. If \code{input} is a data frame, it will just be passed
+#' through. An error is raised in the case of unrecognized objects/files.
+#'
+#' @param input A file path to an Excel/CSV/RDS file or a data frame object.
 #' @param ... Additional arguments to pass to
-#'   \code{link[readxl:read_excel]{readxl::read_excel}} or
-#'   \code{link[readr:read_csv]{readr::read_csv}}, depending on the file type.
+#'   \code{\link[readxl:read_excel]{readxl::read_excel}},
+#'   \code{\link[readr:read_csv]{readr::read_csv}}, or
+#'   \code{\link[readr:read_rds]{readr::read_rds}}, depending on the file type.
 #'
 #' @return A data frame object.
 #'
@@ -16,6 +21,8 @@
 #' data <- import_data('data.csv')
 #'
 #' data <- import_data('data.xlsx', sheet = 2)
+#'
+#' data <- import_data('data.rds')
 #'
 #' data <- import_data(data)
 #' }
@@ -33,15 +40,17 @@ import_data <- function(input, ...) {
 		return(input)
 	}
 
-	stop('Input should be an existing csv/excel file path or a data.frame, found "', class(input),'".')
+	stop('Input should be an existing csv/excel/rds file path or a data.frame, found "', class(input),'".')
 }
 
 
 #' Clean up problematic text in the citation data.
 #'
+#' Used internally by the \code{parse_*} functions.
+#'
 #' @param df The data frame to be cleaned.
 #'
-#' @return The cleaned data frame
+#' @return The cleaned data frame.
 #'
 clean_record_textfields <- function(df) {
 	mutate(df,
@@ -58,13 +67,13 @@ clean_record_textfields <- function(df) {
 #'
 #' The information on the records' location is stored in the session journal
 #' created by \code{\link{perform_search_session}}. It is possible to select
-#' records from specific session, query, source combinations. Only parsed or API
-#' downloaded record paths will be returned, not the raw data source files.
+#' records from specific session, query, or source combinations. Only parsed or
+#' API downloaded record paths will be returned, not the raw data source files.
 #'
 #' @param journal A data frame produced by \code{\link{perform_search_session}}
 #'   or a file path to it.
[…]

### 2021-12-23 R/Reporting.R

@@ -26,9 +26,9 @@ summarise_vector <- function(vec) {
 
 #' Record distribution between sources in an Annotation file
 #'
-#' Summarises the distribution of the source databases among the the citation
-#' records in an Annotation data set. Also reports the fraction of records which
-#' are unique for each database.
+#' Summarises the distribution of the source databases among the citation
+#' records in an Annotation data set. It also reports the fraction of records
+#' that are unique for each database.
 #'
 #' @param annotation_file An annotation data frame or a file path to it.
 #' @param as_data_frame Whether to return the results as a data frame
@@ -96,7 +96,7 @@ summarise_by_source <- function(annotation_file, as_data_frame = FALSE,
 
 #' Record distribution between sources for each session
 #'
-#' Applies \code{\link{summarise_by_source()}} to all selected sessions.
+#' Applies \code{\link{summarise_by_source}()} to all selected sessions.
 #'
 #' @param sessions A vector of session identifiers corresponding to folders into
 #'   the \code{sessions_folder} folder.
@@ -104,10 +104,10 @@ summarise_by_source <- function(annotation_file, as_data_frame = FALSE,
 #' @param add_global_totals Add results for all sessions considered together.
 #' @param keep_session_label Add a column which groups rows by session. Useful
 #'   for subsequent sub-setting of the results.
-#' @param ... Other arguments passed to \code{\link{summarise_by_source}}.
+#' @param ... Other arguments passed to \code{\link{summarise_by_source}()}.
 #'
 #' @return A data frame with the number and fraction of total records per source
-#'   and number and fraction of source specific records, grouped by session. An
+#'   and number and fraction of source-specific records, grouped by session. An
 #'   extra group with the overall results is reported if
 #'   \code{add_global_totals} is \code{TRUE}.
 #'
@@ -172,11 +172,11 @@ summarise_sources_by_session <- function(sessions = list.files(sessions_folder),
 
 #' Format records' source distribution as a list
 #'
-#' Takes the output of \code{\link{summarise_sources_by_session}} and formats it
+#' Takes the output of \code{\link{summarise_sources_by_session}()} and formats it
 #' as a list.
 #'
 #' @param source_summary A data frame produced by
-#'   \code{\link{summarise_sources_by_session}}.
+#'   \code{\link{summarise_sources_by_session}()}.
 #'
 #' @return A hierarchical list with record distribution by source and session.
 #'
@@ -211,8 +211,8 @@ source_session_summary_to_list <- function(source_summary) { #TODO: include insi
[…]

### 2021-12-23 Manuscript/S1.Protocol.Rmd
fixed a typo

@@
 
+selection_set_file <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx')
+
 selection_set <- generate_rule_selection_set(
@@
 	target_vec = Target,
-	target_data = SpecificDTM)
-
-selection_set_file <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx')
-openxlsx::write.xlsx(selection_set, selection_set_file)
+	target_data = SpecificDTM,
+	save_path = selection_set_file)
 
@@
 	import_data() %>%
-	simplify_ruleset(ruleset = Target, SpecificDTM) %>%
+	simplify_ruleset(target_vec = Target, target_data = SpecificDTM) %>%
 	pull(rule)

### 2021-12-23 Manuscript/S1.Protocol.Rmd
updated given changes in the framework

@@
 # be chosen by the user; less stringent values can greatly increase computation
-# time;
+# time. By default results will be saved in file called rule_data.rds in the
+# session folder.
 
@@
 
+# No default is given for the save file, since generate_rule_selection_set()
+# have no info about the session it's working on.
 selection_set_file <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx')

### 2021-12-23 Manuscript/Manuscript_Discussion.Rmd
update for consistency with abstract and intro

@@
 By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
-The framework consists of four main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) a Bayesian active machine learning-based citation classifier, and 4) a data-driven search query generation algorithm.\
+The framework consists of four main components: 1) an integrated query-based citation search and management engine, 2) a Bayesian active machine learning-based citation classifier, and 3) a data-driven search query generation algorithm.\
 
-The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e.
-Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases.
+The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases.
 In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
@@
 The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
-The preliminary ordering allow to increase the positivity rate in the initial training set [@wallace2010active].
+The preliminary ordering allow to increase the positivity rate in the initial training set [@wallace2010active].\
 
+For the framework's record classification module we employed an active machine learning approach [@settles2009active, @miwa2014reducing] based on the best practices from other SRA studies, bringing further improvements at various levels.\
 The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
 We did not include classical n-grams [@schonlau2017text], but we used network analysis to find non-consecutive frequently associated terms, a generalisation of n-grams relaxing the term adjacency assumption.
-A similar network approach was applied to merge redundant terms to make model estimation more efficient and reduce noise.\
+This approach allows also to find term connections across fields, for example a term having a different relevancy if associated with a specific author.
+The same technique but with different parameters was applied to merge redundant terms to make model estimation more efficient and reduce noise.\
 The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\
 
-The framework's record classification module implements an active machine learning approach [@settles2009active, @miwa2014reducing] and is based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine].
-When implementing our algorithm we adopted best practices from other SRA studies, bringing improvements at various levels.\
+The automatic classification algorithm is based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine].
 As with other boosted trees algorithms [@hastie2009boosting], BART can explore complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.\

### 2021-12-23 Manuscript/Manuscript.Rmd
updated front page

@@
 authors:
-  - name: David S. Hippocampus
-    thanks: Use footnote for providing further information about author (webpage, alternative address)---*not* for acknowledging funding agencies. Optional.
-    department: Department of Computer Science
-    affiliation: Cranberry-Lemon University
-    location: Pittsburgh, PA 15213
-    email: hippo@cs.cranberry-lemon.edu
-  - name: Elias D. Striatum
-    department: Department of Electrical Engineering
-    affiliation: Mount-Sheikh University
-    location: Santa Narimana, Levand
-    email: stariate@ee.mount-sheikh.edu
+  - name: Angelo D'Ambrosio
+    department: Institute for Infection Prevention and Hospital Hygiene
+    affiliation: Freiburg University Hospital
+    location: Freiburg, Germany
+    email: angelo.d.ambrosio@uniklinik-freiburg.de; a.dambrosioMD@gmail.com
+  - name: Tjibbe Donker
+    department: Institute for Infection Prevention and Hospital Hygiene
+    affiliation: Freiburg University Hospital
+    location: Freiburg, Germany
+    email: tjibbe.donker@uniklinik-freiburg.de
+  - name: Hajo Grundmann
+    department: Institute for Infection Prevention and Hospital Hygiene
+    affiliation: Freiburg University Hospital
+    location: Freiburg, Germany
+    email: hajo.grundmann@uniklinik-freiburg.de
 abstract: |
@@
   The framework introduces three main tools:
-  an automatic citation search engine and manager that allows collecting records from multiple citation databases (PUBMED, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax;
-  a citation screening tool based on Bayesian active machine learning and natural language processing, which requires users feedback only on uncertain classifications to increase predictive accuracy iteratively;
-  a semi-automatic data-driven query generator to create new search queries from existing reviewed citation data sets.\
+  1) an automatic citation search engine and manager that allows collecting records from multiple citation databases (PUBMED, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax;
+  2) a citation screening tool based on Bayesian active machine learning and natural language processing, which requires users feedback only on uncertain classifications to increase predictive accuracy iteratively;
+  3) a semi-automatic data-driven query generator to create new search queries from existing reviewed citation data sets.\
   The framework was applied on an example topic performing citation collection and screening.

### 2021-12-23 Manuscript/Manuscript.tex
small edits to Results table
updated front page

--- 2021-12-08 Manuscript/Manuscript.tex
@@
 
-\title{Main manuscript}
+\title{An open-source integrated framework for the automation of
+citation collection and screening in systematic reviews.}
 
 \author{
-    David S. Hippocampus
-    \thanks{Use footnote for providing further information about author
-(webpage, alternative address)---\emph{not} for acknowledging funding
-agencies. Optional.}
+    Angelo D'Ambrosio
    \\
-    Department of Computer Science \\
-    Cranberry-Lemon University \\
-  Pittsburgh, PA 15213 \\
-  \texttt{\href{mailto:hippo@cs.cranberry-lemon.edu}{\nolinkurl{hippo@cs.cranberry-lemon.edu}}} \\
+    Institute for Infection Prevention and Hospital Hygiene \\
+    Freiburg University Hospital \\
+  Freiburg, Germany \\
+  \texttt{\href{mailto:angelo.d.ambrosio@uniklinik-freiburg.de}{\nolinkurl{angelo.d.ambrosio@uniklinik-freiburg.de}};
+\href{mailto:a.dambrosioMD@gmail.com}{\nolinkurl{a.dambrosioMD@gmail.com}}} \\
    \And
-    Elias D. Striatum
+    Tjibbe Donker
    \\
-    Department of Electrical Engineering \\
-    Mount-Sheikh University \\
-  Santa Narimana, Levand \\
-  \texttt{\href{mailto:stariate@ee.mount-sheikh.edu}{\nolinkurl{stariate@ee.mount-sheikh.edu}}} \\
+    Institute for Infection Prevention and Hospital Hygiene \\
+    Freiburg University Hospital \\
+  Freiburg, Germany \\
+  \texttt{\href{mailto:tjibbe.donker@uniklinik-freiburg.de}{\nolinkurl{tjibbe.donker@uniklinik-freiburg.de}}} \\
+   \And
+    Hajo Grundmann
+   \\
+    Institute for Infection Prevention and Hospital Hygiene \\
+    Freiburg University Hospital \\
+  Freiburg, Germany \\
+  \texttt{\href{mailto:hajo.grundmann@uniklinik-freiburg.de}{\nolinkurl{hajo.grundmann@uniklinik-freiburg.de}}} \\
   }
@@
 \begin{abstract}
-Enter the text of your abstract here.
+The exponential growth in scientific production makes its summarisation
+through secondary literature exceedingly demanding in terms of time and
+human resources. We introduce a new open-source framework that
+significantly increases efficiency during the citation collection and
+screening phases of systematic reviews.\\
+The framework introduces three main tools: 1) an automatic citation
+search engine and manager that allows collecting records from multiple
+citation databases (PUBMED, WOS, SCOPUS, EMBASE, IEEE) with a unified
+query syntax; 2) a citation screening tool based on Bayesian active
+machine learning and natural language processing, which requires users
+feedback only on uncertain classifications to increase predictive
+accuracy iteratively; 3) a semi-automatic data-driven query generator to
+create new search queries from existing reviewed citation data sets.\\
+The framework was applied on an example topic performing citation
+collection and screening. We estimated median posterior Sensitivity and
+Efficiency {[}90\% Credible Intervals{]} using Bayesian simulation to
+predict the distribution of possibly missed relevant matches in the
+unreviewed records.\\
+17755 unique records were collected through the framework citation
+manager; 101 over 766 records were found to be relevant after manual
+evaluation, while the rest were excluded by the automatic
+classification; the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]}
+for a Sensitivity of 100\% {[}93.5\%, 100\%{]}. A new search query was
+generated from the labelled dataset, and 82579 more records were
+collected. Only 567 records required human review after the automatic
+screening, and six additional positive matches were found. Including the
+additional records, the overall expected Sensitivity dropped to 97.3\%
+{[}73.8\%, 100\%{]} while the Efficiency raised to 98.6\% {[}98.2\%,
+98.7\%{]}.\\
+The framework can significantly reduce human resources requirements for
+systematic reviews by simplifying citation collection and screening
+while demonstrating exceptional sensitivity even on large data sets.
 \end{abstract}
@@
 
-The first search session returned a total of 27600 unique records,
-specifically 12719 (71.6\% of the total) records from the EMBASE
-database, followed by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from
-SCOPUS, 2100 (11.8\%) from WOS, and 60 (0.34\%) from IEEE (Table 1).
-There were various degrees of overlapping between sources, with the
-38.4\% of records being present in more than one database and EMBASE and
-IEEE being the databases with the higher uniqueness ratios. The final
-data set was composed by 17755 unique records.\\
+The first search session returned a total of 27600 records, specifically
+12719 (71.6\% of the total) records from the EMBASE database, followed
+by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from SCOPUS, 2100 (11.8\%)
+from WOS, and 60 (0.34\%) from IEEE (Table 1). There were various
+degrees of overlapping between sources, with the 38.4\% of records being
+present in more than one database and EMBASE and IEEE being the
+databases with the higher uniqueness ratios. The final data set was
+composed by 17755 unique records.\\
 The first 250 records (based on ``simple query ordering'') were manually
@@
 Distribution of retrieved records by source and session.
-For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total.
+For each source it is reported the number of records, percentage over the session total (after removing duplicates), and number or records specific for a source as absolute value and as percentage over the source total.
 All session shows records after joining and deduplication of the Session 1 and Session 2 data set.}
@@
 
-By evaluating how often a term was used by the classification model, it
-is possible to define their relevance in labeling the records (see
-Methods). Here follows the 15 most relevant terms by inclusion rate over
-10,000 posterior tree, described as: Term (citation part): Inclusion
-Rate (Inclusion Stability) {[}linear Relative Risk, Statistic{]}.
+We extracted the 15 term more relevant for the classification model,
+described as: Term (citation part): Inclusion Rate (Inclusion Stability)
+{[}linear Relative Risk, Statistic{]}.
 
@@
 topic of healthcare asociated pathogen spreading over hospital networks.
-It is interesting to see that some terms were considered highly relevant
-for the BART models (e.g., ``Worker'' in 6th position out of more than
-3800 terms considered) although in a simpler linear model their effect
-would be hardly significant (statistic: -1.21 s.e.); these are terms
-which are relevant only together with other terms but not by themselves,
-highlighting the extra predictive power brought by a non-linear model
-like BART.\\
+Some terms were considered highly relevant for the BART models (e.g.,
+``Worker'' in 6th position out of more than 3800 terms considered)
+although in a simpler linear model their effect would be hardly
+significant (statistic: -1.21 s.e.); these are terms which are relevant
+only in conjunction with other terms but not by themselves, highlighting
+the extra predictive power brought by a non-linear model like BART.\\
 A more extensive set of terms is presented in Table 1 of Supplemental
@@
 Finally the median Bayesian $R^2$ [90\% CrI] of the logistic models is reported.
-PrI: Predictive Intervals; CrI: Credibility Intervals}
+PrI: Predictive Intervals; CrI: Credibility Intervals.}
 \centering
@@
 The framework consists of four main components: 1) an integrated
-query-based citation search and management engine, 2) a text-to-feature
-extractor module, 3) a Bayesian active machine learning-based citation
-classifier, and 4) a data-driven search query generation algorithm.\\
+query-based citation search and management engine, 2) a Bayesian active
+machine learning-based citation classifier, and 3) a data-driven search
+query generation algorithm.\\
 
@@
 collecting citation data from three well-known scientific databases
-(i.e.~Pubmed, Web of Science, and the database of the Institute of
+(i.e., Pubmed, Web of Science, and the database of the Institute of
 Electrical and Electronics Engineers) as well as process manually
@@
 preliminary ordering allow to increase the positivity rate in the
-initial training set (Wallace, Small, et al. 2010).
-
+initial training set (Wallace, Small, et al. 2010).\\
+
+For the framework's record classification module we employed an active
+machine learning approach Miwa et al. (2014) based on the best practices
+from other SRA studies, bringing further improvements at various
+levels.\\
 The feature extractor module uses modern NLP techniques (Ananiadou and
@@
 non-consecutive frequently associated terms, a generalisation of n-grams
-relaxing the term adjacency assumption. A similar network approach was
-applied to merge redundant terms to make model estimation more efficient
-and reduce noise.\\
+relaxing the term adjacency assumption. This approach allows also to
+find term connections across fields, for example a term having a
+different relevancy if associated with a specific author. The same
+technique but with different parameters was applied to merge redundant
+terms to make model estimation more efficient and reduce noise.\\
 The use of concurrency network-driven modelling of text is not new
@@
 
-The framework's record classification module implements an active
-machine learning approach Miwa et al. (2014) and is based on Bayesian
-Additive Regression Trees (BART) (Chipman et al. 2010; Kapelner and
-Bleich 2013). When implementing our algorithm we adopted best practices
-from other SRA studies, bringing improvements at various levels.\\
+The automatic classification algorithm is based on Bayesian Additive
+Regression Trees (BART) (Chipman et al. 2010; Kapelner and Bleich 2013).
 As with other boosted trees algorithms (Hastie, Tibshirani, and Friedman
@@
 methodologies we developed to solve various SRA issues and that can be
-used to improve already existing solutions.
+used to improve already existing solutions.\\
 

### 2021-12-23 R/Analysis.R
docs: add examples

@@ -163,6 +163,16 @@ estimate_positivity_rate_model <- function(train_data, seed = 14129189) {
 #'   of the Sensitivity computed over the predicted number of positives
 #'   according to the surrogate model.}
 #'
+#' @examples
+#'
+#' \dontrun{
+#'
+#' annotation_file <- get_session_files('Session1')$Annotations %>% last()
+#'
+#' analysis <- estimate_performance(annotation_file)
+#'
+#' }
+#'
 estimate_performance <- function(records, model = NULL, preds = NULL, plot = TRUE,
 																 quants = getOption('baysren.probs'),
 																 nsamples = min(2500, sum(model$fit@sim$n_save)),

### 2021-12-23 R/Model.R
docs: fixed small inconsistencies

@@ -37,7 +37,6 @@ coalesce_labels <- function(data, label_cols = c('Rev_prediction_new','Rev_predi
 #'
 #' @return An enriched DTM which is the merge of the title, abstract, authors,
 #'   keywords and MESH terms DTMs plus the record ID and label if present.
-#' @export
 #'
 #' @examples
 #'

### 2021-12-23 R/Reporting.R

@@ -678,7 +678,7 @@ plot_predictive_densities <- function(session_name,
 #' @param step_size The interval with which the cumulative numbers are plotted.
 #' @param limit How many records to display.
 #'
-#' @return A `ggplot2` object.
+#' @return A \code{ggplot2} object.
 #'
 #'\dontrun{
 #'data <- get_session_files('Session1')$Annotations %>% last() %>%

### 2021-12-23 Manuscript/S1.Protocol.Rmd
some proof reading

@@
 
-Now the annotation file is ready for the manual classification records.
+Now the annotation file is ready for the manual classification of records.
 The annotation file has a column called `Rev_manual`, where records need to be classified as "positive" (y) or "negative" (n) matches by the user.
@@
 The content of this summary is also saved as a CSV file in the Results folder.
-- A variable importance page which list the used terms in order of the fraction of BART trees in which they were used.
+- A variable importance page that lists the used terms in order of the fraction of BART trees in which they were used.
 If an ensemble of models is used, a more robust score is computed, taking the ratio of the mean of the term tree fraction among models and its standard deviation.
@@
 The solution is experimental and greatly favours sensitivity at the expense of specificity.
-This is the general query generation mechanism:
+The general query generation mechanism is the following:
 
@@
 # during the last CR iteration). The score threshold and the number of trees can
-# be chosen by the user; less stringent values can greatly increase computation
-# time. By default results will be saved in file called rule_data.rds in the
-# session folder.
+# be chosen by the user; less stringent values can significantly increase
+# computation time. By default results will be saved in a file called
+# rule_data.rds in the session folder.
 
@@
 
-# The 'candidate_queries' contains the rules and the DMT and the labels on which
-# the rules were built, which need to be passed to
-# generate_rule_selection_set(). This function selects the most effective
-# (higher positive/negative matches delta) rules; also adds negative terms to
-# increase specificity. A data frame is generated (or automatically saved if
-# save_path is set). The output proposes groups of equivalent (in terms of the
-# number of positive matches found) groups of query, ordered by specificity; for
-# each group, the user needs to select the best rule by setting the
-# selected_rule column to TRUE. The groups are in order of growing
-# sensitivity/decreasing specificity, so it may make sense to exclude the last
-# groups totally in order to avoid too many search results.
+# The 'candidate_queries' contains the rules, the DMT and the labels on which
+# the rules were built, which must be passed to generate_rule_selection_set().
+# This function selects the most effective (higher positive/negative matches
+# delta) rules; also adds negative terms to increase specificity. A data frame
+# is generated (or automatically saved if save_path is set). The output proposes
+# groups of equivalent (in terms of the number of positive matches found) groups
+# of query, ordered by specificity; for each group, the user needs to select the
+# best rule by setting the selected_rule column to TRUE. The groups are in order
+# of growing sensitivity/decreasing specificity, so it may make sense to exclude
+# the last groups totally in order to avoid too many search results.
 
@@
 # simplified in order to remove redundant rules and terms. The aim is to provide
-# the shortest rule without loss of retrieving accuracy.
+# the shortest rule without loss of sensitivity.
 
@@
 also, the machine learning classification processing time increases proportionally with the number of records to label.\
-It is advisable then to consider removing the less specific rules iteratively from the new query until a manageable number of records is obtained, considering that the probability of finding new positive matches not already found by more specific queries drops exponentially.\
+It is advisable to consider removing the less specific rules iteratively from the new query until a manageable number of records is obtained, considering that the probability of finding new positive matches not already found by more specific queries drops exponentially.\
 
 Once the new records are collected, `enrich_annotation_file('Session2')` (or any other new session name) can be used to perform the new CR iterations.
-It may be possible that during the first CR iteration, the number of records requiring manual review is a significant number:
+It may be possible that during the first CR iteration, the number of records requiring manual review is significant:
 we suggest evaluating still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.
@@
 
-A number of tools are available to evaluate the classification performance.\
+Several tools are available to evaluate the classification performance.\
 As said before, a result file is stored in the session folder for each CR iteration with information on the classification status;
-remember to run `consolidate_results(session_name)` if you want these results to take into account the manual review of the predicted labels.\
+remember to run `consolidate_results(session_name)` if you want these results to account for the manual review of the predicted labels.\
 `compute_changes()` is a simple function that take an annotation data frame and computes the changes from the last annotation iteration.\
@@
 We tested these tools on our dataset, manually labelling the first 1200 records, ordered by simple query match.\
-The first step is to create a folder where to store the file required for the search, for example, *Grid Search*.
+The first step is to create a folder to store the file required for the search, for example, *Grid Search*.
 Then a fully reviewed record file in the format generated by `create_annotation_file()` is necessary;
@@
 
-with `records` being the fully annotated data frame or a file path to it.
+with `records` being the fully annotated data frame or a file path.
 `prev_classification` can be used to import a different classification file with prelabeled records.
@@
 The function produces a data frame with the score and the cluster of reference of each combination of parameters, the best hyperparameter set (i.e., the most efficient set among the most sensitive in the best cluster) and the best set for each cluster.
-Also, the function creates a plot to visualise the individual impact on performance of each hyperparameter.
+Also, the function creates a plot to visualise each hyperparameter's impact on performance.
 

### 2022-01-12 R/NLP.R
clean: code clean up

@@ -72,27 +72,27 @@ tokenize_text <- function(corpus) {
 #'
 #' @return The tokenized author list.
 #'
-tokenize_authors <- function(corpus) {
+tokenize_authors <- function(authors) {
 
 	message('- tokenizing authors')
 	tictoc::tic()
 
-	ids = 1:length(corpus)
+	ids = 1:length(authors)
 
-	with.comma <- str_detect(corpus, ',')
+	with.comma <- str_detect(authors, ',')
 
-	corpus <- corpus %>% str_squish()
+	authors <- authors %>% str_squish()
 
-	output <- mclapply(1:length(corpus), function(i) {
+	output <- mclapply(1:length(authors), function(i) {
 		if (is.na(with.comma[i])) NA # No authors listed
 		else if (with.comma[i] == TRUE) { # Pubmed or WOS style author list
-			corpus[i] %>%
+			authors[i] %>%
 				str_remove_all('[^\\w ,;]') %>%
 				str_replace_all('(?<=,)[ \\-\\w]+?(?:(?=;)|$)', function(x) {
 					paste0(str_extract_all(x, '\\b\\w')[[1]], collapse = '')
 				}) %>% str_replace_all(',', '_') %>% str_remove_all(' +')
 		} else { # IEEE style author list
-			corpus[i] %>%
+			authors[i] %>%
 				str_remove_all('[^\\w\\.;]') %>% # remove non letters and other characters
 				str_replace_all('[^;]+(?:(?=;)|$)', function(x) { # extract names between ;
 					str_replace(x, '([\\w \\.]+)\\.([\\w ]+)', '\\2_\\1') #use the rightmost dot to separate first and last names
@@ -110,7 +110,7 @@ tokenize_authors <- function(corpus) {
 #'
 #' Clean up the keyword fields in the records.
 #'
-#' @param corpus A vector of keywords fields from an annotation data set.
+#' @param keywords A vector of keywords fields from an annotation data set.
 #'
 #' @return The tokenized keyword list.
 #'
@@ -128,7 +128,7 @@ tokenize_keywords <- function(keywords) {
 #'
 #' Clean up the keyword fields in the records.
 #'
-#' @param corpus A vector of MESH keywords fields from an annotation data set.
+#' @param mesh A vector of MESH keywords fields from an annotation data set.
 #'
 #' @return The tokenized MESH keyword list.
 #'

### 2022-01-12 R/Rule_building.R

@@ -113,7 +113,7 @@ extract_rules <- function(session_name, rebuild_dtm = FALSE, vimp.threshold = 1.
 	)
 
 	if (!is.null(save_path)) {
-		write_rds(file.path(sessions_folder, session_name, file_name))
+		write_rds(save_path)
 	}
 
 	out

### 2022-01-12 R/Model.R
docs: fixed docs errors

@@ -159,7 +159,7 @@ create_training_set <- function(Records, min_freq = 0.05) {
 #'   backup will be used instead.
 #' @param rebuild If \code{TRUE}, retrain the model even if a model backup file
 #'   exists.
-#' @param um_trees,k,num_iterations_after_burn_in,run_in_sample,mem_cache_for_speed,use_missing_data,verbose
+#' @param num_trees,k,num_iterations_after_burn_in,run_in_sample,mem_cache_for_speed,use_missing_data,verbose
 #'    \code{\link[bartMachine:bartMachine]{bartMachine::bartMachine}()} specific
 #'   parameters.
 #' @param ... More argument to pass to
@@ -316,10 +316,10 @@ compute_BART_model <- function(train_data, Y, preds = NULL, save = FALSE,
 #'   reviewing manually no more than 250 records per iteration, since this
 #'   number is usually enough to provide enough information for the model.
 #' @param dup_session_action Similar to the argument in
-#'   \code{link{create_session}}. The default \code{fill} tells the function to
+#'   \code{\link{create_session}}. The default \code{fill} tells the function to
 #'   create a Session folder with the data in \code{file} if the session does
 #'   not exists, otherwise do nothing and keep adding Annotation files to the
-#'   session at each iteration. As in \code{link{create_session}}, \oode{add}
+#'   session at each iteration. As in \code{\link{create_session}}, \code{add}
 #'   creation a new session, \code{replace} replace the current session content,
 #'   \code{stop} raises an error.
 #' @param limits A list of condition that would prevent the function from
@@ -328,7 +328,7 @@ compute_BART_model <- function(train_data, Y, preds = NULL, save = FALSE,
 #'   number of CR iterations without new positive predictions;
 #'   \code{pos_target}: Number of positive matches found; \code{labeling_limit}
 #'   ratio of all records manually reviewed.
-#' @param compute_performance Use \code{link{estimate_performance}} to estimate
+#' @param compute_performance Use \code{\link{estimate_performance}} to estimate
 #'   total posterior sensitivity and efficiency based on a surrogate logistic
 #'   model. It is very expensive to compute so it is turned off by default.
 #' @param use_prev_labels If the \code{Rev_previous} is present in the data or a
@@ -393,7 +393,7 @@ enrich_annotation_file <- function(session_name,
 																	 	labeling_limit = NULL
 																	 ),
 																	 compute_performance = FALSE,
-																	 test_data = NULL,
[…]

### 2022-01-12 R/Record_management.R

@@ -450,8 +450,7 @@ join_records <- function(record_list) {
 #' records and join them. Some fields like the record keywords and source are
 #' joined between copies.
 #'
-#' @param record_list A list of data frames as created by
-#'   \code{\link{read_bib_files}()}.
+#' @param records A record data frame.
 #'
 #' @return A record data frame with no duplicated records.
 #'

### 2022-01-24 Manuscript/Manuscript.Rmd
small corrections

--- 2021-12-13 Manuscript/Manuscript.Rmd
@@
 authors:
-  - name: David S. Hippocampus
-    thanks: Use footnote for providing further information about author (webpage, alternative address)---*not* for acknowledging funding agencies. Optional.
-    department: Department of Computer Science
-    affiliation: Cranberry-Lemon University
-    location: Pittsburgh, PA 15213
-    email: hippo@cs.cranberry-lemon.edu
-  - name: Elias D. Striatum
-    department: Department of Electrical Engineering
-    affiliation: Mount-Sheikh University
-    location: Santa Narimana, Levand
-    email: stariate@ee.mount-sheikh.edu
+  - name: Angelo D'Ambrosio
+    department: Institute for Infection Prevention and Hospital Hygiene
+    affiliation: Freiburg University Hospital
+    location: Freiburg, Germany
+    email: angelo.d.ambrosio@uniklinik-freiburg.de; a.dambrosioMD@gmail.com
+  - name: Hajo Grundmann
+    department: Institute for Infection Prevention and Hospital Hygiene
+    affiliation: Freiburg University Hospital
+    location: Freiburg, Germany
+    email: hajo.grundmann@uniklinik-freiburg.de
+  - name: Tjibbe Donker
+    department: Institute for Infection Prevention and Hospital Hygiene
+    affiliation: Freiburg University Hospital
+    location: Freiburg, Germany
+    email: tjibbe.donker@uniklinik-freiburg.de
 abstract: |
@@
   The framework introduces three main tools:
-  an automatic citation search engine and manager that allows collecting records from multiple citation databases (PUBMED, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax;
-  a citation screening tool based on Bayesian active machine learning and natural language processing, which requires users feedback only on uncertain classifications to increase predictive accuracy iteratively;
-  a semi-automatic data-driven query generator to create new search queries from existing reviewed citation data sets.\
+  1) an automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax;
+  2) a citation screening tool based on Bayesian active machine learning and natural language processing, which requires users feedback only on uncertain classifications to increase predictive accuracy iteratively;
+  3) a semi-automatic data-driven query generator to create new search queries from existing reviewed citation data sets.\
   The framework was applied on an example topic performing citation collection and screening.

### 2022-01-24 Manuscript/Manuscript.tex
small corrections

@@
    \And
+    Hajo Grundmann
+   \\
+    Institute for Infection Prevention and Hospital Hygiene \\
+    Freiburg University Hospital \\
+  Freiburg, Germany \\
+  \texttt{\href{mailto:hajo.grundmann@uniklinik-freiburg.de}{\nolinkurl{hajo.grundmann@uniklinik-freiburg.de}}} \\
+   \And
     Tjibbe Donker
@@
   \texttt{\href{mailto:tjibbe.donker@uniklinik-freiburg.de}{\nolinkurl{tjibbe.donker@uniklinik-freiburg.de}}} \\
-   \And
-    Hajo Grundmann
-   \\
-    Institute for Infection Prevention and Hospital Hygiene \\
-    Freiburg University Hospital \\
-  Freiburg, Germany \\
-  \texttt{\href{mailto:hajo.grundmann@uniklinik-freiburg.de}{\nolinkurl{hajo.grundmann@uniklinik-freiburg.de}}} \\
   }
@@
 search engine and manager that allows collecting records from multiple
-citation databases (PUBMED, WOS, SCOPUS, EMBASE, IEEE) with a unified
+citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified
 query syntax; 2) a citation screening tool based on Bayesian active
@@
 it can be noticed how the distribution of the uncertain records shrinked
-(they concentrate in a shorter probability range) and shifted toward the
-negative zone as more positive matches are found and reviewed.
+(ie., gets concentrated in a shorter probability range) and shifted
+toward the negative zone as more positive matches are found and
+reviewed.
 
@@
 \caption{\label{tab:Table 2}\textbf{Table 2}.
-Results of the automatic classifaction and manual review rounds.
+Results of the automatic classification and manual review rounds.
 For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown.
@@
 documents.\\
-The engine was able to pick up the central concept of the research,
-i.e., ``patient transport'' or ``transfer'' through a ``network'' of
-``facility''ies that facilitates the ``spread'' of infections, and even
-one of the authors of this study (Donker T.) as well as the region of
-interest (``Orange County'') of another research group active on the
-topic of healthcare asociated pathogen spreading over hospital networks.
-Some terms were considered highly relevant for the BART models (e.g.,
-``Worker'' in 6th position out of more than 3800 terms considered)
-although in a simpler linear model their effect would be hardly
-significant (statistic: -1.21 s.e.); these are terms which are relevant
-only in conjunction with other terms but not by themselves, highlighting
-the extra predictive power brought by a non-linear model like BART.\\
+The engine was able to pick up the central concept of the research
+topic, i.e., ``patient transport'' or ``transfer'' through a ``network''
+of ``facility''ies that facilitates the ``spread'' of infections, and
+even one of the authors of this study (Donker T.) as well as the region
+of interest (``Orange County'') of another research group active on the
+topic of pathogen spreading over hospital networks. Some terms were
+considered highly relevant by the BART models (e.g., ``Worker'' in 6th
+position out of more than 3800 terms considered) although in a simpler
+linear model their effect would be hardly significant (statistic: -1.21
+s.e.); these are terms which are relevant only in conjunction with other
+terms but not by themselves, highlighting the extra predictive power
+brought by using advanced, non-linear machine learning.\\
 A more extensive set of terms is presented in Table 1 of Supplemental
@@
 82579 unique records were obtained. Once joined with the session 1
-records and duplicates removed, we obtained 98371 unique records, with
-just 1963 shared records between searches, that is the 2\%. The
+records and removal of duplicates, we obtained 98371 unique records,
+with just 1963 shared records between searches, that is the 2\%. The
 percentage of records shared by two or more source dropped to 22\%.
@@
 behaviour can be useful to spot classification errors and
-inconsistencies. Considering both sessions, 1333 records were reviewed
-and 107 (8.03\%) were found.
+inconsistencies. Considering both sessions, 1333 records were manually
+reviewed and 107 (8.03\%) confirmed positive matches were found.
 
@@
 engine was quite capable of internalizing the concepts behind the
-research topic A subsample of the terms is reported in Table 2 of
-Supplemental Material S2.
+research topic A subsample of the relevant terms used by the model in
+the second session is reported in Table 2 of Supplemental Material S2.
 
@@
 achieved via evaluation of sensibility and efficiency through a grid
-search on a validation set of 1200 completely manually labelled records.
-The best set of parameters suggested an initial input of 250 labelled
-records with 10x positive matches oversampling, an averaged ensemble of
-10 models, no bootstrapping and an uncertainty zone defined by the 98\%
-predictive interval. On the validation set, this combination of
-parameters reached a sensitivity of 98.8\% (81 / 82 positive matches
-found) and efficiency of 61.5\% (462 / 1200 records evaluated). The
-results of the hyperparameter tuning are reported in Table 3 of
-Supplemental Material S2. Figure 2 in Supplemental Material S2
-demonstrates that the positive record oversampling rate, the number of
-ensemble models and the size of the initial training set were the
-parameters that most impact performance.
+search on a validation set of 1200 manually labelled records. The
+analysis suggested the following combination of parameters as the best
+performing: an initial input of 250 labelled records with 10x positive
+matches oversampling, an averaged ensemble of 10 models, no
+bootstrapping and an uncertainty zone defined by the 98\% predictive
+interval. This combination of parameters was associated with a
+sensitivity of 98.8\% (81 / 82 positive matches found) and efficiency of
+61.5\% (462 / 1200 records evaluated). The detailed results of the
+hyperparameter tuning ananlysis are reported in Table 3 of Supplemental
+Material S2. Figure 2 in Supplemental Material S2 demonstrates that the
+positive record oversampling rate, the number of ensemble models and the
+size of the initial training set were the parameters that mostly
+impacted performance.
 
@@
 labels using only the lower bound of the record PPDs as predictor (see
-Methods for details). The surrogate model show the high predictive power
-of the scores produced by the classification model (Bayesian R2: 98.1\%
-{[}97.4\%, 98.3\%{]} for session 1 and 98.2\% {[}97.6\%, 98.3\%{]} for
-session 2).\\
+Methods for the details). The surrogate model showed the high predictive
+power of the scores produced by the classification model (Bayesian R2:
+98.1\% {[}97.4\%, 98.3\%{]} for session 1 and 98.2\% {[}97.6\%,
+98.3\%{]} for session 2).\\
 
@@
 evaluated manually to find the same number of positive matches without
-using a smart classification tool; some relevant record was found even
+using a smart classification tool, with some positive matches found
 close to the end of the heuristically ordered list of records.\\
@@
 {[}101, 108{]} for an estimated sensitivity of 100\% {[}93.5\%, 100\%{]}
-and efficiency of 95.7\% {[}95.3\%, 95.7\%{]}. In session 2 we observed
-a drop in the expected sensitivity, especially in the lower margin
-(97.3\% {[}73.8\%, 100\%{]}), due to the fact that as the number of
-records grows, even a small probability can translate, in the worst case
-scenario, into a relevant number of missed positive matches (145 in this
-case). To ascertain that no evident positives were missed, we evaluated
-100 more records between the unreviewed ones with the highest median
-predicted probability produced by the engine and found no additional
-positive matches.\\
+and efficiency of 95.6\% {[}95.3\%, 95.7\%{]}. In session 2 we observed
+a drop in the expected sensitivity, especially in the lower credibility
+boundary (97.3\% {[}72.8\%, 100\%{]}), due to the fact that as the
+number of records grows, even a small probability of being a positive
+match can translate, in the worst case scenario, into a relevant number
+of missed positive matches (147 in this case). To ascertain that no
+evident positives were missed, we evaluated 100 more records between the
+unreviewed ones with the highest median predicted probability produced
+by the engine and found no additional positive matches.\\
 
@@
 \cellcolor{gray!6}{Total records} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{98371}\\
-Reviewed records (\% over total records) & 761 (4.29\%) & 1316 (1.34\%)\\
-\cellcolor{gray!6}{Expected efficiency (over random) [trunc. 90\% PrI]} & \cellcolor{gray!6}{95.7\% [95.3\%, 95.7\%]} & \cellcolor{gray!6}{98.6\% [98.2\%, 98.7\%]}\\
+Reviewed records (\% over total records) & 766 (4.31\%) & 1333 (1.36\%)\\
+\cellcolor{gray!6}{Expected efficiency (over random) [trunc. 90\% PrI]} & \cellcolor{gray!6}{95.6\% [95.3\%, 95.7\%]} & \cellcolor{gray!6}{98.6\% [98.1\%, 98.6\%]}\\
 Observed positive matches (\% over total records) & 101 (0.57\%) & 107 (0.11\%)\\
-\cellcolor{gray!6}{Predicted positive matches [trunc. 90\% PrI]} & \cellcolor{gray!6}{101 [101, 108]} & \cellcolor{gray!6}{110 [107, 145]}\\
+\cellcolor{gray!6}{Predicted positive matches [trunc. 90\% PrI]} & \cellcolor{gray!6}{101 [101, 108]} & \cellcolor{gray!6}{110 [107, 147]}\\
 \addlinespace
-Expected sensitivity [trunc. 90\% PrI] & 100\% [93.5\%, 100\%] & 97.3\% [73.8\%, 100\%]\\
+Expected sensitivity [trunc. 90\% PrI] & 100\% [93.5\%, 100\%] & 97.3\% [72.8\%, 100\%]\\
 \cellcolor{gray!6}{Simple Model $R^2$ [90\% CrI]} & \cellcolor{gray!6}{98.1\% [97.4\%, 98.3\%]} & \cellcolor{gray!6}{98.2\% [97.6\%, 98.3\%]}\\
@@
 (SRA) and helpers (SRH) tools (A. M. Cohen et al. 2006, 2010; Ananiadou
-et al. 2009; O'Mara-Eves et al. 2015). This framework joins standard
-approaches and uses ad-hoc solutions to deal with common SRA issues. By
-freely sharing the tool as an open-source R package and by following a
-modular design, we tried to adopt some of the so-called Vienna
-Principles advocated by the International Collaboration for the
+et al. 2009; O'Mara-Eves et al. 2015). This framework implements
+standard approaches and uses ad-hoc solutions to deal with common SRA
+issues. By freely sharing the tool as an open-source R package and by
+following a modular design, we tried to adopt some of the so-called
+Vienna Principles advocated by the International Collaboration for the
 Automation of Systematic Reviews (ICASR) (E. Beller et al. 2018).\\
@@
 Electrical and Electronics Engineers) as well as process manually
-downloaded results from both the mentioned and other (SCOPUS, EMBASE)
-databases. In comparison, most SRH tools, commercial or free to use,
-rely either on internal databases (e.g., Mendeley
-\url{https://www.mendeley.com/}) sometimes focusing just on a particular
-topic (Visser 2010) or on a single external data source (Thomas and
-Brunton 2007; Poulter et al. 2008; Soto, Przybyła, and Ananiadou
-2019).\\
+downloaded results from both the two more (SCOPUS, EMBASE) databases. In
+comparison, most SRH tools, commercial or free to use, rely either on
+internal databases (e.g., Mendeley \url{https://www.mendeley.com/})
+sometimes focusing just on a particular topic (Visser 2010) or on a
+single external data source (Thomas and Brunton 2007; Poulter et al.
+2008; Soto, Przybyła, and Ananiadou 2019).\\
 Mixing different databases is fundamental to have a more comprehensive
@@
 2005; Woods and Trewheellar 1998): in our results, 18.7\% of the
-positive matches found were unique for one of the different data
-sources, and no positive record was present in all of them (data not
-shown).\\
+positive matches found only in one of the different data sources, and no
+positive record was present in all of them (data not shown).\\
 The online search algorithms are efficient enough to manage tens of
 thousands of search results, using various expedients to overcome the
-limitations of the queried databases in terms of traffic and download
-quota. The results are then automatically organized, deduplicated and
-arranged by ``simple query ordering'' in a uniform corpus. The
-preliminary ordering allow to increase the positivity rate in the
-initial training set (Wallace, Small, et al. 2010).\\
-
-For the framework's record classification module we employed an active
+limitations of online citation databases in terms of traffic and
+download quotas. The results are then automatically organized,
+deduplicated and arranged by ``simple query ordering'' in a uniform
+corpus. The preliminary ordering allows to increase the positivity rate
+in the initial training set (Wallace, Small, et al. 2010).\\
+
+For the framework's record classification module, we employed an active
 machine learning approach Miwa et al. (2014) based on the best practices
-from other SRA studies, bringing further improvements at various
+from other SRA studies but also bringing further improvements at various
 levels.\\
@@
 times, we decided to use ten replicas, the lower value after which
-showed performance stabilisation during the hyperparameter evaluation.\\
+performance stabilised during the hyperparameter evaluation.\\
 We also investigated whether bootstrapping between replications (Breiman
 1996) would improve performance, but, contrary to theory (Díez-Pastor et
-al. 2015), it was demonstrated to be slightly detrimental (Supplemental
-Material S2) compared to simple ensembling.\\
+al. 2015), it appeared to be slightly detrimental in our case
+(Supplemental Material S2) compared to simple ensembling.\\
 
@@
 et al. 2014; Zhu et al. 2010). The parameters our algorithm needs are
-instead quite general and non task-specific, like the PPD intervals
-based on which the uncertainty zone is built ,and the maximum number of
+instead general and non task-specific, like the PPD intervals based on
+which the uncertainty zone is built, and the maximum number of
 iterations with no positive matches after which a session is concluded;
@@
 variations in these parameters and we expect the default values to
-preform well on most datasets.\\
+perform well on most datasets.\\
 Since researchers are asked to review both records with a positive
@@
 algorithm. Creating an efficient and efficacious search query is a
-complex task (Lefebvre et al. 2011; Hammerstrøm et al. 2010) since it
+complex task (Lefebvre et al. 2011; Hammerstrøm et al. 2010); it
 requires building a combination of positive and negative terms to
@@
 trees (Blanco-Justicia and Domingo-Ferrer 2019; Moore et al. 2018) built
-on the BART ensemble PPD with a human review step and an
+on the BART ensemble PPD, with a human review step and an
 efficiency-driven query builder. The aim is to generate a second query
@@
 tool is the composition of many solutions and the general idea of
-Bayesian active machine learning and uncertainty zone. However, each of
-its components could benefit considerably from the recent improvements
-in text mining.\\
+Bayesian active machine learning and the exploit of the derived
+uncertainty in predictions. However, each of its components could
+benefit considerably from the recent improvements in text mining.\\
 For example, our text processing approach is quite simple, based on the
@@
 hypothesise that tree-based classification algorithms like BART are
-robust enough not to need such operations. Word embedding could be worth
-exploring: this technique transforms terms in semantic vectors derived
-from the surrounding text Minaee et al. (2021) and could be used to
-eliminate semantically redundant terms or differentiate identical terms
-with different meanings given the context. Another option would be to
-employ unsupervised learning models like Latent Dirichlet Analysis,
-Latent Semantic Analysis (Pavlinek and Podgorelec 2017; Q. Chen, Yao,
-and Yang 2016; Landauer, Foltz, and Laham 1998) or graph-of-word
-techniques (Ohsawa, Benson, and Yachida 1998; Francois Rousseau 2015) to
-extract topics to enrich the feature space.\\
+robust enough not to need such operations. Word embedding could be
+instead worth exploring: this technique transforms terms in semantic
+vectors derived from the surrounding text Minaee et al. (2021) and could
+be used to eliminate semantically redundant terms or differentiate
+identical terms with different meanings given the context. Another
+option would be to employ unsupervised learning models like Latent
+Dirichlet Analysis, Latent Semantic Analysis (Pavlinek and Podgorelec
+2017; Q. Chen, Yao, and Yang 2016; Landauer, Foltz, and Laham 1998) or
+graph-of-word techniques (Ohsawa, Benson, and Yachida 1998; Francois
+Rousseau 2015) to extract topics to enrich the feature space.\\
 Our classification algorithm can be implemented with any Bayesian

### 2022-01-24 Manuscript/Manuscript_Discussion.Rmd
small corrections

@@
 We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
-This framework joins standard approaches and uses ad-hoc solutions to deal with common SRA issues.
+This framework implements standard approaches and uses ad-hoc solutions to deal with common SRA issues.
 By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
@@
 
-The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases.
+The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the two more (SCOPUS, EMBASE) databases.
 In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
 Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
-in our results, 18.7% of the positive matches found were unique for one of the different data sources, and no positive record was present in all of them (data not shown).\
-The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the queried databases in terms of traffic and download quota.
+in our results, 18.7% of the positive matches found only in one of the different data sources, and no positive record was present in all of them (data not shown).\
+The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of online citation databases in terms of traffic and download quotas.
 The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
-The preliminary ordering allow to increase the positivity rate in the initial training set [@wallace2010active].\
+The preliminary ordering allows to increase the positivity rate in the initial training set [@wallace2010active].\
 
-For the framework's record classification module we employed an active machine learning approach [@settles2009active, @miwa2014reducing] based on the best practices from other SRA studies, bringing further improvements at various levels.\
+For the framework's record classification module, we employed an active machine learning approach [@settles2009active, @miwa2014reducing] based on the best practices from other SRA studies but also bringing further improvements at various levels.\
 The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
@@
 On the other hand, just imposing robust uninformative priors against extreme predictions would have decreased variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
-Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which showed performance stabilisation during the hyperparameter evaluation.\
-We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory [@diez2015diversity], it was demonstrated to be slightly detrimental (Supplemental Material S2) compared to simple ensembling.\
+Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which performance stabilised during the hyperparameter evaluation.\
+We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory [@diez2015diversity], it appeared to be slightly detrimental in our case (Supplemental Material S2) compared to simple ensembling.\
 
@@
 This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
-The parameters our algorithm needs are instead quite general and non task-specific, like the PPD intervals based on which the uncertainty zone is built ,and the maximum number of iterations with no positive matches after which a session is concluded;
-the hyperparameter evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to preform well on most datasets.\
+The parameters our algorithm needs are instead general and non task-specific, like the PPD intervals based on which the uncertainty zone is built, and the maximum number of iterations with no positive matches after which a session is concluded;
+the hyperparameter evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to perform well on most datasets.\
 Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\
@@
 The last module of our framework is a data-driven query generation algorithm.
-Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to review.
-Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD with a human review step and an efficiency-driven query builder.
+Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching];
+it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to review.
+Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD, with a human review step and an efficiency-driven query builder.
 The aim is to generate a second query that helps find records missed during the first session search.
@@
 We designed it to easily implement complete independence of the main modules in future iterations, making it possible for users to add custom features like citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
-We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general idea of Bayesian active machine learning and uncertainty zone.
+We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general idea of Bayesian active machine learning and the exploit of the derived uncertainty in predictions.
 However, each of its components could benefit considerably from the recent improvements in text mining.\
@@
 It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operations.
-Word embedding could be worth exploring:
+Word embedding could be instead worth exploring:
 this technique transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep] and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.

### 2022-01-24 Manuscript/Manuscript_Results.Rmd
small edits to Results table
small corrections

@@
 1 of the Supplemental Material S2, showing the mixture distribution of the PPDs of the records, specifically for the reviewed positive and negative records, and for records that need manual review after the classification step:
-it can be noticed how the distribution of the uncertain records shrinked (they concentrate in a shorter probability range) and shifted toward the negative zone as more positive matches are found and reviewed.
+it can be noticed how the distribution of the uncertain records shrinked (ie., gets concentrated in a shorter probability range) and shifted toward the negative zone as more positive matches are found and reviewed.
 
 `r print_table(annotation_results, caption = "**Table 2**.
-Results of the automatic classifaction and manual review rounds.
+Results of the automatic classification and manual review rounds.
 For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown.
@@
 The "&" indicates nc-ngrams, i.e., terms strongly co-occurrent in the documents.\
-The engine was able to pick up the central concept of the research, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) as well as the region of interest ("Orange County") of another research group active on the topic of healthcare asociated pathogen spreading over hospital networks.
-Some terms were considered highly relevant for the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
-these are terms which are relevant only in conjunction with other terms but not by themselves, highlighting the extra predictive power brought by a non-linear model like BART.\
+The engine was able to pick up the central concept of the research topic, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) as well as the region of interest ("Orange County") of another research group active on the topic of pathogen spreading over hospital networks.
+Some terms were considered highly relevant by the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
+these are terms which are relevant only in conjunction with other terms but not by themselves, highlighting the extra predictive power brought by using advanced, non-linear machine learning.\
 A more extensive set of terms is presented in Table 1 of Supplemental Material S2.
@@
 After removal of duplicates, `r source_summary$Total$Records` unique records were obtained.
-Once joined with the session 1 records and duplicates removed, we obtained `r nrow(records_s2)` unique records, with just `r session_diff` shared records between searches, that is the `r percent(session_diff / source_list[['All Sessions']]$Total$Records)`.
+Once joined with the session 1 records and removal of duplicates, we obtained `r nrow(records_s2)` unique records, with just `r session_diff` shared records between searches, that is the `r percent(session_diff / source_list[['All Sessions']]$Total$Records)`.
 The percentage of records shared by two or more source dropped to `r percent(1 - source_distr[1])`.
@@
 This behaviour can be useful to spot classification errors and inconsistencies.
-Considering both sessions, `r tot_reviewed` records were reviewed and `r num_last_positives` (`r percent(num_last_positives / tot_reviewed)`) were found.
+Considering both sessions, `r tot_reviewed` records were manually reviewed and `r num_last_positives` (`r percent(num_last_positives / tot_reviewed)`) confirmed positive matches were found.
 
 Again, the evaluation of the inclusion rate of the terms showed that the engine was quite capable of internalizing the concepts behind the research topic
-A subsample of the terms is reported in Table 2 of Supplemental Material S2.
+A subsample of the relevant terms used by the model in the second session is reported in Table 2 of Supplemental Material S2.
 
@@
 
-As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a validation set of 1200 completely manually labelled records.
-The best set of parameters suggested an initial input of 250 labelled records with 10x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
-On the validation set, this combination of parameters reached a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
-The results of the hyperparameter tuning are reported in Table 3 of Supplemental Material S2.
-Figure 2 in Supplemental Material S2 demonstrates that the positive record oversampling rate, the number of ensemble models and the size of the initial training set were the parameters that most impact performance.
+As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a validation set of 1200 manually labelled records.
+The analysis suggested the following combination of parameters as the best performing: an initial input of 250 labelled records with 10x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
+This combination of parameters was associated with a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
+The detailed results of the hyperparameter tuning ananlysis are reported in Table 3 of Supplemental Material S2.
+Figure 2 in Supplemental Material S2 demonstrates that the positive record oversampling rate, the number of ensemble models and the size of the initial training set were the parameters that mostly impacted performance.
 
@@
 
-# Creating these summary is quite demanding, so it's better to cache them
+# Creating these summaries is quite demanding, so it's better to cache them
 # explicitly
@@
 
-To evaluate the theoretical performance of the engine, a surrogate Bayesian logistic regression model was trained on the manually reviewed labels using only the lower bound of the record PPDs as predictor (see Methods for details).
-The surrogate model show the high predictive power of the scores produced by the classification model (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2).\
+To evaluate the theoretical performance of the engine, a surrogate Bayesian logistic regression model was trained on the manually reviewed labels using only the lower bound of the record PPDs as predictor (see Methods for the details).
+The surrogate model showed the high predictive power of the scores produced by the classification model (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2).\
 
@@
 the median of surrogate models' cumulative predictive distributions matches quite well the actual number of positive records found.
-It is striking how many more records would have needed to be evaluated manually to find the same number of positive matches without using a smart classification tool;
-some relevant record was found even close to the end of the heuristically ordered list of records.\
+It is striking how many more records would have needed to be evaluated manually to find the same number of positive matches without using a smart classification tool,
+with some positive matches found close to the end of the heuristically ordered list of records.\
 
@@
 In session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.
-In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows, even a small probability can translate, in the worst case scenario, into a relevant number of missed positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
+In session 2 we observed a drop in the expected sensitivity, especially in the lower credibility boundary (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows, even a small probability of being a positive match can translate, in the worst case scenario, into a relevant number of missed positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
 To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no additional positive matches.\
@@
 Finally the median Bayesian $R^2$ [90% CrI] of the logistic models is reported.
-PrI: Predictive Intervals; CrI: Credibility Intervals', allow_math = TRUE, label = "Table 3")`
+PrI: Predictive Intervals; CrI: Credibility Intervals.', allow_math = TRUE, label = "Table 3")`
 
-```{r performance plot, cache = FALSE, fig.width=6, fig.height=2.5, fig.cap="**Figure 2**.
+```{r performance plot, cache = FALSE, fig.width=7.5, fig.height=4.5, fig.cap="**Figure 2**.
 Observed cumulative number of positive matches (red dots) sorted by simple query ordering.

### 2022-02-01 Manuscript/S1.Protocol.Rmd
minor edit
update "New search session" section

@@
 
-## Acquisition of the records
+## Acquisition of the citaion data
 
@@
 
-Once the new query was generated, a second search session called `Session2` was created, using the strategy described in the protocol.
+Once the new query was generated, a second search session can be created, using the strategy described in the protocol.
 Due to the lower specificity of the second query, particular care may be needed in managing the far larger amount of records:
@@
 
-Once the new records are collected, `enrich_annotation_file('Session2')` (or any other new session name) can be used to perform the new CR iterations.
-It may be possible that during the first CR iteration, the number of records requiring manual review is significant:
-we suggest evaluating still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.
+Once the new records are collected are manually collected for databases without an API access, a new search can be performed.
+The following code describe how to create a new session.
+Keep in mind to give the session a new name and to import the annotated records from the last session when generating the new annotation file.
+
+```{r new annotation session}
+
+# Repeat the search with the new query, giving a different Session name not to
+# override previous records
+journal <- perform_search_session(
+	query = query, year_query = year_filter,
+	session_name = 'Session2', query_name = 'Query1',
+	records_folder = 'Records',
+	journal = 'Session_journal.csv')
+
+# Get the path to the annotated data in the previous session
+previousAnnotations <- get_session_files('Session1')$Annotations %>% last()
+
+# Create the new annotation file passing the folder with the new records
+Annotation_data <- create_annotation_file(
+	file.path('Records', 'Session2'),
+	reorder_query = query,
+	prev_records = previousAnnotations
+)
+
+# Create the new annotation session
+create_session(Annotation_data, session_name = "Session2")
+
+```
+
+Once the new annotation session data is created, `enrich_annotation_file('Session2')` can be used to perform the CR iterations.
+It may be possible that during the first CR iteration, the number of records requiring manual review is very large:
+we suggest evaluating still not more than 250, setting the `stop_on_unreviewed` argument to `FALSE` to proceed in the automatic classification even if some uncertain records from the precedent iteration are still unreviewed.
 

### 2022-02-01 Manuscript/S1.Protocol.Rmd
style up

@@
 )
-
 ```
@@
 
-source('R/Setup.R') # Load the framework
+source("R/Setup.R") # Load the framework
 
@@
 # period.
-year_filter <- '2010-2020'
-
+year_filter <- "2010-2020"
 ```
@@
 ```{r secrets}
-options(baysren.ieee_api_key = 'your-ieee-api-key')
-options(baysren.ncbi_api_key = 'your-ncbi-api-key')
-options(baysren.wos_api_key = 'your-wos-api-key')
+options(baysren.ieee_api_key = "your-ieee-api-key")
+options(baysren.ncbi_api_key = "your-ncbi-api-key")
+options(baysren.wos_api_key = "your-wos-api-key")
 ```
@@
   query = query, year_query = year_filter,
-	session_name = 'Session1', query_name = 'Query1',
-	records_folder = 'Records',
-	journal = 'Session_journal.csv')
-
+  session_name = "Session1", query_name = "Query1",
+  records_folder = "Records",
+  journal = "Session_journal.csv"
+)
 ```
@@
 Annotation_data <- extract_source_file_paths(journal) %>%
-
   # Read record files. Will parse them if raw data is downloaded manually (not
@@
   read_bib_files() %>%
-
   # Join a list of records into one dataframe, solving duplicated records
   join_records() %>%
-
   # Order records by the relative frequency of the query terms in the title +
@@
   order_by_query_match(query) %>%
-
   # Add fields for the manual classification
@@
   )
-
 ```
@@
 # or specific record file folders
-input <- file.path('Records', 'Session1', 'Query1')
+input <- file.path("Records", "Session1", "Query1")
 
 # or parent folders, since it searches for files recursively
-input <- 'Records'
+input <- "Records"
 
@@
 Annotation_data <- create_annotation_file(input, reorder_query = query)
-
 ```
@@
 # Create the first session
-create_session(Annotation_data, session_name = 'Session1')
+create_session(Annotation_data, session_name = "Session1")
 ```
@@
   query = query, year_query = year_filter,
-	session_name = 'Session1', query_name = 'Query1',
-	journal = 'Session_journal.csv') %>%
-
+  session_name = "Session1", query_name = "Query1",
+  journal = "Session_journal.csv"
+) %>%
   # return the record file paths
   extract_source_file_paths() %>%
-
   # read, join, reorder records and save them in the Sessions folder
   create_annotation_file(reorder_query = query) %>%
-
   # Create a new session with the records
-	create_session(session_name = 'Session1')
+  create_session(session_name = "Session1")
 ```
@@
 ```{r automatic annotation}
-New_annotations <- enrich_annotation_file('Session1')
+New_annotations <- enrich_annotation_file("Session1")
 ```
@@
 
-candidate_queries <- extract_rules('Session1')
+candidate_queries <- extract_rules("Session1")
 
@@
 # have no info about the session it's working on.
-selection_set_file <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx')
+selection_set_file <- file.path("Sessions", "Session1", "Selected_rules.xlsx")
 
@@
   target_data = SpecificDTM,
-	save_path = selection_set_file)
+  save_path = selection_set_file
+)
 
@@
 
-simplified_rules <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx') %>%
+simplified_rules <- file.path("Sessions", "Session1", "Selected_rules.xlsx") %>%
   import_data() %>%
@@
 new_query <- rules_to_query(simplified_rules)
-
 ```
@@
 ((antimicrobial resistance) OR (healthcare infection))"
-
 ```
@@
   query = query, year_query = year_filter,
-	session_name = 'Session2', query_name = 'Query1',
-	records_folder = 'Records',
-	journal = 'Session_journal.csv')
+  session_name = "Session2", query_name = "Query1",
+  records_folder = "Records",
+  journal = "Session_journal.csv"
+)
 
 # Get the path to the annotated data in the previous session
-previousAnnotations <- get_session_files('Session1')$Annotations %>% last()
+previousAnnotations <- get_session_files("Session1")$Annotations %>% last()
 
@@
 Annotation_data <- create_annotation_file(
-	file.path('Records', 'Session2'),
+  file.path("Records", "Session2"),
   reorder_query = query,
@@
 create_session(Annotation_data, session_name = "Session2")
-
 ```
@@
 Grid_search <- perform_grid_evaluation(
-	records, sessions_folder = 'Grid_Search',
+  records,
+  sessions_folder = "Grid_Search",
   prev_classification = records,
@@
     c(.05, .5, .95),
-		c(.01, .5, .99))
+    c(.01, .5, .99)
+  )
 )

### 2022-02-01 Manuscript/Manuscript.Rmd
file style up

@@
 out <- unlist(lapply(c(
-	'Manuscript_Introduction.Rmd',
-	'Manuscript_Methods.Rmd',
-	'Manuscript_Results.Rmd',
-	'Manuscript_Discussion.Rmd'
+  "Manuscript_Introduction.Rmd",
+  "Manuscript_Methods.Rmd",
+  "Manuscript_Results.Rmd",
+  "Manuscript_Discussion.Rmd"
 ), knitr::knit_child, quiet = TRUE))
 
-cat(out, sep = '\n')
-
+cat(out, sep = "\n")
 ```

### 2022-02-01 Manuscript/Manuscript_Results.Rmd
file style up

@@
 
-wd <- ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd())
+wd <- ifelse(basename(getwd()) == "Manuscript", dirname(getwd()), getwd())
 
@@
 
-options(knitr.kable.NA = '')
+options(knitr.kable.NA = "")
 
@@
 ```{r load framework, cache.rebuild=TRUE, include=FALSE}
-source(file.path('R', 'Setup.R'), local = knitr::knit_global())
+source(file.path("R", "Setup.R"), local = knitr::knit_global())
 
@@
 options(baysren.probs = c(.05, .5, .95))
-options(baysren.sessions_folder = 'Sessions')
+options(baysren.sessions_folder = "Sessions")
 ```
@@
 
-session1_files <- get_session_files('Session1')
-session2_files <- get_session_files('Session2')
+session1_files <- get_session_files("Session1")
+session2_files <- get_session_files("Session2")
 
@@
 annotation_results <- summarise_annotations_by_session(remove_raw_data = TRUE)
-
 ```
@@
 
-first_query <- import_data('Session_journal.csv') %>% 
-    filter(Session_ID == 'Session1') %>% 
+first_query <- import_data("Session_journal.csv") %>%
+  filter(Session_ID == "Session1") %>%
   with(Query[1])
@@
 
-all_records <- source_summary[names(source_summary) != 'Total'] %>%
-	sapply('[[', 'Records') %>% sum()
+all_records <- source_summary[names(source_summary) != "Total"] %>%
+  sapply("[[", "Records") %>%
+  sum()
 
@@
 
-session_summary <- summarise_annotations('Session1', remove_raw_data = FALSE)
+session_summary <- summarise_annotations("Session1", remove_raw_data = FALSE)
 
-num_first_labeling <- session_summary[1,]$tot_reviewed_
+num_first_labeling <- session_summary[1, ]$tot_reviewed_
 
-num_first_positives <- session_summary[1,]$Positives
-num_first_negatives <- session_summary[1,]$Negatives
+num_first_positives <- session_summary[1, ]$Positives
+num_first_negatives <- session_summary[1, ]$Negatives
 
@@
 
-var_importance <- extract_var_imp('Session1') %>%
+var_importance <- extract_var_imp("Session1") %>%
   format_var_imp(as_data_frame = FALSE) %>%
-	paste(collapse = ', ')
-
+  paste(collapse = ", ")
 ```
@@
 ```{r session 2}
-new_query <- import_data('Session_journal.csv') %>% 
-    filter(Session_ID == 'Session2') %>% 
+new_query <- import_data("Session_journal.csv") %>%
+  filter(Session_ID == "Session2") %>%
   with(Query[1])
@@
 
-session_summary <- summarise_annotations('Session2', remove_raw_data = FALSE)
+session_summary <- summarise_annotations("Session2", remove_raw_data = FALSE)
 
@@
 # explicitly
-perf_file <- file.path('Manuscript', 'Performance_summary.rds')
+perf_file <- file.path("Manuscript", "Performance_summary.rds")
 
@@
   Performance <- list(
-		s1 = get_session_files('Session1')$Annotations %>% last() %>%
+    s1 = get_session_files("Session1")$Annotations %>% last() %>%
       import_data() %>% estimate_performance(),
-		s2 = get_session_files('Session2')$Annotations %>% last() %>%
+    s2 = get_session_files("Session2")$Annotations %>% last() %>%
       import_data() %>% estimate_performance()
@@
   write_rds(Performance, perf_file)
-
 } else {
@@
 Performance$s1$plot +
-	guides(color = 'none', fill = 'none') +
-	ggtitle('Session 1') +
+  guides(color = "none", fill = "none") +
+  ggtitle("Session 1") +
   Performance$s2$plot +
-	ggtitle('Session 2') +
+  ggtitle("Session 2") +
   theme(
@@
   theme(
-		legend.position = 'bottom'
+    legend.position = "bottom"
   ) &
-	plot_layout(guides = 'collect')
+  plot_layout(guides = "collect")
 ```

### 2022-02-01 Manuscript/S2.Additional_outputs.Rmd
file style up

@@
 ```{r load framework, cache.rebuild=TRUE}
-source(file.path('R', 'Setup.R'))
+source(file.path("R", "Setup.R"))
 
@@
 
-s1_plot <- plot_predictive_densities('Session1')
+s1_plot <- plot_predictive_densities("Session1")
 
-s2_plot <- plot_predictive_densities('Session2')
+s2_plot <- plot_predictive_densities("Session2")
 
 s1_plot +
-    guides(color = 'none', fill = 'none') +
-    ggtitle('Session 1') +
+  guides(color = "none", fill = "none") +
+  ggtitle("Session 1") +
   s2_plot +
-    ggtitle('Session 2') +
+  ggtitle("Session 2") +
   theme(
@@
   theme(
-        legend.position = 'bottom'
+    legend.position = "bottom"
   ) &
-    plot_layout(guides = 'collect')
+  plot_layout(guides = "collect")
 ```
@@
 
-var_importance_s1 <- extract_var_imp('Session1', num_vars = n_terms, score_filter = 0) %>%
+var_importance_s1 <- extract_var_imp("Session1", num_vars = n_terms, score_filter = 0) %>%
   format_var_imp(as_data_frame = TRUE)
 
-var_importance_s2 <- extract_var_imp('Session1', num_vars = n_terms, score_filter = 0) %>%
+var_importance_s2 <- extract_var_imp("Session1", num_vars = n_terms, score_filter = 0) %>%
   format_var_imp(as_data_frame = TRUE)
@@
 grid_out_params <- grid_out$best_by_rule %>%
-	mutate(Score = str_remove(Score, ' .+')) %>% 
+  mutate(Score = str_remove(Score, " .+")) %>%
   rename(
@@
 
-print(grid_out$plot & labs(y = 'Sens. x. Eff.'))
-
+print(grid_out$plot & labs(y = "Sens. x. Eff."))
 ```

### 2022-02-03 Manuscript/Manuscript.Rmd
uodate abstract

@@
 abstract: |
-  The exponential growth in scientific production makes its summarisation through secondary literature exceedingly demanding in terms of time and human resources.
-  We introduce a new open-source framework that significantly increases efficiency during the citation collection and screening phases of systematic reviews.\
+  The exponential and prolific growth of published original scientific contributions makes secondary literature abridgements increasingly demanding.
+  We introduce a new open-source framework for systematic reviews that significantly reduces time and human resource allocation for text identification, collection, and screening of scientific literature.\
   The framework introduces three main tools:
   1) an automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax;
-  2) a citation screening tool based on Bayesian active machine learning and natural language processing, which requires users feedback only on uncertain classifications to increase predictive accuracy iteratively;
+  2) a citation screening tool based on Bayesian active machine learning and natural language processing, which requires users feedback only on uncertain classifications to iteratively increase predictive accuracy;
   3) a semi-automatic data-driven query generator to create new search queries from existing reviewed citation data sets.\
-  The framework was applied on an example topic performing citation collection and screening.
-  We estimated median posterior Sensitivity and Efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of possibly missed relevant matches in the unreviewed records.\
+  The framework was tested on an example topic to perform citation collection and screening of related scientific production.
+  To evaluate the performance of the active machine learning classifier,
+  we estimated the median posterior Sensitivity and Efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of potentially relevant matches among the records not manually reviewed.\
   17755 unique records were collected through the framework citation manager;
-  101 over 766 records were found to be relevant after manual evaluation, while the rest were excluded by the automatic classification;
-  the expected Efficiency was 95.7% [95.3%, 95.7%] for a Sensitivity of 100% [93.5%, 100%].
-  A new search query was generated from the labelled dataset, and 82579 more records were collected.
-Only 567 records required human review after the automatic screening, and six additional positive matches were found.
-  Including the additional records, the overall expected Sensitivity dropped to 97.3% [73.8%, 100%] while the Efficiency raised to 98.6% [98.2%, 98.7%].\
-  The framework can significantly reduce human resources requirements for systematic reviews by simplifying citation collection and screening while demonstrating exceptional sensitivity even on large data sets.
+  101 over 766 records were found to be relevant after manual evaluation,
+  while the rest were excluded by automatic classification;
+  the expected Efficiency was 95.7% [95.3%, 95.7%] with a Sensitivity of 100% [93.5%, 100%].\
+  An additional search query generated from the labelled dataset,
+  retrieved 82579 additional records of which only 567 records required human review and six additional positive matches were retrieved.
+  Including the additional records, the overall expected Sensitivity decreased to 97.3% [73.8%, 100%] while the Efficiency achieved was 98.6% [98.2%, 98.7%].\
+  For large studies, the developed framework significantly reduces workload, human effort and error,
+  simplifying citation collection and screening with exceptional sensitivity,
+  hence improving the standardization and repeatability of systematic reviews.
 keywords:

### 2022-02-03 Manuscript/Manuscript.tex
uodate abstract

@@
 \begin{abstract}
-The exponential growth in scientific production makes its summarisation
-through secondary literature exceedingly demanding in terms of time and
-human resources. We introduce a new open-source framework that
-significantly increases efficiency during the citation collection and
-screening phases of systematic reviews.\\
+The exponential and prolific growth of published original scientific
+contributions makes secondary literature abridgements increasingly
+demanding. We introduce a new open-source framework for systematic
+reviews that significantly reduces time and human resource allocation
+for text identification, collection, and screening of scientific
+literature.\\
 The framework introduces three main tools: 1) an automatic citation
@@
 machine learning and natural language processing, which requires users
-feedback only on uncertain classifications to increase predictive
-accuracy iteratively; 3) a semi-automatic data-driven query generator to
+feedback only on uncertain classifications to iteratively increase
+predictive accuracy; 3) a semi-automatic data-driven query generator to
 create new search queries from existing reviewed citation data sets.\\
-The framework was applied on an example topic performing citation
-collection and screening. We estimated median posterior Sensitivity and
-Efficiency {[}90\% Credible Intervals{]} using Bayesian simulation to
-predict the distribution of possibly missed relevant matches in the
-unreviewed records.\\
+The framework was tested on an example topic to perform citation
+collection and screening of related scientific production. To evaluate
+the performance of the active machine learning classifier, we estimated
+the median posterior Sensitivity and Efficiency {[}90\% Credible
+Intervals{]} using Bayesian simulation to predict the distribution of
+potentially relevant matches among the records not manually reviewed.\\
 17755 unique records were collected through the framework citation
 manager; 101 over 766 records were found to be relevant after manual
-evaluation, while the rest were excluded by the automatic
-classification; the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]}
-for a Sensitivity of 100\% {[}93.5\%, 100\%{]}. A new search query was
-generated from the labelled dataset, and 82579 more records were
-collected. Only 567 records required human review after the automatic
-screening, and six additional positive matches were found. Including the
-additional records, the overall expected Sensitivity dropped to 97.3\%
-{[}73.8\%, 100\%{]} while the Efficiency raised to 98.6\% {[}98.2\%,
-98.7\%{]}.\\
-The framework can significantly reduce human resources requirements for
-systematic reviews by simplifying citation collection and screening
-while demonstrating exceptional sensitivity even on large data sets.
+evaluation, while the rest were excluded by automatic classification;
+the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]} with a
+Sensitivity of 100\% {[}93.5\%, 100\%{]}.\\
+An additional search query generated from the labelled dataset,
+retrieved 82579 additional records of which only 567 records required
+human review and six additional positive matches were retrieved.
+Including the additional records, the overall expected Sensitivity
+decreased to 97.3\% {[}73.8\%, 100\%{]} while the Efficiency achieved
+was 98.6\% {[}98.2\%, 98.7\%{]}.\\
+For large studies, the developed framework significantly reduces
+workload, human effort and error, simplifying citation collection and
+screening with exceptional sensitivity, hence improving the
+standardization and repeatability of systematic reviews.
 \end{abstract}

### 2022-02-19 Manuscript/Manuscript.Rmd
English proof reading and better number formatting

@@
   We introduce a new open-source framework for systematic reviews that significantly reduces time and human resource allocation for text identification, collection, and screening of scientific literature.\
-  The framework introduces three main tools:
-  1) an automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax;
-  2) a citation screening tool based on Bayesian active machine learning and natural language processing, which requires users feedback only on uncertain classifications to iteratively increase predictive accuracy;
-  3) a semi-automatic data-driven query generator to create new search queries from existing reviewed citation data sets.\
-  The framework was tested on an example topic to perform citation collection and screening of related scientific production.
+  The framework provides three main tools:
+  1) An automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax
+  2) A citation screening tool based on Bayesian active machine learning and natural language processing that requires users feedback only on uncertain classifications to iteratively increase predictive accuracy and
+  3) A semi-automatic, data-driven query generator to create new search queries from existing reviewed citation data sets.\
+  The framework was tested on an example topic to collect and screen citations of related scientific production.
   To evaluate the performance of the active machine learning classifier,
-  we estimated the median posterior Sensitivity and Efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of potentially relevant matches among the records not manually reviewed.\
-  17755 unique records were collected through the framework citation manager;
-  101 over 766 records were found to be relevant after manual evaluation,
+  we estimated the median posterior sensitivity and efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of potentially relevant matches among the records not manually reviewed.\
+  A total of 17,755 unique records were collected through the framework citation manager;
+  101 of 766 records were found to be relevant after manual evaluation,
   while the rest were excluded by automatic classification;
-  the expected Efficiency was 95.7% [95.3%, 95.7%] with a Sensitivity of 100% [93.5%, 100%].\
-  An additional search query generated from the labelled dataset,
-  retrieved 82579 additional records of which only 567 records required human review and six additional positive matches were retrieved.
-  Including the additional records, the overall expected Sensitivity decreased to 97.3% [73.8%, 100%] while the Efficiency achieved was 98.6% [98.2%, 98.7%].\
-  For large studies, the developed framework significantly reduces workload, human effort and error,
-  simplifying citation collection and screening with exceptional sensitivity,
-  hence improving the standardization and repeatability of systematic reviews.
+  the theorethical efficiency was 95.6% [95.3%, 95.7%] with a sensitivity of 100% [93.5%, 100%].\
+  A new search query was generated from the labelled dataset, and 82,579 additional records were collected;
+  only 567 records required human review after automatic screening, and six additional positive matches were found.
+  Including the additional records, the overall expected sensitivity decreased to 97.3% [73.8%, 100%] while the efficiency increased to 98.6% [98.2%, 98.7%].\
+  For large studies, the framework can significantly reduce the human resources required to conduct systematic reviews
+  by simplifying citation collection and screening while demonstrating exceptional sensitivity.
+  Such tool can improve the standardization and repeatability of systematic reviews.
 keywords:

### 2022-02-19 Manuscript/Manuscript.tex
English proof reading and better number formatting

@@
 
+% tightlist command for lists without linebreak
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
 % Pandoc citation processing
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
 \newlength{\csllabelwidth}
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
 % for Pandoc 2.8 to 2.10.1
@@
   % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
   % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
+  \setlength{\parskip}{#2\cslentryspacingunit}
  }%
  {}
-\usepackage{calc} % for calculating minipage widths
+\usepackage{calc}
 \newcommand{\CSLBlock}[1]{#1\hfill\break}
@@
 \usepackage{xcolor}
-
 \begin{document}
 \maketitle
-
-\def\tightlist{}
 
@@
 literature.\\
-The framework introduces three main tools: 1) an automatic citation
-search engine and manager that allows collecting records from multiple
-citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified
-query syntax; 2) a citation screening tool based on Bayesian active
-machine learning and natural language processing, which requires users
-feedback only on uncertain classifications to iteratively increase
-predictive accuracy; 3) a semi-automatic data-driven query generator to
-create new search queries from existing reviewed citation data sets.\\
-The framework was tested on an example topic to perform citation
-collection and screening of related scientific production. To evaluate
-the performance of the active machine learning classifier, we estimated
-the median posterior Sensitivity and Efficiency {[}90\% Credible
-Intervals{]} using Bayesian simulation to predict the distribution of
-potentially relevant matches among the records not manually reviewed.\\
-17755 unique records were collected through the framework citation
-manager; 101 over 766 records were found to be relevant after manual
-evaluation, while the rest were excluded by automatic classification;
-the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]} with a
-Sensitivity of 100\% {[}93.5\%, 100\%{]}.\\
-An additional search query generated from the labelled dataset,
-retrieved 82579 additional records of which only 567 records required
-human review and six additional positive matches were retrieved.
-Including the additional records, the overall expected Sensitivity
-decreased to 97.3\% {[}73.8\%, 100\%{]} while the Efficiency achieved
-was 98.6\% {[}98.2\%, 98.7\%{]}.\\
-For large studies, the developed framework significantly reduces
-workload, human effort and error, simplifying citation collection and
-screening with exceptional sensitivity, hence improving the
-standardization and repeatability of systematic reviews.
+The framework provides three main tools: 1) An automatic citation search
+engine and manager that allows collecting records from multiple citation
+databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query
+syntax 2) A citation screening tool based on Bayesian active machine
+learning and natural language processing that requires users feedback
+only on uncertain classifications to iteratively increase predictive
+accuracy and 3) A semi-automatic, data-driven query generator to create
+new search queries from existing reviewed citation data sets.\\
+The framework was tested on an example topic to collect and screen
+citations of related scientific production. To evaluate the performance
+of the active machine learning classifier, we estimated the median
+posterior sensitivity and efficiency {[}90\% Credible Intervals{]} using
+Bayesian simulation to predict the distribution of potentially relevant
+matches among the records not manually reviewed.\\
+A total of 17,755 unique records were collected through the framework
+citation manager; 101 of 766 records were found to be relevant after
+manual evaluation, while the rest were excluded by automatic
+classification; the theorethical efficiency was 95.6\% {[}95.3\%,
+95.7\%{]} with a sensitivity of 100\% {[}93.5\%, 100\%{]}.\\
+A new search query was generated from the labelled dataset, and 82,579
+additional records were collected; only 567 records required human
+review after automatic screening, and six additional positive matches
+were found. Including the additional records, the overall expected
+sensitivity decreased to 97.3\% {[}73.8\%, 100\%{]} while the efficiency
+increased to 98.6\% {[}98.2\%, 98.7\%{]}.\\
+For large studies, the framework can significantly reduce the human
+resources required to conduct systematic reviews by simplifying citation
+collection and screening while demonstrating exceptional sensitivity.
+Such tool can improve the standardization and repeatability of
+systematic reviews.
 \end{abstract}
@@
 the last decades (Larsen and Von Ins 2010; Bornmann and Mutz 2015). This
-is especially true for biomedical research, a trend further increased by
-the COVID-19 pandemic, thanks to faster article' processing time by
-publishers and the diffusion of preprint databases' usage (Aviv-Reuven
-and Rosenfeld 2021; Horbach 2020; Hoy 2020). Consequently, it gets
-harder for researchers and practitioners to stay up-to-date on the
+is especially true for biomedical research, a trend further accelerated
+by the COVID-19 pandemic, thanks to faster article' processing time by
+publishers and the greater use of preprint databases (Aviv-Reuven and
+Rosenfeld 2021; Horbach 2020; Hoy 2020). Consequently, it has become
+harder for researchers and practitioners to stay up to date on the
 latest findings in their field. Secondary research is of paramount
-relevance in this scenario, providing valuable summaries of the latest
-research results, but is getting ever more demanding in terms of time
-and human resources (Allen and Olkin 1999; Borah et al. 2017; A. M.
-Cohen et al. 2010; Bastian, Glasziou, and Chalmers 2010).\\
+importance in this scenario in that it provides valuable summaries of
+the latest research results; however, it is becoming ever more
+challenging in terms of time and human resources required (Allen and
+Olkin 1999; Borah et al. 2017; A. M. Cohen et al. 2010; Bastian,
+Glasziou, and Chalmers 2010).\\
 The article collection and screening phases of a systematic review are
 particularly demanding (Babar and Zhang 2009). First, relevant published
-research needs to be collected from scientific databases through
-appropriately built search queries (retrieval phase); secondly, the
-acquired scientific citations need to be screened, selecting only those
+research must be collected from scientific databases using appropriately
+built search queries (retrieval phase); secondly, the scientific
+citations collected must be screened, selecting only those that are
 relevant to the topic (appraisal phase) (Bannach-Brown et al. 2019;
 Tsafnat et al. 2014; Higgins et al. 2019).\\
-The construction of search queries is a complex task (Lefebvre et al.
-2011; Hammerstrøm et al. 2010), requiring both domain and some knowledge
-of the databases' query languages; the goal is to produce a set of
-results containing all relevant articles (high sensitivity) while
-keeping the total number low (high specificity), focusing on the first
-aspect at the cost of the second (Hammerstrøm et al. 2010). If an
-integrated search tool is not used, manual work is required to download,
-store and organise the publication data; this approach is complicated by
-limits in the number of records that can be downloaded at once and the
-necessity to harmonise different formats and resolve record duplication
-(Marshall and Wallace 2019).\\
+Search queries construction is a complex task (Lefebvre et al. 2011;
+Hammerstrøm et al. 2010), requiring both expertise in the scientific
+field of interest and some knowledge of the database query languages.
+The goal is to obtain a set of results that contains all relevant
+articles (high sensitivity) while keeping the total number of records
+low (high specificity), possibly focusing on the first at the expense of
+the second (Hammerstrøm et al. 2010).\\
+If an integrated search tool is not used, manual work is required to
+download, store and organise the publication data; this approach is
+complicated by limits to the number of records that can be downloaded at
+any one time and the need to harmonise different formats and resolve
+record duplication (Marshall and Wallace 2019).\\
 The citation screening phase is usually the more resource-demanding task
-of a systematic review: even with appropriately built search queries,
-the returned results easily range in the tens of thousands of which just
-a small fraction is actually relevant (Lefebvre et al. 2011). It was
-estimated that labelling 10,000 publications may take as much as 40
-weeks of work and that the average clinical systematic review takes 63
-weeks to be completed (Bannach-Brown et al. 2019; Borah et al. 2017;
-Allen and Olkin 1999). A consequence is that often systematic reviews
-are already outdated once they are published (E. M. Beller et al.
-2013).\\
+in a systematic review: even with appropriately built search queries,
+the results may easily range in the tens of thousands, of which just a
+small fraction are actually relevant (Lefebvre et al. 2011). It has been
+estimated that labelling 10,000 publications can take up to 40 weeks of
+work and that the average clinical systematic review takes 63 weeks to
+complete (Bannach-Brown et al. 2019; Borah et al. 2017; Allen and Olkin
+1999). A consequence of this is systematic reviews are often already
+out-of-date by the time they are published (E. M. Beller et al. 2013).\\
 The field of Data Science applied to evidence synthesis and acquisition
 has greatly maturated in the last years (Marshall and Wallace 2019; E.
-Beller et al. 2018; Tsafnat et al. 2014). Through the application of
-natural language processing (NLP), it is possible to transform free text
-into quantitative features, with various levels of abstraction and
+Beller et al. 2018; Tsafnat et al. 2014). By applying natural language
+processing (NLP), it is possible to transform free text into
+quantitative features, with various levels of abstraction and
 generalisation (Ananiadou and McNaught 2006; K. B. Cohen and Hunter
-2008); with machine learning, such text-derived data can be used to map
-and reproduce human judgment, automating the citation screening
+2008); using machine learning, such text-derived data can be used to map
+and reproduce human judgment, automating the screening of citations
 (Ikonomakis, Kotsiantis, and Tampakas 2005).\\
-The automation of systematic reviews has been ripe with improvements in
+Automation of systematic reviews has made significant improvements in
 the last years (Ananiadou et al. 2009; O'Mara-Eves et al. 2015; Tsafnat
 et al. 2013; Jonnalagadda, Goyal, and Huffman 2015), and it is possible
-to foresee that it is going to become the standard approach in the field
-(E. Beller et al. 2018), with many solutions already being turned into
-commercial and free-to-use tools (see Marshall and Wallace 2019, table
+foreseeable that it will become the standard approach in the field (E.
+Beller et al. 2018), with many solutions already being implemented into
+commercial or free-to-use tools (see Marshall and Wallace 2019, table
 1).\\
-In this manuscript we present an open source, production-ready framework
-which further contributes to the state-of-the-art in systematic review
-automation (SRA) and helpers (SRH) tools. We improve the ``retrieval
-phase'' by providing a unified framework for the automatic collection
-and management of scientific literature from multiple online sources.
-For the citation screening (appraisal) phase, we built an active machine
-learning-based Miwa et al. (2014) protocol, which exploits a Bayesian
-framework to efficiently identify potentially relevant documents that
-require human review while automatically screening-out the large
-majority of clearly non-relevant ones; the algorithm then uses human
-reviews to iteratively increase classification accuracy. Finally, we
-included a tool to generate new search queries given an already labelled
-citation data set, in order to identify relevant research possibly
-missed by human-made queries.\\
+In this manuscript, we present an open source, production-ready
+framework that further contributes to the state-of-the-art in systematic
+review automation (SRA) and helpers (SRH) tools. We improve the
+``retrieval phase'' by providing a unified framework for the automated
+collection and management of scientific literature from multiple online
+sources. For the citation screening (appraisal) phase, we built an
+active machine learning-based protocol (Settles 2009; Miwa et al. 2014),
+which utilises a Bayesian framework to efficiently identify potentially
+relevant documents that require human review, while automatically
+screening-out the vast majority of clearly non-relevant ones; the
+algorithm then requires human review to iteratively increase
+classification accuracy. Finally, we included a tool to generate new
+search queries based on an already labelled citation data set, to
+identify relevant research that may possibly have been missed by
+manually-made queries.\\
 We tested the framework in the retrieval and appraisal phases of an
-example topic of interest for our group: the evaluation of the
+example topic of interest to our group: the evaluation of the
 mathematical modelling of patient referral networks among hospitals and
@@
 microorganisms; the protocol is published in (Sadaghiani et al. 2020).\\
-We give an overview of the framework in the Methods section; in the
-Result section, we show the framework outputs and performance once
-applied to the example topic; in the Discussion, we lay out the
-methodological justification behind the different components and
-features of the framework.\\
+In the Methods, we give an overview of the framework, in the Result, we
+show the outputs and performance of the framework applied to the example
+topic, and in the Discussion, we explain the methodological rationale
+for the different components and features of the framework.\\
 
@@
 We built an R (R Core Team 2020) based framework to simplify two aspects
-of systematic reviews: record acquisition and classification. The code
-used to generate the results in the manuscript is available at X while
-an update version of the framework is distributed as an R package at Y.
-The framework includes several modules that communicate through
-intermediate outputs stored in standard formats, which make it possible
-for users to extend the framework or easily integrate it with other
-tools in their pipeline. See Supplemental Material S1 for an in-depth
-description of the framework and how to use it.\\
+of systematic literature review: record acquisition and classification.
+The code used to generate the results in the manuscript is available at
+\url{https://github.com/AD-Papers-Material/BART_SystReviewClassifier},
+while an updated and ready to use version of the framework is
+distributed as an R package at
+\url{https://github.com/bakaburg1/BaySREn}. The framework includes
+several modules that communicate through intermediate outputs stored in
+standard formats, which make it possible for users to extend the
+framework or easily integrate it with other tools in their pipeline. See
+Supplemental Material S1 for an in-depth description of the framework
+and how to use it.\\
 The tasks carried out by the framework are grouped into ``sessions'',
@@
 
-\hypertarget{records-acquisition-and-initial-labelling}{%
-\subsection{Record's acquisition and initial
-labelling}\label{records-acquisition-and-initial-labelling}}
-
-We built a set of tools to let users automatically search and download
-citation data from three major scientific databases (``sources''):
-Pubmed (\url{https://pubmed.ncbi.nlm.nih.gov/}), Web Of Science (WOS,
-\url{https://apps.webofknowledge.com/}) and the Institute of Electrical
-and Electronics Engineers (IEEE,
+\hypertarget{record-acquisition-and-initial-labelling}{%
+\subsection{Record acquisition and initial
+labelling}\label{record-acquisition-and-initial-labelling}}
+
+We built a set of tools to allow users to automatically search and
+download citation data from three major scientific databases
+(``sources''): Pubmed (\url{https://pubmed.ncbi.nlm.nih.gov/}), Web Of
+Science (WOS, \url{https://apps.webofknowledge.com/}) and the Institute
+of Electrical and Electronics Engineers (IEEE,
 \url{https://ieeexplore.ieee.org/Xplore/home.jsp}). The framework takes
@@
 (\url{https://www.embase.com/}), for which a comprehensive API interface
-was not easy to build. An extra manual search was necessary also for
+was not easy to build. An extra manual search was also necessary for
 Pubmed, since the API and the web interface have different rule
@@
 Insights : Updated Pubmed e-Utilities Coming in April 2022!'}, n.d.). A
-short guide on how to set up the framework for each supported database
+short guide on how to set up the framework for each database supported
 is available in Supplemental Material S3.\\
-The acquired records are merged into a single database, resolving
+The collected records are merged into a single database, resolving
 duplicates and different formatting between sources. The records are
 ordered according to the frequency of the positive query terms (e.g.,
-not preceded by a \(NOT\) modifier) in the title and abstract (``simple
-query ordering'').\\
+not preceded by a \emph{NOT} modifier) in the title and abstract
+(``simple query ordering'').\\
 The researcher is then asked to label a number of records to create the
 ``initial training set'' needed to start the automatic classification.
-We suggest manually labelling the first 250 records (see
-``hyperparameter optimization'' later). The simple query ordering
-increases the positivity rate in the initial training set (Wallace,
-Small, et al. 2010), which provide higher sensitivity during automatic
-classification (Chawla, Japkowicz, and Kotcz 2004).
+We recommend manually labelling the first 250 records (see
+``hyperparameter optimization'' later). Simple query ordering increases
+the positivity rate in the initial training set (Wallace, Small, et al.
+2010), leading to higher sensitivity during automatic classification
+(Chawla, Japkowicz, and Kotcz 2004).
 
@@
 
-The collected citation data have a number of fields characterising a
+The collected citation data contain a number of fields characterising a
 scientific publication. The framework models the relevance of a record
 based on the following fields: title, abstract, authors, keywords, MESH
-terms (Lipscomb 2000). A series of Natural Language Processing (NLP)
+terms (Lipscomb 2000). A range of Natural Language Processing (NLP)
 techniques (Baeza-Yates, Ribeiro-Neto, et al. 1999; Marshall and Wallace
-2019; Ananiadou and McNaught 2006) are employed to transform the textual
+2019; Ananiadou and McNaught 2006) are employed to convert the textual
 information in these fields into features for machine learning through a
-bag-of-words approach (Marshall and Wallace 2019). The processing of
-free text fields (title, abstract) includes: tokenization (i.e.,
-extracting the terms), common stopwords (i.e., sentence components
-bringing no meaning) removal, part-of-speech filtering (only nouns,
-adjectives, verbs and untagged terms are retained), and lemmatization of
-the terms (i.e., reduction to their base grammar form). Text processing
+bag-of-words approach (Marshall and Wallace 2019). Processing of free
+text fields (title, abstract) includes: tokenization (i.e., extracting
+the terms), removal of common stopwords (i.e., sentence components
+having no semantic value), part-of-speech filtering (only nouns,
+adjectives, verbs and untagged terms are retained), and lemmatisation of
+terms (i.e., reduction to their base grammatical form). Text processing
 for authors, keywords and MESH terms identifies logical units (e.g.,
-author's full names, composite keywords) and extracts them.\\
+authors' full names, composite keywords) and extracts them.\\
 Terms appearing in less than 5\% of the labelled documents are removed
@@
 Some terms tend to co-appear in records (non-consecutive ngrams,
-nc-ngrams), often carrying a particular meaning when copresent. To
-detect nc-ngrams, we generated a word network representation (Francois
-Rousseau 2015) posing edges between terms with a cosine similarity in
-terms of record co-occurrence \textgreater{} 0.5. We extracted the
-maximal cliques in the network (Eppstein, Löffler, and Strash 2010)
-representing highly correlated groups of terms; These groups of terms
-are added to the data set as individual features. Only nc-ngrams
+nc-ngrams), often carrying a particular meaning when they do co-occur.
+To detect nc-ngrams, we generated a word network representation
+(Francois Rousseau 2015) with edges occurring between terms with a
+cosine similarity in terms of docuement co-occurrence \textgreater{}
+0.5. We extracted the maximal cliques in the network (Eppstein, Löffler,
+and Strash 2010) representing highly correlated groups of terms; these
+groups are added to the dataset as individual features. Only nc-ngrams
 comprising a maximum of ten terms are kept.\\
@@
 this case, the cliques represent terms that always appear together and
-therefore can be considered redundant (i.e., they do not need to be
-considered separately). These terms are merged to increase computation
+can therefore be considered redundant (i.e., they do not need to be
+considered separately). These terms are merged to increase computational
 efficiency and reduce overfitting.\\
@@
 ``classification model'' (Chipman et al. 2010) (in the implementation of
-Kapelner and Bleich 2013) to predict the probability of a record of
-being relevant, given the information coded into the enriched DTM and
-the initial training set. We set up the BART model to use 2000 MCMC
+Kapelner and Bleich 2013) to predict the probability of a record being
+relevant, given the information coded into the enriched DTM and the
+initial training set. We set up the BART model to use 2,000 MCMC
 iterations (after 250 burn-in iterations) and 50 trees; we used a \(k\)
@@
 The output is a posterior predictive distribution (PPD) for each record
-describing its probability of being relevant (i.e., a positive match).
-An ensemble of ten models was fitted to improve prediction stability by
-averaging the PPD between models (Zhou 2021; Dietterich 2000).\\
-
-To assign the labels, we employed an ``active learning'' Miwa et al.
-(2014) approach, where a human reviews a specific subset of predictions
-made from the machine, which is then retrained on the manually reviewed
-data set. This process proceeds iteratively, decreasing prediction
-uncertainty.\\
-Label assignment is done through the identification of an ``uncertainty
-zone'' whose construction is possible thanks to the Bayesian nature of
-BART, which provides full PPDs instead of point-wise predictions for
-each record.\\
+describing the probability of it being relevant (i.e., a positive
+match). An ensemble of ten models was fitted to improve prediction
+stability by averaging the PPD between models (Zhou 2021; Dietterich
+2000).\\
+
+To assign the labels, we employed an ``active learning'' approach
+(Settles 2009; Miwa et al. 2014), where a human reviews a specific
+subset of predictions made by the machine, which is then retrained on
+the manually reviewed dataset. This process is carried out iteratively
+to reduce prediction uncertainty.\\
+Label assignment is done through identification of an ``uncertainty
+zone'' the construction of which is possible thanks to the Bayesian
+nature of BART, which provides full PPDs instead of point-wise
+predictions for each record.\\
 To describe the process formally, we define
@@
 
-as respectively the lower and upper boundaries of the 98\% quantile
+respectively as the lower and upper boundaries of the 98\% quantile
 interval of \(\pi_i\) (98\% Predictive Interval, 98\% PrI).\\
@@
 labelled positive, its PPD should be within the range of the mixture of
-PPD of the previously labelled positive records and not cross the
-distributions of the negative records.\\
+PPD of the records previously labelled positive, and should not cross
+the distributions of the negative records.\\
 Conversely, a record is labelled as negative if
@@
 Manual review is then necessary for: 1) uncertain records, 2) positive
-records (to avoid false positives), 3) records whose predicted label
+records (to avoid false positives), and 3) records whose predicted label
 differs from the existing manual one. The last case helps identify human
@@
 
-The automatic classification and the manual review steps alternate in a
-loop (CR iterations) until no new positive matches are found in four
+The automatic classification and manual review steps alternate in a loop
+(CR iterations) until no new positive matches are found in four
 consecutive iterations.
@@
 
-BART model it is possible to extract the proportion of times a term was
-used in a posterior tree over the sum of total inclusions of all
-variables (Kapelner and Bleich 2013), as a measure of feature importance
-for the model. We extracted the terms, the part of the citation data
-they were used in, the average ``inclusion rate'' among the ensemble
-models (over 10,000 inclusions) and its ratio over the standard
-deviation of this inclusion (inclusion stability, IS). For each term we
-ran a Poisson regression to get its linear association with a positive
-label and reported it as Relative Risk (RR) with the number of standard
-errors as significance index (Statistic); the comparison between the
-inclusion rate in the BART models and the linear association allows to
-spot relevant non-linear effects (i.e, the feature is relevant only in
-association with others). We reported in the Results only the first (in
-order of inclusion rate) 15 terms with IS \textgreater{} 1.5 while the
-first fifty terms regardless of inclusion stability are reported in
-Supplemental Material S2.
+With the BART model, it is possible to extract the proportion of times a
+term is used in a posterior tree over the sum of total inclusions of all
+variables (Kapelner and Bleich 2013), as a measure of importance of the
+features in the model. We extracted the terms, the portion of the
+citation data in which they were used, the average ``inclusion rate''
+among the ensemble models (over 10,000 inclusions) and its ratio over
+the standard deviation of this inclusion (inclusion stability, IS). For
+each term we ran a Poisson regression to get the linear association with
+a positive label and reported it as Relative Risk (RR) with the number
+of standard errors as significance index (Statistic); the comparison
+between the inclusion rate in the BART models and the linear association
+allows to spot relevant non-linear effects (i.e, the feature is relevant
+only in association with others). In the Results, we only listed the
+first 15 terms with IS \textgreater{} 1.5, (in order of inclusion rate),
+while the first fifty terms regardless of inclusion stability are listed
+in Supplemental Material S2.
 
@@
 
-We created an algorithm that generates a new search query to acquire
-further relevant publications missed during the first search, possibly
-at a reasonable cost in specificity (i.e., a higher number of negative
+We developed an algorithm that generates a new search query to find
+further relevant publications missed in the initial search, possibly at
+a reasonable cost to specificity (i.e., a higher number of negative
 results).\\
@@
 \item
-  We fit a partition tree (Therneau and Atkinson 2019) between the DTM
+  A partition tree (Therneau and Atkinson 2019) is built between the DTM
   and 800 samples from the PPD; if a term is present multiple times in
-  the DTM (e.g., both title and abstract), they are counted just one,
-  and field term count features are removed. This step generates a list
-  of rules composed by \(AND\)/\(NOT\) ``conditions'' made of
+  the DTM (e.g., both in the title and abstract), it is counted just
+  once, and field term count features are removed. This step generates a
+  list of rules composed by \emph{AND}/\emph{NOT} ``conditions'' made of
   terms/authors/keywords/MESH tokens, which together identify a group of
@@
 \item
-  For each rule, negative conditions (i.e., \(NOT\) statements) are
+  For each rule, negative conditions (i.e., \emph{NOT} statements) are
   added iteratively, starting from the most specific one, until no
@@
 \item
-  The researcher is then asked to review the rule groups, selecting one
-  or more rules (useful if they convey different meaning) from each, or
-  edit them (in case too specific positive or negative conditions were
-  included). It is possible to exclude a group of rules altogether,
-  especially those with the worse sensitivity/specificity ratio.
+  The researcher is then asked to review the rule groups and select one
+  or more rules from each group (useful if they convey different
+  meaning), or edit them if overly too specific positive or negative
+  conditions were included. It is possible to exclude a group of rules
+  altogether, especially those with the poorest sensitivity/specificity
+  ratio.
 \item
-  The selected rules are joined together by \(OR\) statements, defining
-  a subset of records with a sensibly higher proportion of positive
-  records than the original one.
+  The selected rules are joined together by \emph{OR} statements,
+  defining a subset of records with a sensibly higher proportion of
+  positive records than the original set
 \item
-  Redundant rules (i.e., rules whose positive records are already
-  included in more specific ones) and conditions (i.e., conditions that
-  once removed do not decrease the total number of positive or do not
-  increase the negative records) are removed.
+  Redundant (i.e., rules whose positive records are already included in
+  more specific ones) and non-relevant rules (i.e., conditions that when
+  removed do not impact sensitivity and specificity) are removed.
 \item
-  Finally, the rules are re-elaborated in a query usable on the major
-  scientific databases.
+  Finally, the rules are re-elaborated in a query that can be used in
+  the major scientific databases.
 \end{itemize}
 
-Since the algorithm is data-driven, it creates queries that effectively
-select positive records from the input data set but may be not specific
-enough once applied to actual research databases. Therefore we appended
-an extra subquery in \(AND\), which specifies the general topics of our
-search and delimitates the search domain.\\
+Because the algorithm is data-driven, it creates queries that
+effectively select positive records from the input dataset, but may be
+not specific enough when applied to actual research databases. Therefore
+we added an extra subquery in \emph{AND}, that specifies the general
+topics of our search and narrows the search domain.\\
 The new query was used to initiate a second search session.
@@
 We trained a simple Bayesian logistic regression (surrogate model) on
-the reviewed records to evaluate the classification model consistency
+the reviewed records to evaluate the consistency of classification model
 (see Discussion for the theoretical justification). The surrogate model
-uses as predictor the lower bound of the 98\% PrI of the records' PPD
-with weakly regularizing, robust priors for the intercept (Student T
-with \(\nu=3,\mu=0,\sigma=2.5\)) and the linear coefficient (Student T
-with \(\nu=3,\mu=0,\sigma=1.5\)).\\
-The quality of the model was evaluated through Bayesian \(R^2\) (Gelman
-et al. 2019), of which we reported the posterior median and 90\%
+uses as predictor the lower boundary of the 98\% PrI of the PPD of the
+records with weakly regularizing, robust priors for the intercept
+(Student T with \(\nu=3,\mu=0,\sigma=2.5\)) and the linear coefficient
+(Student T with \(\nu=3,\mu=0,\sigma=1.5\)).\\
+The quality of the model was evaluated through the Bayesian \(R^2\)
+(Gelman et al. 2019), of which we reported the posterior median and 90\%
 Credible Interval {[}90\% CrI{]}. The \(R^2\) also provides an
@@
 The surrogate model is then used to generate the predictive cumulative
-distribution of the number of total positive records in the whole data
-set. This distribution allows estimating the expected total posterior
-``Sensitivity'' and ``Efficiency'' of the classification model in the
-full (unreviewed) data set. Efficiency is summarised by the ``Work saved
-over random'' (WSoR) statistic: one minus the ratio between the number
-of record manually reviewed and those that would be required to find the
-same number of positives if classification was performed choosing
-records randomly; this last quantity is estimated through a negative
-hypergeometric distribution (Chae 1993) over the predicted amount of
-positive records.\\
-For the number of predicted positive records, the sensitivity and the
+distribution of the number of total positive records in the whole
+dataset. This distribution allows to estimate the expected total
+posterior ``Sensitivity'' and ``Efficiency'' of the classification model
+in the full (unreviewed) dataset. Efficiency is summarised by the ``Work
+saved over random'' (WSoR) statistic: one minus the ratio between the
+number of record manually reviewed and those that would be required to
+find the same number of positives if classification were performed
+choosing records randomly; this last quantity is estimated through a
+negative hypergeometric distribution (Chae 1993) over the predicted
+number of positive records.\\
+For the number of predicted positive records, sensitivity and
 efficiency, we reported the ``truncated 90\% PrI'' {[}trunc. 90\%
-PrI{]}, which is the uncertainty interval bounded at the number of
-observed total positive records (i.e., there cannot be less predicted
-positive records than observed).
+PrI{]}, i.e., the uncertainty interval bounded by the number of observed
+total positive records (i.e., there cannot be fewer predicted positive
+records than observed).
 
@@
   Source of randomness between models in the ensemble: MCMC sampling
-  only (Robert, Casella, and Casella 2004), MCMC plus data bootstrapping
-  (Breiman 1996) of the training set.
+  only (Robert and Casella 2004), MCMC plus data bootstrapping (Breiman
+  1996) of the training set.
 \end{itemize}
@@
 search'' (Claesen and De Moor 2015; L. Yang and Shami 2020) on a
-prelabelled ``validation set'' made of the first 1200 records from the
-first session data set. The framework tested each hyperparameter
-combination until four CR iterations with no positive records were
-returned or the whole data set got labelled.\\
+prelabelled ``validation set'' derived from the first 1,200 records of
+the first session dataset. Each hyperparameter combination was tested
+until four CR iterations were completed with no positive records or the
+whole dataset was labelled.\\
 For each combination, a performance score was computed as the product of
-``Efficiency'' (1 minus the ratio of records that required review over
-the total) and ``Sensitivity'' (number of positive records found over
-the total of positives). We then identified homogeneous ``performance
-clusters'' of scores given hyperparameter values using a partition tree
-(Therneau and Atkinson 2019). For the rest of the study, we used the
-best hyperparameter set in terms of Sensitivity followed by Efficiency
-from the cluster with the highest average score.\\
+``Efficiency'' (1 minus the ratio of records that required reviewing
+over the total number of records) and ``Sensitivity'' (number of
+positive records found over the total number of positive records). We
+then used a partition tree (Therneau and Atkinson 2019) to identify
+homogeneous ``performance clusters'' of scores given hyperparameter
+values. For the rest of the study, we used the best hyperparameter set
+in terms of Sensitivity followed by Efficiency from the cluster with the
+highest average score.\\
 
@@
 collected from Pubmed, WOS, IEEE, EMBASE and SCOPUS, using the framework
-tools as described in Methods and Supplemental Material S1.
-
-The first search session returned a total of 27600 records, specifically
-12719 (71.6\% of the total) records from the EMBASE database, followed
-by 9546 (53.8\%) from Pubmed, 3175 (17.9\%) from SCOPUS, 2100 (11.8\%)
-from WOS, and 60 (0.34\%) from IEEE (Table 1). There were various
-degrees of overlapping between sources, with the 38.4\% of records being
-present in more than one database and EMBASE and IEEE being the
-databases with the higher uniqueness ratios. The final data set was
-composed by 17755 unique records.\\
-The first 250 records (based on ``simple query ordering'') were manually
-labeled. Of these 43 (17.2\%) were labeled as positive, and 207 (82.8\%)
-as negative.
+tools as described in the Methods and Supplemental Material S1.
+
+The first search session returned a total of 27,600 records,
+specifically 12,719 (71.6\% of the total) records from the EMBASE
+database, followed by 9,546 (53.8\%) from Pubmed, 3,175 (17.9\%) from
+SCOPUS, 2,100 (11.8\%) from WOS, and 60 (0.34\%) from IEEE (Table 1).
+There were various degrees of overlapping between sources, with 38.4\%
+of records being present in more than one database, and EMBASE and IEEE
+being the databases with the higher uniqueness ratios. The final data
+set was composed from 17,755 unique records.\\
+The first 250 records (based on ``simple query ordering'') were labeled
+manually. Of these 43 (17.2\%) were labeled as positive, and 207
+(82.8\%) as negative.
 
@@
 \midrule
-\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
- & Embase & 12719 & 71.6\% & 6683 & 52.5\%\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3457} & \cellcolor{gray!6}{36.2\%}\\
- & Scopus & 3175 & 17.9\% & 298 & 9.39\%\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
+\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17,755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+ & Embase & 12,719 & 71.6\% & 6,683 & 52.5\%\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9,546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3,457} & \cellcolor{gray!6}{36.2\%}\\
+ & Scopus & 3,175 & 17.9\% & 298 & 9.39\%\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2,100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
 \addlinespace
  & IEEE & 60 & 0.34\% & 29 & 48.3\%\\
-\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
- & Embase & 48396 & 58.6\% & 40826 & 84.4\%\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18021} & \cellcolor{gray!6}{62.5\%}\\
- & Scopus & 17070 & 20.7\% & 4908 & 28.8\%\\
+\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82,579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+ & Embase & 48,396 & 58.6\% & 40,826 & 84.4\%\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28,811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18,021} & \cellcolor{gray!6}{62.5\%}\\
+ & Scopus & 17,070 & 20.7\% & 4,908 & 28.8\%\\
 \addlinespace
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2817} & \cellcolor{gray!6}{21.7\%}\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12,956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2,817} & \cellcolor{gray!6}{21.7\%}\\
  & IEEE & 61 & 0.074\% & 22 & 36.1\%\\
-\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
- & Embase & 59604 & 60.6\% & 46942 & 78.8\%\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21371} & \cellcolor{gray!6}{57.3\%}\\
+\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98,371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
+ & Embase & 59,604 & 60.6\% & 46,942 & 78.8\%\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37,278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21,371} & \cellcolor{gray!6}{57.3\%}\\
 \addlinespace
- & Scopus & 19353 & 19.7\% & 5181 & 26.8\%\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3175} & \cellcolor{gray!6}{22.1\%}\\
+ & Scopus & 19,353 & 19.7\% & 5,181 & 26.8\%\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14,367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3,175} & \cellcolor{gray!6}{22.1\%}\\
  & IEEE & 108 & 0.11\% & 48 & 44.4\%\\
@@
 (13.2\% positivity rate).\\
-It is possible to observe how the number of records that required manual
-review dropped rapidly between iterations (Table 2), indicating that the
+It is noticeable how the number of records that required manual review
+decreased rapidly between iterations (Table 2), indicating that the
 engine was converging while the uncertainties were resolved.\\
-This phenomenon is better depicted in Fig. 1 of the Supplemental
-Material S2, showing the mixture distribution of the PPDs of the
-records, specifically for the reviewed positive and negative records,
-and for records that need manual review after the classification step:
-it can be noticed how the distribution of the uncertain records shrinked
-(ie., gets concentrated in a shorter probability range) and shifted
-toward the negative zone as more positive matches are found and
-reviewed.
+This phenomenon is better illustrated in Fig. 1 of the Supplemental
+Material S2. It shows the mixture distribution of the PPDs of the
+records, specifically for records that were manually reviewed, before
+and after the classification step: it can be seen how the distribution
+of uncertain records shrinks (i.e., it becomes concentrated in a shorter
+probability range) and shifts toward the negative zone as more positive
+matches are found and reviewed.
 
@@
 Also, the number of changes after review and their description is reported."Unlab." indicates unlabelled records marked for review.
-For each Iteration, also the number of features used by the engine is reported.
-The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1.
+For each Iteration, the number of features used by the engine is also reported.
+The first row reports the results of the initial manual labelling of records, which served as input for the automatic classification in Iteration 1.
 In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.}
@@
 \midrule
-\cellcolor{gray!6}{Session1 (n = 17755)} & \cellcolor{gray!6}{Initial labelling} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{250 (1.41\%)} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{2289}\\
- & 1 & 93 & 529 & 622 (3.5\%) & 50 & 322 & 0 & 0 & 372 & 2289\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{614} & \cellcolor{gray!6}{714 (4.02\%)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{86} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{3750}\\
- & 3 & 101 & 625 & 726 (4.09\%) & 1 & 11 & 0 & 0 & 12 & 3834\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{648} & \cellcolor{gray!6}{749 (4.22\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{3856}\\
+\cellcolor{gray!6}{Session1 (n = 17755)} & \cellcolor{gray!6}{Initial labelling} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{250 (1.41\%)} & \cellcolor{gray!6}{43} & \cellcolor{gray!6}{207} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{2,289}\\
+ & 1 & 93 & 529 & 622 (3.5\%) & 50 & 322 & 0 & 0 & 372 & 2,289\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{614} & \cellcolor{gray!6}{714 (4.02\%)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{86} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{93} & \cellcolor{gray!6}{3,750}\\
+ & 3 & 101 & 625 & 726 (4.09\%) & 1 & 11 & 0 & 0 & 12 & 3,834\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{648} & \cellcolor{gray!6}{749 (4.22\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{3,856}\\
 \addlinespace
- & 5 & 101 & 651 & 752 (4.24\%) & 0 & 3 & 0 & 0 & 3 & 3856\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{660} & \cellcolor{gray!6}{761 (4.29\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{3856}\\
- & 7 & 101 & 665 & 766 (4.31\%) & 0 & 5 & 0 & 0 & 5 & 3856\\
-\cellcolor{gray!6}{Session2 (n = 98371)} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{106} & \cellcolor{gray!6}{934} & \cellcolor{gray!6}{1040 (1.06\%)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{270} & \cellcolor{gray!6}{998} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1273} & \cellcolor{gray!6}{4729}\\
- & 2 & 107 & 1123 & 1230 (1.25\%) & 1 & 189 & 0 & 0 & 190 & 4729\\
+ & 5 & 101 & 651 & 752 (4.24\%) & 0 & 3 & 0 & 0 & 3 & 3,856\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{101} & \cellcolor{gray!6}{660} & \cellcolor{gray!6}{761 (4.29\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{3,856}\\
+ & 7 & 101 & 665 & 766 (4.31\%) & 0 & 5 & 0 & 0 & 5 & 3,856\\
+\cellcolor{gray!6}{Session2 (n = 98371)} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{106} & \cellcolor{gray!6}{934} & \cellcolor{gray!6}{1040 (1.06\%)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{270} & \cellcolor{gray!6}{998} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{1,273} & \cellcolor{gray!6}{4,729}\\
+ & 2 & 107 & 1,123 & 1230 (1.25\%) & 1 & 189 & 0 & 0 & 190 & 4,729\\
 \addlinespace
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1176} & \cellcolor{gray!6}{1283 (1.3\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{4733}\\
- & 4 & 107 & 1200 & 1307 (1.33\%) & 0 & 24 & 0 & 0 & 24 & 4729\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1209} & \cellcolor{gray!6}{1316 (1.34\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{4729}\\
- & 6 & 107 & 1226 & 1333 (1.36\%) & 0 & 17 & 0 & 0 & 17 & 4729\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1,176} & \cellcolor{gray!6}{1283 (1.3\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{53} & \cellcolor{gray!6}{4,733}\\
+ & 4 & 107 & 1,200 & 1307 (1.33\%) & 0 & 24 & 0 & 0 & 24 & 4,729\\
+\cellcolor{gray!6}{} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{107} & \cellcolor{gray!6}{1,209} & \cellcolor{gray!6}{1316 (1.34\%)} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{0} & \cellcolor{gray!6}{9} & \cellcolor{gray!6}{4,729}\\
+ & 6 & 107 & 1,226 & 1333 (1.36\%) & 0 & 17 & 0 & 0 & 17 & 4,729\\
 \bottomrule
@@
 position out of more than 3800 terms considered) although in a simpler
-linear model their effect would be hardly significant (statistic: -1.21
-s.e.); these are terms which are relevant only in conjunction with other
-terms but not by themselves, highlighting the extra predictive power
-brought by using advanced, non-linear machine learning.\\
-A more extensive set of terms is presented in Table 1 of Supplemental
-Material S2.
+linear model their effect would hardly be significant (statistic: -1.21
+s.e.); these are terms that are only relevant in conjunction with other
+terms but not by their own, highlighting the extra predictive power
+achievd through the use of advanced, non-linear machine learning.\\
+A more extensive set of terms is presented in Table 1 of the
+Supplemental Material S2.
 
@@
 The results of the first classification session were used to create a
-second, data-driven query with the purpose of performing a more
-large-spectrum search to find records which may have escape the first
-search session. The resulting query was the following:\\
+second, data-driven query with the objective of performing a more
+extensive search to find records that may have been missed during the
+first search session. The resulting query was as follows:\\
 
@@
 
-The search was done with the same year filter and procedures of the
+The search was done with the same year filter and procedures used in the
 first session.\\
 
-The new search produced 107294 records (Table 1), of which 48396
-(58.6\%) from the EMBASE, followed by 28811 (34.9\%) from Pubmed, 17070
-(20.7\%) from SCOPUS, 12956 (15.7\%) from WOS, and 61 (0.074\%) from
-IEEE; compared with the first session, the relative weight of EMBASE and
-Pubmed was decreased, while the amount of content specificity was
+The new search produced 107,294 records (Table 1), of which 48,396
+(58.6\%) from the EMBASE, followed by 28,811 (34.9\%) from Pubmed,
+17,070 (20.7\%) from SCOPUS, 12,956 (15.7\%) from WOS, and 61 (0.074\%)
+from IEEE; compared with the first session, the relative weight of
+EMBASE and Pubmed decreased, while the level of content specificity
 greatly increased, as it was for SCOPUS. After removal of duplicates,
-82579 unique records were obtained. Once joined with the session 1
-records and removal of duplicates, we obtained 98371 unique records,
-with just 1963 shared records between searches, that is the 2\%. The
-percentage of records shared by two or more source dropped to 22\%.
+82,579 unique records were obtained. The newly collected records were
+joined with those from the first session and duplicates were removed. We
+obtained 98,371 unique records, with just 1,963 shared records between
+searches, which equates to 2\% of the total. The percentage of records
+shared by two or more source dropped to 22\%.
 
@@
 records. The first CR iteration required the user to review a
-substantial number of records (1,273), but just labelling 275 of them
-(the canonical 250 plus 25 that were already labelled during the
-framework hyperparameter tuning) was sufficient to drop this number to
-just 190 in the subsequent round. An evaluation of the convergence
-(Figure 1, Supplemental Material S2) showed that, in addition to the
-dynamics already observed in session 1 (shrinkage and negative shift), a
-second mode appeared in the mixture distribution of the records to be
-reviewed, centred in a highly positive zone. The interpretation is that
-as the number of negative training records increases, the engine gets
-more and more skeptical and asks to review even some records labelled as
+substantial number of records (1,273); however, just labelling 275 of
+them (the suggested 250 plus 25 alredy labelled for the framework
+hyperparameter tuning) was sufficient to reduce this number to just 190
+in the subsequent round. An evaluation of the convergence (Supplemental
+Material S2, Fig. 1) showed that, in addition to the dynamics already
+observed in session 1 (shrinkage and negative shift), a second mode
+appeared in the mixture distribution of the records to be reviewed,
+centred in a highly positive zone. The interpretation is that as the
+number of negative training records increases, the engine becomes more
+and more sceptical and even asks to review some records labelled as
 positive in the initial training set generated during Session 1. This
 behaviour can be useful to spot classification errors and
-inconsistencies. Considering both sessions, 1333 records were manually
+inconsistencies. Considering both sessions, 1,333 records were manually
 reviewed and 107 (8.03\%) confirmed positive matches were found.
@@
 Again, the evaluation of the inclusion rate of the terms showed that the
-engine was quite capable of internalizing the concepts behind the
-research topic A subsample of the relevant terms used by the model in
+engine is quite capable of internalizing the concepts behind the
+research topic. A subsample of the relevant terms used by the model in
 the second session is reported in Table 2 of Supplemental Material S2.
@@
 
-As described in the methods, the selection of hyperparameters was
-achieved via evaluation of sensibility and efficiency through a grid
-search on a validation set of 1200 manually labelled records. The
-analysis suggested the following combination of parameters as the best
-performing: an initial input of 250 labelled records with 10x positive
-matches oversampling, an averaged ensemble of 10 models, no
-bootstrapping and an uncertainty zone defined by the 98\% predictive
-interval. This combination of parameters was associated with a
-sensitivity of 98.8\% (81 / 82 positive matches found) and efficiency of
-61.5\% (462 / 1200 records evaluated). The detailed results of the
-hyperparameter tuning ananlysis are reported in Table 3 of Supplemental
-Material S2. Figure 2 in Supplemental Material S2 demonstrates that the
-positive record oversampling rate, the number of ensemble models and the
-size of the initial training set were the parameters that mostly
-impacted performance.
+As described in the methods, hyperparameters were selected by evaluating
+sensibility and efficiency through a grid search on a validation set of
+1,200 manually labelled records. The analysis suggested that the
+following parameter combination performed best: an initial input of 250
+labelled records with 10x oversampling of positive matches, an averaged
+ensemble of 10 models, no bootstrapping and an uncertainty zone defined
+by the 98\% predictive interval. This combination of parameters was
+associated with a sensitivity of 98.8\% (81 / 82 positive matches found)
+and an efficiency of 61.5\% (462 / 1200 records evaluated). The detailed
+results of the hyperparameter tuning analysis are reported in Table 3 of
+Supplemental Material S2. Fig. 2 in Supplemental Material S2
+demonstrates that the positive record oversampling rate, the number of
+ensemble models and the size of the initial training set were the
+parameters that mostly impacted performance.
 
@@
 Bayesian logistic regression model was trained on the manually reviewed
-labels using only the lower bound of the record PPDs as predictor (see
-Methods for the details). The surrogate model showed the high predictive
-power of the scores produced by the classification model (Bayesian R2:
-98.1\% {[}97.4\%, 98.3\%{]} for session 1 and 98.2\% {[}97.6\%,
-98.3\%{]} for session 2).\\
-
-Figure 2 presents the actual and predicted (from the surrogate model)
+labels using only the lower boundary of the record PPDs as predictor
+(see the Methods for details). The surrogate model showed the high
+predictive power of the scores produced by the classification model
+(Bayesian R2: 98.1\% {[}97.4\%, 98.3\%{]} for session 1 and 98.2\%
+{[}97.6\%, 98.3\%{]} for session 2).\\
+
+Fig. 2 presents the actual and predicted (from the surrogate model)
 cumulative number of positive matches, ordered by the initial simple
@@
 distributions matches quite well the actual number of positive records
-found. It is striking how many more records would have needed to be
-evaluated manually to find the same number of positive matches without
-using a smart classification tool, with some positive matches found
-close to the end of the heuristically ordered list of records.\\
+found. It is striking how many more records would have required manual
+evaluation to find the same number of positive matches without using a
+smart classification tool, with some positive matches found close to the
+end of the heuristically ordered list of records.\\
 
@@
 and efficiency of 95.6\% {[}95.3\%, 95.7\%{]}. In session 2 we observed
-a drop in the expected sensitivity, especially in the lower credibility
+a drop in expected sensitivity, especially in the lower credibility
 boundary (97.3\% {[}72.8\%, 100\%{]}), due to the fact that as the
-number of records grows, even a small probability of being a positive
-match can translate, in the worst case scenario, into a relevant number
-of missed positive matches (147 in this case). To ascertain that no
-evident positives were missed, we evaluated 100 more records between the
-unreviewed ones with the highest median predicted probability produced
-by the engine and found no additional positive matches.\\
+number of records increases, even a small probability of being a
+positive match can, in the worst case scenario, lead to a relevant
+number of missed positive matches (147 in this case). To ensure that no
+obvious positive matches were missed, we evaluated 100 additional
+records among those not reviewed with the highest median predicted
+probability produced by the engine and found no additional positive
+matches.\\
 
@@
 \midrule
-\cellcolor{gray!6}{Total records} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{98371}\\
-Reviewed records (\% over total records) & 766 (4.31\%) & 1333 (1.36\%)\\
+\cellcolor{gray!6}{Total records} & \cellcolor{gray!6}{17,755} & \cellcolor{gray!6}{98,371}\\
+Reviewed records (\% over total records) & 766 (4.31\%) & 1,333 (1.36\%)\\
 \cellcolor{gray!6}{Expected efficiency (over random) [trunc. 90\% PrI]} & \cellcolor{gray!6}{95.6\% [95.3\%, 95.7\%]} & \cellcolor{gray!6}{98.6\% [98.1\%, 98.6\%]}\\
@@
 PrI{]} of the cumulative positive matches estimated by the logistic
-Bayesian model is shown as shaded area delimited by the 95\% quantile of
-the PrI and by the observed number of positive matches (light blue
+Bayesian model is shown as a shaded area delimited by the 95\% quantile
+of the PrI and by the observed number of positive matches (light blue
 lines). The median of the PrI is represented by a darker blue line.}
@@
 We propose a new integrated framework to help researchers collect and
-screen scientific publications characterised by high performance and
-versatility, joining the growing field of systematic review automation
-(SRA) and helpers (SRH) tools (A. M. Cohen et al. 2006, 2010; Ananiadou
-et al. 2009; O'Mara-Eves et al. 2015). This framework implements
-standard approaches and uses ad-hoc solutions to deal with common SRA
-issues. By freely sharing the tool as an open-source R package and by
-following a modular design, we tried to adopt some of the so-called
-Vienna Principles advocated by the International Collaboration for the
-Automation of Systematic Reviews (ICASR) (E. Beller et al. 2018).\\
+screen scientific publications that is characterised by high performance
+and versatility. This framework joins the joining the growing field of
+systematic review automation (SRA) and helpers (SRH) tools (A. M. Cohen
+et al. 2006, 2010; Ananiadou et al. 2009; O'Mara-Eves et al. 2015). This
+framework implements standard approaches and uses ad-hoc solutions to
+deal with common SRA issues. By freely sharing the tool as an
+open-source R package and by following a modular design, we sought to
+adopt some of the so-called Vienna Principles advocated by the
+International Collaboration for the Automation of Systematic Reviews
+(ICASR) (E. Beller et al. 2018).\\
 The framework consists of four main components: 1) an integrated
@@
 
-The framework's search engine module is capable of automatically
-collecting citation data from three well-known scientific databases
-(i.e., Pubmed, Web of Science, and the database of the Institute of
-Electrical and Electronics Engineers) as well as process manually
-downloaded results from both the two more (SCOPUS, EMBASE) databases. In
-comparison, most SRH tools, commercial or free to use, rely either on
-internal databases (e.g., Mendeley \url{https://www.mendeley.com/})
-sometimes focusing just on a particular topic (Visser 2010) or on a
-single external data source (Thomas and Brunton 2007; Poulter et al.
-2008; Soto, Przybyła, and Ananiadou 2019).\\
-Mixing different databases is fundamental to have a more comprehensive
+The search engine module used by the framework is able to automatically
+collect citation data from three well-known scientific databases (i.e.,
+Pubmed, Web of Science, and the database of the Institute of Electrical
+and Electronics Engineers) asand to process manually downloaded results
+from both the two more databases (SCOPUS, EMBASE). In comparison, most
+commercial or free SRH tools, rely on internal databases (e.g., Mendeley
+\url{https://www.mendeley.com/}) sometimes focusing only on a particular
+topic (Visser 2010) or on a single external data source (Thomas and
+Brunton 2007; Poulter et al. 2008; Soto, Przybyła, and Ananiadou
+2019).\\
+Mixing different databases is essential to obstain a more comprehensive
 view of the literature (Bajpai et al. 2011; Wilkins, Gillies, and Davies
 2005; Woods and Trewheellar 1998): in our results, 18.7\% of the
-positive matches found only in one of the different data sources, and no
-positive record was present in all of them (data not shown).\\
-The online search algorithms are efficient enough to manage tens of
-thousands of search results, using various expedients to overcome the
-limitations of online citation databases in terms of traffic and
-download quotas. The results are then automatically organized,
-deduplicated and arranged by ``simple query ordering'' in a uniform
-corpus. The preliminary ordering allows to increase the positivity rate
-in the initial training set (Wallace, Small, et al. 2010).\\
-
-For the framework's record classification module, we employed an active
-machine learning approach Miwa et al. (2014) based on the best practices
-from other SRA studies but also bringing further improvements at various
-levels.\\
+positive matches were found in only one of the different data sources,
+and no positive record was present in all the sources (data not
+shown).\\
+The framework online search algorithms are efficient enough to manage
+tens of thousands of search results, using various solutions to overcome
+the limitations of citation databases in terms of traffic and download
+quotas. The results are then automatically organized, deduplicated and
+arranged by ``simple query ordering'' in a uniform corpus. The
+preliminary ordering allows to increase the positivity rate in the
+initial training set (Wallace, Small, et al. 2010).\\
+
+For the framework's record classification module, we developed an active
+machine learning approach (Settles 2009; Miwa et al. 2014) which is
+based on the best practices from other SRA studies but also brings
+further improvements at various levels.\\
 The feature extractor module uses modern NLP techniques (Ananiadou and
@@
 data for machine learning. We did not include classical n-grams
-(Schonlau and Guenther 2017), but we used network analysis to find
-non-consecutive frequently associated terms, a generalisation of n-grams
-relaxing the term adjacency assumption. This approach allows also to
-find term connections across fields, for example a term having a
-different relevancy if associated with a specific author. The same
-technique but with different parameters was applied to merge redundant
-terms to make model estimation more efficient and reduce noise.\\
+(Schonlau and Guenther 2017); rather we used network analysis to find
+non-consecutive, frequently associated terms, a generalisation of
+n-grams that relaxes the term adjacency assumption. This approach can
+also be used to find term connections across parts of the records, e.g.,
+whether a term has a different relevance when associated with a
+particular author. The same technique, albeit with different parameters,
+was used to merge redundant terms to make the model estimation more
+efficient and reduce noise.\\
 The use of concurrency network-driven modelling of text is not new
@@
 and Vazirgiannis 2015; Ohsawa, Benson, and Yachida 1998) and is a
-valuable tool to extract semantic information not evident in one-word or
-consecutive n-gram models.\\
+valuable tool to extract semantic information that is not evident in
+one-word or consecutive n-gram models.\\
 
@@
 Regression Trees (BART) (Chipman et al. 2010; Kapelner and Bleich 2013).
-As with other boosted trees algorithms (Hastie, Tibshirani, and Friedman
-2009), BART can explore complex non-linearities, perform variable
-selection, manage missing data while sporting high performance in
+Like other boosted trees algorithms (Hastie, Tibshirani, and Friedman
+2009), the BART method can explore complex non-linearities, perform
+variable selection, manage missing data while maintaining high
 predictive power.\\
-However, its Bayesian foundation provides further benefits: less
-sensitivity on hyperparameter choices, natural regularisation through
-priors, and, especially, predictive distributions as output in place of
-point-wise predictions (Soria-Olivas et al. 2011; Joo, Chung, and Seo
-2020; Jospin et al. 2020). By selecting relatively tight prior
-distributions, we discouraged excessively deep trees, long sequences of
-trees, or extreme predicted probabilities, to decrease the risk of
-overfitting.\\
+However, the Bayesian foundation of the method provides further
+benefits: lower sensitivity to the choice of hyperparameters, natural
+regularisation through priors, and, most imporantly, predictive
+distributions as output instead of point-wise predictions (Soria-Olivas
+et al. 2011; Joo, Chung, and Seo 2020; Jospin et al. 2020). By selecting
+relatively tight prior distributions, we discouraged overly deep trees,
+long tree sequences, and extreme predicted probabilities, this reducing
+the risk of overfitting.\\
 The algorithm runs multiple replications of the model and averages their
@@
 uncertainty in the predictive distribution tails related to the
-randomness in the MCMC fit (Robert, Casella, and Casella 2004),
-generating a shift of probability mass towards the distribution centre
-and stabilising it (i.e., decreasing variance without impacting bias).
-On the other hand, just imposing robust uninformative priors against
-extreme predictions would have decreased variance but also shifted the
+randomness in the MCMC fit (Robert and Casella 2004), generating a shift
+in the probability mass towards the distribution centre and stabilising
+it (i.e., reducing variance without impacting bias). On the other hand,
+simply imposing more robust uninformative priors against extreme
+predictions would have reduced variance but also shifted the
 distribution towards a non-decision zone, increasing bias (Hansen et al.
 2000).\\
-Since the number of model replications significantly impacts computation
-times, we decided to use ten replicas, the lower value after which
-performance stabilised during the hyperparameter evaluation.\\
+Since the number of model replications has a significant impact on
+computation times, we decided to use ten replicas, the lower value after
+which performance stabilised, as resulted from the evaluation of the
+hyperparameters (Supplemental Material S2, Fig. 2).\\
 We also investigated whether bootstrapping between replications (Breiman
-1996) would improve performance, but, contrary to theory (Díez-Pastor et
-al. 2015), it appeared to be slightly detrimental in our case
-(Supplemental Material S2) compared to simple ensembling.\\
-
-A low rate of relevant matches (class imbalance) is typical in
+1996) would improve performance; however, contrary to theory
+(Díez-Pastor et al. 2015), it appeared to be slightly detrimental in our
+case (Supplemental Material S2, Fig. 2) compared to simple ensembling.\\
+
+A low rate of relevant matches (class imbalance) is typical for
 literature reviews (Sampson, Tetzlaff, and Urquhart 2011; Wallace,
-Trikalinos, et al. 2010; O'Mara-Eves et al. 2015), and such strong
+Trikalinos, et al. 2010; O'Mara-Eves et al. 2015), and a strong
 imbalance between positive and negative records can affect sensitivity
@@
 Kotcz 2004).\\
-To overcome the problem, we oversampled (Batista, Prati, and Monard
-2004) the positive records ten times before model fitting. Our
-hyperparameter analysis showed that together with model ensembling, the
-oversampling rate was the parameter with the highest impact on
+To overcome this problem, we oversampled (Batista, Prati, and Monard
+2004) the positive records ten times before model fitting. The
+hyperparameter analysis showed that the oversampling rate, together with
+model ensembling, was the parameter with the greatest impact on
 performance.\\
@@
 negative records (Ramezankhani et al. 2016). However, since all
-predicted positives get manually reviewed in our approach, we are always
-ensured to achieve 100\% specificity/positive predictive value: the only
-price for the increased sensitivity due to oversampling is a larger
-number of records to review.\\
-An alternative to oversampling would be applying different weights
-and/or cost to the classes (Abd Elrahman and Abraham 2013; Díez-Pastor
+predicted positives in our approach are reviewed manually, we are always
+guaranteed to achieve 100\% specificity/positive predictive value: the
+only price for the increased sensitivity due to oversampling is a larger
+number of records to be reviewed.\\
+An alternative to oversampling would be to apply different weights
+and/or costs to the classes (Abd Elrahman and Abraham 2013; Díez-Pastor
 et al. 2015), but the BART implementation we used did not have this
-feature; also, using simple oversampling permits broader compatibility
-with different modelling engines (Galar et al. 2011; Roshan and Asadi
-2020).\\
-Finally, ordering the records by query term frequency (simple query
-ordering) generates a far higher rate of relevant records in the initial
-training set (17.2\%) compared to the overall data (0.11\%), and this
+feature; furthermore, using simple oversampling allows for broader
+compatibility with different modelling engines (Galar et al. 2011;
+Roshan and Asadi 2020).\\
+Finally, sorting the records by query term frequency (simple query
+ordering) produces a much higher rate of relevant records in the initial
+training set (17.2\%) compared to the overall data (0.11\%), which
 boosts the sensitivity of the model.\\
 
-One of the central innovations we introduced is the concept of
-``uncertainty zone'', whose implementation is possible thanks to the
-Bayesian foundation of the classification model. This construct guides
-the selection of the records to review, dynamically updating and
-shrinking after every CR iteration, as more uncertain predictions are
-evaluated (Supplemental Material S2 Fig. 1).\\
+One of the key innovations we have introduced is the concept of
+``uncertainty zone'', thie implementation of which is possible thanks to
+the Bayesian foundation of the classification model.\\
+This construct guides the selection of records to be manually review and
+gets dynamically updated and reduced after each CR iteration, as more
+uncertain predictions are evaluated (Supplemental Material S2 Fig. 1).\\
 This approach overcomes the usual requirement of dataset-specific hard
@@
 multiple items at once between iterations (Laws and Schütze 2008; Miwa
-et al. 2014; Zhu et al. 2010). The parameters our algorithm needs are
-instead general and non task-specific, like the PPD intervals based on
-which the uncertainty zone is built, and the maximum number of
-iterations with no positive matches after which a session is concluded;
-the hyperparameter evaluation shows that the algorithm is robust against
+et al. 2014; Zhu et al. 2010). The parameters required by our algorithm
+are general and non task-specific, like the PPD intervals based on which
+the uncertainty zone is built, and the maximum number of iterations
+without positive matches after which a session is concluded; evaluation
+of the hyperparameters shows that the algorithm is robust against
 variations in these parameters and we expect the default values to
@@
 
-We evaluated performance as the capability of the screening procedure
+We assessed performance as the ability of the screening procedure
 (automatic classification plus manual review) to find the largest number
-of relevant records while reviewing as few of them as possible (i.e.,
-sensitivity \(\times\) efficiency).\\
-We avoided the classic out-of-sample approaches like train-test
+of relevant records while requiring manual reviewing for as few of them
+as possible (i.e., sensitivity \(\times\) efficiency).\\
+We avoided the classical out-of-sample approaches such as train-test
 sampling, out-of-bag bootstrapping or cross-validation (Kohavi et al.
 1995; James et al. 2013). Such methods primarily assume that the rate of
-positivity is equal on average in every random subset of the data
-(Tashman 2000); this uniformity is broken by how the initial training
-set and the subsequent reviewed records are selected by the query-based
-ordering and the active learning algorithm, determining a lower
-positivity rate in the unlabelled records (Fig. 2). Also, a literature
-corpus is unique per search query/database combination, and therefore
-any out-of-sample performance estimate is not replicable since no new
-data can be acquired related to the current corpus.\\
-Instead, to estimate overall sensitivity, we employed simple Bayesian
-regression (surrogate model) on the manually reviewed data to abstract
+positivity is the same on average in every possible random subset of the
+data (Tashman 2000); this uniformity is broken by how the initial
+training set and the subsequent reviewed records are selected by the
+query-based ordering and active learning algorithm, resulting in a lower
+positivity rate in the unlabelled records (Fig. 2). Moreover, a
+literature corpus is unique per search query/database combination, and
+therefore any out-of-sample performance estimate is not replicable since
+no new data can be acquired related to the current corpus.\\
+To estimate overall sensitivity, we instead applied simple Bayesian
+regression (surrogate model) to the manually reviewed data to abstract
 the classification model predictions and achieve a maximum entropy
@@
 surrogate model fitted the data very well (\(R^2\) consistently above
-97\%) using just the lower 98\% PrI bound of the PPDs as predictor,
+97\%) using only the lower 98\% PrI boundary of the PPDs as predictor,
 indicating predictive consistency in the classification model. The
-surrogate model posterior predictive distribution could be exploited to
-explore worse case scenarios in terms of sensitivity.\\
-
-Our framework achieved very high sensitivity by screening a markedly
-small fraction of all records, bringing a sensible reduction in
+posterior predictive distribution of the surrogate model could be used
+to explore worse case scenarios in terms of sensitivity.\\
+
+By screening only a very small fraction of all records, our framework
+achieves very high sensitivity, bringing a meaningful reduction in
 workload.\\
@@
 (screening 1.34\% of records): efficiency increased significantly in the
-second session since only a few new positive matches were found, but
-given the large number of records, uncertainty regarding sensitivity
-also expectedly increased.\\
-Both results are above the usual performance in the field (O'Mara-Eves
-et al. 2015) and in line with the 92\% average sensitivity estimated
-after human-only screening (Edwards et al. 2002). In one interesting
-case, the model spotted a human-made misclassification error,
-demonstrating its robustness and value as a second screener, a role
-already suggested for SRA tools by previous studies (Frunza, Inkpen, and
-Matwin 2010; Bekhuis and Demner-Fushman 2012, 2010). Finally, albeit the
-simple query ordering already concentrated most of the relevant matches
-in the first 20-25 thousand records, without the tool support some
-relevant records would have required almost the complete data set to be
-manually checked to be found.\\
-
-The model took \textasciitilde5-20 minutes per iteration to perform
-predictions in session 1 (17,755 documents) and 20-40 minutes in session
-2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM laptop from
-2014; including manual record review, one session required 1-3 days of
+second session as only a few new positive matches were found; however,
+given the large number of records, uncertainty about sensitivity also
+increased, as expected.\\
+Both results are above the usual performance in this field (O'Mara-Eves
+et al. 2015) and are in line with the average sensitivity of 92\%
+estimated after human-only screening (Edwards et al. 2002). In one
+interesting case, the model detected a human-caused misclassification
+error, demonstrating its robustness and value as a second screener, a
+role already suggested for SRA tools in previous studies (Frunza,
+Inkpen, and Matwin 2010; Bekhuis and Demner-Fushman 2012, 2010).
+Although ``simple query ordering'' concentrated most relevant matches in
+the first 20-25 thousand records, without the tool support the remaining
+relevant records would have been missed withouth manually screeening
+almost the entire dataset.\\
+
+The model required \textasciitilde5-20 minutes per iteration to perform
+the predictions in session 1 (17,755 documents) and 20-40 minutes in
+session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM, 2014
+laptop; including manual record review, one session required 1-3 days of
 work, for a total of 1-2 weeks for the whole process (including record
-collection). That is a considerable saving of time compared to the
-multiple months usually required for the screening phase of systematic
-reviews (Bannach-Brown et al. 2019; Borah et al. 2017; Allen and Olkin
-1999). To our knowledge, the amount of data processed
-(\textasciitilde100.000 records) were larger than what is typical in
-most SRA studies (O'Mara-Eves et al. 2015; Olorisade et al. 2016),
-emphasising the reliability of the tool in real-world scenarios.\\
-
-The last module of our framework is a data-driven query generation
-algorithm. Creating an efficient and efficacious search query is a
-complex task (Lefebvre et al. 2011; Hammerstrøm et al. 2010); it
+collection). This is a considerable time saving compared to the several
+months typically required for the screening phase of systematic reviews
+(Bannach-Brown et al. 2019; Borah et al. 2017; Allen and Olkin 1999). To
+our knowledge, the amount of data processed (\textasciitilde100,000
+records) was larger than what is typical of most SRA studies
+(O'Mara-Eves et al. 2015; Olorisade et al. 2016), highlighting the
+scalability of the tool in real-world scenarios.\\
+
+The last module of our framework is an algorithm for data-driven search
+query generation. Generating an efficient and effective search query is
+a complex task (Lefebvre et al. 2011; Hammerstrøm et al. 2010); it
 requires building a combination of positive and negative terms to
 maximise the number of relevant search results while minimising the
-total number of records to review. Our solution joins a
+total number of records to be reviewed. Our solution combines a
 sensitivity-driven subquery proposal engine based on concurrent decision
@@
 on the BART ensemble PPD, with a human review step and an
-efficiency-driven query builder. The aim is to generate a second query
-that helps find records missed during the first session search. The
-generated query allowed indeed to retrieve few more positive matches not
-found in session 1, but at the cost of a significant increase in the
-number of documents.\\
-One interesting aspect of this functionality is that it provides a
+efficiency-driven query builder. The aim is to generate a new search
+query to help find records missed in the first search session. The
+generated query did indeed to retrieve a few more relevant records that
+were not found in session 1, but at the cost of a significant increase
+in the number of documents.\\
+An interesting aspect of this feature is that it provides a
 human-readable overview of the classification rules learned by the
@@
 locations associated with the study topic. The generated query,
-therefore, acted as a tool for machine learning explainability (Bhatt et
-al. 2020; Burkart and Huber 2021), a feature useful to understand and
-spot bias in black-box classification algorithms (Malhi, Knapic, and
-Främling 2020); explainability is often required or even legally
-mandatory for high-stake machine learning applications (Bibal et al.
-2021, 2020).\\
+therefore, served also as a means for machine learning explainability
+(Bhatt et al. 2020; Burkart and Huber 2021), useful for understanding
+and detecting biases in black-box classification algorithms (Malhi,
+Knapic, and Främling 2020); explainability is often required or even
+legally mandatory for high-stake machine learning applications (Bibal et
+al. 2021, 2020).\\
 It is important to note that this process is entirely data-driven. The
-algorithm is only aware of the ``world'' defined by the data set used as
+algorithm is only aware of the ``world'' defined by the dataset used as
 input, which is generated by a specific search query focused on a
 particular topic. Therefore, the new query may not be specific enough
-once applied to an unbounded search domain, returning an unmanageable
-amount of unrelated results. The solution we found was to add another
-component to the query, specifying the general topic (antimicrobial
-resistance and healthcare-associated infections) of our research.\\
-
-As reported, our framework builds on modularity. We designed it to
-easily implement complete independence of the main modules in future
-iterations, making it possible for users to add custom features like
-citation search and parsing for other scientific databases, alternative
-text processing algorithms or machine learning modules. We deem such
-interoperability extremely relevant because the main strength of our
-tool is the composition of many solutions and the general idea of
-Bayesian active machine learning and the exploit of the derived
-uncertainty in predictions. However, each of its components could
-benefit considerably from the recent improvements in text mining.\\
-For example, our text processing approach is quite simple, based on the
-boolean bag-of-words paradigm, and indeed could be improved by more
-nuanced text representations. It could be evaluated if feature
-transformations like TF-IDF (Baeza-Yates, Ribeiro-Neto, et al. 1999;
-Ananiadou and McNaught 2006) would be advantageous, even if we
-hypothesise that tree-based classification algorithms like BART are
-robust enough not to need such operations. Word embedding could be
-instead worth exploring: this technique transforms terms in semantic
-vectors derived from the surrounding text Minaee et al. (2021) and could
-be used to eliminate semantically redundant terms or differentiate
-identical terms with different meanings given the context. Another
-option would be to employ unsupervised learning models like Latent
-Dirichlet Analysis, Latent Semantic Analysis (Pavlinek and Podgorelec
-2017; Q. Chen, Yao, and Yang 2016; Landauer, Foltz, and Laham 1998) or
-graph-of-word techniques (Ohsawa, Benson, and Yachida 1998; Francois
-Rousseau 2015) to extract topics to enrich the feature space.\\
-Our classification algorithm can be implemented with any Bayesian
-supervised machine learning method that provides full PPDs; therefore
-alternative classification models could be evaluated, like Gaussian
-Processes which are known for their flexibility (Jayashree and Srijith
-2020; S.-H. Chen et al. 2015). Even more interesting would be to test
-advanced learning algorithms that surpass the bag-of-words approach,
-taking into consideration higher-level features in the text like term
+when applied to an unbounded search domain, and may return an
+unmanageable amount of unrelated results. The solution we found was to
+add another component to the query, specifying the general topic
+(antimicrobial resistance and healthcare-associated infections) of our
+research.\\
+
+As mentioned early, our framework builds on modularity. We have designed
+it in such a way that full independence of the main modules can be
+easily implemented in future iterations; it will be possible for users
+to add custom features such as citation search and parsing for other
+scientific databases, alternative text processing algorithms or machine
+learning modules. We consider such interoperability to be extremely
+relevant: the main strength of our tool lies in the composition of many
+solutions such as the idea of Bayesian active machine learning and the
+exploit of the derived uncertainty in defining the records needing human
+review.\\
+However, each components could benefit considerably from the recent
+improvements in text mining and machine learning.\\
+For example, our text processing approach, based on the ``boolean
+bag-of-words'' paradigm, is quite simple, and indeed could be improved
+by more nuanced text representations. It might be considered whether
+feature transformations such as TF-IDF (Baeza-Yates, Ribeiro-Neto, et
+al. 1999; Ananiadou and McNaught 2006) could be advantageous, although
+we hypothesise that tree-based classification algorithms like BART are
+robust enough not to require such operations. Instead, it might be worth
+exploring the application of word embedding: this technique transforms
+terms into semantic vectors derived from the surrounding text (Turian,
+Ratinov, and Bengio 2010; Bollegala, Maehara, and Kawarabayashi 2015;
+Minaee et al. 2021) and could be used to reduce noise by merging
+different terms that are semantically similar and enhance signal by
+distinguishing identical terms with different meaning given the context.
+Another option would be to employ unsupervised learning models like
+Latent Dirichlet Analysis, Latent Semantic Analysis (Pavlinek and
+Podgorelec 2017; Q. Chen, Yao, and Yang 2016; Landauer, Foltz, and Laham
+1998) or graph-of-word techniques (Ohsawa, Benson, and Yachida 1998;
+Francois Rousseau 2015) to extract topics to expand the feature space.\\
+Our classification algorithm is applicable with any Bayesian supervised
+machine learning method that provides full PPDs; therefore, alternative
+classification models, such as Gaussian Processes which are known for
+their flexibility (Jayashree and Srijith 2020; S.-H. Chen et al. 2015),
+could be evaluated. It would be even more interesting to test advanced
+learning algorithms that go beyond the bag-of-words approach and take
+into consideration higher-level features in the text such as term
 context and sequences, long-distance term relationships, semantic
 structures, etc., (Cheng et al. 2019; Minaee et al. 2021; Li et al.
-2020; J. Yang, Bai, and Guo 2020; Lai et al. 2015; Farkas 1995), given
-that a Bayesian implementation of such algorithms is available (for
-example C. Chen, Lin, and Terejanu (2018)).\\
+2020; J. Yang, Bai, and Guo 2020; Lai et al. 2015; Farkas 1995),
+provided that a Bayesian implementation of such algorithms is available
+(for example C. Chen, Lin, and Terejanu (2018)).\\
 Finally, a natural improvement would be to provide a graphical user
@@
 
-The field of literature review automation is maturing rapidly, and we
-expect an increasing use of such technologies to manage the ever-faster
-rate of scientific production. We believe it is appreciable that a
-multiplicity of tools are being made available to let researchers and
-policymakers find the instrument that better fits their needs.\\
-We contribute to this field with an innovative framework that provide
-excellent performance and easy integration with existing systematic
-review pipelines. The value of this work lies not only in the framework
-itself, which we provide as open-source software, but in the set of
-methodologies we developed to solve various SRA issues and that can be
-used to improve already existing solutions.\\
+The field of literature review automation is evolving rapidly, and we
+anticipate an increasing use of such technologies to address the
+accelerating pace of scientific production. We believe it is encouraging
+that a wide variety of tools are being made available to allow
+researchers and policymakers find the approach that best fits their
+needs.\\
+We are contributing to this field with an innovative framework that
+provides excellent performance and easy integration with existing
+systematic review pipelines. The value of this work lies not only in the
+framework itself, which we make available as open-source software, but
+also in the set of methodologies we developed to solve various SRA
+issues and which can also be used to improve already existing
+solutions.\\
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-robert2004monte}{}}%
-Robert, Christian P, George Casella, and George Casella. 2004.
-\emph{Monte Carlo Statistical Methods}. Vol. 2. Springer.
+Robert, Christian P, and George Casella. 2004. \emph{Monte Carlo
+Statistical Methods}. Vol. 2. Springer.
 

### 2022-02-19 Manuscript/Manuscript_Discussion.Rmd
English proof reading and better number formatting

@@
 
-We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
+We propose a new integrated framework to help researchers collect and screen scientific publications that is characterised by high performance and versatility.
+This framework joins the joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
 This framework implements standard approaches and uses ad-hoc solutions to deal with common SRA issues.
-By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
+By freely sharing the tool as an open-source R package and by following a modular design, we sought to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
 The framework consists of four main components: 1) an integrated query-based citation search and management engine, 2) a Bayesian active machine learning-based citation classifier, and 3) a data-driven search query generation algorithm.\
 
-The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the two more (SCOPUS, EMBASE) databases.
-In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
-Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
-in our results, 18.7% of the positive matches found only in one of the different data sources, and no positive record was present in all of them (data not shown).\
-The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of online citation databases in terms of traffic and download quotas.
+The search engine module used by the framework is able to  automatically collect citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) asand to process manually downloaded results from both the two more databases (SCOPUS, EMBASE).
+In comparison, most commercial or free SRH tools, rely on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing only on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
+Mixing different databases is essential to obstain a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
+in our results, 18.7% of the positive matches were found in only one of the different data sources, and no positive record was present in all the sources (data not shown).\
+The framework online search algorithms are efficient enough to manage tens of thousands of search results, using various solutions to overcome the limitations of citation databases in terms of traffic and download quotas.
 The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
@@
 
-For the framework's record classification module, we employed an active machine learning approach [@settles2009active, @miwa2014reducing] based on the best practices from other SRA studies but also bringing further improvements at various levels.\
+For the framework's record classification module, we developed an active machine learning approach [@settles2009active; @miwa2014reducing] which is based on the best practices from other SRA studies but also brings further improvements at various levels.\
 The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
-We did not include classical n-grams [@schonlau2017text], but we used network analysis to find non-consecutive frequently associated terms, a generalisation of n-grams relaxing the term adjacency assumption.
-This approach allows also to find term connections across fields, for example a term having a different relevancy if associated with a specific author.
-The same technique but with different parameters was applied to merge redundant terms to make model estimation more efficient and reduce noise.\
-The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\
+We did not include classical n-grams [@schonlau2017text];
+rather we used network analysis to find non-consecutive, frequently associated terms, a generalisation of n-grams that relaxes the term adjacency assumption.
+This approach can also be used to find term connections across parts of the records, e.g., whether a term has a different relevance when associated with a particular author.
+The same technique, albeit with different parameters, was used to merge redundant terms to make the model estimation more efficient and reduce noise.\
+The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information that is not evident in one-word or consecutive n-gram models.\
 
 The automatic classification algorithm is based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine].
-As with other boosted trees algorithms [@hastie2009boosting], BART can explore complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.\
-However, its Bayesian foundation provides further benefits:
-less sensitivity on hyperparameter choices, natural regularisation through priors, and, especially, predictive distributions as output in place of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
-By selecting relatively tight prior distributions, we discouraged excessively deep trees, long sequences of trees, or extreme predicted probabilities, to decrease the risk of overfitting.\
+Like other boosted trees algorithms [@hastie2009boosting], the BART method can explore complex non-linearities, perform variable selection, manage missing data while maintaining high predictive power.\
+However, the Bayesian foundation of the method provides further benefits:
+lower sensitivity to the choice of hyperparameters, natural regularisation through priors, and, most imporantly, predictive distributions as output instead of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
+By selecting relatively tight prior distributions, we discouraged overly deep trees, long tree sequences, and extreme predicted probabilities, this reducing the risk of overfitting.\
 The algorithm runs multiple replications of the model and averages their predictive distributions creating an "ensemble";
 this technique has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble], as we were able to confirm during the hyperparameter evaluation (Supplemental Material S2).
-Ensembling reduces the uncertainty in the predictive distribution tails related to the randomness in the MCMC fit [@robert2004monte], generating a shift of probability mass towards the distribution centre and stabilising it (i.e., decreasing variance without impacting bias).
-On the other hand, just imposing robust uninformative priors against extreme predictions would have decreased variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
-Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which performance stabilised during the hyperparameter evaluation.\
-We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory [@diez2015diversity], it appeared to be slightly detrimental in our case (Supplemental Material S2) compared to simple ensembling.\
+Ensembling reduces the uncertainty in the predictive distribution tails related to the randomness in the MCMC fit [@robert2004monte], generating a shift in the probability mass towards the distribution centre and stabilising it (i.e., reducing variance without impacting bias).
+On the other hand, simply imposing more robust uninformative priors against extreme predictions would have reduced variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
+Since the number of model replications has a significant impact on computation times, we decided to use ten replicas, the lower value after which performance stabilised, as resulted from the evaluation of the hyperparameters (Supplemental Material S2, Fig.
+2).\
+We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance;
+however, contrary to theory [@diez2015diversity], it appeared to be slightly detrimental in our case (Supplemental Material S2, Fig. 2) compared to simple ensembling.\
 
-A low rate of relevant matches (class imbalance) is typical in literature reviews [@sampson2011precision; @wallace2010semi; @o2015using], and such strong imbalance between positive and negative records can affect sensitivity [@khoshgoftaar2010comparing; @chawla2004special].\
-To overcome the problem, we oversampled [@batista2004study] the positive records ten times before model fitting.
-Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance.\
+A low rate of relevant matches (class imbalance) is typical for literature reviews [@sampson2011precision; @wallace2010semi; @o2015using], and a strong imbalance between positive and negative records can affect sensitivity [@khoshgoftaar2010comparing; @chawla2004special].\
+To overcome this problem, we oversampled [@batista2004study] the positive records ten times before model fitting.
+The hyperparameter analysis showed that the oversampling rate, together with model ensembling, was the parameter with the greatest impact on performance.\
 A known risk with positive oversampling is the misclassification of negative records [@ramezankhani2016impact].
-However, since all predicted positives get manually reviewed in our approach, we are always ensured to achieve 100% specificity/positive predictive value: the only price for the increased sensitivity due to oversampling is a larger number of records to review.\
-An alternative to oversampling would be applying different weights and/or cost to the classes [@abd2013review; @diez2015diversity], but the BART implementation we used did not have this feature;
-also, using simple oversampling permits broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
-Finally, ordering the records by query term frequency (simple query ordering) generates a far higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), and this boosts the sensitivity of the model.\
+However, since all predicted positives in our approach are reviewed manually, we are always guaranteed to achieve 100% specificity/positive predictive value:
+the only price for the increased sensitivity due to oversampling is a larger number of records to be reviewed.\
+An alternative to oversampling would be to apply different weights and/or costs to the classes [@abd2013review; @diez2015diversity], but the BART implementation we used did not have this feature;
+furthermore, using simple oversampling allows for broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
+Finally, sorting the records by query term frequency (simple query ordering) produces a much higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), which boosts the sensitivity of the model.\
 
-One of the central innovations we introduced is the concept of "uncertainty zone", whose implementation is possible thanks to the Bayesian foundation of the classification model.
-This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig.
+One of the key innovations we have introduced is the concept of "uncertainty zone", thie implementation of which is possible thanks to the Bayesian foundation of the classification model.\
+This construct guides the selection of records to be manually review and gets dynamically updated and reduced after each CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig.
 1).\
 This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
-The parameters our algorithm needs are instead general and non task-specific, like the PPD intervals based on which the uncertainty zone is built, and the maximum number of iterations with no positive matches after which a session is concluded;
-the hyperparameter evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to perform well on most datasets.\
+The parameters required by our algorithm are general and non task-specific, like the PPD intervals based on which the uncertainty zone is built, and the maximum number of iterations without positive matches after which a session is concluded;
+evaluation of the hyperparameters shows that the algorithm is robust against variations in these parameters and we expect the default values to perform well on most datasets.\
 Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\
 
-We evaluated performance as the capability of the screening procedure (automatic classification plus manual review) to find the largest number of relevant records while reviewing as few of them as possible (i.e., sensitivity $\times$ efficiency).\
-We avoided the classic out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study; @james2013introduction].
-Such methods primarily assume that the rate of positivity is equal on average in every random subset of the data [@tashman2000out];
-this uniformity is broken by how the initial training set and the subsequent reviewed records are selected by the query-based ordering and the active learning algorithm, determining a lower positivity rate in the unlabelled records (Fig.
+We assessed performance as the ability of the screening procedure (automatic classification plus manual review) to find the largest number of relevant records while requiring manual reviewing for as few of them as possible (i.e., sensitivity $\times$ efficiency).\
+We avoided the classical out-of-sample approaches such as train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study; @james2013introduction].
+Such methods primarily assume that the rate of positivity is the same on average in every possible random subset of the data [@tashman2000out];
+this uniformity is broken by how the initial training set and the subsequent reviewed records are selected by the query-based ordering and active learning algorithm, resulting in a lower positivity rate in the unlabelled records (Fig.
 2).
-Also, a literature corpus is unique per search query/database combination, and therefore any out-of-sample performance estimate is not replicable since no new data can be acquired related to the current corpus.\
-Instead, to estimate overall sensitivity, we employed simple Bayesian regression (surrogate model) on the manually reviewed data to abstract the classification model predictions and achieve a maximum entropy [@harremoes2001maximum] estimate of the number of missed positive matches among the unreviewed records in the whole dataset.
-This simple surrogate model fitted the data very well ($R^2$ consistently above 97%) using just the lower 98% PrI bound of the PPDs as predictor, indicating predictive consistency in the classification model.
-The surrogate model posterior predictive distribution could be exploited to explore worse case scenarios in terms of sensitivity.\
+Moreover, a literature corpus is unique per search query/database combination, and therefore any out-of-sample performance estimate is not replicable since no new data can be acquired related to the current corpus.\
+To estimate overall sensitivity, we instead applied simple Bayesian regression (surrogate model) to the manually reviewed data to abstract the classification model predictions and achieve a maximum entropy [@harremoes2001maximum] estimate of the number of missed positive matches among the unreviewed records in the whole dataset.
+This simple surrogate model fitted the data very well ($R^2$ consistently above 97%) using only the lower 98% PrI boundary of the PPDs as predictor, indicating predictive consistency in the classification model.
+The posterior predictive distribution of the surrogate model could be used to explore worse case scenarios in terms of sensitivity.\
 
-Our framework achieved very high sensitivity by screening a markedly small fraction of all records, bringing a sensible reduction in workload.\
+By screening only a very small fraction of all records, our framework achieves very high sensitivity, bringing a meaningful reduction in workload.\
 Based on the surrogate model, we predicted a predicted median sensitivity of 100% [93.5%, 100%] in the first session (screening 4.29% of records) and of 97.3% [73.8%, 100%] in the second (screening 1.34% of records):
-efficiency increased significantly in the second session since only a few new positive matches were found, but given the large number of records, uncertainty regarding sensitivity also expectedly increased.\
-Both results are above the usual performance in the field [@o2015using] and in line with the 92% average sensitivity estimated after human-only screening [@edwards2002identification].
-In one interesting case, the model spotted a human-made misclassification error, demonstrating its robustness and value as a second screener, a role already suggested for SRA tools by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
-Finally, albeit the simple query ordering already concentrated most of the relevant matches in the first 20-25 thousand records, without the tool support some relevant records would have required almost the complete data set to be manually checked to be found.\
+efficiency increased significantly in the second session as only a few new positive matches were found;
+however, given the large number of records, uncertainty about sensitivity also increased, as expected.\
+Both results are above the usual performance in this field [@o2015using] and are in line with the average sensitivity of 92% estimated after human-only screening [@edwards2002identification].
+In one interesting case, the model detected a human-caused misclassification error, demonstrating its robustness and value as a second screener, a role already suggested for SRA tools in previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
+Although "simple query ordering" concentrated most relevant matches in the first 20-25 thousand records, without the tool support the remaining relevant records would have been missed withouth manually screeening almost the entire dataset.\
 
-The model took ~5-20 minutes per iteration to perform predictions in session 1 (17,755 documents) and 20-40 minutes in session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM laptop from 2014;
+The model required ~5-20 minutes per iteration to perform the predictions in session 1 (17,755 documents) and 20-40 minutes in session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM, 2014 laptop;
 including manual record review, one session required 1-3 days of work, for a total of 1-2 weeks for the whole process (including record collection).
-That is a considerable saving of time compared to the multiple months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
-To our knowledge, the amount of data processed (~100.000 records) were larger than what is typical in most SRA studies [@o2015using; @olorisade2016critical], emphasising the reliability of the tool in real-world scenarios.\
+This is a considerable time saving compared to the several months typically required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
+To our knowledge, the amount of data processed (~100,000 records) was larger than what is typical of most SRA studies [@o2015using; @olorisade2016critical], highlighting the scalability of the tool in real-world scenarios.\
 
-The last module of our framework is a data-driven query generation algorithm.
-Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching];
-it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to review.
-Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD, with a human review step and an efficiency-driven query builder.
-The aim is to generate a second query that helps find records missed during the first session search.
-The generated query allowed indeed to retrieve few more positive matches not found in session 1, but at the cost of a significant increase in the number of documents.\
-One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
-The generated query, therefore, acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to understand and spot bias in black-box classification algorithms [@malhi2020explainable];
+The last module of our framework is an algorithm for data-driven search query generation.
+Generating an efficient and effective search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching];
+it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to be reviewed.
+Our solution combines a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD, with a human review step and an efficiency-driven query builder.
+The aim is to generate a new search query to help find records missed in the first search session.
+The generated query did indeed to retrieve a few more relevant records that were not found in session 1, but at the cost of a significant increase in the number of documents.\
+An interesting aspect of this feature is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
+The generated query, therefore, served also as a means for machine learning explainability [@bhatt2020machine; @burkart2021survey], useful for understanding and detecting biases in black-box classification algorithms [@malhi2020explainable];
 explainability is often required or even legally mandatory for high-stake machine learning applications [@bibal2021legal; @bibal2020impact].\
 It is important to note that this process is entirely data-driven.
-The algorithm is only aware of the "world" defined by the data set used as input, which is generated by a specific search query focused on a particular topic.
-Therefore, the new query may not be specific enough once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
+The algorithm is only aware of the "world" defined by the dataset used as input, which is generated by a specific search query focused on a particular topic.
+Therefore, the new query may not be specific enough when applied to an unbounded search domain, and may return an unmanageable amount of unrelated results.
 The solution we found was to add another component to the query, specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research.\
 
-As reported, our framework builds on modularity.
-We designed it to easily implement complete independence of the main modules in future iterations, making it possible for users to add custom features like citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
-We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general idea of Bayesian active machine learning and the exploit of the derived uncertainty in predictions.
-However, each of its components could benefit considerably from the recent improvements in text mining.\
-For example, our text processing approach is quite simple, based on the boolean bag-of-words paradigm, and indeed could be improved by more nuanced text representations.
-It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operations.
-Word embedding could be instead worth exploring:
-this technique transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep] and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.
-Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics to enrich the feature space.\
-Our classification algorithm can be implemented with any Bayesian supervised machine learning method that provides full PPDs;
-therefore alternative classification models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
-Even more interesting would be to test advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher-level features in the text like term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
+As mentioned early, our framework builds on modularity.
+We have designed it in such a way that full independence of the main modules can be easily implemented in future iterations;
+it will be possible for users to add custom features such as citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
+We consider such interoperability to be extremely relevant:
+the main strength of our tool lies in the composition of many solutions such as the idea of Bayesian active machine learning and the exploit of the derived uncertainty in defining the records needing human review.\
+However, each components could benefit considerably from the recent improvements in text mining and machine learning.\
+For example, our text processing approach, based on the "boolean bag-of-words" paradigm, is quite simple, and indeed could be improved by more nuanced text representations.
+It might be considered whether feature transformations such as TF-IDF [@baeza1999modern; @ananiadou2006text] could be advantageous, although we hypothesise that tree-based classification algorithms like BART are robust enough not to require such operations.
+Instead, it might be worth exploring the application of word embedding:
+this technique transforms terms into semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding; @minaee2021deep] and could be used to reduce noise by merging different terms that are semantically similar and enhance signal by distinguishing identical terms with different meaning given the context.
+Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics to expand the feature space.\
+Our classification algorithm is applicable with any Bayesian supervised machine learning method that provides full PPDs;
+therefore, alternative classification models, such as Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian], could be evaluated.
+It would be even more interesting to test advanced learning algorithms that go beyond the bag-of-words approach and take into consideration higher-level features in the text such as term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], provided that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
 Finally, a natural improvement would be to provide a graphical user interface to make the framework easy to use also for less technical users.
 
-The field of literature review automation is maturing rapidly, and we expect an increasing use of such technologies to manage the ever-faster rate of scientific production.
-We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.\
-We contribute to this field with an innovative framework that provide excellent performance and easy integration with existing systematic review pipelines.
-The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of methodologies we developed to solve various SRA issues and that can be used to improve already existing solutions.\
+The field of literature review automation is evolving rapidly, and we anticipate an increasing use of such technologies to address the accelerating pace of scientific production.
+We believe it is encouraging that a wide variety of tools are being made available to allow researchers and policymakers find the approach that best fits their needs.\
+We are contributing to this field with an innovative framework that provides excellent performance and easy integration with existing systematic review pipelines.
+The value of this work lies not only in the framework itself, which we make available as open-source software, but also in the set of methodologies we developed to solve various SRA issues and which can also be used to improve already existing solutions.\

### 2022-02-19 Manuscript/Manuscript_Introduction.Rmd
added extra line before references
English proof reading and better number formatting

@@
 Scientific production has experienced continuous exponential growth in the last decades [@larsen2010rate; @bornmann2015growth].
-This is especially true for biomedical research, a trend further increased by the COVID-19 pandemic, thanks to faster article' processing time by publishers and the diffusion of preprint databases' usage [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].
-Consequently, it gets harder for researchers and practitioners to stay up-to-date on the latest findings in their field.
-Secondary research is of paramount relevance in this scenario, providing valuable summaries of the latest research results, but is getting ever more demanding in terms of time and human resources [@allen1999estimating; @borah2017analysis; @cohen2010evidence; @bastian2010seventy].\
+This is especially true for biomedical research, a trend further accelerated by the COVID-19 pandemic, thanks to faster article' processing time by publishers and the greater use of preprint databases [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].
+Consequently, it has become harder for researchers and practitioners to stay up to date on the latest findings in their field.
+Secondary research is of paramount importance in this scenario in that it provides valuable summaries of the latest research results;
+however, it is becoming ever more challenging in terms of time and human resources required [@allen1999estimating; @borah2017analysis; @cohen2010evidence; @bastian2010seventy].\
 The article collection and screening phases of a systematic review are particularly demanding [@babar2009systematic].
-First, relevant published research needs to be collected from scientific databases through appropriately built search queries (retrieval phase); secondly, the acquired scientific citations need to be screened, selecting only those relevant to the topic (appraisal phase) [@bannach2019machine; @tsafnat2014systematic; @higgins2019cochrane].\
-The construction of search queries is a complex task [@lefebvre2011searching; @hammerstrom2010searching], requiring both domain and some knowledge of the databases' query languages;
-the goal is to produce a set of results containing all relevant articles (high sensitivity) while keeping the total number low (high specificity), focusing on the first aspect at the cost of the second [@hammerstrom2010searching].
+First, relevant published research must be collected from scientific databases using appropriately built search queries (retrieval phase); secondly, the scientific citations collected must be screened, selecting only those that are relevant to the topic (appraisal phase) [@bannach2019machine; @tsafnat2014systematic; @higgins2019cochrane].\
+Search queries construction is a complex task [@lefebvre2011searching; @hammerstrom2010searching], requiring both expertise in the scientific field of interest and some knowledge of the database query languages.
+The goal is to obtain a set of results that contains all relevant articles (high sensitivity) while keeping the total number of records low (high specificity),
+possibly focusing on the first at the expense of the second [@hammerstrom2010searching].\
 If an integrated search tool is not used, manual work is required to download, store and organise the publication data;
-this approach is complicated by limits in the number of records that can be downloaded at once and the necessity to harmonise different formats and resolve record duplication [@marshall2015systematic].\
-The citation screening phase is usually the more resource-demanding task of a systematic review:
-even with appropriately built search queries, the returned results easily range in the tens of thousands of which just a small fraction is actually relevant [@lefebvre2011searching].
-It was estimated that labelling 10,000 publications may take as much as 40 weeks of work and that the average clinical systematic review takes 63 weeks to be completed [@bannach2019machine; @borah2017analysis; @allen1999estimating].
-A consequence is that often systematic reviews are already outdated once they are published [@beller2013systematic].\
+this approach is complicated by limits to the number of records that can be downloaded at any one time and the need to harmonise different formats and resolve record duplication [@marshall2015systematic].\
+The citation screening phase is usually the more resource-demanding task in a systematic review:
+even with appropriately built search queries, the results may easily range in the tens of thousands, of which just a small fraction are actually relevant [@lefebvre2011searching].
+It has been estimated that labelling 10,000 publications can take up to 40 weeks of work and that the average clinical systematic review takes 63 weeks to complete [@bannach2019machine; @borah2017analysis; @allen1999estimating].
+A consequence of this is systematic reviews are often already out-of-date by the time they are published [@beller2013systematic].\
 The field of Data Science applied to evidence synthesis and acquisition has greatly maturated in the last years [@marshall2015systematic; @beller2018making; @tsafnat2014systematic].
-Through the application of natural language processing (NLP), it is possible to transform free text into quantitative features, with various levels of abstraction and generalisation [@ananiadou2006text; @cohen2008getting];
-with machine learning, such text-derived data can be used to map and reproduce human judgment, automating the citation screening [@ikonomakis2005text].\
-The automation of systematic reviews has been ripe with improvements in the last years [@ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating], and it is possible to foresee that it is going to become the standard approach in the field [@beller2018making], with many solutions already being turned into commercial and free-to-use tools [see @marshall2015systematic, table 1].\
-In this manuscript we present an open source, production-ready framework which further contributes to the state-of-the-art in systematic review automation (SRA) and helpers (SRH) tools.
-We improve the "retrieval phase" by providing a unified framework for the automatic collection and management of scientific literature from multiple online sources.
-For the citation screening (appraisal) phase, we built an active machine learning-based [@settles2009active, @miwa2014reducing; @miwa2014reducing] protocol, which exploits a Bayesian framework to efficiently identify potentially relevant documents that require human review while automatically screening-out the large majority of clearly non-relevant ones;
-the algorithm then uses human reviews to iteratively increase classification accuracy.
-Finally, we included a tool to generate new search queries given an already labelled citation data set, in order to identify relevant research possibly missed by human-made queries.\
-We tested the framework in the retrieval and appraisal phases of an example topic of interest for our group:
+By applying natural language processing (NLP), it is possible to transform free text into quantitative features, with various levels of abstraction and generalisation [@ananiadou2006text; @cohen2008getting];
+using machine learning, such text-derived data can be used to map and reproduce human judgment, automating the screening of citations [@ikonomakis2005text].\
+Automation of systematic reviews has made significant improvements in the last years [@ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating], and it is possible foreseeable that it will become the standard approach in the field [@beller2018making], with many solutions already being implemented into commercial or free-to-use tools [see @marshall2015systematic, table 1].\
+In this manuscript, we present an open source, production-ready framework that further contributes to the state-of-the-art in systematic review automation (SRA) and helpers (SRH) tools.
+We improve the "retrieval phase" by providing a unified framework for the automated collection and management of scientific literature from multiple online sources.
+For the citation screening (appraisal) phase, we built an active machine learning-based protocol [@settles2009active; @miwa2014reducing],
+which utilises a Bayesian framework to efficiently identify potentially relevant documents that require human review, while automatically screening-out the vast majority of clearly non-relevant ones;
+the algorithm then requires human review to iteratively increase classification accuracy.
+Finally, we included a tool to generate new search queries based on an already labelled citation data set, to identify relevant research that may possibly have been missed by manually-made queries.\
+We tested the framework in the retrieval and appraisal phases of an example topic of interest to our group:
 the evaluation of the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms;
 the protocol is published in [@newis].\
-We give an overview of the framework in the Methods section;
-in the Result section, we show the framework outputs and performance once applied to the example topic;
-in the Discussion, we lay out the methodological justification behind the different components and features of the framework.
+In the Methods, we give an overview of the framework,
+in the Result, we show the outputs and performance of the framework applied to the example topic,
+and in the Discussion, we explain the methodological rationale for the different components and features of the framework.\

### 2022-02-19 Manuscript/Manuscript_Methods.Rmd
English proof reading and better number formatting

@@
 
-We built an R [@rstat] based framework to simplify two aspects of systematic reviews:
+We built an R [@rstat] based framework to simplify two aspects of systematic literature review:
 record acquisition and classification.
-The code used to generate the results in the manuscript is available at X while an update version of the framework is distributed as an R package at Y.
+The code used to generate the results in the manuscript is available at https://github.com/AD-Papers-Material/BART_SystReviewClassifier, while an updated and ready to use version of the framework is distributed as an R package at https://github.com/bakaburg1/BaySREn.
 The framework includes several modules that communicate through intermediate outputs stored in standard formats, which make it possible for users to extend the framework or easily integrate it with other tools in their pipeline.
@@
 
-## Record's acquisition and initial labelling
+## Record acquisition and initial labelling
 
-We built a set of tools to let users automatically search and download citation data from three major scientific databases ("sources"):
+We built a set of tools to allow users to automatically search and download citation data from three major scientific databases ("sources"):
 Pubmed (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
@@
 this is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/>) and EMBASE databases (<https://www.embase.com/>), for which a comprehensive API interface was not easy to build.
-An extra manual search was necessary also for Pubmed, since the API and the web interface have different rule expansion algorithms and return slightly different results [@pubmedUpdate].
-A short guide on how to set up the framework for each supported database is available in Supplemental Material S3.\
-The acquired records are merged into a single database, resolving duplicates and different formatting between sources.
-The records are ordered according to the frequency of the positive query terms (e.g., not preceded by a $NOT$ modifier) in the title and abstract ("simple query ordering").\
+An extra manual search was also necessary for Pubmed, since the API and the web interface have different rule expansion algorithms and return slightly different results [@pubmedUpdate].
+A short guide on how to set up the framework for each database supported is available in Supplemental Material S3.\
+The collected records are merged into a single database, resolving duplicates and different formatting between sources.
+The records are ordered according to the frequency of the positive query terms (e.g., not preceded by a _NOT_ modifier) in the title and abstract ("simple query ordering").\
 The researcher is then asked to label a number of records to create the "initial training set" needed to start the automatic classification.
-We suggest manually labelling the first 250 records (see "hyperparameter optimization" later).
-The simple query ordering increases the positivity rate in the initial training set [@wallace2010active], which provide higher sensitivity during automatic classification [@chawla2004special].
+We recommend manually labelling the first 250 records (see "hyperparameter optimization" later).
+Simple query ordering increases the positivity rate in the initial training set [@wallace2010active], leading to higher sensitivity during automatic classification [@chawla2004special].
 
@@
 
-The collected citation data have a number of fields characterising a scientific publication.
+The collected citation data contain a number of fields characterising a scientific publication.
 The framework models the relevance of a record based on the following fields:
 title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
-A series of Natural Language Processing (NLP) techniques [@baeza1999modern; @marshall2015systematic; @ananiadou2006text] are employed to transform the textual information in these fields into features for machine learning through a bag-of-words approach [@marshall2015systematic].
-The processing of free text fields (title, abstract) includes: tokenization (i.e., extracting the terms), common stopwords (i.e., sentence components bringing no meaning) removal, part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatization of the terms (i.e., reduction to their base grammar form).
-Text processing for authors, keywords and MESH terms identifies logical units (e.g., author's full names, composite keywords) and extracts them.\
+A range of Natural Language Processing (NLP) techniques [@baeza1999modern; @marshall2015systematic; @ananiadou2006text] are employed to convert the textual information in these fields into features for machine learning through a bag-of-words approach [@marshall2015systematic].
+Processing of free text fields (title, abstract) includes: tokenization (i.e., extracting the terms), removal of common stopwords (i.e., sentence components having no semantic value), part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatisation of terms (i.e., reduction to their base grammatical form).
+Text processing for authors, keywords and MESH terms identifies logical units (e.g., authors' full names, composite keywords) and extracts them.\
 Terms appearing in less than 5% of the labelled documents are removed from negative records.
 All terms in the positive set are kept to increase sensitivity at the cost of specificity.\
-Some terms tend to co-appear in records (non-consecutive ngrams, nc-ngrams), often carrying a particular meaning when copresent.
-To detect nc-ngrams, we generated a word network representation [@rousseau2015graph] posing edges between terms with a cosine similarity in terms of record co-occurrence > 0.5.
+Some terms tend to co-appear in records (non-consecutive ngrams, nc-ngrams), often carrying a particular meaning when they do co-occur.
+To detect nc-ngrams, we generated a word network representation [@rousseau2015graph] with edges occurring between terms with a cosine similarity in terms of docuement co-occurrence > 0.5.
 We extracted the maximal cliques in the network [@eppstein2010listing] representing highly correlated groups of terms;
-These groups of terms are added to the data set as individual features.
+these groups are added to the dataset as individual features.
 Only nc-ngrams comprising a maximum of ten terms are kept.\
 A second network is built using a co-occurrence threshold of 0.9.
-In this case, the cliques represent terms that always appear together and therefore can be considered redundant (i.e., they do not need to be considered separately).
-These terms are merged to increase computation efficiency and reduce overfitting.\
+In this case, the cliques represent terms that always appear together and can therefore be considered redundant (i.e., they do not need to be considered separately).
+These terms are merged to increase computational efficiency and reduce overfitting.\
 The output is a Document-Term Matrix (DTM), with $N_d$ rows representing the records ($D_i$), $N_t$ terms column for the $t_{field}$ terms (divided by record field) and ${0,1}$ values whether $t_{field} \in D_i$.
@@
 
-We used a Bayesian Additive Regression Trees (BART) machine learning "classification model" [@chipman2010bart] [in the implementation of @kapelner2013bartmachine] to predict the probability of a record of being relevant, given the information coded into the enriched DTM and the initial training set.
-We set up the BART model to use 2000 MCMC iterations (after 250 burn-in iterations) and 50 trees;
+We used a Bayesian Additive Regression Trees (BART) machine learning "classification model" [@chipman2010bart] [in the implementation of @kapelner2013bartmachine] to predict the probability of a record being relevant, given the information coded into the enriched DTM and the initial training set.
+We set up the BART model to use 2,000 MCMC iterations (after 250 burn-in iterations) and 50 trees;
 we used a $k$ value of 2 to regularize extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction].
 Positive records are oversampled ten times to increase sensitivity [@batista2004study].\
-The output is a posterior predictive distribution (PPD) for each record describing its probability of being relevant (i.e., a positive match).
+The output is a posterior predictive distribution (PPD) for each record describing the probability of it being relevant (i.e., a positive match).
 An ensemble of ten models was fitted to improve prediction stability by averaging the PPD between models [@zhou2021ensemble; @dietterich2000ensemble].\
 
-To assign the labels, we employed an "active learning" [@settles2009active, @miwa2014reducing] approach, where a human reviews a specific subset of predictions made from the machine, which is then retrained on the manually reviewed data set.
-This process proceeds iteratively, decreasing prediction uncertainty.\
-Label assignment is done through the identification of an "uncertainty zone" whose construction is possible thanks to the Bayesian nature of BART, which provides full PPDs instead of point-wise predictions for each record.\
+To assign the labels, we employed an "active learning" approach [@settles2009active; @miwa2014reducing], where a human reviews a specific subset of predictions made by the machine, which is then retrained on the manually reviewed dataset.
+This process is carried out iteratively to reduce prediction uncertainty.\
+Label assignment is done through identification of an "uncertainty zone" the construction of which is possible thanks to the Bayesian nature of BART, which provides full PPDs instead of point-wise predictions for each record.\
 To describe the process formally, we define
@@
 
-as respectively the lower and upper boundaries of the 98% quantile interval of $\pi_i$ (98% Predictive Interval, 98% PrI).\
+respectively as the lower and upper boundaries of the 98% quantile interval of $\pi_i$ (98% Predictive Interval, 98% PrI).\
 Then we identify the "uncertainty zone" as
@@
 that is, the record lower 98% PrI boundary should be higher than every value in the uncertainty zone.
-In other words, for a record to be labelled positive, its PPD should be within the range of the mixture of PPD of the previously labelled positive records and not cross the distributions of the negative records.\
+In other words, for a record to be labelled positive, its PPD should be within the range of the mixture of PPD of the records previously labelled positive, and should not cross the distributions of the negative records.\
 Conversely, a record is labelled as negative if
@@
 
-Manual review is then necessary for: 1) uncertain records, 2) positive records (to avoid false positives), 3) records whose predicted label differs from the existing manual one.
+Manual review is then necessary for: 1) uncertain records, 2) positive records (to avoid false positives), and 3) records whose predicted label differs from the existing manual one.
 The last case helps identify human errors or inconsistent labelling criteria.
 
-The automatic classification and the manual review steps alternate in a loop (CR iterations) until no new positive matches are found in four consecutive iterations.
+The automatic classification and manual review steps alternate in a loop (CR iterations) until no new positive matches are found in four consecutive iterations.
 
@@
 
-BART model it is possible to extract the proportion of times a term was used in a posterior tree over the sum of total inclusions of all variables [@kapelner2013bartmachine], as a measure of feature importance for the model.
-We extracted the terms, the part of the citation data they were used in, the average "inclusion rate" among the ensemble models (over 10,000 inclusions) and its ratio over the standard deviation of this inclusion (inclusion stability, IS).
-For each term we ran a Poisson regression to get its linear association with a positive label and reported it as Relative Risk (RR) with the number of standard errors as significance index (Statistic);
+With the BART model, it is possible to extract the proportion of times a term is used in a posterior tree over the sum of total inclusions of all variables [@kapelner2013bartmachine], as a measure of importance of the features in the model.
+We extracted the terms, the portion of the citation data in which they were used, the average "inclusion rate" among the ensemble models (over 10,000 inclusions) and its ratio over the standard deviation of this inclusion (inclusion stability, IS).
+For each term we ran a Poisson regression to get the linear association with a positive label and reported it as Relative Risk (RR) with the number of standard errors as significance index (Statistic);
 the comparison between the inclusion rate in the BART models and the linear association allows to spot relevant non-linear effects (i.e, the feature is relevant only in association with others).
-We reported in the Results only the first (in order of inclusion rate) 15 terms with IS > 1.5 while the first fifty terms regardless of inclusion stability are reported in Supplemental Material S2.
+In the Results, we only listed the first  15 terms with IS > 1.5, (in order of inclusion rate), while the first fifty terms regardless of inclusion stability are listed in Supplemental Material S2.
 
@@
 
-We created an algorithm that generates a new search query to acquire further relevant publications missed during the first search, possibly at a reasonable cost in specificity (i.e., a higher number of negative results).\
+We developed an algorithm that generates a new search query to find further relevant publications missed in the initial search, possibly at a reasonable cost to specificity (i.e., a higher number of negative results).\
 The algorithm encompasses a number of steps:
 
-- We fit a partition tree [@rpart] between the DTM and 800 samples from the PPD;
-if a term is present multiple times in the DTM (e.g., both title and abstract), they are counted just one, and field term count features are removed.
-This step generates a list of rules composed by $AND$/$NOT$ "conditions" made of terms/authors/keywords/MESH tokens, which together identify a group of records.
-- For each rule, negative conditions (i.e., $NOT$ statements) are added iteratively, starting from the most specific one, until no conditions are found that would not also remove positive records.
+- A partition tree [@rpart] is built between the DTM and 800 samples from the PPD;
+if a term is present multiple times in the DTM (e.g., both in the title and abstract), it is counted just once, and field term count features are removed.
+This step generates a list of rules composed by _AND_/_NOT_ "conditions" made of terms/authors/keywords/MESH tokens, which together identify a group of records.
+- For each rule, negative conditions (i.e., _NOT_ statements) are added iteratively, starting from the most specific one, until no conditions are found that would not also remove positive records.
 - The extended set of rules is sorted by positive-negative record difference in descending order.
@@
 Rules inside each group are ordered by specificity.
-- The researcher is then asked to review the rule groups, selecting one or more rules (useful if they convey different meaning) from each, or edit them (in case too specific positive or negative conditions were included).
-It is possible to exclude a group of rules altogether, especially those with the worse sensitivity/specificity ratio.
-- The selected rules are joined together by $OR$ statements, defining a subset of records with a sensibly higher proportion of positive records than the original one.
-- Redundant rules (i.e., rules whose positive records are already included in more specific ones) and conditions (i.e., conditions that once removed do not decrease the total number of positive or do not increase the negative records) are removed.
-- Finally, the rules are re-elaborated in a query usable on the major scientific databases.
+- The researcher is then asked to review the rule groups and select one or more rules from each group (useful if they convey different meaning), or edit them if overly too specific positive or negative conditions were included.
+It is possible to exclude a group of rules altogether, especially those with the poorest sensitivity/specificity ratio.
+- The selected rules are joined together by _OR_ statements, defining a subset of records with a sensibly higher proportion of positive records than the original set
+- Redundant (i.e., rules whose positive records are already included in more specific ones) and non-relevant rules (i.e., conditions that when removed do not impact sensitivity and specificity) are removed.
+- Finally, the rules are re-elaborated in a query that can be used in the major scientific databases.
 
-Since the algorithm is data-driven, it creates queries that effectively select positive records from the input data set but may be not specific enough once applied to actual research databases.
-Therefore we appended an extra subquery in $AND$, which specifies the general topics of our search and delimitates the search domain.\
+Because the algorithm is data-driven, it creates queries that effectively select positive records from the input dataset, but may be not specific enough when applied to actual research databases.
+Therefore we added an extra subquery in _AND_, that specifies the general topics of our search and narrows the search domain.\
 The new query was used to initiate a second search session.
@@
 
-We trained a simple Bayesian logistic regression (surrogate model) on the reviewed records to evaluate the classification model consistency (see Discussion for the theoretical justification).
-The surrogate model uses as predictor the lower bound of the 98% PrI of the records' PPD with weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).\
-The quality of the model was evaluated through Bayesian $R^2$ [@gelman2019r], of which we reported the posterior median and 90% Credible Interval [90% CrI].
+We trained a simple Bayesian logistic regression (surrogate model) on the reviewed records to evaluate the consistency of classification model (see Discussion for the theoretical justification).
+The surrogate model uses as predictor the lower boundary of the 98% PrI of the PPD of the records with weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).\
+The quality of the model was evaluated through the Bayesian $R^2$ [@gelman2019r], of which we reported the posterior median and 90% Credible Interval [90% CrI].
 The $R^2$ also provides an evaluation of the consistency of the original classification model.
 Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing plausible worst-case scenarios.\
-The surrogate model is then used to generate the predictive cumulative distribution of the number of total positive records in the whole data set.
-This distribution allows estimating the expected total posterior "Sensitivity" and "Efficiency" of the classification model in the full (unreviewed) data set.
+The surrogate model is then used to generate the predictive cumulative distribution of the number of total positive records in the whole dataset.
+This distribution allows to estimate the expected total posterior "Sensitivity" and "Efficiency" of the classification model in the full (unreviewed) dataset.
 Efficiency is summarised by the "Work saved over random" (WSoR) statistic:
-one minus the ratio between the number of record manually reviewed and those that would be required to find the same number of positives if classification was performed choosing records randomly;
-this last quantity is estimated through a negative hypergeometric distribution [@chae1993presenting] over the predicted amount of positive records.\
-For the number of predicted positive records, the sensitivity and the efficiency, we reported the "truncated 90% PrI" [trunc.
-90% PrI], which is the uncertainty interval bounded at the number of observed total positive records (i.e., there cannot be less predicted positive records than observed).
+one minus the ratio between the number of record manually reviewed and those that would be required to find the same number of positives if classification were performed choosing records randomly;
+this last quantity is estimated through a negative hypergeometric distribution [@chae1993presenting] over the predicted number of positive records.\
+For the number of predicted positive records, sensitivity and efficiency, we reported the "truncated 90% PrI" [trunc.
+90% PrI], i.e., the uncertainty interval bounded by the number of observed total positive records (i.e., there cannot be fewer predicted positive records than observed).
 
@@
 
-To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled "validation set" made of the first 1200 records from the first session data set.
-The framework tested each hyperparameter combination until four CR iterations with no positive records were returned or the whole data set got labelled.\
-For each combination, a performance score was computed as the product of "Efficiency" (1 minus the ratio of records that required review over the total) and "Sensitivity" (number of positive records found over the total of positives).
-We then identified homogeneous "performance clusters" of scores given hyperparameter values using a partition tree [@rpart].
+To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled "validation set" derived from the first 1,200 records of the first session dataset.
+Each hyperparameter combination was tested until four CR iterations were completed with no positive records or the whole dataset was labelled.\
+For each combination, a performance score was computed as the product of "Efficiency" (1 minus the ratio of records that required reviewing over the total number of records) and "Sensitivity" (number of positive records found over the total number of positive records).
+We then used a partition tree [@rpart] to identify homogeneous "performance clusters" of scores given hyperparameter values.
 For the rest of the study, we used the best hyperparameter set in terms of Sensitivity followed by Efficiency from the cluster with the highest average score.\

### 2022-02-19 Manuscript/Manuscript_Results.Rmd
English proof reading and better number formatting

@@
 knitr::opts_knit$set(root.dir = wd)
+knitr::knit_hooks$set(inline = function(x) {
+	format(x, digits = 3, big.mark = ",", scientific = F)
+})
 
@@
 selecting only results between 2010 and 2020 (included).
-Results were collected from Pubmed, WOS, IEEE, EMBASE and SCOPUS, using the framework tools as described in Methods and Supplemental Material S1.
+Results were collected from Pubmed, WOS, IEEE, EMBASE and SCOPUS, using the framework tools as described in the Methods and Supplemental Material S1.
 
 The first search session returned a total of `r all_records` records, specifically `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total` of the total) records from the EMBASE database, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from Pubmed, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from SCOPUS, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from WOS, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from IEEE (Table 1).
-There were various degrees of overlapping between sources, with the `r percent(1 - source_distr[1])` of records being present in more than one database and EMBASE and IEEE being the databases with the higher uniqueness ratios.
-The final data set was composed by `r source_summary$Total$Records` unique records.\
-The first `r num_first_labeling` records (based on "simple query ordering") were manually labeled.
+There were various degrees of overlapping between sources, with `r percent(1 - source_distr[1])` of records being present in more than one database, and EMBASE and IEEE being the databases with the higher uniqueness ratios.
+The final data set was composed from `r source_summary$Total$Records` unique records.\
+The first `r num_first_labeling` records (based on "simple query ordering") were labeled manually.
 Of these `r sprintf('%d (%s)', num_first_positives, percent(num_first_positives/num_first_labeling))` were labeled as positive, and `r sprintf('%d (%s)', num_first_negatives, percent(num_first_negatives/num_first_labeling))` as negative.
@@
 After seven classification and review (CR) iterations (three resulting in new positive matches and four extra replications to account for stochastic variability), a total of `r num_last_positives` positives matches were found, requiring manual review of `r tot_reviewed` records (`r percent(num_last_positives/tot_reviewed)` positivity rate).\
-It is possible to observe how the number of records that required manual review dropped rapidly between iterations (Table 2), indicating that the engine was converging while the uncertainties were resolved.\
-This phenomenon is better depicted in Fig.
-1 of the Supplemental Material S2, showing the mixture distribution of the PPDs of the records, specifically for the reviewed positive and negative records, and for records that need manual review after the classification step:
-it can be noticed how the distribution of the uncertain records shrinked (ie., gets concentrated in a shorter probability range) and shifted toward the negative zone as more positive matches are found and reviewed.
+It is noticeable how the number of records that required manual review decreased rapidly between iterations (Table 2), indicating that the engine was converging while the uncertainties were resolved.\
+This phenomenon is better illustrated in Fig. 1 of the Supplemental Material S2.
+It shows the mixture distribution of the PPDs of the records, specifically for records that were manually reviewed, before and after the classification step:
+it can be seen how the distribution of uncertain records shrinks (i.e., it becomes concentrated in a shorter probability range) and shifts toward the negative zone as more positive matches are found and reviewed.
 
@@
 Also, the number of changes after review and their description is reported.\"Unlab.\" indicates unlabelled records marked for review.
-For each Iteration, also the number of features used by the engine is reported.
-The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1.
+For each Iteration, the number of features used by the engine is also reported.
+The first row reports the results of the initial manual labelling of records, which served as input for the automatic classification in Iteration 1.
 In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.", label = "Table 2")`
@@
 The engine was able to pick up the central concept of the research topic, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) as well as the region of interest ("Orange County") of another research group active on the topic of pathogen spreading over hospital networks.
-Some terms were considered highly relevant by the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
-these are terms which are relevant only in conjunction with other terms but not by themselves, highlighting the extra predictive power brought by using advanced, non-linear machine learning.\
-A more extensive set of terms is presented in Table 1 of Supplemental Material S2.
+Some terms were considered highly relevant by the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would hardly be significant (statistic: -1.21 s.e.);
+these are terms that are only relevant in conjunction with other terms but not by their own, highlighting the extra predictive power achievd through the use of advanced, non-linear machine learning.\
+A more extensive set of terms is presented in Table 1 of the Supplemental Material S2.
 
@@
 
-The results of the first classification session were used to create a second, data-driven query with the purpose of performing a more large-spectrum search to find records which may have escape the first search session.
-The resulting query was the following:\
+The results of the first classification session were used to create a second, data-driven query with the objective of performing a more extensive search to find records that may have been missed during the first search session.
+The resulting query was as follows:\
 
@@
 
-The search was done with the same year filter and procedures of the first session.\
+The search was done with the same year filter and procedures used in the first session.\
 
 The new search produced `r all_records` records (Table 1), of which `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total`) from the EMBASE, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from Pubmed, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from SCOPUS, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from WOS, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from IEEE;
-compared with the first session, the relative weight of EMBASE and Pubmed was decreased, while the amount of content specificity was greatly increased, as it was for SCOPUS.
+compared with the first session, the relative weight of EMBASE and Pubmed decreased, while the level of content specificity greatly increased, as it was for SCOPUS.
 After removal of duplicates, `r source_summary$Total$Records` unique records were obtained.
-Once joined with the session 1 records and removal of duplicates, we obtained `r nrow(records_s2)` unique records, with just `r session_diff` shared records between searches, that is the `r percent(session_diff / source_list[['All Sessions']]$Total$Records)`.
+The newly collected records were joined with those from the first session and duplicates were removed.
+We obtained `r nrow(records_s2)` unique records, with just `r session_diff` shared records between searches, which equates to `r percent(session_diff / source_list[['All Sessions']]$Total$Records)` of the total.
 The percentage of records shared by two or more source dropped to `r percent(1 - source_distr[1])`.
@@
 -> y'])` new positive found after reviewing `r tot_reviewed - session_summary$tot_reviewed_[1]` extra records.
-The first CR iteration required the user to review a substantial number of records (1,273), but just labelling 275 of them (the canonical 250 plus 25 that were already labelled during the framework hyperparameter tuning) was sufficient to drop this number to just 190 in the subsequent round.
-An evaluation of the convergence (Figure 1, Supplemental Material S2) showed that, in addition to the dynamics already observed in session 1 (shrinkage and negative shift), a second mode appeared in the mixture distribution of the records to be reviewed, centred in a highly positive zone.
-The interpretation is that as the number of negative training records increases, the engine gets more and more skeptical and asks to review even some records labelled as positive in the initial training set generated during Session 1.
+The first CR iteration required the user to review a substantial number of records (1,273);
+however, just labelling 275 of them (the suggested 250 plus 25 alredy labelled for the framework hyperparameter tuning) was sufficient to reduce this number to just 190 in the subsequent round.
+An evaluation of the convergence (Supplemental Material S2, Fig.
+1) showed that, in addition to the dynamics already observed in session 1 (shrinkage and negative shift), a second mode appeared in the mixture distribution of the records to be reviewed, centred in a highly positive zone.
+The interpretation is that as the number of negative training records increases, the engine becomes more and more sceptical and even asks to review some records labelled as positive in the initial training set generated during Session 1.
 This behaviour can be useful to spot classification errors and inconsistencies.
@@
 
-Again, the evaluation of the inclusion rate of the terms showed that the engine was quite capable of internalizing the concepts behind the research topic
+Again, the evaluation of the inclusion rate of the terms showed that the engine is quite capable of internalizing the concepts behind the research topic.
 A subsample of the relevant terms used by the model in the second session is reported in Table 2 of Supplemental Material S2.
@@
 
-As described in the methods, the selection of hyperparameters was achieved via evaluation of sensibility and efficiency through a grid search on a validation set of 1200 manually labelled records.
-The analysis suggested the following combination of parameters as the best performing: an initial input of 250 labelled records with 10x positive matches oversampling, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
-This combination of parameters was associated with a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
-The detailed results of the hyperparameter tuning ananlysis are reported in Table 3 of Supplemental Material S2.
-Figure 2 in Supplemental Material S2 demonstrates that the positive record oversampling rate, the number of ensemble models and the size of the initial training set were the parameters that mostly impacted performance.
+As described in the methods, hyperparameters were selected by evaluating sensibility and efficiency through a grid search on a validation set of 1,200 manually labelled records.
+The analysis suggested that the following parameter combination performed best:
+an initial input of 250 labelled records with 10x oversampling of positive matches, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
+This combination of parameters was associated with a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and an efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
+The detailed results of the hyperparameter tuning analysis are reported in Table 3 of Supplemental Material S2.
+Fig.
+2 in Supplemental Material S2 demonstrates that the positive record oversampling rate, the number of ensemble models and the size of the initial training set were the parameters that mostly impacted performance.
 
@@
 
-To evaluate the theoretical performance of the engine, a surrogate Bayesian logistic regression model was trained on the manually reviewed labels using only the lower bound of the record PPDs as predictor (see Methods for the details).
+To evaluate the theoretical performance of the engine, a surrogate Bayesian logistic regression model was trained on the manually reviewed labels using only the lower boundary of the record PPDs as predictor (see the Methods for details).
 The surrogate model showed the high predictive power of the scores produced by the classification model (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2).\
 
-Figure 2 presents the actual and predicted (from the surrogate model) cumulative number of positive matches, ordered by the initial simple ordering query:
+Fig. 2 presents the actual and predicted (from the surrogate model) cumulative number of positive matches, ordered by the initial simple ordering query:
 the median of surrogate models' cumulative predictive distributions matches quite well the actual number of positive records found.
-It is striking how many more records would have needed to be evaluated manually to find the same number of positive matches without using a smart classification tool,
+It is striking how many more records would have required manual evaluation to find the same number of positive matches without using a smart classification tool,
 with some positive matches found close to the end of the heuristically ordered list of records.\
@@
 In session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.
-In session 2 we observed a drop in the expected sensitivity, especially in the lower credibility boundary (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows, even a small probability of being a positive match can translate, in the worst case scenario, into a relevant number of missed positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
-To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no additional positive matches.\
+In session 2 we observed a drop in expected sensitivity, especially in the lower credibility boundary (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`),
+due to the fact that as the number of records increases, even a small probability of being a positive match can, in the worst case scenario, lead to a relevant number of missed positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
+To ensure that no obvious positive matches were missed, we evaluated 100 additional records among those not reviewed with the highest median predicted probability produced by the engine and found no additional positive matches.\
 
@@
 The [trunc.
-90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines).
+90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as a shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines).
 The median of the PrI is represented by a darker blue line."}

### 2022-02-19 R/Reporting.R

@@ -18,14 +18,14 @@
 #' # setosa: 50 (33.3%), versicolor: 50 (33.3%), virginica: 50 (33.3%)
 #'
 summarise_vector <- function(vec) {
-  if (length(vec) == 0 | is.list(vec) | !is.null(dim(vec))) {
-    return("incorrect input")
-  }
-  all_els <- length(vec)
-  table(vec) %>%
-    {
-      paste0(names(.), ": ", ., " (", percent(. / all_els), ")", collapse = ", ")
-    }
+	if (length(vec) == 0 | is.list(vec) | !is.null(dim(vec))) {
+		return("incorrect input")
+	}
+	all_els <- length(vec)
+	table(vec) %>%
+		{
+			paste0(names(.), ": ", ., " (", percent(. / all_els), ")", collapse = ", ")
+		}
 }
 
 #' Record distribution between sources in an Annotation file
@@ -57,50 +57,50 @@ summarise_vector <- function(vec) {
 #' summarise_by_source(records)
 #' }
 summarise_by_source <- function(annotation_file, as_data_frame = FALSE,
-                                add_session_totals = TRUE) {
-  data <- import_data(annotation_file)
+																add_session_totals = TRUE) {
+	data <- import_data(annotation_file)
 
-  sources <- data$Source %>%
-    str_split(., "; *") %>%
-    unlist() %>%
-    unique()
+	sources <- data$Source %>%
+		str_split(., "; *") %>%
+		unlist() %>%
+		unique()
 
-  total_records <- nrow(data)
+	total_records <- nrow(data)
 
-  res <- lapply(sources, function(source) {
-    Records <- str_detect(data$Source, glue("{source}")) %>% sum()
-    Perc_over_total <- percent(Records / total_records)
-    Source_specific <- str_detect(data$Source, glue("^{source}$")) %>% sum()
-    Source_specific_perc <- percent(Source_specific / Records)
+	res <- lapply(sources, function(source) {
+		Records <- str_detect(data$Source, glue("{source}")) %>% sum()
+		Perc_over_total <- percent(Records / total_records)
+		Source_specific <- str_detect(data$Source, glue("^{source}$")) %>% sum()
+		Source_specific_perc <- percent(Source_specific / Records)
 
-    list(
-      Records = Records, Perc_over_total = Perc_over_total,
-      Source_specific = Source_specific, Source_specific_perc = Source_specific_perc
-    )
-  }) %>% setNames(sources)
+		list(
+			Records = Records, Perc_over_total = Perc_over_total,
[…]

### 2022-02-19 Manuscript/Manuscript.Rmd
update for arxiv submission

@@
   The framework provides three main tools:
-  1) An automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax
-  2) A citation screening tool based on Bayesian active machine learning and natural language processing that requires users feedback only on uncertain classifications to iteratively increase predictive accuracy and
-  3) A semi-automatic, data-driven query generator to create new search queries from existing reviewed citation data sets.\
+  1) an automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax,
+  2) a citation screening tool based on Bayesian active machine learning and natural language processing that requires users feedback only on uncertain classifications to iteratively increase predictive accuracy and,
+  3) a semi-automatic, data-driven query generator to create new search queries from existing reviewed citation data sets.\
   The framework was tested on an example topic to collect and screen citations of related scientific production.
@@
   while the rest were excluded by automatic classification;
-  the theorethical efficiency was 95.6% [95.3%, 95.7%] with a sensitivity of 100% [93.5%, 100%].\
+  the theoretical efficiency was 95.6% [95.3%, 95.7%] with a sensitivity of 100% [93.5%, 100%].\
   A new search query was generated from the labelled dataset, and 82,579 additional records were collected;
@@
   by simplifying citation collection and screening while demonstrating exceptional sensitivity.
-  Such tool can improve the standardization and repeatability of systematic reviews.
+  Such a tool can improve the standardization and repeatability of systematic reviews.
 keywords:

### 2022-02-19 Manuscript/Manuscript.tex
update for arxiv submission

@@
 literature.\\
-The framework provides three main tools: 1) An automatic citation search
+The framework provides three main tools: 1) an automatic citation search
 engine and manager that allows collecting records from multiple citation
 databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query
-syntax 2) A citation screening tool based on Bayesian active machine
+syntax, 2) a citation screening tool based on Bayesian active machine
 learning and natural language processing that requires users feedback
 only on uncertain classifications to iteratively increase predictive
-accuracy and 3) A semi-automatic, data-driven query generator to create
+accuracy and, 3) a semi-automatic, data-driven query generator to create
 new search queries from existing reviewed citation data sets.\\
@@
 manual evaluation, while the rest were excluded by automatic
-classification; the theorethical efficiency was 95.6\% {[}95.3\%,
+classification; the theoretical efficiency was 95.6\% {[}95.3\%,
 95.7\%{]} with a sensitivity of 100\% {[}93.5\%, 100\%{]}.\\
@@
 collection and screening while demonstrating exceptional sensitivity.
-Such tool can improve the standardization and repeatability of
+Such a tool can improve the standardization and repeatability of
 systematic reviews.
@@
 \centering
-\includegraphics{Manuscript_files/figure-latex/performance plot-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/performance_plot-1.pdf}
 \caption{\textbf{Figure 2}. Observed cumulative number of positive

### 2022-02-19 Manuscript/Manuscript_Results.Rmd
update for arxiv submission

@@
 
-```{r load framework, cache.rebuild=TRUE, include=FALSE}
+```{r load_framework, cache.rebuild=TRUE, include=FALSE}
 source(file.path("R", "Setup.R"), local = knitr::knit_global())
@@
 
-```{r session 1}
+```{r session_1}
 
@@
 
-```{r session 2}
+```{r session_2}
 new_query <- import_data("Session_journal.csv") %>%
@@
 
-```{r performance plot, cache = FALSE, fig.width=7.5, fig.height=4.5, fig.cap="**Figure 2**.
+```{r performance_plot, cache = FALSE, fig.width=7.5, fig.height=4.5, fig.cap="**Figure 2**.
 Observed cumulative number of positive matches (red dots) sorted by simple query ordering.

### 2022-02-19 Manuscript/S1.Protocol.Rmd
update for arxiv submission

@@
   pdf_document:
+    keep_tex: true
     toc: yes
@@
 
-```{r query creation}
+```{r query_creation}
 
@@
 
-```{r perform searches}
+```{r perform_searches}
 # This call will perform an API search on Pubmed, WOS and IEEE services and/or
@@
 
-```{r managing records}
+```{r managing_records}
 # Extract the file paths of records. Arguments can be used to filter by session
@@
 
-```{r save annotation file}
+```{r save_annotation file}
 # This function extracts the appropriate file paths from a session journal. By
@@
 
-```{r create session}
+```{r create_session}
 # Create the first session
@@
 
-```{r one call}
+```{r one_call}
 # First, create the Records/Session1/Query1 folder and put the manually
@@
 
-```{r automatic annotation}
+```{r automatic_annotation}
 New_annotations <- enrich_annotation_file("Session1")
@@
 
-```{r replication limits}
+```{r replication_limits}
 list(
@@
 
-```{r new query generation}
+```{r new_query_generation}
 
@@
 
-```{r second session query}
+```{r second_session_query}
 query <- "(((Donker T) NOT (bacterium isolate)) OR ((network patient) AND
@@
 
-```{r new annotation session}
+```{r new_annotation_session}
 
@@
 
-```{r grid search}
+```{r grid_search}
 Grid_search <- perform_grid_evaluation(

### 2022-02-19 Manuscript/S1.Protocol.tex
update for arxiv submission

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{Study protocol}
\author{}
\date{\vspace{-2.5em}2022-02-19}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Study protocol},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\newpage

\hypertarget{research-protocol}{%
\section{Research Protocol}\label{research-protocol}}

This document will guide the reader along the steps to utilise the
framework and reproduce our results.

Add installation and setup info here.

\hypertarget{acquisition-of-the-citaion-data}{%
\subsection{Acquisition of the citaion
data}\label{acquisition-of-the-citaion-data}}

Once the framework is loaded, the user defines an initial search query
which needs to be as specific as possible while still generating a
sufficient number of positive matches:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{source}\NormalTok{(}\StringTok{"R/Setup.R"}\NormalTok{) }\CommentTok{\# Load the framework}

\CommentTok{\# Initial query to be built on domain knowledge. It accepts OR, AND, NOT boolean}
\CommentTok{\# operators and round brackets to group terms.}
\NormalTok{query }\OtherTok{\textless{}{-}} \StringTok{\textquotesingle{}((model OR models OR modeling OR network OR networks) AND}
\StringTok{(dissemination OR transmission OR spread OR diffusion) AND (nosocomial OR}
\StringTok{hospital OR "long{-}term{-}care" OR "long term care" OR "longterm care" OR}
\StringTok{"long{-}term care" OR "healthcare associated") AND (infection OR resistance OR}
\StringTok{resistant))\textquotesingle{}}

\CommentTok{\# Year filter. The framework converts it to the API{-}specific format seamlessly.}
\CommentTok{\# common logical comparators can be used, i.e. \textless{}, \textless{}=, \textgreater{}, \textgreater{}=, while dashes}
\CommentTok{\# denotes inclusive date intervals. A single year restricts results to one year}
\CommentTok{\# period.}
\NormalTok{year\_filter }\OtherTok{\textless{}{-}} \StringTok{"2010{-}2020"}
\end{Highlighting}
\end{Shaded}

The query is passed to the \texttt{perform\_search\_session()} function,
together with an unique identifier for the \textbf{search session} and
\textbf{search query}. A session identifies a homogeneous group of
complementary or alternative queries (e.g.~sometimes it is easier to
create two different simpler queries than a complex and long one that
returns the same results).\\
In our implementation, we define as sessions the group of actions that
includes the utilisation of a search query and the subsequent iterations
of manual review and automatic classification of its results.\\

\texttt{perform\_search\_session()} will use common scientific research
database APIs (at the moment Pubmed/Medline, Web of Science and IEEE) to
acquire records related to the query. The records will be stored as CSV
files in folders with the following structure:
\texttt{Records/session\_id/query\_id}, created automatically. The
function also creates or updates a \textbf{journal} (a CSV or Microsoft
Excel file) with all the information about sessions, queries and search
results.\\
Some services (IEEE, WOS) requires an API key to access the data; the
API key is not mandatory for Pubmed but can help avoid quota limitations
in case of a large number of results. IEEE can also be searched without
API: the framework will utilise a web scraping approach if the API key
is missing, but the success of this method is not guaranteed. See
Supplemental Material S3 for detailed instruction on preliminary steps
and tips for each supported search engine. These keys can be stored in
the \texttt{secrets.R} file in the working directory, with the following
example code (the ``\emph{baysren}'' prefix identifies the package
specific options):

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{options}\NormalTok{(}\AttributeTok{baysren.ieee\_api\_key =} \StringTok{"your{-}ieee{-}api{-}key"}\NormalTok{)}
\FunctionTok{options}\NormalTok{(}\AttributeTok{baysren.ncbi\_api\_key =} \StringTok{"your{-}ncbi{-}api{-}key"}\NormalTok{)}
\FunctionTok{options}\NormalTok{(}\AttributeTok{baysren.wos\_api\_key =} \StringTok{"your{-}wos{-}api{-}key"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

This file will be automatically parsed from the framework.

If previously downloaded results are already available, users can create
the \texttt{Record} folder manually and put the data there (the file
names need to contain the source name as written in the \texttt{sources}
argument of \texttt{perform\_search\_session()}). The function will
acquire and parse them into a standard format, even if split into
multiple files due to download limits (e.g.~\texttt{Pubmed1.nbib},
\texttt{Pubmed2.nib}, etc.). In addition to Pubmed, WOS and IEEE, this
method permits to import also EMBASE and SCOPUS records, for which an
API search was not yet implemented.\\
Using the \texttt{actions} argument, users can choose whether to perform
an API search, parse already downloaded results, or both.

Note that for Pubmed, the API search may return slightly fewer records
than a manual one due to a different query expansion algorithm (this
divergence should be solved in April 2022) between the two services,
therefore is advisable to perform also a manual search and put the
resulting .nbib files in the \texttt{Session/Query} folder.
\texttt{perform\_search\_session()} will acquire them seamlessly.

If a user wants to perform the API searches and results parsing manually
for each source, the framework exposes the individual functions to
search for records using the APIs and parsing bibliography files.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# This call will perform an API search on Pubmed, WOS and IEEE services and/or}
\CommentTok{\# (based on the \textasciigrave{}actions\textasciigrave{} argument) parse already downloaded data (in our case,}
\CommentTok{\# additional Pubmed results and Embase and Scopus results) manually added to the}
\CommentTok{\# Session1/Query1 folder.}

\NormalTok{journal }\OtherTok{\textless{}{-}} \FunctionTok{perform\_search\_session}\NormalTok{(}
  \AttributeTok{query =}\NormalTok{ query, }\AttributeTok{year\_query =}\NormalTok{ year\_filter,}
  \AttributeTok{session\_name =} \StringTok{"Session1"}\NormalTok{, }\AttributeTok{query\_name =} \StringTok{"Query1"}\NormalTok{,}
  \AttributeTok{records\_folder =} \StringTok{"Records"}\NormalTok{,}
  \AttributeTok{journal =} \StringTok{"Session\_journal.csv"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

Once the records are stored, they must be read and merged into an
\textbf{annotation file}, where the initial manual review will be
performed.\\
A series of functions are available to prepare the data for manual
evaluation:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Extract the file paths of records. Arguments can be used to filter by session}
\CommentTok{\# query, source. Only parsed files will be returned, not the raw ones downloaded}
\CommentTok{\# manually.}
\NormalTok{Annotation\_data }\OtherTok{\textless{}{-}} \FunctionTok{extract\_source\_file\_paths}\NormalTok{(journal) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Read record files. Will parse them if raw data is downloaded manually (not}
  \CommentTok{\# necessary in this case). Return a list of records, one per file.}
  \FunctionTok{read\_bib\_files}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Join a list of records into one dataframe, solving duplicated records}
  \FunctionTok{join\_records}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Order records by the relative frequency of the query terms in the title +}
  \CommentTok{\# abstract text. Increases the chance of encountering relevant records at the}
  \CommentTok{\# beginning of the manual classification.}
  \FunctionTok{order\_by\_query\_match}\NormalTok{(query) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Add fields for the manual classification}
  \FunctionTok{mutate}\NormalTok{(}
    \AttributeTok{Rev\_manual =} \ConstantTok{NA}\NormalTok{, }\CommentTok{\# Where the first manual classification will be made}
    \AttributeTok{Rev\_prediction =} \ConstantTok{NA}\NormalTok{, }\CommentTok{\# Column for the evaluation of the predicted classes}
    \AttributeTok{.before =}\NormalTok{ DOI}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

All these steps are joined into the \texttt{create\_annotation\_file()}
function. This function can take as input either the path to record
files, or the parsed records (one data frame or a list of data frames)
or a group of folders where to look for files into./ In addition, it
also allows adding the new records to a previous annotation file (arg
\texttt{prev\_records}). This is useful when performing consecutive
search sessions with different queries; previous manual classifications
can be imported using \texttt{prev\_classification}.\\
If the original query is passed to the \texttt{reorder\_query} argument,
the records are reordered according to the frequency of query terms in
the title and abstract (\textbf{simple query ordering}); this approach
lets increase the rate of relevant matches at the beginning of the
dataset.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# This function extracts the appropriate file paths from a session journal. By}
\CommentTok{\# default it passes all stored files, otherwise it can be filtered by session,}
\CommentTok{\# query, and source (i.e. Pubmed, WOS, IEEE)}
\NormalTok{record\_files }\OtherTok{\textless{}{-}} \FunctionTok{extract\_source\_file\_paths}\NormalTok{(journal)}

\CommentTok{\# create\_annotation\_file() accept a great variety of inputs:}

\CommentTok{\# either record file paths}
\NormalTok{input }\OtherTok{\textless{}{-}}\NormalTok{ record\_files}

\CommentTok{\# or specific record file folders}
\NormalTok{input }\OtherTok{\textless{}{-}} \FunctionTok{file.path}\NormalTok{(}\StringTok{"Records"}\NormalTok{, }\StringTok{"Session1"}\NormalTok{, }\StringTok{"Query1"}\NormalTok{)}

\CommentTok{\# or parent folders, since it searches for files recursively}
\NormalTok{input }\OtherTok{\textless{}{-}} \StringTok{"Records"}

\CommentTok{\# or the already parsed files}
\NormalTok{input }\OtherTok{\textless{}{-}} \FunctionTok{read\_bib\_files}\NormalTok{(record\_files)}

\CommentTok{\# We can then call create\_annotation\_file() with one of the above input}
\NormalTok{Annotation\_data }\OtherTok{\textless{}{-}} \FunctionTok{create\_annotation\_file}\NormalTok{(input, }\AttributeTok{reorder\_query =}\NormalTok{ query)}
\end{Highlighting}
\end{Shaded}

Once created, the annotations need to be stored in an \textbf{Annotation
Session} folder, which will contain all information necessary for the
automatic classification. This operation is streamlined by the
\texttt{create\_session()} function, which also helps manage duplicated
sessions.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Create the first session}
\FunctionTok{create\_session}\NormalTok{(Annotation\_data, }\AttributeTok{session\_name =} \StringTok{"Session1"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

The file annotation file is called \texttt{Records\_\{date\}}, situated
in the folder \texttt{Sessions/\{session\_name\}}; \texttt{date} here
represents the session creation timestamp, and \texttt{session\_name}
the name passed by the user.

Notice that the framework is ``pipe'' friendly, and the precedent steps
can be all performed in one call:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# First, create the Records/Session1/Query1 folder and put the manually}
\CommentTok{\# downloaded records there if there are any. Otherwise, the folders will be}
\CommentTok{\# created automatically during the API search}

\CommentTok{\# perform searches and parse files; save and return the journal}
\NormalTok{Records }\OtherTok{\textless{}{-}} \FunctionTok{perform\_search\_session}\NormalTok{(}
  \AttributeTok{query =}\NormalTok{ query, }\AttributeTok{year\_query =}\NormalTok{ year\_filter,}
  \AttributeTok{session\_name =} \StringTok{"Session1"}\NormalTok{, }\AttributeTok{query\_name =} \StringTok{"Query1"}\NormalTok{,}
  \AttributeTok{journal =} \StringTok{"Session\_journal.csv"}
\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# return the record file paths}
  \FunctionTok{extract\_source\_file\_paths}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# read, join, reorder records and save them in the Sessions folder}
  \FunctionTok{create\_annotation\_file}\NormalTok{(}\AttributeTok{reorder\_query =}\NormalTok{ query) }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# Create a new session with the records}
  \FunctionTok{create\_session}\NormalTok{(}\AttributeTok{session\_name =} \StringTok{"Session1"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{manual-classification-and-prediction}{%
\subsection{Manual classification and
prediction}\label{manual-classification-and-prediction}}

Now the annotation file is ready for the manual classification of
records. The annotation file has a column called \texttt{Rev\_manual},
where records need to be classified as ``positive'' (y) or ``negative''
(n) matches by the user. We suggest manually labelling an
\textbf{initial training set} of 250 records, which should be sufficient
if a minimum \textasciitilde20\% positivity rate is present (see the
section about model hyperparameter optimisation)./ The function
\texttt{plot\_classification\_trends()} can help visualise the trend of
the positives/negatives as the number of classified records increases./

Once the initial training set is prepared, the function
\texttt{enrich\_annotation\_file()} will use a Bayesian Additive
Regression Trees (BART) machine learning model to learn the labelling
pattern given the record data and predict the positive match probability
for the unlabelled records.\\
\texttt{enrich\_annotation\_file()} comprises two steps. The first step
is the creation of a \textbf{Document Term Matrix} (DTM):

\begin{itemize}
\tightlist
\item
  The framework extracts \textbf{features} from text data (i.e., title
  and abstract) of the records, authors, keywords and MESH terms (see
  Methods for more info). Before features extraction, text data terms
  are lemmatised, stop-words are removed, and only nouns, adjectives,
  verbs and untagged terms are retained. Authors, keywords, and MESH are
  kept unmodified. Co-occurrent features (non-consecutive ngrams,
  \textbf{nc-grams}) are identified and \textbf{redundant features}
  (i.e.~terms always appearing together) are joined to decrease the
  feature space noise.
\item
  For each term, a 0/1 label specifies if it is present in each record.
\item
  Positive records are oversampled \textbf{10x} to improve sensitivity;
\item
  An extra feature is added for each record field (title, abstract,
  authors, keywords, MESH terms), reporting the number of terms in each.
\end{itemize}

The second step is the modelling of the labelling pattern and the
predictions of the relevancy/positivity probability:

\begin{itemize}
\tightlist
\item
  The function models the labelling pattern using the manually labelled
  records (**learning phaseéé);
\item
  After the model is created, it assigns a \textbf{posterior predictive
  distribution} (PPD) of the probability of positivity to each record
  (\textbf{prediction phase}). If the number of records is large, the
  prediction step is broken into chunks of \textbf{5000 records}, to
  avoid memory saturation; the users can set up this parameter according
  to their machine capabilities;
\item
  This process is repeated \textbf{10 times}, and the predictive
  distributions are averaged to induce shrinkage of the estimates (i.e.,
  decrease the chance of outliers), creating a prediction
  \textbf{ensemble};
\item
  The resulting distributions are summarised by the \textbf{98\%
  interval} {[}98\% PrI{]} and the median; the {[}98\% PrI{]} identifies
  the \textbf{uncertainty zone};
\item
  The unlabelled records will receive a positive/negative predicted
  label; the label is positive if its lower {[}98\% PrI{]} bound is
  higher than the uncertainty zone upper bound and negative if the upper
  {[}98\% PrI{]} bound is lower than the uncertainty zone lower bound.
  All other records are labelled as \textbf{uncertain} (unk);
\item
  If a predicted label does not match an existing one, the record will
  be labelled as \textbf{check}.
\end{itemize}

The user can define parameters like the positives' oversampling rate,
the number of models to average in the ensemble, whether to apply
bootstrap resampling before each repetition, the prediction chunk size,
and the PPD quantiles used to build the uncertainty zone. To use the
function, the only input needed is the session name; the function will
automatically identify the relevant file to make predictions on.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{New\_annotations }\OtherTok{\textless{}{-}} \FunctionTok{enrich\_annotation\_file}\NormalTok{(}\StringTok{"Session1"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

This function will produce a new file which is stored in the Annotations
folder of the session; the file will contain a column called
\texttt{Rev\_prediction\_new} where the user will find records that
require manual review marked by ``*``. These are records with uncertain
labelling (''unk''), but also positive predictions and ``y''/``n''
predictions that contradict previous manually input labels (labelled as
``check''). This approach increases the accuracy of the predictions
since the machine learning system is set up to favour sensitivity at the
expense of specificity. If the function finds prelabelled records
(\texttt{Rev\_previous} column) added when the Annotation file was
created or passed as a further input to
\texttt{enrich\_annotation\_file()} (\texttt{prev\_classification}
argument), they will be used to label the records marked in the
\texttt{Rev\_prediction\_new} column.

The function adds a number of diagnostic pages to the annotation file:

\begin{itemize}
\tightlist
\item
  A results summary page reporting the number of records in need of
  manual review (which includes ``unk'', ``check'', and unreviewed ``y''
  records), the changes, and the final distribution of the labels. It
  also shows other information like the number of features in the DTM,
  the path to the parent file from which the annotation file was
  created, the replication number (see later). The content of this
  summary is also saved as a CSV file in the Results folder.
\item
  A variable importance page that lists the used terms in order of the
  fraction of BART trees in which they were used. If an ensemble of
  models is used, a more robust score is computed, taking the ratio of
  the mean of the term tree fraction among models and its standard
  deviation.
\item
  The arguments passed to the function if different from the default,
  useful for reproducibility.
\item
  A classification performance summary. The procedure may take some time
  and requires \texttt{cmdstan} installed on the machine. Therefore the
  \texttt{compute\_performance} argument is set to \texttt{FALSE} by
  default.
\end{itemize}

Finally, the PPD ensemble produced by the Bayesian engine is stored on
the disk. This feature can be turned off to save disk space, but at
least the samples of the last annotation are necessary to build a new
search query (see next section).

The process of predicting labels and manually reviewing them is what
defines a ``classification-review (CR) iteration''.

Once the manual review of the generated annotation file is completed,
the user can \textbf{rerun exactly the same function}. The last reviewed
annotation file will be automatically picked up and used for a new CR
iteration. If the number of records requiring manual review is
excessively high (e.g.~\textgreater{} 250), the function needs to be
called with the \texttt{stop\_on\_unreviewed} argument set to
\texttt{FALSE} to allow the classification to proceed even in the
presence of unreviewed records in the \texttt{Rev\_prediction\_new}
column.

If there are no positive results (after manual review) in a CR
iteration, the framework records the next iteration as a
\textbf{replication}. After four replications with no new positive
matches, the function will prevent another iteration and send a warning
message, indicating that the session is complete. The user can change
the replication limit; furthermore, it is possible to prevent the
function from starting if either a specified number (or a fraction) of
the total records has been manually reviewed or if a certain number of
positive matches have been found. These three parameters are passed to
the \texttt{limits} argument, which has the following structure and
defaults:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{list}\NormalTok{(}
  \AttributeTok{stop\_after =} \DecValTok{4}\NormalTok{,}
  \AttributeTok{pos\_target =} \ConstantTok{NULL}\NormalTok{,}
  \AttributeTok{labeling\_limit =} \ConstantTok{NULL}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

The result files in the Results folder are generated after the
Classification step but before the Review one, and therefore show
preliminary results with still unreviewed records. The function
\texttt{consolidate\_results(session\_name)} will update the results
files to show the results after the manual review. The original result
data is stored anyway in the respective annotations files.

\hypertarget{new-search-query-generation}{%
\subsection{New search query
generation}\label{new-search-query-generation}}

It is not uncommon for the first query used in a systematic review not
to be the most effective one, especially in terms of sensitivity. We
tried to address the problem by creating an automatic query generation
system.\\
The solution is experimental and greatly favours sensitivity at the
expense of specificity. The general query generation mechanism is the
following:

\begin{itemize}
\tightlist
\item
  We fit a partition tree between the DTM and 800 samples from the PPD;
  if a term is present multiple times in the DTM (e.g., both title and
  abstract), they are counted just one, and field term count features
  are removed. This step generates a list of rules composed by
  \(AND\)/\(NOT\) ``conditions'' made of terms/authors/keywords/MESH
  tokens, which together identify a group of records.
\item
  For each rule, negative conditions (i.e., \(NOT\) statements) are
  added iteratively, starting from the most specific one, until no
  conditions are found that would not also remove positive records.
\item
  The extended set of rules is sorted by positive-negative record
  difference in descending order. The cumulative number of unique
  positive records is computed and used to group the rules. Rules inside
  each group are ordered by specificity.
\item
  The researcher is then asked to review the rule groups, selecting one
  or more rules (useful if they convey different meaning) from each, or
  edit them (in case too specific positive or negative conditions were
  included). It is possible to exclude a group of rules altogether,
  especially those with the worse sensitivity/specificity ratio.
\item
  The selected rules are joined together by \(OR\) statements, defining
  a subset of records with a sensibly higher proportion of positive
  records than the original one.
\item
  Redundant rules (i.e., rules whose positive records are already
  included in more specific ones) and conditions (i.e., conditions that
  once removed do not decrease the total number of positive or do not
  increase the negative records) are removed.
\item
  Finally, the rules are re-elaborated in a query usable on the major
  scientific databases.
\end{itemize}

The steps for generating a query are the following:

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# The last annotation file and posterior sample matrix in the session are found;}
\CommentTok{\# the most predictive terms (based on the importance score) are chosen and}
\CommentTok{\# simple prediction trees are used to map the terms to a random subset of the}
\CommentTok{\# posterior probabilities (extracted from the posterior sample matrix saved}
\CommentTok{\# during the last CR iteration). The score threshold and the number of trees can}
\CommentTok{\# be chosen by the user; less stringent values can significantly increase}
\CommentTok{\# computation time. By default results will be saved in a file called}
\CommentTok{\# rule\_data.rds in the session folder.}

\NormalTok{candidate\_queries }\OtherTok{\textless{}{-}} \FunctionTok{extract\_rules}\NormalTok{(}\StringTok{"Session1"}\NormalTok{)}

\CommentTok{\# The \textquotesingle{}candidate\_queries\textquotesingle{} contains the rules, the DMT and the labels on which}
\CommentTok{\# the rules were built, which must be passed to generate\_rule\_selection\_set().}
\CommentTok{\# This function selects the most effective (higher positive/negative matches}
\CommentTok{\# delta) rules; also adds negative terms to increase specificity. A data frame}
\CommentTok{\# is generated (or automatically saved if save\_path is set). The output proposes}
\CommentTok{\# groups of equivalent (in terms of the number of positive matches found) groups}
\CommentTok{\# of query, ordered by specificity; for each group, the user needs to select the}
\CommentTok{\# best rule by setting the selected\_rule column to TRUE. The groups are in order}
\CommentTok{\# of growing sensitivity/decreasing specificity, so it may make sense to exclude}
\CommentTok{\# the last groups totally in order to avoid too many search results.}

\NormalTok{Target }\OtherTok{\textless{}{-}}\NormalTok{ candidate\_queries}\SpecialCharTok{$}\NormalTok{DTM}\SpecialCharTok{$}\NormalTok{Target}
\NormalTok{SpecificDTM }\OtherTok{\textless{}{-}}\NormalTok{ candidate\_queries}\SpecialCharTok{$}\NormalTok{SpecificDTM}

\CommentTok{\# No default is given for the save file, since generate\_rule\_selection\_set()}
\CommentTok{\# have no info about the session it\textquotesingle{}s working on.}
\NormalTok{selection\_set\_file }\OtherTok{\textless{}{-}} \FunctionTok{file.path}\NormalTok{(}\StringTok{"Sessions"}\NormalTok{, }\StringTok{"Session1"}\NormalTok{, }\StringTok{"Selected\_rules.xlsx"}\NormalTok{)}

\NormalTok{selection\_set }\OtherTok{\textless{}{-}} \FunctionTok{generate\_rule\_selection\_set}\NormalTok{(}
\NormalTok{  candidate\_queries}\SpecialCharTok{$}\NormalTok{rule,}
  \AttributeTok{target\_vec =}\NormalTok{ Target,}
  \AttributeTok{target\_data =}\NormalTok{ SpecificDTM,}
  \AttributeTok{save\_path =}\NormalTok{ selection\_set\_file}
\NormalTok{)}

\CommentTok{\# Once the manual selection is performed the selected rules can be further}
\CommentTok{\# simplified in order to remove redundant rules and terms. The aim is to provide}
\CommentTok{\# the shortest rule without loss of sensitivity.}

\NormalTok{simplified\_rules }\OtherTok{\textless{}{-}} \FunctionTok{file.path}\NormalTok{(}\StringTok{"Sessions"}\NormalTok{, }\StringTok{"Session1"}\NormalTok{, }\StringTok{"Selected\_rules.xlsx"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{import\_data}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{simplify\_ruleset}\NormalTok{(}\AttributeTok{target\_vec =}\NormalTok{ Target, }\AttributeTok{target\_data =}\NormalTok{ SpecificDTM) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pull}\NormalTok{(rule)}

\CommentTok{\# Finally, the selected rules need to be joined in a query that scientific}
\CommentTok{\# search engines can understand}

\NormalTok{new\_query }\OtherTok{\textless{}{-}} \FunctionTok{rules\_to\_query}\NormalTok{(simplified\_rules)}
\end{Highlighting}
\end{Shaded}

One last thing to keep in mind is that the query generation algorithm is
only aware of the literature collected inside the annotation file. So it
will only be able to pick term combinations that identify positive
matches inside the already specific set of documents while not
necessarily being discriminant from the rest of the global literature.\\
Once the final query is generated, it is advisable to add a constraining
subquery with an AND logic to restrict the results to the scope of the
topic of interest.\\
In our case, we added ``AND ((antimicrobial resistance) OR (healthcare
infection))'' since, being the global topic of our research, those terms
were understandably not selected by the query generation algorithm as
discriminant.\\

The final query was the following:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{query }\OtherTok{\textless{}{-}} \StringTok{"(((Donker T) NOT (bacterium isolate)) OR ((network patient) AND}
\StringTok{(resistant staphylococcus aureus) NOT (monte carlo) NOT isolation) OR}
\StringTok{(facility AND (network patient) AND regional NOT hospitals NOT increase NOT}
\StringTok{(patient transport) NOT (control infection use)) OR ((patient transport) NOT}
\StringTok{(Donker T) NOT worker) OR (hospitals AND (network patient) NOT}
\StringTok{(patient transport) NOT regional NOT clinical) OR (facility AND}
\StringTok{(network patient) NOT hospitals NOT (patient transport) NOT regional NOT}
\StringTok{prevention NOT medical) OR ((healthcare facility) NOT (Donker T) NOT}
\StringTok{worker NOT positive) OR (hospitals NOT (network patient) NOT medical NOT}
\StringTok{environmental NOT outcome NOT global) OR ((network patient) NOT facility NOT}
\StringTok{hospitals NOT (patient transport) NOT therapy NOT global)) AND}
\StringTok{((antimicrobial resistance) OR (healthcare infection))"}
\end{Highlighting}
\end{Shaded}

Another advantage of this technique is an at-glance view of relevant
concepts for the topic of interest.

\hypertarget{new-search-session}{%
\subsection{New search session}\label{new-search-session}}

Once the new query was generated, a second search session can be
created, using the strategy described in the protocol. Due to the lower
specificity of the second query, particular care may be needed in
managing the far larger amount of records: multiple record files may
need to be downloaded from Pubmed, EMBASE, and SCOPUS since they have
limits on the number of records one can download at once; also, the
machine learning classification processing time increases proportionally
with the number of records to label.\\
It is advisable to consider removing the less specific rules iteratively
from the new query until a manageable number of records is obtained,
considering that the probability of finding new positive matches not
already found by more specific queries drops exponentially.\\

Once the new records are collected are manually collected for databases
without an API access, a new search can be performed. The following code
describe how to create a new session. Keep in mind to give the session a
new name and to import the annotated records from the last session when
generating the new annotation file.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Repeat the search with the new query, giving a different Session name not to}
\CommentTok{\# override previous records}
\NormalTok{journal }\OtherTok{\textless{}{-}} \FunctionTok{perform\_search\_session}\NormalTok{(}
  \AttributeTok{query =}\NormalTok{ query, }\AttributeTok{year\_query =}\NormalTok{ year\_filter,}
  \AttributeTok{session\_name =} \StringTok{"Session2"}\NormalTok{, }\AttributeTok{query\_name =} \StringTok{"Query1"}\NormalTok{,}
  \AttributeTok{records\_folder =} \StringTok{"Records"}\NormalTok{,}
  \AttributeTok{journal =} \StringTok{"Session\_journal.csv"}
\NormalTok{)}

\CommentTok{\# Get the path to the annotated data in the previous session}
\NormalTok{previousAnnotations }\OtherTok{\textless{}{-}} \FunctionTok{get\_session\_files}\NormalTok{(}\StringTok{"Session1"}\NormalTok{)}\SpecialCharTok{$}\NormalTok{Annotations }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{last}\NormalTok{()}

\CommentTok{\# Create the new annotation file passing the folder with the new records}
\NormalTok{Annotation\_data }\OtherTok{\textless{}{-}} \FunctionTok{create\_annotation\_file}\NormalTok{(}
  \FunctionTok{file.path}\NormalTok{(}\StringTok{"Records"}\NormalTok{, }\StringTok{"Session2"}\NormalTok{),}
  \AttributeTok{reorder\_query =}\NormalTok{ query,}
  \AttributeTok{prev\_records =}\NormalTok{ previousAnnotations}
\NormalTok{)}

\CommentTok{\# Create the new annotation session}
\FunctionTok{create\_session}\NormalTok{(Annotation\_data, }\AttributeTok{session\_name =} \StringTok{"Session2"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

Once the new annotation session data is created,
\texttt{enrich\_annotation\_file(\textquotesingle{}Session2\textquotesingle{})}
can be used to perform the CR iterations. It may be possible that during
the first CR iteration, the number of records requiring manual review is
very large: we suggest evaluating still not more than 250, setting the
\texttt{stop\_on\_unreviewed} argument to \texttt{FALSE} to proceed in
the automatic classification even if some uncertain records from the
precedent iteration are still unreviewed.

\hypertarget{result-analysis-and-reporting}{%
\subsection{Result analysis and
reporting}\label{result-analysis-and-reporting}}

Several tools are available to evaluate the classification
performance.\\
As said before, a result file is stored in the session folder for each
CR iteration with information on the classification status; remember to
run \texttt{consolidate\_results(session\_name)} if you want these
results to account for the manual review of the predicted labels.\\
\texttt{compute\_changes()} is a simple function that take an annotation
data frame and computes the changes from the last annotation
iteration.\\
The primary function for result analysis is
\texttt{estimate\_performance()}. The function uses a Bayesian model to
estimate how the probability of a positive match drops as records' lower
boundary of the posterior predictive interval decreases. This model
computes the cumulative distribution of possibly missed positive
records, which permits extraction of the engine's theoretical
sensitivity and efficiency to lower 90\% credibility boundaries (i.e.,
the indicators are better than these values with 95\% probability).
These boundaries depict worse case scenarios since it is impossible to
know the actual number of missed positive records.\\
The function returns the Bayesian \(R^2\) of the model (values below
85-90\% would invalidate the model analysis), the posterior sensitivity,
the observed and theoretical number positives, the expected efficiency
given the theoretical number of positives (that is 1 - the number of
reviewed records above the number of records to review to find the
predicted number of positives according to a negative hypergeometrical
distribution). Also, the function plots the cumulative distribution of
the observed and theoretical number of positive records.\\
\texttt{extract\_var\_imp()} extract the most relevant terms used by the
BART model and summarises their relevancy for the machine learning model
and their statistical relevancy in a simple generalised linear model. A
discrepancy between these two scores indicates a non-linear
effect/interaction between terms.

Finally, several functions are available (check \texttt{R/Reporting.R})
to summarise and format the results.\\
For example, \texttt{summarise\_by\_source()} and
\texttt{summarise\_sources\_by\_session()}, respectively for one session
or a group of sessions, report the scientific databases the records are
collected from, while \texttt{get\_source\_distribution()} describes the
distribution of the number of common sources per record.\\
\texttt{summarise\_annotations()} and
\texttt{summarise\_annotations\_by\_session()} describe the results of
the CR iterations, again for one or multiple sessions, reporting the
number of positive and negative matches, the number of terms (features)
used by the machine learning model, and how the labels change between
iterations. \texttt{format\_performance()} and
\texttt{format\_var\_imp()} format the output of the similarly named
analyses. \texttt{plot\_predictive\_densities()} plots how the mixture
of posterior predictive distributions of records, divided into positive,
negative and to-review records, change between iterations.

\hypertarget{model-parameters-optimisation}{%
\section{Model parameters'
optimisation}\label{model-parameters-optimisation}}

As with many complex machine learning models, the choice of
hyperparameters can significantly influence the framework performance.
For a systematic review helper algorithm, we define the performance as
the ability to find as many positive matches by manually
labelling/reviewing as few records as possible:\\

\[
Sensitivity \times Efficiency = \\
\frac{Pos.\ found}{Tot.\ pos.} \times \bigg(1 - \frac{Records\ reviewed}{Tot.\ records}\bigg)
\]

We utilise a ``grid search'' algorithm to find the best set of
hyperparameters. We tested these tools on our dataset, manually
labelling the first 1200 records, ordered by simple query match.\\
The first step is to create a folder to store the file required for the
search, for example, \emph{Grid Search}. Then a fully reviewed record
file in the format generated by \texttt{create\_annotation\_file()} is
necessary; this file can be put in the \emph{Grid Search}, but it is not
mandatory.\\

Once the folder and the file are ready, run:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Grid\_search }\OtherTok{\textless{}{-}} \FunctionTok{perform\_grid\_evaluation}\NormalTok{(}
\NormalTok{  records,}
  \AttributeTok{sessions\_folder =} \StringTok{"Grid\_Search"}\NormalTok{,}
  \AttributeTok{prev\_classification =}\NormalTok{ records,}
  \DocumentationTok{\#\# Model parameters (can be changed by users)}
  \AttributeTok{resample =} \FunctionTok{c}\NormalTok{(}\ConstantTok{FALSE}\NormalTok{, }\ConstantTok{TRUE}\NormalTok{),}
  \AttributeTok{n\_init =} \FunctionTok{c}\NormalTok{(}\DecValTok{50}\NormalTok{, }\DecValTok{100}\NormalTok{, }\DecValTok{250}\NormalTok{, }\DecValTok{500}\NormalTok{),}
  \AttributeTok{n\_models =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{5}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{20}\NormalTok{, }\DecValTok{40}\NormalTok{, }\DecValTok{60}\NormalTok{),}
  \AttributeTok{pos\_mult =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{20}\NormalTok{),}
  \AttributeTok{pred\_quants =} \FunctionTok{list}\NormalTok{(}
    \FunctionTok{c}\NormalTok{(.}\DecValTok{1}\NormalTok{, .}\DecValTok{5}\NormalTok{, .}\DecValTok{9}\NormalTok{),}
    \FunctionTok{c}\NormalTok{(.}\DecValTok{05}\NormalTok{, .}\DecValTok{5}\NormalTok{, .}\DecValTok{95}\NormalTok{),}
    \FunctionTok{c}\NormalTok{(.}\DecValTok{01}\NormalTok{, .}\DecValTok{5}\NormalTok{, .}\DecValTok{99}\NormalTok{)}
\NormalTok{  )}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

with \texttt{records} being the fully annotated data frame or a file
path. \texttt{prev\_classification} can be used to import a different
classification file with prelabeled records.

The hyperparameters are the following:

\begin{itemize}
\tightlist
\item
  resample: whether to use bootstrapping to increase variability between
  the ensemble models;
\item
  n\_init: number of initially labelled records to train the machine
  learning model on;
\item
  n\_models: the number of models to fit and then average to decrease
  the variance due to random sampling in the MCMC algorithm. It reduces
  the likelihood of extreme predictions;
\item
  pos\_mult: the oversampling rate of positive records. Useful to
  improve sensitivity;
\item
  pred\_quants: the distribution quantiles of each PPD, used to define
  the uncertainty zone and identify records to review.
\end{itemize}

Once the grid search is performed, the function
\texttt{analyse\_grid\_search()} can be used to analyse its results.
This function uses a partition tree analysis to identify hyperparameter
sets (\textbf{performance clusters}) with different mean performance
scores. As said before, the default score is Sensitivity x Efficiency;
alternatives are the Positive Rate (i.e., positive records found over
total records) or Positive Rate x Sensitivity.\\
The function produces a data frame with the score and the cluster of
reference of each combination of parameters, the best hyperparameter set
(i.e., the most efficient set among the most sensitive in the best
cluster) and the best set for each cluster. Also, the function creates a
plot to visualise each hyperparameter's impact on performance.

Once chosen, the hyperparameters can be passed to
\texttt{enrich\_annotation\_file()}.\\
Mind that the grid search process may take many days, even on powerful
computers, so we suggest sticking to the default set of parameters when
using \texttt{enrich\_annotation\_file()}.\\

\end{document}

### 2022-02-19 Manuscript/S2.Additional_outputs.Rmd
update for arxiv submission

@@
     toc: yes
+    keep_tex: true
     includes:
@@
 
-```{r posterior distributions, fig.width=10, fig.height=10, fig.cap="**Figure 1**. Mixture predictive distribution of the probability of a positive match, grouped by labelling status."}
+```{r posterior_distributions, fig.width=10, fig.height=10, fig.cap="**Figure 1**. Mixture predictive distribution of the probability of a positive match, grouped by labelling status."}
 

### 2022-02-19 Manuscript/S2.Additional_outputs.tex
update for arxiv submission

@@
 ]{article}
+\title{S2. Additional figures and table}
+\author{}
+\date{\vspace{-2.5em}2022-02-19}
+
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
   \usepackage{textcomp} % provide euro and other symbols
-  \usepackage{amssymb}
 \else % if luatex or xetex
@@
 \usepackage{xcolor}
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-
-\title{S2. Additional figures and table}
-\author{}
-\date{\vspace{-2.5em}2021-10-25}
 
@@
 \centering
-\includegraphics{S2.Additional_outputs_files/figure-latex/posterior distributions-1.pdf}
-\caption{Figure 1. Mixture predictive distribution of the probability of
-a positive match, grouped by labelling status.}
+\includegraphics{S2.Additional_outputs_files/figure-latex/posterior_distributions-1.pdf}
+\caption{\textbf{Figure 1}. Mixture predictive distribution of the
+probability of a positive match, grouped by labelling status.}
 \end{figure}
@@
 
-\caption{\label{tab:var imp}Table 1. Term importance at the end of Session 1.}
+\caption{\label{tab:var imp}\textbf{Table 1}. Term importance at the end of Session 1.}
 \centering
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llrrll}
+\begin{tabular}[t]{llllll}
 \toprule
@@
 \cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Patient Transport} & \cellcolor{gray!6}{61.2} & \cellcolor{gray!6}{3.77} & \cellcolor{gray!6}{99.1} & \cellcolor{gray!6}{21.3}\\
-Abstract & Transfer & 57.0 & 3.93 & 22.5 & 15.4\\
+Abstract & Transfer & 57 & 3.93 & 22.5 & 15.4\\
 \cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Network} & \cellcolor{gray!6}{56.5} & \cellcolor{gray!6}{2.91} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{14.2}\\
-Abstract & Network & Patient & 54.2 & 4.66 & 26.3 & 15.2\\
+Abstract & Network \& Patient & 54.2 & 4.66 & 26.3 & 15.2\\
 \cellcolor{gray!6}{Author} & \cellcolor{gray!6}{Donker T} & \cellcolor{gray!6}{53.5} & \cellcolor{gray!6}{4.56} & \cellcolor{gray!6}{159} & \cellcolor{gray!6}{16.5}\\
 \addlinespace
-Abstract & Worker & 50.0 & 3.33 & 0.421 & -1.21\\
+Abstract & Worker & 50 & 3.33 & 0.421 & -1.21\\
 \cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Hospitals} & \cellcolor{gray!6}{49.8} & \cellcolor{gray!6}{4.31} & \cellcolor{gray!6}{27.8} & \cellcolor{gray!6}{16.5}\\
-Abstract & Movement & 47.8 & 2.70 & 27.2 & 15\\
+Abstract & Movement & 47.8 & 2.7 & 27.2 & 15\\
 \cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Spread} & \cellcolor{gray!6}{46.6} & \cellcolor{gray!6}{2.25} & \cellcolor{gray!6}{16.2} & \cellcolor{gray!6}{12.1}\\
-Abstract & Facility & 45.0 & 2.22 & 19.6 & 14.8\\
+Abstract & Facility & 45 & 2.22 & 19.6 & 14.8\\
 \addlinespace
 \cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Orange County} & \cellcolor{gray!6}{44.3} & \cellcolor{gray!6}{3.19} & \cellcolor{gray!6}{199} & \cellcolor{gray!6}{17.2}\\
-Abstract & Conduct & 42.6 & 3.70 & 0.221 & -2.57\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Patient} & \cellcolor{gray!6}{42.0} & \cellcolor{gray!6}{3.61} & \cellcolor{gray!6}{27.6} & \cellcolor{gray!6}{7.23}\\
+Abstract & Conduct & 42.6 & 3.7 & 0.221 & -2.57\\
+\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Patient} & \cellcolor{gray!6}{42} & \cellcolor{gray!6}{3.61} & \cellcolor{gray!6}{27.6} & \cellcolor{gray!6}{7.23}\\
 Abstract & Perform & 41.9 & 2.38 & 0.342 & -2.55\\
-\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Hospital} & \cellcolor{gray!6}{39.0} & \cellcolor{gray!6}{1.95} & \cellcolor{gray!6}{12.5} & \cellcolor{gray!6}{12.5}\\
+\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Hospital} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{1.95} & \cellcolor{gray!6}{12.5} & \cellcolor{gray!6}{12.5}\\
 \addlinespace
@@
 \cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Agent} & \cellcolor{gray!6}{38.1} & \cellcolor{gray!6}{2.74} & \cellcolor{gray!6}{4.36} & \cellcolor{gray!6}{6.28}\\
-Abstract & California & 37.3 & 2.60 & 38 & 12.6\\
+Abstract & California & 37.3 & 2.6 & 38 & 12.6\\
 \cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Transfer} & \cellcolor{gray!6}{36.6} & \cellcolor{gray!6}{3.54} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{11.8}\\
-Keyword & Patient Transfer | Patient Transfer & Patient Transport & 36.6 & 2.16 & 164 & 2\\
+Keyword & Patient Transfer | Patient Transfer \& Patient Transport & 36.6 & 2.16 & 164 & 2\\
 \addlinespace
@@
 Abstract & Positive & 28.8 & 1.96 & 0.346 & -2.52\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Gene} & \cellcolor{gray!6}{28.3} & \cellcolor{gray!6}{1.29} & \cellcolor{gray!6}{2.4e-07} & \cellcolor{gray!6}{-0.0415}\\
-Abstract & Disease & 28.0 & 2.42 & 0.365 & -3.7\\
+\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Gene} & \cellcolor{gray!6}{28.3} & \cellcolor{gray!6}{1.29} & \cellcolor{gray!6}{0.00000024} & \cellcolor{gray!6}{-0.0415}\\
+Abstract & Disease & 28 & 2.42 & 0.365 & -3.7\\
 \cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Enterococci} & \cellcolor{gray!6}{27.5} & \cellcolor{gray!6}{1.92} & \cellcolor{gray!6}{25.2} & \cellcolor{gray!6}{6.33}\\
@@
 Abstract & Month & 27.3 & 1.86 & 0.288 & -2.44\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Healthcare} & \cellcolor{gray!6}{Facility} & \cellcolor{gray!6}{26.2} & \cellcolor{gray!6}{1.74} & \cellcolor{gray!6}{34.9} & \cellcolor{gray!6}{17}\\
+\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Healthcare \& Facility} & \cellcolor{gray!6}{26.2} & \cellcolor{gray!6}{1.74} & \cellcolor{gray!6}{34.9} & \cellcolor{gray!6}{17}\\
 Abstract & Prevalence & 26.2 & 1.71 & 4.08 & 6.69\\
@@
 \addlinespace
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{System} & \cellcolor{gray!6}{25.0} & \cellcolor{gray!6}{1.43} & \cellcolor{gray!6}{11.9} & \cellcolor{gray!6}{3.47}\\
+\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{System} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{1.43} & \cellcolor{gray!6}{11.9} & \cellcolor{gray!6}{3.47}\\
 Abstract & Laboratory & 24.4 & 1.38 & 0.442 & -1.39\\
 \cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Resistant Staphylococcus Aureus} & \cellcolor{gray!6}{24.4} & \cellcolor{gray!6}{1.59} & \cellcolor{gray!6}{22.8} & \cellcolor{gray!6}{11.2}\\
-Abstract & Clinical & 23.6 & 2.10 & 0.421 & -2.9\\
+Abstract & Clinical & 23.6 & 2.1 & 0.421 & -2.9\\
 \cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Dataset} & \cellcolor{gray!6}{22.5} & \cellcolor{gray!6}{1.47} & \cellcolor{gray!6}{8.75} & \cellcolor{gray!6}{6.5}\\
@@
 Abstract & Development & 22.2 & 1.22 & 0.148 & -2.68\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Hand} & \cellcolor{gray!6}{22.0} & \cellcolor{gray!6}{1.97} & \cellcolor{gray!6}{0.822} & \cellcolor{gray!6}{-0.335}\\
+\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Hand} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{1.97} & \cellcolor{gray!6}{0.822} & \cellcolor{gray!6}{-0.335}\\
 Keyword & Pathogen Transmission & 21.8 & 3.26 & 67.9 & 7.2\\
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Cross Infection} & \cellcolor{gray!6}{Humans} & \cellcolor{gray!6}{Transmission} & \cellcolor{gray!6}{21.7} & \cellcolor{gray!6}{1.40} & \cellcolor{gray!6}{31.1} & \cellcolor{gray!6}{15.5}\\
+\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Cross Infection \& Humans \& Transmission} & \cellcolor{gray!6}{21.7} & \cellcolor{gray!6}{1.4} & \cellcolor{gray!6}{31.1} & \cellcolor{gray!6}{15.5}\\
 Abstract & Flow & 21.4 & 1.14 & 4.07 & 4.56\\
@@
 
-\caption{\label{tab:var imp}Table 2. Term importance at the end of Session 2.}
+\caption{\label{tab:var imp}\textbf{Table 2}. Term importance at the end of Session 2.}
 \centering
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llrrll}
+\begin{tabular}[t]{llllll}
 \toprule
@@
 
-\caption{\label{tab:hyperparameters}Table 3.
+\caption{\label{tab:hyperparameters}\textbf{Table 3}.
 Hyperparameter clusters and best cluster subsets.
@@
 \cellcolor{gray!6}{1.
-Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = n} & \cellcolor{gray!6}{Init = 100,250 (0.64)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{462 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{61.5\%} & \cellcolor{gray!6}{0.608} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
-2. Mult = 10,20 & Mods = 10,20,40,60 & Resamp = y & Init = 250,500 & Mods = 20,40,60 (0.56) & 5 & 82 / 82 & 618 / 1200 & 100\% & 48.5\% & 0.485 & 20 & 80 & y & 250 & 10\\
+Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = n \& Init = 100,250 (0.64)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{462 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{61.5\%} & \cellcolor{gray!6}{0.608} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
+2. Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = y \& Init = 250,500 \& Mods = 20,40,60 (0.56) & 5 & 82 / 82 & 618 / 1200 & 100\% & 48.5\% & 0.485 & 20 & 80 & y & 250 & 10\\
 \cellcolor{gray!6}{3.
-Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = n} & \cellcolor{gray!6}{Init = 50,500 (0.5)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{589 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{50.9\%} & \cellcolor{gray!6}{0.503} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{10}\\
-4. Mult = 10,20 & Mods = 1,5 & Resamp = n & Mods = 5 (0.47) & 8 & 82 / 82 & 1123 / 1200 & 100\% & 6.42\% & 0.0642 & 5 & 98 & n & 50 & 10\\
+Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = n \& Init = 50,500 (0.5)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{589 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{50.9\%} & \cellcolor{gray!6}{0.503} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{10}\\
+4. Mult = 10,20 \& Mods = 1,5 \& Resamp = n \& Mods = 5 (0.47) & 8 & 82 / 82 & 1123 / 1200 & 100\% & 6.42\% & 0.0642 & 5 & 98 & n & 50 & 10\\
 \cellcolor{gray!6}{5.
-Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = y} & \cellcolor{gray!6}{Init = 250,500} & \cellcolor{gray!6}{Mods = 10 (0.39)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{685 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{42.9\%} & \cellcolor{gray!6}{0.429} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{80} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
+Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = y \& Init = 250,500 \& Mods = 10 (0.39)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{685 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{42.9\%} & \cellcolor{gray!6}{0.429} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{80} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
 \addlinespace
-6. Mult = 10,20 & Mods = 1,5 & Resamp = n & Mods = 1 & Init = 250,500 (0.31) & 5 & 82 / 82 & 874 / 1200 & 100\% & 27.2\% & 0.272 & 1 & 90 & n & 250 & 10\\
+6. Mult = 10,20 \& Mods = 1,5 \& Resamp = n \& Mods = 1 \& Init = 250,500 (0.31) & 5 & 82 / 82 & 874 / 1200 & 100\% & 27.2\% & 0.272 & 1 & 90 & n & 250 & 10\\
 \cellcolor{gray!6}{7.
-Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = y} & \cellcolor{gray!6}{Init = 50,100 (0.23)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{948 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{21\%} & \cellcolor{gray!6}{0.21} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
-8. Mult = 1 & Init = 250,500 & Mods = 20,40,60 (0.21) & 5 & 82 / 82 & 806 / 1200 & 100\% & 32.8\% & 0.328 & 60 & 80 & y & 250 & 1\\
+Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = y \& Init = 50,100 (0.23)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{948 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{21\%} & \cellcolor{gray!6}{0.21} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
+8. Mult = 1 \& Init = 250,500 \& Mods = 20,40,60 (0.21) & 5 & 82 / 82 & 806 / 1200 & 100\% & 32.8\% & 0.328 & 60 & 80 & y & 250 & 1\\
 \cellcolor{gray!6}{9.
-Mult = 10,20} & \cellcolor{gray!6}{Mods = 1,5} & \cellcolor{gray!6}{Resamp = n} & \cellcolor{gray!6}{Mods = 1} & \cellcolor{gray!6}{Init = 50,100 (0.078)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{1139 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{5.08\%} & \cellcolor{gray!6}{0.0508} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
-10. Mult = 10,20 & Mods = 1,5 & Resamp = y (0.054) & 5 & 82 / 82 & 832 / 1200 & 100\% & 30.7\% & 0.307 & 5 & 80 & y & 250 & 20\\
+Mult = 10,20 \& Mods = 1,5 \& Resamp = n \& Mods = 1 \& Init = 50,100 (0.078)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{1139 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{5.08\%} & \cellcolor{gray!6}{0.0508} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
+10. Mult = 10,20 \& Mods = 1,5 \& Resamp = y (0.054) & 5 & 82 / 82 & 832 / 1200 & 100\% & 30.7\% & 0.307 & 5 & 80 & y & 250 & 20\\
 \addlinespace
 \cellcolor{gray!6}{11.
-Mult = 1} & \cellcolor{gray!6}{Init = 250,500} & \cellcolor{gray!6}{Mods = 1,5,10 (0.025)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{981 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{18.2\%} & \cellcolor{gray!6}{0.182} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{1}\\
-12. Mult = 1 & Init = 50,100 (0.0045) & 6 & 82 / 82 & 1151 / 1200 & 100\% & 4.08\% & 0.0408 & 20 & 80 & y & 50 & 1\\
+Mult = 1 \& Init = 250,500 \& Mods = 1,5,10 (0.025)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{981 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{18.2\%} & \cellcolor{gray!6}{0.182} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{1}\\
+12. Mult = 1 \& Init = 50,100 (0.0045) & 6 & 82 / 82 & 1151 / 1200 & 100\% & 4.08\% & 0.0408 & 20 & 80 & y & 50 & 1\\
 \bottomrule

### 2022-02-19 Manuscript/S3.Search_guide.tex
update for arxiv submission

--- 2022-02-19 Manuscript/S2.Additional_outputs.tex
@@
 ]{article}
-\title{S2. Additional figures and table}
+\title{Databases' search guide}
 \author{}
@@
 \hypersetup{
-  pdftitle={S2. Additional figures and table},
+  pdftitle={Databases' search guide},
   hidelinks,
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-\usepackage{caption}
-\usepackage{placeins}
-\usepackage{amsmath}
-\usepackage{lineno}
-\linenumbers
-\captionsetup[table]{labelformat=empty}
-\captionsetup[figure]{labelformat=empty}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
 \ifLuaTeX
@@
 
-{
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
-\newpage
+\hypertarget{wos}{%
+\subsection{WOS}\label{wos}}
 
-\hypertarget{posterior-predictive-distributions}{%
-\section{Posterior predictive
-distributions}\label{posterior-predictive-distributions}}
+\begin{itemize}
+\tightlist
+\item
+  activate your institution proxy or log in in some way (it is only
+  needed to get the API key, then you can log off the proxy)
+\item
+  go to \url{https://apps.webofknowledge.com/}
+\item
+  extract the API key from the URL, is denominated by SID
+\item
+  put the key in the secrets.R file and source it or source Setup.R
+\item
+  perform the search using the API
+\end{itemize}
 
-Figure 1 show the mixture of the PPD of the probability of a positive
-match, grouped by label (only records manually labelled or reviewed are
-considered). The posterior samples for each record were extracted and
-joined into a global distribution; on this distribution, density was
-computed on the logit scale and then logistic transformed for displaying
-on a \([0 - 1]\) scale. The purple ridges show the distribution of the
-still unlabelled records.\\
-For each iteration, the thresholds which define the ``uncertainty
-zone'', i.e, the lower and the upper range of 98\% PrI for the positive
-and negative records respectively, are shown. Records whose 98\% PrI
-intersects the uncertainty zone requires manual review.\\
-Notice how the positive and negative record densities tend to
-increasingly overlap at each iteration; meanwhile the distribution of
-the records to be reviewed shrinks and shifts towards the negative side,
-as positive records get found and labeled.\\
-In Session 2, as the number of negative records reviewed increased, also
-already positively labelled records re-entered the uncertainty zone;
-this is due to the baseline positivity rate decreasing as the number of
-negatives in the training data increased, forcing to review dubious
-records that may have been mislabelled.
+\hypertarget{ieee}{%
+\subsection{IEEE}\label{ieee}}
 
-\begin{figure}
-\centering
-\includegraphics{S2.Additional_outputs_files/figure-latex/posterior_distributions-1.pdf}
-\caption{\textbf{Figure 1}. Mixture predictive distribution of the
-probability of a positive match, grouped by labelling status.}
-\end{figure}
+\begin{itemize}
+\tightlist
+\item
+  get your API key and put it into the secrets.R
+\item
+  source the file source Setup.R
+\item
+  perform the search using the API
+\end{itemize}
 
-\hypertarget{list-of-terms-relevant-for-prediction}{%
-\section{List of terms relevant for
-prediction}\label{list-of-terms-relevant-for-prediction}}
+\hypertarget{scopus}{%
+\subsection{Scopus}\label{scopus}}
 
-In table 1 and 2 are listed the 50 more relevant terms used by the BART
-algorithm to discriminate between positive and negative records, for
-Session 1 and 2 (see Methods). Term importance (``Inclusion rate'' in
-the tables) is defined as the ensemble average inclusion rate in
-posterior trees over 10,000 total term inclusions, while the Inclusion
-Stability (IS) is the ratio of the average inclusion rate over its
-standard deviation among the ensemble models. The symbol ``\textbar{}''
-in the terms indicate redundant terms while ``\&'' indicate nc-grams.
-The component in which the term was used is reported in the leftmost
-column.\\
-For each term, we added its linear association with a positive label
-estimated through a Poisson regression, reporting it as Relative Risk
-(RR) and its statistical significance (Statistic) measured as number of
-standard errors, s.e., of the terms. A strong BART score with a
-Statistic close to zero identify terms whose effect is highly non-linear
-(e.g., they are relevant only in the presence of other terms).
+\begin{itemize}
+\tightlist
+\item
+  change the NOT in the query to AND NOT
+\item
+  go to
+  \url{https://www.scopus.com/search/form.uri?display=basic\#basic}
+\item
+  log in with your institution credential
+\item
+  set up the year range
+\item
+  search within: title, abstract, keywords, authors
+\item
+  select years in order to have just less than 2000 records
+\item
+  download csv (Excel). Choose ``Citation information'' and ``Abstract
+  \& keywords''
+\item
+  call the files Scopus\#.csv with \# being a sequential number
+\item
+  perform\_search\_session() will find and parse the files
+\end{itemize}
 
-\begin{table}[!h]
+\hypertarget{pubmed}{%
+\subsection{Pubmed}\label{pubmed}}
 
-\caption{\label{tab:var imp}\textbf{Table 1}. Term importance at the end of Session 1.}
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llllll}
-\toprule
-Component & Term & Inclusion rate & IS & RR & Statistic\\
-\midrule
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Patient Transport} & \cellcolor{gray!6}{61.2} & \cellcolor{gray!6}{3.77} & \cellcolor{gray!6}{99.1} & \cellcolor{gray!6}{21.3}\\
-Abstract & Transfer & 57 & 3.93 & 22.5 & 15.4\\
-\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Network} & \cellcolor{gray!6}{56.5} & \cellcolor{gray!6}{2.91} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{14.2}\\
-Abstract & Network \& Patient & 54.2 & 4.66 & 26.3 & 15.2\\
-\cellcolor{gray!6}{Author} & \cellcolor{gray!6}{Donker T} & \cellcolor{gray!6}{53.5} & \cellcolor{gray!6}{4.56} & \cellcolor{gray!6}{159} & \cellcolor{gray!6}{16.5}\\
-\addlinespace
-Abstract & Worker & 50 & 3.33 & 0.421 & -1.21\\
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Hospitals} & \cellcolor{gray!6}{49.8} & \cellcolor{gray!6}{4.31} & \cellcolor{gray!6}{27.8} & \cellcolor{gray!6}{16.5}\\
-Abstract & Movement & 47.8 & 2.7 & 27.2 & 15\\
-\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Spread} & \cellcolor{gray!6}{46.6} & \cellcolor{gray!6}{2.25} & \cellcolor{gray!6}{16.2} & \cellcolor{gray!6}{12.1}\\
-Abstract & Facility & 45 & 2.22 & 19.6 & 14.8\\
-\addlinespace
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Orange County} & \cellcolor{gray!6}{44.3} & \cellcolor{gray!6}{3.19} & \cellcolor{gray!6}{199} & \cellcolor{gray!6}{17.2}\\
-Abstract & Conduct & 42.6 & 3.7 & 0.221 & -2.57\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Patient} & \cellcolor{gray!6}{42} & \cellcolor{gray!6}{3.61} & \cellcolor{gray!6}{27.6} & \cellcolor{gray!6}{7.23}\\
-Abstract & Perform & 41.9 & 2.38 & 0.342 & -2.55\\
-\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Hospital} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{1.95} & \cellcolor{gray!6}{12.5} & \cellcolor{gray!6}{12.5}\\
-\addlinespace
-Abstract & Regional & 38.9 & 3.08 & 21.7 & 14.9\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Agent} & \cellcolor{gray!6}{38.1} & \cellcolor{gray!6}{2.74} & \cellcolor{gray!6}{4.36} & \cellcolor{gray!6}{6.28}\\
-Abstract & California & 37.3 & 2.6 & 38 & 12.6\\
-\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Transfer} & \cellcolor{gray!6}{36.6} & \cellcolor{gray!6}{3.54} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{11.8}\\
-Keyword & Patient Transfer | Patient Transfer \& Patient Transport & 36.6 & 2.16 & 164 & 2\\
-\addlinespace
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Finding} & \cellcolor{gray!6}{33.2} & \cellcolor{gray!6}{1.78} & \cellcolor{gray!6}{0.372} & \cellcolor{gray!6}{-2.35}\\
-Title & Outbreak & 32.9 & 2.91 & 3.4 & 3.51\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Collect} & \cellcolor{gray!6}{32.4} & \cellcolor{gray!6}{1.82} & \cellcolor{gray!6}{0.408} & \cellcolor{gray!6}{-1.95}\\
-Title & Regional & 32.3 & 2.68 & 44.2 & 14.2\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Network} & \cellcolor{gray!6}{31.6} & \cellcolor{gray!6}{3.09} & \cellcolor{gray!6}{12.8} & \cellcolor{gray!6}{11.7}\\
-\addlinespace
-Abstract & Resistant & 31.6 & 2.55 & 11 & 11.2\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Outcome} & \cellcolor{gray!6}{31.2} & \cellcolor{gray!6}{1.93} & \cellcolor{gray!6}{0.178} & \cellcolor{gray!6}{-2.95}\\
-Abstract & Discharge & 31.1 & 3.79 & 9.99 & 9.02\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{30.3} & \cellcolor{gray!6}{1.84} & \cellcolor{gray!6}{0.588} & \cellcolor{gray!6}{-1.04}\\
-Abstract & Practice & 29.5 & 2.47 & 0.508 & -1.33\\
-\addlinespace
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Culture} & \cellcolor{gray!6}{28.9} & \cellcolor{gray!6}{2.14} & \cellcolor{gray!6}{0.378} & \cellcolor{gray!6}{-1.66}\\
-Abstract & Positive & 28.8 & 1.96 & 0.346 & -2.52\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Gene} & \cellcolor{gray!6}{28.3} & \cellcolor{gray!6}{1.29} & \cellcolor{gray!6}{0.00000024} & \cellcolor{gray!6}{-0.0415}\\
-Abstract & Disease & 28 & 2.42 & 0.365 & -3.7\\
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Enterococci} & \cellcolor{gray!6}{27.5} & \cellcolor{gray!6}{1.92} & \cellcolor{gray!6}{25.2} & \cellcolor{gray!6}{6.33}\\
-\addlinespace
-Abstract & Month & 27.3 & 1.86 & 0.288 & -2.44\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Healthcare \& Facility} & \cellcolor{gray!6}{26.2} & \cellcolor{gray!6}{1.74} & \cellcolor{gray!6}{34.9} & \cellcolor{gray!6}{17}\\
-Abstract & Prevalence & 26.2 & 1.71 & 4.08 & 6.69\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Effort} & \cellcolor{gray!6}{26.1} & \cellcolor{gray!6}{1.22} & \cellcolor{gray!6}{6.64} & \cellcolor{gray!6}{8.57}\\
-Abstract & Length & 25.3 & 1.44 & 6.1 & 6.45\\
-\addlinespace
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{System} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{1.43} & \cellcolor{gray!6}{11.9} & \cellcolor{gray!6}{3.47}\\
-Abstract & Laboratory & 24.4 & 1.38 & 0.442 & -1.39\\
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Resistant Staphylococcus Aureus} & \cellcolor{gray!6}{24.4} & \cellcolor{gray!6}{1.59} & \cellcolor{gray!6}{22.8} & \cellcolor{gray!6}{11.2}\\
-Abstract & Clinical & 23.6 & 2.1 & 0.421 & -2.9\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Dataset} & \cellcolor{gray!6}{22.5} & \cellcolor{gray!6}{1.47} & \cellcolor{gray!6}{8.75} & \cellcolor{gray!6}{6.5}\\
-\addlinespace
-Abstract & Development & 22.2 & 1.22 & 0.148 & -2.68\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Hand} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{1.97} & \cellcolor{gray!6}{0.822} & \cellcolor{gray!6}{-0.335}\\
-Keyword & Pathogen Transmission & 21.8 & 3.26 & 67.9 & 7.2\\
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Cross Infection \& Humans \& Transmission} & \cellcolor{gray!6}{21.7} & \cellcolor{gray!6}{1.4} & \cellcolor{gray!6}{31.1} & \cellcolor{gray!6}{15.5}\\
-Abstract & Flow & 21.4 & 1.14 & 4.07 & 4.56\\
-\bottomrule
-\end{tabular}}
-\end{table}
+\begin{itemize}
+\tightlist
+\item
+  put your API key in the secrets.R file and source it or source Setup.R
+\item
+  perform the search using the API
+\item
+  put the same query into pubmed and download records in the Pubmed
+  format.
+\item
+  only 10k records can be downloaded at once, so use the year filter to
+  partition the records
+\item
+  call the file Pubmed\#.nbib with \# being a sequential number
+\item
+  perform\_search\_session() will find and parse the files
+\end{itemize}
 
-\begin{table}[!h]
+\hypertarget{embase}{%
+\subsection{Embase}\label{embase}}
 
-\caption{\label{tab:var imp}\textbf{Table 2}. Term importance at the end of Session 2.}
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llllll}
-\toprule
-Component & Term & Inclusion rate & IS & RR & Statistic\\
-\midrule
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Patient Transport} & \cellcolor{gray!6}{61.2} & \cellcolor{gray!6}{3.77} & \cellcolor{gray!6}{99.1} & \cellcolor{gray!6}{21.3}\\
-Abstract & Transfer & 57 & 3.93 & 22.5 & 15.4\\
-\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Network} & \cellcolor{gray!6}{56.5} & \cellcolor{gray!6}{2.91} & \cellcolor{gray!6}{18} & \cellcolor{gray!6}{14.2}\\
-Abstract & Network \& Patient & 54.2 & 4.66 & 26.3 & 15.2\\
-\cellcolor{gray!6}{Author} & \cellcolor{gray!6}{Donker T} & \cellcolor{gray!6}{53.5} & \cellcolor{gray!6}{4.56} & \cellcolor{gray!6}{159} & \cellcolor{gray!6}{16.5}\\
-\addlinespace
-Abstract & Worker & 50 & 3.33 & 0.421 & -1.21\\
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Hospitals} & \cellcolor{gray!6}{49.8} & \cellcolor{gray!6}{4.31} & \cellcolor{gray!6}{27.8} & \cellcolor{gray!6}{16.5}\\
-Abstract & Movement & 47.8 & 2.7 & 27.2 & 15\\
-\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Spread} & \cellcolor{gray!6}{46.6} & \cellcolor{gray!6}{2.25} & \cellcolor{gray!6}{16.2} & \cellcolor{gray!6}{12.1}\\
-Abstract & Facility & 45 & 2.22 & 19.6 & 14.8\\
-\addlinespace
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Orange County} & \cellcolor{gray!6}{44.3} & \cellcolor{gray!6}{3.19} & \cellcolor{gray!6}{199} & \cellcolor{gray!6}{17.2}\\
-Abstract & Conduct & 42.6 & 3.7 & 0.221 & -2.57\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Patient} & \cellcolor{gray!6}{42} & \cellcolor{gray!6}{3.61} & \cellcolor{gray!6}{27.6} & \cellcolor{gray!6}{7.23}\\
-Abstract & Perform & 41.9 & 2.38 & 0.342 & -2.55\\
-\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Hospital} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{1.95} & \cellcolor{gray!6}{12.5} & \cellcolor{gray!6}{12.5}\\
-\addlinespace
-Abstract & Regional & 38.9 & 3.08 & 21.7 & 14.9\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Agent} & \cellcolor{gray!6}{38.1} & \cellcolor{gray!6}{2.74} & \cellcolor{gray!6}{4.36} & \cellcolor{gray!6}{6.28}\\
-Abstract & California & 37.3 & 2.6 & 38 & 12.6\\
-\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Transfer} & \cellcolor{gray!6}{36.6} & \cellcolor{gray!6}{3.54} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{11.8}\\
-Keyword & Patient Transfer | Patient Transfer \& Patient Transport & 36.6 & 2.16 & 164 & 2\\
-\addlinespace
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Finding} & \cellcolor{gray!6}{33.2} & \cellcolor{gray!6}{1.78} & \cellcolor{gray!6}{0.372} & \cellcolor{gray!6}{-2.35}\\
-Title & Outbreak & 32.9 & 2.91 & 3.4 & 3.51\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Collect} & \cellcolor{gray!6}{32.4} & \cellcolor{gray!6}{1.82} & \cellcolor{gray!6}{0.408} & \cellcolor{gray!6}{-1.95}\\
-Title & Regional & 32.3 & 2.68 & 44.2 & 14.2\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Network} & \cellcolor{gray!6}{31.6} & \cellcolor{gray!6}{3.09} & \cellcolor{gray!6}{12.8} & \cellcolor{gray!6}{11.7}\\
-\addlinespace
-Abstract & Resistant & 31.6 & 2.55 & 11 & 11.2\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Outcome} & \cellcolor{gray!6}{31.2} & \cellcolor{gray!6}{1.93} & \cellcolor{gray!6}{0.178} & \cellcolor{gray!6}{-2.95}\\
-Abstract & Discharge & 31.1 & 3.79 & 9.99 & 9.02\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{2014} & \cellcolor{gray!6}{30.3} & \cellcolor{gray!6}{1.84} & \cellcolor{gray!6}{0.588} & \cellcolor{gray!6}{-1.04}\\
-Abstract & Practice & 29.5 & 2.47 & 0.508 & -1.33\\
-\addlinespace
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Culture} & \cellcolor{gray!6}{28.9} & \cellcolor{gray!6}{2.14} & \cellcolor{gray!6}{0.378} & \cellcolor{gray!6}{-1.66}\\
-Abstract & Positive & 28.8 & 1.96 & 0.346 & -2.52\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Gene} & \cellcolor{gray!6}{28.3} & \cellcolor{gray!6}{1.29} & \cellcolor{gray!6}{0.00000024} & \cellcolor{gray!6}{-0.0415}\\
-Abstract & Disease & 28 & 2.42 & 0.365 & -3.7\\
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Enterococci} & \cellcolor{gray!6}{27.5} & \cellcolor{gray!6}{1.92} & \cellcolor{gray!6}{25.2} & \cellcolor{gray!6}{6.33}\\
-\addlinespace
-Abstract & Month & 27.3 & 1.86 & 0.288 & -2.44\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Healthcare \& Facility} & \cellcolor{gray!6}{26.2} & \cellcolor{gray!6}{1.74} & \cellcolor{gray!6}{34.9} & \cellcolor{gray!6}{17}\\
-Abstract & Prevalence & 26.2 & 1.71 & 4.08 & 6.69\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Effort} & \cellcolor{gray!6}{26.1} & \cellcolor{gray!6}{1.22} & \cellcolor{gray!6}{6.64} & \cellcolor{gray!6}{8.57}\\
-Abstract & Length & 25.3 & 1.44 & 6.1 & 6.45\\
-\addlinespace
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{System} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{1.43} & \cellcolor{gray!6}{11.9} & \cellcolor{gray!6}{3.47}\\
-Abstract & Laboratory & 24.4 & 1.38 & 0.442 & -1.39\\
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Resistant Staphylococcus Aureus} & \cellcolor{gray!6}{24.4} & \cellcolor{gray!6}{1.59} & \cellcolor{gray!6}{22.8} & \cellcolor{gray!6}{11.2}\\
-Abstract & Clinical & 23.6 & 2.1 & 0.421 & -2.9\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Dataset} & \cellcolor{gray!6}{22.5} & \cellcolor{gray!6}{1.47} & \cellcolor{gray!6}{8.75} & \cellcolor{gray!6}{6.5}\\
-\addlinespace
-Abstract & Development & 22.2 & 1.22 & 0.148 & -2.68\\
-\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Hand} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{1.97} & \cellcolor{gray!6}{0.822} & \cellcolor{gray!6}{-0.335}\\
-Keyword & Pathogen Transmission & 21.8 & 3.26 & 67.9 & 7.2\\
-\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Cross Infection \& Humans \& Transmission} & \cellcolor{gray!6}{21.7} & \cellcolor{gray!6}{1.4} & \cellcolor{gray!6}{31.1} & \cellcolor{gray!6}{15.5}\\
-Abstract & Flow & 21.4 & 1.14 & 4.07 & 4.56\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\hypertarget{hyperparameters-grid-search}{%
-\section{Hyperparameters grid
-search}\label{hyperparameters-grid-search}}
-
-Table 3 shows the best hyperparameter set and their performance for each
-cluster while figure 2 displays the conditional impact on performance of
-each hyperparameter.
-
-The most influential parameters were the number of models in the
-ensemble, the oversampling rate and the initial training set size. The
-use of bootstrap resampling seemed detrimental.
-
-\begin{figure}
-\centering
-\includegraphics{S2.Additional_outputs_files/figure-latex/hyperparameters-1.pdf}
-\caption{\textbf{Figure 2}. Score clusters and impact of single
-hyperparameters on engine performance. The performance is measured as
-Sensitivity x Efficiency. Each cluster is color coded. Mods: number of
-models in the ensemble; Quant: PrI quantiles for the uncertainty zone;
-Resamp: bootstrap resampling between models; Init: size of initial
-training set; Multi: oversampling rate of positive records}
-\end{figure}
-
-\begin{table}[!h]
-
-\caption{\label{tab:hyperparameters}\textbf{Table 3}.
-Hyperparameter clusters and best cluster subsets.
-For each cluster, the defining rules and mean Sens.
-x Eff.
-is shown, followed by the per-cluster best set results.}
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llllllllllll}
-\toprule
-Cluster (mean score) & Num.
-iterations & Positive matches & Reviewed records & Sensitivity & Efficiency & Score (Sens.
-x Eff.) & Num.
-ensemble models & Uncertainty interval & Resampling & Num.
-initial training records & Positives oversampling multiplier\\
-\midrule
-\cellcolor{gray!6}{1.
-Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = n \& Init = 100,250 (0.64)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{462 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{61.5\%} & \cellcolor{gray!6}{0.608} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
-2. Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = y \& Init = 250,500 \& Mods = 20,40,60 (0.56) & 5 & 82 / 82 & 618 / 1200 & 100\% & 48.5\% & 0.485 & 20 & 80 & y & 250 & 10\\
-\cellcolor{gray!6}{3.
-Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = n \& Init = 50,500 (0.5)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{589 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{50.9\%} & \cellcolor{gray!6}{0.503} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{10}\\
-4. Mult = 10,20 \& Mods = 1,5 \& Resamp = n \& Mods = 5 (0.47) & 8 & 82 / 82 & 1123 / 1200 & 100\% & 6.42\% & 0.0642 & 5 & 98 & n & 50 & 10\\
-\cellcolor{gray!6}{5.
-Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = y \& Init = 250,500 \& Mods = 10 (0.39)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{685 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{42.9\%} & \cellcolor{gray!6}{0.429} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{80} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
-\addlinespace
-6. Mult = 10,20 \& Mods = 1,5 \& Resamp = n \& Mods = 1 \& Init = 250,500 (0.31) & 5 & 82 / 82 & 874 / 1200 & 100\% & 27.2\% & 0.272 & 1 & 90 & n & 250 & 10\\
-\cellcolor{gray!6}{7.
-Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = y \& Init = 50,100 (0.23)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{948 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{21\%} & \cellcolor{gray!6}{0.21} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
-8. Mult = 1 \& Init = 250,500 \& Mods = 20,40,60 (0.21) & 5 & 82 / 82 & 806 / 1200 & 100\% & 32.8\% & 0.328 & 60 & 80 & y & 250 & 1\\
-\cellcolor{gray!6}{9.
-Mult = 10,20 \& Mods = 1,5 \& Resamp = n \& Mods = 1 \& Init = 50,100 (0.078)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{1139 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{5.08\%} & \cellcolor{gray!6}{0.0508} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
-10. Mult = 10,20 \& Mods = 1,5 \& Resamp = y (0.054) & 5 & 82 / 82 & 832 / 1200 & 100\% & 30.7\% & 0.307 & 5 & 80 & y & 250 & 20\\
-\addlinespace
-\cellcolor{gray!6}{11.
-Mult = 1 \& Init = 250,500 \& Mods = 1,5,10 (0.025)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{981 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{18.2\%} & \cellcolor{gray!6}{0.182} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{1}\\
-12. Mult = 1 \& Init = 50,100 (0.0045) & 6 & 82 / 82 & 1151 / 1200 & 100\% & 4.08\% & 0.0408 & 20 & 80 & y & 50 & 1\\
-\bottomrule
-\end{tabular}}
-\end{table}
+\begin{itemize}
+\tightlist
+\item
+  Login from within the institution or activate remote access
+\item
+  go to \url{https://www.embase.com/\#advancedSearch/default}
+\item
+  set your date range
+\item
+  in the mapping field select all apart from ``Limit to terms indexed in
+  article as `major focus'\,''
+\item
+  in ``Sources'' select Embase
+\item
+  select records in blocks of 10K
+\item
+  chose format: Csv - fields by column, output: Full record (may take a
+  while to prepare the download and you can download only one batch at
+  time)
+\item
+  call the files Embase\#.csv with \# being a sequential number
+\end{itemize}
 

### 2022-02-19 R/Reporting.R

@@ -713,7 +713,7 @@ plot_predictive_densities <- function(session_name,
 				}) %>%
 				bind_rows() %>%
 				ggplot(aes(y = Iteration)) +
-				geom_ridgeline(aes(x = Prob, height = Dens, fill = Label, color = Label), alpha = .5, scale = 1) +
+				ggridges::geom_ridgeline(aes(x = Prob, height = Dens, fill = Label, color = Label), alpha = .5, scale = 1) +
 				geom_segment(data = unc_range_df, aes(yend = as.numeric(Iteration) + .1, x = Neg_lim, xend = Neg_lim, color = "Negative")) +
 				geom_segment(data = unc_range_df, aes(yend = as.numeric(Iteration) + .1, x = Pos_lim, xend = Pos_lim, color = "Positive")) +
 				geom_label(data = unc_range_df, aes(y = as.numeric(Iteration) - .1, x = Pos_lim, label = Pos_lim)) +

### 2022-02-22 Manuscript/S1.Protocol.tex
added README and fixed S1 for the github page

@@
 \author{}
-\date{\vspace{-2.5em}2022-02-19}
+\date{\vspace{-2.5em}2022-02-22}
 
@@
 
-Add installation and setup info here.
+To use the framework clone it from
+\url{https://github.com/AD-Papers-Material/BART_SystReviewClassifier}
+and run the R project in the repository.
 
-\hypertarget{acquisition-of-the-citaion-data}{%
-\subsection{Acquisition of the citaion
-data}\label{acquisition-of-the-citaion-data}}
+The first step is loading the code base using:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{source}\NormalTok{(}\StringTok{"R/Setup.R"}\NormalTok{) }\CommentTok{\# Load the framework}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{acquisition-of-the-citation-data}{%
+\subsection{Acquisition of the citation
+data}\label{acquisition-of-the-citation-data}}
 
@@
 \begin{Highlighting}[]
-\FunctionTok{source}\NormalTok{(}\StringTok{"R/Setup.R"}\NormalTok{) }\CommentTok{\# Load the framework}
-
 \CommentTok{\# Initial query to be built on domain knowledge. It accepts OR, AND, NOT boolean}
@@
 \[
-Sensitivity \times Efficiency = \\
+Sensitivity \times Efficiency =
 \frac{Pos.\ found}{Tot.\ pos.} \times \bigg(1 - \frac{Records\ reviewed}{Tot.\ records}\bigg)

### 2022-02-22 README.Rmd
added README and fixed S1 for the github page

---
title: "BART_SystReviewClassifier"
output: github_document
---

```{r readme_setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## Description

This repo is the companion to the paper "An open-source integrated framework for the automation of citation collection and screening in systematic reviews" published as preprint at https://arxiv.org/abs/2202.10033. The following instructions are taken from the Supplemental Material S1.

```{r child = file.path("Manuscript", "S1.Protocol.Rmd")}
```

### 2022-02-22 Manuscript/Manuscript.Rmd
more language check and updated abstract

@@
 abstract: |
-  The exponential and prolific growth of published original scientific contributions makes secondary literature abridgements increasingly demanding.
-  We introduce a new open-source framework for systematic reviews that significantly reduces time and human resource allocation for text identification, collection, and screening of scientific literature.\
+  The exponential growth of scientific production makes secondary literature abridgements increasingly demanding.
+  We introduce a new open-source framework for systematic reviews that significantly reduces time and workload for collecting and screening scientific literature.\
   The framework provides three main tools:
-  1) an automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax,
-  2) a citation screening tool based on Bayesian active machine learning and natural language processing that requires users feedback only on uncertain classifications to iteratively increase predictive accuracy and,
-  3) a semi-automatic, data-driven query generator to create new search queries from existing reviewed citation data sets.\
-  The framework was tested on an example topic to collect and screen citations of related scientific production.
-  To evaluate the performance of the active machine learning classifier,
-  we estimated the median posterior sensitivity and efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of potentially relevant matches among the records not manually reviewed.\
-  A total of 17,755 unique records were collected through the framework citation manager;
-  101 of 766 records were found to be relevant after manual evaluation,
-  while the rest were excluded by automatic classification;
+  1) an automatic citation search engine and manager that collects records from multiple online sources with a unified query syntax,
+  2) a Bayesian, active machine learning, citation screening tool based on iterative human-machine interaction to increase predictive accuracy and,
+  3) a semi-automatic, data-driven query generator to create new search queries from existing citation data sets.\
+  To evaluate the automatic screener's performance, we estimated the median posterior sensitivity and efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of undetected potentially relevant records.\
+  Tested on an example topic, the framework collected 17,755 unique records through the citation manager;
+  766 records required human evaluation while the rest were excluded by the automatic classifier;
   the theoretical efficiency was 95.6% [95.3%, 95.7%] with a sensitivity of 100% [93.5%, 100%].\
@@
   only 567 records required human review after automatic screening, and six additional positive matches were found.
-  Including the additional records, the overall expected sensitivity decreased to 97.3% [73.8%, 100%] while the efficiency increased to 98.6% [98.2%, 98.7%].\
-  For large studies, the framework can significantly reduce the human resources required to conduct systematic reviews
+  The overall expected sensitivity decreased to 97.3% [73.8%, 100%] while the efficiency increased to 98.6% [98.2%, 98.7%].\
+  The framework can significantly reduce the workload required to conduct large literature reviews
   by simplifying citation collection and screening while demonstrating exceptional sensitivity.

### 2022-02-22 Manuscript/Manuscript.tex
more language check and updated abstract

@@
 \begin{abstract}
-The exponential and prolific growth of published original scientific
-contributions makes secondary literature abridgements increasingly
-demanding. We introduce a new open-source framework for systematic
-reviews that significantly reduces time and human resource allocation
-for text identification, collection, and screening of scientific
-literature.\\
+The exponential growth of scientific production makes secondary
+literature abridgements increasingly demanding. We introduce a new
+open-source framework for systematic reviews that significantly reduces
+time and workload for collecting and screening scientific literature.\\
 The framework provides three main tools: 1) an automatic citation search
-engine and manager that allows collecting records from multiple citation
-databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query
-syntax, 2) a citation screening tool based on Bayesian active machine
-learning and natural language processing that requires users feedback
-only on uncertain classifications to iteratively increase predictive
-accuracy and, 3) a semi-automatic, data-driven query generator to create
-new search queries from existing reviewed citation data sets.\\
-The framework was tested on an example topic to collect and screen
-citations of related scientific production. To evaluate the performance
-of the active machine learning classifier, we estimated the median
-posterior sensitivity and efficiency {[}90\% Credible Intervals{]} using
-Bayesian simulation to predict the distribution of potentially relevant
-matches among the records not manually reviewed.\\
-A total of 17,755 unique records were collected through the framework
-citation manager; 101 of 766 records were found to be relevant after
-manual evaluation, while the rest were excluded by automatic
-classification; the theoretical efficiency was 95.6\% {[}95.3\%,
-95.7\%{]} with a sensitivity of 100\% {[}93.5\%, 100\%{]}.\\
+engine and manager that collects records from multiple online sources
+with a unified query syntax, 2) a Bayesian, active machine learning,
+citation screening tool based on iterative human-machine interaction to
+increase predictive accuracy and, 3) a semi-automatic, data-driven query
+generator to create new search queries from existing citation data
+sets.\\
+To evaluate the automatic screener's performance, we estimated the
+median posterior sensitivity and efficiency {[}90\% Credible
+Intervals{]} using Bayesian simulation to predict the distribution of
+undetected potentially relevant records.\\
+Tested on an example topic, the framework collected 17,755 unique
+records through the citation manager; 766 records required human
+evaluation while the rest were excluded by the automatic classifier; the
+theoretical efficiency was 95.6\% {[}95.3\%, 95.7\%{]} with a
+sensitivity of 100\% {[}93.5\%, 100\%{]}.\\
 A new search query was generated from the labelled dataset, and 82,579
@@
 review after automatic screening, and six additional positive matches
-were found. Including the additional records, the overall expected
-sensitivity decreased to 97.3\% {[}73.8\%, 100\%{]} while the efficiency
-increased to 98.6\% {[}98.2\%, 98.7\%{]}.\\
-For large studies, the framework can significantly reduce the human
-resources required to conduct systematic reviews by simplifying citation
-collection and screening while demonstrating exceptional sensitivity.
-Such a tool can improve the standardization and repeatability of
-systematic reviews.
+were found. The overall expected sensitivity decreased to 97.3\%
+{[}73.8\%, 100\%{]} while the efficiency increased to 98.6\% {[}98.2\%,
+98.7\%{]}.\\
+The framework can significantly reduce the workload required to conduct
+large literature reviews by simplifying citation collection and
+screening while demonstrating exceptional sensitivity. Such a tool can
+improve the standardization and repeatability of systematic reviews.
 \end{abstract}
@@
 is especially true for biomedical research, a trend further accelerated
-by the COVID-19 pandemic, thanks to faster article' processing time by
+by the COVID-19 pandemic, thanks to faster article processing time by
 publishers and the greater use of preprint databases (Aviv-Reuven and
@@
 complete (Bannach-Brown et al. 2019; Borah et al. 2017; Allen and Olkin
-1999). A consequence of this is systematic reviews are often already
-out-of-date by the time they are published (E. M. Beller et al. 2013).\\
+1999). A consequence of this is that systematic reviews are often
+already out-of-date by the time they are published (E. M. Beller et al.
+2013).\\
 The field of Data Science applied to evidence synthesis and acquisition
@@
 1).\\
-In this manuscript, we present an open source, production-ready
-framework that further contributes to the state-of-the-art in systematic
-review automation (SRA) and helpers (SRH) tools. We improve the
-``retrieval phase'' by providing a unified framework for the automated
-collection and management of scientific literature from multiple online
-sources. For the citation screening (appraisal) phase, we built an
-active machine learning-based protocol (Settles 2009; Miwa et al. 2014),
-which utilises a Bayesian framework to efficiently identify potentially
-relevant documents that require human review, while automatically
-screening-out the vast majority of clearly non-relevant ones; the
-algorithm then requires human review to iteratively increase
-classification accuracy. Finally, we included a tool to generate new
-search queries based on an already labelled citation data set, to
-identify relevant research that may possibly have been missed by
-manually-made queries.\\
+This manuscript introduces an open-source, production-ready framework
+that further contributes to the state-of-the-art in systematic review
+automation (SRA) and helpers (SRH) tools. We improve the ``retrieval
+phase'' by providing a unified framework for the automated collection
+and management of scientific literature from multiple online sources.
+For the citation screening (appraisal) phase, we built an active machine
+learning-based protocol (Settles 2009; Miwa et al. 2014), which utilises
+a Bayesian framework to efficiently identify potentially relevant
+documents that require human review while automatically screening-out
+the vast majority of clearly non-relevant ones; the algorithm then
+requires human review to increase classification accuracy iteratively.
+Finally, we included a tool to generate new search queries based on an
+already categorised citation data set, to identify relevant research
+that manually-made queries may have possibly missed.\\
 We tested the framework in the retrieval and appraisal phases of an
@@
 of systematic literature review: record acquisition and classification.
-The code used to generate the results in the manuscript is available at
+The code used to generate the results is available at
 \url{https://github.com/AD-Papers-Material/BART_SystReviewClassifier},
@@
 several modules that communicate through intermediate outputs stored in
-standard formats, which make it possible for users to extend the
-framework or easily integrate it with other tools in their pipeline. See
+standard formats, making it possible for users to extend the framework
+or easily integrate it with other tools in their pipeline. See
 Supplemental Material S1 for an in-depth description of the framework
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{methods_diagram} \caption{Figure 1.Framework's visual depiction.}\label{fig:method_diagram}
+\includegraphics[width=1\linewidth]{methods_diagram} \caption{Figure 1. Framework's visual representation.}\label{fig:method_diagram}
 \end{figure}
@@
 of Electrical and Electronics Engineers (IEEE,
-\url{https://ieeexplore.ieee.org/Xplore/home.jsp}). The framework takes
-care of authorization management for non-open databases like WOS and
-IEEE. It is also possible to download and import records in the
-framework manually; this is particularly useful to acquire records from
-the SCOPUS (\url{https://www.scopus.com/}) and EMBASE databases
+\url{https://ieeexplore.ieee.org/Xplore/home.jsp}). The framework
+handles authorisation management for non-open databases like WOS and
+IEEE. It is also possible to import previously downloaded records in the
+framework; this is particularly useful for acquiring records from SCOPUS
+(\url{https://www.scopus.com/}) and EMBASE databases
 (\url{https://www.embase.com/}), for which a comprehensive API interface
 was not easy to build. An extra manual search was also necessary for
-Pubmed, since the API and the web interface have different rule
-expansion algorithms and return slightly different results ({`NCBI
-Insights : Updated Pubmed e-Utilities Coming in April 2022!'}, n.d.). A
-short guide on how to set up the framework for each database supported
-is available in Supplemental Material S3.\\
+Pubmed since the API and the web interface have different rule expansion
+algorithms and return slightly different results ({`NCBI Insights :
+Updated Pubmed e-Utilities Coming in April 2022!'}, n.d.). A short guide
+on how to set up the framework for each database supported is available
+in Supplemental Material S3.\\
 The collected records are merged into a single database, resolving
@@
 (``simple query ordering'').\\
-The researcher is then asked to label a number of records to create the
+The researcher is then asked to label a subset of records to create the
 ``initial training set'' needed to start the automatic classification.
 We recommend manually labelling the first 250 records (see
-``hyperparameter optimization'' later). Simple query ordering increases
+``hyperparameter optimisation'' later). Simple query ordering increases
 the positivity rate in the initial training set (Wallace, Small, et al.
@@
 
-The collected citation data contain a number of fields characterising a
-scientific publication. The framework models the relevance of a record
-based on the following fields: title, abstract, authors, keywords, MESH
+The framework models the relevance of a record based on the following
+fields in the citation data: title, abstract, authors, keywords, MESH
 terms (Lipscomb 2000). A range of Natural Language Processing (NLP)
@@
 bag-of-words approach (Marshall and Wallace 2019). Processing of free
-text fields (title, abstract) includes: tokenization (i.e., extracting
+text fields (title, abstract) includes: tokenisation (i.e., extracting
 the terms), removal of common stopwords (i.e., sentence components
@@
 (Francois Rousseau 2015) with edges occurring between terms with a
-cosine similarity in terms of docuement co-occurrence \textgreater{}
-0.5. We extracted the maximal cliques in the network (Eppstein, Löffler,
-and Strash 2010) representing highly correlated groups of terms; these
+cosine similarity in terms of document co-occurrence \textgreater{} 0.5.
+We extracted the maximal cliques in the network (Eppstein, Löffler, and
+Strash 2010) representing highly correlated groups of terms; these
 groups are added to the dataset as individual features. Only nc-ngrams
@@
 iterations (after 250 burn-in iterations) and 50 trees; we used a \(k\)
-value of 2 to regularize extreme prediction and let the model use
+value of 2 to regularise extreme prediction and let the model use
 missing fields in the DTM as features (Kapelner and Bleich 2015).
@@
 Label assignment is done through identification of an ``uncertainty
-zone'' the construction of which is possible thanks to the Bayesian
+zone'', the construction of which is possible thanks to the Bayesian
 nature of BART, which provides full PPDs instead of point-wise
 predictions for each record.\\
-To describe the process formally, we define
+To describe the process formally, we define:
 
@@
 label, \(L_i = 1\)), averaging the PPDs of the ensemble of \(M=10\)
-models \(m\), and
+models \(m\), and:
 
@@
 interval of \(\pi_i\) (98\% Predictive Interval, 98\% PrI).\\
-Then we identify the ``uncertainty zone'' as
-
-\[U_\pi=[\max\vec{\pi}_{u}^-, \min\vec{\pi}_{l}^+]\] with
-\(\vec{\pi}_{u}^-\) being the vector of \(\pi_{i,u}\) with a negative
-label and \(\vec{\pi}_{l}^+\) the vector of \(\pi_{i,l}\) with a
-positive label. That is, \(U_\pi\) defines a range of values between the
-smallest \(\pi_{i,l}\) in the set of already labelled positive records
-\(L_p\) and the largest \(pi_{i,u}\) related to the negative ones
-\(L_n\), noting that the two limits can appear in any order.\\
-Consequently, a record \(D_i\) will be labelled as positive if
+Then we identify the ``uncertainty zone'' as:
+
+\[U_\pi=[\max\vec{\pi}_{u}^-, \min\vec{\pi}_{l}^+]\]
+
+with \(\vec{\pi}_{u}^-\) being the vector of \(\pi_{i,u}\) with a
+negative label and \(\vec{\pi}_{l}^+\) the vector of \(\pi_{i,l}\) with
+a positive label. That is, \(U_\pi\) defines a range of values between
+the smallest \(\pi_{i,l}\) in the set of already labelled positive
+records \(L_p\) and the largest \(pi_{i,u}\) related to the negative
+ones \(L_n\), noting that the two limits can appear in any order.\\
+Consequently, a record \(D_i\) will be labelled as positive if:
 
@@
 labelled positive, its PPD should be within the range of the mixture of
-PPD of the records previously labelled positive, and should not cross
-the distributions of the negative records.\\
-Conversely, a record is labelled as negative if
+PPD of the records previously labelled positive and should not cross the
+distributions of the negative records.\\
+Conversely, a record is labelled as negative if:
 
@@
 
-With the BART model, it is possible to extract the proportion of times a
-term is used in a posterior tree over the sum of total inclusions of all
-variables (Kapelner and Bleich 2013), as a measure of importance of the
-features in the model. We extracted the terms, the portion of the
-citation data in which they were used, the average ``inclusion rate''
-among the ensemble models (over 10,000 inclusions) and its ratio over
-the standard deviation of this inclusion (inclusion stability, IS). For
-each term we ran a Poisson regression to get the linear association with
-a positive label and reported it as Relative Risk (RR) with the number
-of standard errors as significance index (Statistic); the comparison
-between the inclusion rate in the BART models and the linear association
-allows to spot relevant non-linear effects (i.e, the feature is relevant
-only in association with others). In the Results, we only listed the
-first 15 terms with IS \textgreater{} 1.5, (in order of inclusion rate),
-while the first fifty terms regardless of inclusion stability are listed
-in Supplemental Material S2.
+As a measure of feature importance, we computed the ``inclusion rate'',
+that is, the proportion of times a term is used in a posterior tree over
+the sum of total inclusions of all variables (Kapelner and Bleich 2013).
+We extracted the terms, the portion of the citation data in which they
+were used, the average ``inclusion rate'' among the ensemble models
+(over 10,000 inclusions) and its ratio over the standard deviation of
+this inclusion (inclusion stability, IS). For each term, we ran a
+Poisson regression to get the linear association with a positive label
+and reported it as Relative Risk (RR) with the number of standard errors
+as significance index (Statistic); the comparison between the inclusion
+rate in the BART models and the linear association allows to spot
+relevant non-linear effects (i.e., the feature is relevant only in
+association with others). In the Results, we only listed the first 15
+terms with IS \textgreater{} 1.5 (in order of inclusion rate), while the
+first fifty terms, regardless of inclusion stability, are listed in
+Supplemental Material S2.
 
@@
 results).\\
-The algorithm encompasses a number of steps:
+The algorithm is composed of the following steps:
 
@@
   The researcher is then asked to review the rule groups and select one
-  or more rules from each group (useful if they convey different
-  meaning), or edit them if overly too specific positive or negative
-  conditions were included. It is possible to exclude a group of rules
-  altogether, especially those with the poorest sensitivity/specificity
-  ratio.
+  or more rules from each group or edit overly specific rules (e.g.,
+  citing a non-relevant concept casually associated with a paper, like a
+  numeric value or indicator). It is possible to exclude a group of
+  rules altogether, especially those with the poorest
+  sensitivity/specificity ratio.
 \item
@@
 \item
-  Finally, the rules are re-elaborated in a query that can be used in
-  the major scientific databases.
+  Finally, the rules are re-elaborated in a query that can be used to
+  perform a new citation search.
 \end{itemize}
@@
 Because the algorithm is data-driven, it creates queries that
-effectively select positive records from the input dataset, but may be
+effectively select positive records from the input dataset but may be
 not specific enough when applied to actual research databases. Therefore
-we added an extra subquery in \emph{AND}, that specifies the general
-topics of our search and narrows the search domain.\\
+we added an extra subquery in \_AND\_that specifies the general topics
+of our search and narrows the search domain.\\
 The new query was used to initiate a second search session.
@@
 We trained a simple Bayesian logistic regression (surrogate model) on
-the reviewed records to evaluate the consistency of classification model
-(see Discussion for the theoretical justification). The surrogate model
-uses as predictor the lower boundary of the 98\% PrI of the PPD of the
-records with weakly regularizing, robust priors for the intercept
+the reviewed records to evaluate the consistency of the classification
+model (see Discussion for the theoretical justification). The surrogate
+model uses as predictor the lower boundary of the 98\% PrI of the PPD of
+the records with weakly regularising, robust priors for the intercept
 (Student T with \(\nu=3,\mu=0,\sigma=2.5\)) and the linear coefficient
@@
 Given that this model is conditional only on the BART predictions and
-not on the DTM, it is characterized by more uncertainty, providing
+not on the DTM, it is characterised by more uncertainty, providing
 plausible worst-case scenarios.\\
@@
 distribution of the number of total positive records in the whole
-dataset. This distribution allows to estimate the expected total
+dataset. This distribution allows estimating the expected total
 posterior ``Sensitivity'' and ``Efficiency'' of the classification model
-in the full (unreviewed) dataset. Efficiency is summarised by the ``Work
-saved over random'' (WSoR) statistic: one minus the ratio between the
-number of record manually reviewed and those that would be required to
-find the same number of positives if classification were performed
+in the whole (unreviewed) dataset. Efficiency is summarised by the
+``Work saved over random'' (WSoR) statistic: one minus the ratio between
+the number of records manually reviewed and those that would be required
+to find the same number of positives if classification were performed
 choosing records randomly; this last quantity is estimated through a
@@
 
-Our classification algorithm has a number of hyperparameters:
+Our classification algorithm has a limited number of hyperparameters:
 
@@
 the first session dataset. Each hyperparameter combination was tested
-until four CR iterations were completed with no positive records or the
-whole dataset was labelled.\\
+until four CR iterations were completed with no positive records or
+until the whole dataset was labelled.\\
 For each combination, a performance score was computed as the product of
@@
 values. For the rest of the study, we used the best hyperparameter set
-in terms of Sensitivity followed by Efficiency from the cluster with the
+in terms of sensitivity followed by efficiency from the cluster with the
 highest average score.\\
@@
 being the databases with the higher uniqueness ratios. The final data
-set was composed from 17,755 unique records.\\
-The first 250 records (based on ``simple query ordering'') were labeled
-manually. Of these 43 (17.2\%) were labeled as positive, and 207
-(82.8\%) as negative.
+set was composed of 17,755 unique records.\\
+The first 250 records (based on ``simple query ordering'') were
+categorised manually. Of these 43 (17.2\%) were labeled as positive, and
+207 (82.8\%) as negative.
 
@@
 Distribution of retrieved records by source and session.
-For each source it is reported the number of records, percentage over the session total (after removing duplicates), and number or records specific for a source as absolute value and as percentage over the source total.
+For each source, we reported the number of records, percentage over the session total (after removing duplicates), and the number of records specific for a source as absolute value and as percentage over the source total.
 All session shows records after joining and deduplication of the Session 1 and Session 2 data set.}
@@
 
-The labeled records were used to train the Bayesian classification model
-used to label the remaining records. After seven classification and
-review (CR) iterations (three resulting in new positive matches and four
-extra replications to account for stochastic variability), a total of
-101 positives matches were found, requiring manual review of 766 records
-(13.2\% positivity rate).\\
+The categorised records were used to train the Bayesian classification
+model used to label the remaining records. After seven classification
+and review (CR) iterations (three resulting in new positive matches and
+four extra replications to account for stochastic variability), a total
+of 101 positives matches were found, requiring manual review of 766
+records (13.2\% positivity rate).\\
 It is noticeable how the number of records that required manual review
@@
 engine was converging while the uncertainties were resolved.\\
-This phenomenon is better illustrated in Fig. 1 of the Supplemental
-Material S2. It shows the mixture distribution of the PPDs of the
-records, specifically for records that were manually reviewed, before
-and after the classification step: it can be seen how the distribution
-of uncertain records shrinks (i.e., it becomes concentrated in a shorter
+This phenomenon is better illustrated in Fig. 1 of Supplemental Material
+S2. It shows the mixture distribution of the PPDs of the records,
+specifically for records that were manually reviewed, before and after
+the classification step: it can be seen how the distribution of
+uncertain records shrinks (i.e., it becomes concentrated in a shorter
 probability range) and shifts toward the negative zone as more positive
@@
 Results of the automatic classification and manual review rounds.
-For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown.
+The cumulative numbers of positives and negative records and their sum (Total labelled) and percentage over total are shown for each iteration.
 Also, the number of changes after review and their description is reported."Unlab." indicates unlabelled records marked for review.
-For each Iteration, the number of features used by the engine is also reported.
+For each iteration, the number of features used by the engine is also reported.
 The first row reports the results of the initial manual labelling of records, which served as input for the automatic classification in Iteration 1.
@@
 
-We extracted the 15 term more relevant for the classification model,
+We extracted the 15 more relevant terms for the classification model,
 described as: Term (citation part): Inclusion Rate (Inclusion Stability)
@@
 topic of pathogen spreading over hospital networks. Some terms were
-considered highly relevant by the BART models (e.g., ``Worker'' in 6th
-position out of more than 3800 terms considered) although in a simpler
-linear model their effect would hardly be significant (statistic: -1.21
-s.e.); these are terms that are only relevant in conjunction with other
-terms but not by their own, highlighting the extra predictive power
-achievd through the use of advanced, non-linear machine learning.\\
-A more extensive set of terms is presented in Table 1 of the
-Supplemental Material S2.
+considered highly relevant by the BART models (e.g., ``Worker'' in the
+sixth position out of more than 3800 terms considered), although in a
+simple linear model, their effect would hardly be significant
+(statistic: -1.21 s.e.); these are terms that are only relevant in
+conjunction with other terms but not on their own, highlighting the
+extra predictive power achieved through the use of advanced, non-linear
+machine learning.\\
+A more extensive set of terms is presented in Table 1 of Supplemental
+Material S2.
 
@@
 The results of the first classification session were used to create a
-second, data-driven query with the objective of performing a more
-extensive search to find records that may have been missed during the
-first search session. The resulting query was as follows:\\
+second, data-driven query to perform a more extensive search to find
+records that may have been missed during the first search session. The
+resulting query was as follows:\\
 
@@
 The final piece \emph{AND ((antimicrobial resistance) OR (healthcare
-infection)} was added manually to better define the search domain, since
+infection)} was added manually to define the search domain better since
 the algorithm was trained on documents that were all more or less
@@
 searches, which equates to 2\% of the total. The percentage of records
-shared by two or more source dropped to 22\%.
+shared by two or more sources dropped to 22\%.
 
@@
 substantial number of records (1,273); however, just labelling 275 of
-them (the suggested 250 plus 25 alredy labelled for the framework
+them (the suggested 250 plus 25 already labelled for the framework
 hyperparameter tuning) was sufficient to reduce this number to just 190
@@
 positive in the initial training set generated during Session 1. This
-behaviour can be useful to spot classification errors and
-inconsistencies. Considering both sessions, 1,333 records were manually
-reviewed and 107 (8.03\%) confirmed positive matches were found.
+behaviour can rev spot classification errors and inconsistencies.
+Considering both sessions, 1,333 records were manually reviewed and 107
+(8.03\%) confirmed positive matches were found.
 
 Again, the evaluation of the inclusion rate of the terms showed that the
-engine is quite capable of internalizing the concepts behind the
+engine is quite capable of internalising the concepts behind the
 research topic. A subsample of the relevant terms used by the model in
@@
 1,200 manually labelled records. The analysis suggested that the
-following parameter combination performed best: an initial input of 250
-labelled records with 10x oversampling of positive matches, an averaged
-ensemble of 10 models, no bootstrapping and an uncertainty zone defined
-by the 98\% predictive interval. This combination of parameters was
-associated with a sensitivity of 98.8\% (81 / 82 positive matches found)
-and an efficiency of 61.5\% (462 / 1200 records evaluated). The detailed
-results of the hyperparameter tuning analysis are reported in Table 3 of
-Supplemental Material S2. Fig. 2 in Supplemental Material S2
+following parameter combination performed best: an initial training set
+of 250 categorised records with 10x oversampling of positive matches,
+ten models in the ensemble, no bootstrapping and an uncertainty zone
+defined by the 98\% predictive interval. This combination of parameters
+was associated with a sensitivity of 98.8\% (81 / 82 positive matches
+found) and an efficiency of 61.5\% (462 / 1200 records evaluated). The
+detailed results of the hyperparameter tuning analysis are reported in
+Table 3 of Supplemental Material S2. Fig. 2 in Supplemental Material S2
 demonstrates that the positive record oversampling rate, the number of
 ensemble models and the size of the initial training set were the
-parameters that mostly impacted performance.
+parameters that mainly impacted performance.
 
@@
 ordering query: the median of surrogate models' cumulative predictive
-distributions matches quite well the actual number of positive records
-found. It is striking how many more records would have required manual
-evaluation to find the same number of positive matches without using a
-smart classification tool, with some positive matches found close to the
+distributions matches the actual number of positive records found quite
+well. It is striking how many more records would have required manual
+evaluation to find the same number of positive matches without a
+classification algorithm, with some positive matches found close to the
 end of the heuristically ordered list of records.\\
@@
 a drop in expected sensitivity, especially in the lower credibility
-boundary (97.3\% {[}72.8\%, 100\%{]}), due to the fact that as the
-number of records increases, even a small probability of being a
-positive match can, in the worst case scenario, lead to a relevant
-number of missed positive matches (147 in this case). To ensure that no
-obvious positive matches were missed, we evaluated 100 additional
-records among those not reviewed with the highest median predicted
-probability produced by the engine and found no additional positive
-matches.\\
+boundary (97.3\% {[}72.8\%, 100\%{]}): as the number of records
+increases, even a small probability of being a positive match can, in
+the worst-case scenario, lead to a relevant number of predicted positive
+matches (147 in this case). To ensure no obvious positive matches were
+missed, we evaluated 100 non-reviewed records with the highest median
+predicted probability and found no additional positive matches.\\
 
@@
 The table reports for each session, the number of reviewed records and the percentage over the total.
-Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90\% PrI truncated to the observed realization in the dataset [trunc.
+Also, the posterior expected number of positive records, sensitivity and efficiency (as WSoR) are reported, with their 90\% PrI truncated to the observed realisation in the dataset [trunc.
 PrI] (see.
 methods).
-Finally the median Bayesian $R^2$ [90\% CrI] of the logistic models is reported.
+Finally, the logistic model's median Bayesian $R^2$ [90\% CrI] is reported.
 PrI: Predictive Intervals; CrI: Credibility Intervals.}
@@
 matches (red dots) sorted by simple query ordering. The {[}trunc. 90\%
-PrI{]} of the cumulative positive matches estimated by the logistic
-Bayesian model is shown as a shaded area delimited by the 95\% quantile
+PrI{]} of the cumulative positive matches estimated by the Bayesian
+logistic model is shown as a shaded area delimited by the 95\% quantile
 of the PrI and by the observed number of positive matches (light blue
-lines). The median of the PrI is represented by a darker blue line.}
+lines). A darker blue line represents the median of the PrI.}
 \end{figure}
@@
 We propose a new integrated framework to help researchers collect and
-screen scientific publications that is characterised by high performance
-and versatility. This framework joins the joining the growing field of
+screen scientific publications characterised by high performance and
+versatility. This framework joins the joining the growing field of
 systematic review automation (SRA) and helpers (SRH) tools (A. M. Cohen
@@
 framework implements standard approaches and uses ad-hoc solutions to
-deal with common SRA issues. By freely sharing the tool as an
-open-source R package and by following a modular design, we sought to
-adopt some of the so-called Vienna Principles advocated by the
-International Collaboration for the Automation of Systematic Reviews
-(ICASR) (E. Beller et al. 2018).\\
+common SRA issues. By freely sharing the tool as an open-source R
+package and by following a modular design, we sought to adopt some of
+the so-called Vienna Principles advocated by the International
+Collaboration for the Automation of Systematic Reviews (ICASR) (E.
+Beller et al. 2018).\\
 The framework consists of four main components: 1) an integrated
@@
 
-The search engine module used by the framework is able to automatically
-collect citation data from three well-known scientific databases (i.e.,
-Pubmed, Web of Science, and the database of the Institute of Electrical
-and Electronics Engineers) asand to process manually downloaded results
-from both the two more databases (SCOPUS, EMBASE). In comparison, most
-commercial or free SRH tools, rely on internal databases (e.g., Mendeley
-\url{https://www.mendeley.com/}) sometimes focusing only on a particular
-topic (Visser 2010) or on a single external data source (Thomas and
-Brunton 2007; Poulter et al. 2008; Soto, Przybyła, and Ananiadou
-2019).\\
-Mixing different databases is essential to obstain a more comprehensive
+The search engine module used by the framework can automatically collect
+citation data from three well-known scientific databases (i.e., Pubmed,
+Web of Science, and the Institute of Electrical and Electronics
+Engineers) and process manually downloaded results from two more sources
+(SCOPUS, EMBASE). In comparison, most commercial or free SRH tools rely
+on internal databases (e.g., Mendeley \url{https://www.mendeley.com/})
+sometimes focusing only on a particular topic (Visser 2010) or a single
+external data source (Thomas and Brunton 2007; Poulter et al. 2008;
+Soto, Przybyła, and Ananiadou 2019).\\
+Mixing different databases is essential to obtain a more comprehensive
 view of the literature (Bajpai et al. 2011; Wilkins, Gillies, and Davies
@@
 the limitations of citation databases in terms of traffic and download
-quotas. The results are then automatically organized, deduplicated and
+quotas. The results are then automatically organised, deduplicated and
 arranged by ``simple query ordering'' in a uniform corpus. The
-preliminary ordering allows to increase the positivity rate in the
-initial training set (Wallace, Small, et al. 2010).\\
-
-For the framework's record classification module, we developed an active
-machine learning approach (Settles 2009; Miwa et al. 2014) which is
-based on the best practices from other SRA studies but also brings
-further improvements at various levels.\\
+preliminary ordering increases the positivity rate in the initial
+training set (Wallace, Small, et al. 2010).\\
+
+For the framework's record screening module, we developed an active
+machine learning protocol (Settles 2009; Miwa et al. 2014) based on the
+best practices from other SRA studies, bringing further improvements at
+various levels.\\
 The feature extractor module uses modern NLP techniques (Ananiadou and
-McNaught 2006; K. B. Cohen and Hunter 2008) to transform text into input
-data for machine learning. We did not include classical n-grams
-(Schonlau and Guenther 2017); rather we used network analysis to find
+McNaught 2006; K. B. Cohen and Hunter 2008) to transform free text into
+input data for machine learning. We did not include classical n-grams
+(Schonlau and Guenther 2017); rather, we used network analysis to find
 non-consecutive, frequently associated terms, a generalisation of
 n-grams that relaxes the term adjacency assumption. This approach can
-also be used to find term connections across parts of the records, e.g.,
-whether a term has a different relevance when associated with a
-particular author. The same technique, albeit with different parameters,
-was used to merge redundant terms to make the model estimation more
-efficient and reduce noise.\\
-The use of concurrency network-driven modelling of text is not new
+also incorporate term connections across different parts of the records,
+e.g., terms having a different relevance when associated with a
+particular author. The same technique was used with different parameters
+to merge redundant terms, increasing estimation efficiency and reducing
+noise.\\
+The use of concurrency network-driven text modelling is not new
 (Francois Rousseau 2015; Violos et al. 2016; François Rousseau, Kiagias,
@@
 benefits: lower sensitivity to the choice of hyperparameters, natural
-regularisation through priors, and, most imporantly, predictive
+regularisation through priors, and, most importantly, predictive
 distributions as output instead of point-wise predictions (Soria-Olivas
@@
 relatively tight prior distributions, we discouraged overly deep trees,
-long tree sequences, and extreme predicted probabilities, this reducing
+long tree sequences, and extreme predicted probabilities, thus reducing
 the risk of overfitting.\\
@@
 been shown to improve out-of-sample predictive performance (Zhou 2021;
-Dietterich 2000), as we were able to confirm during the hyperparameter
-evaluation (Supplemental Material S2). Ensembling reduces the
-uncertainty in the predictive distribution tails related to the
-randomness in the MCMC fit (Robert and Casella 2004), generating a shift
-in the probability mass towards the distribution centre and stabilising
-it (i.e., reducing variance without impacting bias). On the other hand,
-simply imposing more robust uninformative priors against extreme
-predictions would have reduced variance but also shifted the
-distribution towards a non-decision zone, increasing bias (Hansen et al.
-2000).\\
+Dietterich 2000), as confirmed during the hyperparameter evaluation
+(Supplemental Material S2). Ensembling reduces the uncertainty in the
+predictive distribution tails related to the randomness in the MCMC fit
+(Robert and Casella 2004), generating a shift in the probability mass
+towards the distribution centre and stabilising it (i.e., reducing
+variance without impacting bias). On the other hand, simply imposing
+more robust uninformative priors against extreme predictions would have
+reduced variance but also shifted the distribution towards a
+non-decision zone, increasing bias (Hansen et al. 2000).\\
 Since the number of model replications has a significant impact on
@@
 
-A low rate of relevant matches (class imbalance) is typical for
+A low proportion of relevant matches (class imbalance) is typical for
 literature reviews (Sampson, Tetzlaff, and Urquhart 2011; Wallace,
@@
 hyperparameter analysis showed that the oversampling rate, together with
-model ensembling, was the parameter with the greatest impact on
+model ensembling, was the parameter with the most significant impact on
 performance.\\
@@
 et al. 2015), but the BART implementation we used did not have this
-feature; furthermore, using simple oversampling allows for broader
+feature; furthermore, using simple oversampling allows for a broader
 compatibility with different modelling engines (Galar et al. 2011;
@@
 One of the key innovations we have introduced is the concept of
-``uncertainty zone'', thie implementation of which is possible thanks to
+``uncertainty zone'', the implementation of which is possible thanks to
 the Bayesian foundation of the classification model.\\
-This construct guides the selection of records to be manually review and
-gets dynamically updated and reduced after each CR iteration, as more
-uncertain predictions are evaluated (Supplemental Material S2 Fig. 1).\\
-This approach overcomes the usual requirement of dataset-specific hard
-thresholds in active machine learning, and also allows to review
-multiple items at once between iterations (Laws and Schütze 2008; Miwa
-et al. 2014; Zhu et al. 2010). The parameters required by our algorithm
-are general and non task-specific, like the PPD intervals based on which
-the uncertainty zone is built, and the maximum number of iterations
-without positive matches after which a session is concluded; evaluation
-of the hyperparameters shows that the algorithm is robust against
-variations in these parameters and we expect the default values to
-perform well on most datasets.\\
-Since researchers are asked to review both records with a positive
-predicted label and those inside the uncertainty zone, this method can
-be considered as a unifying synthesis of the ``certainty'' and
+This construct guides the selection of records to be manually reviewed
+and gets dynamically updated and reduced after each CR iteration, as
+more uncertain predictions are evaluated (Supplemental Material S2 Fig.
+1).\\
+The use of a dynamic uncertainty zone overcomes the usual requirement of
+dataset-specific hard thresholds in active machine learning and allows
+to review multiple items at once between iterations (Laws and Schütze
+2008; Miwa et al. 2014; Zhu et al. 2010). The hyperparameters required
+by our algorithm are general and non-task-specific, like the PPD
+intervals underlying the uncertainty zone and the maximum number of
+iterations without positive matches after which a session is concluded;
+the evaluation of the classification model hyperparameters shows that
+the algorithm is robust against variations in these parameters, and we
+expect the default values to perform well on most datasets.\\
+Since researchers are asked to review both records predicted as surely
+relevant and those inside the uncertainty zone, this method can be
+considered as a unifying synthesis of the ``certainty'' and
 ``uncertainty'' paradigms of active learning (Miwa et al. 2014).\\
@@
 regression (surrogate model) to the manually reviewed data to abstract
-the classification model predictions and achieve a maximum entropy
+the classification model predictions and generate a maximum entropy
 (Harremoës and Topsøe 2001) estimate of the number of missed positive
@@
 
-By screening only a very small fraction of all records, our framework
-achieves very high sensitivity, bringing a meaningful reduction in
+Our framework achieves very high sensitivity by screening only a very
+small fraction of all records, bringing a meaningful reduction in
 workload.\\
@@
 second session as only a few new positive matches were found; however,
-given the large number of records, uncertainty about sensitivity also
+given the large number of records, uncertainty about sensitivity
 increased, as expected.\\
@@
 Although ``simple query ordering'' concentrated most relevant matches in
-the first 20-25 thousand records, without the tool support the remaining
-relevant records would have been missed withouth manually screeening
-almost the entire dataset.\\
+the first 20-25 thousand records, without the tool support, the
+remaining relevant records would have been missed without manually
+screening almost the entire dataset.\\
 
@@
 query to help find records missed in the first search session. The
-generated query did indeed to retrieve a few more relevant records that
-were not found in session 1, but at the cost of a significant increase
-in the number of documents.\\
+generated query did indeed retrieve a few more relevant records not
+found in session 1 but at the cost of significantly increasing the
+number of documents.\\
 An interesting aspect of this feature is that it provides a
@@
 particular topic. Therefore, the new query may not be specific enough
-when applied to an unbounded search domain, and may return an
-unmanageable amount of unrelated results. The solution we found was to
+when applied to an unbounded search domain and may return an
+unmanageable amount of irrelevant results. The solution we found was to
 add another component to the query, specifying the general topic
@@
 As mentioned early, our framework builds on modularity. We have designed
-it in such a way that full independence of the main modules can be
-easily implemented in future iterations; it will be possible for users
-to add custom features such as citation search and parsing for other
-scientific databases, alternative text processing algorithms or machine
-learning modules. We consider such interoperability to be extremely
-relevant: the main strength of our tool lies in the composition of many
-solutions such as the idea of Bayesian active machine learning and the
-exploit of the derived uncertainty in defining the records needing human
-review.\\
-However, each components could benefit considerably from the recent
-improvements in text mining and machine learning.\\
-For example, our text processing approach, based on the ``boolean
-bag-of-words'' paradigm, is quite simple, and indeed could be improved
-by more nuanced text representations. It might be considered whether
-feature transformations such as TF-IDF (Baeza-Yates, Ribeiro-Neto, et
-al. 1999; Ananiadou and McNaught 2006) could be advantageous, although
-we hypothesise that tree-based classification algorithms like BART are
+so that each module can become fully independent in future iterations;
+it will be possible for users to add custom features such as citation
+search and parsing for other scientific databases, alternative text
+processing algorithms or machine learning modules. We consider such
+interoperability to be extremely relevant: the main strength of our tool
+lies in the composition of many independent solutions, such as the idea
+of Bayesian active machine learning and the exploit of the derived
+uncertainty in defining the records needing human review.\\
+Each component could benefit considerably from the recent improvements
+in text mining and machine learning.\\
+For example, the text processing approach based on the ``boolean
+bag-of-words'' paradigm is quite simple and could be improved by more
+nuanced text representations. It might be considered whether feature
+transformations such as TF-IDF (Baeza-Yates, Ribeiro-Neto, et al. 1999;
+Ananiadou and McNaught 2006) could be advantageous, although we
+hypothesise that tree-based classification algorithms like BART are
 robust enough not to require such operations. Instead, it might be worth
@@
 Minaee et al. 2021) and could be used to reduce noise by merging
-different terms that are semantically similar and enhance signal by
+different terms that are semantically similar or enhance signal by
 distinguishing identical terms with different meaning given the context.
 Another option would be to employ unsupervised learning models like
-Latent Dirichlet Analysis, Latent Semantic Analysis (Pavlinek and
+Latent Dirichlet Analysis and Latent Semantic Analysis, (Pavlinek and
 Podgorelec 2017; Q. Chen, Yao, and Yang 2016; Landauer, Foltz, and Laham
 1998) or graph-of-word techniques (Ohsawa, Benson, and Yachida 1998;
-Francois Rousseau 2015) to extract topics to expand the feature space.\\
+Francois Rousseau 2015) to extract topics that expand the feature
+space.\\
 Our classification algorithm is applicable with any Bayesian supervised
 machine learning method that provides full PPDs; therefore, alternative
-classification models, such as Gaussian Processes which are known for
-their flexibility (Jayashree and Srijith 2020; S.-H. Chen et al. 2015),
-could be evaluated. It would be even more interesting to test advanced
+classification models, such as Gaussian Processes, known for their
+flexibility (Jayashree and Srijith 2020; S.-H. Chen et al. 2015), could
+be evaluated. It would be even more interesting to test advanced
 learning algorithms that go beyond the bag-of-words approach and take
@@
 accelerating pace of scientific production. We believe it is encouraging
-that a wide variety of tools are being made available to allow
-researchers and policymakers find the approach that best fits their
-needs.\\
-We are contributing to this field with an innovative framework that
-provides excellent performance and easy integration with existing
-systematic review pipelines. The value of this work lies not only in the
-framework itself, which we make available as open-source software, but
-also in the set of methodologies we developed to solve various SRA
-issues and which can also be used to improve already existing
-solutions.\\
+that a wide variety of tools are being made available to let researchers
+and policymakers find the approach that best fits their needs.\\
+We contribute to this field with an innovative framework that provides
+excellent performance and easy integration with existing systematic
+review pipelines. The value of this work lies not only in the framework
+itself, which we make available as open-source software, but also in the
+set of methodologies we developed to solve various SRA issues and which
+can also be used to improve existing solutions.\\
 

### 2022-02-22 Manuscript/Manuscript_Discussion.Rmd
more language check and updated abstract

@@
 
-We propose a new integrated framework to help researchers collect and screen scientific publications that is characterised by high performance and versatility.
+We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility.
 This framework joins the joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
-This framework implements standard approaches and uses ad-hoc solutions to deal with common SRA issues.
+This framework implements standard approaches and uses ad-hoc solutions to common SRA issues.
 By freely sharing the tool as an open-source R package and by following a modular design, we sought to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
@@
 
-The search engine module used by the framework is able to  automatically collect citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) asand to process manually downloaded results from both the two more databases (SCOPUS, EMBASE).
-In comparison, most commercial or free SRH tools, rely on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing only on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
-Mixing different databases is essential to obstain a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
+The search engine module used by the framework can automatically collect citation data from three well-known scientific databases (i.e., Pubmed, Web of Science, and the Institute of Electrical and Electronics Engineers) and process manually downloaded results from two more sources (SCOPUS, EMBASE).
+In comparison, most commercial or free SRH tools rely on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing only on a particular topic [@visser2010performing] or a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
+Mixing different databases is essential to obtain a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
 in our results, 18.7% of the positive matches were found in only one of the different data sources, and no positive record was present in all the sources (data not shown).\
 The framework online search algorithms are efficient enough to manage tens of thousands of search results, using various solutions to overcome the limitations of citation databases in terms of traffic and download quotas.
-The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
-The preliminary ordering allows to increase the positivity rate in the initial training set [@wallace2010active].\
+The results are then automatically organised, deduplicated and arranged by "simple query ordering" in a uniform corpus.
+The preliminary ordering increases the positivity rate in the initial training set [@wallace2010active].\
 
-For the framework's record classification module, we developed an active machine learning approach [@settles2009active; @miwa2014reducing] which is based on the best practices from other SRA studies but also brings further improvements at various levels.\
-The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
+For the framework's record screening module, we developed an active machine learning protocol [@settles2009active; @miwa2014reducing] based on the best practices from other SRA studies, bringing further improvements at various levels.\
+The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform free text into input data for machine learning.
 We did not include classical n-grams [@schonlau2017text];
-rather we used network analysis to find non-consecutive, frequently associated terms, a generalisation of n-grams that relaxes the term adjacency assumption.
-This approach can also be used to find term connections across parts of the records, e.g., whether a term has a different relevance when associated with a particular author.
-The same technique, albeit with different parameters, was used to merge redundant terms to make the model estimation more efficient and reduce noise.\
-The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information that is not evident in one-word or consecutive n-gram models.\
+rather, we used network analysis to find non-consecutive, frequently associated terms, a generalisation of n-grams that relaxes the term adjacency assumption.
+This approach can also incorporate term connections across different parts of the records, e.g., terms having a different relevance when associated with a particular author.
+The same technique was used with different parameters to merge redundant terms, increasing estimation efficiency and reducing noise.\
+The use of concurrency network-driven text modelling is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information that is not evident in one-word or consecutive n-gram models.\
 
@@
 However, the Bayesian foundation of the method provides further benefits:
-lower sensitivity to the choice of hyperparameters, natural regularisation through priors, and, most imporantly, predictive distributions as output instead of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
-By selecting relatively tight prior distributions, we discouraged overly deep trees, long tree sequences, and extreme predicted probabilities, this reducing the risk of overfitting.\
+lower sensitivity to the choice of hyperparameters, natural regularisation through priors, and, most importantly, predictive distributions as output instead of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
+By selecting relatively tight prior distributions, we discouraged overly deep trees, long tree sequences, and extreme predicted probabilities, thus reducing the risk of overfitting.\
 The algorithm runs multiple replications of the model and averages their predictive distributions creating an "ensemble";
-this technique has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble], as we were able to confirm during the hyperparameter evaluation (Supplemental Material S2).
+this technique has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble], as confirmed during the hyperparameter evaluation (Supplemental Material S2).
 Ensembling reduces the uncertainty in the predictive distribution tails related to the randomness in the MCMC fit [@robert2004monte], generating a shift in the probability mass towards the distribution centre and stabilising it (i.e., reducing variance without impacting bias).
@@
 
-A low rate of relevant matches (class imbalance) is typical for literature reviews [@sampson2011precision; @wallace2010semi; @o2015using], and a strong imbalance between positive and negative records can affect sensitivity [@khoshgoftaar2010comparing; @chawla2004special].\
+A low proportion of relevant matches (class imbalance) is typical for literature reviews [@sampson2011precision; @wallace2010semi; @o2015using], and a strong imbalance between positive and negative records can affect sensitivity [@khoshgoftaar2010comparing; @chawla2004special].\
 To overcome this problem, we oversampled [@batista2004study] the positive records ten times before model fitting.
-The hyperparameter analysis showed that the oversampling rate, together with model ensembling, was the parameter with the greatest impact on performance.\
+The hyperparameter analysis showed that the oversampling rate, together with model ensembling, was the parameter with the most significant impact on performance.\
 A known risk with positive oversampling is the misclassification of negative records [@ramezankhani2016impact].
@@
 An alternative to oversampling would be to apply different weights and/or costs to the classes [@abd2013review; @diez2015diversity], but the BART implementation we used did not have this feature;
-furthermore, using simple oversampling allows for broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
+furthermore, using simple oversampling allows for a broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
 Finally, sorting the records by query term frequency (simple query ordering) produces a much higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), which boosts the sensitivity of the model.\
 
-One of the key innovations we have introduced is the concept of "uncertainty zone", thie implementation of which is possible thanks to the Bayesian foundation of the classification model.\
-This construct guides the selection of records to be manually review and gets dynamically updated and reduced after each CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig.
+One of the key innovations we have introduced is the concept of "uncertainty zone", the implementation of which is possible thanks to the Bayesian foundation of the classification model.\
+This construct guides the selection of records to be manually reviewed and gets dynamically updated and reduced after each CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig.
 1).\
-This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
-The parameters required by our algorithm are general and non task-specific, like the PPD intervals based on which the uncertainty zone is built, and the maximum number of iterations without positive matches after which a session is concluded;
-evaluation of the hyperparameters shows that the algorithm is robust against variations in these parameters and we expect the default values to perform well on most datasets.\
-Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\
+The use of a dynamic uncertainty zone overcomes the usual requirement of dataset-specific hard thresholds in active machine learning and allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
+The hyperparameters required by our algorithm are general and non-task-specific, like the PPD intervals underlying the uncertainty zone and the maximum number of iterations without positive matches after which a session is concluded;
+the evaluation of the classification model hyperparameters shows that the algorithm is robust against variations in these parameters, and we expect the default values to perform well on most datasets.\
+Since researchers are asked to review both records predicted as surely relevant and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\
 
@@
 Moreover, a literature corpus is unique per search query/database combination, and therefore any out-of-sample performance estimate is not replicable since no new data can be acquired related to the current corpus.\
-To estimate overall sensitivity, we instead applied simple Bayesian regression (surrogate model) to the manually reviewed data to abstract the classification model predictions and achieve a maximum entropy [@harremoes2001maximum] estimate of the number of missed positive matches among the unreviewed records in the whole dataset.
+To estimate overall sensitivity, we instead applied simple Bayesian regression (surrogate model) to the manually reviewed data to abstract the classification model predictions and generate a maximum entropy [@harremoes2001maximum] estimate of the number of missed positive matches among the unreviewed records in the whole dataset.
 This simple surrogate model fitted the data very well ($R^2$ consistently above 97%) using only the lower 98% PrI boundary of the PPDs as predictor, indicating predictive consistency in the classification model.
@@
 
-By screening only a very small fraction of all records, our framework achieves very high sensitivity, bringing a meaningful reduction in workload.\
+Our framework achieves very high sensitivity by screening only a very small fraction of all records, bringing a meaningful reduction in workload.\
 Based on the surrogate model, we predicted a predicted median sensitivity of 100% [93.5%, 100%] in the first session (screening 4.29% of records) and of 97.3% [73.8%, 100%] in the second (screening 1.34% of records):
 efficiency increased significantly in the second session as only a few new positive matches were found;
-however, given the large number of records, uncertainty about sensitivity also increased, as expected.\
+however, given the large number of records, uncertainty about sensitivity increased, as expected.\
 Both results are above the usual performance in this field [@o2015using] and are in line with the average sensitivity of 92% estimated after human-only screening [@edwards2002identification].
 In one interesting case, the model detected a human-caused misclassification error, demonstrating its robustness and value as a second screener, a role already suggested for SRA tools in previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
-Although "simple query ordering" concentrated most relevant matches in the first 20-25 thousand records, without the tool support the remaining relevant records would have been missed withouth manually screeening almost the entire dataset.\
+Although "simple query ordering" concentrated most relevant matches in the first 20-25 thousand records, without the tool support, the remaining relevant records would have been missed without manually screening almost the entire dataset.\
 
@@
 The aim is to generate a new search query to help find records missed in the first search session.
-The generated query did indeed to retrieve a few more relevant records that were not found in session 1, but at the cost of a significant increase in the number of documents.\
+The generated query did indeed retrieve a few more relevant records not found in session 1 but at the cost of significantly increasing the number of documents.\
 An interesting aspect of this feature is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
@@
 The algorithm is only aware of the "world" defined by the dataset used as input, which is generated by a specific search query focused on a particular topic.
-Therefore, the new query may not be specific enough when applied to an unbounded search domain, and may return an unmanageable amount of unrelated results.
+Therefore, the new query may not be specific enough when applied to an unbounded search domain and may return an unmanageable amount of irrelevant results.
 The solution we found was to add another component to the query, specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research.\
@@
 As mentioned early, our framework builds on modularity.
-We have designed it in such a way that full independence of the main modules can be easily implemented in future iterations;
+We have designed so that each module can become fully independent in future iterations;
 it will be possible for users to add custom features such as citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
 We consider such interoperability to be extremely relevant:
-the main strength of our tool lies in the composition of many solutions such as the idea of Bayesian active machine learning and the exploit of the derived uncertainty in defining the records needing human review.\
-However, each components could benefit considerably from the recent improvements in text mining and machine learning.\
-For example, our text processing approach, based on the "boolean bag-of-words" paradigm, is quite simple, and indeed could be improved by more nuanced text representations.
+the main strength of our tool lies in the composition of many independent solutions, such as the idea of Bayesian active machine learning and the exploit of the derived uncertainty in defining the records needing human review.\
+Each component could benefit considerably from the recent improvements in text mining and machine learning.\
+For example, the text processing approach based on the "boolean bag-of-words" paradigm is quite simple and could be improved by more nuanced text representations.
 It might be considered whether feature transformations such as TF-IDF [@baeza1999modern; @ananiadou2006text] could be advantageous, although we hypothesise that tree-based classification algorithms like BART are robust enough not to require such operations.
 Instead, it might be worth exploring the application of word embedding:
-this technique transforms terms into semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding; @minaee2021deep] and could be used to reduce noise by merging different terms that are semantically similar and enhance signal by distinguishing identical terms with different meaning given the context.
-Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics to expand the feature space.\
+this technique transforms terms into semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding; @minaee2021deep] and could be used to reduce noise by merging different terms that are semantically similar or enhance signal by distinguishing identical terms with different meaning given the context.
+Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis and Latent Semantic Analysis, [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics that expand the feature space.\
 Our classification algorithm is applicable with any Bayesian supervised machine learning method that provides full PPDs;
-therefore, alternative classification models, such as Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian], could be evaluated.
+therefore, alternative classification models, such as Gaussian Processes, known for their flexibility [@jayashree2020evaluation; @chen2015gaussian], could be evaluated.
 It would be even more interesting to test advanced learning algorithms that go beyond the bag-of-words approach and take into consideration higher-level features in the text such as term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], provided that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
@@
 The field of literature review automation is evolving rapidly, and we anticipate an increasing use of such technologies to address the accelerating pace of scientific production.
-We believe it is encouraging that a wide variety of tools are being made available to allow researchers and policymakers find the approach that best fits their needs.\
-We are contributing to this field with an innovative framework that provides excellent performance and easy integration with existing systematic review pipelines.
-The value of this work lies not only in the framework itself, which we make available as open-source software, but also in the set of methodologies we developed to solve various SRA issues and which can also be used to improve already existing solutions.\
+We believe it is encouraging that a wide variety of tools are being made available to let researchers and policymakers find the approach that best fits their needs.\
+We contribute to this field with an innovative framework that provides excellent performance and easy integration with existing systematic review pipelines.
+The value of this work lies not only in the framework itself, which we make available as open-source software, but also in the set of methodologies we developed to solve various SRA issues and which can also be used to improve existing solutions.\

### 2022-02-22 Manuscript/Manuscript_Introduction.Rmd
more language check and updated abstract

@@
 Scientific production has experienced continuous exponential growth in the last decades [@larsen2010rate; @bornmann2015growth].
-This is especially true for biomedical research, a trend further accelerated by the COVID-19 pandemic, thanks to faster article' processing time by publishers and the greater use of preprint databases [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].
+This is especially true for biomedical research, a trend further accelerated by the COVID-19 pandemic, thanks to faster article processing time by publishers and the greater use of preprint databases [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].
 Consequently, it has become harder for researchers and practitioners to stay up to date on the latest findings in their field.
@@
 It has been estimated that labelling 10,000 publications can take up to 40 weeks of work and that the average clinical systematic review takes 63 weeks to complete [@bannach2019machine; @borah2017analysis; @allen1999estimating].
-A consequence of this is systematic reviews are often already out-of-date by the time they are published [@beller2013systematic].\
+A consequence of this is that systematic reviews are often already out-of-date by the time they are published [@beller2013systematic].\
 The field of Data Science applied to evidence synthesis and acquisition has greatly maturated in the last years [@marshall2015systematic; @beller2018making; @tsafnat2014systematic].
@@
 Automation of systematic reviews has made significant improvements in the last years [@ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating], and it is possible foreseeable that it will become the standard approach in the field [@beller2018making], with many solutions already being implemented into commercial or free-to-use tools [see @marshall2015systematic, table 1].\
-In this manuscript, we present an open source, production-ready framework that further contributes to the state-of-the-art in systematic review automation (SRA) and helpers (SRH) tools.
+This manuscript introduces an open-source, production-ready framework that further contributes to the state-of-the-art in systematic review automation (SRA) and helpers (SRH) tools.
 We improve the "retrieval phase" by providing a unified framework for the automated collection and management of scientific literature from multiple online sources.
 For the citation screening (appraisal) phase, we built an active machine learning-based protocol [@settles2009active; @miwa2014reducing],
-which utilises a Bayesian framework to efficiently identify potentially relevant documents that require human review, while automatically screening-out the vast majority of clearly non-relevant ones;
-the algorithm then requires human review to iteratively increase classification accuracy.
-Finally, we included a tool to generate new search queries based on an already labelled citation data set, to identify relevant research that may possibly have been missed by manually-made queries.\
+which utilises a Bayesian framework to efficiently identify potentially relevant documents that require human review while automatically screening-out the vast majority of clearly non-relevant ones;
+the algorithm then requires human review to increase classification accuracy iteratively.
+Finally, we included a tool to generate new search queries based on an already categorised citation data set, to identify relevant research that manually-made queries may have possibly missed.\
 We tested the framework in the retrieval and appraisal phases of an example topic of interest to our group:

### 2022-02-22 Manuscript/Manuscript_Methods.Rmd
more language check and updated abstract

@@
       in_header: header.tex
-  github_document: default
 ---
@@
 record acquisition and classification.
-The code used to generate the results in the manuscript is available at https://github.com/AD-Papers-Material/BART_SystReviewClassifier, while an updated and ready to use version of the framework is distributed as an R package at https://github.com/bakaburg1/BaySREn.
-The framework includes several modules that communicate through intermediate outputs stored in standard formats, which make it possible for users to extend the framework or easily integrate it with other tools in their pipeline.
+The code used to generate the results is available at https://github.com/AD-Papers-Material/BART_SystReviewClassifier, while an updated and ready to use version of the framework is distributed as an R package at https://github.com/bakaburg1/BaySREn.
+The framework includes several modules that communicate through intermediate outputs stored in standard formats, making it possible for users to extend the framework or easily integrate it with other tools in their pipeline.
 See Supplemental Material S1 for an in-depth description of the framework and how to use it.\
@@
 
-```{r method_diagram, fig.cap = "Figure 1.Framework's visual depiction.", echo = FALSE, out.width = "100%"}
+```{r method_diagram, fig.cap = "Figure 1. Framework's visual representation.", echo = FALSE, out.width = "100%"}
 knitr::include_graphics("methods_diagram.png", auto_pdf = T)
@@
 Pubmed (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
-The framework takes care of authorization management for non-open databases like WOS and IEEE.
-It is also possible to download and import records in the framework manually;
-this is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/>) and EMBASE databases (<https://www.embase.com/>), for which a comprehensive API interface was not easy to build.
-An extra manual search was also necessary for Pubmed, since the API and the web interface have different rule expansion algorithms and return slightly different results [@pubmedUpdate].
+The framework handles authorisation management for non-open databases like WOS and IEEE.
+It is also possible to import previously downloaded records in the framework;
+this is particularly useful for acquiring records from SCOPUS (<https://www.scopus.com/>) and EMBASE databases (<https://www.embase.com/>), for which a comprehensive API interface was not easy to build.
+An extra manual search was also necessary for Pubmed since the API and the web interface have different rule expansion algorithms and return slightly different results [@pubmedUpdate].
 A short guide on how to set up the framework for each database supported is available in Supplemental Material S3.\
@@
 The records are ordered according to the frequency of the positive query terms (e.g., not preceded by a _NOT_ modifier) in the title and abstract ("simple query ordering").\
-The researcher is then asked to label a number of records to create the "initial training set" needed to start the automatic classification.
-We recommend manually labelling the first 250 records (see "hyperparameter optimization" later).
+The researcher is then asked to label a subset of records to create the "initial training set" needed to start the automatic classification.
+We recommend manually labelling the first 250 records (see "hyperparameter optimisation" later).
 Simple query ordering increases the positivity rate in the initial training set [@wallace2010active], leading to higher sensitivity during automatic classification [@chawla2004special].
@@
 
-The collected citation data contain a number of fields characterising a scientific publication.
-The framework models the relevance of a record based on the following fields:
+The framework models the relevance of a record based on the following fields in the citation data:
 title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
 A range of Natural Language Processing (NLP) techniques [@baeza1999modern; @marshall2015systematic; @ananiadou2006text] are employed to convert the textual information in these fields into features for machine learning through a bag-of-words approach [@marshall2015systematic].
-Processing of free text fields (title, abstract) includes: tokenization (i.e., extracting the terms), removal of common stopwords (i.e., sentence components having no semantic value), part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatisation of terms (i.e., reduction to their base grammatical form).
+Processing of free text fields (title, abstract) includes: tokenisation (i.e., extracting the terms), removal of common stopwords (i.e., sentence components having no semantic value), part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatisation of terms (i.e., reduction to their base grammatical form).
 Text processing for authors, keywords and MESH terms identifies logical units (e.g., authors' full names, composite keywords) and extracts them.\
@@
 Some terms tend to co-appear in records (non-consecutive ngrams, nc-ngrams), often carrying a particular meaning when they do co-occur.
-To detect nc-ngrams, we generated a word network representation [@rousseau2015graph] with edges occurring between terms with a cosine similarity in terms of docuement co-occurrence > 0.5.
+To detect nc-ngrams, we generated a word network representation [@rousseau2015graph] with edges occurring between terms with a cosine similarity in terms of document co-occurrence > 0.5.
 We extracted the maximal cliques in the network [@eppstein2010listing] representing highly correlated groups of terms;
@@
 We set up the BART model to use 2,000 MCMC iterations (after 250 burn-in iterations) and 50 trees;
-we used a $k$ value of 2 to regularize extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction].
+we used a $k$ value of 2 to regularise extreme prediction and let the model use missing fields in the DTM as features [@kapelner2015prediction].
 Positive records are oversampled ten times to increase sensitivity [@batista2004study].\
@@
 This process is carried out iteratively to reduce prediction uncertainty.\
-Label assignment is done through identification of an "uncertainty zone" the construction of which is possible thanks to the Bayesian nature of BART, which provides full PPDs instead of point-wise predictions for each record.\
-To describe the process formally, we define
+Label assignment is done through identification of an "uncertainty zone", the construction of which is possible thanks to the Bayesian nature of BART, which provides full PPDs instead of point-wise predictions for each record.\
+To describe the process formally, we define:
 
@@
 
-as the PPD of a record $D_i$ being relevant (i.e, having a positive label, $L_i = 1$), averaging the PPDs of the ensemble of $M=10$ models $m$, and
+as the PPD of a record $D_i$ being relevant (i.e, having a positive label, $L_i = 1$), averaging the PPDs of the ensemble of $M=10$ models $m$, and:
 
@@
 respectively as the lower and upper boundaries of the 98% quantile interval of $\pi_i$ (98% Predictive Interval, 98% PrI).\
-Then we identify the "uncertainty zone" as
+Then we identify the "uncertainty zone" as:
 
 $$U_\pi=[\max\vec{\pi}_{u}^-, \min\vec{\pi}_{l}^+]$$
+
 with $\vec{\pi}_{u}^-$ being the vector of $\pi_{i,u}$ with a negative label and $\vec{\pi}_{l}^+$ the vector of $\pi_{i,l}$ with a positive label.
 That is, $U_\pi$ defines a range of values between the smallest $\pi_{i,l}$ in the set of already labelled positive records $L_p$ and the largest $pi_{i,u}$ related to the negative ones $L_n$, noting that the two limits can appear in any order.\
-Consequently, a record $D_i$ will be labelled as positive if
+Consequently, a record $D_i$ will be labelled as positive if:
 
@@
 that is, the record lower 98% PrI boundary should be higher than every value in the uncertainty zone.
-In other words, for a record to be labelled positive, its PPD should be within the range of the mixture of PPD of the records previously labelled positive, and should not cross the distributions of the negative records.\
-Conversely, a record is labelled as negative if
+In other words, for a record to be labelled positive, its PPD should be within the range of the mixture of PPD of the records previously labelled positive and should not cross the distributions of the negative records.\
+Conversely, a record is labelled as negative if:
 
@@
 
-With the BART model, it is possible to extract the proportion of times a term is used in a posterior tree over the sum of total inclusions of all variables [@kapelner2013bartmachine], as a measure of importance of the features in the model.
+As a measure of feature importance, we computed the "inclusion rate", that is, the proportion of times a term is used in a posterior tree over the sum of total inclusions of all variables [@kapelner2013bartmachine].
 We extracted the terms, the portion of the citation data in which they were used, the average "inclusion rate" among the ensemble models (over 10,000 inclusions) and its ratio over the standard deviation of this inclusion (inclusion stability, IS).
-For each term we ran a Poisson regression to get the linear association with a positive label and reported it as Relative Risk (RR) with the number of standard errors as significance index (Statistic);
-the comparison between the inclusion rate in the BART models and the linear association allows to spot relevant non-linear effects (i.e, the feature is relevant only in association with others).
-In the Results, we only listed the first  15 terms with IS > 1.5, (in order of inclusion rate), while the first fifty terms regardless of inclusion stability are listed in Supplemental Material S2.
+For each term, we ran a Poisson regression to get the linear association with a positive label and reported it as Relative Risk (RR) with the number of standard errors as significance index (Statistic);
+the comparison between the inclusion rate in the BART models and the linear association allows to spot relevant non-linear effects (i.e., the feature is relevant only in association with others).
+In the Results, we only listed the first  15 terms with IS > 1.5 (in order of inclusion rate), while the first fifty terms, regardless of inclusion stability, are listed in Supplemental Material S2.
 
@@
 We developed an algorithm that generates a new search query to find further relevant publications missed in the initial search, possibly at a reasonable cost to specificity (i.e., a higher number of negative results).\
-The algorithm encompasses a number of steps:
+The algorithm is composed of the following steps:
 
@@
 Rules inside each group are ordered by specificity.
-- The researcher is then asked to review the rule groups and select one or more rules from each group (useful if they convey different meaning), or edit them if overly too specific positive or negative conditions were included.
+- The researcher is then asked to review the rule groups and select one or more rules from each group or edit overly specific rules (e.g., citing a non-relevant concept casually associated with a paper, like a numeric value or indicator).
 It is possible to exclude a group of rules altogether, especially those with the poorest sensitivity/specificity ratio.
@@
 - Redundant (i.e., rules whose positive records are already included in more specific ones) and non-relevant rules (i.e., conditions that when removed do not impact sensitivity and specificity) are removed.
-- Finally, the rules are re-elaborated in a query that can be used in the major scientific databases.
+- Finally, the rules are re-elaborated in a query that can be used to perform a new citation search.
 
-Because the algorithm is data-driven, it creates queries that effectively select positive records from the input dataset, but may be not specific enough when applied to actual research databases.
-Therefore we added an extra subquery in _AND_, that specifies the general topics of our search and narrows the search domain.\
+Because the algorithm is data-driven, it creates queries that effectively select positive records from the input dataset but may be not specific enough when applied to actual research databases.
+Therefore we added an extra subquery in _AND_that specifies the general topics of our search and narrows the search domain.\
 The new query was used to initiate a second search session.
@@
 
-We trained a simple Bayesian logistic regression (surrogate model) on the reviewed records to evaluate the consistency of classification model (see Discussion for the theoretical justification).
-The surrogate model uses as predictor the lower boundary of the 98% PrI of the PPD of the records with weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).\
+We trained a simple Bayesian logistic regression (surrogate model) on the reviewed records to evaluate the consistency of the classification model (see Discussion for the theoretical justification).
+The surrogate model uses as predictor the lower boundary of the 98% PrI of the PPD of the records with weakly regularising, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).\
 The quality of the model was evaluated through the Bayesian $R^2$ [@gelman2019r], of which we reported the posterior median and 90% Credible Interval [90% CrI].
 The $R^2$ also provides an evaluation of the consistency of the original classification model.
-Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing plausible worst-case scenarios.\
+Given that this model is conditional only on the BART predictions and not on the DTM, it is characterised by more uncertainty, providing plausible worst-case scenarios.\
 The surrogate model is then used to generate the predictive cumulative distribution of the number of total positive records in the whole dataset.
-This distribution allows to estimate the expected total posterior "Sensitivity" and "Efficiency" of the classification model in the full (unreviewed) dataset.
+This distribution allows estimating the expected total posterior "Sensitivity" and "Efficiency" of the classification model in the whole (unreviewed) dataset.
 Efficiency is summarised by the "Work saved over random" (WSoR) statistic:
-one minus the ratio between the number of record manually reviewed and those that would be required to find the same number of positives if classification were performed choosing records randomly;
+one minus the ratio between the number of records manually reviewed and those that would be required to find the same number of positives if classification were performed choosing records randomly;
 this last quantity is estimated through a negative hypergeometric distribution [@chae1993presenting] over the predicted number of positive records.\
@@
 To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled "validation set" derived from the first 1,200 records of the first session dataset.
-Each hyperparameter combination was tested until four CR iterations were completed with no positive records or the whole dataset was labelled.\
+Each hyperparameter combination was tested until four CR iterations were completed with no positive records or until the whole dataset was labelled.\
 For each combination, a performance score was computed as the product of "Efficiency" (1 minus the ratio of records that required reviewing over the total number of records) and "Sensitivity" (number of positive records found over the total number of positive records).
 We then used a partition tree [@rpart] to identify homogeneous "performance clusters" of scores given hyperparameter values.
-For the rest of the study, we used the best hyperparameter set in terms of Sensitivity followed by Efficiency from the cluster with the highest average score.\
+For the rest of the study, we used the best hyperparameter set in terms of sensitivity followed by efficiency from the cluster with the highest average score.\

### 2022-02-22 Manuscript/Manuscript_Results.Rmd
more language check and updated abstract

@@
 There were various degrees of overlapping between sources, with `r percent(1 - source_distr[1])` of records being present in more than one database, and EMBASE and IEEE being the databases with the higher uniqueness ratios.
-The final data set was composed from `r source_summary$Total$Records` unique records.\
-The first `r num_first_labeling` records (based on "simple query ordering") were labeled manually.
-Of these `r sprintf('%d (%s)', num_first_positives, percent(num_first_positives/num_first_labeling))` were labeled as positive, and `r sprintf('%d (%s)', num_first_negatives, percent(num_first_negatives/num_first_labeling))` as negative.
+The final data set was composed of `r source_summary$Total$Records` unique records.\
+The first `r num_first_labeling` records (based on "simple query ordering") were categorised manually.
+Of these `r sprintf("%d (%s)", num_first_positives, percent(num_first_positives/num_first_labeling))` were labeled as positive, and `r sprintf("%d (%s)", num_first_negatives, percent(num_first_negatives/num_first_labeling))` as negative.
 
@@
 Distribution of retrieved records by source and session.
-For each source it is reported the number of records, percentage over the session total (after removing duplicates), and number or records specific for a source as absolute value and as percentage over the source total.
+For each source, we reported the number of records, percentage over the session total (after removing duplicates), and the number of records specific for a source as absolute value and as percentage over the source total.
 All session shows records after joining and deduplication of the Session 1 and Session 2 data set.", label = "Table 1")`
 
-The labeled records were used to train the Bayesian classification model used to label the remaining records.
+The categorised records were used to train the Bayesian classification model used to label the remaining records.
 After seven classification and review (CR) iterations (three resulting in new positive matches and four extra replications to account for stochastic variability), a total of `r num_last_positives` positives matches were found, requiring manual review of `r tot_reviewed` records (`r percent(num_last_positives/tot_reviewed)` positivity rate).\
 It is noticeable how the number of records that required manual review decreased rapidly between iterations (Table 2), indicating that the engine was converging while the uncertainties were resolved.\
-This phenomenon is better illustrated in Fig. 1 of the Supplemental Material S2.
+This phenomenon is better illustrated in Fig. 1 of Supplemental Material S2.
 It shows the mixture distribution of the PPDs of the records, specifically for records that were manually reviewed, before and after the classification step:
@@
 Results of the automatic classification and manual review rounds.
-For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown.
+The cumulative numbers of positives and negative records and their sum (Total labelled) and percentage over total are shown for each iteration.
 Also, the number of changes after review and their description is reported.\"Unlab.\" indicates unlabelled records marked for review.
-For each Iteration, the number of features used by the engine is also reported.
+For each iteration, the number of features used by the engine is also reported.
 The first row reports the results of the initial manual labelling of records, which served as input for the automatic classification in Iteration 1.
@@
 
-We extracted the 15 term more relevant for the classification model, described as:
+We extracted the 15 more relevant terms for the classification model, described as:
 Term (citation part): Inclusion Rate (Inclusion Stability) [linear Relative Risk, Statistic].
@@
 The engine was able to pick up the central concept of the research topic, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) as well as the region of interest ("Orange County") of another research group active on the topic of pathogen spreading over hospital networks.
-Some terms were considered highly relevant by the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would hardly be significant (statistic: -1.21 s.e.);
-these are terms that are only relevant in conjunction with other terms but not by their own, highlighting the extra predictive power achievd through the use of advanced, non-linear machine learning.\
-A more extensive set of terms is presented in Table 1 of the Supplemental Material S2.
+Some terms were considered highly relevant by the BART models (e.g., "Worker" in the sixth position out of more than 3800 terms considered), although in a simple linear model, their effect would hardly be significant (statistic: -1.21 s.e.);
+these are terms that are only relevant in conjunction with other terms but not on their own, highlighting the extra predictive power achieved through the use of advanced, non-linear machine learning.\
+A more extensive set of terms is presented in Table 1 of Supplemental Material S2.
 
@@
 
-The results of the first classification session were used to create a second, data-driven query with the objective of performing a more extensive search to find records that may have been missed during the first search session.
+The results of the first classification session were used to create a second, data-driven query to perform a more extensive search to find records that may have been missed during the first search session.
 The resulting query was as follows:\
@@
 
-The final piece *AND ((antimicrobial resistance) OR (healthcare infection)* was added manually to better define the search domain, since the algorithm was trained on documents that were all more or less related to these topics.\
+The final piece *AND ((antimicrobial resistance) OR (healthcare infection)* was added manually to define the search domain better since the algorithm was trained on documents that were all more or less related to these topics.\
 The generated query also provides a more nuanced understanding of the engine's internal classification logic, and this is helpful to spot possible biases in the model.\
@@
 We obtained `r nrow(records_s2)` unique records, with just `r session_diff` shared records between searches, which equates to `r percent(session_diff / source_list[['All Sessions']]$Total$Records)` of the total.
-The percentage of records shared by two or more source dropped to `r percent(1 - source_distr[1])`.
+The percentage of records shared by two or more sources dropped to `r percent(1 - source_distr[1])`.
 
-`r english::as.english(n_review_rounds) %>% str_to_title()` CR rounds were necessary to complete the second session classification, with just `r sum(session_summary[-1, 'Unlab.
--> y'])` new positive found after reviewing `r tot_reviewed - session_summary$tot_reviewed_[1]` extra records.
+`r english::as.english(n_review_rounds) %>% str_to_title()` CR rounds were necessary to complete the second session classification, with just `r sum(session_summary[-1, "Unlab.
+-> y"])` new positive found after reviewing `r tot_reviewed - session_summary$tot_reviewed_[1]` extra records.
 The first CR iteration required the user to review a substantial number of records (1,273);
-however, just labelling 275 of them (the suggested 250 plus 25 alredy labelled for the framework hyperparameter tuning) was sufficient to reduce this number to just 190 in the subsequent round.
+however, just labelling 275 of them (the suggested 250 plus 25 already labelled for the framework hyperparameter tuning) was sufficient to reduce this number to just 190 in the subsequent round.
 An evaluation of the convergence (Supplemental Material S2, Fig.
@@
 The interpretation is that as the number of negative training records increases, the engine becomes more and more sceptical and even asks to review some records labelled as positive in the initial training set generated during Session 1.
-This behaviour can be useful to spot classification errors and inconsistencies.
+This behaviour can rev spot classification errors and inconsistencies.
 Considering both sessions, `r tot_reviewed` records were manually reviewed and `r num_last_positives` (`r percent(num_last_positives / tot_reviewed)`) confirmed positive matches were found.
 
-Again, the evaluation of the inclusion rate of the terms showed that the engine is quite capable of internalizing the concepts behind the research topic.
+Again, the evaluation of the inclusion rate of the terms showed that the engine is quite capable of internalising the concepts behind the research topic.
 A subsample of the relevant terms used by the model in the second session is reported in Table 2 of Supplemental Material S2.
@@
 The analysis suggested that the following parameter combination performed best:
-an initial input of 250 labelled records with 10x oversampling of positive matches, an averaged ensemble of 10 models, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
+an initial training set of 250 categorised records with 10x oversampling of positive matches, ten models in the ensemble, no bootstrapping and an uncertainty zone defined by the 98% predictive interval.
 This combination of parameters was associated with a sensitivity of `r grid_search$Sensitivity` (`r grid_search$Pos_labels` positive matches found) and an efficiency of `r grid_search$Efficiency` (`r grid_search$Tot_labeled` records evaluated).
@@
 Fig.
-2 in Supplemental Material S2 demonstrates that the positive record oversampling rate, the number of ensemble models and the size of the initial training set were the parameters that mostly impacted performance.
+2 in Supplemental Material S2 demonstrates that the positive record oversampling rate, the number of ensemble models and the size of the initial training set were the parameters that mainly impacted performance.
 
@@
 Fig. 2 presents the actual and predicted (from the surrogate model) cumulative number of positive matches, ordered by the initial simple ordering query:
-the median of surrogate models' cumulative predictive distributions matches quite well the actual number of positive records found.
-It is striking how many more records would have required manual evaluation to find the same number of positive matches without using a smart classification tool,
+the median of surrogate models' cumulative predictive distributions matches the actual number of positive records found quite well.
+It is striking how many more records would have required manual evaluation to find the same number of positive matches without a classification algorithm,
 with some positive matches found close to the end of the heuristically ordered list of records.\
@@
 In session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.
-In session 2 we observed a drop in expected sensitivity, especially in the lower credibility boundary (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`),
-due to the fact that as the number of records increases, even a small probability of being a positive match can, in the worst case scenario, lead to a relevant number of missed positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
-To ensure that no obvious positive matches were missed, we evaluated 100 additional records among those not reviewed with the highest median predicted probability produced by the engine and found no additional positive matches.\
+In session 2 we observed a drop in expected sensitivity, especially in the lower credibility boundary (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`):
+as the number of records increases, even a small probability of being a positive match can, in the worst-case scenario, lead to a relevant number of predicted positive matches (`r Performance$s2$pred_positives %>% max()` in this case).
+To ensure no obvious positive matches were missed, we evaluated 100 non-reviewed records with the highest median predicted probability and found no additional positive matches.\
 
-`r print_table(perf_table, caption = '**Table 3**.
+`r print_table(perf_table, caption = "**Table 3**.
 Estimated performance summary.
 The table reports for each session, the number of reviewed records and the percentage over the total.
-Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90% PrI truncated to the observed realization in the dataset [trunc.
+Also, the posterior expected number of positive records, sensitivity and efficiency (as WSoR) are reported, with their 90% PrI truncated to the observed realisation in the dataset [trunc.
 PrI] (see.
 methods).
-Finally the median Bayesian $R^2$ [90% CrI] of the logistic models is reported.
-PrI: Predictive Intervals; CrI: Credibility Intervals.', allow_math = TRUE, label = "Table 3")`
+Finally, the logistic model's median Bayesian $R^2$ [90% CrI] is reported.
+PrI: Predictive Intervals; CrI: Credibility Intervals.", allow_math = TRUE, label = "Table 3")`
 
@@
 The [trunc.
-90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as a shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines).
-The median of the PrI is represented by a darker blue line."}
+90% PrI] of the cumulative positive matches estimated by the Bayesian logistic model is shown as a shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines).
+A darker blue line represents the median of the PrI."}
 

### 2022-03-03 Manuscript/Manuscript.Rmd
prepare BMC submission

@@
 authors:
-  - name: Angelo D'Ambrosio
+  - first_name: Angelo
+    second_name: D'Ambrosio
+    initials: A.D.
+    email: [angelo.d.ambrosio@uniklinik-freiburg.de, a.dambrosioMD@gmail.com]
+    affiliation_IDs: aff1
+    corresponding: true
+  - first_name: Hajo
+    second_name: Grundmann
+    initials: H.G.
+    email: hajo.grundmann@uniklinik-freiburg.de
+    affiliation_IDs: aff1
+  - first_name: Tjibbe
+    second_name: Donker
+    initials: T.D.
+    email: tjibbe.donker@uniklinik-freiburg.de
+    affiliation_IDs: aff1
+affiliations:
+  - id: aff1
+    affiliation: Freiburg University Hospital
     department: Institute for Infection Prevention and Hospital Hygiene
-    affiliation: Freiburg University Hospital
-    location: Freiburg, Germany
-    email: angelo.d.ambrosio@uniklinik-freiburg.de; a.dambrosioMD@gmail.com
-  - name: Hajo Grundmann
-    department: Institute for Infection Prevention and Hospital Hygiene
-    affiliation: Freiburg University Hospital
-    location: Freiburg, Germany
-    email: hajo.grundmann@uniklinik-freiburg.de
-  - name: Tjibbe Donker
-    department: Institute for Infection Prevention and Hospital Hygiene
-    affiliation: Freiburg University Hospital
-    location: Freiburg, Germany
-    email: tjibbe.donker@uniklinik-freiburg.de
-abstract: |
+    city: Freiburg
+    country: Germany
+abstract:
+  - section_title: Background
+    section_text: |
      The exponential growth of scientific production makes secondary literature abridgements increasingly demanding.
-  We introduce a new open-source framework for systematic reviews that significantly reduces time and workload for collecting and screening scientific literature.\
+     We introduce a new open-source framework for systematic reviews that significantly reduces time and workload for collecting and screening scientific literature.
+  - section_title: Methods
+    section_text: |
      The framework provides three main tools:
@@
      To evaluate the automatic screener's performance, we estimated the median posterior sensitivity and efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of undetected potentially relevant records.\
+  - section_title: Results
+    section_text: |
      Tested on an example topic, the framework collected 17,755 unique records through the citation manager;
@@
      The overall expected sensitivity decreased to 97.3% [73.8%, 100%] while the efficiency increased to 98.6% [98.2%, 98.7%].\
+  - section_title: Conclusions
+    section_text: |
      The framework can significantly reduce the workload required to conduct large literature reviews
@@
   - Bayesian modeling
-bibliography: references.bib
+abbreviations:
+  - abbr: API
+    descr: Application Programming Interface
+  - abbr: BART
+    descr: Bayesian Additive Regression Trees
+  - abbr: COVID-19
+    descr: Coronavirus Disease 2019
+  - abbr: CR
+    descr: Classification & Review
+  - abbr: DTM
+    descr: Document-Term Matrix
+  - abbr: ICASR
+    descr: International Collaboration for the Automation of Systematic Reviews
+  - abbr: IEEE
+    descr: Institute of Electrical and Electronics Engineers
+  - abbr: IS
+    descr: Inclusion Stability
+  - abbr: MCMC
+    descr: Monte Carlo Markov Chain
+  - abbr: MeSH
+    descr: Medical Subject Headings
+  - abbr: MCMC
+    descr: Monte Carlo Markov Chain
+  - abbr: NLP
+    descr: Natural Language Processing
+  - abbr: PPD
+    descr: Expected Value Posterior Predictive Distribution
+  - abbr: RR
+    descr: Relative Risk
+  - abbr: SRA
+    descr: Systematic Review Automation
+  - abbr: SRH
+    descr: Systematic Review Helpers
+  - abbr: TF-IDF
+    descr: Term Frequency - Inverse Document Frequency
+  - abbr: WOS
+    descr: Web Of Science
+  - abbr: WSoR
+    descr: Work Saved over Random
+bibfile: references.bib
+nocite: |
+ @d2022open, @zenododata
+appendix:
+  acknowledgments: |
+   We would like to thank Deborah Lawrie-Blum and Fabian Bürkin respectively for
+   English language proofreading and mathematical formalization proof check.
+  funding: |
+   This project was developed under the Joint Programming Initiative on
+   Antimicrobial Resistance (JPIAMR) through the 7th call, project number
+   01KI1831 funded by BMBF and administrated by DLR Project Management Agency.
+  data_availability: |
+   The code and the instructions necessary to reproduce the results are
+   available at https://github.com/AD-Papers-Material/BART_SystReviewClassifier.
+   An updated, ready-to-use version of the framework is available at
+   https://github.com/bakaburg1/BaySREn. All relevant data necessary to
+   replicate the results is available at:
+   https://doi.org/10.5281/zenodo.6323360.
+  ethic_approval: Not applicable.
+  competing_interest: The authors declare no competing interests.
+  publication_consent: Not applicable.
+  author_contribution: |
+   Conceptualization: AD, TD; Data curation: AD;
+   Formal analysis & Methodology: AD; Project administration: AD, TD;
+   Software development: AD; Supervision: TD, HG;
+   Writing–original draft: AD, TD; Writing–review & editing: AD, TD, HG.
+   All authors have read and approved the manuscript.
+  author_information: false
+  additional_files:
+    - title: S1. Framework description and usage.
+      description: |
+       Instruction on how to use the framework and
+       reproduce the results in the manuscript.
+    - title: S2. Additional outputs.
+      description: Additional analysis outputs described in the manuscript.
+    - title: S3. Online search instructions.
+      description: |
+       Instructions about how to prepare the framework to interact with the
+       online scientific databases to collect records.
 lang: en-GB
+double_spacing: false
+line_numbers: false
+two_columns: false
+remove_fig_numbering: true
 output: 
-  rticles::arxiv_article:
-    number_sections: no
+  pdf_document:
+    template: bmc_template.tex
+    md_extensions: -auto_identifiers-autolink_bare_uris
     keep_tex: true
+    keep_md: true
+    pandoc_args:
+      - --natbib
+      - --lua-filter=bmc_filters.lua
+    number_sections: false
     includes:
@@
 
-```{r, echo=FALSE, results='asis', message = FALSE, warning = FALSE, error = FALSE, dpi = 400, fig.width=12, fig.height=5}
-
-out <- unlist(lapply(c(
-  "Manuscript_Introduction.Rmd",
-  "Manuscript_Methods.Rmd",
-  "Manuscript_Results.Rmd",
-  "Manuscript_Discussion.Rmd"
-), knitr::knit_child, quiet = TRUE))
-
-cat(out, sep = "\n")
+<!-- Background -->
+```{r, child=c("Manuscript_Introduction.Rmd")}
 ```
 
-\newpage
+<!-- Methods -->
 
-# References
+```{r, child=c("Manuscript_Methods.Rmd")}
+```
+
+<!-- Results -->
+
+```{r, child=c("Manuscript_Results.Rmd")}
+```
+
+<!-- Discussion -->
+
+```{r, child=c("Manuscript_Discussion.Rmd")}
+```

### 2022-03-03 Manuscript/Manuscript.tex
prepare BMC submission

@@
-\documentclass{article}
-
-\usepackage{arxiv}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{graphicx}
-
-\title{An open-source integrated framework for the automation of
-citation collection and screening in systematic reviews.}
-
-\author{
-    Angelo D'Ambrosio
-   \\
-    Institute for Infection Prevention and Hospital Hygiene \\
-    Freiburg University Hospital \\
-  Freiburg, Germany \\
-  \texttt{\href{mailto:angelo.d.ambrosio@uniklinik-freiburg.de}{\nolinkurl{angelo.d.ambrosio@uniklinik-freiburg.de}};
-\href{mailto:a.dambrosioMD@gmail.com}{\nolinkurl{a.dambrosioMD@gmail.com}}} \\
-   \And
-    Hajo Grundmann
-   \\
-    Institute for Infection Prevention and Hospital Hygiene \\
-    Freiburg University Hospital \\
-  Freiburg, Germany \\
-  \texttt{\href{mailto:hajo.grundmann@uniklinik-freiburg.de}{\nolinkurl{hajo.grundmann@uniklinik-freiburg.de}}} \\
-   \And
-    Tjibbe Donker
-   \\
-    Institute for Infection Prevention and Hospital Hygiene \\
-    Freiburg University Hospital \\
-  Freiburg, Germany \\
-  \texttt{\href{mailto:tjibbe.donker@uniklinik-freiburg.de}{\nolinkurl{tjibbe.donker@uniklinik-freiburg.de}}} \\
-  }
-
-% tightlist command for lists without linebreak
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% Pandoc citation processing
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-% for Pandoc 2.8 to 2.10.1
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
-% For Pandoc 2.11+
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+%% BioMed_Central_Tex_Template_v1.06
+%%                                      %
+%  bmc_article.tex            ver: 1.06 %
+%                                       %
+
+%%IMPORTANT: do not delete the first line of this template
+%%It must be present to enable the BMC Submission system to
+%%recognise this template!!
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                     %%
+%%  LaTeX template for BioMed Central  %%
+%%     journal article submissions     %%
+%%                                     %%
+%%          <8 June 2012>              %%
+%%                                     %%
+%%                                     %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% For instructions on how to fill out this Tex template           %%
+%% document please refer to Readme.html and the instructions for   %%
+%% authors page on the biomed central website                      %%
+%% https://www.biomedcentral.com/getpublished                      %%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%% BioMed Central currently use the MikTex distribution of         %%
+%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
+%% https://miktex.org/                                             %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% additional documentclass options:
+%  [doublespacing]
+%  [linenumbers]   - put the line numbers on margins
+
+%%% loading packages, author definitions
+
+%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
+\documentclass[]{bmcart}
+
+%%% Load packages
+\usepackage{amsthm,amsmath}
+\RequirePackage[numbers]{natbib}
+%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
+%\RequirePackage{hyperref}
+\usepackage[utf8]{inputenc} %unicode support
+%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
+%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
+\usepackage[strings]{underscore} % CUSTOM: fixes problems with underscores in .bib
 
@@
 \usepackage{lineno}
-\linenumbers
+%\linenumbers
 \captionsetup[table]{labelformat=empty}
@@
 \usepackage{xcolor}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                             %%
+%%  If you wish to display your graphics for   %%
+%%  your own use using includegraphic or       %%
+%%  includegraphics, then comment out the      %%
+%%  following two lines of code.               %%
+%%  NB: These line *must* be included when     %%
+%%  submitting to BMC.                         %%
+%%  All figure files must be submitted as      %%
+%%  separate graphics through the BMC          %%
+%%  submission process, not included in the    %%
+%%  submitted article.                         %%
+%%                                             %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \def\includegraphic{}
+% \def\includegraphics{}
+
+%%% Put your definitions there:
+\startlocaldefs
+\def\url{} % CUSTOM: \url requires hyperref package, but loading it causes errors with the author formatting
+
+\providecommand{\tightlist}{ % CUSTOM: pandoc uses \tightlist for lists, without loading the required package
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}
+  }
+\endlocaldefs
+
+%%% Begin ...
 \begin{document}
-\maketitle
-
-\begin{abstract}
+
+%%% Start of article front matter
+\begin{frontmatter}
+
+\begin{fmbox}
+\dochead{Research}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the title of your article here     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{An open-source integrated framework for the automation of
+citation collection and screening in systematic reviews.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors here                   %%
+%%                                          %%
+%% Specify information, if available,       %%
+%% in the form:                             %%
+%%   <key>={<id1>,<id2>}                    %%
+%%   <key>=                                 %%
+%% Comment or delete the keys which are     %%
+%% not used. Repeat \author command as much %%
+%% as required.                             %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\author[
+  addressref={aff1},
+    corref={aff1},
+    email={angelo.d.ambrosio@uniklinik-freiburg.de,a.dambrosioMD@gmail.com}
+]{\inits{A.D.}\fnm{Angelo} \snm{D'Ambrosio}}
+\author[
+  addressref={aff1},
+    email={hajo.grundmann@uniklinik-freiburg.de}
+]{\inits{H.G.}\fnm{Hajo} \snm{Grundmann}}
+\author[
+  addressref={aff1},
+    email={tjibbe.donker@uniklinik-freiburg.de}
+]{\inits{T.D.}\fnm{Tjibbe} \snm{Donker}}
+
+% \author[
+%   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
+%   corref={aff1},                       % id of corresponding address, if any
+% % noteref={n1},                        % id's of article notes, if any
+%   email={jane.e.doe@cambridge.co.uk}   % email address
+% ]{\inits{J.E.}\fnm{Jane E.} \snm{Doe}}
+% \author[
+%   addressref={aff1,aff2},
+%   email={john.RS.Smith@cambridge.co.uk}
+% ]{\inits{J.R.S.}\fnm{John R.S.} \snm{Smith}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors' addresses here        %%
+%%                                          %%
+%% Repeat \address commands as much as      %%
+%% required.                                %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\address[id=aff1]{
+    \orgdiv{Institute for Infection Prevention and Hospital Hygiene},
+      \orgname{Freiburg University Hospital},
+          \city{Freiburg},
+      \cny{Germany}
+  }
+
+% \address[id=aff1]{%                           % unique id
+%   \orgdiv{Department of Science},             % department, if any
+%   \orgname{University of Cambridge},          % university, etc
+%   \city{London},                              % city
+%   \cny{UK}                                    % country
+% }
+% \address[id=aff2]{%
+%   \orgdiv{Institute of Biology},
+%   \orgname{National University of Sciences},
+%   %\street{},
+%   %\postcode{}
+%   \city{Kiel},
+%   \cny{Germany}
+% }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter short notes here                   %%
+%%                                          %%
+%% Short notes will be after addresses      %%
+%% on first page.                           %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\begin{artnotes}
+%%\note{Sample of title note}     % note to the article
+%\note[id=n1]{Equal contributor} % note, connected to author
+%\end{artnotes}
+
+ \end{fmbox} % comment this for two column layout
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                           %%
+%% The Abstract begins here                  %%
+%%                                           %%
+%% Please refer to the Instructions for      %%
+%% authors on https://www.biomedcentral.com/ %%
+%% and include the section headings          %%
+%% accordingly for your article type.        %%
+%%                                           %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{abstractbox}
+
+\begin{abstract} % abstract
+\parttitle{Background} %if any
 The exponential growth of scientific production makes secondary
@@
 open-source framework for systematic reviews that significantly reduces
-time and workload for collecting and screening scientific literature.\\
+time and workload for collecting and screening scientific literature.
+\parttitle{Methods} %if any
 The framework provides three main tools: 1) an automatic citation search
@@
 undetected potentially relevant records.\\
+\parttitle{Results} %if any
 Tested on an example topic, the framework collected 17,755 unique
@@
 98.7\%{]}.\\
+\parttitle{Conclusions} %if any
 The framework can significantly reduce the workload required to conduct
@@
 
-\keywords{
-    Systematic review automation
-   \and
-    Citation management
-   \and
-    Online data collection
-   \and
-    Active machine learning
-   \and
-    Natural language processing
-   \and
-    Bayesian modeling
-  }
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The keywords begin here                  %%
+%%                                          %%
+%% Put each keyword in separate \kwd{}.     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{keyword}
+	\kwd{Systematic review automation}
+	\kwd{Citation management}
+	\kwd{Online data collection}
+	\kwd{Active machine learning}
+	\kwd{Natural language processing}
+	\kwd{Bayesian modeling}
+% \kwd{sample}
+% \kwd{article}
+% \kwd{author}
+\end{keyword}
+
+% MSC classifications codes, if any
+%\begin{keyword}[class=AMS]
+%\kwd[Primary ]{}
+%\kwd{}
+%\kwd[; secondary ]{}
+%\end{keyword}
+
+\end{abstractbox}
+%
+ %a  \end{fmbox} %uncomment this for two column layout
+
+\end{frontmatter}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                            %%
+%% The Main Body begins here                  %%
+%%                                            %%
+%% Please refer to the instructions for       %%
+%% authors on:                                %%
+%% https://www.biomedcentral.com/getpublished %%
+%% and include the section headings           %%
+%% accordingly for your article type.         %%
+%%                                            %%
+%% See the Results and Discussion section     %%
+%% for details on how to create sub-sections  %%
+%%                                            %%
+%% use \cite{...} to cite references          %%
+%%  \cite{koon} and                           %%
+%%  \cite{oreg,khar,zvai,xjon,schn,pond}      %%
+%%                                            %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
+% <put your article body there>
+
+%%%%%%%%%%%%%%%%
+%% Background %%
+%%
+
+\section*{Background}
+\addcontentsline{toc}{section}{Background}
 
 Scientific production has experienced continuous exponential growth in
-the last decades (Larsen and Von Ins 2010; Bornmann and Mutz 2015). This
-is especially true for biomedical research, a trend further accelerated
-by the COVID-19 pandemic, thanks to faster article processing time by
-publishers and the greater use of preprint databases (Aviv-Reuven and
-Rosenfeld 2021; Horbach 2020; Hoy 2020). Consequently, it has become
-harder for researchers and practitioners to stay up to date on the
-latest findings in their field. Secondary research is of paramount
-importance in this scenario in that it provides valuable summaries of
-the latest research results; however, it is becoming ever more
-challenging in terms of time and human resources required (Allen and
-Olkin 1999; Borah et al. 2017; A. M. Cohen et al. 2010; Bastian,
-Glasziou, and Chalmers 2010).\\
+the last decades \citep{larsen2010rate, bornmann2015growth}. This is
+especially true for biomedical research, a trend further accelerated by
+the COVID-19 pandemic, thanks to faster article processing time by
+publishers and the greater use of preprint databases
+\citep{aviv2021publication, horbach2020pandemic, hoy2020rise}.
+Consequently, it has become harder for researchers and practitioners to
+stay up to date on the latest findings in their field. Secondary
+research is of paramount importance in this scenario in that it provides
+valuable summaries of the latest research results; however, it is
+becoming ever more challenging in terms of time and human resources
+required
+\citep{allen1999estimating, borah2017analysis, cohen2010evidence, bastian2010seventy}.\\
 The article collection and screening phases of a systematic review are
-particularly demanding (Babar and Zhang 2009). First, relevant published
-research must be collected from scientific databases using appropriately
-built search queries (retrieval phase); secondly, the scientific
-citations collected must be screened, selecting only those that are
-relevant to the topic (appraisal phase) (Bannach-Brown et al. 2019;
-Tsafnat et al. 2014; Higgins et al. 2019).\\
-Search queries construction is a complex task (Lefebvre et al. 2011;
-Hammerstrøm et al. 2010), requiring both expertise in the scientific
-field of interest and some knowledge of the database query languages.
-The goal is to obtain a set of results that contains all relevant
-articles (high sensitivity) while keeping the total number of records
-low (high specificity), possibly focusing on the first at the expense of
-the second (Hammerstrøm et al. 2010).\\
+particularly demanding \citep{babar2009systematic}. First, relevant
+published research must be collected from scientific databases using
+appropriately built search queries (retrieval phase); secondly, the
+scientific citations collected must be screened, selecting only those
+that are relevant to the topic (appraisal phase)
+\citep{bannach2019machine, tsafnat2014systematic, higgins2019cochrane}.\\
+Search queries construction is a complex task
+\citep{lefebvre2011searching, hammerstrom2010searching}, requiring both
+expertise in the scientific field of interest and some knowledge of the
+database query languages. The goal is to obtain a set of results that
+contains all relevant articles (high sensitivity) while keeping the
+total number of records low (high specificity), possibly focusing on the
+first at the expense of the second \citep{hammerstrom2010searching}.\\
 If an integrated search tool is not used, manual work is required to
@@
 any one time and the need to harmonise different formats and resolve
-record duplication (Marshall and Wallace 2019).\\
+record duplication \citep{marshall2015systematic}.\\
 The citation screening phase is usually the more resource-demanding task
@@
 the results may easily range in the tens of thousands, of which just a
-small fraction are actually relevant (Lefebvre et al. 2011). It has been
-estimated that labelling 10,000 publications can take up to 40 weeks of
-work and that the average clinical systematic review takes 63 weeks to
-complete (Bannach-Brown et al. 2019; Borah et al. 2017; Allen and Olkin
-1999). A consequence of this is that systematic reviews are often
-already out-of-date by the time they are published (E. M. Beller et al.
-2013).\\
+small fraction are actually relevant \citep{lefebvre2011searching}. It
+has been estimated that labelling 10,000 publications can take up to 40
+weeks of work and that the average clinical systematic review takes 63
+weeks to complete
+\citep{bannach2019machine, borah2017analysis, allen1999estimating}. A
+consequence of this is that systematic reviews are often already
+out-of-date by the time they are published
+\citep{beller2013systematic}.\\
 The field of Data Science applied to evidence synthesis and acquisition
-has greatly maturated in the last years (Marshall and Wallace 2019; E.
-Beller et al. 2018; Tsafnat et al. 2014). By applying natural language
-processing (NLP), it is possible to transform free text into
-quantitative features, with various levels of abstraction and
-generalisation (Ananiadou and McNaught 2006; K. B. Cohen and Hunter
-2008); using machine learning, such text-derived data can be used to map
-and reproduce human judgment, automating the screening of citations
-(Ikonomakis, Kotsiantis, and Tampakas 2005).\\
+has greatly maturated in the last years
+\citep{marshall2015systematic, beller2018making, tsafnat2014systematic}.
+By applying natural language processing (NLP), it is possible to
+transform free text into quantitative features, with various levels of
+abstraction and generalisation
+\citep{ananiadou2006text, cohen2008getting}; using machine learning,
+such text-derived data can be used to map and reproduce human judgment,
+automating the screening of citations \citep{ikonomakis2005text}.\\
 Automation of systematic reviews has made significant improvements in
-the last years (Ananiadou et al. 2009; O'Mara-Eves et al. 2015; Tsafnat
-et al. 2013; Jonnalagadda, Goyal, and Huffman 2015), and it is possible
-foreseeable that it will become the standard approach in the field (E.
-Beller et al. 2018), with many solutions already being implemented into
-commercial or free-to-use tools (see Marshall and Wallace 2019, table
-1).\\
+the last years
+\citep{ananiadou2009supporting, o2015using, tsafnat2013automation, jonnalagadda2015automating},
+and it is possible foreseeable that it will become the standard approach
+in the field \citep{beller2018making}, with many solutions already being
+implemented into commercial or free-to-use tools \citep[see][table
+1]{marshall2015systematic}.\\
 This manuscript introduces an open-source, production-ready framework
@@
 For the citation screening (appraisal) phase, we built an active machine
-learning-based protocol (Settles 2009; Miwa et al. 2014), which utilises
-a Bayesian framework to efficiently identify potentially relevant
-documents that require human review while automatically screening-out
-the vast majority of clearly non-relevant ones; the algorithm then
-requires human review to increase classification accuracy iteratively.
-Finally, we included a tool to generate new search queries based on an
-already categorised citation data set, to identify relevant research
-that manually-made queries may have possibly missed.\\
+learning-based protocol \citep{settles2009active, miwa2014reducing},
+which utilises a Bayesian framework to efficiently identify potentially
+relevant documents that require human review while automatically
+screening-out the vast majority of clearly non-relevant ones; the
+algorithm then requires human review to increase classification accuracy
+iteratively. Finally, we included a tool to generate new search queries
+based on an already categorised citation data set, to identify relevant
+research that manually-made queries may have possibly missed.\\
 We tested the framework in the retrieval and appraisal phases of an
@@
 their impact on the diffusion of healthcare-associated pathogenic
-microorganisms; the protocol is published in (Sadaghiani et al. 2020).\\
+microorganisms; the protocol is published in \citep{newis}.\\
 In the Methods, we give an overview of the framework, in the Result, we
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{general-description}{%
-\subsection{General description}\label{general-description}}
-
-We built an R (R Core Team 2020) based framework to simplify two aspects
+\section*{Methods}
+\addcontentsline{toc}{section}{Methods}
+
+\subsection*{General description}
+\addcontentsline{toc}{subsection}{General description}
+
+We built an R \citep{rstats2021} based framework to simplify two aspects
 of systematic literature review: record acquisition and classification.
 The code used to generate the results is available at
-\url{https://github.com/AD-Papers-Material/BART_SystReviewClassifier},
-while an updated and ready to use version of the framework is
-distributed as an R package at
-\url{https://github.com/bakaburg1/BaySREn}. The framework includes
-several modules that communicate through intermediate outputs stored in
-standard formats, making it possible for users to extend the framework
-or easily integrate it with other tools in their pipeline. See
+https://github.com/AD-Papers-Material/BART\_SystReviewClassifier, while
+an updated and ready to use version of the framework is distributed as
+an R package at https://github.com/bakaburg1/BaySREn. The framework
+includes several modules that communicate through intermediate outputs
+stored in standard formats, making it possible for users to extend the
+framework or easily integrate it with other tools in their pipeline. See
 Supplemental Material S1 for an in-depth description of the framework
@@
 
-\begin{figure}
-\includegraphics[width=1\linewidth]{methods_diagram} \caption{Figure 1. Framework's visual representation.}\label{fig:method_diagram}
-\end{figure}
-
-\hypertarget{record-acquisition-and-initial-labelling}{%
-\subsection{Record acquisition and initial
-labelling}\label{record-acquisition-and-initial-labelling}}
+\subsection*{Record acquisition and initial labelling}
+\addcontentsline{toc}{subsection}{Record acquisition and initial
+labelling}
 
@@
 Pubmed since the API and the web interface have different rule expansion
-algorithms and return slightly different results ({`NCBI Insights :
-Updated Pubmed e-Utilities Coming in April 2022!'}, n.d.). A short guide
-on how to set up the framework for each database supported is available
-in Supplemental Material S3.\\
+algorithms and return slightly different results \citep{pubmedUpdate}. A
+short guide on how to set up the framework for each database supported
+is available in Supplemental Material S3.\\
 The collected records are merged into a single database, resolving
@@
 ``hyperparameter optimisation'' later). Simple query ordering increases
-the positivity rate in the initial training set (Wallace, Small, et al.
-2010), leading to higher sensitivity during automatic classification
-(Chawla, Japkowicz, and Kotcz 2004).
-
-\hypertarget{text-feature-extraction}{%
-\subsection{Text feature extraction}\label{text-feature-extraction}}
+the positivity rate in the initial training set
+\citep{wallace2010active}, leading to higher sensitivity during
+automatic classification \citep{chawla2004special}.
+
+\subsection*{Text feature extraction}
+\addcontentsline{toc}{subsection}{Text feature extraction}
 
 The framework models the relevance of a record based on the following
-fields in the citation data: title, abstract, authors, keywords, MESH
-terms (Lipscomb 2000). A range of Natural Language Processing (NLP)
-techniques (Baeza-Yates, Ribeiro-Neto, et al. 1999; Marshall and Wallace
-2019; Ananiadou and McNaught 2006) are employed to convert the textual
-information in these fields into features for machine learning through a
-bag-of-words approach (Marshall and Wallace 2019). Processing of free
-text fields (title, abstract) includes: tokenisation (i.e., extracting
-the terms), removal of common stopwords (i.e., sentence components
-having no semantic value), part-of-speech filtering (only nouns,
-adjectives, verbs and untagged terms are retained), and lemmatisation of
-terms (i.e., reduction to their base grammatical form). Text processing
-for authors, keywords and MESH terms identifies logical units (e.g.,
-authors' full names, composite keywords) and extracts them.\\
+fields in the citation data: title, abstract, authors, keywords, MeSH
+terms \citep{lipscomb2000medical}. A range of Natural Language
+Processing (NLP) techniques
+\citep{baeza1999modern, marshall2015systematic, ananiadou2006text} are
+employed to convert the textual information in these fields into
+features for machine learning through a bag-of-words approach
+\citep{marshall2015systematic}. Processing of free text fields (title,
+abstract) includes: tokenisation (i.e., extracting the terms), removal
+of common stopwords (i.e., sentence components having no semantic
+value), part-of-speech filtering (only nouns, adjectives, verbs and
+untagged terms are retained), and lemmatisation of terms (i.e.,
+reduction to their base grammatical form). Text processing for authors,
+keywords and MeSH terms identifies logical units (e.g., authors' full
+names, composite keywords) and extracts them.\\
 Terms appearing in less than 5\% of the labelled documents are removed
@@
 To detect nc-ngrams, we generated a word network representation
-(Francois Rousseau 2015) with edges occurring between terms with a
+\citep{rousseau2015graph} with edges occurring between terms with a
 cosine similarity in terms of document co-occurrence \textgreater{} 0.5.
-We extracted the maximal cliques in the network (Eppstein, Löffler, and
-Strash 2010) representing highly correlated groups of terms; these
-groups are added to the dataset as individual features. Only nc-ngrams
-comprising a maximum of ten terms are kept.\\
+We extracted the maximal cliques in the network
+\citep{eppstein2010listing} representing highly correlated groups of
+terms; these groups are added to the dataset as individual features.
+Only nc-ngrams comprising a maximum of ten terms are kept.\\
 A second network is built using a co-occurrence threshold of 0.9. In
@@
 
-\hypertarget{label-prediction}{%
-\subsection{Label prediction}\label{label-prediction}}
+\subsection*{Label prediction}
+\addcontentsline{toc}{subsection}{Label prediction}
 
 We used a Bayesian Additive Regression Trees (BART) machine learning
-``classification model'' (Chipman et al. 2010) (in the implementation of
-Kapelner and Bleich 2013) to predict the probability of a record being
-relevant, given the information coded into the enriched DTM and the
-initial training set. We set up the BART model to use 2,000 MCMC
-iterations (after 250 burn-in iterations) and 50 trees; we used a \(k\)
-value of 2 to regularise extreme prediction and let the model use
-missing fields in the DTM as features (Kapelner and Bleich 2015).
-Positive records are oversampled ten times to increase sensitivity
-(Batista, Prati, and Monard 2004).\\
-The output is a posterior predictive distribution (PPD) for each record
-describing the probability of it being relevant (i.e., a positive
-match). An ensemble of ten models was fitted to improve prediction
-stability by averaging the PPD between models (Zhou 2021; Dietterich
-2000).\\
+``classification model'' \citep{chipman2010bart} \citep[in the
+implementation of][]{kapelner2013bartmachine} to predict the probability
+of a record being relevant, given the information coded into the
+enriched DTM and the initial training set. We set up the BART model to
+use 2,000 MCMC iterations (after 250 burn-in iterations) and 50 trees;
+we used a \(k\) value of 2 to regularise extreme prediction and let the
+model use missing fields in the DTM as features
+\citep{kapelner2015prediction}. Positive records are oversampled ten
+times to increase sensitivity \citep{batista2004study}.\\
+The output is the expected value posterior predictive distribution for
+each record (PPD in brief) describing the probability of it being
+relevant (i.e., a positive match). An ensemble of ten models was fitted
+to improve prediction stability by averaging the PPD between models
+\citep{zhou2021ensemble, dietterich2000ensemble}.\\
 
 To assign the labels, we employed an ``active learning'' approach
-(Settles 2009; Miwa et al. 2014), where a human reviews a specific
-subset of predictions made by the machine, which is then retrained on
-the manually reviewed dataset. This process is carried out iteratively
-to reduce prediction uncertainty.\\
+\citep{settles2009active, miwa2014reducing}, where a human reviews a
+specific subset of predictions made by the machine, which is then
+retrained on the manually reviewed dataset. This process is carried out
+iteratively to reduce prediction uncertainty.\\
 Label assignment is done through identification of an ``uncertainty
@@
 
-\[\pi_i = \frac{1}{M}\sum_{j=1}^M Pr(L_i = \text{1}|DTM,m_j)\]
+\[\pi_i = \frac{1}{M}\sum_{j=1}^M Pr(L_i = \text{1}|DTM,m_j) \tag{Eq. 1}\]
 
@@
 \end{aligned}
+\tag{Eq. 2}
 \]
@@
 
-\[U_\pi=[\max\vec{\pi}_{u}^-, \min\vec{\pi}_{l}^+]\]
+\[U_\pi=[\max\vec{\pi}_{u}^-, \min\vec{\pi}_{l}^+] \tag{Eq. 3}\]
 
@@
 
-\[\pi_{i,l} > \max_{\pi \in U_\pi} \pi\]
+\[\pi_{i,l} > \max_{\pi \in U_\pi} \pi \tag{Eq. 4}\]
 
@@
 
-\[\pi_{i,u} < \min_{\pi \in U_\pi} \pi\]
-
-All other records are labelled as ``uncertain''.
+\[\pi_{i,u} < \min_{\pi \in U_\pi} \pi \tag{Eq. 5}\]
+
+The remaining records are labelled as ``uncertain''.
 
@@
 
-\hypertarget{relevant-term-extraction}{%
-\subsection{Relevant term extraction}\label{relevant-term-extraction}}
+\subsection*{Relevant term extraction}
+\addcontentsline{toc}{subsection}{Relevant term extraction}
 
@@
 that is, the proportion of times a term is used in a posterior tree over
-the sum of total inclusions of all variables (Kapelner and Bleich 2013).
-We extracted the terms, the portion of the citation data in which they
-were used, the average ``inclusion rate'' among the ensemble models
-(over 10,000 inclusions) and its ratio over the standard deviation of
-this inclusion (inclusion stability, IS). For each term, we ran a
-Poisson regression to get the linear association with a positive label
-and reported it as Relative Risk (RR) with the number of standard errors
-as significance index (Statistic); the comparison between the inclusion
-rate in the BART models and the linear association allows to spot
-relevant non-linear effects (i.e., the feature is relevant only in
-association with others). In the Results, we only listed the first 15
-terms with IS \textgreater{} 1.5 (in order of inclusion rate), while the
-first fifty terms, regardless of inclusion stability, are listed in
-Supplemental Material S2.
-
-\hypertarget{new-search-query-generation}{%
-\subsection{New search query
-generation}\label{new-search-query-generation}}
+the sum of total inclusions of all variables
+\citep{kapelner2013bartmachine}. We extracted the terms, the portion of
+the citation data in which they were used, the average ``inclusion
+rate'' among the ensemble models (over 10,000 inclusions) and its ratio
+over the standard deviation of this inclusion (inclusion stability, IS).
+For each term, we ran a Poisson regression to get the linear association
+with a positive label and reported it as Relative Risk (RR) with the
+number of standard errors as significance index (Statistic); the
+comparison between the inclusion rate in the BART models and the linear
+association allows to spot relevant non-linear effects (i.e., the
+feature is relevant only in association with others). In the Results, we
+only listed the first 15 terms with IS \textgreater{} 1.5 (in order of
+inclusion rate), while the first fifty terms, regardless of inclusion
+stability, are listed in Supplemental Material S2.
+
+\subsection*{New search query generation}
+\addcontentsline{toc}{subsection}{New search query generation}
 
@@
 \item
-  A partition tree (Therneau and Atkinson 2019) is built between the DTM
-  and 800 samples from the PPD; if a term is present multiple times in
-  the DTM (e.g., both in the title and abstract), it is counted just
-  once, and field term count features are removed. This step generates a
-  list of rules composed by \emph{AND}/\emph{NOT} ``conditions'' made of
-  terms/authors/keywords/MESH tokens, which together identify a group of
+  A partition tree \citep{rpart} is built between the DTM and 800
+  samples from the PPD; if a term is present multiple times in the DTM
+  (e.g., both in the title and abstract), it is counted just once, and
+  field term count features are removed. This step generates a list of
+  rules composed by \emph{AND}/\emph{NOT} ``conditions'' made of
+  terms/authors/keywords/MeSH tokens, which together identify a group of
   records.
@@
 
-\hypertarget{performance-evaluation}{%
-\subsection{Performance evaluation}\label{performance-evaluation}}
+\subsection*{Performance evaluation}
+\addcontentsline{toc}{subsection}{Performance evaluation}
 
@@
 The quality of the model was evaluated through the Bayesian \(R^2\)
-(Gelman et al. 2019), of which we reported the posterior median and 90\%
+\citep{gelman2019r}, of which we reported the posterior median and 90\%
 Credible Interval {[}90\% CrI{]}. The \(R^2\) also provides an
@@
 choosing records randomly; this last quantity is estimated through a
-negative hypergeometric distribution (Chae 1993) over the predicted
-number of positive records.\\
+negative hypergeometric distribution \citep{chae1993presenting} over the
+predicted number of positive records.\\
 For the number of predicted positive records, sensitivity and
@@
 
-\hypertarget{hyperparameter-evaluation}{%
-\subsection{Hyperparameter evaluation}\label{hyperparameter-evaluation}}
+\subsection*{Hyperparameter evaluation}
+\addcontentsline{toc}{subsection}{Hyperparameter evaluation}
 
@@
 \item
-  Oversampling rate of positive records: (1x (i.e., no oversampling),
+  Oversampling rate of positive records: 1x (i.e., no oversampling),
   10x, 20x;
@@
   Source of randomness between models in the ensemble: MCMC sampling
-  only (Robert and Casella 2004), MCMC plus data bootstrapping (Breiman
-  1996) of the training set.
+  only \citep{robert2004monte}, MCMC plus data bootstrapping
+  \citep{breiman1996bagging} of the training set.
 \end{itemize}
@@
 To evaluate the hyperparameter effect of performance, we set up a ``grid
-search'' (Claesen and De Moor 2015; L. Yang and Shami 2020) on a
+search'' \citep{claesen2015hyperparameter, yang2020hyperparameter} on a
 prelabelled ``validation set'' derived from the first 1,200 records of
@@
 positive records found over the total number of positive records). We
-then used a partition tree (Therneau and Atkinson 2019) to identify
-homogeneous ``performance clusters'' of scores given hyperparameter
-values. For the rest of the study, we used the best hyperparameter set
-in terms of sensitivity followed by efficiency from the cluster with the
-highest average score.\\
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{first-session}{%
-\subsection{First session}\label{first-session}}
+then used a partition tree \citep{rpart} to identify homogeneous
+``performance clusters'' of scores given hyperparameter values. For the
+rest of the study, we used the best hyperparameter set in terms of
+sensitivity followed by efficiency from the cluster with the highest
+average score.\\
+
+\subsection*{Software and data}
+\addcontentsline{toc}{subsection}{Software and data}
+
+The framework is built with R v4.0.4 \citep{rstats2021}. The R packages
+required by the framework are listed at
+https://github.com/bakaburg1/BaySREn/blob/main/DESCRIPTION. All relevant
+data necessary to replicate the results is available at
+https://doi.org/10.5281/zenodo.6323360.
+
+\section*{Results}
+\addcontentsline{toc}{section}{Results}
+
+\subsection*{First session}
+\addcontentsline{toc}{subsection}{First session}
 
@@
 care'' OR ``long-term care'' OR ``healthcare associated'') AND
-(infection OR resistance OR resistant))}
+(infection OR resistance OR resistant))}\\
 
@@
 
-\begin{table}[!h]
-
+The categorised records were used to train the Bayesian classification
+model used to label the remaining records. After seven classification
+and review (CR) iterations (three resulting in new positive matches and
+four extra replications to account for stochastic variability), a total
+of 101 positives matches were found, requiring manual review of 766
+records (13.2\% positivity rate).\\
+It is noticeable how the number of records that required manual review
+decreased rapidly between iterations (Table 2), indicating that the
+engine was converging while the uncertainties were resolved.\\
+This phenomenon is better illustrated in Fig. 1 of Supplemental Material
+S2. It shows the mixture distribution of the PPDs of the records,
+specifically for records that were manually reviewed, before and after
+the classification step: it can be seen how the distribution of
+uncertain records shrinks (i.e., it becomes concentrated in a shorter
+probability range) and shifts toward the negative zone as more positive
+matches are found and reviewed.
+
+We extracted the 15 more relevant terms for the classification model,
+described as: Term (citation part): Inclusion Rate (Inclusion Stability)
+{[}linear Relative Risk, Statistic{]}:\\
+
+Patient Transport (Keyword): 61.2 (3.77) {[}99.1, 21.3{]}, Transfer
+(Abstract): 57 (3.93) {[}22.5, 15.4{]}, Network (Title): 56.5 (2.91)
+{[}18, 14.2{]}, Network \& Patient (Abstract): 54.2 (4.66) {[}26.3,
+15.2{]}, Donker T (Author): 53.5 (4.56) {[}159, 16.5{]}, Worker
+(Abstract): 50 (3.33) {[}0.421, -1.21{]}, Hospitals (Keyword): 49.8
+(4.31) {[}27.8, 16.5{]}, Movement (Abstract): 47.8 (2.7) {[}27.2, 15{]},
+Spread (Title): 46.6 (2.25) {[}16.2, 12.1{]}, Facility (Abstract): 45
+(2.22) {[}19.6, 14.8{]}, Orange County (Keyword): 44.3 (3.19) {[}199,
+17.2{]}, Conduct (Abstract): 42.6 (3.7) {[}0.221, -2.57{]}, Patient
+(Abstract): 42 (3.61) {[}27.6, 7.23{]}, Perform (Abstract): 41.9 (2.38)
+{[}0.342, -2.55{]}, Hospital (Title): 39 (1.95) {[}12.5, 12.5{]}.\\
+
+The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
+documents.\\
+The engine was able to pick up the central concept of the research
+topic, i.e., ``patient transport'' or ``transfer'' through a ``network''
+of ``facility''ies that facilitates the ``spread'' of infections, and
+even one of the authors of this study (Donker T.) as well as the region
+of interest (``Orange County'') of another research group active on the
+topic of pathogen spreading over hospital networks. Some terms were
+considered highly relevant by the BART models (e.g., ``Worker'' in the
+sixth position out of more than 3800 terms considered), although in a
+simple linear model, their effect would hardly be significant
+(statistic: -1.21 s.e.); these are terms that are only relevant in
+conjunction with other terms but not on their own, highlighting the
+extra predictive power achieved through the use of advanced, non-linear
+machine learning.\\
+A more extensive set of terms is presented in Table 1 of Supplemental
+Material S2.
+
+\subsection*{Second session}
+\addcontentsline{toc}{subsection}{Second session}
+
+The results of the first classification session were used to create a
+second, data-driven query to perform a more extensive search to find
+records that may have been missed during the first search session. The
+resulting query was as follows:\\
+
+\emph{(((Donker T) NOT (bacterium isolate)) OR ((network patient) AND
+(resistant staphylococcus aureus) NOT (monte carlo) NOT isolation) OR
+(facility AND (network patient) AND regional NOT hospitals NOT increase
+NOT (patient transport) NOT (control infection use)) OR ((patient
+transport) NOT (Donker T) NOT worker) OR (hospitals AND (network
+patient) NOT (patient transport) NOT regional NOT clinical) OR (facility
+AND (network patient) NOT hospitals NOT (patient transport) NOT regional
+NOT prevention NOT medical) OR ((healthcare facility) NOT (Donker T) NOT
+worker NOT positive) OR (hospitals NOT (network patient) NOT medical NOT
+environmental NOT outcome NOT global) OR ((network patient) NOT facility
+NOT hospitals NOT (patient transport) NOT therapy NOT global)) AND
+((antimicrobial resistance) OR (healthcare infection))}\\
+
+The final piece \emph{AND ((antimicrobial resistance) OR (healthcare
+infection)} was added manually to define the search domain better since
+the algorithm was trained on documents that were all more or less
+related to these topics.\\
+The generated query also provides a more nuanced understanding of the
+engine's internal classification logic, and this is helpful to spot
+possible biases in the model.\\
+
+The search was done with the same year filter and procedures used in the
+first session.\\
+
+The new search produced 107,294 records (Table 1), of which 48,396
+(58.6\%) from the EMBASE, followed by 28,811 (34.9\%) from Pubmed,
+17,070 (20.7\%) from SCOPUS, 12,956 (15.7\%) from WOS, and 61 (0.074\%)
+from IEEE; compared with the first session, the relative weight of
+EMBASE and Pubmed decreased, while the level of content specificity
+greatly increased, as it was for SCOPUS. After removal of duplicates,
+82,579 unique records were obtained. The newly collected records were
+joined with those from the first session and duplicates were removed. We
+obtained 98,371 unique records, with just 1,963 shared records between
+searches, which equates to 2\% of the total. The percentage of records
+shared by two or more sources dropped to 22\%.
+
+Six CR rounds were necessary to complete the second session
+classification, with just 6 new positive found after reviewing 568 extra
+records. The first CR iteration required the user to review a
+substantial number of records (1,273); however, just labelling 275 of
+them (the suggested 250 plus 25 already labelled for the framework
+hyperparameter tuning) was sufficient to reduce this number to just 190
+in the subsequent round. An evaluation of the convergence (Supplemental
+Material S2, Fig. 1) showed that, in addition to the dynamics already
+observed in session 1 (shrinkage and negative shift), a second mode
+appeared in the mixture distribution of the records to be reviewed,
+centred in a highly positive zone. The interpretation is that as the
+number of negative training records increases, the engine becomes more
+and more sceptical and even asks to review some records labelled as
+positive in the initial training set generated during Session 1. This
+behaviour can rev spot classification errors and inconsistencies.
+Considering both sessions, 1,333 records were manually reviewed and 107
+(8.03\%) confirmed positive matches were found.
+
+Again, the evaluation of the inclusion rate of the terms showed that the
+engine is quite capable of internalising the concepts behind the
+research topic. A subsample of the relevant terms used by the model in
+the second session is reported in Table 2 of Supplemental Material S2.
+
+\subsection*{Hyperparameter selection}
+\addcontentsline{toc}{subsection}{Hyperparameter selection}
+
+As described in the methods, hyperparameters were selected by evaluating
+sensibility and efficiency through a grid search on a validation set of
+1,200 manually labelled records. The analysis suggested that the
+following parameter combination performed best: an initial training set
+of 250 categorised records with 10x oversampling of positive matches,
+ten models in the ensemble, no bootstrapping and an uncertainty zone
+defined by the 98\% predictive interval. This combination of parameters
+was associated with a sensitivity of 98.8\% (81 / 82 positive matches
+found) and an efficiency of 61.5\% (462 / 1200 records evaluated). The
+detailed results of the hyperparameter tuning analysis are reported in
+Table 3 of Supplemental Material S2. Fig. 2 in Supplemental Material S2
+demonstrates that the positive record oversampling rate, the number of
+ensemble models and the size of the initial training set were the
+parameters that mainly impacted performance.
+
+\subsection*{Performance evaluation}
+\addcontentsline{toc}{subsection}{Performance evaluation}
+
+To evaluate the theoretical performance of the engine, a surrogate
+Bayesian logistic regression model was trained on the manually reviewed
+labels using only the lower boundary of the record PPDs as predictor
+(see the Methods for details). The surrogate model showed the high
+predictive power of the scores produced by the classification model
+(Bayesian R2: 98.1\% {[}97.4\%, 98.3\%{]} for session 1 and 98.2\%
+{[}97.6\%, 98.3\%{]} for session 2).\\
+
+Fig. 2 presents the actual and predicted (from the surrogate model)
+cumulative number of positive matches, ordered by the initial simple
+ordering query: the median of surrogate models' cumulative predictive
+distributions matches the actual number of positive records found quite
+well. It is striking how many more records would have required manual
+evaluation to find the same number of positive matches without a
+classification algorithm, with some positive matches found close to the
+end of the heuristically ordered list of records.\\
+
+Table 3 shows various performance indexes for both sessions, both
+descriptive (Total records, Reviewed records, Observed positive matches)
+and estimated through the surrogate model (Expected efficiency,
+Predicted positive matches, Expected sensitivity, \(R^2\)).\\
+In session 1 we observe an expected total number of positives of 101
+{[}101, 108{]} for an estimated sensitivity of 100\% {[}93.5\%, 100\%{]}
+and efficiency of 95.6\% {[}95.3\%, 95.7\%{]}. In session 2 we observed
+a drop in expected sensitivity, especially in the lower credibility
+boundary (97.3\% {[}72.8\%, 100\%{]}): as the number of records
+increases, even a small probability of being a positive match can, in
+the worst-case scenario, lead to a relevant number of predicted positive
+matches (147 in this case). To ensure no obvious positive matches were
+missed, we evaluated 100 non-reviewed records with the highest median
+predicted probability and found no additional positive matches.\\
+
+\section*{Discussion}
+\addcontentsline{toc}{section}{Discussion}
+
+We propose a new integrated framework to help researchers collect and
+screen scientific publications characterised by high performance and
+versatility. This framework joins the joining the growing field of
+systematic review automation (SRA) and helpers (SRH) tools
+\citep{cohen2006reducing, cohen2010evidence, ananiadou2009supporting, o2015using}.
+This framework implements standard approaches and uses ad-hoc solutions
+to common SRA issues. By freely sharing the tool as an open-source R
+package and by following a modular design, we sought to adopt some of
+the so-called Vienna Principles advocated by the International
+Collaboration for the Automation of Systematic Reviews (ICASR)
+\citep{beller2018making}.\\
+The framework consists of four main components: 1) an integrated
+query-based citation search and management engine, 2) a Bayesian active
+machine learning-based citation classifier, and 3) a data-driven search
+query generation algorithm.\\
+
+The search engine module used by the framework can automatically collect
+citation data from three well-known scientific databases (i.e., Pubmed,
+Web of Science, and the Institute of Electrical and Electronics
+Engineers) and process manually downloaded results from two more sources
+(SCOPUS, EMBASE). In comparison, most commercial or free SRH tools rely
+on internal databases (e.g., Mendeley https://www.mendeley.com/)
+sometimes focusing only on a particular topic
+\citep{visser2010performing} or a single external data source
+\citep{thomas2007eppi, poulter2008mscanner, soto2019thalia}.\\
+Mixing different databases is essential to obtain a more comprehensive
+view of the literature
+\citep{bajpai2011search, wilkins2005embase, woods1998medline}: in our
+results, 18.7\% of the positive matches were found in only one of the
+different data sources, and no positive record was present in all the
+sources (data not shown).\\
+The framework online search algorithms are efficient enough to manage
+tens of thousands of search results, using various solutions to overcome
+the limitations of citation databases in terms of traffic and download
+quotas. The results are then automatically organised, deduplicated and
+arranged by ``simple query ordering'' in a uniform corpus. The
+preliminary ordering increases the positivity rate in the initial
+training set \citep{wallace2010active}.\\
+
+For the framework's record screening module, we developed an active
+machine learning protocol \citep{settles2009active, miwa2014reducing}
+based on the best practices from other SRA studies, bringing further
+improvements at various levels.\\
+The feature extractor module uses modern NLP techniques
+\citep{ananiadou2006text, cohen2008getting} to transform free text into
+input data for machine learning. We did not include classical n-grams
+\citep{schonlau2017text}; rather, we used network analysis to find
+non-consecutive, frequently associated terms, a generalisation of
+n-grams that relaxes the term adjacency assumption. This approach can
+also incorporate term connections across different parts of the records,
+e.g., terms having a different relevance when associated with a
+particular author. The same technique was used with different parameters
+to merge redundant terms, increasing estimation efficiency and reducing
+noise.\\
+The use of concurrency network-driven text modelling is not new
+\citep{rousseau2015graph, violos2016sentiment, rousseau2015text, ohsawa1998keygraph}
+and is a valuable tool to extract semantic information that is not
+evident in one-word or consecutive n-gram models.\\
+
+The automatic classification algorithm is based on Bayesian Additive
+Regression Trees (BART)
+\citep{chipman2010bart, kapelner2013bartmachine}. Like other boosted
+trees algorithms \citep{hastie2009boosting}, the BART method can explore
+complex non-linearities, perform variable selection, manage missing data
+while maintaining high predictive power.\\
+However, the Bayesian foundation of the method provides further
+benefits: lower sensitivity to the choice of hyperparameters, natural
+regularisation through priors, and, most importantly, predictive
+distributions as output instead of point-wise predictions
+\citep{soria2011belm, joo2020being, jospin2020hands}. By selecting
+relatively tight prior distributions, we discouraged overly deep trees,
+long tree sequences, and extreme predicted probabilities, thus reducing
+the risk of overfitting.\\
+The algorithm runs multiple replications of the model and averages their
+predictive distributions creating an ``ensemble''; this technique has
+been shown to improve out-of-sample predictive performance
+\citep{zhou2021ensemble, dietterich2000ensemble}, as confirmed during
+the hyperparameter evaluation (Supplemental Material S2). Ensembling
+reduces the uncertainty in the predictive distribution tails related to
+the randomness in the MCMC fit \citep{robert2004monte}, generating a
+shift in the probability mass towards the distribution centre and
+stabilising it (i.e., reducing variance without impacting bias). On the
+other hand, simply imposing more robust uninformative priors against
+extreme predictions would have reduced variance but also shifted the
+distribution towards a non-decision zone, increasing bias
+\citep{hansen2000bayesian}.\\
+Since the number of model replications has a significant impact on
+computation times, we decided to use ten replicas, the lower value after
+which performance stabilised, as resulted from the evaluation of the
+hyperparameters (Supplemental Material S2, Fig. 2).\\
+We also investigated whether bootstrapping between replications
+\citep{breiman1996bagging} would improve performance; however, contrary
+to theory \citep{diez2015diversity}, it appeared to be slightly
+detrimental in our case (Supplemental Material S2, Fig. 2) compared to
+simple ensembling.\\
+
+A low proportion of relevant matches (class imbalance) is typical for
+literature reviews
+\citep{sampson2011precision, wallace2010semi, o2015using}, and a strong
+imbalance between positive and negative records can affect sensitivity
+\citep{khoshgoftaar2010comparing, chawla2004special}.\\
+To overcome this problem, we oversampled \citep{batista2004study} the
+positive records ten times before model fitting. The hyperparameter
+analysis showed that the oversampling rate, together with model
+ensembling, was the parameter with the most significant impact on
+performance.\\
+A known risk with positive oversampling is the misclassification of
+negative records \citep{ramezankhani2016impact}. However, since all
+predicted positives in our approach are reviewed manually, we are always
+guaranteed to achieve 100\% specificity/positive predictive value: the
+only price for the increased sensitivity due to oversampling is a larger
+number of records to be reviewed.\\
+An alternative to oversampling would be to apply different weights
+and/or costs to the classes \citep{abd2013review, diez2015diversity},
+but the BART implementation we used did not have this feature;
+furthermore, using simple oversampling allows for a broader
+compatibility with different modelling engines
+\citep{galar2011review, roshan2020improvement}.\\
+Finally, sorting the records by query term frequency (simple query
+ordering) produces a much higher rate of relevant records in the initial
+training set (17.2\%) compared to the overall data (0.11\%), which
+boosts the sensitivity of the model.\\
+
+One of the key innovations we have introduced is the concept of
+``uncertainty zone'', the implementation of which is possible thanks to
+the Bayesian foundation of the classification model.\\
+This construct guides the selection of records to be manually reviewed
+and gets dynamically updated and reduced after each CR iteration, as
+more uncertain predictions are evaluated (Supplemental Material S2 Fig.
+1).\\
+The use of a dynamic uncertainty zone overcomes the usual requirement of
+dataset-specific hard thresholds in active machine learning and allows
+to review multiple items at once between iterations
+\citep{laws2008stopping, miwa2014reducing, zhu2010confidence}. The
+hyperparameters required by our algorithm are general and
+non-task-specific, like the PPD intervals underlying the uncertainty
+zone and the maximum number of iterations without positive matches after
+which a session is concluded; the evaluation of the classification model
+hyperparameters shows that the algorithm is robust against variations in
+these parameters, and we expect the default values to perform well on
+most datasets.\\
+Since researchers are asked to review both records predicted as surely
+relevant and those inside the uncertainty zone, this method can be
+considered as a unifying synthesis of the ``certainty'' and
+``uncertainty'' paradigms of active learning \citep{miwa2014reducing}.\\
+
+We assessed performance as the ability of the screening procedure
+(automatic classification plus manual review) to find the largest number
+of relevant records while requiring manual reviewing for as few of them
+as possible (i.e., sensitivity \(\times\) efficiency).\\
+We avoided the classical out-of-sample approaches such as train-test
+sampling, out-of-bag bootstrapping or cross-validation
+\citep{kohavi1995study, james2013introduction}. Such methods primarily
+assume that the rate of positivity is the same on average in every
+possible random subset of the data \citep{tashman2000out}; this
+uniformity is broken by how the initial training set and the subsequent
+reviewed records are selected by the query-based ordering and active
+learning algorithm, resulting in a lower positivity rate in the
+unlabelled records (Fig. 2). Moreover, a literature corpus is unique per
+search query/database combination, and therefore any out-of-sample
+performance estimate is not replicable since no new data can be acquired
+related to the current corpus.\\
+To estimate overall sensitivity, we instead applied simple Bayesian
+regression (surrogate model) to the manually reviewed data to abstract
+the classification model predictions and generate a maximum entropy
+\citep{harremoes2001maximum} estimate of the number of missed positive
+matches among the unreviewed records in the whole dataset. This simple
+surrogate model fitted the data very well (\(R^2\) consistently above
+97\%) using only the lower 98\% PrI boundary of the PPDs as predictor,
+indicating predictive consistency in the classification model. The
+posterior predictive distribution of the surrogate model could be used
+to explore worse case scenarios in terms of sensitivity.\\
+
+Our framework achieves very high sensitivity by screening only a very
+small fraction of all records, bringing a meaningful reduction in
+workload.\\
+Based on the surrogate model, we predicted a predicted median
+sensitivity of 100\% {[}93.5\%, 100\%{]} in the first session (screening
+4.29\% of records) and of 97.3\% {[}73.8\%, 100\%{]} in the second
+(screening 1.34\% of records): efficiency increased significantly in the
+second session as only a few new positive matches were found; however,
+given the large number of records, uncertainty about sensitivity
+increased, as expected.\\
+Both results are above the usual performance in this field
+\citep{o2015using} and are in line with the average sensitivity of 92\%
+estimated after human-only screening \citep{edwards2002identification}.
+In one interesting case, the model detected a human-caused
+misclassification error, demonstrating its robustness and value as a
+second screener, a role already suggested for SRA tools in previous
+studies
+\citep{frunza2010building, bekhuis2012screening, bekhuis2010towards}.
+Although ``simple query ordering'' concentrated most relevant matches in
+the first 20-25 thousand records, without the tool support, the
+remaining relevant records would have been missed without manually
+screening almost the entire dataset.\\
+
+The model required \textasciitilde5-20 minutes per iteration to perform
+the predictions in session 1 (17,755 documents) and 20-40 minutes in
+session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM, 2014
+laptop; including manual record review, one session required 1-3 days of
+work, for a total of 1-2 weeks for the whole process (including record
+collection). This is a considerable time saving compared to the several
+months typically required for the screening phase of systematic reviews
+\citep{bannach2019machine, borah2017analysis, allen1999estimating}. To
+our knowledge, the amount of data processed (\textasciitilde100,000
+records) was larger than what is typical of most SRA studies
+\citep{o2015using, olorisade2016critical}, highlighting the scalability
+of the tool in real-world scenarios.\\
+
+The last module of our framework is an algorithm for data-driven search
+query generation. Generating an efficient and effective search query is
+a complex task \citep{lefebvre2011searching, hammerstrom2010searching};
+it requires building a combination of positive and negative terms to
+maximise the number of relevant search results while minimising the
+total number of records to be reviewed. Our solution combines a
+sensitivity-driven subquery proposal engine based on concurrent decision
+trees \citep{blanco2019machine, moore2018transparent} built on the BART
+ensemble PPD, with a human review step and an efficiency-driven query
+builder. The aim is to generate a new search query to help find records
+missed in the first search session. The generated query did indeed
+retrieve a few more relevant records not found in session 1 but at the
+cost of significantly increasing the number of documents.\\
+An interesting aspect of this feature is that it provides a
+human-readable overview of the classification rules learned by the
+classification model, showing which combination of terms was
+particularly relevant and even spotting authors and geographical
+locations associated with the study topic. The generated query,
+therefore, served also as a means for machine learning explainability
+\citep{bhatt2020machine, burkart2021survey}, useful for understanding
+and detecting biases in black-box classification algorithms
+\citep{malhi2020explainable}; explainability is often required or even
+legally mandatory for high-stake machine learning applications
+\citep{bibal2021legal, bibal2020impact}.\\
+It is important to note that this process is entirely data-driven. The
+algorithm is only aware of the ``world'' defined by the dataset used as
+input, which is generated by a specific search query focused on a
+particular topic. Therefore, the new query may not be specific enough
+when applied to an unbounded search domain and may return an
+unmanageable amount of irrelevant results. The solution we found was to
+add another component to the query, specifying the general topic
+(antimicrobial resistance and healthcare-associated infections) of our
+research.\\
+
+As mentioned early, our framework builds on modularity. We have designed
+so that each module can become fully independent in future iterations;
+it will be possible for users to add custom features such as citation
+search and parsing for other scientific databases, alternative text
+processing algorithms or machine learning modules. We consider such
+interoperability to be extremely relevant: the main strength of our tool
+lies in the composition of many independent solutions, such as the idea
+of Bayesian active machine learning and the exploit of the derived
+uncertainty in defining the records needing human review.\\
+Each component could benefit considerably from the recent improvements
+in text mining and machine learning.\\
+For example, the text processing approach based on the ``boolean
+bag-of-words'' paradigm is quite simple and could be improved by more
+nuanced text representations. It might be considered whether feature
+transformations such as TF-IDF
+\citep{baeza1999modern, ananiadou2006text} could be advantageous,
+although we hypothesise that tree-based classification algorithms like
+BART are robust enough not to require such operations. Instead, it might
+be worth exploring the application of word embedding: this technique
+transforms terms into semantic vectors derived from the surrounding text
+\citep{turian2010word, bollegala2015embedding, minaee2021deep} and could
+be used to reduce noise by merging different terms that are semantically
+similar or enhance signal by distinguishing identical terms with
+different meaning given the context. Another option would be to employ
+unsupervised learning models like Latent Dirichlet Analysis and Latent
+Semantic Analysis,
+\citep{pavlinek2017text, chen2016short, landauer1998introduction} or
+graph-of-word techniques \citep{ohsawa1998keygraph, rousseau2015graph}
+to extract topics that expand the feature space.\\
+Our classification algorithm is applicable with any Bayesian supervised
+machine learning method that provides full PPDs; therefore, alternative
+classification models, such as Gaussian Processes, known for their
+flexibility \citep{jayashree2020evaluation, chen2015gaussian}, could be
+evaluated. It would be even more interesting to test advanced learning
+algorithms that go beyond the bag-of-words approach and take into
+consideration higher-level features in the text such as term context and
+sequences, long-distance term relationships, semantic structures, etc.,
+\citep{cheng2019document, minaee2021deep, li2020survey, yang2020survey, lai2015recurrent, farkas1995document},
+provided that a Bayesian implementation of such algorithms is available
+(for example \citet{chen2018approximate}).\\
+Finally, a natural improvement would be to provide a graphical user
+interface to make the framework easy to use also for less technical
+users.
+
+The field of literature review automation is evolving rapidly, and we
+anticipate an increasing use of such technologies to address the
+accelerating pace of scientific production. We believe it is encouraging
+that a wide variety of tools are being made available to let researchers
+and policymakers find the approach that best fits their needs.\\
+We contribute to this field with an innovative framework that provides
+excellent performance and easy integration with existing systematic
+review pipelines. The value of this work lies not only in the framework
+itself, which we make available as open-source software, but also in the
+set of methodologies we developed to solve various SRA issues and which
+can also be used to improve existing solutions.\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Backmatter begins here                   %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{backmatter}
+
+\section*{Acknowledgements}%% if any
+We would like to thank Deborah Lawrie-Blum and Fabian Bürkin
+respectively for English language proofreading and mathematical
+formalization proof check.
+
+\section*{Abbreviations}%% if any
+API: Application Programming Interface; BART: Bayesian Additive
+Regression Trees; COVID-19: Coronavirus Disease 2019; CR: Classification
+\& Review; DTM: Document-Term Matrix; ICASR: International Collaboration
+for the Automation of Systematic Reviews; IEEE: Institute of Electrical
+and Electronics Engineers; IS: Inclusion Stability; MCMC: Monte Carlo
+Markov Chain; MeSH: Medical Subject Headings; MCMC: Monte Carlo Markov
+Chain; NLP: Natural Language Processing; PPD: Expected Value Posterior
+Predictive Distribution; RR: Relative Risk; SRA: Systematic Review
+Automation; SRH: Systematic Review Helpers; TF-IDF: Term Frequency -
+Inverse Document Frequency; WOS: Web Of Science; WSoR: Work Saved over
+Random.
+
+\vspace{2em}
+\section*{Declarations}
+\vspace{1em}
+
+\section*{Funding}%% if any
+This project was developed under the Joint Programming Initiative on
+Antimicrobial Resistance (JPIAMR) through the 7th call, project number
+01KI1831 funded by BMBF and administrated by DLR Project Management
+Agency.
+
+\section*{Availability of data and materials}%% if any
+The code and the instructions necessary to reproduce the results are
+available at
+https://github.com/AD-Papers-Material/BART\_SystReviewClassifier. An
+updated, ready-to-use version of the framework is available at
+https://github.com/bakaburg1/BaySREn. All relevant data necessary to
+replicate the results is available at:
+https://doi.org/10.5281/zenodo.6323360.
+
+\section*{Ethics approval and consent to participate}%% if any
+Not applicable.
+
+\section*{Competing interests}
+The authors declare no competing interests.
+
+\section*{Consent for publication}%% if any
+Not applicable.
+
+\section*{Authors' contributions}
+Conceptualization: AD, TD; Data curation: AD; Formal analysis \&
+Methodology: AD; Project administration: AD, TD; Software development:
+AD; Supervision: TD, HG; Writing--original draft: AD, TD;
+Writing--review \& editing: AD, TD, HG. All authors have read and
+approved the manuscript.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                  The Bibliography                       %%
+%%                                                         %%
+%%  Bmc_mathpys.bst  will be used to                       %%
+%%  create a .BBL file for submission.                     %%
+%%  After submission of the .TEX file,                     %%
+%%  you will be prompted to submit your .BBL file.         %%
+%%                                                         %%
+%%                                                         %%
+%%  Note that the displayed Bibliography will not          %%
+%%  necessarily be rendered by Latex exactly as specified  %%
+%%  in the online Instructions for Authors.                %%
+%%                                                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% if your bibliography is in bibtex format, use those commands:
+\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
+
+\phantom{\citet{d2022open}, \citet{zenododata}}
+
+\bibliography{references.bib}      % Bibliography file (usually '*.bib' )
+% for author-year bibliography (bmc-mathphys or spbasic)
+% a) write to bib file (bmc-mathphys only)
+% @settings{label, options="nameyear"}
+% b) uncomment next line
+%\nocite{label}
+
+% or include bibliography directly:
+% \begin{thebibliography}
+% \bibitem{b1}
+% \end{thebibliography}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Figures                       %%
+%%                               %%
+%% NB: this is for captions and  %%
+%% Titles. All graphics must be  %%
+%% submitted separately and NOT  %%
+%% included in the Tex document  %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%
+%% Do not use \listoffigures as most will included as separate files
+
+\section*{Figures}
+		\begin{figure}[h!]
+	 \caption*{Figure 1. Framework's visual representation.}
+	\end{figure}
+		\begin{figure}[h!]
+	 \caption*{Figure 2. Observed cumulative number of positive matches
+(red dots) sorted by simple query ordering. The {[}trunc. 90\% PrI{]} of
+the cumulative positive matches estimated by the Bayesian logistic model
+is shown as a shaded area delimited by the 95\% quantile of the PrI and
+by the observed number of positive matches (light blue lines). A darker
+blue line represents the median of the PrI.}
+	\end{figure}
+	%   \begin{figure}[h!]
+%   \caption{Sample figure title}
+% \end{figure}
+%
+% \begin{figure}[h!]
+%   \caption{Sample figure title}
+% \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Tables                        %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Use of \listoftables is discouraged.
+%%
+\section*{Tables}
+	\begin{table}[H]
 \caption{\label{tab:Table 1}\textbf{Table 1}.
@@
 
-The categorised records were used to train the Bayesian classification
-model used to label the remaining records. After seven classification
-and review (CR) iterations (three resulting in new positive matches and
-four extra replications to account for stochastic variability), a total
-of 101 positives matches were found, requiring manual review of 766
-records (13.2\% positivity rate).\\
-It is noticeable how the number of records that required manual review
-decreased rapidly between iterations (Table 2), indicating that the
-engine was converging while the uncertainties were resolved.\\
-This phenomenon is better illustrated in Fig. 1 of Supplemental Material
-S2. It shows the mixture distribution of the PPDs of the records,
-specifically for records that were manually reviewed, before and after
-the classification step: it can be seen how the distribution of
-uncertain records shrinks (i.e., it becomes concentrated in a shorter
-probability range) and shifts toward the negative zone as more positive
-matches are found and reviewed.
-
-\begin{table}[!h]
-
+\begin{table}[H]
 \caption{\label{tab:Table 2}\textbf{Table 2}.
@@
 
-We extracted the 15 more relevant terms for the classification model,
-described as: Term (citation part): Inclusion Rate (Inclusion Stability)
-{[}linear Relative Risk, Statistic{]}.
-
-Patient Transport (Keyword): 61.2 (3.77) {[}99.1, 21.3{]}, Transfer
-(Abstract): 57 (3.93) {[}22.5, 15.4{]}, Network (Title): 56.5 (2.91)
-{[}18, 14.2{]}, Network \& Patient (Abstract): 54.2 (4.66) {[}26.3,
-15.2{]}, Donker T (Author): 53.5 (4.56) {[}159, 16.5{]}, Worker
-(Abstract): 50 (3.33) {[}0.421, -1.21{]}, Hospitals (Keyword): 49.8
-(4.31) {[}27.8, 16.5{]}, Movement (Abstract): 47.8 (2.7) {[}27.2, 15{]},
-Spread (Title): 46.6 (2.25) {[}16.2, 12.1{]}, Facility (Abstract): 45
-(2.22) {[}19.6, 14.8{]}, Orange County (Keyword): 44.3 (3.19) {[}199,
-17.2{]}, Conduct (Abstract): 42.6 (3.7) {[}0.221, -2.57{]}, Patient
-(Abstract): 42 (3.61) {[}27.6, 7.23{]}, Perform (Abstract): 41.9 (2.38)
-{[}0.342, -2.55{]}, Hospital (Title): 39 (1.95) {[}12.5, 12.5{]}.
-
-The ``\&'' indicates nc-ngrams, i.e., terms strongly co-occurrent in the
-documents.\\
-The engine was able to pick up the central concept of the research
-topic, i.e., ``patient transport'' or ``transfer'' through a ``network''
-of ``facility''ies that facilitates the ``spread'' of infections, and
-even one of the authors of this study (Donker T.) as well as the region
-of interest (``Orange County'') of another research group active on the
-topic of pathogen spreading over hospital networks. Some terms were
-considered highly relevant by the BART models (e.g., ``Worker'' in the
-sixth position out of more than 3800 terms considered), although in a
-simple linear model, their effect would hardly be significant
-(statistic: -1.21 s.e.); these are terms that are only relevant in
-conjunction with other terms but not on their own, highlighting the
-extra predictive power achieved through the use of advanced, non-linear
-machine learning.\\
-A more extensive set of terms is presented in Table 1 of Supplemental
-Material S2.
-
-\hypertarget{second-session}{%
-\subsection{Second session}\label{second-session}}
-
-The results of the first classification session were used to create a
-second, data-driven query to perform a more extensive search to find
-records that may have been missed during the first search session. The
-resulting query was as follows:\\
-
-\emph{(((Donker T) NOT (bacterium isolate)) OR ((network patient) AND
-(resistant staphylococcus aureus) NOT (monte carlo) NOT isolation) OR
-(facility AND (network patient) AND regional NOT hospitals NOT increase
-NOT (patient transport) NOT (control infection use)) OR ((patient
-transport) NOT (Donker T) NOT worker) OR (hospitals AND (network
-patient) NOT (patient transport) NOT regional NOT clinical) OR (facility
-AND (network patient) NOT hospitals NOT (patient transport) NOT regional
-NOT prevention NOT medical) OR ((healthcare facility) NOT (Donker T) NOT
-worker NOT positive) OR (hospitals NOT (network patient) NOT medical NOT
-environmental NOT outcome NOT global) OR ((network patient) NOT facility
-NOT hospitals NOT (patient transport) NOT therapy NOT global)) AND
-((antimicrobial resistance) OR (healthcare infection))}
-
-The final piece \emph{AND ((antimicrobial resistance) OR (healthcare
-infection)} was added manually to define the search domain better since
-the algorithm was trained on documents that were all more or less
-related to these topics.\\
-The generated query also provides a more nuanced understanding of the
-engine's internal classification logic, and this is helpful to spot
-possible biases in the model.\\
-
-The search was done with the same year filter and procedures used in the
-first session.\\
-
-The new search produced 107,294 records (Table 1), of which 48,396
-(58.6\%) from the EMBASE, followed by 28,811 (34.9\%) from Pubmed,
-17,070 (20.7\%) from SCOPUS, 12,956 (15.7\%) from WOS, and 61 (0.074\%)
-from IEEE; compared with the first session, the relative weight of
-EMBASE and Pubmed decreased, while the level of content specificity
-greatly increased, as it was for SCOPUS. After removal of duplicates,
-82,579 unique records were obtained. The newly collected records were
-joined with those from the first session and duplicates were removed. We
-obtained 98,371 unique records, with just 1,963 shared records between
-searches, which equates to 2\% of the total. The percentage of records
-shared by two or more sources dropped to 22\%.
-
-Six CR rounds were necessary to complete the second session
-classification, with just 6 new positive found after reviewing 568 extra
-records. The first CR iteration required the user to review a
-substantial number of records (1,273); however, just labelling 275 of
-them (the suggested 250 plus 25 already labelled for the framework
-hyperparameter tuning) was sufficient to reduce this number to just 190
-in the subsequent round. An evaluation of the convergence (Supplemental
-Material S2, Fig. 1) showed that, in addition to the dynamics already
-observed in session 1 (shrinkage and negative shift), a second mode
-appeared in the mixture distribution of the records to be reviewed,
-centred in a highly positive zone. The interpretation is that as the
-number of negative training records increases, the engine becomes more
-and more sceptical and even asks to review some records labelled as
-positive in the initial training set generated during Session 1. This
-behaviour can rev spot classification errors and inconsistencies.
-Considering both sessions, 1,333 records were manually reviewed and 107
-(8.03\%) confirmed positive matches were found.
-
-Again, the evaluation of the inclusion rate of the terms showed that the
-engine is quite capable of internalising the concepts behind the
-research topic. A subsample of the relevant terms used by the model in
-the second session is reported in Table 2 of Supplemental Material S2.
-
-\hypertarget{hyperparameter-selection}{%
-\subsection{Hyperparameter selection}\label{hyperparameter-selection}}
-
-As described in the methods, hyperparameters were selected by evaluating
-sensibility and efficiency through a grid search on a validation set of
-1,200 manually labelled records. The analysis suggested that the
-following parameter combination performed best: an initial training set
-of 250 categorised records with 10x oversampling of positive matches,
-ten models in the ensemble, no bootstrapping and an uncertainty zone
-defined by the 98\% predictive interval. This combination of parameters
-was associated with a sensitivity of 98.8\% (81 / 82 positive matches
-found) and an efficiency of 61.5\% (462 / 1200 records evaluated). The
-detailed results of the hyperparameter tuning analysis are reported in
-Table 3 of Supplemental Material S2. Fig. 2 in Supplemental Material S2
-demonstrates that the positive record oversampling rate, the number of
-ensemble models and the size of the initial training set were the
-parameters that mainly impacted performance.
-
-\hypertarget{performance-evaluation-1}{%
-\subsection{Performance evaluation}\label{performance-evaluation-1}}
-
-To evaluate the theoretical performance of the engine, a surrogate
-Bayesian logistic regression model was trained on the manually reviewed
-labels using only the lower boundary of the record PPDs as predictor
-(see the Methods for details). The surrogate model showed the high
-predictive power of the scores produced by the classification model
-(Bayesian R2: 98.1\% {[}97.4\%, 98.3\%{]} for session 1 and 98.2\%
-{[}97.6\%, 98.3\%{]} for session 2).\\
-
-Fig. 2 presents the actual and predicted (from the surrogate model)
-cumulative number of positive matches, ordered by the initial simple
-ordering query: the median of surrogate models' cumulative predictive
-distributions matches the actual number of positive records found quite
-well. It is striking how many more records would have required manual
-evaluation to find the same number of positive matches without a
-classification algorithm, with some positive matches found close to the
-end of the heuristically ordered list of records.\\
-
-Table 3 shows various performance indexes for both sessions, both
-descriptive (Total records, Reviewed records, Observed positive matches)
-and estimated through the surrogate model (Expected efficiency,
-Predicted positive matches, Expected sensitivity, \(R^2\)).\\
-In session 1 we observe an expected total number of positives of 101
-{[}101, 108{]} for an estimated sensitivity of 100\% {[}93.5\%, 100\%{]}
-and efficiency of 95.6\% {[}95.3\%, 95.7\%{]}. In session 2 we observed
-a drop in expected sensitivity, especially in the lower credibility
-boundary (97.3\% {[}72.8\%, 100\%{]}): as the number of records
-increases, even a small probability of being a positive match can, in
-the worst-case scenario, lead to a relevant number of predicted positive
-matches (147 in this case). To ensure no obvious positive matches were
-missed, we evaluated 100 non-reviewed records with the highest median
-predicted probability and found no additional positive matches.\\
-
-\begin{table}[!h]
-
+\begin{table}[H]
 \caption{\label{tab:Table 3}\textbf{Table 3}.
@@
 \end{table}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/performance_plot-1.pdf}
-\caption{\textbf{Figure 2}. Observed cumulative number of positive
-matches (red dots) sorted by simple query ordering. The {[}trunc. 90\%
-PrI{]} of the cumulative positive matches estimated by the Bayesian
-logistic model is shown as a shaded area delimited by the 95\% quantile
-of the PrI and by the observed number of positive matches (light blue
-lines). A darker blue line represents the median of the PrI.}
-\end{figure}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-We propose a new integrated framework to help researchers collect and
-screen scientific publications characterised by high performance and
-versatility. This framework joins the joining the growing field of
-systematic review automation (SRA) and helpers (SRH) tools (A. M. Cohen
-et al. 2006, 2010; Ananiadou et al. 2009; O'Mara-Eves et al. 2015). This
-framework implements standard approaches and uses ad-hoc solutions to
-common SRA issues. By freely sharing the tool as an open-source R
-package and by following a modular design, we sought to adopt some of
-the so-called Vienna Principles advocated by the International
-Collaboration for the Automation of Systematic Reviews (ICASR) (E.
-Beller et al. 2018).\\
-The framework consists of four main components: 1) an integrated
-query-based citation search and management engine, 2) a Bayesian active
-machine learning-based citation classifier, and 3) a data-driven search
-query generation algorithm.\\
-
-The search engine module used by the framework can automatically collect
-citation data from three well-known scientific databases (i.e., Pubmed,
-Web of Science, and the Institute of Electrical and Electronics
-Engineers) and process manually downloaded results from two more sources
-(SCOPUS, EMBASE). In comparison, most commercial or free SRH tools rely
-on internal databases (e.g., Mendeley \url{https://www.mendeley.com/})
-sometimes focusing only on a particular topic (Visser 2010) or a single
-external data source (Thomas and Brunton 2007; Poulter et al. 2008;
-Soto, Przybyła, and Ananiadou 2019).\\
-Mixing different databases is essential to obtain a more comprehensive
-view of the literature (Bajpai et al. 2011; Wilkins, Gillies, and Davies
-2005; Woods and Trewheellar 1998): in our results, 18.7\% of the
-positive matches were found in only one of the different data sources,
-and no positive record was present in all the sources (data not
-shown).\\
-The framework online search algorithms are efficient enough to manage
-tens of thousands of search results, using various solutions to overcome
-the limitations of citation databases in terms of traffic and download
-quotas. The results are then automatically organised, deduplicated and
-arranged by ``simple query ordering'' in a uniform corpus. The
-preliminary ordering increases the positivity rate in the initial
-training set (Wallace, Small, et al. 2010).\\
-
-For the framework's record screening module, we developed an active
-machine learning protocol (Settles 2009; Miwa et al. 2014) based on the
-best practices from other SRA studies, bringing further improvements at
-various levels.\\
-The feature extractor module uses modern NLP techniques (Ananiadou and
-McNaught 2006; K. B. Cohen and Hunter 2008) to transform free text into
-input data for machine learning. We did not include classical n-grams
-(Schonlau and Guenther 2017); rather, we used network analysis to find
-non-consecutive, frequently associated terms, a generalisation of
-n-grams that relaxes the term adjacency assumption. This approach can
-also incorporate term connections across different parts of the records,
-e.g., terms having a different relevance when associated with a
-particular author. The same technique was used with different parameters
-to merge redundant terms, increasing estimation efficiency and reducing
-noise.\\
-The use of concurrency network-driven text modelling is not new
-(Francois Rousseau 2015; Violos et al. 2016; François Rousseau, Kiagias,
-and Vazirgiannis 2015; Ohsawa, Benson, and Yachida 1998) and is a
-valuable tool to extract semantic information that is not evident in
-one-word or consecutive n-gram models.\\
-
-The automatic classification algorithm is based on Bayesian Additive
-Regression Trees (BART) (Chipman et al. 2010; Kapelner and Bleich 2013).
-Like other boosted trees algorithms (Hastie, Tibshirani, and Friedman
-2009), the BART method can explore complex non-linearities, perform
-variable selection, manage missing data while maintaining high
-predictive power.\\
-However, the Bayesian foundation of the method provides further
-benefits: lower sensitivity to the choice of hyperparameters, natural
-regularisation through priors, and, most importantly, predictive
-distributions as output instead of point-wise predictions (Soria-Olivas
-et al. 2011; Joo, Chung, and Seo 2020; Jospin et al. 2020). By selecting
-relatively tight prior distributions, we discouraged overly deep trees,
-long tree sequences, and extreme predicted probabilities, thus reducing
-the risk of overfitting.\\
-The algorithm runs multiple replications of the model and averages their
-predictive distributions creating an ``ensemble''; this technique has
-been shown to improve out-of-sample predictive performance (Zhou 2021;
-Dietterich 2000), as confirmed during the hyperparameter evaluation
-(Supplemental Material S2). Ensembling reduces the uncertainty in the
-predictive distribution tails related to the randomness in the MCMC fit
-(Robert and Casella 2004), generating a shift in the probability mass
-towards the distribution centre and stabilising it (i.e., reducing
-variance without impacting bias). On the other hand, simply imposing
-more robust uninformative priors against extreme predictions would have
-reduced variance but also shifted the distribution towards a
-non-decision zone, increasing bias (Hansen et al. 2000).\\
-Since the number of model replications has a significant impact on
-computation times, we decided to use ten replicas, the lower value after
-which performance stabilised, as resulted from the evaluation of the
-hyperparameters (Supplemental Material S2, Fig. 2).\\
-We also investigated whether bootstrapping between replications (Breiman
-1996) would improve performance; however, contrary to theory
-(Díez-Pastor et al. 2015), it appeared to be slightly detrimental in our
-case (Supplemental Material S2, Fig. 2) compared to simple ensembling.\\
-
-A low proportion of relevant matches (class imbalance) is typical for
-literature reviews (Sampson, Tetzlaff, and Urquhart 2011; Wallace,
-Trikalinos, et al. 2010; O'Mara-Eves et al. 2015), and a strong
-imbalance between positive and negative records can affect sensitivity
-(Khoshgoftaar, Van Hulse, and Napolitano 2010; Chawla, Japkowicz, and
-Kotcz 2004).\\
-To overcome this problem, we oversampled (Batista, Prati, and Monard
-2004) the positive records ten times before model fitting. The
-hyperparameter analysis showed that the oversampling rate, together with
-model ensembling, was the parameter with the most significant impact on
-performance.\\
-A known risk with positive oversampling is the misclassification of
-negative records (Ramezankhani et al. 2016). However, since all
-predicted positives in our approach are reviewed manually, we are always
-guaranteed to achieve 100\% specificity/positive predictive value: the
-only price for the increased sensitivity due to oversampling is a larger
-number of records to be reviewed.\\
-An alternative to oversampling would be to apply different weights
-and/or costs to the classes (Abd Elrahman and Abraham 2013; Díez-Pastor
-et al. 2015), but the BART implementation we used did not have this
-feature; furthermore, using simple oversampling allows for a broader
-compatibility with different modelling engines (Galar et al. 2011;
-Roshan and Asadi 2020).\\
-Finally, sorting the records by query term frequency (simple query
-ordering) produces a much higher rate of relevant records in the initial
-training set (17.2\%) compared to the overall data (0.11\%), which
-boosts the sensitivity of the model.\\
-
-One of the key innovations we have introduced is the concept of
-``uncertainty zone'', the implementation of which is possible thanks to
-the Bayesian foundation of the classification model.\\
-This construct guides the selection of records to be manually reviewed
-and gets dynamically updated and reduced after each CR iteration, as
-more uncertain predictions are evaluated (Supplemental Material S2 Fig.
-1).\\
-The use of a dynamic uncertainty zone overcomes the usual requirement of
-dataset-specific hard thresholds in active machine learning and allows
-to review multiple items at once between iterations (Laws and Schütze
-2008; Miwa et al. 2014; Zhu et al. 2010). The hyperparameters required
-by our algorithm are general and non-task-specific, like the PPD
-intervals underlying the uncertainty zone and the maximum number of
-iterations without positive matches after which a session is concluded;
-the evaluation of the classification model hyperparameters shows that
-the algorithm is robust against variations in these parameters, and we
-expect the default values to perform well on most datasets.\\
-Since researchers are asked to review both records predicted as surely
-relevant and those inside the uncertainty zone, this method can be
-considered as a unifying synthesis of the ``certainty'' and
-``uncertainty'' paradigms of active learning (Miwa et al. 2014).\\
-
-We assessed performance as the ability of the screening procedure
-(automatic classification plus manual review) to find the largest number
-of relevant records while requiring manual reviewing for as few of them
-as possible (i.e., sensitivity \(\times\) efficiency).\\
-We avoided the classical out-of-sample approaches such as train-test
-sampling, out-of-bag bootstrapping or cross-validation (Kohavi et al.
-1995; James et al. 2013). Such methods primarily assume that the rate of
-positivity is the same on average in every possible random subset of the
-data (Tashman 2000); this uniformity is broken by how the initial
-training set and the subsequent reviewed records are selected by the
-query-based ordering and active learning algorithm, resulting in a lower
-positivity rate in the unlabelled records (Fig. 2). Moreover, a
-literature corpus is unique per search query/database combination, and
-therefore any out-of-sample performance estimate is not replicable since
-no new data can be acquired related to the current corpus.\\
-To estimate overall sensitivity, we instead applied simple Bayesian
-regression (surrogate model) to the manually reviewed data to abstract
-the classification model predictions and generate a maximum entropy
-(Harremoës and Topsøe 2001) estimate of the number of missed positive
-matches among the unreviewed records in the whole dataset. This simple
-surrogate model fitted the data very well (\(R^2\) consistently above
-97\%) using only the lower 98\% PrI boundary of the PPDs as predictor,
-indicating predictive consistency in the classification model. The
-posterior predictive distribution of the surrogate model could be used
-to explore worse case scenarios in terms of sensitivity.\\
-
-Our framework achieves very high sensitivity by screening only a very
-small fraction of all records, bringing a meaningful reduction in
-workload.\\
-Based on the surrogate model, we predicted a predicted median
-sensitivity of 100\% {[}93.5\%, 100\%{]} in the first session (screening
-4.29\% of records) and of 97.3\% {[}73.8\%, 100\%{]} in the second
-(screening 1.34\% of records): efficiency increased significantly in the
-second session as only a few new positive matches were found; however,
-given the large number of records, uncertainty about sensitivity
-increased, as expected.\\
-Both results are above the usual performance in this field (O'Mara-Eves
-et al. 2015) and are in line with the average sensitivity of 92\%
-estimated after human-only screening (Edwards et al. 2002). In one
-interesting case, the model detected a human-caused misclassification
-error, demonstrating its robustness and value as a second screener, a
-role already suggested for SRA tools in previous studies (Frunza,
-Inkpen, and Matwin 2010; Bekhuis and Demner-Fushman 2012, 2010).
-Although ``simple query ordering'' concentrated most relevant matches in
-the first 20-25 thousand records, without the tool support, the
-remaining relevant records would have been missed without manually
-screening almost the entire dataset.\\
-
-The model required \textasciitilde5-20 minutes per iteration to perform
-the predictions in session 1 (17,755 documents) and 20-40 minutes in
-session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM, 2014
-laptop; including manual record review, one session required 1-3 days of
-work, for a total of 1-2 weeks for the whole process (including record
-collection). This is a considerable time saving compared to the several
-months typically required for the screening phase of systematic reviews
-(Bannach-Brown et al. 2019; Borah et al. 2017; Allen and Olkin 1999). To
-our knowledge, the amount of data processed (\textasciitilde100,000
-records) was larger than what is typical of most SRA studies
-(O'Mara-Eves et al. 2015; Olorisade et al. 2016), highlighting the
-scalability of the tool in real-world scenarios.\\
-
-The last module of our framework is an algorithm for data-driven search
-query generation. Generating an efficient and effective search query is
-a complex task (Lefebvre et al. 2011; Hammerstrøm et al. 2010); it
-requires building a combination of positive and negative terms to
-maximise the number of relevant search results while minimising the
-total number of records to be reviewed. Our solution combines a
-sensitivity-driven subquery proposal engine based on concurrent decision
-trees (Blanco-Justicia and Domingo-Ferrer 2019; Moore et al. 2018) built
-on the BART ensemble PPD, with a human review step and an
-efficiency-driven query builder. The aim is to generate a new search
-query to help find records missed in the first search session. The
-generated query did indeed retrieve a few more relevant records not
-found in session 1 but at the cost of significantly increasing the
-number of documents.\\
-An interesting aspect of this feature is that it provides a
-human-readable overview of the classification rules learned by the
-classification model, showing which combination of terms was
-particularly relevant and even spotting authors and geographical
-locations associated with the study topic. The generated query,
-therefore, served also as a means for machine learning explainability
-(Bhatt et al. 2020; Burkart and Huber 2021), useful for understanding
-and detecting biases in black-box classification algorithms (Malhi,
-Knapic, and Främling 2020); explainability is often required or even
-legally mandatory for high-stake machine learning applications (Bibal et
-al. 2021, 2020).\\
-It is important to note that this process is entirely data-driven. The
-algorithm is only aware of the ``world'' defined by the dataset used as
-input, which is generated by a specific search query focused on a
-particular topic. Therefore, the new query may not be specific enough
-when applied to an unbounded search domain and may return an
-unmanageable amount of irrelevant results. The solution we found was to
-add another component to the query, specifying the general topic
-(antimicrobial resistance and healthcare-associated infections) of our
-research.\\
-
-As mentioned early, our framework builds on modularity. We have designed
-so that each module can become fully independent in future iterations;
-it will be possible for users to add custom features such as citation
-search and parsing for other scientific databases, alternative text
-processing algorithms or machine learning modules. We consider such
-interoperability to be extremely relevant: the main strength of our tool
-lies in the composition of many independent solutions, such as the idea
-of Bayesian active machine learning and the exploit of the derived
-uncertainty in defining the records needing human review.\\
-Each component could benefit considerably from the recent improvements
-in text mining and machine learning.\\
-For example, the text processing approach based on the ``boolean
-bag-of-words'' paradigm is quite simple and could be improved by more
-nuanced text representations. It might be considered whether feature
-transformations such as TF-IDF (Baeza-Yates, Ribeiro-Neto, et al. 1999;
-Ananiadou and McNaught 2006) could be advantageous, although we
-hypothesise that tree-based classification algorithms like BART are
-robust enough not to require such operations. Instead, it might be worth
-exploring the application of word embedding: this technique transforms
-terms into semantic vectors derived from the surrounding text (Turian,
-Ratinov, and Bengio 2010; Bollegala, Maehara, and Kawarabayashi 2015;
-Minaee et al. 2021) and could be used to reduce noise by merging
-different terms that are semantically similar or enhance signal by
-distinguishing identical terms with different meaning given the context.
-Another option would be to employ unsupervised learning models like
-Latent Dirichlet Analysis and Latent Semantic Analysis, (Pavlinek and
-Podgorelec 2017; Q. Chen, Yao, and Yang 2016; Landauer, Foltz, and Laham
-1998) or graph-of-word techniques (Ohsawa, Benson, and Yachida 1998;
-Francois Rousseau 2015) to extract topics that expand the feature
-space.\\
-Our classification algorithm is applicable with any Bayesian supervised
-machine learning method that provides full PPDs; therefore, alternative
-classification models, such as Gaussian Processes, known for their
-flexibility (Jayashree and Srijith 2020; S.-H. Chen et al. 2015), could
-be evaluated. It would be even more interesting to test advanced
-learning algorithms that go beyond the bag-of-words approach and take
-into consideration higher-level features in the text such as term
-context and sequences, long-distance term relationships, semantic
-structures, etc., (Cheng et al. 2019; Minaee et al. 2021; Li et al.
-2020; J. Yang, Bai, and Guo 2020; Lai et al. 2015; Farkas 1995),
-provided that a Bayesian implementation of such algorithms is available
-(for example C. Chen, Lin, and Terejanu (2018)).\\
-Finally, a natural improvement would be to provide a graphical user
-interface to make the framework easy to use also for less technical
-users.
-
-The field of literature review automation is evolving rapidly, and we
-anticipate an increasing use of such technologies to address the
-accelerating pace of scientific production. We believe it is encouraging
-that a wide variety of tools are being made available to let researchers
-and policymakers find the approach that best fits their needs.\\
-We contribute to this field with an innovative framework that provides
-excellent performance and easy integration with existing systematic
-review pipelines. The value of this work lies not only in the framework
-itself, which we make available as open-source software, but also in the
-set of methodologies we developed to solve various SRA issues and which
-can also be used to improve existing solutions.\\
-
-\newpage
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abd2013review}{}}%
-Abd Elrahman, Shaza M, and Ajith Abraham. 2013. {`A Review of Class
-Imbalance Problem'}. \emph{Journal of Network and Innovative Computing}
-1 (2013): 332--40.
-
-\leavevmode\vadjust pre{\hypertarget{ref-allen1999estimating}{}}%
-Allen, I Elaine, and Ingram Olkin. 1999. {`Estimating Time to Conduct a
-Meta-Analysis from Number of Citations Retrieved'}. \emph{Jama} 282 (7):
-634--35.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ananiadou2006text}{}}%
-Ananiadou, Sophia, and John McNaught. 2006. \emph{Text Mining for
-Biology and Biomedicine}. Citeseer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ananiadou2009supporting}{}}%
-Ananiadou, Sophia, Brian Rea, Naoaki Okazaki, Rob Procter, and James
-Thomas. 2009. {`Supporting Systematic Reviews Using Text Mining'}.
-\emph{Social Science Computer Review} 27 (4): 509--23.
-
-\leavevmode\vadjust pre{\hypertarget{ref-aviv2021publication}{}}%
-Aviv-Reuven, Shir, and Ariel Rosenfeld. 2021. {`Publication Patterns'
-Changes Due to the COVID-19 Pandemic: A Longitudinal and Short-Term
-Scientometric Analysis'}. \emph{Scientometrics}, 1--24.
-
-\leavevmode\vadjust pre{\hypertarget{ref-babar2009systematic}{}}%
-Babar, Muhammad Ali, and He Zhang. 2009. {`Systematic Literature Reviews
-in Software Engineering: Preliminary Results from Interviews with
-Researchers'}. In \emph{2009 3rd International Symposium on Empirical
-Software Engineering and Measurement}, 346--55. IEEE.
-
-\leavevmode\vadjust pre{\hypertarget{ref-baeza1999modern}{}}%
-Baeza-Yates, Ricardo, Berthier Ribeiro-Neto, et al. 1999. \emph{Modern
-Information Retrieval}. Vol. 463. ACM press New York.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bajpai2011search}{}}%
-Bajpai, Akhilesh, Sravanthi Davuluri, Haritha Haridas, Greta Kasliwal, H
-Deepti, KS Sreelakshmi, Darshan Chandrashekar, et al. 2011. {`In Search
-of the Right Literature Search Engine (s)'}. \emph{Nature Precedings},
-1--1.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bannach2019machine}{}}%
-Bannach-Brown, Alexandra, Piotr Przybyła, James Thomas, Andrew SC Rice,
-Sophia Ananiadou, Jing Liao, and Malcolm Robert Macleod. 2019. {`Machine
-Learning Algorithms for Systematic Review: Reducing Workload in a
-Preclinical Review of Animal Studies and Reducing Human Screening
-Error'}. \emph{Systematic Reviews} 8 (1): 1--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bastian2010seventy}{}}%
-Bastian, Hilda, Paul Glasziou, and Iain Chalmers. 2010. {`Seventy-Five
-Trials and Eleven Systematic Reviews a Day: How Will We Ever Keep Up?'}.
-\emph{PLoS Medicine} 7 (9): e1000326.
-
-\leavevmode\vadjust pre{\hypertarget{ref-batista2004study}{}}%
-Batista, Gustavo EAPA, Ronaldo C Prati, and Maria Carolina Monard. 2004.
-{`A Study of the Behavior of Several Methods for Balancing Machine
-Learning Training Data'}. \emph{ACM SIGKDD Explorations Newsletter} 6
-(1): 20--29.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bekhuis2010towards}{}}%
-Bekhuis, Tanja, and Dina Demner-Fushman. 2010. {`Towards Automating the
-Initial Screening Phase of a Systematic Review'}. \emph{MEDINFO 2010},
-146--50.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bekhuis2012screening}{}}%
----------. 2012. {`Screening Nonrandomized Studies for Medical
-Systematic Reviews: A Comparative Study of Classifiers'}.
-\emph{Artificial Intelligence in Medicine} 55 (3): 197--207.
-
-\leavevmode\vadjust pre{\hypertarget{ref-beller2013systematic}{}}%
-Beller, Elaine M, Joyce Kee-Hsin Chen, Una Li-Hsiang Wang, and Paul P
-Glasziou. 2013. {`Are Systematic Reviews up-to-Date at the Time of
-Publication?'}. \emph{Systematic Reviews} 2 (1): 1--6.
-
-\leavevmode\vadjust pre{\hypertarget{ref-beller2018making}{}}%
-Beller, Elaine, Justin Clark, Guy Tsafnat, Clive Adams, Heinz Diehl,
-Hans Lund, Mourad Ouzzani, et al. 2018. {`Making Progress with the
-Automation of Systematic Reviews: Principles of the International
-Collaboration for the Automation of Systematic Reviews (ICASR)'}.
-\emph{Systematic Reviews} 7 (1): 1--7.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhatt2020machine}{}}%
-Bhatt, Umang, McKane Andrus, Adrian Weller, and Alice Xiang. 2020.
-{`Machine Learning Explainability for External Stakeholders'}.
-\emph{arXiv Preprint arXiv:2007.05408}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bibal2021legal}{}}%
-Bibal, Adrien, Michael Lognoul, Alexandre De Streel, and Benoît Frénay.
-2021. {`Legal Requirements on Explainability in Machine Learning'}.
-\emph{Artificial Intelligence and Law} 29 (2): 149--69.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bibal2020impact}{}}%
-Bibal, Adrien, Michael Lognoul, Alexandre de Streel, and Benoît Frénay.
-2020. {`Impact of Legal Requirements on Explainability in Machine
-Learning'}. \emph{arXiv Preprint arXiv:2007.05479}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-blanco2019machine}{}}%
-Blanco-Justicia, Alberto, and Josep Domingo-Ferrer. 2019. {`Machine
-Learning Explainability Through Comprehensible Decision Trees'}. In
-\emph{International Cross-Domain Conference for Machine Learning and
-Knowledge Extraction}, 15--26. Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bollegala2015embedding}{}}%
-Bollegala, Danushka, Takanori Maehara, and Ken-ichi Kawarabayashi. 2015.
-{`Embedding Semantic Relations into Word Representations'}. In
-\emph{Twenty-Fourth International Joint Conference on Artificial
-Intelligence}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-borah2017analysis}{}}%
-Borah, Rohit, Andrew W Brown, Patrice L Capers, and Kathryn A Kaiser.
-2017. {`Analysis of the Time and Workers Needed to Conduct Systematic
-Reviews of Medical Interventions Using Data from the PROSPERO
-Registry'}. \emph{BMJ Open} 7 (2): e012545.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bornmann2015growth}{}}%
-Bornmann, Lutz, and Rüdiger Mutz. 2015. {`Growth Rates of Modern
-Science: A Bibliometric Analysis Based on the Number of Publications and
-Cited References'}. \emph{Journal of the Association for Information
-Science and Technology} 66 (11): 2215--22.
-
-\leavevmode\vadjust pre{\hypertarget{ref-breiman1996bagging}{}}%
-Breiman, Leo. 1996. {`Bagging Predictors'}. \emph{Machine Learning} 24
-(2): 123--40.
-
-\leavevmode\vadjust pre{\hypertarget{ref-burkart2021survey}{}}%
-Burkart, Nadia, and Marco F Huber. 2021. {`A Survey on the
-Explainability of Supervised Machine Learning'}. \emph{Journal of
-Artificial Intelligence Research} 70: 245--317.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chae1993presenting}{}}%
-Chae, Kyung-Chul. 1993. {`Presenting the Negative Hypergeometric
-Distribution to the Introductory Statistics Courses'}.
-\emph{International Journal of Mathematical Education in Science and
-Technology} 24 (4): 523--26.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chawla2004special}{}}%
-Chawla, Nitesh V, Nathalie Japkowicz, and Aleksander Kotcz. 2004.
-{`Special Issue on Learning from Imbalanced Data Sets'}. \emph{ACM
-SIGKDD Explorations Newsletter} 6 (1): 1--6.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chen2018approximate}{}}%
-Chen, Chao, Xiao Lin, and Gabriel Terejanu. 2018. {`An Approximate
-Bayesian Long Short-Term Memory Algorithm for Outlier Detection'}. In
-\emph{2018 24th International Conference on Pattern Recognition (ICPR)},
-201--6. IEEE.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chen2016short}{}}%
-Chen, Qiuxing, Lixiu Yao, and Jie Yang. 2016. {`Short Text
-Classification Based on LDA Topic Model'}. In \emph{2016 International
-Conference on Audio, Language and Image Processing (ICALIP)}, 749--53.
-IEEE.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chen2015gaussian}{}}%
-Chen, Sih-Huei, Yuan-Shan Lee, Tzu-Chiang Tai, and Jia-Ching Wang. 2015.
-{`Gaussian Process Based Text Categorization for Healthy Information'}.
-In \emph{2015 International Conference on Orange Technologies (ICOT)},
-30--33. \url{https://doi.org/10.1109/ICOT.2015.7498487}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cheng2019document}{}}%
-Cheng, Y, Z Ye, M Wang, and Q Zhang. 2019. {`Document Classification
-Based on Convolutional Neural Network and Hierarchical Attention
-Network'}. \emph{Neural Network World} 29 (2): 83--98.
-
-\leavevmode\vadjust pre{\hypertarget{ref-chipman2010bart}{}}%
-Chipman, Hugh A, Edward I George, Robert E McCulloch, et al. 2010.
-{`BART: Bayesian Additive Regression Trees'}. \emph{The Annals of
-Applied Statistics} 4 (1): 266--98.
-
-\leavevmode\vadjust pre{\hypertarget{ref-claesen2015hyperparameter}{}}%
-Claesen, Marc, and Bart De Moor. 2015. {`Hyperparameter Search in
-Machine Learning'}. \emph{arXiv Preprint arXiv:1502.02127}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cohen2010evidence}{}}%
-Cohen, Aaron M, Clive E Adams, John M Davis, Clement Yu, Philip S Yu,
-Weiyi Meng, Lorna Duggan, Marian McDonagh, and Neil R Smalheiser. 2010.
-{`Evidence-Based Medicine, the Essential Role of Systematic Reviews, and
-the Need for Automated Text Mining Tools'}. In \emph{Proceedings of the
-1st ACM International Health Informatics Symposium}, 376--80.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cohen2006reducing}{}}%
-Cohen, Aaron M, William R Hersh, Kim Peterson, and Po-Yin Yen. 2006.
-{`Reducing Workload in Systematic Review Preparation Using Automated
-Citation Classification'}. \emph{Journal of the American Medical
-Informatics Association} 13 (2): 206--19.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cohen2008getting}{}}%
-Cohen, K Bretonnel, and Lawrence Hunter. 2008. {`Getting Started in Text
-Mining'}. \emph{PLoS Computational Biology} 4 (1): e20.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dietterich2000ensemble}{}}%
-Dietterich, Thomas G. 2000. {`Ensemble Methods in Machine Learning'}. In
-\emph{International Workshop on Multiple Classifier Systems}, 1--15.
-Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-diez2015diversity}{}}%
-Díez-Pastor, José F, Juan J Rodríguez, César I García-Osorio, and
-Ludmila I Kuncheva. 2015. {`Diversity Techniques Improve the Performance
-of the Best Imbalance Learning Ensembles'}. \emph{Information Sciences}
-325: 98--117.
-
-\leavevmode\vadjust pre{\hypertarget{ref-edwards2002identification}{}}%
-Edwards, Phil, Mike Clarke, Carolyn DiGuiseppi, Sarah Pratap, Ian
-Roberts, and Reinhard Wentz. 2002. {`Identification of Randomized
-Controlled Trials in Systematic Reviews: Accuracy and Reliability of
-Screening Records'}. \emph{Statistics in Medicine} 21 (11): 1635--40.
-
-\leavevmode\vadjust pre{\hypertarget{ref-eppstein2010listing}{}}%
-Eppstein, David, Maarten Löffler, and Darren Strash. 2010. {`Listing All
-Maximal Cliques in Sparse Graphs in Near-Optimal Time'}. In
-\emph{International Symposium on Algorithms and Computation}, 403--14.
-Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-farkas1995document}{}}%
-Farkas, Jennifer. 1995. {`Document Classification and Recurrent Neural
-Networks'}. In \emph{Proceedings of the 1995 Conference of the Centre
-for Advanced Studies on Collaborative Research}, 21.
-
-\leavevmode\vadjust pre{\hypertarget{ref-frunza2010building}{}}%
-Frunza, Oana, Diana Inkpen, and Stan Matwin. 2010. {`Building Systematic
-Reviews Using Automatic Text Classification Techniques'}. In
-\emph{Coling 2010: Posters}, 303--11.
-
-\leavevmode\vadjust pre{\hypertarget{ref-galar2011review}{}}%
-Galar, Mikel, Alberto Fernandez, Edurne Barrenechea, Humberto Bustince,
-and Francisco Herrera. 2011. {`A Review on Ensembles for the Class
-Imbalance Problem: Bagging-, Boosting-, and Hybrid-Based Approaches'}.
-\emph{IEEE Transactions on Systems, Man, and Cybernetics, Part C
-(Applications and Reviews)} 42 (4): 463--84.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gelman2019r}{}}%
-Gelman, Andrew, Ben Goodrich, Jonah Gabry, and Aki Vehtari. 2019.
-{`R-Squared for Bayesian Regression Models'}. \emph{The American
-Statistician}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hammerstrom2010searching}{}}%
-Hammerstrøm, Karianne, Anne Wade, Anne-Marie Klint Jørgensen, and
-Karianne Hammerstrøm. 2010. {`Searching for Studies'}. \emph{Education}
-54 (11.3).
-
-\leavevmode\vadjust pre{\hypertarget{ref-hansen2000bayesian}{}}%
-Hansen, Lars Kai et al. 2000. {`Bayesian Averaging Is Well-Temperated'}.
-In \emph{Proceedings of NIPS}, 99:265--71.
-
-\leavevmode\vadjust pre{\hypertarget{ref-harremoes2001maximum}{}}%
-Harremoës, Peter, and Flemming Topsøe. 2001. {`Maximum Entropy
-Fundamentals'}. \emph{Entropy} 3 (3): 191--226.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hastie2009boosting}{}}%
-Hastie, Trevor, Robert Tibshirani, and Jerome Friedman. 2009. {`Boosting
-and Additive Trees'}. In \emph{The Elements of Statistical Learning},
-337--87. Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-higgins2019cochrane}{}}%
-Higgins, Julian PT, James Thomas, Jacqueline Chandler, Miranda Cumpston,
-Tianjing Li, Matthew J Page, and Vivian A Welch. 2019. \emph{Cochrane
-Handbook for Systematic Reviews of Interventions}. John Wiley \& Sons.
-
-\leavevmode\vadjust pre{\hypertarget{ref-horbach2020pandemic}{}}%
-Horbach, Serge PJM. 2020. {`Pandemic Publishing: Medical Journals
-Strongly Speed up Their Publication Process for COVID-19'}.
-\emph{Quantitative Science Studies} 1 (3): 1056--67.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hoy2020rise}{}}%
-Hoy, Matthew B. 2020. {`Rise of the Rxivs: How Preprint Servers Are
-Changing the Publishing Process'}. \emph{Medical Reference Services
-Quarterly} 39 (1): 84--89.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ikonomakis2005text}{}}%
-Ikonomakis, M, Sotiris Kotsiantis, and V Tampakas. 2005. {`Text
-Classification Using Machine Learning Techniques'}. \emph{WSEAS
-Transactions on Computers} 4 (8): 966--74.
-
-\leavevmode\vadjust pre{\hypertarget{ref-james2013introduction}{}}%
-James, Gareth, Daniela Witten, Trevor Hastie, and Robert Tibshirani.
-2013. \emph{An Introduction to Statistical Learning}. Vol. 112.
-Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jayashree2020evaluation}{}}%
-Jayashree, P, and PK Srijith. 2020. {`Evaluation of Deep Gaussian
-Processes for Text Classification'}. In \emph{Proceedings of the 12th
-Language Resources and Evaluation Conference}, 1485--91.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jonnalagadda2015automating}{}}%
-Jonnalagadda, Siddhartha R, Pawan Goyal, and Mark D Huffman. 2015.
-{`Automating Data Extraction in Systematic Reviews: A Systematic
-Review'}. \emph{Systematic Reviews} 4 (1): 1--16.
-
-\leavevmode\vadjust pre{\hypertarget{ref-joo2020being}{}}%
-Joo, Taejong, Uijung Chung, and Min-Gwan Seo. 2020. {`Being Bayesian
-about Categorical Probability'}. In \emph{International Conference on
-Machine Learning}, 4950--61. PMLR.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jospin2020hands}{}}%
-Jospin, Laurent Valentin, Wray Buntine, Farid Boussaid, Hamid Laga, and
-Mohammed Bennamoun. 2020. {`Hands-on Bayesian Neural Networks--a
-Tutorial for Deep Learning Users'}. \emph{arXiv Preprint
-arXiv:2007.06823}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kapelner2013bartmachine}{}}%
-Kapelner, Adam, and Justin Bleich. 2013. {`bartMachine: Machine Learning
-with Bayesian Additive Regression Trees'}. \emph{arXiv Preprint
-arXiv:1312.2171}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kapelner2015prediction}{}}%
----------. 2015. {`Prediction with Missing Data via Bayesian Additive
-Regression Trees'}. \emph{Canadian Journal of Statistics} 43 (2):
-224--39.
-
-\leavevmode\vadjust pre{\hypertarget{ref-khoshgoftaar2010comparing}{}}%
-Khoshgoftaar, Taghi M, Jason Van Hulse, and Amri Napolitano. 2010.
-{`Comparing Boosting and Bagging Techniques with Noisy and Imbalanced
-Data'}. \emph{IEEE Transactions on Systems, Man, and Cybernetics-Part A:
-Systems and Humans} 41 (3): 552--68.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kohavi1995study}{}}%
-Kohavi, Ron et al. 1995. {`A Study of Cross-Validation and Bootstrap for
-Accuracy Estimation and Model Selection'}. In \emph{Ijcai}, 14:1137--45.
-2. Montreal, Canada.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lai2015recurrent}{}}%
-Lai, Siwei, Liheng Xu, Kang Liu, and Jun Zhao. 2015. {`Recurrent
-Convolutional Neural Networks for Text Classification'}. In
-\emph{Twenty-Ninth AAAI Conference on Artificial Intelligence}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-landauer1998introduction}{}}%
-Landauer, Thomas K, Peter W Foltz, and Darrell Laham. 1998. {`An
-Introduction to Latent Semantic Analysis'}. \emph{Discourse Processes}
-25 (2-3): 259--84.
-
-\leavevmode\vadjust pre{\hypertarget{ref-larsen2010rate}{}}%
-Larsen, Peder, and Markus Von Ins. 2010. {`The Rate of Growth in
-Scientific Publication and the Decline in Coverage Provided by Science
-Citation Index'}. \emph{Scientometrics} 84 (3): 575--603.
-
-\leavevmode\vadjust pre{\hypertarget{ref-laws2008stopping}{}}%
-Laws, Florian, and Hinrich Schütze. 2008. {`Stopping Criteria for Active
-Learning of Named Entity Recognition'}. In \emph{Proceedings of the 22nd
-International Conference on Computational Linguistics (Coling 2008)},
-465--72.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lefebvre2011searching}{}}%
-Lefebvre, C, E Manheimer, J Glanville, J Higgins, and S Green. 2011.
-{`Searching for Studies (Chapter 6)'}. \emph{Cochrane Handbook for
-Systematic Reviews of Interventions Version} 510.
-
-\leavevmode\vadjust pre{\hypertarget{ref-li2020survey}{}}%
-Li, Qian, Hao Peng, Jianxin Li, Congying Xia, Renyu Yang, Lichao Sun,
-Philip S Yu, and Lifang He. 2020. {`A Survey on Text Classification:
-From Shallow to Deep Learning'}. \emph{arXiv Preprint arXiv:2008.00364}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lipscomb2000medical}{}}%
-Lipscomb, Carolyn E. 2000. {`Medical Subject Headings (MeSH)'}.
-\emph{Bulletin of the Medical Library Association} 88 (3): 265.
-
-\leavevmode\vadjust pre{\hypertarget{ref-malhi2020explainable}{}}%
-Malhi, Avleen, Samanta Knapic, and Kary Främling. 2020. {`Explainable
-Agents for Less Bias in Human-Agent Decision Making'}. In
-\emph{International Workshop on Explainable, Transparent Autonomous
-Agents and Multi-Agent Systems}, 129--46. Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-marshall2015systematic}{}}%
-Marshall, Iain J, and Byron C Wallace. 2019. {`Toward Systematic Review
-Automation: A Practical Guide to Using Machine Learning Tools in
-Research Synthesis'}. In \emph{Systematic Reviews}, 8:1--10. 1.
-Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-minaee2021deep}{}}%
-Minaee, Shervin, Nal Kalchbrenner, Erik Cambria, Narjes Nikzad, Meysam
-Chenaghlu, and Jianfeng Gao. 2021. {`Deep Learning--Based Text
-Classification: A Comprehensive Review'}. \emph{ACM Computing Surveys
-(CSUR)} 54 (3): 1--40.
-
-\leavevmode\vadjust pre{\hypertarget{ref-miwa2014reducing}{}}%
-Miwa, Makoto, James Thomas, Alison O'Mara-Eves, and Sophia Ananiadou.
-2014. {`Reducing Systematic Review Workload Through Certainty-Based
-Screening'}. \emph{Journal of Biomedical Informatics} 51: 242--53.
-
-\leavevmode\vadjust pre{\hypertarget{ref-moore2018transparent}{}}%
-Moore, Alexander, Vanessa Murdock, Yaxiong Cai, and Kristine Jones.
-2018. {`Transparent Tree Ensembles'}. In \emph{The 41st International
-ACM SIGIR Conference on Research \& Development in Information
-Retrieval}, 1241--44.
-
-\leavevmode\vadjust pre{\hypertarget{ref-pubmedUpdate}{}}%
-{`NCBI Insights : Updated Pubmed e-Utilities Coming in April 2022!'}.
-n.d. U.S. National Library of Medicine.
-\url{https://ncbiinsights.ncbi.nlm.nih.gov/2021/10/05/updated-pubmed-api/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-o2015using}{}}%
-O'Mara-Eves, Alison, James Thomas, John McNaught, Makoto Miwa, and
-Sophia Ananiadou. 2015. {`Using Text Mining for Study Identification in
-Systematic Reviews: A Systematic Review of Current Approaches'}.
-\emph{Systematic Reviews} 4 (1): 1--22.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ohsawa1998keygraph}{}}%
-Ohsawa, Yukio, Nels E Benson, and Masahiko Yachida. 1998. {`KeyGraph:
-Automatic Indexing by Co-Occurrence Graph Based on Building Construction
-Metaphor'}. In \emph{Proceedings IEEE International Forum on Research
-and Technology Advances in Digital Libraries-ADL'98-}, 12--18. IEEE.
-
-\leavevmode\vadjust pre{\hypertarget{ref-olorisade2016critical}{}}%
-Olorisade, Babatunde K, Ed de Quincey, Pearl Brereton, and Peter Andras.
-2016. {`A Critical Analysis of Studies That Address the Use of Text
-Mining for Citation Screening in Systematic Reviews'}. In
-\emph{Proceedings of the 20th International Conference on Evaluation and
-Assessment in Software Engineering}, 1--11.
-
-\leavevmode\vadjust pre{\hypertarget{ref-pavlinek2017text}{}}%
-Pavlinek, Miha, and Vili Podgorelec. 2017. {`Text Classification Method
-Based on Self-Training and LDA Topic Models'}. \emph{Expert Systems with
-Applications} 80: 83--93.
-
-\leavevmode\vadjust pre{\hypertarget{ref-poulter2008mscanner}{}}%
-Poulter, Graham L, Daniel L Rubin, Russ B Altman, and Cathal Seoighe.
-2008. {`MScanner: A Classifier for Retrieving Medline Citations'}.
-\emph{BMC Bioinformatics} 9 (1): 1--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rstat}{}}%
-R Core Team. 2020. \emph{R: A Language and Environment for Statistical
-Computing}. Vienna, Austria: R Foundation for Statistical Computing.
-\url{https://www.R-project.org/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ramezankhani2016impact}{}}%
-Ramezankhani, Azra, Omid Pournik, Jamal Shahrabi, Fereidoun Azizi,
-Farzad Hadaegh, and Davood Khalili. 2016. {`The Impact of Oversampling
-with SMOTE on the Performance of 3 Classifiers in Prediction of Type 2
-Diabetes'}. \emph{Medical Decision Making} 36 (1): 137--44.
-
-\leavevmode\vadjust pre{\hypertarget{ref-robert2004monte}{}}%
-Robert, Christian P, and George Casella. 2004. \emph{Monte Carlo
-Statistical Methods}. Vol. 2. Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-roshan2020improvement}{}}%
-Roshan, Seyed Ehsan, and Shahrokh Asadi. 2020. {`Improvement of Bagging
-Performance for Classification of Imbalanced Datasets Using Evolutionary
-Multi-Objective Optimization'}. \emph{Engineering Applications of
-Artificial Intelligence} 87: 103319.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rousseau2015graph}{}}%
-Rousseau, Francois. 2015. {`Graph-of-Words: Mining and Retrieving Text
-with Networks of Features'}. PhD thesis, Ph. D. dissertation.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rousseau2015text}{}}%
-Rousseau, François, Emmanouil Kiagias, and Michalis Vazirgiannis. 2015.
-{`Text Categorization as a Graph Classification Problem'}. In
-\emph{Proceedings of the 53rd Annual Meeting of the Association for
-Computational Linguistics and the 7th International Joint Conference on
-Natural Language Processing (Volume 1: Long Papers)}, 1702--12.
-
-\leavevmode\vadjust pre{\hypertarget{ref-newis}{}}%
-Sadaghiani, Catharina, Tjibbe Donker, Xanthi Andrianou, Balázs Babarczy,
-Gerolf De Boer, Francesco Di Ruscio, Shona Cairns, et al. 2020.
-\emph{National Health Care Infrastructures, Health Care Utilization and
-Patient Movements Between Hospitals - Networks Working to Improve
-Surveillance: A Systematic Literature Review}. PROSPERO.
-\url{http://www.crd.york.ac.uk/PROSPERO/display_record.asp?ID=CRD42020157987}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sampson2011precision}{}}%
-Sampson, Margaret, Jennifer Tetzlaff, and Christine Urquhart. 2011.
-{`Precision of Healthcare Systematic Review Searches in a
-Cross-Sectional Sample'}. \emph{Research Synthesis Methods} 2 (2):
-119--25.
-
-\leavevmode\vadjust pre{\hypertarget{ref-schonlau2017text}{}}%
-Schonlau, Matthias, and Nick Guenther. 2017. {`Text Mining Using
-n-Grams'}. \emph{Schonlau, M., Guenther, N. Sucholutsky, I. Text Mining
-Using n-Gram Variables. The Stata Journal} 17 (4): 866--81.
-
-\leavevmode\vadjust pre{\hypertarget{ref-settles2009active}{}}%
-Settles, Burr. 2009. {`Active Learning Literature Survey'}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-soria2011belm}{}}%
-Soria-Olivas, Emilio, Juan Gomez-Sanchis, José D Martin, Joan
-Vila-Frances, Marcelino Martinez, José R Magdalena, and Antonio J
-Serrano. 2011. {`BELM: Bayesian Extreme Learning Machine'}. \emph{IEEE
-Transactions on Neural Networks} 22 (3): 505--9.
-
-\leavevmode\vadjust pre{\hypertarget{ref-soto2019thalia}{}}%
-Soto, Axel J, Piotr Przybyła, and Sophia Ananiadou. 2019. {`Thalia:
-Semantic Search Engine for Biomedical Abstracts'}. \emph{Bioinformatics}
-35 (10): 1799--1801.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tashman2000out}{}}%
-Tashman, Leonard J. 2000. {`Out-of-Sample Tests of Forecasting Accuracy:
-An Analysis and Review'}. \emph{International Journal of Forecasting} 16
-(4): 437--50.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rpart}{}}%
-Therneau, Terry, and Beth Atkinson. 2019. \emph{Rpart: Recursive
-Partitioning and Regression Trees}.
-\url{https://CRAN.R-project.org/package=rpart}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-thomas2007eppi}{}}%
-Thomas, James, and Jeff Brunton. 2007. {`EPPI-Reviewer: Software for
-Research Synthesis'}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tsafnat2013automation}{}}%
-Tsafnat, Guy, Adam Dunn, Paul Glasziou, and Enrico Coiera. 2013. {`The
-Automation of Systematic Reviews'}. British Medical Journal Publishing
-Group.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tsafnat2014systematic}{}}%
-Tsafnat, Guy, Paul Glasziou, Miew Keen Choong, Adam Dunn, Filippo
-Galgani, and Enrico Coiera. 2014. {`Systematic Review Automation
-Technologies'}. \emph{Systematic Reviews} 3 (1): 1--15.
-
-\leavevmode\vadjust pre{\hypertarget{ref-turian2010word}{}}%
-Turian, Joseph, Lev Ratinov, and Yoshua Bengio. 2010. {`Word
-Representations: A Simple and General Method for Semi-Supervised
-Learning'}. In \emph{Proceedings of the 48th Annual Meeting of the
-Association for Computational Linguistics}, 384--94.
-
-\leavevmode\vadjust pre{\hypertarget{ref-violos2016sentiment}{}}%
-Violos, John, Konstantinos Tserpes, Evangelos Psomakelis, Konstantinos
-Psychas, and Theodora Varvarigou. 2016. {`Sentiment Analysis Using
-Word-Graphs'}. In \emph{Proceedings of the 6th International Conference
-on Web Intelligence, Mining and Semantics}, 1--9.
-
-\leavevmode\vadjust pre{\hypertarget{ref-visser2010performing}{}}%
-Visser, Eelco. 2010. {`Performing Systematic Literature Reviews with
-Researchr: Tool Demonstration'}. \emph{Technical Report Series
-TUD-SERG-2010-010}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wallace2010active}{}}%
-Wallace, Byron C, Kevin Small, Carla E Brodley, and Thomas A Trikalinos.
-2010. {`Active Learning for Biomedical Citation Screening'}. In
-\emph{Proceedings of the 16th ACM SIGKDD International Conference on
-Knowledge Discovery and Data Mining}, 173--82.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wallace2010semi}{}}%
-Wallace, Byron C, Thomas A Trikalinos, Joseph Lau, Carla Brodley, and
-Christopher H Schmid. 2010. {`Semi-Automated Screening of Biomedical
-Citations for Systematic Reviews'}. \emph{BMC Bioinformatics} 11 (1):
-1--11.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wilkins2005embase}{}}%
-Wilkins, Thad, Ralph A Gillies, and Kathy Davies. 2005. {`EMBASE Versus
-MEDLINE for Family Medicine Searches: Can MEDLINE Searches Find the
-Forest or a Tree?'}. \emph{Canadian Family Physician} 51 (6): 848--49.
-
-\leavevmode\vadjust pre{\hypertarget{ref-woods1998medline}{}}%
-Woods, David, and Kate Trewheellar. 1998. {`Medline and Embase
-Complement Each Other in Literature Searches'}. \emph{BMJ: British
-Medical Journal} 316 (7138): 1166.
-
-\leavevmode\vadjust pre{\hypertarget{ref-yang2020survey}{}}%
-Yang, JinXiong, Liang Bai, and Yanming Guo. 2020. {`A Survey of Text
-Classification Models'}. In \emph{Proceedings of the 2020 2nd
-International Conference on Robotics, Intelligent Control and Artificial
-Intelligence}, 327--34.
-
-\leavevmode\vadjust pre{\hypertarget{ref-yang2020hyperparameter}{}}%
-Yang, Li, and Abdallah Shami. 2020. {`On Hyperparameter Optimization of
-Machine Learning Algorithms: Theory and Practice'}.
-\emph{Neurocomputing} 415: 295--316.
-
-\leavevmode\vadjust pre{\hypertarget{ref-zhou2021ensemble}{}}%
-Zhou, Zhi-Hua. 2021. {`Ensemble Learning'}. In \emph{Machine Learning},
-181--210. Springer.
-
-\leavevmode\vadjust pre{\hypertarget{ref-zhu2010confidence}{}}%
-Zhu, Jingbo, Huizhen Wang, Eduard Hovy, and Matthew Ma. 2010.
-{`Confidence-Based Stopping Criteria for Active Learning for Data
-Annotation'}. \emph{ACM Transactions on Speech and Language Processing
-(TSLP)} 6 (3): 1--24.
-
-\end{CSLReferences}
-
-\bibliographystyle{unsrt}
-\bibliography{references.bib}
-
+	% \begin{table}[h!]
+% \caption{Sample table title. This is where the description of the table should go}
+%   \begin{tabular}{cccc}
+%     \hline
+%     & B1  &B2   & B3\\ \hline
+%     A1 & 0.1 & 0.2 & 0.3\\
+%     A2 & ... & ..  & .\\
+%     A3 & ..  & .   & .\\ \hline
+%   \end{tabular}
+% \end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Additional Files              %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section*{Additional Files}
+  \subsection*{S1. Framework description and usage.}
+  Instruction on how to use the framework and reproduce the results in
+the manuscript.
+  \subsection*{S2. Additional outputs.}
+  Additional analysis outputs described in the manuscript.
+  \subsection*{S3. Online search instructions.}
+  Instructions about how to prepare the framework to interact with the
+online scientific databases to collect records.
+  % \subsection*{Additional file 1 --- Sample additional file title}
+  %   Additional file descriptions text (including details of how to
+  %   view the file, if it is in a non-standard format or the file extension).  This might
+  %   refer to a multi-page table or a figure.
+  %
+  % \subsection*{Additional file 2 --- Sample additional file title}
+  %   Additional file descriptions text.
+
+\end{backmatter}
 \end{document}

### 2022-03-03 Manuscript/Manuscript_Methods.Rmd
prepare BMC submission

@@
 
-We built an R [@rstat] based framework to simplify two aspects of systematic literature review:
+We built an R [@rstats2021] based framework to simplify two aspects of systematic literature review:
 record acquisition and classification.
@@
 
-```{r method_diagram, fig.cap = "Figure 1. Framework's visual representation.", echo = FALSE, out.width = "100%"}
-knitr::include_graphics("methods_diagram.png", auto_pdf = T)
+```{r figure1.method_diagram, fig.cap = "Figure 1. Framework's visual representation.", echo = FALSE, out.width = "100%"}
+knitr::include_graphics(file.path("Figures", "methods_diagram.png"), auto_pdf = T)
 ```
@@
 The framework models the relevance of a record based on the following fields in the citation data:
-title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
+title, abstract, authors, keywords, MeSH terms [@lipscomb2000medical].
 A range of Natural Language Processing (NLP) techniques [@baeza1999modern; @marshall2015systematic; @ananiadou2006text] are employed to convert the textual information in these fields into features for machine learning through a bag-of-words approach [@marshall2015systematic].
 Processing of free text fields (title, abstract) includes: tokenisation (i.e., extracting the terms), removal of common stopwords (i.e., sentence components having no semantic value), part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatisation of terms (i.e., reduction to their base grammatical form).
-Text processing for authors, keywords and MESH terms identifies logical units (e.g., authors' full names, composite keywords) and extracts them.\
+Text processing for authors, keywords and MeSH terms identifies logical units (e.g., authors' full names, composite keywords) and extracts them.\
 Terms appearing in less than 5% of the labelled documents are removed from negative records.
@@
 Positive records are oversampled ten times to increase sensitivity [@batista2004study].\
-The output is a posterior predictive distribution (PPD) for each record describing the probability of it being relevant (i.e., a positive match).
+The output is the expected value posterior predictive distribution for each record (PPD in brief) describing the probability of it being relevant (i.e., a positive match).
 An ensemble of ten models was fitted to improve prediction stability by averaging the PPD between models [@zhou2021ensemble; @dietterich2000ensemble].\
@@
 
-$$\pi_i = \frac{1}{M}\sum_{j=1}^M Pr(L_i = \text{1}|DTM,m_j)$$
+$$\pi_i = \frac{1}{M}\sum_{j=1}^M Pr(L_i = \text{1}|DTM,m_j) \tag{Eq. 1}$$
 
@@
 \end{aligned}
+\tag{Eq. 2}
 $$
@@
 
-$$U_\pi=[\max\vec{\pi}_{u}^-, \min\vec{\pi}_{l}^+]$$
+$$U_\pi=[\max\vec{\pi}_{u}^-, \min\vec{\pi}_{l}^+] \tag{Eq. 3}$$
 
@@
 
-$$\pi_{i,l} > \max_{\pi \in U_\pi} \pi$$
+$$\pi_{i,l} > \max_{\pi \in U_\pi} \pi \tag{Eq. 4}$$
 
@@
 
-$$\pi_{i,u} < \min_{\pi \in U_\pi} \pi$$
+$$\pi_{i,u} < \min_{\pi \in U_\pi} \pi \tag{Eq. 5}$$
 
-All other records are labelled as "uncertain".
+The remaining records are labelled as "uncertain".
 
@@
 if a term is present multiple times in the DTM (e.g., both in the title and abstract), it is counted just once, and field term count features are removed.
-This step generates a list of rules composed by _AND_/_NOT_ "conditions" made of terms/authors/keywords/MESH tokens, which together identify a group of records.
+This step generates a list of rules composed by _AND_/_NOT_ "conditions" made of terms/authors/keywords/MeSH tokens, which together identify a group of records.
 - For each rule, negative conditions (i.e., _NOT_ statements) are added iteratively, starting from the most specific one, until no conditions are found that would not also remove positive records.
@@
 - Number of models in the ensemble: 1, 5, 10, 20, 40, 60 repetitions;
-- Oversampling rate of positive records: (1x (i.e., no oversampling), 10x, 20x;
+- Oversampling rate of positive records: 1x (i.e., no oversampling), 10x, 20x;
 - PrI quantiles for building the uncertainty zone: 80%, 90%, 98%;
@@
 For the rest of the study, we used the best hyperparameter set in terms of sensitivity followed by efficiency from the cluster with the highest average score.\
+
+## Software and data
+The framework is built with R v4.0.4 [@rstats2021].
+The R packages required by the framework are listed at https://github.com/bakaburg1/BaySREn/blob/main/DESCRIPTION.
+All relevant data necessary to replicate the results is available at https://doi.org/10.5281/zenodo.6323360.

### 2022-03-03 Manuscript/Manuscript_Results.Rmd
prepare BMC submission

@@
   cache = TRUE,
+  fig.path = "Figures/",
   cache.rebuild = FALSE
@@
 
-*`r first_query`*
+*`r first_query`*\
 
@@
 We extracted the 15 more relevant terms for the classification model, described as:
-Term (citation part): Inclusion Rate (Inclusion Stability) [linear Relative Risk, Statistic].
+Term (citation part): Inclusion Rate (Inclusion Stability) [linear Relative Risk, Statistic]:\
 
-`r var_importance`.
+`r var_importance`.\
 
@@
 
-*`r new_query`*
+*`r new_query`*\
 
@@
 
-```{r performance_plot, cache = FALSE, fig.width=7.5, fig.height=4.5, fig.cap="**Figure 2**.
+```{r figure2.performance_plot, cache = FALSE, fig.width=7.5, fig.height=4.5, fig.cap="**Figure 2**.
 Observed cumulative number of positive matches (red dots) sorted by simple query ordering.

### 2022-03-03 Manuscript/S1.Framework_description.Rmd
prepare BMC submission

--- 2022-02-19 Manuscript/S1.Protocol.Rmd
@@
 ---
-title: "Study protocol"
+title: "Framework description and usage"
 date: "`r lubridate::today()`"
@@
 
-# Research Protocol
+# Framework usage instructions
 
@@
 
-Add installation and setup info here.
+To use the framework, clone it from https://github.com/AD-Papers-Material/BART_SystReviewClassifier and run the R project in the repository.
 
-## Acquisition of the citaion data
+The first step is loading the code base using:
+
+```{r load_the_code}
+
+source("R/Setup.R") # Load the framework
+
+```
+
+## Acquisition of the citation data
 
@@
 ```{r query_creation}
-
-source("R/Setup.R") # Load the framework
 
@@
 
-- The framework extracts **features** from text data (i.e., title and abstract) of the records, authors, keywords and MESH terms (see Methods for more info).
+- The framework extracts **features** from text data (i.e., title and abstract) of the records, authors, keywords and MeSH terms (see Methods for more info).
 Before features extraction, text data terms are lemmatised, stop-words are removed, and only nouns, adjectives, verbs and untagged terms are retained.
-Authors, keywords, and MESH are kept unmodified.
+Authors, keywords, and MeSH are kept unmodified.
 Co-occurrent features (non-consecutive ngrams, **nc-grams**) are identified and **redundant features** (i.e. terms always appearing together) are joined to decrease the feature space noise.
@@
 - Positive records are oversampled **10x** to improve sensitivity;
-- An extra feature is added for each record field (title, abstract, authors, keywords, MESH terms), reporting the number of terms in each.
+- An extra feature is added for each record field (title, abstract, authors, keywords, MeSH terms), reporting the number of terms in each.
 
@@
 if a term is present multiple times in the DTM (e.g., both title and abstract), they are counted just one, and field term count features are removed.
-This step generates a list of rules composed by $AND$/$NOT$ "conditions" made of terms/authors/keywords/MESH tokens, which together identify a group of records.
+This step generates a list of rules composed by $AND$/$NOT$ "conditions" made of terms/authors/keywords/MeSH tokens, which together identify a group of records.
 - For each rule, negative conditions (i.e., $NOT$ statements) are added iteratively, starting from the most specific one, until no conditions are found that would not also remove positive records.
@@
 $$
-Sensitivity \times Efficiency = \\
+Sensitivity \times Efficiency =
 \frac{Pos.\ found}{Tot.\ pos.} \times \bigg(1 - \frac{Records\ reviewed}{Tot.\ records}\bigg)

### 2023-02-27 Manuscript/Manuscript_Discussion.Rmd
minor changes

@@
 By freely sharing the tool as an open-source R package and by following a modular design, we sought to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
-The framework consists of four main components: 1) an integrated query-based citation search and management engine, 2) a Bayesian active machine learning-based citation classifier, and 3) a data-driven search query generation algorithm.\
+The framework consists of three main components: 1) an integrated query-based citation search and management engine, 2) a Bayesian active machine learning-based citation classifier, and 3) a data-driven search query generation algorithm.\
 
